### 2015-06-25 skeleton.tex
Recent changes, re remove 3C core stuff

\documentclass{emulateapj}
\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{tleung@astro.cornell.edu}
\newcommand{\Msun}{\mbox{$M_{\odot}$}}
\newcommand{\Rsun}{\mbox{R$_{\odot}$}}
\newcommand{\Lsun}{\mbox{L$_{\odot}$}}
\newcommand{\rarr}{$\rightarrow$}
\newcommand{\CO}{\mbox{CO($J$ = 3 $\rightarrow$ 2) }}
\newcommand{\Lp}{\mbox{$L^{\prime}_{\rm CO(1-0)}$}}
\newcommand{\LpU}{\mbox{K km s$^{-1}$ pc$^2$}}
\newcommand{\eg}{{\sl e.g.,~}}
\newcommand{\ie}{{\sl i.e.,~}}
\newcommand{\pmOne}{$^{-1}$}
%\slugcomment{{\sc Accepted to ApJ:} August 1, 2006}
\usepackage{amsmath}
\usepackage{natbib}
\citestyle{aa}
\shorttitle{Study of a strongly lensed type-2 quasar host SMG at $z$ = 2.221}
%\shortauthors{Leung and Riechers}

\begin{document}
\title{\CO observation in a strongly lensed type-2 quasar host SMG at $z$ = 2.221 with
continuum detection in the foreground lensing FR-II radio galaxy at $z$ = 0.685}
\author{No name}
%\author{T. K. Daisy Leung\altaffilmark{1} and Dominik R. Riechers\altaffilmark{2}}
%\affil{Astronomy Department, Cornell Unviersity}
%\altaffiltext{1}{tleung@astro.cornell.edu}
%\altaffiltext{2}{dr@astro.cornell.edu}

\begin{abstract}
We report the detection of \CO line emission in SMM J0939+8315 ($z$ = 2.221), a
strongly lensed high-redshift submillimeter galaxy (SMG) hosting a type-2 quasar using
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). This lensing system consists of a
foreground radio galaxy and a companion galaxy at $z$ = 0.685. A lensing magnification of $\mu_{\rm 1 mm}$ = 9.74 $\pm$ 1.4 amplified the intrinsic luminosities of the CO emission. This allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background quasar host SMG. Prior to correcting for lensing 
amplification, we measure the
velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (14.6 $\pm$ 0.9) Jy km s\pmOne,
corresponding to a lensing-corrected CO($J$ = 1 \rarr 0) line luminosity of \Lp = (4.1 $\pm$ 
0.9) $\times$ 10$^{10}$ \LpU. This
translates to a molecular gas mass of $M_{\rm gas}$ = 3.3 $\times$ 10$^{10}M_\odot$, assuming a conversion
factor of $\alpha_{\rm CO}$ = 0.8 \Msun (\LpU)\pmOne. We report marginally resolved continuum 
emission from the foreground radio galaxy 3C220.3 with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
 at 104 GHz (1.7 mm rest-frame), allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
fit
 both an optically thick and optically thin modified blackbody models to the SED of the SMG using existing
infrared photometric data. Our SED fitting favours an optically thick model, yielding dust mass of $M_{\rm
dust}$ = 50.5$^{20.4}_{-20.2}$ $\times$ 10$^8$\Msun, and total infrared (IR) luminosity of $L$ = 88.5$^{+2.6}
_{-2.6}\times$10$^{12}$\Lsun, prior to lensing correction. We conclude that the properties (\eg gas mass, gas mass 
fraction, SFR) of the molecular gas reservoir in SMM
J0939+8315 based on our \CO observation is similar to other high redshift
SMGs. \\
NEED TO  FIX: 
report SFR, gas-to-dust ratio.. Comparison, etc. 
\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

\section{Introduction}\label{sec:intro}
Submillimeter-selected galaxies (SMGs) are found predominantly at redshift $z \sim$ 1-3, during the epoch of stellar mass and 
galaxy assembly. These galaxies are luminous in submillimeter (submm) due to the re-radiation from the dust components in the
 far-infrared (FIR) wavelengths. Large sky surveys (e.g., HERMES, HATLAS) with submm facilities have lead to growing consensus
  of the observable properties of SMGs. SMGs are a population of galaxy at high redshifts that are typically dusty, gas-rich, 
  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) in infrared with high star formation rates ($\gtrsim $ 500 \Msun yr\pmOne). (e.g., Lagache et al. 2005, cite more recent). \par
  To characterize the properties of the gas reservoirs in the ISM, where active star formation takes place, CO rotational lines have been commonly used as a tracer due to its high abundance in the ISM as well as its low excitation energy, the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep{Carilli13a}. Recent observations of the CO line of SMGs at $z \sim$ 1-3 have  
provided evidence that SMGs have large gas reservoirs typical of \textgreater 10$^{10}$\Msun. In most cases, detailed studies are carried out on SMGs that are gravitationally lensed, the lensing amplification boost the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys (Negrello 10, cite). \par
One of such lens system has a peculiar configuration consisting of a SMG, SMM J0939+8315 (hereafter SMM J0939), hosting a 
type-2 quasar host at $z$ = 2.221 being strongly lensed by a double-lobed Fanaroff-Riley Class II (FR-II) \citep*{Fanaroff74} radio galaxy (3C220.3) which has a 
companion galaxy B at $z$ = 0.685. The two lenses are separated by 1\farcs5. The redshift of the background SMG has 
been measured through the detection of CIV 1459\AA\
 and HeII 1640\AA\
line emissions \citep[hereafter H14]{Haas14}, these line detections provide conceiving evidence of AGN activity in the SMG, as well as the 
existence of a type-2 quasar.
The background SMG has a lensing-magnified flux density of $F_{\rm 250\mu m}$ = 440 $\pm$ 15 mJy, which is one of 
the
brightest known even among lensed
SMGs.

In this paper, we present the detection of \CO line emission obtained with the Combined
Array for Research in Millimeter Astronomy (CARMA) in the background SMG
SMM J0939 at $z$ = 2.221. The underlying radio continuum at 104 GHz allows us to put constraints on the SED of the 
foreground radio galaxy. This paper is organized as follows: in \S \ref{sec:obs}, we describe the
observations of the \CO line emission with CARMA; in \S \ref{sec:res}, we report the
detection of the CO line in the background galaxy as well as the continuum in the foreground galaxy; in \S
\ref{sec:Lens}, we present our lens modeling analysis; in \S \ref{sec:SED}, we perform SED fitting to 3C220.3
and SMM J0939 and derive the intrinsic properties of the interstellar medium (ISM) in the SMG; in \S \ref{sec:conclusions}, we
conclude our findings by comparing to other SMGs at high redshifts.

We adopt a standard $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km Mpc\pmOne
s\pmOne, $\Omega_{\rm M}$ = 0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
The luminosity distances at $z$ = 0.685 and $z$ = 2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
corresponds to 8.406 kpc at $z$ = 2.221, and 7.169 kpc at $z$ = 0.685.

\section{Observations}\label{sec:obs}
\subsection{CARMA} \label{sec:carmadata}
Observations of the \CO rotational transition ($\nu_{rest}$ = 345.7959899 GHz),
redshifted to $\nu_{obs}$ = 107.357 GHz (2.794 mm) towards the background galaxy SMM
J0939+8315 ($z$ = 2.221) were carried out using CARMA (programme ID: cf0142; P.I.: D. Riechers).
We used the 3mm receivers with a bandwidth of 3.75 GHz in each sideband, at 5.208 MHz ($\sim$14.5 km s\pmOne)
resolution to cover the \CO line and the underlying 2.877 mm continuum emission. The CO($J$ = 3 
\rarr 2) line was placed on the
upper sideband with the local oscillator frequency tuned to $\nu_{\rm LO}$ = 104.2609 GHz.
Observations were carried out under good
weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator and the quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The {\sc MIRIAD} package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
the CLEAN algorithm with ``natural" weighting, this yields a synthesized clean beam size of 13$\farcs$57 $\times$ 
5\farcs77 . The final rms noise is $\sigma$ = 0.7 Jy km s\pmOne $\rm beam^{-1}$ over
a channel width of 135.4 MHz (corresponding to $\sim$378.1 km s\pmOne). The continuum image is created by
averaging over all the line-free channels, this yields a synthesized clean beam size of 16\farcs67 $\times$ 7\farcs17 and a 
rms noise of 0.55 mJy beam\pmOne.

% mom0 map channels [72, 85], each channel is 29.088 km/s, i.e. total velocity range is 378.144 km/s, which is 135.408 
%MHz
\section{Results}\label{sec:res}
\subsection{New results: Continuum Emission} 
% So integrated - peak should be approx. the extended components ~ (7.18 - 5.56 mJy)
%      --- Integrated:   7.18 +/- 0.69 mJy
%      --- Peak:         5.56 +/- 0.54 mJy/beam

%Deconvolution size bigger than expected (if just radio core):
%1) phase error that wasn't well calibrated (~30/360 $\times$\appox 16") ~ 1-2"
%2) low SNR giving rise to fitting error ~ 4" from `imfit`
%3) PA beam align with RG (radio galaxy) orientation
Averaging over all the line-free channels, we detect a 10$\sigma$ continuum emission at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz (2.877 mm) in the observed-frame, corresponding to $\sim$2.79 mm at $z$ = 0.658. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum to be dominated by emissions from the foreground galaxy. We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission, the deconvolved source size is 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60, and the integrated flux density is 7.18 $\pm$ 0.69 mJy. At the peak position of the continuum emission, the peak flux density is S$_\nu$ = 5.56 $\pm$ 0.54 
mJy beam\pmOne.
In Figure \ref{fig:cont}, we show the continuum emission at 104 GHz overlaid on the 9 GHz continuum measurement reported by \citet{Haas14}. This figure demonstrates that at the resolution of our observation, the continuum detection is marginally resolved, it is therefore plausible that both non-thermal and thermal emissions from the lobes and the radio core contribute to the integrated flux density in our measurement.

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel}
\caption{The central cross on each image indicates the position of the radio core of 3C220.3. Contour levels of the 9 GHz continuum 
emission start at $\pm$4$\sigma$ of $\sigma$ = 0.0641 mJy beam\pmOne and increment at steps of $\pm$2$^n\sigma$, 
where n is positive integers; contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne.
Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 16\farcs67 $\times$ 7\farcs17, at P.A. = 
-58$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
foreground radio galaxy 3C220.3 overlaid the 9 GHz emission (green) (H14). The rms in the 9GHz image is $\sigma$ 
= 0.0641 mJy beam\pmOne. The synthesized beam size of the VLA observations is 0$\farcs$60 $\times$ 0$\farcs$23 at P.A. 
76$\degr$. 
\label{fig:cont}}
\end{figure*}

\subsection{New results: \CO line emission}
We detect \CO line emission toward the background SMG SMM J0939. Figure \ref{fig:mom0} shows the line profile at the peak position of the CO emission. Fitting a four-parameter single-component Gaussian to the spectrum yields a peak flux density of 19.9 $\pm
$ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy, and FWHM of 541.65 $\pm$ 31.91 km s\pmOne. 
The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, the 
synthesized beam size of the SMA observation is 1\farcs42$ \times $1\farcs16, at P.A. -34.0\degr. As such, the \CO detection in the SMG is spatially unresolved. We construct a velocity-integrated (0th moment) map of the \CO 
emission using the continuum-subtracted data in the visibility plane, this results in velocity-integrated \CO line flux of $S_{\rm CO}$ = 14.6 $\pm$ 0.9 Jy km s\pmOne over a velocity range of $\Delta v$ = $\sim$378.1 km s\pmOne, the uncertainty does not include $\sim$ 15\% calibration uncertainty. We ignore the primary beam correction given that the source is close to the phase center, and that the source is unresolved (\ie much smaller than the primary beam size).

\begin{figure*}[tbph] 
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel}
\includegraphics[width=0.65\textwidth]{Figure/peak28_WiderSpectrum}
\caption{The central cross on each image sets the coordinates for alignment between plots. The contour starts at $\pm$3$\sigma$, 
incrementing at
steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the \CO line emission in 
the background SMG with $\sigma$ = 0.7 Jy km s\pmOne beam\pmOne. The angular resolution is 13$\farcs$57 $\times$ 
5\farcs77, as shown in the bottom left corner. 
Top Right: Contours of \CO emission (red) overlaid on the SMA 1 mm dust continuum (green) with $
\sigma$ = 0.84 mJy beam\pmOne. The beam size of the SMA data is 1\farcs42$ \times $1\farcs16, P.A. -34\degr, as shown 
in the bottom left corner. From this image, it is apparent that the extent of the background SMG is smaller than the beam 
size of the CARMA observations, hence the \CO line detection is spatially unresolved. Bottom: 
The spectrum at the CO emission peak position with spectral resolution of $\Delta v$ $\sim$29.1 km s\pmOne.
Solid black line shows the Gaussian fit to the \CO line profile. Yellow histogram shows the 
flux density as a function of velocity offset, where 0 km/s corresponds to $z$ = 2.221. \label{fig:mom0}}
\end{figure*}

\section{Analysis}
\subsection{Lens Modelling} \label{sec:Lens} 
To study the intrinsic properties of the background galaxy, we determine the magnification factor by performing
lens modeling using the SMA 1 mm archival data of this system. The lens modeling is carried out in the visibility
(uv-) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}
\citep{Bussmann15a}. The code uses affine-invariant Markov chain Monte Carlo (MCMC) to sample the posterior
probability density function (PDF) of the model parameters. In our lens model, the surface mass densities of both
lenses are represented by singular isothermal ellipsoid (SIE) profiles, and the source is assumed to have an
elliptical Gaussian profile. The code does not include an external shear parameter. \newline
We fix the phase center to coordinates ($\alpha$, $\delta$) (J2000) = (144.84809\degr, 83.25725\degr), the
offset positions of the lenses and source are referenced to this phase center. The primary lens (3C220.3) is
described by 5 free parameters: the angular offset relative to
the chosen phase center in the image ($\Delta \alpha_{\rm
lens0}$ and $\Delta \delta_{\rm lens0}$), the angular Einstein radius ($\theta_{\rm E,0}$), the
axial ratio ($q_{\rm lens0}$), and the position angle ($\phi_{\rm lens0}$). The secondary lens (companion B) is
described by 3 free parameters: $\theta_{\rm E,1}$, $q_{\rm lens1}$, and $\phi_{\rm lens1}$. The angular offset
of the secondary
lens is sampled with respect to ($\Delta \alpha_{\rm lens0}$ and $\Delta \delta_{\rm lens0}$) of
the primary lens.
The source (SMM J0939) is parameterized by
6 free parameters: the position of the source relative to the
primary lens ($\Delta \alpha_{\rm s}$ and $\Delta
\delta_{\rm s}$), the total intrinsic flux density ($S$), the
effective radius ($r_{\rm s} = \sqrt{a_{\rm s} b_{\rm s}}$), the axial
ratio ($q_{\rm s}$ =  $b_{\rm s}/a_{\rm s}$), and the position angle
($\phi_{\rm s}$).
The total number of free parameters is $N_{\rm free}$ = 14. The best-fit model is obtained by maximizing the
Gaussian likelihood function $ \mathcal{L} $ according to:
\begin{equation}
    \mathcal{L} = \sum_{u, v}\left( \frac{|V_{\rm data} - V_{\rm
    model}|^2}{\sigma^2} + {\rm log}(2 \pi \sigma^2) \right)
\end{equation}
\noindent where $\sigma$ is determined from the scatter in the visibilities within a
single spectral window (natural weighting).

We initialize the positions and the Einstein radii of both lenses, and the position of the source using the
values of the best-fit lens model \citet{Haas14} performed on Keck K-band near-infrared image. For each of
these parameters, we impose a uniform prior in the range $\in\pm$3$\sigma$, where $\sigma$ is the uncertainty
reported in their paper. The axial ratios of the lenses are restricted to $q_{\rm lens} > 0.3$. We initialize 512
walkers and 6000 steps to identify the best-fit model parameters.
\begin{figure}[!tbpH]
\centering
\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_model_bestfit}
\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_bestfit}
\caption{We perform lens modeling using the latest version of {\sc uvmcmcfit} on the SMA 1 mm continuum data.
In this two lenses model, we initialize the lenses' positions using the values reported by \citet{Haas14}. Left:
Grayscale: Our best-fit model assuming an elliptical Gaussian profile for the background SMG. Magenta ellipses:
Half-light area of the background SMG. Orange Lines: Critical curves of foreground lenses. Black dots: Positions of
the two lenses. Red contours: Observed SMA 1 mm continuum. The contours start at 2$\sigma$, incrementing at
steps of $\pm$2$\sqrt{\rm 2}\sigma$. Right: Solid contours show the positive residuals at the same levels and dashed contours
show the negative residuals. \label{fig:lens}}
\end{figure}

The resulting best-fit model as shown in Figure \ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
The best-fit model yields a magnification
factor of $\mu_{\rm 1mm}$ = 9.73 $\pm$ 1.38, this is consistent the value reported by \citet{Haas14} within errors. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
1.22 $\pm$ 0.01 (8.75 kpc at $z$ = 0.685) and $\theta_{E}$ = 0.73 $\pm$ 0.02 (5.23 kpc at $z$ = 0.685),
the corresponding masses within the Einstein radii are $M(\theta < \theta_{\rm E})$ = (4.90 $\pm$ 0.58) $\times$ 10$^{11}$ 
\Msun and $M(\theta < \theta_{\rm E})$ = (1.76 $\pm$ 0.33) $\times$ 10$^{11}$ \Msun, respectively. All best-fit
parameters are listed in Table \ref{tab:lensParam}.
\input{table_lensParams}

\subsection{SED fitting} \label{sec:SED}
\subsubsection{3C220.3}

We detect the radio continuum with peak flux density of S$_\nu$ = 5.56 $\pm$ 0.54 mJy at $\nu_{\rm cont}$ = 104.2106 GHz 
(2.877 mm) in the observed-frame. In this lens system, the foreground galaxy (3C220.3) is a double-lobed FR-II radio galaxy, 
hence we expect the continuum to be dominated by emissions from the foreground galaxy.

====== I will edit this: \\
Previous studies suggest that at 104 GHz, contributions from the radio core dominates over that from the radio lobes and jets (cite), thus we 
expect the emission from the core component to dominate our continuum measurement; however, the integrated flux density is measured 
to be 7.18 $\pm$ 0.69 mJy. Since the orientation of the synthesized beam aligns with the axis along the 
lobes of the radio galaxy as shown in Figure \ref{fig:cont}, we interpret the difference in the peak flux 
density and the integrated flux density as the source (core and lobes) being partially resolved, i.e., the continuum detection 
includes emissions from the lobes. Furthermore, the contours of the 104 GHz continuum are
centered on the north lobe of the radio galaxy in the overlay image, this further supports our argument. 
\citet{Mullin06a} report an upper limit on the radio core of 0.17 mJy at 4.6 GHz, whereas \citet{Haas14} 
report a detection of the radio core of 0.8 mJy at 9 GHz, as shown in Figure \ref{fig:SED}.\\
====== Please keep on reading from here.

We fit the SED of the radio galaxy using previous data listed in Table \ref{tab:SEDdataRadio}, following Equation (1) by \citet{Cleary07a}, the fit can be expressed as a functional form:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_v^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution. 
\\ ====== I will edit this ====
In their paper, they limit $\nu_t >$ 1 MHz, 30 GHz $< \nu_c^{\rm lobe}$ 3000 GHz, which give best-fit parameters, and we use their parameters to plot the fit, and we extrapolate to 104 GHz, which is = blah mJy, which is consistent with our continuum measurement. Therefore the 10$\sigma$ detection of the partially resolved continuum emission suggests a 
non-negligible contribution coming from the lobe emission, the peak flux density therefore does not corresponds to the core 
emission. 
\\ ==================
\input{table_SED}

\begin{figure}[!tbph]
\centering
\includegraphics[width=0.5\textwidth]{Figure/3C220_3FullSED}
\caption{Figure shows the SED of 3C220.3 and SMM J0939 including the new measurements presented in this paper. 
Black markers represent existing data of 3C220.3 (see table \ref{tab:SEDdataRadio}). Red markers at 104 GHz corresponds to 
our continuum measurements (integrated, peak, and difference). The dashed black line corresponds to the parabolic function we 
fit to the data associated with the radio galaxy following \citet{Cleary07a}. The dashed blue line and 
the dashed dot magenta line correspond to the best-fit SED of the background SMG, using an optically thick model, and an 
optically thin model, respectively. The photometric data of the SMG are reported by \citet{Haas14}. \label{fig:SED}}
\end{figure}

\subsubsection{SMM J0939+8315} 
To constrain the dust and gas properties in the ISM of SMM J0939, we perform SED fitting on the
photometric data obtained with {\it Herschel}/PACS and SPIRE, at wavelengths
between observed-frame 70 \micron-1000 \micron, and interferometric data with SMA at 1 mm (H14). We use the publicly
available software {\sc mbb\_emcee} to perform SED fitting, the code uses an affine-invariant Markov chain Monte
Carlo (MCMC) approach, the details are described by \citet{Riechers13a} and \citet{Dowell14a}. The
functional form of the fit comprises of a modified blackbody function with a power law S$_{\lambda} \propto \lambda^\alpha
$ attached to the blue
side.
We fit both an optically thick and optically thin model. In the optically thick case, the wavelength $
\lambda_0$ = $\frac{c}{\nu_0}$ is an additional parameter which represents where the optical
depth $\tau_{\nu}$ = ($\nu$/$\nu_0$)$^\beta$ reaches unity. Thus, the functional form of the modified blackbody
in the optically thick regime is as follows:
\begin{equation}
\rm S_{\lambda} \propto \frac{(1-exp^{-(\frac{\lambda_0 (1+z)}{\lambda})^{\beta}})(\frac{c}{\lambda})^3}
{exp^{\frac{hc}{\lambda\rm{kT/(1+z)} } }-1}
\end{equation}
and in the optically thin regime, the functional form reduces to:
\begin{equation}
\rm S_{\lambda} \propto \frac{(\frac{c}{\lambda})^{\beta+3}}{exp^{\frac{hc}{\lambda\rm{kT/(1+z)}}}-1}
\end{equation}
where T is the rest-frame characteristic cold dust temperature (fitting to the FIR part), $\lambda_0$ is rest-frame wavelength
where the optical depth reaches unity, $\beta$ is the dust emissivity (or spectral index of the dust extinction
curve), and $\alpha$ is the power law spectral index. The overall fit is normalized using the observed-frame 500
$\micron$ flux density, hence this becomes an additional parameter in the fit. In both models, we impose an upper limit on $
\lambda_0$ to 2000 \micron, and the observed-frame dust temperature $T_{\rm d}/(1+z)$ to 60 K. We fix the upper limit on 
$\beta$ to be 3.0 and 2.2 for the optically thin model and optically thick model, respectively.

\input{table_mbb}
The best-fit values in both regimes are listed in Table \ref{tab:mbb}. The best-fit solution of an optically thin
model corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of an optically thick model
corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than the optically thin
model. In the subsequent analysis, we employ the inferred values from the optically thick model.
The best-fit solution yields a far-infrared (FIR) luminosity of $L_{\rm FIR (42.5-122.5\micron)}$ = 53.33$^{+1.14}_{-1.13}\times$10$^{12}L_
\odot$, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$ = 88.52$^{+2.62}_{-2.63}\times$10$
^{12}$\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64 m$^2$ kg\pmOne at 125.0 $
\micron$ \citep{Dunne03a}, we derive the dust mass using the following expression:
\begin{equation}
M_{\rm dust} = S_{\nu} D_{L}^2 [(1 + z) \kappa_{\nu} B_{\nu}]^{-1} \tau_{\nu} [1-
\exp(-\tau_{\nu})]^{-1}
\end{equation}
where $S_{\nu}$ is the flux density, $D_{\rm L}$ is the luminosity distance, $\kappa_{\nu}$ is the dust
absorption coefficient, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function,
all quantities are expressed in the observed-frame. We find a dust mass of $M_{\rm dust}$ =
50.47$^{20.42}_{-20.15}\times$10$^8$\Msun, the uncertainties do not include those of $\kappa_{\nu}$. These values are based on SED fitting to the photometric data, i.e. prior
to lensing correction.

\\ ======= I will edit this ======= 
With the limited amount of data in the FIR, $\beta$ and $M_{\rm dust}$ are weakly constrained (see appendix), we explore other possible blah.
We perform another fit imposing upper limit on beta to be 3.0, Hence, dust mass is blah
\\ ====================

%In most cases, $\alpha$ is poorly constrained, with the fits only providing a lower limit. Because of the way the
%blue-side power law is joined to the MBB,
%this simply amounts to a statement that the merge point between the power law and the thermal SED lies at
%wavelengths lower than the shortest
%wavelength photometry point (250 micron). (in Dowell et al. 2014)

\subsection{Molecular gas mass}
==== I will edit this ===== \\
Radford et al. (1991) calibration using local galaxies, calibrated H2 gas mass to CO L conversion using the cold gas (trace using G.S. CO), for high z galaxies with CO(higher J) line observations, make assumptions on the CO excitation conditions.

It has been long assumed that the molecular gas in the ISM traced by CO is thermalized given their high star formation rates (e.g. Greve et al. 2005; Coppin et al. 2008; Tacconi et al. 2008). With the few SMGs with CO(1-0) and higher J co observations to date,
Recent CO(1-0) observations of SMGs have demonstrated that SMGs can indeed be subthermally excited. (Bothwell et al. 2013, Harris et al. (2010). In these galaxies with subthermal excitation at the (3-2) transition, the brightness temperature ratio between CO(3-2) and CO(1-0) is $<$ 0.8. with an average radio of R31 = 0.6 pm 0.1 \citep[\eg][]{Harris10a,Carilli10a,Swinbank2010a,Ivison11a,Ivison10d}. While these brightness temperature ratios are blah in SMGs, observations of high-z quasars suggest that the host galaxies have ratios close to unity (e.g., Riechers 
et al. 2006; 2011a; Ivison et al. 2012). Since only \CO line has been detected on this object, we adopt 1 here since the source is hosting a quasar.
\\ ========

% Michalowski et al. 2010, Santini et al. 2010
% typical of local ULIRGs is ~ 100)
%\citep{Riechers11b}

We derive the molecular gas mass in
this SMG assuming thermalized excitation or assuming thermalized optically thick CO, i.e. the brightness temperature ratio 
between \CO
and ($J$ = 1 \rarr 0) is $R_{31}$ = 1 \citep[\eg][and references therein]{Riechers11a,Scott11a}
%(\eg Ivison et al. 2008, 2012). 
We calculate the CO($J$ = 1 \rarr 0) line luminosity using standard relations 
\citep[\eg][]{Solomon05a,Carilli13a}:
\begin{equation}
L^{\prime}_{\rm CO} = \frac{3.25\times10^7}{\nu_{\rm CO (3-2), rest}^2}\times \frac{D_L^2}{\mu} \times
\frac{I_{\rm CO(3-2)}} {R_{\rm 31} (1 + z)}
\end{equation}
this corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ ($\mu$/9.74)\pmOne (\rm K km s
\pmOne pc$^2$)
after lensing correction. The inferred total molecular gas mass is therefore M$_{\rm gas}$ = (3.303$\pm$blah) $\times
$10$^{10}$ ($\alpha$/0.8) ($\mu$/9.74)$^{-1}$ \Msun. We assumed a conversion factor of $\alpha_{\rm CO}$ =
0.8 \Msun (\LpU)\pmOne based on empirical relations from local ULIRGs, which is typically
adopted for SMGs \citep{Bothwell13a,Tacconi10a,Daddi2010a}. As derived in the previous section, SMM has a dust mass of $M_{\rm dust}
$=50.47$^{20.42}_{-20.15}\times$10$^8$ \Msun (before lensing correction), this corresponds to a gas-to-dust
ratio of $f_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 63.74 $\pm$ blah , which is in good agreement with the range 
of values found in other SMGs (cite).

% ~ 120 for MW (Coppin 2007)
% ~ 60 for typical SMG (coppin 2008)
% ~ 100 for LBG (coppin 2007)

\subsection{Star formation rate}
We derive the star formation rate (SFR) using the \citet{Kennicutt98a} relation, assuming a \citet{Chabrier03a}
stellar initial mass (IMF) function: SFR = 1.0 $\times$ 10$^{-10}\times$ ($L_{\rm IR\ or\ FIR}$). This yields SFR$_{\rm IR}$ 
= (909.12$\pm$155.67) $\times\ (\mu/9.74)^{-1}$ [$M\sun$ yr\pmOne] and SFR$_{\rm FIR}$ 547.71$\times(\mu/9.74)^{-1}$ [M$
\sun$ yr\pmOne] using lensing-corrected (far-)infrared luminosities (L$_{\rm IR}$ and L$_{\rm FIR}$) derived from our SED 
fitting, and assuming negligible contributions from AGN heating.

Assuming constant SFR, the minimum time for which the starburst in SMM J0939 can be maintained at its
current SFR is approximated by the gas depletion timescale $\tau$ = $M_{\rm gas}$/SFR, which is $\tau_{\rm IR}$ = 36.33 
Myr, and $\tau_{\rm FIR}$ = 60.30 Myr.

Move to discussion: Compare THIS NUMBER: with other SMGs (\eg \citep{Greve05a}).

\subsection{SFE}
% The ratio between LIR ($\propto$ SFR) and L$^\prime$CO ($\propto$ Mgas)
%Frayer: Since the IR luminosity is proportional to the SFR and the CO L is proportional to the molecular gas mass, the IR-to-
%CO L ratio provides an indication of the SFE. Strong starburst and ULIRGs tend to show high IR-to-CO L ratios of $\gtrsim$ 
%100 L$\sun$ ( K km/s pc2)-1 \citep[\eg][]{Solomon05a}. 
%\citet{Greve05a} found an average L(IR)/L$\prime
%$CO ratio for SMGs which was a factor of two larger than that for local ULIRGs

The SFR per unit mass of molecular gas is commonly taken as a
measure of the star formation efficiency, SFE = SFR/$M_{\rm gas}$. We compute the ratio using lensing-corrected (far-)infrared 
luminosities ($L_{\rm IR}$ and $L_{\rm FIR}$) and CO($J$ = 1 \rarr 0) luminosity SFE = $L_{\rm F/IR}$/\Lp, this ratio makes no assumptions on the gas mass conversion factor $\alpha$ and is independent of the 
choice of IMF, however, this assumes that differential lensing effect between the CO and infrared emission is negligible.

or IR-to-CO line L ratio
Fix comparison HERE blah blah blah blah

We find a ratio of SFE$_{\rm IR}$ = 220.22 Myr\pmOne and SFE$_{\rm FIR}$ = 132.68 Myr\pmOne, which are comparable
to what is found in "typical" SMGs (tacconi et al. 2006, Riechers et al. 2010, cite).
%Note: SFE values for ULIRGs and distant SMGs typically exceed 100 \Lsun [K km/s pc$^2$]\pmOne
%(\eg Yao et al. 2003; Neri et al. 2003; Greve et al. 2005; Bouche et al. 2007).

\subsection{Dynamical mass} %% check half light radius error, and comparison
We derive the dynamical mass of SMM J0939 using an isotropic virial estimator \citep[\eg][]{Engel10a}:
\begin{equation}
M_{\rm dyn} = 2.8\times 10^5 \times \Delta \rm v_{\rm line}^ 2 \times r
\end{equation}
where the line width $\Delta \rm v_{\rm line}^ 2$ is based on our \CO line
measurement and $r$ is approximated with the half-light radius of the best-fit lens model. This yields $M_{\rm dyn}$ = blah, and gas-to-
dynamical mass fraction of $f_{\rm gas-to-dyn}$ = 2.03.\\ \\

\\ ===== That's it for now ==========
Compare to other. blah blah blah dynamical mass, is it consistent with molecular gas mass?

\subsection{SFR surface density}
% using dynamical mass and Eddington luminosity limit
To compute surface densities we divided half of the star formation rate or gas mass (so that no assumption of IMF) by the area subtended by the half-light (or effective) radius.

\section{Discussion And Conclusions} \label{sec:conclusions}
We present blah

A lensed SMG that is likely to be hosting a type-2 quasar, this source offers an exceptional opportunity to
investigate the gas mass and dynamics of this
poorly-studied population of high z galaxies.

In this paper, we present blah of a strongly lensed blah at z = 2.221, at the epoch of cosmic star formation (cite)
This paper focuses on a blah source J0939+8315, a lensing galaxy.
We report a detection of \CO line.
The continuum detection is marginally resolved, we place constraints on the SED of the foreground galaxy (accounting for radio 
core and lobes emission). Our CO measurement confirms the redshift of this source, which was previously measured using CIV and HeII lines (H14).

The detection of CO in SMM J0939, implying a large molecular gas reservoir, once again demonstrates the active SF in SMGs. 
The large CO luminosity suggests that a signification fraction of the FIR luminosity comes from SF, providing power for dust to re-radiate in FIR. BUt we also know that this source has an dust-enshrouded AGN, boosting the IR.
The SFR inferred from the CO measurement is common for SMGs. the large amount of molecular gas further supports the picture that SMGs are galaxies with making up most of the stellar mass in the early universe, and is responsible for galaxy evolution and formation.

The magnification factor is blah, providing an opportunity to carry out detailed studies of the ISM in this population.

We perform SED fitting of the SMG to get M$_{\rm dust}$, L$_{\rm FIR}$ of blah, L$_{\rm IR}$ of blah, yielding SFR of 
blah . Comparing our findings to other SMGs / similar populations, we find blah, which is blah.

We compare the properties of SMM J0939 with two other SMGs with detailed studies -- HLSW-01 and the cosmic Eyelash. All sources are lensed, making spectral lines measurements relatively feasible than their fainter, un-lensed ``siblings".

Properties and comparison with similar galaxies in Table \ref{tab:comapreSMG}
\input{table_compareSMG}
Discussion of SMG, broad, population.
look at "Lensed QSOs at high z observational, CO measurements (DB)" note

\acknowledgments

We acknowledge the WENSS team for providing the radio measurements for 3C220.3.
Facilities: \facility{CARMA}

\bibliographystyle{apj}
\bibliography{J0939}

\appendix

\begin{figure}[!tbp]
\centering
\includegraphics[width=0.90\textwidth]{Figure/posteriorPDFs}
\caption{Figure shows the marginalized posterior probabilities of each parameter in our lens modeling.
\label{fig:LensPDF}}
\end{figure}

\begin{figure}[!tbp]
\centering
\includegraphics[width=0.55\textwidth]{Figure/CorrelationPlot__thick_500_500}
\includegraphics[width=0.55\textwidth]{Figure/CorrelationPlot__thin_testSMA}
\caption{Resulting correlation plot from our SED fitting. Plots on the diagonal axes are marginalized posterior probability 
distribution of each
parameter. Off-diagonal plots are 2D histograms between parameters. Cross denotes where the best-fit value corresponds to in 
the 2D correlation plot. Top: Optically thick
model. Bottom: Optically thin model. The parameter T (NEED TO FIX: consider making this to T/(1+z); changed axes labels, increase font size, replace with useful title) is the observed-frame characteristic dust temperature.
\label{fig:sedlikelihood}}
\end{figure}

\end{document}

### 2015-06-26 Code/SED_fittingparamPlot.py
Modified plot settings

@@ -12,7 +12,21 @@ Purpose:
 Look at resulting fits from mbb_emcee
 plot probabilities of parameters
 """
-
+# matplotlib.rc('text', usetex=True)
+matplotlib.rc('xtick', labelsize=12)
+matplotlib.rc('ytick', labelsize=12)
+font = {'family': 'Arial Narrow',
+        'weight': 'bold',
+        'size': 13}
+matplotlib.rc('font', **font)
+# monospace sans-serif
+axes = {
+    'titlesize': 'xx-large',
+    'labelsize': 'x-large',
+    'labelweight': 'normal',
+    'linewidth': 1.5
+}
+matplotlib.rc('axes', **axes)
 
 def convergence(plotTitle='ln prob', saveFig=False):
     """
@@ -475,8 +489,8 @@ def triplot(chain, color=True, weights=None, interpolate=False, smooth=True,
     from matplotlib.ticker import FormatStrFormatter, NullFormatter, NullLocator, MaxNLocator
 
     # rcParams settings
-    plt.rcParams['ytick.labelsize'] = 10.0
-    plt.rcParams['xtick.labelsize'] = 10.0
+#    plt.rcParams['ytick.labelsize'] = 10.0
+#    plt.rcParams['xtick.labelsize'] = 10.0
 #    plt.rcParams['text.usetex'] = True
     plt.rcParams['figure.figsize'] = figsize
 
@@ -558,7 +572,7 @@ def triplot(chain, color=True, weights=None, interpolate=False, smooth=True,
     f.subplots_adjust(wspace=0.1)
     if saveFig == True:
         outfile = 'CorrelationPlot__'
-        savefig('../Figure/' + outfile + filename.replace('.h5', '.eps'), dvi=600)
+        savefig('../Figure/' + outfile + filename.replace('.h5', '.png'), dvi=600)
     else:
         plt.show()
 
@@ -694,6 +708,7 @@ def BestFit(verbose=True):
 
 def S_100Rest(alpha=0.80):
     """
+    06- 25 2015: SHOULD REMOVE THIS, no reason to use 100 GHz for deriving qIR if we have different beta than 1.5 (condon 91 or 92)
     Compute flux density at rest frame 100 GHz
 
     Inputs:
@@ -755,19 +770,21 @@ if __name__ == '__main__':
 #    chain_iter(nburn=100, saveFig=save_op)
 #    Ramdon()
[…]

### 2015-06-27 Code/SEDfit.py
Take out other 3C point, fix plot setting

@@ -4,15 +4,21 @@ import matplotlib.pyplot as plt
 from scipy.constants import k, h, c
 import matplotlib
 
-
-matplotlib.rc('text', usetex=True)
-matplotlib.rc('xtick', labelsize=15)
-matplotlib.rc('ytick', labelsize=15)
-font = {'family': 'sans-serif',
+# matplotlib.rc('text', usetex=True)
+matplotlib.rc('xtick', labelsize=17)
+matplotlib.rc('ytick', labelsize=17)
+font = {'family': 'Arial Narrow',
         'weight': 'bold',
-        'size': 20}
+        'size': 15}
 matplotlib.rc('font', **font)
 # monospace sans-serif
+axes = {
+    'titlesize': 'xx-large',
+    'labelsize': 'x-large',
+    'labelweight': 'normal',
+    'linewidth': 1.5
+}
+matplotlib.rc('axes', **axes)
 
 
 def savefigure(f, verbose=True, dirStr='../Figure/'):
@@ -102,17 +108,6 @@ Core_3c220dot3_Hz = np.array([9.e9, 4.86e9])    # Hz
 Point_Continuum_Jy = np.array([5.56e-3, 7.18e-3, 1.62e-3])
 Point_Cont_Hz = np.array([1.042e11, 1.042e11, 1.02e11])     # Hz
 Point_error_Jy = np.array([5.0647e-4, 5.0647e-4, 5.0647e-4])    # Jy
-# =======================================================
-# compare to similiar FR II galaxies
-# 3C6.1:
-# 7.3 mJy @ 8GHz and 10.14mJy at 1.4 GHz
-Core_3c6dot1_Jy = np.array([7.3e-3, 10.14e-3])      # Jy
-Core_3c6dot1_freq = np.array([8e9, 1.4e9])  # Hz
-# 3C 263:
-# 161.1 mJy @ 5 GHz and 0.119 Jy @ 8GHz
-Core_3c263_Jy = np.array([161.1e-3, 0.119])
-Core_3c263_freq = np.array([5e9, 8e9])      # Hz
-# =======================================================
 
 
 ########################################
@@ -137,6 +132,13 @@ Radio_Hz, Radio_Jy, Radio_error = ([dat[0] for dat in Radio_data],
 Radio_Hz, Radio_Jy, Radio_error = (np.asarray(Radio_Hz),
                                    np.asarray(Radio_Jy),
[…]

### 2015-06-27 Code/SEDfit.py
Remove figure legend frame, make it prettier

@@ -420,8 +420,11 @@ p_fit_thin = ax.plot(p_wave, res_thin.best_fit_sed(
 ax.set_xlabel(r'$\lambda_{\rm obs}\ [\mu$m]', fontsize=17, fontweight='normal')
 # ax.set_title('SMM J0939+8315', fontsize=20,  fontweight='bold')
 ax.set_ylabel(r'$\rm S_{\nu}$ [mJy]', fontsize=20,  fontweight='bold')
-plt.legend(loc='best', fontsize=15, numpoints=1,
+led = plt.legend(loc='best', fontsize=15, numpoints=1,
            fancybox=True, borderpad=0.2, handlelength=2, labelspacing=0.1)
+led.get_frame().set_alpha(0) # this will make the box totally transparent
+led.get_frame().set_edgecolor('white') # this will make the edges of the border white to match the background instead
+
 ax.set_xscale('log')
 ax.set_yscale('log')
 ax_top.set_xscale('log')

### 2015-06-27 Code/SEDfit.py
Fix plot cut out labels

@@ -5,8 +5,8 @@ from scipy.constants import k, h, c
 import matplotlib
 
 # matplotlib.rc('text', usetex=True)
-matplotlib.rc('xtick', labelsize=17)
-matplotlib.rc('ytick', labelsize=17)
+matplotlib.rc('xtick', labelsize=20)
+matplotlib.rc('ytick', labelsize=20)
 font = {'family': 'Arial Narrow',
         'weight': 'bold',
         'size': 15}
@@ -41,7 +41,7 @@ def savefigure(f, verbose=True, dirStr='../Figure/'):
             print "... Directory {:s} exists...".format(dirStr)
     os.system('rm -rf ' + f + '.png' + ' ' + f + '.eps')
     plt.savefig(dirStr + f + '.png')
-    plt.savefig(dirStr + f + '.eps', dvi=600)
+#    plt.savefig(dirStr + f + '.eps', dvi=600)
 
 
 def read_data_fromtxt(filename):
@@ -338,16 +338,18 @@ class Wavelength2FreqTransform(Freq2WavelengthTransform):
 
 
 plt.clf()
-fig = plt.figure(1, figsize=(12, 8))
+fig = plt.figure(1, figsize=(20, 8))
+fig.subplots_adjust(left=0.12, right=0.96, top=0.85, bottom=0.15, wspace=0.39)
 ax = SubplotHost(fig, 1, 1, 1)
 fig.add_subplot(ax)
+
 # print "*** !! Redshifting axis for z = 2.221, if undesired, change in
 # function"
 
 aux_trans = mtransforms.BlendedGenericTransform(
     Wavelength2FreqTransform(), mtransforms.IdentityTransform())
 ax_top = ax.twin(aux_trans)
-ax_top.set_xlabel(r'$\nu_{\rm obs}$ [GHz]', size=18, fontweight='normal')
+ax_top.set_xlabel(r'$\nu_{\rm obs}$ [GHz]', size=16, fontweight='bold')
 ax_top.set_viewlim_mode("transform")
 ax_top.axis["right"].toggle(ticklabels=False)
 
@@ -417,9 +419,9 @@ res_thin = mbb_emcee.mbb_results(h5file=filename_thin)
 p_fit_thin = ax.plot(p_wave, res_thin.best_fit_sed(
     p_wave), '-', color='c', lw=4, label='Optically Thin Fit', alpha=0.6)
 
[…]

### 2015-06-27 skeleton.tex
Up to molecular gas mass section

@@
-\documentclass{emulateapj}
+%\documentclass{emulateapj}
+\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
+\usepackage{hyperref}
 \newcommand{\vdag}{(v)^\dagger}
@@
 \newcommand{\pmOne}{$^{-1}$}
+\newcommand\tna{\,\tablenotemark{a}}
+\newcommand\tnb{\,\tablenotemark{b}}
+\newcommand\tnc{\,\tablenotemark{c}}
+\newcommand\tnd{\,\tablenotemark{d}}
+\newcommand\tne{\,\tablenotemark{e}}
+\newcommand\tnf{\,\tablenotemark{f}}
+\newcommand\tng{\,\tablenotemark{g}}
+
 %\slugcomment{{\sc Accepted to ApJ:} August 1, 2006}
@@
 \title{\CO observation in a strongly lensed type-2 quasar host SMG at $z$ = 2.221 with
-continuum detection in the foreground lensing FR-II radio galaxy at $z$ = 0.685}
+continuum detection in the lensing FR-II galaxy 3C220.3}
 \author{No name}
-%\author{T. K. Daisy Leung\altaffilmark{1} and Dominik R. Riechers\altaffilmark{2}}
+%\author{T. K. Daisy Leung\altaffilmark{1} and Dominik R. Riechers}
 %\affil{Astronomy Department, Cornell Unviersity}
 %\altaffiltext{1}{tleung@astro.cornell.edu}
-%\altaffiltext{2}{dr@astro.cornell.edu}
 
@@
 emission from the foreground radio galaxy 3C220.3 with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
- at 104 GHz (1.7 mm rest-frame), allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
+ at 104 GHz, allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
 fit
@@
 \section{Introduction}\label{sec:intro}
-Submillimeter-selected galaxies (SMGs) are found predominantly at redshift $z \sim$ 1-3, during the epoch of stellar mass and 
+Submillimeter-selected galaxies (SMGs) are predominantly found at redshift $z \sim$ 1-3, during the epoch of stellar mass and 
 galaxy assembly. These galaxies are luminous in submillimeter (submm) due to the re-radiation from the dust components in the
- far-infrared (FIR) wavelengths. Large sky surveys (e.g., HERMES, HATLAS) with submm facilities have lead to growing consensus
-  of the observable properties of SMGs. SMGs are a population of galaxy at high redshifts that are typically dusty, gas-rich, 
+ far-infrared (FIR) wavelengths. Followup observations of SMGs discovered in large sky surveys (e.g., HERMES, HATLAS) with sub-(mm) facilities have led to growing consensus
+  of the observable properties of SMGs (cite). SMG is a population of high-redshift galaxy that are typically dusty, gas-rich, 
   and luminous ($\gtrsim$ 10$^{12}$ \Lsun) in infrared with high star formation rates ($\gtrsim $ 500 \Msun yr\pmOne). (e.g., Lagache et al. 2005, cite more recent). \par
-  To characterize the properties of the gas reservoirs in the ISM, where active star formation takes place, CO rotational lines have been commonly used as a tracer due to its high abundance in the ISM as well as its low excitation energy, the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep{Carilli13a}.
+  To characterize the physical properties of the gas reservoirs in the ISM where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to the high abundance of this molecule in the ISM as well as its low excitation energy, the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep{Carilli13a}.
 Recent observations of the CO line of SMGs at $z \sim$ 1-3 have
 provided evidence that SMGs have large gas reservoirs typical of \textgreater 10$^{10}$\Msun.
-In most cases, detailed studies are carried out on SMGs that are gravitationally lensed, the lensing amplification boost the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys (Negrello 10, cite).
+In most cases, detailed studies are carried out on SMGs that are gravitationally lensed, lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys (Negrello 10, cite).
 \par
 One of such lens system has a peculiar configuration consisting of a SMG, SMM J0939+8315 (hereafter SMM J0939), hosting a 
-type-2 quasar host at $z$ = 2.221 being strongly lensed by a double-lobed Fanaroff-Riley Class II (FR-II) \citep*{Fanaroff74} radio galaxy (3C220.3) which has a 
-companion galaxy B at $z$ = 0.685. The two lenses are separated by 1\farcs5. The redshift of the background SMG has 
+type-2 quasar at $z$ = 2.221. SMM J0939 is being strongly lensed by a double-lobed Fanaroff-Riley Class II (FR-II) \citep*{Fanaroff74} radio galaxy (3C220.3) which has a 
+companion galaxy B at $z$ = 0.685, separated by 1\farcs5. SMM J0939 is currently
+the brightest known lensed
+SMGs, with lensing-magnified flux density of SMM J0939 $F_{\rm 250\mu m}$ = 440 $\pm$ 15 mJy. The redshift of SMM J0939 has 
 been measured through the detection of CIV 1459\AA\
  and HeII 1640\AA\
-line emissions \citep[hereafter H14]{Haas14}, these line detections provide conceiving evidence of AGN activity in the SMG, as well as the 
-existence of a type-2 quasar.
-The background SMG has a lensing-magnified flux density of $F_{\rm 250\mu m}$ = 440 $\pm$ 15 mJy, which is one of 
-the
-brightest known even among lensed
-SMGs.
+line emissions \citep[hereafter H14]{Haas14}, these line detections provide conceivable evidence of AGN activity in this SMG, as well as the identification of a type-2 quasar.
 
@@
 and SMM J0939 and derive the intrinsic properties of the interstellar medium (ISM) in the SMG; in \S \ref{sec:conclusions}, we
-conclude our findings by comparing to other SMGs at high redshifts.
+conclude our findings by comparing to other SMGs at similar redshifts.
 
@@
 \subsection{CARMA} \label{sec:carmadata}
-Observations of the \CO rotational transition ($\nu_{rest}$ = 345.7959899 GHz),
+Observations of the \CO rotational transition ($\nu_{\rm rest}$ = 345.7959899 GHz),
 redshifted to $\nu_{obs}$ = 107.357 GHz (2.794 mm) towards the background galaxy SMM
@@
 \subsection{New results: Continuum Emission} 
-% So integrated - peak should be approx. the extended components ~ (7.18 - 5.56 mJy)
-%      --- Integrated:   7.18 +/- 0.69 mJy
-%      --- Peak:         5.56 +/- 0.54 mJy/beam
-
-%Deconvolution size bigger than expected (if just radio core):
-%1) phase error that wasn't well calibrated (~30/360 $\times$\appox 16") ~ 1-2"
-%2) low SNR giving rise to fitting error ~ 4" from `imfit`
-%3) PA beam align with RG (radio galaxy) orientation
 Averaging over all the line-free channels, we detect a 10$\sigma$ continuum emission at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz (2.877 mm) in the observed-frame, corresponding to $\sim$2.79 mm at $z$ = 0.658.
@@
 Fitting a four-parameter single-component Gaussian to the spectrum yields a peak flux density of 19.9 $\pm
-$ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy, and FWHM of 541.65 $\pm$ 31.91 km s\pmOne. 
+$ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy, and full width at half-maximum (FWHM) of 541.65 $\pm$ 31.91 km s\pmOne. 
 The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, the 
@@
 \centering
-\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_model_bestfit}
-\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_bestfit}
+\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_model_goodfit0771}
+\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_goodfit0771}
 \caption{We perform lens modeling using the latest version of {\sc uvmcmcfit} on the SMA 1 mm continuum data.
@@
 the corresponding masses within the Einstein radii are $M(\theta < \theta_{\rm E})$ = (4.90 $\pm$ 0.58) $\times$ 10$^{11}$ 
-\Msun and $M(\theta < \theta_{\rm E})$ = (1.76 $\pm$ 0.33) $\times$ 10$^{11}$ \Msun, respectively. All best-fit
+\Msun 
+and $M(\theta < \theta_{\rm E})$ = (1.76 $\pm$ 0.33) $\times$ 10$^{11}$ \Msun, respectively. All best-fit
 parameters are listed in Table \ref{tab:lensParam}.
@@
 \subsubsection{3C220.3}
-
-We detect the radio continuum with peak flux density of S$_\nu$ = 5.56 $\pm$ 0.54 mJy at $\nu_{\rm cont}$ = 104.2106 GHz 
-(2.877 mm) in the observed-frame. In this lens system, the foreground galaxy (3C220.3) is a double-lobed FR-II radio galaxy, 
-hence we expect the continuum to be dominated by emissions from the foreground galaxy.
-
-====== I will edit this: \\
-Previous studies suggest that at 104 GHz, contributions from the radio core dominates over that from the radio lobes and jets (cite), thus we 
-expect the emission from the core component to dominate our continuum measurement; however, the integrated flux density is measured 
-to be 7.18 $\pm$ 0.69 mJy. Since the orientation of the synthesized beam aligns with the axis along the 
-lobes of the radio galaxy as shown in Figure \ref{fig:cont}, we interpret the difference in the peak flux 
-density and the integrated flux density as the source (core and lobes) being partially resolved, i.e., the continuum detection 
-includes emissions from the lobes. Furthermore, the contours of the 104 GHz continuum are
-centered on the north lobe of the radio galaxy in the overlay image, this further supports our argument. 
-\citet{Mullin06a} report an upper limit on the radio core of 0.17 mJy at 4.6 GHz, whereas \citet{Haas14} 
-report a detection of the radio core of 0.8 mJy at 9 GHz, as shown in Figure \ref{fig:SED}.\\
-====== Please keep on reading from here.
-
-We fit the SED of the radio galaxy using previous data listed in Table \ref{tab:SEDdataRadio}, following Equation (1) by \citet{Cleary07a}, the fit can be expressed as a functional form:
+In the theory of synchrotron emission, continuum emission from extended components of a radio galaxy decreases with increasing frequencies, and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$ where the spectral index $\alpha$ is $\gtrsim$ 0.5.
+While the contribution from extended components decreases, studies using samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises and dominates the flux density at higher frequencies (cite).
+Consequently, we expect the peak flux density in our continuum detection of $S_{\rm 104GHz}$ = 5.56 $\pm$ 0.54 mJy to be dominated by the unresolved core component of the foreground FR-II.
+On the other hand, the integrated flux density of 7.18 $\pm$ 0.69 mJy is suggestive of a marginally resolved detection of the extended components with non-negligible emission.
+This is plausible given that the orientation of the synthesized beam in our observations aligns with the axis along the
+lobes of the radio galaxy, as shown in Figure \ref{fig:cont}.
+We investigate this disparity by fitting an SED to existing data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to estimate the flux density of the lobes at the frequency of our continuum measurement.
+For the core, an upper limit of $<$0.17 mJy at 4.6 GHz \citep{Mullin06a}, and a clear detection of 0.8 mJy at 9 GHz (H14) is indicative of a substantially inverted spectrum of the core, although we note that these measurements are taken across epochs.
+All measurements are plotted in Figure \ref{fig:SED}.
+\input{table_SED}
+Following Equation (1) in \citet{Cleary07a}, the fit to the lobes can be expressed as a parabolic function:
 \begin{equation}
@@
 where $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_v^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution.
-\\ ====== I will edit this ====
-In their paper, they limit $\nu_t >$ 1 MHz, 30 GHz $< \nu_c^{\rm lobe}$ 3000 GHz, which give best-fit parameters, and we use their parameters to plot the fit, and we extrapolate to 104 GHz, which is = blah mJy, which is consistent with our continuum measurement.
-Therefore the 10$\sigma$ detection of the partially resolved continuum emission suggests a
-non-negligible contribution coming from the lobe emission, the peak flux density therefore does not corresponds to the core 
-emission. 
-\\ ==================
-\input{table_SED}
+
+The resulting fit is shown in Figure \ref{fig:SED}, the extrapolated flux density at 104 GHz is consistent with the peak flux density of our continuum measurement.
+The 10$\sigma$ detection of the continuum thereby suggests
+non-negligible contributions from the lobes, and the peak flux density therefore does not appear to be dominated by the core 
+emission. Furthermore, the contours of the 104 GHz continuum are
+centered on the northern lobe as illustrated by the overlay image in Figure \ref{fig:cont}, this further supports our argument.
+This finding is consistent with a recent study by \citet{Hardcastle08a}, where a few radio galaxies blah blah.
+At the resolution of our observation, it is unclear whether the integrated flux is dominated by the hotspot or the lobes.
 
@@
 \includegraphics[width=0.5\textwidth]{Figure/3C220_3FullSED}
-\caption{Figure shows the SED of 3C220.3 and SMM J0939 including the new measurements presented in this paper. 
-Black markers represent existing data of 3C220.3 (see table \ref{tab:SEDdataRadio}). Red markers at 104 GHz corresponds to 
-our continuum measurements (integrated, peak, and difference). The dashed black line corresponds to the parabolic function we 
-fit to the data associated with the radio galaxy following \citet{Cleary07a}. The dashed blue line and 
-the dashed dot magenta line correspond to the best-fit SED of the background SMG, using an optically thick model, and an 
-optically thin model, respectively. The photometric data of the SMG are reported by \citet{Haas14}. \label{fig:SED}}
+\caption{The SED of 3C220.3 and SMM J0939 including the new measurements presented in this paper. 
+Black dots represent existing data of 3C220.3 (see table \ref{tab:SEDdataRadio}). Red dots at 104 GHz corresponds to 
+our continuum measurements (integrated, peak, and difference). The purple line corresponds to the parabolic function we 
+fit to the data associated with the radio galaxy following \citet{Cleary07a}. The dashed purple line and 
+the solid cyan line correspond to the best-fit SED models of the background SMG. The photometric data of the SMG are reported by \citet{Haas14}. \label{fig:SED}}
 \end{figure}
@@
 \end{equation}
-where T is the rest-frame characteristic cold dust temperature (fitting to the FIR part), $\lambda_0$ is rest-frame wavelength
+where $T$ is the rest-frame characteristic cold dust temperature, $\lambda_0$ is rest-frame wavelength
 where the optical depth reaches unity, $\beta$ is the dust emissivity (or spectral index of the dust extinction
@@
 $\micron$ flux density, hence this becomes an additional parameter in the fit. In both models, we impose an upper limit on $
-\lambda_0$ to 2000 \micron, and the observed-frame dust temperature $T_{\rm d}/(1+z)$ to 60 K. We fix the upper limit on 
+\lambda_0$ to 2000 \micron, and the observed-frame dust temperature $T/(1+z)$ to 60 K. We fix the upper limit on 
 $\beta$ to be 3.0 and 2.2 for the optically thin model and optically thick model, respectively.
@@
 \input{table_mbb}
-The best-fit values in both regimes are listed in Table \ref{tab:mbb}. The best-fit solution of an optically thin
+The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in appendix. The best-fit solution of an optically thin
 model corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of an optically thick model
@@
 model. In the subsequent analysis, we employ the inferred values from the optically thick model.
-The best-fit solution yields a far-infrared (FIR) luminosity of $L_{\rm FIR (42.5-122.5\micron)}$ = 53.33$^{+1.14}_{-1.13}\times$10$^{12}L_
-\odot$, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$ = 88.52$^{+2.62}_{-2.63}\times$10$
+The best-fit solution yields a far-infrared (FIR) luminosity of $L_{\rm FIR (42.5-122.5\micron)}$ = 53.33$^{+1.14}_{-1.13}\times$10$^{12}$\Lsun, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$ = 88.52$^{+2.62}_{-2.63}\times$10$
 ^{12}$\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64 m$^2$ kg\pmOne at 125.0 $
@@
 to lensing correction.
-
-\\ ======= I will edit this ======= 
-With the limited amount of data in the FIR, $\beta$ and $M_{\rm dust}$ are weakly constrained (see appendix), we explore other possible blah.
-We perform another fit imposing upper limit on beta to be 3.0, Hence, dust mass is blah
-\\ ====================
-
-%In most cases, $\alpha$ is poorly constrained, with the fits only providing a lower limit. Because of the way the
-%blue-side power law is joined to the MBB,
-%this simply amounts to a statement that the merge point between the power law and the thermal SED lies at
-%wavelengths lower than the shortest
-%wavelength photometry point (250 micron). (in Dowell et al. 2014)
+With the limited amount of data in the FIR, $M_{\rm dust}$ is weakly constrained; in another optically thick model where the upper limit of $\beta$ is set to 3.0, all fitting parameters of the best-fit solution is similar to those using an upper limit of 2.2, vary at most blah\% except for $\lambda_0$, which blah blah, the dust mass is boosted by a factor of $\sim$2.
 
 \subsection{Molecular gas mass}
-==== I will edit this ===== \\
-Radford et al.
-(1991) calibration using local galaxies, calibrated H2 gas mass to CO L conversion using the cold gas (trace using G.S.
-CO), for high z galaxies with CO(higher J) line observations, make assumptions on the CO excitation conditions.
+The ground state CO transition line, CO($J$ = 1 \rarr 0) has been used as a tracer of the cold molecular gas in galaxies for over a decade.
+For high-redshift galaxies, the CO(J$>$1) transition lines are
+, assumptions on the CO excitation conditions is required to derive the molecular gas mass using the H2 to CO relation.
 
-It has been long assumed that the molecular gas in the ISM traced by CO is thermalized given their high star formation rates (e.g.
+It has long been assumed that the molecular gas in the ISM of SMGs traced by CO is thermalized given their high star formation rates (e.g.
 Greve et al.
@@
 with an average radio of R31 = 0.6 pm 0.1 \citep[\eg][]{Harris10a,Carilli10a,Swinbank2010a,Ivison11a,Ivison10d}.
-While these brightness temperature ratios are blah in SMGs, observations of high-z quasars suggest that the host galaxies have ratios close to unity (e.g., Riechers
+While these brightness temperature ratios are $\sim$0.6 in SMGs, observations of high-z quasars suggest that the host galaxies have ratios close to unity (e.g., Riechers
 et al. 2006; 2011a; Ivison et al. 2012). Since only \CO line has been detected on this object, we adopt 1 here since the source is hosting a quasar.
-\\ ========
-
-% Michalowski et al. 2010, Santini et al. 2010
-% typical of local ULIRGs is ~ 100)
-%\citep{Riechers11b}
 
 We derive the molecular gas mass in
-this SMG assuming thermalized excitation or assuming thermalized optically thick CO, i.e. the brightness temperature ratio 
+this SMG assuming thermalized excitation of CO, i.e. the brightness temperature ratio 
 between \CO
@@
 \end{equation}
-this corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ ($\mu$/9.74)\pmOne (\rm K km s
+this corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ \pmOne (\rm K km s
 \pmOne pc$^2$)
-after lensing correction. The inferred total molecular gas mass is therefore M$_{\rm gas}$ = (3.303$\pm$blah) $\times
-$10$^{10}$ ($\alpha$/0.8) ($\mu$/9.74)$^{-1}$ \Msun. We assumed a conversion factor of $\alpha_{\rm CO}$ =
+after lensing correction. The inferred total molecular gas mass is therefore M$_{\rm gas}$ = (3.3$\pm$0.7) $\times
+$10$^{10}$ ($\alpha$/0.8) \Msun. We assumed a conversion factor of $\alpha_{\rm CO}$ =
 0.8 \Msun (\LpU)\pmOne based on empirical relations from local ULIRGs, which is typically
-adopted for SMGs \citep{Bothwell13a,Tacconi10a,Daddi2010a}. As derived in the previous section, SMM has a dust mass of $M_{\rm dust}
-$=50.47$^{20.42}_{-20.15}\times$10$^8$ \Msun (before lensing correction), this corresponds to a gas-to-dust
-ratio of $f_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 63.74 $\pm$ blah , which is in good agreement with the range 
-of values found in other SMGs (cite).
+adopted for SMGs \citep{Bothwell13a,Tacconi10a,Daddi2010a}. 
+Combining with the dust mass derived from SED fitting, the gas-to-dust
+ratio is $f_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 63.74 $\pm$ blah , which is in good agreement with the range 
+of values found in other SMGs \citep{Coppin08a}.
 
@@
 stellar initial mass (IMF) function: SFR = 1.0 $\times$ 10$^{-10}\times$ ($L_{\rm IR\ or\ FIR}$). This yields SFR$_{\rm IR}$ 
-= (909.12$\pm$155.67) $\times\ (\mu/9.74)^{-1}$ [$M\sun$ yr\pmOne] and SFR$_{\rm FIR}$ 547.71$\times(\mu/9.74)^{-1}$ [M$
+= (909.12 $\pm$ 155.67) $\times\ (\mu/9.74)^{-1}$ [$M\sun$ yr\pmOne] and SFR$_{\rm FIR}$ (547.71 $\pm$ 89.28) $\times(\mu/9.74)^{-1}$ [M$
 \sun$ yr\pmOne] using lensing-corrected (far-)infrared luminosities (L$_{\rm IR}$ and L$_{\rm FIR}$) derived from our SED 
@@
 Assuming constant SFR, the minimum time for which the starburst in SMM J0939 can be maintained at its
-current SFR is approximated by the gas depletion timescale $\tau$ = $M_{\rm gas}$/SFR, which is $\tau_{\rm IR}$ = 36.33 
-Myr, and $\tau_{\rm FIR}$ = 60.30 Myr.
+current SFR is approximated by the gas depletion timescale $\tau$ = $M_{\rm gas}$/SFR, which is $\tau_{\rm IR}$ = 36.33$\pm$ blah 
+Myr, and $\tau_{\rm FIR}$ = 60.30$\pm$blah Myr.
 
@@
 \subsection{SFE}
-% The ratio between LIR ($\propto$ SFR) and L$^\prime$CO ($\propto$ Mgas)
-%Frayer: Since the IR luminosity is proportional to the SFR and the CO L is proportional to the molecular gas mass, the IR-to-
-%CO L ratio provides an indication of the SFE. Strong starburst and ULIRGs tend to show high IR-to-CO L ratios of $\gtrsim$ 
-%100 L$\sun$ ( K km/s pc2)-1 \citep[\eg][]{Solomon05a}. 
-%\citet{Greve05a} found an average L(IR)/L$\prime
-%$CO ratio for SMGs which was a factor of two larger than that for local ULIRGs
-
 The SFR per unit mass of molecular gas is commonly taken as a
 measure of the star formation efficiency, SFE = SFR/$M_{\rm gas}$. We compute the ratio using lensing-corrected (far-)infrared 
-luminosities ($L_{\rm IR}$ and $L_{\rm FIR}$) and CO($J$ = 1 \rarr 0) luminosity SFE = $L_{\rm F/IR}$/\Lp, this ratio makes no assumptions on the gas mass conversion factor $\alpha$ and is independent of the
+luminosities ($L_{\rm IR}$ or $L_{\rm FIR}$) and CO($J$ = 1 \rarr 0) luminosity SFE = $L_{\rm F/IR}$/\Lp, this ratio makes no assumptions on the gas mass conversion factor $\alpha$ and is independent of the
 choice of IMF, however, this assumes that differential lensing effect between the CO and infrared emission is negligible.
-
-or IR-to-CO line L ratio
-Fix comparison HERE blah blah blah blah
 
@@
 to what is found in "typical" SMGs (tacconi et al. 2006, Riechers et al. 2010, cite).
-%Note: SFE values for ULIRGs and distant SMGs typically exceed 100 \Lsun [K km/s pc$^2$]\pmOne
-%(\eg Yao et al. 2003; Neri et al. 2003; Greve et al. 2005; Bouche et al. 2007).
+Greve 05.
 
@@
 \begin{equation}
-M_{\rm dyn} = 2.8\times 10^5 \times \Delta \rm v_{\rm line}^ 2 \times r
+M_{\rm dyn} = 2.8\times 10^5\Delta \rm v_{\rm line}^ 2 R_{\rm eff}
 \end{equation}
 where the line width $\Delta \rm v_{\rm line}^ 2$ is based on our \CO line
-measurement and $r$ is approximated with the half-light radius of the best-fit lens model. This yields $M_{\rm dyn}$ = blah, and gas-to-
-dynamical mass fraction of $f_{\rm gas-to-dyn}$ = 2.03.\\ \\
+measurement and $R_{\rm eff}$ is approximated with the half-light radius of the best-fit lens model. This yields $M_{\rm dyn}$ = blah, and gas-to-
+dynamical mass fraction of $f_{\rm gas-to-dyn}$ = 2.03.
 
-\\ ===== That's it for now ==========
 Compare to other. blah blah blah dynamical mass, is it consistent with molecular gas mass?
@@
 the 2D correlation plot. Top: Optically thick
-model.
-Bottom: Optically thin model.
-The parameter T (NEED TO FIX: consider making this to T/(1+z); changed axes labels, increase font size, replace with useful title) is the observed-frame characteristic dust temperature.
+model. Bottom: Optically thin model. The parameter T/(1+z) is the observed-frame characteristic dust temperature.
 \label{fig:sedlikelihood}}

### 2015-06-28 skeleton.tex
Up to dyn mass

@@
 \shorttitle{Study of a strongly lensed type-2 quasar host SMG at $z$ = 2.221}
-%\shortauthors{Leung and Riechers}
+\shortauthors{Leung \& Riechers}
 
@@
 continuum detection in the lensing FR-II galaxy 3C220.3}
-\author{No name}
-%\author{T. K. Daisy Leung\altaffilmark{1} and Dominik R. Riechers}
-%\affil{Astronomy Department, Cornell Unviersity}
-%\altaffiltext{1}{tleung@astro.cornell.edu}
+\author{T. K. Daisy Leung\altaffilmark{1} and Dominik R. Riechers}
+\affil{Astronomy Department, Cornell Unviersity}
+\altaffiltext{1}{tleung@astro.cornell.edu}
 
 \begin{abstract}
-We report the detection of \CO line emission in SMM J0939+8315 ($z$ = 2.221), a
+We report the detection of \CO line emission in SMM J0939+8315 at $z$ = 2.221, a
 strongly lensed high-redshift submillimeter galaxy (SMG) hosting a type-2 quasar using
 the Combined Array for Research in Millimeter-wave Astronomy (CARMA). This lensing system consists of a
-foreground radio galaxy and a companion galaxy at $z$ = 0.685.
+foreground radio galaxy 3C220.3 and a companion galaxy at $z$ = 0.685.
 A lensing magnification of $\mu_{\rm 1 mm}$ = 9.74 $\pm$ 1.4 amplified the intrinsic luminosities of the CO emission.
@@
 0.9) $\times$ 10$^{10}$ \LpU. This
-translates to a molecular gas mass of $M_{\rm gas}$ = 3.3 $\times$ 10$^{10}M_\odot$, assuming a conversion
-factor of $\alpha_{\rm CO}$ = 0.8 \Msun (\LpU)\pmOne. We report marginally resolved continuum 
-emission from the foreground radio galaxy 3C220.3 with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
+translates to a molecular gas mass of $M_{\rm gas}$ = 3.3 $\times$ 10$^{10}M_\odot$. We report marginally resolved continuum 
+emission from the foreground galaxy with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
  at 104 GHz, allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
 fit
- both an optically thick and optically thin modified blackbody models to the SED of the SMG using existing
-infrared photometric data. Our SED fitting favours an optically thick model, yielding dust mass of $M_{\rm
+ both an optically thick and optically thin modified blackbody models to the SED of the SMG, the preferable optically thick model  yields dust mass of $M_{\rm
 dust}$ = 50.5$^{20.4}_{-20.2}$ $\times$ 10$^8$\Msun, and total infrared (IR) luminosity of $L$ = 88.5$^{+2.6}
@@
 SMM J0939 at $z$ = 2.221. The underlying radio continuum at 104 GHz allows us to put constraints on the SED of the 
-foreground radio galaxy. This paper is organized as follows: in \S \ref{sec:obs}, we describe the
+foreground radio galaxy.
+
+This paper is organized as follows: in \S \ref{sec:obs}, we describe the
 observations of the \CO line emission with CARMA; in \S \ref{sec:res}, we report the
@@
 lenses are represented by singular isothermal ellipsoid (SIE) profiles, and the source is assumed to have an
-elliptical Gaussian profile. The code does not include an external shear parameter. \newline
+elliptical Gaussian profile. The code does not include an external shear parameter.
+
 We fix the phase center to coordinates ($\alpha$, $\delta$) (J2000) = (144.84809\degr, 83.25725\degr), the
@@
 the corresponding masses within the Einstein radii are $M(\theta < \theta_{\rm E})$ = (4.90 $\pm$ 0.58) $\times$ 10$^{11}$ 
-\Msun 
+\Msun\ 
 and $M(\theta < \theta_{\rm E})$ = (1.76 $\pm$ 0.33) $\times$ 10$^{11}$ \Msun, respectively. All best-fit
@@
 On the other hand, the integrated flux density of 7.18 $\pm$ 0.69 mJy is suggestive of a marginally resolved detection of the extended components with non-negligible emission.
-This is plausible given that the orientation of the synthesized beam in our observations aligns with the axis along the
+This is plausible given that the orientation of the synthesized beam in our observations is in alignment with the axis along the
 lobes of the radio galaxy, as shown in Figure \ref{fig:cont}.
@@
 to lensing correction.
-With the limited amount of data in the FIR, $M_{\rm dust}$ is weakly constrained; in another optically thick model where the upper limit of $\beta$ is set to 3.0, all fitting parameters of the best-fit solution is similar to those using an upper limit of 2.2, vary at most blah\% except for $\lambda_0$, which blah blah, the dust mass is boosted by a factor of $\sim$2.
+With the limited amount of data in the FIR, $M_{\rm dust}$ is weakly constrained; in another fit to the optically thick model where the upper limit of $\beta$ is set to 3.0, all fitting parameters of the best-fit solution are similar to those using an upper limit of 2.2, we find that the deviation of each is at most $\sim$3\% whereas the dust mass is boosted by a factor of $\sim$2.
 
 \subsection{Molecular gas mass}
-The ground state CO transition line, CO($J$ = 1 \rarr 0) has been used as a tracer of the cold molecular gas in galaxies for over a decade.
-For high-redshift galaxies, the CO(J$>$1) transition lines are
-, assumptions on the CO excitation conditions is required to derive the molecular gas mass using the H2 to CO relation.
-
-It has long been assumed that the molecular gas in the ISM of SMGs traced by CO is thermalized given their high star formation rates (e.g.
-Greve et al.
-2005; Coppin et al.
-2008; Tacconi et al.
-2008).
-With the few SMGs with CO(1-0) and higher J co observations to date,
-Recent CO(1-0) observations of SMGs have demonstrated that SMGs can indeed be subthermally excited.
-(Bothwell et al.
-2013, Harris et al.
-(2010).
-In these galaxies with subthermal excitation at the (3-2) transition, the brightness temperature ratio between CO(3-2) and CO(1-0) is $<$ 0.8.
-with an average radio of R31 = 0.6 pm 0.1 \citep[\eg][]{Harris10a,Carilli10a,Swinbank2010a,Ivison11a,Ivison10d}.
-While these brightness temperature ratios are $\sim$0.6 in SMGs, observations of high-z quasars suggest that the host galaxies have ratios close to unity (e.g., Riechers
-et al. 2006; 2011a; Ivison et al. 2012). Since only \CO line has been detected on this object, we adopt 1 here since the source is hosting a quasar.
-
-We derive the molecular gas mass in
-this SMG assuming thermalized excitation of CO, i.e. the brightness temperature ratio 
-between \CO
-and ($J$ = 1 \rarr 0) is $R_{31}$ = 1 \citep[\eg][and references therein]{Riechers11a,Scott11a}
-%(\eg Ivison et al. 2008, 2012). 
-We calculate the CO($J$ = 1 \rarr 0) line luminosity using standard relations 
+The ground state CO transition line, CO($J$ = 1 \rarr\ 0) has been used as a tracer of the cold molecular gas in galaxies for 
+over a decade \citep*[\eg][]{Downes98a}. For high-redshift galaxies, the CO($J$ $>$ 1) transition lines are frequently observed as
+ the CO($J$ = 1 \rarr\ 0) line is redshifted to wavelengths that can only be observed with a few telescopes \citep{Carilli13a}, 
+ hence assumptions on the CO excitation conditions are required to derive the molecular gas mass using the H$_{\rm 2}$-to-CO 
+ relation. Prior to the observations of the CO($J$ = 1 \rarr\ 0) line in SMGs, it has been assumed that the molecular gas in the
+  ISM traced by CO transition lines is thermalized due to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
+   Nonetheless, recent CO($J$ = 1 \rarr\ 0) observations have demonstrated that SMGs can indeed be subthermally excited
+   \citep{Bothwell13a, Harris10a}. Based on SMGs with observations of both the \CO and the CO($J$ = 1 \rarr\ 0) lines, the 
+   brightness temperature ratio between \CO
+and ($J$ = 1 \rarr\ 0) has been inferred as $R_{\rm 31}<$ 0.8 \citep
+   {Harris10a,Carilli10a,Swinbank2010a,Ivison11a,Ivison10d}. In contrast, observations of high-redshift quasar hosts suggest that the ratio 
+   is $\sim$1 \citep{Riechers06a, Riechers11a, Scott11a}. 
+Here, we derive the molecular gas mass assuming thermalized excitation of CO, i.e., we adopt $R_{\rm 31}$ = 1 as SMM J0939 is 
+postulated to be hosting a quasar. We calculate the CO($J$ = 1 \rarr\ 0) line luminosity using standard relation 
 \citep[\eg][]{Solomon05a,Carilli13a}:
@@
 \end{equation}
-this corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ \pmOne (\rm K km s
-\pmOne pc$^2$)
-after lensing correction. The inferred total molecular gas mass is therefore M$_{\rm gas}$ = (3.3$\pm$0.7) $\times
-$10$^{10}$ ($\alpha$/0.8) \Msun. We assumed a conversion factor of $\alpha_{\rm CO}$ =
-0.8 \Msun (\LpU)\pmOne based on empirical relations from local ULIRGs, which is typically
-adopted for SMGs \citep{Bothwell13a,Tacconi10a,Daddi2010a}. 
-Combining with the dust mass derived from SED fitting, the gas-to-dust
-ratio is $f_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 63.74 $\pm$ blah , which is in good agreement with the range 
+this corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ \LpU after lensing correction.
+The inferred total molecular gas mass is therefore $M_{\rm gas}$ = (3.3 $\pm$ 0.9) $\times
+$10$^{10}$ \Msun. We assumed a conversion factor of $\alpha_{\rm CO}$ =
+0.8 \Msun (\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
+adopted for SMGs \citep[\eg][]{Bothwell13a,Tacconi10a,Daddi2010a}. 
+The gas-to-dust
+ratio is $f_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 63.74 $\pm$ blah , this is in good agreement with the range 
 of values found in other SMGs \citep{Coppin08a}.
-
-% ~ 120 for MW (Coppin 2007)
-% ~ 60 for typical SMG (coppin 2008)
-% ~ 100 for LBG (coppin 2007)
 
@@
 We derive the star formation rate (SFR) using the \citet{Kennicutt98a} relation, assuming a \citet{Chabrier03a}
-stellar initial mass (IMF) function: SFR = 1.0 $\times$ 10$^{-10}\times$ ($L_{\rm IR\ or\ FIR}$). This yields SFR$_{\rm IR}$ 
-= (909.12 $\pm$ 155.67) $\times\ (\mu/9.74)^{-1}$ [$M\sun$ yr\pmOne] and SFR$_{\rm FIR}$ (547.71 $\pm$ 89.28) $\times(\mu/9.74)^{-1}$ [M$
-\sun$ yr\pmOne] using lensing-corrected (far-)infrared luminosities (L$_{\rm IR}$ and L$_{\rm FIR}$) derived from our SED 
+stellar initial mass (IMF) function. This yields SFR$_{\rm IR}$ 
+= 909.12 $\pm$ 155.67 $M\sun$ yr\pmOne and SFR$_{\rm FIR}$ = 547.71 $\pm$ 89.28 $M
+\sun$ yr\pmOne\ using lensing-corrected (far-)infrared luminosities (L$_{\rm IR}$ and L$_{\rm FIR}$) derived from SED 
 fitting, and assuming negligible contributions from AGN heating.
@@
 Assuming constant SFR, the minimum time for which the starburst in SMM J0939 can be maintained at its
-current SFR is approximated by the gas depletion timescale $\tau$ = $M_{\rm gas}$/SFR, which is $\tau_{\rm IR}$ = 36.33$\pm$ blah 
-Myr, and $\tau_{\rm FIR}$ = 60.30$\pm$blah Myr.
+current SFR can be approximated as the gas depletion timescale, $\tau$ = $M_{\rm gas}$/SFR. 
+This corresponds to $\tau_{\rm IR}$ = 36.33 $\pm$ blah Myr, and $\tau_{\rm FIR}$ = 60.30 $\pm$ blah Myr.
 
-Move to discussion: Compare THIS NUMBER: with other SMGs (\eg \citep{Greve05a}).
+Move to discussion: Compare THIS NUMBER: with other SMGs \citep[\eg][]{Greve05a}.
 
-\subsection{SFE}
+\subsection{star formation efficiency}
 The SFR per unit mass of molecular gas is commonly taken as a
-measure of the star formation efficiency, SFE = SFR/$M_{\rm gas}$. We compute the ratio using lensing-corrected (far-)infrared 
-luminosities ($L_{\rm IR}$ or $L_{\rm FIR}$) and CO($J$ = 1 \rarr 0) luminosity SFE = $L_{\rm F/IR}$/\Lp, this ratio makes no assumptions on the gas mass conversion factor $\alpha$ and is independent of the
+measure of the star formation efficiency, SFE = SFR/$M_{\rm gas}$. We compute this ratio using lensing-corrected (far-)infrared 
+luminosities ($L_{\rm IR}$, $L_{\rm FIR}$) and CO($J$ = 1 \rarr\ 0) luminosity: SFE = $L_{\rm F/IR}$/\Lp, this ratio makes no assumptions on the gas mass conversion factor $\alpha$ as well as the 
 choice of IMF, however, this assumes that differential lensing effect between the CO and infrared emission is negligible. 
+The resulting ratios are SFE$_{\rm IR}$ = 220.22 $\pm$ blah Myr\pmOne\ and SFE$_{\rm FIR}$ = 132.68 $\pm$ blah Myr\pmOne, which are comparable
+to what is found in "typical" SMGs \citep{Riechers10, Tacconi06, Greve05a}.
 
-We find a ratio of SFE$_{\rm IR}$ = 220.22 Myr\pmOne and SFE$_{\rm FIR}$ = 132.68 Myr\pmOne, which are comparable
-to what is found in "typical" SMGs (tacconi et al. 2006, Riechers et al. 2010, cite).
-Greve 05.
-
-\subsection{Dynamical mass} %% check half light radius error, and comparison
+\subsection{Dynamical mass} 
 We derive the dynamical mass of SMM J0939 using an isotropic virial estimator \citep[\eg][]{Engel10a}:
 \begin{equation}
-M_{\rm dyn} = 2.8\times 10^5\Delta \rm v_{\rm line}^ 2 R_{\rm eff}
+M_{\rm dyn} = 2.8\times 10^5\Delta v_{\rm line}^ 2 R_{\rm eff}
 \end{equation}
-where the line width $\Delta \rm v_{\rm line}^ 2$ is based on our \CO line
-measurement and $R_{\rm eff}$ is approximated with the half-light radius of the best-fit lens model. This yields $M_{\rm dyn}$ = blah, and gas-to-
-dynamical mass fraction of $f_{\rm gas-to-dyn}$ = 2.03.
+where we employ the FWHM line width of our \CO measurement for $\Delta v_{\rm line}$,
+and the half-light radius from lens modeling for $R_{\rm eff}$, assuming the dust emission traces the same emitting region as the CO.
+This yields $M_{\rm dyn}$ = blah, and gas-to-dynamical mass fraction of $f_{\rm gas-to-dyn}$ = BLAH2.03.
 
@@
 
-A lensed SMG that is likely to be hosting a type-2 quasar, this source offers an exceptional opportunity to
+This paper focuses on a blah source J0939+8315, a lensed SMG that is likely to be hosting a type-2 quasar, this source offers an exceptional opportunity to
 investigate the gas mass and dynamics of this
@@
 In this paper, we present blah of a strongly lensed blah at z = 2.221, at the epoch of cosmic star formation (cite)
-This paper focuses on a blah source J0939+8315, a lensing galaxy.
+
 We report a detection of \CO line.
@@
 
-We perform SED fitting of the SMG to get M$_{\rm dust}$, L$_{\rm FIR}$ of blah, L$_{\rm IR}$ of blah, yielding SFR of 
+The properties of this SMG blah, M$_{\rm dust}$, L$_{\rm FIR}$ of blah, L$_{\rm IR}$ of blah, yielding SFR of 
 blah . Comparing our findings to other SMGs / similar populations, we find blah, which is blah.
@@
 We compare the properties of SMM J0939 with two other SMGs with detailed studies -- HLSW-01 and the cosmic Eyelash.
-All sources are lensed, making spectral lines measurements relatively feasible than their fainter, un-lensed ``siblings".
+All sources are lensed, making spectral lines measurements relatively feasible than the fainter, un-lensed sources of the same population.
 

### 2015-06-29 skeleton.tex
before today's correction, going to stick with IR L derived properties

@@
 \begin{document}
-\title{\CO observation in a strongly lensed type-2 quasar host SMG at $z$ = 2.221 with
-continuum detection in the lensing FR-II galaxy 3C220.3}
-\author{T. K. Daisy Leung\altaffilmark{1} and Dominik R. Riechers}
-\affil{Astronomy Department, Cornell Unviersity}
-\altaffiltext{1}{tleung@astro.cornell.edu}
+\title{A Massive Molecular Gas Reservoir in the $z$ = 2.221 Type-2 Active Galactic Nucleus Host Galaxy SMM J0939+8315 lensed by the Radio Galaxy 3C220.3}
+\author{T. K. Daisy Leung and Dominik A. Riechers}
+\affil{Department of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14853, USA; tleung@astro.cornell.edu}
 
@@
 foreground radio galaxy 3C220.3 and a companion galaxy at $z$ = 0.685.
-A lensing magnification of $\mu_{\rm 1 mm}$ = 9.74 $\pm$ 1.4 amplified the intrinsic luminosities of the CO emission.
+A lensing magnification of $\mu_{\rm L}$ = 9.74 $\pm$ 1.4 amplified the intrinsic luminosities of the CO emission.
 This allows us to place constraints on the intrinsic properties
@@
  far-infrared (FIR) wavelengths. Followup observations of SMGs discovered in large sky surveys (e.g., HERMES, HATLAS) with sub-(mm) facilities have led to growing consensus
-  of the observable properties of SMGs (cite). SMG is a population of high-redshift galaxy that are typically dusty, gas-rich, 
-  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) in infrared with high star formation rates ($\gtrsim $ 500 \Msun yr\pmOne). (e.g., Lagache et al. 2005, cite more recent). \par
+  of the observable properties of SMGs (cite, blah). SMG is a population of high-redshift galaxy that are typically dusty, gas-rich, 
+  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) in infrared with high star formation rates ($\gtrsim $ 500 \Msun yr\pmOne) \citep[\eg][]{Lagache05a}.
+
   To characterize the physical properties of the gas reservoirs in the ISM where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to the high abundance of this molecule in the ISM as well as its low excitation energy, the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep{Carilli13a}.
@@
 provided evidence that SMGs have large gas reservoirs typical of \textgreater 10$^{10}$\Msun.
-In most cases, detailed studies are carried out on SMGs that are gravitationally lensed, lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys (Negrello 10, cite).
+In most cases, detailed studies are carried out on SMGs that are gravitationally lensed as lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a}.
 \par
@@
 Array for Research in Millimeter Astronomy (CARMA) in the background SMG
-SMM J0939 at $z$ = 2.221. The underlying radio continuum at 104 GHz allows us to put constraints on the SED of the 
+SMM J0939 at $z$ = 2.221. The underlying continuum at 104 GHz allows us to put constraints on the SED of the 
 foreground radio galaxy.
@@
 redshifted to $\nu_{obs}$ = 107.357 GHz (2.794 mm) towards the background galaxy SMM
-J0939+8315 ($z$ = 2.221) were carried out using CARMA (programme ID: cf0142; P.I.: D. Riechers).
-We used the 3mm receivers with a bandwidth of 3.75 GHz in each sideband, at 5.208 MHz ($\sim$14.5 km s\pmOne)
+J0939 ($z$ = 2.221) were carried out using CARMA (programme ID: cf0142; P.I. Riechers).
+We used the 3mm receivers with bandwidth of 3.75 GHz in each sideband, at 5.208 MHz ($\sim$14.5 km s\pmOne)
 resolution to cover the \CO line and the underlying 2.877 mm continuum emission. The CO($J$ = 3 
-\rarr 2) line was placed on the
+\rarr 2) line was placed in the
 upper sideband with the local oscillator frequency tuned to $\nu_{\rm LO}$ = 104.2609 GHz.
 Observations were carried out under good
-weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
+weather conditions in E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
 equivalent on-source time after discarding unusable visibility data.
@@
 $15\% calibration accuracy.
-The {\sc MIRIAD} package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
+The {\sc MIRIAD} package was used to calibrate and analyze the visibility data which are deconvolved and imaged using
 the CLEAN algorithm with ``natural" weighting, this yields a synthesized clean beam size of 13$\farcs$57 $\times$ 
-5\farcs77 . The final rms noise is $\sigma$ = 0.7 Jy km s\pmOne $\rm beam^{-1}$ over
-a channel width of 135.4 MHz (corresponding to $\sim$378.1 km s\pmOne). The continuum image is created by
-averaging over all the line-free channels, this yields a synthesized clean beam size of 16\farcs67 $\times$ 7\farcs17 and a 
+5\farcs77 for the upper sideband image cube.
+The final rms noise is $\sigma$ = 0.7 Jy km s\pmOne $\rm beam^{-1}$ over channel width of 145.8 MHz (corresponding to $\sim$407.2 km s\pmOne).
+The continuum image is created by
+averaging over all the line-free channels, this yields a synthesized clean beam size of 16\farcs67 $\times$ 7\farcs17 and 
 rms noise of 0.55 mJy beam\pmOne.
@@
 foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum to be dominated by emissions from the foreground galaxy.
-We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission, the deconvolved source size is 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60, and the integrated flux density is 7.18 $\pm$ 0.69 mJy.
+We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission, the deconvolved source size of 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60, and the integrated flux density of 7.18 $\pm$ 0.69 mJy.
 At the peak position of the continuum emission, the peak flux density is S$_\nu$ = 5.56 $\pm$ 0.54
@@
 emission start at $\pm$4$\sigma$ of $\sigma$ = 0.0641 mJy beam\pmOne and increment at steps of $\pm$2$^n\sigma$, 
-where n is positive integers; contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
+where n is positive integer; contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
 of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne.
@@
 We construct a velocity-integrated (0th moment) map of the \CO
-emission using the continuum-subtracted data in the visibility plane, this results in velocity-integrated \CO line flux of $S_{\rm CO}$ = 14.6 $\pm$ 0.9 Jy km s\pmOne over a velocity range of $\Delta v$ = $\sim$378.1 km s\pmOne, the uncertainty does not include $\sim$ 15\% calibration uncertainty.
-We ignore the primary beam correction given that the source is close to the phase center, and that the source is unresolved (\ie much smaller than the primary beam size).
+emission using the continuum-subtracted data in the visibility plane, this results in velocity-integrated \CO line flux of $S_{\rm CO}$ = 14.6 $\pm$ 0.9 Jy km s\pmOne over a velocity range of $\Delta v$ = $\sim$407.2 km s\pmOne, the uncertainty does not include $\sim$ 15\% calibration uncertainty.
+We ignore primary beam correction given that the source is close to the phase center, and that the source is unresolved (\ie much smaller than the primary beam size).
 
@@
 To study the intrinsic properties of the background galaxy, we determine the magnification factor by performing
-lens modeling using the SMA 1 mm archival data of this system. The lens modeling is carried out in the visibility
-(uv-) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}
-\citep{Bussmann15a}. The code uses affine-invariant Markov chain Monte Carlo (MCMC) to sample the posterior
-probability density function (PDF) of the model parameters. In our lens model, the surface mass densities of both
+lens modeling using the SMA 1 mm archival data of this system. Lens modeling is carried out in the visibility
+(uv-) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}\footnote{https://github.com/sbussmann/uvmcmcfit}
+\citep{Bussmann15a}. The code uses an affine-invariant Markov chain Monte Carlo (MCMC) approach to sample the posterior
+probability density function (PDF) of the model parameters. In the code, the surface mass densities of both
 lenses are represented by singular isothermal ellipsoid (SIE) profiles, and the source is assumed to have an
@@
 We initialize the positions and the Einstein radii of both lenses, and the position of the source using the
-values of the best-fit lens model \citet{Haas14} performed on Keck K-band near-infrared image. For each of
+values of the best-fit lens model that \citet{Haas14} performed on Keck K-band near-infrared image. For each of
 these parameters, we impose a uniform prior in the range $\in\pm$3$\sigma$, where $\sigma$ is the uncertainty
@@
 The best-fit model yields a magnification
-factor of $\mu_{\rm 1mm}$ = 9.73 $\pm$ 1.38, this is consistent the value reported by \citet{Haas14} within errors.
+factor of $\mu_{\rm L}$ = 9.73 $\pm$ 1.38, this is consistent the value reported by \citet{Haas14} within errors.
 The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
@@
 non-negligible contributions from the lobes, and the peak flux density therefore does not appear to be dominated by the core 
-emission. Furthermore, the contours of the 104 GHz continuum are
+emission. Besides, the contours of the 104 GHz continuum are
 centered on the northern lobe as illustrated by the overlay image in Figure \ref{fig:cont}, this further supports our argument.
@@
 between observed-frame 70 \micron-1000 \micron, and interferometric data with SMA at 1 mm (H14). We use the publicly
-available software {\sc mbb\_emcee} to perform SED fitting, the code uses an affine-invariant Markov chain Monte
+available software {\sc mbb\_emcee}\footnote{https://github.com/aconley/mbb\_emcee} to perform SED fitting, the code uses an affine-invariant Markov chain Monte
 Carlo (MCMC) approach, the details are described by \citet{Riechers13a} and \citet{Dowell14a}. The
-functional form of the fit comprises of a modified blackbody function with a power law S$_{\lambda} \propto \lambda^\alpha
+functional form of the fit comprises of a single-temperature, modified blackbody function with a power law S$_{\lambda} \propto \lambda^\alpha
 $ attached to the blue
@@
 all quantities are expressed in the observed-frame. We find a dust mass of $M_{\rm dust}$ =
-50.47$^{20.42}_{-20.15}\times$10$^8$\Msun, the uncertainties do not include those of $\kappa_{\nu}$. These values are based on SED fitting to the photometric data, i.e. prior
+50.5$^{20.4}_{-20.2}\times$10$^8$\Msun, the uncertainties do not include those of $\kappa_{\nu}$. These values are based on SED fitting to the photometric data, i.e. prior
 to lensing correction.
@@
 The ground state CO transition line, CO($J$ = 1 \rarr\ 0) has been used as a tracer of the cold molecular gas in galaxies for 
-over a decade \citep*[\eg][]{Downes98a}. For high-redshift galaxies, the CO($J$ $>$ 1) transition lines are frequently observed as
+over a decade \citep*[\eg][]{Downes98a,Wilson70a}. For high-redshift galaxies, the CO($J$ $>$ 1) transition lines are frequently observed as
  the CO($J$ = 1 \rarr\ 0) line is redshifted to wavelengths that can only be observed with a few telescopes \citep{Carilli13a}, 
@@
    brightness temperature ratio between \CO
-and ($J$ = 1 \rarr\ 0) has been inferred as $R_{\rm 31}<$ 0.8 \citep
+and ($J$ = 1 \rarr\ 0) has been inferred as $R_{\rm 31}\ <$ 0.8 \citep
    {Harris10a,Carilli10a,Swinbank2010a,Ivison11a,Ivison10d}. In contrast, observations of high-redshift quasar hosts suggest that the ratio 
-   is $\sim$1 \citep{Riechers06a, Riechers11a, Scott11a}. 
+   is $R_{\rm 31}\ \sim\ $1 \citep{Riechers06a, Riechers11a, Scott11a}. 
 Here, we derive the molecular gas mass assuming thermalized excitation of CO, i.e., we adopt $R_{\rm 31}$ = 1 as SMM J0939 is 
@@
 \end{equation}
-this corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ \LpU after lensing correction.
-The inferred total molecular gas mass is therefore $M_{\rm gas}$ = (3.3 $\pm$ 0.9) $\times
+this corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ \LpU\ after lensing correction.
+The inferred total molecular gas mass is therefore $M_{\rm gas}$ = (3.303 $\pm$ 0.696) $\times
 $10$^{10}$ \Msun. We assumed a conversion factor of $\alpha_{\rm CO}$ =
 0.8 \Msun (\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
-adopted for SMGs \citep[\eg][]{Bothwell13a,Tacconi10a,Daddi2010a}. 
+adopted for SMGs \citep[\eg][]{Tacconi10a,Bothwell13a}. 
 The gas-to-dust
@@
 current SFR can be approximated as the gas depletion timescale, $\tau$ = $M_{\rm gas}$/SFR. 
-This corresponds to $\tau_{\rm IR}$ = 36.33 $\pm$ blah Myr, and $\tau_{\rm FIR}$ = 60.30 $\pm$ blah Myr.
+This corresponds to $\tau_{\rm IR}$ = 36.33 $\pm$ 2.96 Myr, and $\tau_{\rm FIR}$ = 60.30 $\pm$ 42.20 Myr.
 
@@
 
-\subsection{star formation efficiency}
+\subsection{Star formation efficiency}
 The SFR per unit mass of molecular gas is commonly taken as a
@@
 choice of IMF, however, this assumes that differential lensing effect between the CO and infrared emission is negligible. 
-The resulting ratios are SFE$_{\rm IR}$ = 220.22 $\pm$ blah Myr\pmOne\ and SFE$_{\rm FIR}$ = 132.68 $\pm$ blah Myr\pmOne, which are comparable
+The resulting ratios are SFE$_{\rm IR}$ = 220.22 $\pm$ 15 Myr\pmOne\ and SFE$_{\rm FIR}$ = 132.68 $\pm$ blah Myr\pmOne, which are comparable
 to what is found in "typical" SMGs \citep{Riechers10, Tacconi06, Greve05a}.
@@
 and the half-light radius from lens modeling for $R_{\rm eff}$, assuming the dust emission traces the same emitting region as the CO.
-This yields $M_{\rm dyn}$ = blah, and gas-to-dynamical mass fraction of $f_{\rm gas-to-dyn}$ = BLAH2.03.
+This yields $M_{\rm dyn}$ = (7.32 $\pm$ 3.14) $\times$ 10$^{10}$\Msun , and gas-to-dynamical mass fraction of $f_{\rm gas-to-dyn}$ = $\approx$ 0.45, consistent that of other SMGs \citep{Greve06a,Tacconi06a}.
 
-Compare to other. blah blah blah dynamical mass, is it consistent with molecular gas mass?
-
-\subsection{SFR surface density}
-% using dynamical mass and Eddington luminosity limit
+\subsection{SFR and gas surface densities}
 To compute surface densities we divided half of the star formation rate or gas mass (so that no assumption of IMF) by the area subtended by the half-light (or effective) radius.
+ the surface density of star formation against the molecular gas surface density.
 
@@
 
+We derive physical properties of the molecular gas in the ISM using IR as well as FIR luminosities.
+As studies have shown that contaminations of AGN in the FIR is less than blah \%, while most studies on SMGs uses the bolometric IR luminsoity, hence we derive these quantities using LIR as well for comparison.
+
 We compare the properties of SMM J0939 with two other SMGs with detailed studies -- HLSW-01 and the cosmic Eyelash.
@@
 \includegraphics[width=0.90\textwidth]{Figure/posteriorPDFs}
-\caption{Figure shows the marginalized posterior probabilities of each parameter in our lens modeling.
+\caption{Marginalized posterior probabilities of each parameter in our lens modeling.
 \label{fig:LensPDF}}
@@
 \centering
-\includegraphics[width=0.55\textwidth]{Figure/CorrelationPlot__thick_500_500}
-\includegraphics[width=0.55\textwidth]{Figure/CorrelationPlot__thin_testSMA}
-\caption{Resulting correlation plot from our SED fitting. Plots on the diagonal axes are marginalized posterior probability 
+\includegraphics[width=0.47\textwidth]{Figure/CorrelationPlot__thick_500_500}
+\includegraphics[width=0.47\textwidth]{Figure/CorrelationPlot__thin_testSMA}
+\caption{Correlation plots from our SED fitting. Plots on the diagonal axes are marginalized posterior probability 
 distribution of each
-parameter. Off-diagonal plots are 2D histograms between parameters. Cross denotes where the best-fit value corresponds to in 
+parameter. Off-diagonal plots are 2D histograms between parameters. Crosses denote the best-fit values in 
 the 2D correlation plot. Top: Optically thick
-model. Bottom: Optically thin model. The parameter T/(1+z) is the observed-frame characteristic dust temperature.
+model. Bottom: Optically thin model. $T/(1+z)$ is the observed-frame characteristic dust temperature.
 \label{fig:sedlikelihood}}

### 2015-06-30 skeleton.tex
Changed plot settings for SED betting showing errors and points; change tick colors; changed cont and line zoom to match; edited paper based on DR's comments

@@
 We report the detection of \CO line emission in SMM J0939+8315 at $z$ = 2.221, a
-strongly lensed high-redshift submillimeter galaxy (SMG) hosting a type-2 quasar using
-the Combined Array for Research in Millimeter-wave Astronomy (CARMA). This lensing system consists of a
-foreground radio galaxy 3C220.3 and a companion galaxy at $z$ = 0.685.
-A lensing magnification of $\mu_{\rm L}$ = 9.74 $\pm$ 1.4 amplified the intrinsic luminosities of the CO emission.
-This allows us to place constraints on the intrinsic properties
-of the cold gas and dust in the interstellar medium (ISM) of the background quasar host SMG. Prior to correcting for lensing 
-amplification, we measure the
-velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (14.6 $\pm$ 0.9) Jy km s\pmOne,
+strongly lensed high-redshift submillimeter galaxy (SMG) using
+the Combined Array for Research in Millimeter-wave Astronomy (CARMA). The lensing system consists of a
+foreground radio galaxy 3C220.3 and a companion galaxy at $z$ = 0.685. This allows us to place constraints on the intrinsic properties
+of the cold gas and dust in the interstellar medium (ISM) of the background SMG which hosts a type-2 quasar. Prior to correcting for lensing 
+amplification, we measure a velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (14.6 $\pm$ 0.9) Jy km s\pmOne,
 corresponding to a lensing-corrected CO($J$ = 1 \rarr 0) line luminosity of \Lp = (4.1 $\pm$ 
@@
 \section{Introduction}\label{sec:intro}
-Submillimeter-selected galaxies (SMGs) are predominantly found at redshift $z \sim$ 1-3, during the epoch of stellar mass and 
+Submillimeter-selected galaxies (SMGs) are predominantly found at redshift $z \sim$ 1$-$3, during the epoch of stellar mass and 
 galaxy assembly. These galaxies are luminous in submillimeter (submm) due to the re-radiation from the dust components in the
- far-infrared (FIR) wavelengths. Followup observations of SMGs discovered in large sky surveys (e.g., HERMES, HATLAS) with sub-(mm) facilities have led to growing consensus
+ far-infrared (FIR) wavelengths. Followup observations of SMGs discovered in large sky surveys (e.g., HerMES, H-ATLAS) (cite) with sub-(mm) facilities have led to growing consensus
   of the observable properties of SMGs (cite, blah). SMG is a population of high-redshift galaxy that are typically dusty, gas-rich, 
@@
   To characterize the physical properties of the gas reservoirs in the ISM where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to the high abundance of this molecule in the ISM as well as its low excitation energy, the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep{Carilli13a}.
-Recent observations of the CO line of SMGs at $z \sim$ 1-3 have
+Recent observations of the CO line of SMGs at $z \sim$ 1$-$3 have
 provided evidence that SMGs have large gas reservoirs typical of \textgreater 10$^{10}$\Msun.
@@
 type-2 quasar at $z$ = 2.221. SMM J0939 is being strongly lensed by a double-lobed Fanaroff-Riley Class II (FR-II) \citep*{Fanaroff74} radio galaxy (3C220.3) which has a 
-companion galaxy B at $z$ = 0.685, separated by 1\farcs5. SMM J0939 is currently
-the brightest known lensed
+companion galaxy B at $z$ = 0.685, separated by 1\farcs5. SMM J0939 is currently one of the brightest known lensed
 SMGs, with lensing-magnified flux density of SMM J0939 $F_{\rm 250\mu m}$ = 440 $\pm$ 15 mJy. The redshift of SMM J0939 has 
@@
  and HeII 1640\AA\
-line emissions \citep[hereafter H14]{Haas14}, these line detections provide conceivable evidence of AGN activity in this SMG, as well as the identification of a type-2 quasar.
+line emissions \citep[hereafter H14]{Haas14}. These line detections provide conceivable evidence of active galactic nuclei (AGN) activity in this SMG, suggesting the presence of a type-2 quasar.
 
-In this paper, we present the detection of \CO line emission obtained with the Combined
-Array for Research in Millimeter Astronomy (CARMA) in the background SMG
-SMM J0939 at $z$ = 2.221. The underlying continuum at 104 GHz allows us to put constraints on the SED of the 
+In this paper, we present the detection of \CO line emission in the background SMG
+SMM J0939 at $z$ = 2.221 obtained with the Combined
+Array for Research in Millimeter Astronomy (CARMA). The underlying continuum at 104 GHz allows us to put constraints on the SED of the 
 foreground radio galaxy.
@@
 This paper is organized as follows: in \S \ref{sec:obs}, we describe the
-observations of the \CO line emission with CARMA; in \S \ref{sec:res}, we report the
-detection of the CO line in the background galaxy as well as the continuum in the foreground galaxy; in \S
+observations of \CO line emission with CARMA; in \S \ref{sec:res}, we report the
+detection of CO emission in the background galaxy, as well as continuum emission in the foreground galaxy; in \S
 \ref{sec:Lens}, we present our lens modeling analysis; in \S \ref{sec:SED}, we perform SED fitting to 3C220.3
-and SMM J0939 and derive the intrinsic properties of the interstellar medium (ISM) in the SMG; in \S \ref{sec:conclusions}, we
-conclude our findings by comparing to other SMGs at similar redshifts.
+and SMM J0939, and derive the intrinsic properties of the interstellar medium (ISM) in the SMG; in \S \ref{sec:conclusions}, we
+conclude our findings by comparing to other similarly bright, strongly-lensed SMGs at similar redshifts.
 
@@
 Observations of the \CO rotational transition ($\nu_{\rm rest}$ = 345.7959899 GHz),
-redshifted to $\nu_{obs}$ = 107.357 GHz (2.794 mm) towards the background galaxy SMM
+redshifted to $\nu_{obs}$ = 107.357 GHz (2.79 mm) towards the background galaxy SMM
 J0939 ($z$ = 2.221) were carried out using CARMA (programme ID: cf0142; P.I. Riechers).
@@
 The {\sc MIRIAD} package was used to calibrate and analyze the visibility data which are deconvolved and imaged using
-the CLEAN algorithm with ``natural" weighting, this yields a synthesized clean beam size of 13$\farcs$57 $\times$ 
-5\farcs77 for the upper sideband image cube.
-The final rms noise is $\sigma$ = 0.7 Jy km s\pmOne $\rm beam^{-1}$ over channel width of 145.8 MHz (corresponding to $\sim$407.2 km s\pmOne).
+the CLEAN algorithm with ``natural" weighting, this yields a synthesized clean beam size of 13$\farcs$5 $\times$ 
+5\farcs8 for the upper sideband image cube.
+The final rms noise is $\sigma$ = 0.7 Jy km s\pmOne $\rm beam^{-1}$ over channel width of 145.8 MHz (corresponding to $\sim$407 km s\pmOne).
 The continuum image is created by
-averaging over all the line-free channels, this yields a synthesized clean beam size of 16\farcs67 $\times$ 7\farcs17 and 
+averaging over all the line-free channels, this yields a synthesized clean beam size of 16\farcs7 $\times$ 7\farcs2 and an 
 rms noise of 0.55 mJy beam\pmOne.
@@
 
-We fix the phase center to coordinates ($\alpha$, $\delta$) (J2000) = (144.84809\degr, 83.25725\degr), the
+We fix the phase center to coordinates ($\alpha$, $\delta$) (J2000) = (9:39:23.54, 83:15:26.10), the
 offset positions of the lenses and source are referenced to this phase center. The primary lens (3C220.3) is
@@
 \includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_goodfit0771}
-\caption{We perform lens modeling using the latest version of {\sc uvmcmcfit} on the SMA 1 mm continuum data.
-In this two lenses model, we initialize the lenses' positions using the values reported by \citet{Haas14}. Left:
+\caption{Lens modeling of SMM J0939 using {\sc uvmcmcfit} on the SMA 1 mm continuum data.
+In this two lenses model, we initialize the lenses' positions using the values reported by H14. Left:
 Grayscale: Our best-fit model assuming an elliptical Gaussian profile for the background SMG. Magenta ellipses:
 Half-light area of the background SMG. Orange Lines: Critical curves of foreground lenses. Black dots: Positions of
-the two lenses. Red contours: Observed SMA 1 mm continuum. The contours start at 2$\sigma$, incrementing at
+the two lenses. Red contours: Observed SMA 1 mm continuum. The contours start at $\pm$2$\sigma$, incrementing at
 steps of $\pm$2$\sqrt{\rm 2}\sigma$. Right: Solid contours show the positive residuals at the same levels and dashed contours
@@
 The best-fit model yields a magnification
-factor of $\mu_{\rm L}$ = 9.73 $\pm$ 1.38, this is consistent the value reported by \citet{Haas14} within errors.
-The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
+factor of $\mu_{\rm L}$ = 9.74 $\pm$ 1.38, this is consistent the value reported by H14 within errors. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
 1.22 $\pm$ 0.01 (8.75 kpc at $z$ = 0.685) and $\theta_{E}$ = 0.73 $\pm$ 0.02 (5.23 kpc at $z$ = 0.685),
-the corresponding masses within the Einstein radii are $M(\theta < \theta_{\rm E})$ = (4.90 $\pm$ 0.58) $\times$ 10$^{11}$ 
+the corresponding masses within the Einstein radii are RECOMPUTE using MEDIAN $M(\theta < \theta_{\rm E})$ = (4.90 $\pm$ 0.58) $\times$ 10$^{11}$ 
 \Msun\ 
@@
 \subsubsection{3C220.3}
-In the theory of synchrotron emission, continuum emission from extended components of a radio galaxy decreases with increasing frequencies, and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$ where the spectral index $\alpha$ is $\gtrsim$ 0.5.
+Synchrotron continuum emission from extended components of a radio galaxy decreases with increasing frequencies, and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$ where the spectral index $\alpha$ is $\gtrsim$ 0.5.
 While the contribution from extended components decreases, studies using samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises and dominates the flux density at higher frequencies (cite).
-Consequently, we expect the peak flux density in our continuum detection of $S_{\rm 104GHz}$ = 5.56 $\pm$ 0.54 mJy to be dominated by the unresolved core component of the foreground FR-II.
+Consequently, we would naively expect the integrated flux density in our continuum detection of $S_{\rm 104GHz}$ = 7.18 $\pm$ 0.69 mJy to be dominated by the unresolved core component of the foreground FR-II.
 On the other hand, the integrated flux density of 7.18 $\pm$ 0.69 mJy is suggestive of a marginally resolved detection of the extended components with non-negligible emission.
@@
 We investigate this disparity by fitting an SED to existing data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to estimate the flux density of the lobes at the frequency of our continuum measurement.
-For the core, an upper limit of $<$0.17 mJy at 4.6 GHz \citep{Mullin06a}, and a clear detection of 0.8 mJy at 9 GHz (H14) is indicative of a substantially inverted spectrum of the core, although we note that these measurements are taken across epochs.
-All measurements are plotted in Figure \ref{fig:SED}.
+For the core, an upper limit of $<$0.17 mJy at 4.6 GHz \citep{Mullin06a}, and a clear detection of 0.8 mJy at 9 GHz (H14) appears to be indicative of a substantially inverted spectrum of the core, although we note that these measurements are taken across epochs (Figure \ref{fig:SED}).
 \input{table_SED}
@@
 \end{equation}
-where $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_v^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution.
+where $F_{\nu}^{\mathrm lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_v^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution.
 
-The resulting fit is shown in Figure \ref{fig:SED}, the extrapolated flux density at 104 GHz is consistent with the peak flux density of our continuum measurement.
-The 10$\sigma$ detection of the continuum thereby suggests
+The extrapolated flux density at 104 GHz is consistent with the peak flux density of our continuum measurement (Figure \ref{fig:SED}). The 10$\sigma$ detection of the continuum thereby suggests
 non-negligible contributions from the lobes, and the peak flux density therefore does not appear to be dominated by the core 
-emission. Besides, the contours of the 104 GHz continuum are
-centered on the northern lobe as illustrated by the overlay image in Figure \ref{fig:cont}, this further supports our argument.
+emission. Besides, the peak of the 104 GHz continuum is
+centered toward the northern lobe (Figure \ref{fig:cont}), which further supports our argument.
 This finding is consistent with a recent study by \citet{Hardcastle08a}, where a few radio galaxies blah blah.
@@
 \centering
-\includegraphics[width=0.5\textwidth]{Figure/3C220_3FullSED}
-\caption{The SED of 3C220.3 and SMM J0939 including the new measurements presented in this paper. 
-Black dots represent existing data of 3C220.3 (see table \ref{tab:SEDdataRadio}). Red dots at 104 GHz corresponds to 
+\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED}
+\caption{The SED of 3C220.3 (solid blue line) and SMM J0939 (dashed blue line and solid cyan line) including the new measurements presented in this paper. 
+Black dots represent existing data of 3C220.3 (see Table \ref{tab:SEDdataRadio}). Red dots at 104 GHz correspond to 
 our continuum measurements (integrated, peak, and difference). The purple line corresponds to the parabolic function we 
-fit to the data associated with the radio galaxy following \citet{Cleary07a}. The dashed purple line and 
-the solid cyan line correspond to the best-fit SED models of the background SMG. The photometric data of the SMG are reported by \citet{Haas14}. \label{fig:SED}}
+fit to the data associated with the radio galaxy, following \citet{Cleary07a}. The dashed purple line and 
+the solid cyan line correspond to the best-fit SED models of the background SMG. The photometric data of the SMG are reported by H14. \label{fig:SED}}
 \end{figure}
@@
 photometric data obtained with {\it Herschel}/PACS and SPIRE, at wavelengths
-between observed-frame 70 \micron-1000 \micron, and interferometric data with SMA at 1 mm (H14). We use the publicly
+between observed-frame 70 \micron $-$ 500 \micron, and interferometric data with the SMA at 1 mm (H14). We use the publicly
 available software {\sc mbb\_emcee}\footnote{https://github.com/aconley/mbb\_emcee} to perform SED fitting, the code uses an affine-invariant Markov chain Monte
 Carlo (MCMC) approach, the details are described by \citet{Riechers13a} and \citet{Dowell14a}. The
-functional form of the fit comprises of a single-temperature, modified blackbody function with a power law S$_{\lambda} \propto \lambda^\alpha
-$ attached to the blue
-side.
-We fit both an optically thick and optically thin model. In the optically thick case, the wavelength $
-\lambda_0$ = $\frac{c}{\nu_0}$ is an additional parameter which represents where the optical
-depth $\tau_{\nu}$ = ($\nu$/$\nu_0$)$^\beta$ reaches unity. Thus, the functional form of the modified blackbody
+functional form of the fit comprises a single-temperature, modified blackbody function joined to a $S_{\lambda} \propto \lambda^\alpha
+$ power law on the blue
+side of the SED.
+We fit both optically thick and optically thin models. In the optically thick case, the wavelength $
+\lambda_0$ = ${c}/{\nu_0}$ is an additional parameter which represents where the optical
+depth $\tau_{\nu} =$ ($\nu$/$\nu_0$)$^\beta$ reaches unity. Thus, the functional form of the modified blackbody
 in the optically thick regime is as follows:
@@
 $\micron$ flux density, hence this becomes an additional parameter in the fit. In both models, we impose an upper limit on $
-\lambda_0$ to 2000 \micron, and the observed-frame dust temperature $T/(1+z)$ to 60 K. We fix the upper limit on 
+\lambda_0$ to 2000 \micron, and on the observed-frame dust temperature $T/(1+z)$ to 60 K. We fix the upper limit on 
 $\beta$ to be 3.0 and 2.2 for the optically thin model and optically thick model, respectively.
@@
 \input{table_mbb}
-The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in appendix. The best-fit solution of an optically thin
+The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in the Appendix. The best-fit solution of an optically thin
 model corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of an optically thick model
-corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than the optically thin
-model. In the subsequent analysis, we employ the inferred values from the optically thick model.
-The best-fit solution yields a far-infrared (FIR) luminosity of $L_{\rm FIR (42.5-122.5\micron)}$ = 53.33$^{+1.14}_{-1.13}\times$10$^{12}$\Lsun, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$ = 88.52$^{+2.62}_{-2.63}\times$10$
+corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than in the optically thin
+case. In the subsequent analysis, we employ the inferred values from the optically thick model.
+The best-fit solution yields a far-infrared (FIR) luminosity of $L_{\rm FIR (42.5-122.5\micron)}$ = 53.3$^{+1.1}_{-1.1}\times$10$^{12}$\Lsun, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$ = 88.5$^{+2.6}_{-2.6}\times$10$
 ^{12}$\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64 m$^2$ kg\pmOne at 125.0 $
@@
 \end{equation}
-where $S_{\nu}$ is the flux density, $D_{\rm L}$ is the luminosity distance, $\kappa_{\nu}$ is the dust
-absorption coefficient, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function,
+where $S_{\nu}$ is the flux density in ergs/s/cm$^{2}$/Hz , $D_{\rm L}$ is the luminosity distance in cm, $\kappa_{\nu}$ is the dust
+absorption coefficient in cm$^2$ g\pmOne, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function,
 all quantities are expressed in the observed-frame. We find a dust mass of $M_{\rm dust}$ =
@@
 to lensing correction.
-With the limited amount of data in the FIR, $M_{\rm dust}$ is weakly constrained; in another fit to the optically thick model where the upper limit of $\beta$ is set to 3.0, all fitting parameters of the best-fit solution are similar to those using an upper limit of 2.2, we find that the deviation of each is at most $\sim$3\% whereas the dust mass is boosted by a factor of $\sim$2.
+With the limited amount of data in the FIR, $M_{\rm dust}$ is weakly constrained; in another fit to the optically thick model where the upper limit of $\beta$ is set to 3.0, all fitting parameters of the best-fit solution are similar to those using an upper limit of 2.2; we find that while the deviation of each is at most $\sim$3\%, the dust mass is boosted by a factor of $\sim$2.
 
@@
    Nonetheless, recent CO($J$ = 1 \rarr\ 0) observations have demonstrated that SMGs can indeed be subthermally excited
-   \citep{Bothwell13a, Harris10a}. Based on SMGs with observations of both the \CO and the CO($J$ = 1 \rarr\ 0) lines, the 
+   \citep{Harris10a,Riechers11c,Riechers11d,Ivison11a}. Based on SMGs with observations of both the \CO and the CO($J$ = 1 \rarr\ 0) lines, the 
    brightness temperature ratio between \CO
 and ($J$ = 1 \rarr\ 0) has been inferred as $R_{\rm 31}\ <$ 0.8 \citep
-   {Harris10a,Carilli10a,Swinbank2010a,Ivison11a,Ivison10d}. In contrast, observations of high-redshift quasar hosts suggest that the ratio 
+   {Harris10a,Carilli10a,Swinbank2010a,Riechers11d,Ivison11a,Ivison10d}. In contrast, observations of high-redshift quasar hosts suggest that the ratio 
    is $R_{\rm 31}\ \sim\ $1 \citep{Riechers06a, Riechers11a, Scott11a}. 
 Here, we derive the molecular gas mass assuming thermalized excitation of CO, i.e., we adopt $R_{\rm 31}$ = 1 as SMM J0939 is 
-postulated to be hosting a quasar. We calculate the CO($J$ = 1 \rarr\ 0) line luminosity using standard relation 
+postulated to be hosting a type-2 quasar. We calculate the CO($J$ = 1 \rarr\ 0) line luminosity using standard relation 
 \citep[\eg][]{Solomon05a,Carilli13a}:
@@
 \end{equation}
-this corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ \LpU\ after lensing correction.
+where $\nu_{\rm CO (3-2), rest}$ is the rest-frame frequency of \CO in Hz, $D_L^2$ is the luminosity distance in Mpc, and $I_{\rm CO(3-2)}$ is the \CO line intensity in Jy km s\pmOne\.
+This corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ (9.74/$\mu_{\rm L}$) \LpU\ after lensing correction.
 The inferred total molecular gas mass is therefore $M_{\rm gas}$ = (3.303 $\pm$ 0.696) $\times
@@
 0.8 \Msun (\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
-adopted for SMGs \citep[\eg][]{Tacconi10a,Bothwell13a}. 
+adopted for SMGs \citep[\eg][]{Tacconi06a,Tacconi08a,Bothwell13a}. 
 The gas-to-dust
-ratio is $f_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 63.74 $\pm$ blah , this is in good agreement with the range 
-of values found in other SMGs \citep{Coppin08a}.
+ratio is $f_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 64 $\pm$ blah , this is in good agreement with the range 
+of values found in other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.
 
@@
 \end{equation}
-where we employ the FWHM line width of our \CO measurement for $\Delta v_{\rm line}$,
+where $\Delta v_{\rm line}$ is in km s\pmOne, $R_{\rm eff}$ is in kpc, and $M_{\rm dyn}$ is in \Msun.
+We employ the FWHM line width of our \CO measurement for $\Delta v_{\rm line}$,
 and the half-light radius from lens modeling for $R_{\rm eff}$, assuming the dust emission traces the same emitting region as the CO.
@@
 
-The detection of CO in SMM J0939, implying a large molecular gas reservoir, once again demonstrates the active SF in SMGs. 
+The detection of CO in SMM J0939, implying a large molecular gas reservoir, demonstrates the active SF in SMGs. 
 The large CO luminosity suggests that a signification fraction of the FIR luminosity comes from SF, providing power for dust to re-radiate in FIR.
@@
 look at "Lensed QSOs at high z observational, CO measurements (DB)" note
+
+Comparison to CO in other type-2 QSO: F10214+2724 \citep{Riechers11a}
 

### 2015-06-30 Code/Plot_Image.py

@@ -37,8 +37,8 @@ SMA_max = 0.00634805
 VLA_ra = 1.448437499980E+02
 VLA_dec = 8.325666666846E+01
 sizep = 0.0025
-sizePcont_noise = 0.017
-sizePLine = 0.006
+sizePcont_noise = 0.0103
+sizePLine = 0.0103
 ra_center = 144.84933
 dec_center = 83.257175
 
@@ -60,28 +60,30 @@ dy = 0.90
 ########################################
 # intialize base figure
 ########################################
-fvla = aplpy.FITSFigure(label['VLA'][0], \
-        figure=fig, subplot=[x0,row_a,width,dy])
-fvla.show_grayscale(stretch='log', vmin=vla_min, vmax=vla_max, vmid=-0.001)
 
 fcont = aplpy.FITSFigure(label['cont'][0], \
-        figure=fig, subplot=[x0+width+2*x_gap, row_a, width, dy])
+        figure=fig, subplot=[x0,row_a,width,dy])
 fcont.show_colorscale(cmap=mpl.cm.jet, stretch='log', vmin=min_cont, vmax=max_cont, vmid=-0.5)
+
+fvla = aplpy.FITSFigure(label['VLA'][0], \
+        figure=fig, subplot=[x0+width+2*x_gap, row_a, width, dy])
+fvla.show_grayscale(stretch='log', vmin=vla_min, vmax=vla_max, vmid=-0.001)
+
 
 flin = aplpy.FITSFigure(label['lin'][0], \
         figure=fig_line, subplot=[x0,row_a,width,dy])
 flin.show_colorscale(cmap=mpl.cm.jet)   #, vmin=min_line, vmax=max_line, vmid=min_line-0.5, stretch='log')
 fSMA = aplpy.FITSFigure(label['SMA'][0], figure=fig_line, subplot=[x0+width+2*x_gap, row_a, width, dy])
-fSMA.show_grayscale(stretch='log', vmin=SMA_min, vmax=SMA_max, vmid=SMA_min-0.01)
+fSMA.show_grayscale(stretch='log', vmin=SMA_min, vmax=SMA_max, vmid=-0.05)
 
 ########################################
 # Contours
 ########################################
+fcont.show_contour(label['cont'][0], colors='black', levels=sigma_contour_CARMA(sigma_cont), linewidths=1.5, layer='fg')
 fvla.show_contour(label['VLA'][0], colors="lime", levels=sigma_contour_array(sigma_9ghz), linewidths=2, layer='fg')
[…]

### 2015-06-30 Code/SEDfit.py

@@ -20,7 +20,6 @@ axes = {
 }
 matplotlib.rc('axes', **axes)
 
-
 def savefigure(f, verbose=True, dirStr='../Figure/'):
     """
     Save figure in designatied directory and make directory if it doesn't alraedy exist
@@ -373,11 +372,11 @@ errorfill(GHz2um(Radio_Hz[6:] * Hz2GHz),
 ax.errorbar(GHz2um(Radio_Hz[6:] * Hz2GHz),
             Radio_Jy[6:] * Jy2mJy,
             Radio_error[6:] * Jy2mJy,
-            fmt='.k', ecolor='darkgray', label='Previous Data', ms=11, capsize=4, elinewidth=4)      # mJy
+            fmt='.k', ecolor='darkgray', label='Previous Data', ms=11, capsize=8, elinewidth=4, capthick=1.5) # mJy
 
 ax.errorbar(GHz2um(Point_Cont_Hz * Hz2GHz),
             Point_Continuum_Jy * Jy2mJy, Point_error_Jy * Jy2mJy,
-            fmt='.r', ecolor='darkgrey', label='New continuum data', ms=13, capsize=4, elinewidth=4)
+            fmt='.r', ecolor='darkgrey', label='New continuum data', ms=13, capsize=8, elinewidth=4, capthick=1.5)
 
 ax.plot(GHz2um(Core_3c220dot3_Hz[0] * Hz2GHz), Core_3c220dot3_Jy[0] * Jy2mJy,
         'or',
@@ -390,7 +389,7 @@ ax.errorbar(GHz2um(Core_3c220dot3_Hz[1] * Hz2GHz),
 
 yfit = lobeSyn(Radio_Hz[6:], *theta_best)
 # errorfill(GHz2um(Radio_Hz[6:] * Hz2GHz), yfit, Radio_error[6:] * Jy2mJy, ax=ax)
-ax.plot(GHz2um(Radio_Hz[6:] * Hz2GHz), yfit, 'b-', linewidth=4, label='Lobe fit', alpha=0.5)
+ax.plot(GHz2um(Radio_Hz[6:] * Hz2GHz), yfit, 'b-', linewidth=4, label='Lobe fit', alpha=0.35)
 
 epsilon = 50.e9     # extra buffer
 start_Hz = 1e10
@@ -398,8 +397,7 @@ end_Hz = Avg_cont_freq + epsilon
[…]

### 2015-06-30 Code/SEDfit.py
save as pdf

@@ -337,7 +337,7 @@ class Wavelength2FreqTransform(Freq2WavelengthTransform):
 
 
 plt.clf()
-fig = plt.figure(1, figsize=(20, 8))
+fig = plt.figure(1, figsize=(12, 8))
 fig.subplots_adjust(left=0.12, right=0.96, top=0.85, bottom=0.15, wspace=0.39)
 ax = SubplotHost(fig, 1, 1, 1)
 fig.add_subplot(ax)
@@ -429,6 +429,7 @@ ax.set_xscale('log')
 ax.set_yscale('log')
 ax_top.set_xscale('log')
 ax_top.set_yscale('log')
+#ax.set_rasterized(True)
 
 ############################################
 # Save Figure
@@ -438,7 +439,7 @@ response = raw_input('Save fig?: (y/n)')
 if response.lower() in ['y', 'yes']:
     filename = '3C220_3_FullSED'
     savefigure(filename)
-    fig.savefig('../Figure/' + filename + '2.png')
+    fig.savefig('../Figure/' + filename + '2.pdf')
 elif response.lower() in ['n', 'no']:
     plt.show()
 else:

### 2015-06-30 Code/FgContIm.py
calculate line sigma properly with number of channels, add a function to plot low SNR contours

@@ -30,33 +30,50 @@ def sigma_contour_array(sigma):
 
 def sigma_contour_CARMA(sigma):
     """
-    return list of sigma multiples, -3,-2,2,3...11 * sqrt(2) * sigma
+    return list of sigma multiples, -4,-3,3...20  * sigma
     """
-    arr = range(-4, 11)
+    arr = range(-4, 20)
     arr.remove(0)
     arr.remove(1)
+    arr.remove(2)
     arr.remove(-1)
-    arr = [i * np.sqrt(2) * sigma for i in arr]
+    arr.remove(-2)
+#    arr = [i * np.sqrt(2) * sigma for i in arr]
+    arr = [i * sigma for i in arr]
+    return arr
+
+def sigma_contour_lowSNR(sigma):
+    """
+    return list of sigma multiples, -4,-3,-2,2,...20  * sigma
+    """
+    arr = range(-4, 20)
+    arr.remove(0)
+    arr.remove(1)
+#    arr.remove(2)
+    arr.remove(-1)
+#    arr.remove(-2)
+#    arr = [i * np.sqrt(2) * sigma for i in arr]
+    arr = [i * sigma for i in arr]
     return arr
 
 
-def standard_plot_setup(sp, ra_center, dec_center, size):
+def standard_plot_setup(sp, ra_center, dec_center, size, tc='black'):
     sp.set_frame_color('black')
     sp.frame.set_linewidth(1)
     sp.set_system_latex(True)
     sp.recenter(x=ra_center, y=dec_center, radius=size)   # width = blah, height = blah     # Scaling and panning
 
-    sp.tick_labels.set_font(size='medium', weight='bold')      # size='10'
+    sp.tick_labels.set_font(size='large', weight='bold')      # size='10'
     sp.tick_labels.set_style('colons')
     sp.tick_labels.set_xformat('hh:mm:ss')
     sp.tick_labels.set_yformat('dd:mm:ss')
-    sp.ticks.set_color('black')
+    sp.ticks.set_color(tc)
     sp.ticks.set_linewidth(2)
     sp.ticks.set_length(10)
     sp.ticks.set_minor_frequency(4)
     # sp.ticks.set_xspacing(45*15/3600.)        # deg
 
-    sp.axis_labels.set_font(size='medium', weight='bold')      # (size='12')
+    sp.axis_labels.set_font(size='large', weight='bold')      # (size='12')
[…]

### 2015-06-30 Code/Plot_Image.py

@@ -22,7 +22,7 @@ fig_line = plt.figure(2, figsize=(12, 5))
 ########################################
 sigma_9ghz = 6.41094e-05
 sigma_cont = 5.0e-4
-sigma_line = 0.7    # on the mom0 map, MIRIAD imfit RMS residual is 7.45E-01
+sigma_line = 1.49
 sigma_SMA = 0.000836951
 
 vla_min = -0.000270099
@@ -37,8 +37,8 @@ SMA_max = 0.00634805
 VLA_ra = 1.448437499980E+02
 VLA_dec = 8.325666666846E+01
 sizep = 0.0025
-sizePcont_noise = 0.0103
-sizePLine = 0.0103
+sizePcont_noise = 0.00920
+sizePLine = 0.0075
 ra_center = 144.84933
 dec_center = 83.257175
 
@@ -82,9 +82,9 @@ fSMA.show_grayscale(stretch='log', vmin=SMA_min, vmax=SMA_max, vmid=-0.05)
 fcont.show_contour(label['cont'][0], colors='black', levels=sigma_contour_CARMA(sigma_cont), linewidths=1.5, layer='fg')
 fvla.show_contour(label['VLA'][0], colors="lime", levels=sigma_contour_array(sigma_9ghz), linewidths=2, layer='fg')
 fvla.show_contour(label['cont'][0], colors='red', levels=sigma_contour_CARMA(sigma_cont), linewidths=2, layer='fg_cont')
-flin.show_contour(label['lin'][0], colors="white", levels=sigma_contour_CARMA(sigma_line), linewidths=2, layer='mol')
+flin.show_contour(label['lin'][0], colors="white", levels=sigma_contour_lowSNR(sigma_line), linewidths=2, layer='mol')
 fSMA.show_contour(label['SMA'][0], colors="lime", levels=sigma_contour_CARMA(sigma_SMA), linewidths=1.8, layer='bf_cont')
-fSMA.show_contour(label['lin'][0], colors="red", levels=sigma_contour_CARMA(sigma_line), linewidths=2, layer='mol')
+fSMA.show_contour(label['lin'][0], colors="red", levels=sigma_contour_lowSNR(sigma_line), linewidths=2, layer='mol')
 
 ########################################
 # beam

### 2015-06-30 Code/Plot_Image.py
Fix sigma_line for mom0 map using chan 65 to 85

@@ -22,7 +22,7 @@ fig_line = plt.figure(2, figsize=(12, 5))
 ########################################
 sigma_9ghz = 6.41094e-05
 sigma_cont = 5.0e-4
-sigma_line = 1.49
+sigma_line = 1.826
 sigma_SMA = 0.000836951
 
 vla_min = -0.000270099

### 2015-06-30 Code/err.py
to calculate uncertainties using sigma or delta

@@ -1,0 +1,80 @@
+freq_CO32 = 345.651     # GHz
+dl = 19052          # Mpc at 2.221
+z = 2.221
+I_line = 10.7
+del_I = 2.12    # sigma of CO(3-2) line intensity Jy km/s
+mu = 10.1298
+del_mu = 1.38
+alpha = 0.8
+rkpc = 0.105907102426 * 8.406
+del_kpc = 0.03309 * 8.406
+vel = 541.65
+del_vel = 31.9
+LIR = 88.52e12    # before lensing correction, from mbb
+del_IR_noMu = 2.62e12
+M_dust = 50.47e+8  # before lensing correction, from mbb
+sig_Mdust_noMu = 20.42e8
+M_dyn = 7.35e10
+Mgas = 2.326e10    # with lensing correction
+
+#####################
+#####################
+sig_LprimeCO = (3.25e7 / freq_CO32**2 * dl**2 / (1+z))**(.5) * ((del_I/mu)**2 + (del_mu/mu**2*I_line)**2)**(.5)
+del_LprimeCO = 3.25e7 / freq_CO32**2 * dl**2 / (1+z) * ((del_I/mu) + (del_mu/mu**2*I_line))
+
+sig_LprimeCO_noMu = (3.25e7 / freq_CO32**2 * dl**2 / (1+z))**(.5) * (del_I/mu)
+del_LprimeCO_noMu = 3.25e7 / freq_CO32**2 * dl**2 / (1+z) * (del_I/mu)
+
+LprimCO_noMu = 3.25e7/freq_CO32**2 * dl**2 / (1+z) * I_line
+
+sig_Mgas = alpha * sig_LprimeCO
+del_Mgas = alpha * del_LprimeCO
+
+Mgas_noMu = alpha * LprimCO_noMu
+sig_Mgas_noMu = alpha * sig_LprimeCO_noMu
+del_Mgas_noMu = alpha * del_LprimeCO_noMu
+
+# With lensing correction M_dust
+sig_Mdust = ((M_dust/mu**2 * del_mu)**2 + (sig_Mdust_noMu/mu)**2)**(.5)
+del_Mdust = M_dust/mu**2 * del_mu + sig_Mdust_noMu/mu
+
[…]

### 2015-07-04 skeleton.tex
Editing Radio SED section

@@
 of the cold gas and dust in the interstellar medium (ISM) of the background SMG which hosts a type-2 quasar. Prior to correcting for lensing 
-amplification, we measure a velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (14.6 $\pm$ 0.9) Jy km s\pmOne,
-corresponding to a lensing-corrected CO($J$ = 1 \rarr 0) line luminosity of \Lp = (4.1 $\pm$ 
-0.9) $\times$ 10$^{10}$ \LpU. This
-translates to a molecular gas mass of $M_{\rm gas}$ = 3.3 $\times$ 10$^{10}M_\odot$. We report marginally resolved continuum 
+amplification, we measure a velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (10.1 $\pm$ 1.1) Jy km s\pmOne,
+corresponding to a lensing-corrected CO($J$ = 1 \rarr 0) line luminosity of \Lp = (2.7 $\pm$ 
+blah) $\times$ 10$^{10}$ \LpU. This
+translates to a molecular gas mass of $M_{\rm gas}$ = 2.2 $\times$ 10$^{10}M_\odot$. We report marginally resolved continuum 
 emission from the foreground galaxy with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
@@
 \subsection{CARMA} \label{sec:carmadata}
-Observations of the \CO rotational transition ($\nu_{\rm rest}$ = 345.7959899 GHz),
-redshifted to $\nu_{obs}$ = 107.357 GHz (2.79 mm) towards the background galaxy SMM
-J0939 ($z$ = 2.221) were carried out using CARMA (programme ID: cf0142; P.I. Riechers).
-We used the 3mm receivers with bandwidth of 3.75 GHz in each sideband, at 5.208 MHz ($\sim$14.5 km s\pmOne)
-resolution to cover the \CO line and the underlying 2.877 mm continuum emission. The CO($J$ = 3 
-\rarr 2) line was placed in the
-upper sideband with the local oscillator frequency tuned to $\nu_{\rm LO}$ = 104.2609 GHz.
+Observations of the \CO rotational transition ($\nu_{\rm rest}$ = 345.7959899 GHz) towards the background galaxy SMM
+J0939 ($z$ = 2.221) were carried out using CARMA at the redshifted frequency of $\nu_{obs}$ = 107.357 GHz (2.79 mm)  (program ID: cf0142; P.I.: Riechers).
+The 3 mm receivers were used to cover the redshifted CO($J$ = 3 $\rightarrow$ 2) line and the underlying 2.877 mm continuum emission, employing a correlator setup to provide a bandwidth of 3.75 GHz in each sideband and spectral resolution of 5.208 MHz ($\sim$14.5 km s\pmOne).
+The line was placed in the
+upper sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$ 104.2609 GHz.
 Observations were carried out under good
@@
 5\farcs8 for the upper sideband image cube.
-The final rms noise is $\sigma$ = 0.7 Jy km s\pmOne $\rm beam^{-1}$ over channel width of 145.8 MHz (corresponding to $\sim$407 km s\pmOne).
+The final rms noise is $\sigma_{\rm ch}$ = 13.7 mJy beam\pmOne\ per bin with a channel width of $\sim$29 km\pmOne, and $\sigma$ = 1.825 Jy km s\pmOne\ $\rm beam^{-1}$ over a channel width of 218.7 MHz (corresponding to $\sim$610 km s\pmOne).
 The continuum image is created by
@@
 
-% mom0 map channels [72, 85], each channel is 29.088 km/s, i.e. total velocity range is 378.144 km/s, which is 135.408 
+% mom0 map channels [65, 85], each channel is 29.088 km/s, i.e. total velocity range is 610.848 km/s, which is 218.736 
 %MHz
@@
 \subsection{New results: Continuum Emission} 
-Averaging over all the line-free channels, we detect a 10$\sigma$ continuum emission at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz (2.877 mm) in the observed-frame, corresponding to $\sim$2.79 mm at $z$ = 0.658.
+Averaging over all the line-free channels, we detect continuum emission at 10$\sigma$ significance at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz ($\sim$2.9 mm) in the observed-frame, corresponding to 61.8 GHz ($\sim$1.7 mm) at $z$ = 0.658.
 In this lens system, the
 foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum to be dominated by emissions from the foreground galaxy.
-We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission, the deconvolved source size of 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60, and the integrated flux density of 7.18 $\pm$ 0.69 mJy.
+We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission.
+The deconvolved source size is 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60, and the integrated flux density is 7.18 $\pm$ 0.69 mJy.
 At the peak position of the continuum emission, the peak flux density is S$_\nu$ = 5.56 $\pm$ 0.54
 mJy beam\pmOne.
-In Figure \ref{fig:cont}, we show the continuum emission at 104 GHz overlaid on the 9 GHz continuum measurement reported by \citet{Haas14}.
-This figure demonstrates that at the resolution of our observation, the continuum detection is marginally resolved, it is therefore plausible that both non-thermal and thermal emissions from the lobes and the radio core contribute to the integrated flux density in our measurement.
+In Figure \ref{fig:cont}, we show the continuum emission at 104 GHz overlaid on the 9 GHz continuum measurement reported by H14.
+This demonstrates that at the resolution of our observation, the continuum detection is marginally resolved.
+It is therefore plausible that both non-thermal emission from the lobes and the radio core dominate the integrated flux density in our measurement.
 
@@
 \includegraphics[width=0.80\textwidth]{Figure/ContPanel}
-\caption{The central cross on each image indicates the position of the radio core of 3C220.3. Contour levels of the 9 GHz continuum 
-emission start at $\pm$4$\sigma$ of $\sigma$ = 0.0641 mJy beam\pmOne and increment at steps of $\pm$2$^n\sigma$, 
-where n is positive integer; contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
+\caption{The central cross on each image indicates the position of the radio core of 3C220.3. The contour levels of the 9 GHz continuum 
+emission start at $\pm$4$\sigma$ of $\sigma$ = 0.064 mJy beam\pmOne and increment at steps of $\pm$2$^n\sigma$, 
+where n is a positive integer; the contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
 of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne.
-Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 16\farcs67 $\times$ 7\farcs17, at P.A. = 
+Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 16\farcs7 $\times$ 7\farcs2, at P.A. = 
 -58$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
 foreground radio galaxy 3C220.3 overlaid the 9 GHz emission (green) (H14). The rms in the 9GHz image is $\sigma$ 
-= 0.0641 mJy beam\pmOne. The synthesized beam size of the VLA observations is 0$\farcs$60 $\times$ 0$\farcs$23 at P.A. 
+= 0.064 mJy beam\pmOne. The synthesized beam size of the VLA observations is 0$\farcs$6 $\times$ 0$\farcs$2 at P.A. 
 76$\degr$. 
@@
 \subsection{New results: \CO line emission}
-We detect \CO line emission toward the background SMG SMM J0939.
+We detect \CO line emission toward the background SMG SMM J0939 at $z$ = 2.221.
 Figure \ref{fig:mom0} shows the line profile at the peak position of the CO emission.
 Fitting a four-parameter single-component Gaussian to the spectrum yields a peak flux density of 19.9 $\pm
-$ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy, and full width at half-maximum (FWHM) of 541.65 $\pm$ 31.91 km s\pmOne. 
-The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, the 
-synthesized beam size of the SMA observation is 1\farcs42$ \times $1\farcs16, at P.A.
--34.0\degr.
-As such, the \CO detection in the SMG is spatially unresolved.
+$ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy, and full width at half-maximum (FWHM) of 542 $\pm$ 32 km s\pmOne. 
+The spatial extent of the SMG is $\sim$5$\arcsec$ as shown in the Submillimeter Array (SMA) 1 mm dust continuum in Figure \ref{fig:mom0}.
+As such, the \CO emission in the SMG is spatially unresolved.
 We construct a velocity-integrated (0th moment) map of the \CO
-emission using the continuum-subtracted data in the visibility plane, this results in velocity-integrated \CO line flux of $S_{\rm CO}$ = 14.6 $\pm$ 0.9 Jy km s\pmOne over a velocity range of $\Delta v$ = $\sim$407.2 km s\pmOne, the uncertainty does not include $\sim$ 15\% calibration uncertainty.
+emission using the data with continuum subtracted in the visibility plane.
+This results in a velocity-integrated \CO line flux of $S_{\rm CO}$ = 10.7 $\pm$ 0.2 Jy km s\pmOne over the FWZI velocity range of $\Delta v$ = $\sim$914 km s\pmOne, the uncertainty does not include $\sim$ 15\% calibration uncertainty.
 We ignore primary beam correction given that the source is close to the phase center, and that the source is unresolved (\ie much smaller than the primary beam size).
+The \CO spectroscopy confirms the redshift of SMM J0939 at $z$ = 2.221 $\pm$ blah.
 
@@
 \includegraphics[width=0.65\textwidth]{Figure/peak28_WiderSpectrum}
-\caption{The central cross on each image sets the coordinates for alignment between plots. The contour starts at $\pm$3$\sigma$, 
+\caption{The central cross on each image sets the coordinates for alignment between plots. The contour starts at $\pm$2$\sigma$, 
 incrementing at
 steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the \CO line emission in 
-the background SMG with $\sigma$ = 0.7 Jy km s\pmOne beam\pmOne. The angular resolution is 13$\farcs$57 $\times$ 
-5\farcs77, as shown in the bottom left corner. 
-Top Right: Contours of \CO emission (red) overlaid on the SMA 1 mm dust continuum (green) with $
-\sigma$ = 0.84 mJy beam\pmOne. The beam size of the SMA data is 1\farcs42$ \times $1\farcs16, P.A. -34\degr, as shown 
+the background SMG with $\sigma$ = 1.8 Jy km s\pmOne beam\pmOne, over a velocity range of $\Delta v\sim$610 km s\pmOne\. The angular resolution is 13$\farcs$6 $\times$ 
+5\farcs8, as shown in the bottom left corner. 
+Top Right: Contours of \CO emission (red) overlaid on the SMA 1 mm dust continuum (green; H14) with $
+\sigma$ = 0.84 mJy beam\pmOne. The beam size of the SMA data is 1\farcs4$ \times $1\farcs2, P.A. -34\degr, as shown 
 in the bottom left corner. From this image, it is apparent that the extent of the background SMG is smaller than the beam 
 size of the CARMA observations, hence the \CO line detection is spatially unresolved. Bottom: 
-The spectrum at the CO emission peak position with spectral resolution of $\Delta v$ $\sim$29.1 km s\pmOne.
+The spectrum extracted at peak position of the CO emission, the spectral resolution is $\Delta v$ $\sim$29 km s\pmOne\ with an rms of $\sigma_{\rm ch}$ = 12.5 mJy beam\pmOne\ per channel.
 Solid black line shows the Gaussian fit to the \CO line profile. Yellow histogram shows the 
@@
 \centering
-\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_model_goodfit0771}
-\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_goodfit0771}
-\caption{Lens modeling of SMM J0939 using {\sc uvmcmcfit} on the SMA 1 mm continuum data.
-In this two lenses model, we initialize the lenses' positions using the values reported by H14. Left:
-Grayscale: Our best-fit model assuming an elliptical Gaussian profile for the background SMG. Magenta ellipses:
-Half-light area of the background SMG. Orange Lines: Critical curves of foreground lenses. Black dots: Positions of
-the two lenses. Red contours: Observed SMA 1 mm continuum. The contours start at $\pm$2$\sigma$, incrementing at
-steps of $\pm$2$\sqrt{\rm 2}\sigma$. Right: Solid contours show the positive residuals at the same levels and dashed contours
-show the negative residuals. \label{fig:lens}}
+\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_model_goodfit1970}
+\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_goodfit1970}
+\caption{Double-lens modeling of SMM J0939 using {\sc uvmcmcfit} on the SMA 1 mm continuum data.
+The contours start at $\pm$2$\sigma$, incrementing at
+steps of $\pm$2$\sqrt{\rm 2}\sigma$. Solid contours show the positive residuals and dashed contours
+show the negative residuals. 
+Left: SMA 1 mm continuum (red contours) overlaid on the best-fit model (grayscale image) assuming an elliptical Gaussian profile for the background SMG.
+The lenses are represented as black dots and the half-light area of the background source is represented as magenta ellipse, and the orange lines represent the critical curves in the image plane.
+Right: The residual contours overlaid on the image, obtained by taking the Fourier transformed of the difference between the SMA continuum and the best-fit model in the visibility plane.
+\label{fig:lens}}
 \end{figure}
@@
 The best-fit model yields a magnification
-factor of $\mu_{\rm L}$ = 9.74 $\pm$ 1.38, this is consistent the value reported by H14 within errors. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
-1.22 $\pm$ 0.01 (8.75 kpc at $z$ = 0.685) and $\theta_{E}$ = 0.73 $\pm$ 0.02 (5.23 kpc at $z$ = 0.685),
-the corresponding masses within the Einstein radii are RECOMPUTE using MEDIAN $M(\theta < \theta_{\rm E})$ = (4.90 $\pm$ 0.58) $\times$ 10$^{11}$ 
+factor of $\mu_{\rm L}$ = 10.13 $\pm$ 1.38, this is consistent the value reported by H14 within errors. All best-fit
+parameters are listed in Table \ref{tab:lensParam}. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
+1.22 $\pm$ 0.01 (8.75 kpc at $z$ = 0.685) and $\theta_{E}$ = 0.75 $\pm$ 0.02 (5.34 kpc at $z$ = 0.685),
+the corresponding masses within the Einstein radii are $M(\theta < \theta_{\rm E})$ = (4.86 $\pm$ 0.08) $\times$ 10$^{11}$ 
 \Msun\ 
-and $M(\theta < \theta_{\rm E})$ = (1.76 $\pm$ 0.33) $\times$ 10$^{11}$ \Msun, respectively. All best-fit
-parameters are listed in Table \ref{tab:lensParam}.
+and $M(\theta < \theta_{\rm E})$ = (1.82 $\pm$ 0.07) $\times$ 10$^{11}$ \Msun, respectively. 
 \input{table_lensParams}
@@
 \subsubsection{3C220.3}
-Synchrotron continuum emission from extended components of a radio galaxy decreases with increasing frequencies, and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$ where the spectral index $\alpha$ is $\gtrsim$ 0.5.
-While the contribution from extended components decreases, studies using samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises and dominates the flux density at higher frequencies (cite).
-Consequently, we would naively expect the integrated flux density in our continuum detection of $S_{\rm 104GHz}$ = 7.18 $\pm$ 0.69 mJy to be dominated by the unresolved core component of the foreground FR-II.
-On the other hand, the integrated flux density of 7.18 $\pm$ 0.69 mJy is suggestive of a marginally resolved detection of the extended components with non-negligible emission.
-This is plausible given that the orientation of the synthesized beam in our observations is in alignment with the axis along the
-lobes of the radio galaxy, as shown in Figure \ref{fig:cont}.
-We investigate this disparity by fitting an SED to existing data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to estimate the flux density of the lobes at the frequency of our continuum measurement.
-For the core, an upper limit of $<$0.17 mJy at 4.6 GHz \citep{Mullin06a}, and a clear detection of 0.8 mJy at 9 GHz (H14) appears to be indicative of a substantially inverted spectrum of the core, although we note that these measurements are taken across epochs (Figure \ref{fig:SED}).
+Synchrotron continuum emission from extended components of a radio galaxy decreases with increasing frequencies, 
+and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$ where the 
+spectral index $\alpha$ is $\gtrsim$ 0.5. While the contribution from extended components decreases, studies using 
+samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises 
+and dominates the flux density at higher frequencies \citep{Kellermann81a,Begelman84a}. At observed-frame $\sim$90 GHz, 
+observations of the FR-II radio galaxy, 3C220.1 at $z$ = 0.610 has been reported to be the case 
+\citep{Hardcastle08a}. Besides, an upper 
+limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a}, and a clear detection of 0.8 mJy at 9 GHz (H14) appears to 
+be indicative of a substantially inverted spectrum of the core (Figure \ref{fig:SED}).
+Consequently, we would naively expect the integrated flux density in our continuum detection of $S_{\rm 104GHz}$ = 7.18 $\pm$ 0.69 mJy to be dominated by the unresolved core component of the foreground FR-II, which is at $z$ = 0.685.
+== wouldn't this be contradicting if we know the core is unresolved, why would we jump into looking at the integrated flux ==
+However, the inferred deconvolved spatial size of the source matching that in a resolved image (in Figure 1) is 
+suggestive of a marginally resolved detection of the extended components with non-negligible emission. 
+This is plausible given that the orientation of the synthesized beam in our observations is in alignment with the 
+axis along the 
+lobes of the radio galaxy, as shown in Figure \ref{fig:cont}. We investigate this disparity by fitting an SED to 
+existing data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to 
+estimate the flux density of the lobes at the frequency of our continuum measurement. 
 \input{table_SED}
@@
 \end{equation}
-where $F_{\nu}^{\mathrm lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_v^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution.
+where $F_{\nu}^{\mathrm lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_c^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution.
+The extrapolated flux density of the lobe-fit at 104 GHz is consistent with the peak flux density of our continuum measurement (Figure \ref{fig:SED}).
+The 10$\sigma$ detection of the continuum thereby suggests
+a dominant contribution from the lobes, and the peak flux density therefore does not appear to be emission toward the core. Moreover, the peak position of the 104 GHz continuum is
+centered toward the northern lobe (Figure \ref{fig:cont}), which further supports our argument. 
+%This finding 
+%is consistent with a recent study by \citet{Hardcastle08a}, where they reported null detection of the radio cores of 
+%two FR-II radio galaxies 3C 20 at $z$ = 0.174 and 3C 295 at $z$ = 0.461 at observed-frame $\sim$90GHz. 
+We do not extrapolate the core measurements to the frequency of our continuum, as previous measurements of the core are taken 
+across epochs.
 
-The extrapolated flux density at 104 GHz is consistent with the peak flux density of our continuum measurement (Figure \ref{fig:SED}). The 10$\sigma$ detection of the continuum thereby suggests
-non-negligible contributions from the lobes, and the peak flux density therefore does not appear to be dominated by the core 
-emission. Besides, the peak of the 104 GHz continuum is
-centered toward the northern lobe (Figure \ref{fig:cont}), which further supports our argument.
-This finding is consistent with a recent study by \citet{Hardcastle08a}, where a few radio galaxies blah blah.
-At the resolution of our observation, it is unclear whether the integrated flux is dominated by the hotspot or the lobes.
+Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, while others exhibit a clear spectral steepening either between cm and mm wavelengths (e.g., 3C123); at the resolution of our observation, it is unclear whether the integrated flux is dominated by the hotspot or the lobes.
+But it would be important for hotpot emission studies because this is at restframe sim60 GHz,
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED}
+\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED_longticks.pdf}
 \caption{The SED of 3C220.3 (solid blue line) and SMM J0939 (dashed blue line and solid cyan line) including the new measurements presented in this paper. 
@@
 \end{equation}
-where $\nu_{\rm CO (3-2), rest}$ is the rest-frame frequency of \CO in Hz, $D_L^2$ is the luminosity distance in Mpc, and $I_{\rm CO(3-2)}$ is the \CO line intensity in Jy km s\pmOne\.
-This corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ (9.74/$\mu_{\rm L}$) \LpU\ after lensing correction.
+where $\nu_{\rm CO (3-2), rest}$ is the rest-frame frequency of the \CO line in GHz, $D_L^2$ is the luminosity distance in Mpc, and $I_{\rm CO(3-2)}$ is the \CO line intensity in Jy km s\pmOne.
+This corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ (10.73/$\mu_{\rm L}$) \LpU\ after lensing correction.
 The inferred total molecular gas mass is therefore $M_{\rm gas}$ = (3.303 $\pm$ 0.696) $\times
@@
 
+In this paper, we blah. However, many questions regarding jets in radio galaxies remain. For example,
+
 Comparison to CO in other type-2 QSO: F10214+2724 \citep{Riechers11a}

### 2015-07-04 skeleton.tex
Done Radio SED section for now

@@
 samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises 
-and dominates the flux density at higher frequencies \citep{Kellermann81a,Begelman84a}. At observed-frame $\sim$90 GHz, 
+and dominates the flux density at higher frequencies \citep{Kellermann81a,Begelman84a}. At observed-frame $\sim$ 90 GHz, 
 observations of the FR-II radio galaxy, 3C220.1 at $z$ = 0.610 has been reported to be the case 
 \citep{Hardcastle08a}. Besides, an upper 
-limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a}, and a clear detection of 0.8 mJy at 9 GHz (H14) appears to 
+limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a} and a clear detection of 0.8 mJy at 9 GHz (H14) appears to 
 be indicative of a substantially inverted spectrum of the core (Figure \ref{fig:SED}).
@@
 \input{table_SED}
-Following Equation (1) in \citet{Cleary07a}, the fit to the lobes can be expressed as a parabolic function:
+Following Equation (1) in \citet{Cleary07a}, the fit to the lobes emission can be expressed as a parabolic function:
 \begin{equation}
@@
 \end{equation}
-where $F_{\nu}^{\mathrm lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches unity, and $\nu_c^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy distribution.
-The extrapolated flux density of the lobe-fit at 104 GHz is consistent with the peak flux density of our continuum measurement (Figure \ref{fig:SED}).
-The 10$\sigma$ detection of the continuum thereby suggests
-a dominant contribution from the lobes, and the peak flux density therefore does not appear to be emission toward the core. Moreover, the peak position of the 104 GHz continuum is
-centered toward the northern lobe (Figure \ref{fig:cont}), which further supports our argument. 
-%This finding 
-%is consistent with a recent study by \citet{Hardcastle08a}, where they reported null detection of the radio cores of 
-%two FR-II radio galaxies 3C 20 at $z$ = 0.174 and 3C 295 at $z$ = 0.461 at observed-frame $\sim$90GHz. 
-We do not extrapolate the core measurements to the frequency of our continuum, as previous measurements of the core are taken 
-across epochs.
-
-Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, while others exhibit a clear spectral steepening either between cm and mm wavelengths (e.g., 3C123); at the resolution of our observation, it is unclear whether the integrated flux is dominated by the hotspot or the lobes.
-But it would be important for hotpot emission studies because this is at restframe sim60 GHz,
+where $F_{\nu}^{\mathrm lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending 
+of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches 
+unity, and $\nu_c^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy 
+distribution. 
+The extrapolated flux density at 104 GHz is consistent with the peak flux density of our continuum 
+measurement (Figure \ref{fig:SED}). The 10$\sigma$ detection of the continuum thereby suggests
+a dominant contribution from the lobes, and the peak flux density therefore does not appear to be emission toward 
+the core. Moreover, the peak position of the 104 GHz continuum is
+centered toward the northern lobe (Figure \ref{fig:cont}), which further supports our argument. We did not 
+extrapolate the core measurements to the frequency of our continuum, as previous measurements of the core are 
+taken 
+across epochs.\par
+Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, and some exhibit spectral steepening either between cm or mm wavelengths (e.g., 3C123); at the resolution of our observation, it is unclear whether the integrated flux is dominated by the hotspot or the lobes.
+Nonetheless, high resolution observations of 3C220.3 at mm wavelengths (rest-frame $\sim$ 60 GHz) will provide important insight on hotspot emission studies.
 

### 2015-07-05 skeleton.tex
Ok SFR

@@
 \begin{document}
-\title{A Massive Molecular Gas Reservoir in the $z$ = 2.221 Type-2 Active Galactic Nucleus Host Galaxy SMM J0939+8315 lensed by the Radio Galaxy 3C220.3}
+\title{A Massive Molecular Gas Reservoir in the Type-2 Quasar Host Galaxy SMM J0939+8315 at $z$ = 2.221  lensed by the Radio Galaxy 3C220.3}
 \author{T. K. Daisy Leung and Dominik A. Riechers}
@@
 of the cold gas and dust in the interstellar medium (ISM) of the background SMG which hosts a type-2 quasar. Prior to correcting for lensing 
-amplification, we measure a velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (10.1 $\pm$ 1.1) Jy km s\pmOne,
+amplification, we measure a velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (10.7 $\pm$ 2.1) Jy km s\pmOne,
 corresponding to a lensing-corrected CO($J$ = 1 \rarr 0) line luminosity of \Lp = (2.7 $\pm$ 
@@
 galaxy assembly. These galaxies are luminous in submillimeter (submm) due to the re-radiation from the dust components in the
- far-infrared (FIR) wavelengths. Followup observations of SMGs discovered in large sky surveys (e.g., HerMES, H-ATLAS) (cite) with sub-(mm) facilities have led to growing consensus
+ far-infrared (FIR) wavelengths. Followup observations of SMGs discovered in large sky surveys (\eg HerMES, H-ATLAS) (cite) with sub-(mm) facilities have led to growing consensus
   of the observable properties of SMGs (cite, blah). SMG is a population of high-redshift galaxy that are typically dusty, gas-rich, 
@@
 SMM J0939 at $z$ = 2.221 obtained with the Combined
-Array for Research in Millimeter Astronomy (CARMA). The underlying continuum at 104 GHz allows us to put constraints on the SED of the 
-foreground radio galaxy.
+Array for Research in Millimeter Astronomy (CARMA), and the study of the ISM in great detail. The underlying continuum at 104 GHz allows us to put constraints on the SED of the 
+foreground FR-II galaxy at mm wavelengths.
 
 This paper is organized as follows: in \S \ref{sec:obs}, we describe the
-observations of \CO line emission with CARMA; in \S \ref{sec:res}, we report the
+observations of the \CO line emission with CARMA; in \S \ref{sec:res}, we report the
 detection of CO emission in the background galaxy, as well as continuum emission in the foreground galaxy; in \S
@@
 \subsection{CARMA} \label{sec:carmadata}
-Observations of the \CO rotational transition ($\nu_{\rm rest}$ = 345.7959899 GHz) towards the background galaxy SMM
+Observations of the \CO rotational transition ($\nu_{\rm rest}$ = 345.7959899 GHz) toward the background galaxy SMM
 J0939 ($z$ = 2.221) were carried out using CARMA at the redshifted frequency of $\nu_{obs}$ = 107.357 GHz (2.79 mm)  (program ID: cf0142; P.I.: Riechers).
-The 3 mm receivers were used to cover the redshifted CO($J$ = 3 $\rightarrow$ 2) line and the underlying 2.877 mm continuum emission, employing a correlator setup to provide a bandwidth of 3.75 GHz in each sideband and spectral resolution of 5.208 MHz ($\sim$14.5 km s\pmOne).
+The 3 mm receivers were used to cover the redshifted CO($J$ = 3 $\rightarrow$ 2) line and the nearby 2.88 mm continuum emission, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of 5.208 MHz ($\sim$14.5 km s\pmOne).
 The line was placed in the
-upper sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$ 104.2609 GHz.
+upper sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$104.2609 GHz.
 Observations were carried out under good
-weather conditions in E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
+weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
 equivalent on-source time after discarding unusable visibility data.
@@
 pointing, amplitude, and phase calibration. Mars was observed as the primary
-absolute flux calibrator and the quasar 3C273 was observed as the secondary
+absolute flux calibrator, and the quasar 3C273 was observed as the secondary
 flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
@@
 The {\sc MIRIAD} package was used to calibrate and analyze the visibility data which are deconvolved and imaged using
-the CLEAN algorithm with ``natural" weighting, this yields a synthesized clean beam size of 13$\farcs$5 $\times$ 
+the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 13$\farcs$6 $\times$ 
 5\farcs8 for the upper sideband image cube.
@@
 
-% mom0 map channels [65, 85], each channel is 29.088 km/s, i.e. total velocity range is 610.848 km/s, which is 218.736 
-%MHz
 \section{Results}\label{sec:res}
 \subsection{New results: Continuum Emission} 
-Averaging over all the line-free channels, we detect continuum emission at 10$\sigma$ significance at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz ($\sim$2.9 mm) in the observed-frame, corresponding to 61.8 GHz ($\sim$1.7 mm) at $z$ = 0.658.
+Averaging over all the line-free channels, we detect continuum emission at 10$\sigma$ significance at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz ($\sim$2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$1.7 mm) at $z$ = 0.685.
 In this lens system, the
-foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum to be dominated by emissions from the foreground galaxy.
+foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum to be dominated by synchrotron emission from the foreground galaxy.
 We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission.
@@
 mJy beam\pmOne.
-In Figure \ref{fig:cont}, we show the continuum emission at 104 GHz overlaid on the 9 GHz continuum measurement reported by H14.
+An overlay image of the 104 GHz continuum emission on the 9 GHz continuum measurement (H14) is shown in Figure \ref{fig:cont}.
 This demonstrates that at the resolution of our observation, the continuum detection is marginally resolved.
-It is therefore plausible that both non-thermal emission from the lobes and the radio core dominate the integrated flux density in our measurement.
+It is therefore plausible that non-thermal emission from both the lobes and the radio core dominate the integrated flux density in our measurement.
 
@@
 \includegraphics[width=0.80\textwidth]{Figure/ContPanel}
-\caption{The central cross on each image indicates the position of the radio core of 3C220.3. The contour levels of the 9 GHz continuum 
-emission start at $\pm$4$\sigma$ of $\sigma$ = 0.064 mJy beam\pmOne and increment at steps of $\pm$2$^n\sigma$, 
-where n is a positive integer; the contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
-of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne.
+\caption{The central cross on each image indicates the position of the radio core of 3C220.3. The contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
+of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne; the contour levels of the 9 GHz continuum 
+emission start at $\pm$4$\sigma$ of $\sigma$ = 0.064 mJy beam\pmOne\ and increment at steps of $\pm$2$^n\sigma$, 
+where n is a positive integer.
 Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 16\farcs7 $\times$ 7\farcs2, at P.A. = 
 -58$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
-foreground radio galaxy 3C220.3 overlaid the 9 GHz emission (green) (H14). The rms in the 9GHz image is $\sigma$ 
-= 0.064 mJy beam\pmOne. The synthesized beam size of the VLA observations is 0$\farcs$6 $\times$ 0$\farcs$2 at P.A. 
+foreground radio galaxy 3C220.3 overlaid on the 9 GHz emission (green and grayscale) (H14). The synthesized beam size of the VLA observations is 0$\farcs$6 $\times$ 0$\farcs$2 at P.A. 
 76$\degr$. 
@@
 \subsection{New results: \CO line emission}
-We detect \CO line emission toward the background SMG SMM J0939 at $z$ = 2.221.
-Figure \ref{fig:mom0} shows the line profile at the peak position of the CO emission.
-Fitting a four-parameter single-component Gaussian to the spectrum yields a peak flux density of 19.9 $\pm
+We detect \CO line emission at 5$\sigma$ significance toward the background SMG SMM J0939 at $z$ = 2.221.
+The line profile in Figure \ref{fig:mom0} is extracted at the peak position of the CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 19.9 $\pm
 $ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy, and full width at half-maximum (FWHM) of 542 $\pm$ 32 km s\pmOne. 
@@
 emission using the data with continuum subtracted in the visibility plane.
-This results in a velocity-integrated \CO line flux of $S_{\rm CO}$ = 10.7 $\pm$ 0.2 Jy km s\pmOne over the FWZI velocity range of $\Delta v$ = $\sim$914 km s\pmOne, the uncertainty does not include $\sim$ 15\% calibration uncertainty.
-We ignore primary beam correction given that the source is close to the phase center, and that the source is unresolved (\ie much smaller than the primary beam size).
-The \CO spectroscopy confirms the redshift of SMM J0939 at $z$ = 2.221 $\pm$ blah.
+This results in a velocity-integrated \CO line flux of $S_{\rm CO}$ = 10.7 $\pm$ 2.12 Jy km s\pmOne\ over the FWZI velocity range of $\Delta v\sim$914 km s\pmOne, the uncertainty does not include $\sim$ 15\% calibration uncertainty.
+We ignore primary beam correction given that the source is close to the phase center, and the source is unresolved (\ie much smaller than the primary beam size).
+This \CO line measurement confirms the redshift of SMM J0939 at $z$ = 2.221 $\pm$ blah.
 
@@
 \includegraphics[width=0.65\textwidth]{Figure/peak28_WiderSpectrum}
-\caption{The central cross on each image sets the coordinates for alignment between plots. The contour starts at $\pm$2$\sigma$, 
-incrementing at
-steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the \CO line emission in 
-the background SMG with $\sigma$ = 1.8 Jy km s\pmOne beam\pmOne, over a velocity range of $\Delta v\sim$610 km s\pmOne\. The angular resolution is 13$\farcs$6 $\times$ 
-5\farcs8, as shown in the bottom left corner. 
-Top Right: Contours of \CO emission (red) overlaid on the SMA 1 mm dust continuum (green; H14) with $
-\sigma$ = 0.84 mJy beam\pmOne. The beam size of the SMA data is 1\farcs4$ \times $1\farcs2, P.A. -34\degr, as shown 
-in the bottom left corner. From this image, it is apparent that the extent of the background SMG is smaller than the beam 
-size of the CARMA observations, hence the \CO line detection is spatially unresolved. Bottom: 
-The spectrum extracted at peak position of the CO emission, the spectral resolution is $\Delta v$ $\sim$29 km s\pmOne\ with an rms of $\sigma_{\rm ch}$ = 12.5 mJy beam\pmOne\ per channel.
+\caption{The central cross on each image corresponds to the same coordinates.
+The contour levels start at $\pm$2$\sigma$ and $\pm$3$\sigma$ for the CARMA line emission and the SMA continuum emission, respectively, incrementing at
+steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the \CO line emission toward 
+the background SMG with $\sigma$ = 1.8 Jy km s\pmOne\ beam\pmOne over a velocity range of $\Delta v\sim$610 km s\pmOne\ . The angular resolution is 13$\farcs$6 $\times$ 
+5\farcs8, as indicated in the bottom left corner. 
+Top Right: Contours of the \CO line emission (red) overlaid on the SMA 1 mm dust continuum (green; H14) with $\sigma_{\rm 1 mm}$ = 0.84 mJy beam\pmOne.
+The beam size of the SMA data is 1\farcs4$ \times $1\farcs2, P.A.
+-34\degr, as shown
+in the bottom left corner. Bottom: 
+The spectrum extracted at the peak position of the CO line emission. The spectral resolution is $\Delta v$ $\sim$29 km s\pmOne\ with an rms of $\sigma_{\rm ch}$ = 12.5 mJy beam\pmOne\ per channel.
 Solid black line shows the Gaussian fit to the \CO line profile. Yellow histogram shows the 
-flux density as a function of velocity offset, where 0 km/s corresponds to $z$ = 2.221. \label{fig:mom0}}
+flux density as a function of velocity offset, where 0 km s\pmOne\ corresponds to $z$ = 2.221. \label{fig:mom0}}
 \end{figure*}
@@
 
-We initialize the positions and the Einstein radii of both lenses, and the position of the source using the
-values of the best-fit lens model that \citet{Haas14} performed on Keck K-band near-infrared image. For each of
+We initialize the positions and Einstein radii of both lenses, and the position of the source using the
+best-fit values of the lens model H14 performed on Keck K-band (near-infrared) data. For each of
 these parameters, we impose a uniform prior in the range $\in\pm$3$\sigma$, where $\sigma$ is the uncertainty
@@
 Left: SMA 1 mm continuum (red contours) overlaid on the best-fit model (grayscale image) assuming an elliptical Gaussian profile for the background SMG.
-The lenses are represented as black dots and the half-light area of the background source is represented as magenta ellipse, and the orange lines represent the critical curves in the image plane.
-Right: The residual contours overlaid on the image, obtained by taking the Fourier transformed of the difference between the SMA continuum and the best-fit model in the visibility plane.
-\label{fig:lens}}
+The lenses are represented as black dots, the half-light area of the background source is represented as magenta ellipse, and the critical curves are represented as orange curves.
+Right: Residual contours and image obtained by taking the Fourier transform of the difference between the SMA data and the best-fit model in the visibility plane. \label{fig:lens}}
 \end{figure}
@@
 across epochs.\par
-Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, and some exhibit spectral steepening either between cm or mm wavelengths (e.g., 3C123); at the resolution of our observation, it is unclear whether the integrated flux is dominated by the hotspot or the lobes.
+Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, and some exhibit spectral steepening either between cm or mm wavelengths (\eg 3C123); at the resolution of our observation, however, it is unclear whether the integrated flux is dominated by the emission from the compact hotspot or the emission from the surrounding diffuse lobe components.
 Nonetheless, high resolution observations of 3C220.3 at mm wavelengths (rest-frame $\sim$ 60 GHz) will provide important insight on hotspot emission studies.
@@
 The best-fit solution yields a far-infrared (FIR) luminosity of $L_{\rm FIR (42.5-122.5\micron)}$ = 53.3$^{+1.1}_{-1.1}\times$10$^{12}$\Lsun, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$ = 88.5$^{+2.6}_{-2.6}\times$10$
-^{12}$\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64 m$^2$ kg\pmOne at 125.0 $
+^{12}$\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64 m$^2$ kg\pmOne\ at 125.0 $
 \micron$ \citep{Dunne03a}, we derive the dust mass using the following expression:
@@
 all quantities are expressed in the observed-frame. We find a dust mass of $M_{\rm dust}$ =
-50.5$^{20.4}_{-20.2}\times$10$^8$\Msun, the uncertainties do not include those of $\kappa_{\nu}$. These values are based on SED fitting to the photometric data, i.e. prior
+50.5$^{20.4}_{-20.2}\times$10$^8$\Msun, the uncertainties do not include those of $\kappa_{\nu}$. These values are based on SED fitting to the photometric data, \ie prior
 to lensing correction.
-With the limited amount of data in the FIR, $M_{\rm dust}$ is weakly constrained; in another fit to the optically thick model where the upper limit of $\beta$ is set to 3.0, all fitting parameters of the best-fit solution are similar to those using an upper limit of 2.2; we find that while the deviation of each is at most $\sim$3\%, the dust mass is boosted by a factor of $\sim$2.
+
+With the limited amount of data in the FIR waveband, the dust mass is weakly constrained. 
+We perform an additional optically thick model fitting where we loosen the upper limit of $\beta$ from 2.2 to 3.0, while the difference between all best-fit parameters in this scenario and those using an upper limit of 2.2 (see Table \ref{tab:mbb}) is within 3\%, we find that the dust mass is boosted by a factor of $\sim$2.
 
 \subsection{Molecular gas mass}
-The ground state CO transition line, CO($J$ = 1 \rarr\ 0) has been used as a tracer of the cold molecular gas in galaxies for 
-over a decade \citep*[\eg][]{Downes98a,Wilson70a}. For high-redshift galaxies, the CO($J$ $>$ 1) transition lines are frequently observed as
- the CO($J$ = 1 \rarr\ 0) line is redshifted to wavelengths that can only be observed with a few telescopes \citep{Carilli13a}, 
+While the ground state CO transition line, CO($J$ = 1 \rarr\ 0) traces the cold molecular gas in the ISM
+\citep*[\eg][]{Downes98a,Wilson70a}, CO($J$ $>$ 1) transition lines are frequently observed at high redshifts as the
+ ground state CO transition line is redshifted to lower frequencies that can only be observed with a few telescopes 
+ \citep{Carilli13a}, 
  hence assumptions on the CO excitation conditions are required to derive the molecular gas mass using the H$_{\rm 2}$-to-CO 
- relation. Prior to the observations of the CO($J$ = 1 \rarr\ 0) line in SMGs, it has been assumed that the molecular gas in the
-  ISM traced by CO transition lines is thermalized due to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
-   Nonetheless, recent CO($J$ = 1 \rarr\ 0) observations have demonstrated that SMGs can indeed be subthermally excited
-   \citep{Harris10a,Riechers11c,Riechers11d,Ivison11a}. Based on SMGs with observations of both the \CO and the CO($J$ = 1 \rarr\ 0) lines, the 
-   brightness temperature ratio between \CO
-and ($J$ = 1 \rarr\ 0) has been inferred as $R_{\rm 31}\ <$ 0.8 \citep
+ relation. 
+Prior to the observations of the ground state CO line in SMGs, it has been assumed that the molecular gas in the
+  ISM traced by CO lines is thermalized due to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
+   Yet, recent observations of this line have demonstrated that SMGs can indeed be subthermally excited
+   \citep{Harris10a,Riechers11c,Riechers11d,Ivison11a}; based on observations toward SMGs of both the \CO and the CO($J$ = 1 \rarr\ 0) lines, the 
+   brightness temperature ratio has been inferred as $R_{\rm 31}<$ 0.8 \citep
    {Harris10a,Carilli10a,Swinbank2010a,Riechers11d,Ivison11a,Ivison10d}. In contrast, observations of high-redshift quasar hosts suggest that the ratio 
-   is $R_{\rm 31}\ \sim\ $1 \citep{Riechers06a, Riechers11a, Scott11a}. 
-Here, we derive the molecular gas mass assuming thermalized excitation of CO, i.e., we adopt $R_{\rm 31}$ = 1 as SMM J0939 is 
-postulated to be hosting a type-2 quasar. We calculate the CO($J$ = 1 \rarr\ 0) line luminosity using standard relation 
+   is $R_{\rm 31}\sim$ 1 \citep{Riechers06a, Riechers11a, Scott11a}. 
+Here, we derive the molecular gas mass assuming thermalized excitation of CO, \eg we adopt $R_{\rm 31}$ = 1 as SMM J0939 is 
+postulated to be hosting a type-2 quasar. \par
+We calculate the CO($J$ = 1 \rarr\ 0) line luminosity using standard relation 
 \citep[\eg][]{Solomon05a,Carilli13a}:
@@
 \end{equation}
-where $\nu_{\rm CO (3-2), rest}$ is the rest-frame frequency of the \CO line in GHz, $D_L^2$ is the luminosity distance in Mpc, and $I_{\rm CO(3-2)}$ is the \CO line intensity in Jy km s\pmOne.
-This corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ (10.73/$\mu_{\rm L}$) \LpU\ after lensing correction.
-The inferred total molecular gas mass is therefore $M_{\rm gas}$ = (3.303 $\pm$ 0.696) $\times
-$10$^{10}$ \Msun. We assumed a conversion factor of $\alpha_{\rm CO}$ =
+where $\nu_{\rm CO (3-2), rest}$ is the rest-frame frequency of the \CO line in GHz, $D_L$ is the luminosity distance in Mpc, and $I_{\rm CO(3-2)}$ is the \CO line flux in Jy km s\pmOne.
+This corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (2.91 $\pm$ 0.78)$\times$10$^{10}$(10.1/$\mu_{\rm L}$) \LpU\ after correcting for lensing magnification; the inferred total molecular gas mass is therefore $M_{\rm gas}$ = (2.33 $\pm$ 0.62) $\times$10$^{10}$\Msun.
+We assumed a conversion factor of $\alpha_{\rm CO}$ =
 0.8 \Msun (\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
 adopted for SMGs \citep[\eg][]{Tacconi06a,Tacconi08a,Bothwell13a}. 
-The gas-to-dust
-ratio is $f_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 64 $\pm$ blah , this is in good agreement with the range 
-of values found in other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.
-
+This results in a gas-to-dust
+ratio of $f_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 47 $\pm$ 21, this is in good agreement with the 
+values found in other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.
+% find an excellent agreement of blah with blah
 \subsection{Star formation rate}
 We derive the star formation rate (SFR) using the \citet{Kennicutt98a} relation, assuming a \citet{Chabrier03a}
-stellar initial mass (IMF) function. This yields SFR$_{\rm IR}$ 
-= 909.12 $\pm$ 155.67 $M\sun$ yr\pmOne and SFR$_{\rm FIR}$ = 547.71 $\pm$ 89.28 $M
-\sun$ yr\pmOne\ using lensing-corrected (far-)infrared luminosities (L$_{\rm IR}$ and L$_{\rm FIR}$) derived from SED 
-fitting, and assuming negligible contributions from AGN heating.
+stellar initial mass (IMF) function. This yields a SFR$_{\rm IR}$ of 874 $\pm$ 122 $M\sun$ yr\pmOne, derived using the lensing-corrected total IR luminosity (L$_{\rm IR}$) derived from SED 
+fitting, and assuming negligible contributions from AGN heating, which is at most BLAH \% as no evidence of warm dust (from MIR). \footnote{SFR$_{\rm FIR}$ = 526 $\pm$ 72 $M_
+\odot$ yr\pmOne\ }
 
@@
 current SFR can be approximated as the gas depletion timescale, $\tau$ = $M_{\rm gas}$/SFR. 
-This corresponds to $\tau_{\rm IR}$ = 36.33 $\pm$ 2.96 Myr, and $\tau_{\rm FIR}$ = 60.30 $\pm$ 42.20 Myr.
+This corresponds to $\tau_{\rm IR}$ = 25.6 $\pm$ 0.6 Myr.
 
@@
 The SFR per unit mass of molecular gas is commonly taken as a
-measure of the star formation efficiency, SFE = SFR/$M_{\rm gas}$. We compute this ratio using lensing-corrected (far-)infrared 
-luminosities ($L_{\rm IR}$, $L_{\rm FIR}$) and CO($J$ = 1 \rarr\ 0) luminosity: SFE = $L_{\rm F/IR}$/\Lp, this ratio makes no assumptions on the gas mass conversion factor $\alpha$ as well as the 
+measure of the star formation efficiency, SFE = SFR/$M_{\rm gas}$. We compute this ratio using lensing-corrected infrared 
+luminosities ($L_{\rm IR}$) and CO($J$ = 1 \rarr\ 0) luminosity: SFE = $L_{\rm IR}$/\Lp, this ratio makes no assumptions on the gas mass conversion factor $\alpha$ as well as the 
 choice of IMF, however, this assumes that differential lensing effect between the CO and infrared emission is negligible. 
-The resulting ratios are SFE$_{\rm IR}$ = 220.22 $\pm$ 15 Myr\pmOne\ and SFE$_{\rm FIR}$ = 132.68 $\pm$ blah Myr\pmOne, which are comparable
+The resulting ratios are SFE$_{\rm IR}$ = 300 $\pm$ 10 Myr\pmOne, which is comparable
 to what is found in "typical" SMGs \citep{Riechers10, Tacconi06, Greve05a}.
@@
 and the half-light radius from lens modeling for $R_{\rm eff}$, assuming the dust emission traces the same emitting region as the CO.
-This yields $M_{\rm dyn}$ = (7.32 $\pm$ 3.14) $\times$ 10$^{10}$\Msun , and gas-to-dynamical mass fraction of $f_{\rm gas-to-dyn}$ = $\approx$ 0.45, consistent that of other SMGs \citep{Greve06a,Tacconi06a}.
+This yields $M_{\rm dyn}$ = (7.4 $\pm$ 2.4) $\times$ 10$^{10}$\Msun , and gas-to-dynamical mass fraction of $f_{\rm gas-to-dyn}$ = $\approx$ 0.32, consistent that of other SMGs \citep{Greve06a,Tacconi06a}.
 

### 2015-07-05 Code/err.py

@@ -2,7 +2,7 @@ freq_CO32 = 345.651     # GHz
 dl = 19052          # Mpc at 2.221
 z = 2.221
 I_line = 10.7
-del_I = 2.12    # sigma of CO(3-2) line intensity Jy km/s
+del_I = 2.12   # sigma of CO(3-2) line intensity Jy km/s
 mu = 10.1298
 del_mu = 1.38
 alpha = 0.8
@@ -11,6 +11,8 @@ del_kpc = 0.03309 * 8.406
 vel = 541.65
 del_vel = 31.9
 LIR = 88.52e12    # before lensing correction, from mbb
+LFIR = 53.330e12
+del_FIR_noMu = 1.14e12
 del_IR_noMu = 2.62e12
 M_dust = 50.47e+8  # before lensing correction, from mbb
 sig_Mdust_noMu = 20.42e8
@@ -19,10 +21,10 @@ Mgas = 2.326e10    # with lensing correction
 
 #####################
 #####################
-sig_LprimeCO = (3.25e7 / freq_CO32**2 * dl**2 / (1+z))**(.5) * ((del_I/mu)**2 + (del_mu/mu**2*I_line)**2)**(.5)
+sig_LprimeCO = (3.25e7 / freq_CO32**2 * dl**2 / (1+z)) * ((del_I/mu)**2 + (del_mu/mu**2*I_line)**2)**(.5)
 del_LprimeCO = 3.25e7 / freq_CO32**2 * dl**2 / (1+z) * ((del_I/mu) + (del_mu/mu**2*I_line))
 
-sig_LprimeCO_noMu = (3.25e7 / freq_CO32**2 * dl**2 / (1+z))**(.5) * (del_I/mu)
+sig_LprimeCO_noMu = (3.25e7 / freq_CO32**2 * dl**2 / (1+z)) * (del_I/mu)
 del_LprimeCO_noMu = 3.25e7 / freq_CO32**2 * dl**2 / (1+z) * (del_I/mu)
 
 LprimCO_noMu = 3.25e7/freq_CO32**2 * dl**2 / (1+z) * I_line
@@ -34,18 +36,25 @@ Mgas_noMu = alpha * LprimCO_noMu
 sig_Mgas_noMu = alpha * sig_LprimeCO_noMu
 del_Mgas_noMu = alpha * del_LprimeCO_noMu
 
[…]

### 2015-07-18 Code/Plot_Image.py
modify sigma, min, max, and vmid for 65-85lin mom0

@@ -12,6 +12,7 @@ for k in label.iterkeys():
     files = glob.glob(path+'*'+k+'*.fits')
     label[k] = files
 
+print label
 
 fig = plt.figure(3, figsize=(12, 5))
 fig_line = plt.figure(2, figsize=(12, 5))
@@ -22,23 +23,23 @@ fig_line = plt.figure(2, figsize=(12, 5))
 ########################################
 sigma_9ghz = 6.41094e-05
 sigma_cont = 5.0e-4
-sigma_line = 1.826
+sigma_line = 1.663      # chan 65-85 not pretty mom0    # 0.984      # chan72,90 (pretty) mom0 without options=double,mosaic
 sigma_SMA = 0.000836951
 
 vla_min = -0.000270099
 vla_max = 0.00960869
 max_cont = 5.347e-3
 min_cont = -1.94e-3
-max_line = 9.609
-min_line = -0.2700985
+max_line = 8.93562
+min_line = -8.836704
 SMA_min = -0.00210908
 SMA_max = 0.00634805
 
 VLA_ra = 1.448437499980E+02
 VLA_dec = 8.325666666846E+01
 sizep = 0.0025
-sizePcont_noise = 0.00920
-sizePLine = 0.0075
+sizePcont_noise = 0.012
+sizePLine = 0.012
 ra_center = 144.84933
 dec_center = 83.257175
 
@@ -72,7 +73,7 @@ fvla.show_grayscale(stretch='log', vmin=vla_min, vmax=vla_max, vmid=-0.001)
 
 flin = aplpy.FITSFigure(label['lin'][0], \
         figure=fig_line, subplot=[x0,row_a,width,dy])
-flin.show_colorscale(cmap=mpl.cm.jet)   #, vmin=min_line, vmax=max_line, vmid=min_line-0.5, stretch='log')
+flin.show_colorscale(cmap=mpl.cm.jet, vmin=min_line, vmax=max_line, vmid=-25, stretch='log')
 fSMA = aplpy.FITSFigure(label['SMA'][0], figure=fig_line, subplot=[x0+width+2*x_gap, row_a, width, dy])
 fSMA.show_grayscale(stretch='log', vmin=SMA_min, vmax=SMA_max, vmid=-0.05)
 
[…]

### 2015-07-19 Code/Plot_Image.py
Using the set of mom0, cont from pretty; sigma, max, min changes, mom0 using 72-90 to get 7sigma, also mom0 from 3sigma

@@ -21,41 +21,41 @@ fig_line = plt.figure(2, figsize=(12, 5))
 ########################################
 # user define area
 ########################################
-sigma_9ghz = 6.41094e-05
-sigma_cont = 5.0e-4
-sigma_line = 1.663      # chan 65-85 not pretty mom0    # 0.984      # chan72,90 (pretty) mom0 without options=double,mosaic
-sigma_SMA = 0.000836951
+sigma_9ghz          = 6.41094e-05
+sigma_cont          = 5.1e-4
+sigma_line          = 1.0 # 1.35   # chan 65,85 (pretty)     # 1.0      # chan72,90 (pretty) mom0 without options=double,mosaic
+sigma_SMA           = 0.000836951
 
-vla_min = -0.000270099
-vla_max = 0.00960869
-max_cont = 5.347e-3
-min_cont = -1.94e-3
-max_line = 8.93562
-min_line = -8.836704
-SMA_min = -0.00210908
-SMA_max = 0.00634805
+vla_min             = -0.000270099
+vla_max             = 0.00960869
+max_cont            = 4.796309E-03
+min_cont            = -2.038660E-03
+max_line            = 8.93562
+min_line            = -8.836704
+SMA_min             = -0.00210908
+SMA_max             = 0.00634805
 
-VLA_ra = 1.448437499980E+02
-VLA_dec = 8.325666666846E+01
-sizep = 0.0025
-sizePcont_noise = 0.012
-sizePLine = 0.012
-ra_center = 144.84933
-dec_center = 83.257175
+VLA_ra              = 1.448437499980E+02
+VLA_dec             = 8.325666666846E+01
+sizep               = 0.0025
+sizePcont_noise     = 0.012
+sizePLine           = 0.012
+ra_center           = 144.84933
+dec_center          = 83.257175
 
 # WMAP9, flat Universe
-z_radio = 0.685
-scale_radio = 7.169     # kpc/"
-z_SMG = 2.221
-scale_SMG = 8.406       # kpc/"
+z_radio             = 0.685
+scale_radio         = 7.169     # kpc/"
+z_SMG               = 2.221
+scale_SMG           = 8.406       # kpc/"
 
 # # positions for crosses, centering on radio core
 ra_cross, dec_cross = ra_center, dec_center
[…]

### 2015-07-19 skeleton.tex
Edit since DR's comments up to before RADIO SED

@@
 \newcommand{\rarr}{$\rightarrow$}
-\newcommand{\CO}{\mbox{CO($J$ = 3 $\rightarrow$ 2) }}
+\newcommand{\CO}{\mbox{CO($J$\,=\,3\,$\rightarrow$\,2) }}
 \newcommand{\Lp}{\mbox{$L^{\prime}_{\rm CO(1-0)}$}}
-\newcommand{\LpU}{\mbox{K km s$^{-1}$ pc$^2$}}
+\newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
 \newcommand{\eg}{{\sl e.g.,~}}
 \newcommand{\ie}{{\sl i.e.,~}}
-\newcommand{\pmOne}{$^{-1}$}
+\newcommand{\pmOne}{\mbox{$^{-1}$}}
 \newcommand\tna{\,\tablenotemark{a}}
@@
 \citestyle{aa}
-\shorttitle{Study of a strongly lensed type-2 quasar host SMG at $z$ = 2.221}
+\shorttitle{Study of a strongly lensed type-2 quasar host SMG at $z$\,=\,2.221}
 \shortauthors{Leung \& Riechers}
@@
 \begin{document}
-\title{A Massive Molecular Gas Reservoir in the Type-2 Quasar Host Galaxy SMM J0939+8315 at $z$ = 2.221  lensed by the Radio Galaxy 3C220.3}
+\title{A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3}
 \author{T. K. Daisy Leung and Dominik A. Riechers}
-\affil{Department of Astronomy, Cornell University, Space Sciences Building, Ithaca, NY 14853, USA; tleung@astro.cornell.edu}
+\affil{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; tleung@astro.cornell.edu}
 
 \begin{abstract}
-We report the detection of \CO line emission in SMM J0939+8315 at $z$ = 2.221, a
-strongly lensed high-redshift submillimeter galaxy (SMG) using
-the Combined Array for Research in Millimeter-wave Astronomy (CARMA). The lensing system consists of a
-foreground radio galaxy 3C220.3 and a companion galaxy at $z$ = 0.685. This allows us to place constraints on the intrinsic properties
-of the cold gas and dust in the interstellar medium (ISM) of the background SMG which hosts a type-2 quasar. Prior to correcting for lensing 
-amplification, we measure a velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$ = (10.7 $\pm$ 2.1) Jy km s\pmOne,
-corresponding to a lensing-corrected CO($J$ = 1 \rarr 0) line luminosity of \Lp = (2.7 $\pm$ 
-blah) $\times$ 10$^{10}$ \LpU. This
-translates to a molecular gas mass of $M_{\rm gas}$ = 2.2 $\times$ 10$^{10}M_\odot$. We report marginally resolved continuum 
-emission from the foreground galaxy with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
- at 104 GHz, allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
-fit
- both an optically thick and optically thin modified blackbody models to the SED of the SMG, the preferable optically thick model  yields dust mass of $M_{\rm
-dust}$ = 50.5$^{20.4}_{-20.2}$ $\times$ 10$^8$\Msun, and total infrared (IR) luminosity of $L$ = 88.5$^{+2.6}
-_{-2.6}\times$10$^{12}$\Lsun, prior to lensing correction. We conclude that the properties (\eg gas mass, gas mass 
-fraction, SFR) of the molecular gas reservoir in SMM
-J0939+8315 based on our \CO observation is similar to other high redshift
-SMGs. \\
-NEED TO  FIX: 
-report SFR, gas-to-dust ratio.. Comparison, etc. 
+We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy\,(SMG) SMM\,J0939+8315 at $z$\,=\,2.2212\,$\pm$\,0.0001, using  
+the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
+The SMG is lensed by the radio galaxy 3C220.3 and its companion galaxy at $z$\,=\,0.685. 
+This measurement allows us to place constraints on the intrinsic properties
+of the cold gas and dust in the interstellar medium (ISM) of the background SMG which hosts a type-2 quasar, as well as on the spectral energy distribution (SED) of the foreground radio galaxy using the marginally resolved continuum
+emission detected at an integrated flux density of $S_\nu$\,=\,7.5\,$\pm$\,1.3 mJy
+ at 104 GHz.
+We measure a velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$\,=\,(10.7\,$\pm$\,1.3)\,Jy\,km\,s\pmOne,
+corresponding to a lensing- and excitation-corrected CO line luminosity of \Lp\,=\,(2.9\,$\pm$\,0.8)\,$\times$\,10$^{10}$\,(10.1/$\mu_{\rm L}$)\,\LpU, where $\mu_{\rm L}$ is the lensing magnification factor inferred from our lens modeling of the 1\,mm continuum emission.
+ This
+translates to a molecular gas mass of $M_{\rm gas}$\,=\,(2.3\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,\Msun. We 
+fit optically thick and optically thin modified blackbody models to the SED of the SMG.
+The preferred optically thick model yields a characteristic dust temperature of $T_{\rm dust}$\,=\,63.1$^{+1.1}_{-1.3}$\,K in the rest-frame, a dust mass of $M_{\rm dust}$\,=\,(5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,\Msun, and a total infrared (IR) luminosity of $L_{\rm IR}$\,=\,(9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,\Lsun, after correcting for lensing magnification.
+We conclude that the intrinsics properties (\eg gas mass, gas mass
+fraction, star formation rate) of the molecular gas reservoir in SMM
+J0939+8315 based on our \CO observations is similar to other high redshift
+SMGs. 
 \end{abstract}
@@
 \section{Introduction}\label{sec:intro}
-Submillimeter-selected galaxies (SMGs) are predominantly found at redshift $z \sim$ 1$-$3, during the epoch of stellar mass and 
-galaxy assembly. These galaxies are luminous in submillimeter (submm) due to the re-radiation from the dust components in the
- far-infrared (FIR) wavelengths. Followup observations of SMGs discovered in large sky surveys (\eg HerMES, H-ATLAS) (cite) with sub-(mm) facilities have led to growing consensus
-  of the observable properties of SMGs (cite, blah). SMG is a population of high-redshift galaxy that are typically dusty, gas-rich, 
-  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) in infrared with high star formation rates ($\gtrsim $ 500 \Msun yr\pmOne) \citep[\eg][]{Lagache05a}.
+Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1$-$3, during the epoch of stellar mass and 
+galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}. 
+These galaxies are luminous at submillimeter (submm) wavelengths due to the re-radiation of dust emission peaking at 
+rest-frame far-infrared (FIR) wavelengths \citep{blain02a}. 
+In the past $\sim$5\,\,years, considerable amounts of effort have been invested into follow-up observations of SMGs that were 
+discovered in large sky surveys \citep[\eg H-ATLAS, HerMES; ][]{Eales10a,Oliver12a}, conducted using (sub)-mm facilities.
+These detailed studies have led to growing consensus that SMGs are a population of high-redshift galaxies that are extremely dusty, gas-rich,
+  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) at the infrared wavebands, with high star formation rates \citep[$\gtrsim $ 500 \Msun yr\pmOne; \eg][]{Lagache05a}.
 
-  To characterize the physical properties of the gas reservoirs in the ISM where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to the high abundance of this molecule in the ISM as well as its low excitation energy, the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep{Carilli13a}.
-Recent observations of the CO line of SMGs at $z \sim$ 1$-$3 have
-provided evidence that SMGs have large gas reservoirs typical of \textgreater 10$^{10}$\Msun.
-In most cases, detailed studies are carried out on SMGs that are gravitationally lensed as lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a}.
-\par
-One of such lens system has a peculiar configuration consisting of a SMG, SMM J0939+8315 (hereafter SMM J0939), hosting a 
-type-2 quasar at $z$ = 2.221. SMM J0939 is being strongly lensed by a double-lobed Fanaroff-Riley Class II (FR-II) \citep*{Fanaroff74} radio galaxy (3C220.3) which has a 
-companion galaxy B at $z$ = 0.685, separated by 1\farcs5. SMM J0939 is currently one of the brightest known lensed
-SMGs, with lensing-magnified flux density of SMM J0939 $F_{\rm 250\mu m}$ = 440 $\pm$ 15 mJy. The redshift of SMM J0939 has 
-been measured through the detection of CIV 1459\AA\
- and HeII 1640\AA\
-line emissions \citep[hereafter H14]{Haas14}. These line detections provide conceivable evidence of active galactic nuclei (AGN) activity in this SMG, suggesting the presence of a type-2 quasar.
+  To characterize the physical properties of the gas reservoirs in the ISM where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[See \eg][]{Carilli13a}.
+Recent observations of CO in SMGs at $z$\,$\sim$\,1$-$3 have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Riechers11c,Riechers11d,Ivison11a,Bothwell13a}.
 
-In this paper, we present the detection of \CO line emission in the background SMG
-SMM J0939 at $z$ = 2.221 obtained with the Combined
-Array for Research in Millimeter Astronomy (CARMA), and the study of the ISM in great detail. The underlying continuum at 104 GHz allows us to put constraints on the SED of the 
-foreground FR-II galaxy at mm wavelengths.
+Many recent follow-up observations and thus detailed studies are carried out on SMGs that are gravitationally lensed,
+ as lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a,Oliver12a}. 
+A particularly interesting, peculiar submm-bright lensing system discovered serendipitously  
+consists of a type-2 quasar host SMG -- SMM\,J0939+8315 (hereafter SMM\,J0939), lensed by the double-lobed Fanaroff-Riley 
+Class II \citep*[FR-II; ][]{Fanaroff74} radio galaxy 3C220.3 and its
+companion galaxy B at $z$\,=\,0.685, where the two lensing galaxies are separated by 1\farcs5. 
+SMM\,J0939 is currently one of the brightest known lensed
+SMGs, with a lensing-magnified flux density of $S_{\rm 250\mu m}$\,=\,440\,$\pm$\,15 mJy. 
+Previous detections of CIV\,1459\AA\
+ and HeII\,1640\AA\ line emission toward SMM\,J0939 
+ place the redshift of this galaxy at $z$\,=\,2.221, and suggest the presence of a type-2 quasar,  
+indicating active galactic nucleus activity in this SMG \citep[hereafter H14]{Haas14}.
 
-This paper is organized as follows: in \S \ref{sec:obs}, we describe the
-observations of the \CO line emission with CARMA; in \S \ref{sec:res}, we report the
-detection of CO emission in the background galaxy, as well as continuum emission in the foreground galaxy; in \S
-\ref{sec:Lens}, we present our lens modeling analysis; in \S \ref{sec:SED}, we perform SED fitting to 3C220.3
-and SMM J0939, and derive the intrinsic properties of the interstellar medium (ISM) in the SMG; in \S \ref{sec:conclusions}, we
-conclude our findings by comparing to other similarly bright, strongly-lensed SMGs at similar redshifts.
+In this paper, we present the detection of \CO line emission toward the background SMG obtained with the Combined
+Array for Research in Millimeter Astronomy (CARMA), which refines the redshift, and permits the study of the physical conditions in the ISM of SMM\,J0939 in great detail.
+Our measurement of the underlying continuum emission put constraints on the SED of the different components of the foreground FR-II galaxy at mm wavelength ($\sim$104 GHz).
+Based on the magnification factor from our lens model, we infer intrinsic properties of SMM\,J0939 and thereby
+conclude this paper by comparing our findings to other similarly bright, strongly-lensed SMGs at $z$\,\,$\sim$\,\,2.
 
-We adopt a standard $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km Mpc\pmOne
-s\pmOne, $\Omega_{\rm M}$ = 0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
-The luminosity distances at $z$ = 0.685 and $z$ = 2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
-corresponds to 8.406 kpc at $z$ = 2.221, and 7.169 kpc at $z$ = 0.685.
+We adopt a standard $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km\,\,Mpc\pmOne\,\,s\pmOne, $\Omega_{\rm M}$\,=\,0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
+The luminosity distances at $z$\,=\,0.685 and $z$\,=\,2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
+corresponds to 8.406 kpc at $z$\,=\,2.221, and 7.169 kpc at $z$\,=\,0.685.
 
@@
 \subsection{CARMA} \label{sec:carmadata}
-Observations of the \CO rotational transition ($\nu_{\rm rest}$ = 345.7959899 GHz) toward the background galaxy SMM
-J0939 ($z$ = 2.221) were carried out using CARMA at the redshifted frequency of $\nu_{obs}$ = 107.357 GHz (2.79 mm)  (program ID: cf0142; P.I.: Riechers).
-The 3 mm receivers were used to cover the redshifted CO($J$ = 3 $\rightarrow$ 2) line and the nearby 2.88 mm continuum emission, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and spectral resolution of 5.208 MHz ($\sim$14.5 km s\pmOne).
+Observations of the \CO rotational transition ($\nu_{\rm rest}$\,=\,345.7959899 GHz) toward the background galaxy SMM
+J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; P.I.: Riechers).
+The 3\,mm receivers were used to cover the redshifted \CO line and the nearby 2.88\,mm continuum emission, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and a spectral resolution of 5.208 MHz ($\sim$14.5 km\,\,s\pmOne).
 The line was placed in the
-upper sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$104.2609 GHz.
+upper sideband, with the local oscillator tuned to $\nu_{\rm LO}$\,$\sim$104.2609 GHz.
 Observations were carried out under good
-weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
-equivalent on-source time after discarding unusable visibility data.
-The nearby source J1039+811 (0.65Jy) was observed every 20 minutes for
+weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-equivalent on-source time after discarding unusable visibility data.
+The nearby source J1039+811 (0.65\,\,Jy) was observed every 20 minutes for
 pointing, amplitude, and phase calibration. Mars was observed as the primary
@@
 $15\% calibration accuracy.
-The {\sc MIRIAD} package was used to calibrate and analyze the visibility data which are deconvolved and imaged using
-the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 13$\farcs$6 $\times$ 
-5\farcs8 for the upper sideband image cube.
-The final rms noise is $\sigma_{\rm ch}$ = 13.7 mJy beam\pmOne\ per bin with a channel width of $\sim$29 km\pmOne, and $\sigma$ = 1.825 Jy km s\pmOne\ $\rm beam^{-1}$ over a channel width of 218.7 MHz (corresponding to $\sim$610 km s\pmOne).
+The {\sc MIRIAD} package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
+the CLEAN algorithm with ``natural" weighting.
+This yields a synthesized clean beam size of 11$\farcs$3\,$\times$\,6\farcs1, at a position angle of $-$56.1$\degr$ east of north for the upper sideband image cube.
+The rms noise of the data prior to continuum subtraction is $\sigma_{\rm ch}$\,=\,8.75\,\,mJy\,\,beam\pmOne\ per bin 
+with a channel width of $\sim$29 km\,\,s\pmOne
+% spectra
+, whereas the final rms noise of the continuum subtracted data is $\sigma_{\rm ch}$\,=\,8.71\,\,mJy\,\,beam\pmOne\ per bin with 
+the same channel width, and $\sigma$\,=\,1.00\,Jy\,\,km\,\,s\pmOne\,\,$\rm beam^{-1}$ over a channel 
+width of 198 MHz (corresponding to $\sim$553\,\,km\,\,s\pmOne). 
+%mom0
 The continuum image is created by
-averaging over all the line-free channels, this yields a synthesized clean beam size of 16\farcs7 $\times$ 7\farcs2 and an 
-rms noise of 0.55 mJy beam\pmOne.
+averaging over all line-free channels, this yields a synthesized clean beam size of 11\farcs9\,$\times$\,6\farcs5, at a position angle of $-$55.9$\degr$ east of north and an 
+rms noise of 0.51\,\,mJy\,\,beam\pmOne.
 
 \section{Results}\label{sec:res}
-\subsection{New results: Continuum Emission} 
-Averaging over all the line-free channels, we detect continuum emission at 10$\sigma$ significance at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz ($\sim$2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$1.7 mm) at $z$ = 0.685.
+%\subsection{New Results: Continuum Emission} 
+\subsection{New Results: 3C220.3} 
+Averaging over all line-free channels, we detect continuum emission at 9$\sigma$ significance at an averaged frequency of $\nu_{cont}$\,=\,104.2106 GHz ($\sim$2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$1.7 mm) at $z$\,=\,0.685.
 In this lens system, the
-foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum to be dominated by synchrotron emission from the foreground galaxy.
+foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum emission to be dominated by the foreground galaxy (see \S \ref{sec:SEDFg} for details).
 We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission.
-The deconvolved source size is 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60, and the integrated flux density is 7.18 $\pm$ 0.69 mJy.
-At the peak position of the continuum emission, the peak flux density is S$_\nu$ = 5.56 $\pm$ 0.54
-mJy beam\pmOne.
+The deconvolved source size is (10\farcs9\,$\pm$\,4\farcs0)\,$\times$\,(3\farcs4\,$\pm$\,2\farcs1), and the integrated flux density is 7.50\,$\pm$\,1.30\,\,mJy.
+At the peak position of the continuum emission, the peak flux density is S$_\nu$\,=\,4.91\,$\pm$\,0.54\,\,mJy\,\,beam\pmOne.
 An overlay image of the 104 GHz continuum emission on the 9 GHz continuum measurement (H14) is shown in Figure \ref{fig:cont}.
-This demonstrates that at the resolution of our observation, the continuum detection is marginally resolved.
+This demonstrates that at the resolution of our observations, the continuum emission is marginally resolved.
 It is therefore plausible that non-thermal emission from both the lobes and the radio core dominate the integrated flux density in our measurement.
+
+The frequency range of our observations covers the HCO$^+$(2$-$1), HNC($J$\,=\,2\,$\rightarrow$\,1), and H$_2$O(3$_{13}$\,$-$\,2$_{20}$) 
+transition line emission in the foreground galaxy, at 
+the redshifted frequencies of 105.86, 107.71, and 108.79\,\,GHz, respectively. We establish 3$\sigma$ upper limits employing a typical line width of 
+$\sim$\,300\,\,km\,\,s\pmOne, based on the CO($J$\,=\,1\,$\rightarrow$\,0) line measurement in the sample of local radio galaxies \citep[$z$ $<$ 0.1; ][]{Smolcic11a}, resulting in 3$\sigma$ of 7.839\,\,Jy\,\,km\,\,s\pmOne.\\ \\
+Question for DR: 3sigma using FWHM or total line width (FWZI?)
 
@@
 \centering
-\includegraphics[width=0.80\textwidth]{Figure/ContPanel}
-\caption{The central cross on each image indicates the position of the radio core of 3C220.3. The contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
+\includegraphics[width=0.80\textwidth]{Figure/ContPanel.pdf}
+\caption{Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 11\farcs9\,$\times$\,6\farcs5, at P.A.\,=\,
+$-$56$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
+foreground radio galaxy 3C220.3 overlaid on the 9 GHz emission (green contours and grayscale; H14). The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A. 
+76$\degr$. The central cross on each image indicates the position of the radio core of 3C220.3. The contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
 of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne; the contour levels of the 9 GHz continuum 
-emission start at $\pm$4$\sigma$ of $\sigma$ = 0.064 mJy beam\pmOne\ and increment at steps of $\pm$2$^n\sigma$, 
-where n is a positive integer.
-Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 16\farcs7 $\times$ 7\farcs2, at P.A. = 
--58$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
-foreground radio galaxy 3C220.3 overlaid on the 9 GHz emission (green and grayscale) (H14). The synthesized beam size of the VLA observations is 0$\farcs$6 $\times$ 0$\farcs$2 at P.A. 
-76$\degr$. 
+emission start at $\pm$4$\sigma$ where $\sigma$\,=\,0.064 mJy beam\pmOne\ and increment at steps of $\pm$2$^n\sigma$, 
+where $n$ is a positive integer.
 \label{fig:cont}}
 \end{figure*}
-
-\subsection{New results: \CO line emission}
-We detect \CO line emission at 5$\sigma$ significance toward the background SMG SMM J0939 at $z$ = 2.221.
-The line profile in Figure \ref{fig:mom0} is extracted at the peak position of the CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 19.9 $\pm
-$ 2.2 mJy superimposed on a continuum level of 3.46 $\pm$ 0.40 mJy, and full width at half-maximum (FWHM) of 542 $\pm$ 32 km s\pmOne. 
-The spatial extent of the SMG is $\sim$5$\arcsec$ as shown in the Submillimeter Array (SMA) 1 mm dust continuum in Figure \ref{fig:mom0}.
-As such, the \CO emission in the SMG is spatially unresolved.
+%\subsection{New Results: \CO Line Emission}
+\subsection{New Results: SMM\,J0939\\ \CO Line Emission}
+We detect \CO line emission at $\sim$10(?yes?no?)$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
+The spatial extent of this SMG is $\sim$5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum in Figure \ref{fig:mom0}; as such, the detected \CO line emission is spatially unresolved.
+The line profile in Figure \ref{fig:mom0} is therefore extracted at the peak position of the unresolved CO emission.
+Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.83\,$\pm$\,2.68\,\,mJy, superimposed on a continuum level of 4.19\,$\pm$\,0.49\,\,mJy, and full width at half-maximum (FWHM) of 557\,$\pm$\,36\,\,km\,\,s\pmOne.
 We construct a velocity-integrated (0th moment) map of the \CO 
-emission using the data with continuum subtracted in the visibility plane.
-This results in a velocity-integrated \CO line flux of $S_{\rm CO}$ = 10.7 $\pm$ 2.12 Jy km s\pmOne\ over the FWZI velocity range of $\Delta v\sim$914 km s\pmOne, the uncertainty does not include $\sim$ 15\% calibration uncertainty.
-We ignore primary beam correction given that the source is close to the phase center, and the source is unresolved (\ie much smaller than the primary beam size).
-This \CO line measurement confirms the redshift of SMM J0939 at $z$ = 2.221 $\pm$ blah.
+emission from the data after subtracting continuum emission in the visibility plane.
+This results in a velocity-integrated \CO line flux of $S_{\rm CO}$\,=\,10.7\,$\pm$\,1.3 Jy km\,\,s\pmOne\ over the FWZI velocity range of $\Delta v\sim$\,914 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration uncertainty.
+We ignore primary beam correction given that the source is close to the phase center and is unresolved (\ie much smaller than the primary beam size).
+Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.22122\,$\pm$\,0.00007.
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{Figure/LinePanel}
-\includegraphics[width=0.65\textwidth]{Figure/peak28_WiderSpectrum}
-\caption{The central cross on each image corresponds to the same coordinates.
-The contour levels start at $\pm$2$\sigma$ and $\pm$3$\sigma$ for the CARMA line emission and the SMA continuum emission, respectively, incrementing at
-steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the \CO line emission toward 
-the background SMG with $\sigma$ = 1.8 Jy km s\pmOne\ beam\pmOne over a velocity range of $\Delta v\sim$610 km s\pmOne\ . The angular resolution is 13$\farcs$6 $\times$ 
-5\farcs8, as indicated in the bottom left corner. 
-Top Right: Contours of the \CO line emission (red) overlaid on the SMA 1 mm dust continuum (green; H14) with $\sigma_{\rm 1 mm}$ = 0.84 mJy beam\pmOne.
+\includegraphics[width=0.8\textwidth]{Figure/LinePanel.pdf}
+\includegraphics[width=0.65\textwidth]{Figure/smmj0939-co32_spec.eps}
+\caption{Top Left: Continuum-subtracted moment-0 map of \CO line emission toward 
+the background SMG with $\sigma$\,=\,1.00\,Jy\,\,km\,\,s\pmOne\ beam\pmOne\ over a velocity range of $\Delta v\sim$553\,km\,\,s\pmOne.
+The angular resolution is 11$\farcs$3\,$\times$\,6\farcs1, at P.A.\,=\,$-$56\degr, as indicated in the bottom left corner.
+Top Right: Contours of the \CO line emission (red) overlaid on the SMA 1\,mm dust continuum (green contours and grayscale; H14) with $\sigma_{\rm 1\,mm}$\,=\,0.84 mJy beam\pmOne.
 The beam size of the SMA data is 1\farcs4$ \times $1\farcs2, P.A.
--34\degr, as shown
-in the bottom left corner. Bottom: 
-The spectrum extracted at the peak position of the CO line emission. The spectral resolution is $\Delta v$ $\sim$29 km s\pmOne\ with an rms of $\sigma_{\rm ch}$ = 12.5 mJy beam\pmOne\ per channel.
+$-$34\degr, as shown
+in the bottom left corner. 
+The central cross on each image corresponds to the same coordinates as in Figure \ref{fig:cont}. The contour levels start at $\pm$3$\sigma$, incrementing at
+steps of $\pm$1$\sigma$. 
+Bottom: 
+Spectrum extracted at the peak position of CO line emission, with a spectral resolution of $\Delta v$ $\sim$29 km\,\,s\pmOne\, and an rms of $\sigma_{\rm ch}$\,=\,8.75 mJy beam\pmOne\ per channel.
 Solid black line shows the Gaussian fit to the \CO line profile. Yellow histogram shows the 
-flux density as a function of velocity offset, where 0 km s\pmOne\ corresponds to $z$ = 2.221. \label{fig:mom0}}
+flux density as a function of velocity offset, where the velocity scale is relative to $z$\,=\,2.221. 
+%where 0 km\,\,s\pmOne\ corresponds to $z$\,=\,2.221. 
+\label{fig:mom0}}
 \end{figure*}
@@
 To study the intrinsic properties of the background galaxy, we determine the magnification factor by performing
-lens modeling using the SMA 1 mm archival data of this system. Lens modeling is carried out in the visibility
-(uv-) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}\footnote{https://github.com/sbussmann/uvmcmcfit}
+lens modeling on the SMA 1\,mm archival data of this system. Lens modeling is carried out in the visibility
+({\it uv-}) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}\footnote{https://github.com/sbussmann/uvmcmcfit}
 \citep{Bussmann15a}. The code uses an affine-invariant Markov chain Monte Carlo (MCMC) approach to sample the posterior
@@
 
-We fix the phase center to coordinates ($\alpha$, $\delta$) (J2000) = (9:39:23.54, 83:15:26.10), the
-offset positions of the lenses and source are referenced to this phase center. The primary lens (3C220.3) is
-described by 5 free parameters: the angular offset relative to
+We fix the phase center to coordinates ($\alpha$,\,$\delta$)\,\,(J2000)\,=\,(9:39:23.54,\,\,83:15:26.10), the
+angular offsets of the lenses and source are referenced to this phase center. The primary lens (3C220.3) is
+described by five free parameters: the angular offset relative to
 the chosen phase center in the image ($\Delta \alpha_{\rm
-lens0}$ and $\Delta \delta_{\rm lens0}$), the angular Einstein radius ($\theta_{\rm E,0}$), the
+lens0}$ and $\Delta \delta_{\rm lens0}$), the angular Einstein radius ($\theta_{\rm E0}$), the
 axial ratio ($q_{\rm lens0}$), and the position angle ($\phi_{\rm lens0}$). The secondary lens (companion B) is
-described by 3 free parameters: $\theta_{\rm E,1}$, $q_{\rm lens1}$, and $\phi_{\rm lens1}$. The angular offset
+described by three free parameters: $\theta_{\rm E1}$, $q_{\rm lens1}$, and $\phi_{\rm lens1}$. The angular offset
 of the secondary
@@
 the primary lens.
-The source (SMM J0939) is parameterized by
-6 free parameters: the position of the source relative to the
+The source (SMM\,J0939) is parameterized by
+six free parameters: the position of the source relative to the
 primary lens ($\Delta \alpha_{\rm s}$ and $\Delta
-\delta_{\rm s}$), the total intrinsic flux density ($S$), the
-effective radius ($r_{\rm s} = \sqrt{a_{\rm s} b_{\rm s}}$), the axial
-ratio ($q_{\rm s}$ =  $b_{\rm s}/a_{\rm s}$), and the position angle
+\delta_{\rm s}$), the total intrinsic flux density ($S_\nu$), the
+effective radius ($r_{\rm s}\,=\,\sqrt{a_{\rm s} b_{\rm s}}$), the axial
+ratio ($q_{\rm s}$\,=\, $b_{\rm s}/a_{\rm s}$), and the position angle
 ($\phi_{\rm s}$).
-The total number of free parameters is $N_{\rm free}$ = 14. The best-fit model is obtained by maximizing the
+The total number of free parameters is $N_{\rm free}$\,=\,14. The best-fit model is obtained by maximizing the
 Gaussian likelihood function $ \mathcal{L} $ according to:
 \begin{equation}
-    \mathcal{L} = \sum_{u, v}\left( \frac{|V_{\rm data} - V_{\rm
+    \mathcal{L}\,=\,\sum_{u, v}\left( \frac{|V_{\rm data} - V_{\rm
     model}|^2}{\sigma^2} + {\rm log}(2 \pi \sigma^2) \right)
@@
 \noindent where $\sigma$ is determined from the scatter in the visibilities within a
-single spectral window (natural weighting).
+single spectral window (``natural" weighting).
 
@@
 \includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_goodfit1970}
-\caption{Double-lens modeling of SMM J0939 using {\sc uvmcmcfit} on the SMA 1 mm continuum data.
+\caption{Double-lens modeling of SMM\,J0939 using {\sc uvmcmcfit} on the SMA 1\,mm continuum data.
 The contours start at $\pm$2$\sigma$, incrementing at
@@
 show the negative residuals. 
-Left: SMA 1 mm continuum (red contours) overlaid on the best-fit model (grayscale image) assuming an elliptical Gaussian profile for the background SMG.
+Left: SMA 1\,mm continuum (red contours) overlaid on the best-fit model (grayscale image) assuming an elliptical Gaussian profile for the background SMG.
 The lenses are represented as black dots, the half-light area of the background source is represented as magenta ellipse, and the critical curves are represented as orange curves.
@@
 
-The resulting best-fit model as shown in Figure \ref{fig:lens} shows no significant bowls in the residual
+The resulting best-fit model as shown in Figure\,\,\ref{fig:lens} shows no significant bowls in the residual
 image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
-The best-fit model yields a magnification
-factor of $\mu_{\rm L}$ = 10.13 $\pm$ 1.38, this is consistent the value reported by H14 within errors. All best-fit
-parameters are listed in Table \ref{tab:lensParam}. The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ =
-1.22 $\pm$ 0.01 (8.75 kpc at $z$ = 0.685) and $\theta_{E}$ = 0.75 $\pm$ 0.02 (5.34 kpc at $z$ = 0.685),
-the corresponding masses within the Einstein radii are $M(\theta < \theta_{\rm E})$ = (4.86 $\pm$ 0.08) $\times$ 10$^{11}$ 
-\Msun\ 
-and $M(\theta < \theta_{\rm E})$ = (1.82 $\pm$ 0.07) $\times$ 10$^{11}$ \Msun, respectively. 
+Our best-fit model yields a magnification
+factor of $\mu_{\rm L}$\,=\,10.13\,$\pm$\,1.38, this is consistent the value reported by H14 within the errors. All best-fit
+parameters are listed in Table \ref{tab:lensParam}.
+The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$\,=\,1.22\,$\pm$\,0.01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$\,=\,0.75\,$\pm$\,0.02 (5.34 kpc at $z$\,=\,0.685),
+the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_{\rm E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_{\rm E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
 \input{table_lensParams}
 
-\subsection{SED fitting} \label{sec:SED}
-\subsubsection{3C220.3}
-Synchrotron continuum emission from extended components of a radio galaxy decreases with increasing frequencies, 
-and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$ where the 
+\subsection{SED Fitting} \label{sec:SED}
+\subsubsection{3C220.3}\label{sec:SEDFg}
+Synchrotron continuum emission from extended components of a radio galaxy decreases with increasing radio frequencies, 
+and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$, where the 
 spectral index $\alpha$ is $\gtrsim$ 0.5. While the contribution from extended components decreases, studies using 
 samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises 
-and dominates the flux density at higher frequencies \citep{Kellermann81a,Begelman84a}. At observed-frame $\sim$ 90 GHz, 
-observations of the FR-II radio galaxy, 3C220.1 at $z$ = 0.610 has been reported to be the case 
-\citep{Hardcastle08a}. Besides, an upper 
-limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a} and a clear detection of 0.8 mJy at 9 GHz (H14) appears to 
-be indicative of a substantially inverted spectrum of the core (Figure \ref{fig:SED}).
-Consequently, we would naively expect the integrated flux density in our continuum detection of $S_{\rm 104GHz}$ = 7.18 $\pm$ 0.69 mJy to be dominated by the unresolved core component of the foreground FR-II, which is at $z$ = 0.685.
-== wouldn't this be contradicting if we know the core is unresolved, why would we jump into looking at the integrated flux ==
-However, the inferred deconvolved spatial size of the source matching that in a resolved image (in Figure 1) is 
+and dominates the flux density at higher frequencies \citep{Kellermann81a,Begelman84a}.
+This has been observed in a FR-II galaxy at a similar redshift\,--\,3C220.1 at the redshift of $z$\,=\,0.610, where observations were carried out at observed-frame $\sim$\,90 GHz \citep{Hardcastle08a}.
+It is noteworthy that prior to our observations, 3C220.1 was the only FR-II galaxy with high frequency observations at $z$\,$>$\,0.6.
+Previous studies of the core component of 3C220.3 have established upper
+limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a} and an unambiguous detection of 0.8 mJy at 9 GHz (H14), suggesting a substantially inverted spectrum of the core (Figure \ref{fig:SED}).
+Consequently, we may naively expect the integrated flux density in our continuum detection of $S_{\rm 104GHz}$\,=\,7.50\,$\pm$\,1.30\,\,mJy to be dominated by the unresolved core component of the foreground FR-II galaxy, which is at $z$\,=\,0.685.
+However, the inferred deconvolved spatial size of the source matching that in the resolved image (see Figure 1) is 
 suggestive of a marginally resolved detection of the extended components with non-negligible emission. 
@@
 axis along the 
-lobes of the radio galaxy, as shown in Figure \ref{fig:cont}. We investigate this disparity by fitting an SED to 
-existing data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to 
+lobes of the radio galaxy, as shown in Figure \ref{fig:cont}. We investigate this disparity by fitting models to 
+existing SED data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to 
 estimate the flux density of the lobes at the frequency of our continuum measurement. 
 \input{table_SED}
-Following Equation (1) in \citet{Cleary07a}, the fit to the lobes emission can be expressed as a parabolic function:
+Following Equation (1) in \citet{Cleary07a}, the fit to the lobe emission can be expressed as a parabolic function:
 \begin{equation}
@@
 distribution. 
-The extrapolated flux density at 104 GHz is consistent with the peak flux density of our continuum 
-measurement (Figure \ref{fig:SED}). The 10$\sigma$ detection of the continuum thereby suggests
+The extrapolated flux density at 104\,\,GHz is consistent with the flux density of our continuum 
+measurement (Figure \ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests
 a dominant contribution from the lobes, and the peak flux density therefore does not appear to be emission toward 
-the core. Moreover, the peak position of the 104 GHz continuum is
+the core. Moreover, the peak position of the 104\,\,GHz continuum is
 centered toward the northern lobe (Figure \ref{fig:cont}), which further supports our argument. We did not 
@@
 taken 
-across epochs.\par
-Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, and some exhibit spectral steepening either between cm or mm wavelengths (\eg 3C123); at the resolution of our observation, however, it is unclear whether the integrated flux is dominated by the emission from the compact hotspot or the emission from the surrounding diffuse lobe components.
-Nonetheless, high resolution observations of 3C220.3 at mm wavelengths (rest-frame $\sim$ 60 GHz) will provide important insight on hotspot emission studies.
+across different epochs. 
+EDIT HERE \par
+From our interpretation, we place an upper limit of $S_\nu$\,$<$\,2.59 mJy on the core component using the difference.
+\par
+Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, where some exhibit spectral steepening in cm and mm wavelengths (\eg 3C123).
+At the resolution of our observations, it is unclear whether the integrated flux is dominated by the emission from the compact hotspot or the emission from the surrounding diffuse lobe components.
 
@@
 \includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED_longticks.pdf}
-\caption{The SED of 3C220.3 (solid blue line) and SMM J0939 (dashed blue line and solid cyan line) including the new measurements presented in this paper. 
+\caption{The SED of 3C220.3 (solid purple line) and SMM\,J0939 (dashed purple line and solid cyan line) including the new measurements presented in this paper. 
 Black dots represent existing data of 3C220.3 (see Table \ref{tab:SEDdataRadio}). Red dots at 104 GHz correspond to 
@@
 
-\subsubsection{SMM J0939+8315} 
-To constrain the dust and gas properties in the ISM of SMM J0939, we perform SED fitting on the
+\subsubsection{SMM\,J0939+8315} \label{sec:SEDBg}
+To constrain the dust and gas properties in the ISM of SMM\,J0939, we perform SED fitting to the
 photometric data obtained with {\it Herschel}/PACS and SPIRE, at wavelengths
-between observed-frame 70 \micron $-$ 500 \micron, and interferometric data with the SMA at 1 mm (H14). We use the publicly
-available software {\sc mbb\_emcee}\footnote{https://github.com/aconley/mbb\_emcee} to perform SED fitting, the code uses an affine-invariant Markov chain Monte
-Carlo (MCMC) approach, the details are described by \citet{Riechers13a} and \citet{Dowell14a}. The
+between observed-frame 70 \micron $-$ 500 \micron, and interferometric data with the SMA at 1\,mm (H14). We use the publicly
+available software {\sc mbb\_emcee}\footnote{https://github.com/aconley/mbb\_emcee} to perform the SED fitting; the code uses an affine-invariant Markov chain Monte
+Carlo (MCMC) approach, and further details of the code are given by \citet{Riechers13a} and \citet{Dowell14a}. The
 functional form of the fit comprises a single-temperature, modified blackbody function joined to a $S_{\lambda} \propto \lambda^\alpha
@@
 We fit both optically thick and optically thin models. In the optically thick case, the wavelength $
-\lambda_0$ = ${c}/{\nu_0}$ is an additional parameter which represents where the optical
+\lambda_0$\,=\,${c}/{\nu_0}$ is an additional parameter representing the rest-frame wavelength at which the optical
 depth $\tau_{\nu} =$ ($\nu$/$\nu_0$)$^\beta$ reaches unity. Thus, the functional form of the modified blackbody
@@
 \end{equation}
-where $T$ is the rest-frame characteristic cold dust temperature, $\lambda_0$ is rest-frame wavelength
-where the optical depth reaches unity, $\beta$ is the dust emissivity (or spectral index of the dust extinction
+where $T$ is the rest-frame characteristic cold dust temperature, $\beta$ is the dust emissivity (or spectral index of the dust extinction
 curve), and $\alpha$ is the power law spectral index. The overall fit is normalized using the observed-frame 500
-$\micron$ flux density, hence this becomes an additional parameter in the fit. In both models, we impose an upper limit on $
-\lambda_0$ to 2000 \micron, and on the observed-frame dust temperature $T/(1+z)$ to 60 K. We fix the upper limit on 
+$\micron$ flux density, hence this becomes an additional parameter in the fit.
+For both models, we impose an upper limit on the observed-frame dust temperature ($T/(1+z)$) to 60 K, and for the optically thick model, we impose an upper limit on $\lambda_0$ to 2000\,\,\micron.
+Additionally, we fix the upper limits on
 $\beta$ to be 3.0 and 2.2 for the optically thin model and optically thick model, respectively.
@@
 The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in the Appendix. The best-fit solution of an optically thin
-model corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of an optically thick model
-corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than in the optically thin
+model corresponds to $\chi^2$\,=\,5.31 with 3 degrees of freedom, whereas that of an optically thick model
+corresponds to $\chi^2$\,=\,2.25 with 2 degrees of freedom, suggesting a better fit than in the optically thin
 case. In the subsequent analysis, we employ the inferred values from the optically thick model.
-The best-fit solution yields a far-infrared (FIR) luminosity of $L_{\rm FIR (42.5-122.5\micron)}$ = 53.3$^{+1.1}_{-1.1}\times$10$^{12}$\Lsun, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$ = 88.5$^{+2.6}_{-2.6}\times$10$
-^{12}$\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64 m$^2$ kg\pmOne\ at 125.0 $
+The best-fit solution yields a rest-frame FIR luminosity of $L_{\rm FIR (42.5-122.5\micron)}$\,=\,53.3$^{+1.1}_{-1.1}\times$10$^{12}$\Lsun, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$\,=\,88.5$^{+2.6}_{-2.6}\times$10$
+^{12}$\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$\,=\,2.64 m$^2$ kg\pmOne\ at 125.0 $
 \micron$ \citep{Dunne03a}, we derive the dust mass using the following expression:
 \begin{equation}
-M_{\rm dust} = S_{\nu} D_{L}^2 [(1 + z) \kappa_{\nu} B_{\nu}]^{-1} \tau_{\nu} [1-
+M_{\rm dust}\,=\,S_{\nu} D_{L}^2 [(1 + z) \kappa_{\nu} B_{\nu}]^{-1} \tau_{\nu} [1-
 \exp(-\tau_{\nu})]^{-1}
@@
 absorption coefficient in cm$^2$ g\pmOne, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function,
-all quantities are expressed in the observed-frame. We find a dust mass of $M_{\rm dust}$ =
-50.5$^{20.4}_{-20.2}\times$10$^8$\Msun, the uncertainties do not include those of $\kappa_{\nu}$. These values are based on SED fitting to the photometric data, \ie prior
+all quantities are expressed in the observed-frame.
+We find a dust mass of $M_{\rm dust}$\,=\,50.5$^{20.4}_{-20.2}\times$10$^8$\,\,\Msun, the uncertainties do not include those of $\kappa_{\nu}$.
+These values are based on SED fitting to the photometric data, \ie prior
 to lensing correction.
@@
 With the limited amount of data in the FIR waveband, the dust mass is weakly constrained. 
-We perform an additional optically thick model fitting where we loosen the upper limit of $\beta$ from 2.2 to 3.0, while the difference between all best-fit parameters in this scenario and those using an upper limit of 2.2 (see Table \ref{tab:mbb}) is within 3\%, we find that the dust mass is boosted by a factor of $\sim$2.
+We perform an additional SED fitting using an optically thick model where we loosen the upper limit of $\beta$ from 2.2 to 3.0, while the difference between all best-fit parameters in this scenario and those using an upper limit of 2.2 (see Table \ref{tab:mbb}) is within 3\%, we find that the dust mass is boosted by a factor of $\sim$2.
 
-\subsection{Molecular gas mass}
-While the ground state CO transition line, CO($J$ = 1 \rarr\ 0) traces the cold molecular gas in the ISM
+\subsection{Molecular Gas Mass}
+While the ground state CO transition line, CO($J$\,=\,1 \rarr\ 0) traces the cold molecular gas in the ISM
 \citep*[\eg][]{Downes98a,Wilson70a}, CO($J$ $>$ 1) transition lines are frequently observed at high redshifts as the
@@
    Yet, recent observations of this line have demonstrated that SMGs can indeed be subthermally excited
-   \citep{Harris10a,Riechers11c,Riechers11d,Ivison11a}; based on observations toward SMGs of both the \CO and the CO($J$ = 1 \rarr\ 0) lines, the 
+   \citep{Harris10a,Riechers11c,Riechers11d,Ivison11a}; based on observations toward SMGs of both the \CO and the CO($J$\,=\,1 \rarr\ 0) lines, the 
    brightness temperature ratio has been inferred as $R_{\rm 31}<$ 0.8 \citep
@@
    is $R_{\rm 31}\sim$ 1 \citep{Riechers06a, Riechers11a, Scott11a}. 
-Here, we derive the molecular gas mass assuming thermalized excitation of CO, \eg we adopt $R_{\rm 31}$ = 1 as SMM J0939 is 
-postulated to be hosting a type-2 quasar. \par
-We calculate the CO($J$ = 1 \rarr\ 0) line luminosity using standard relation 
+Here, we derive the molecular gas mass 
+assuming thermalized excitation of CO, 
+\eg we adopt $R_{\rm 31}$\,=\,1 as SMM\,J0939 is 
+postulated to be hosting a type-2 quasar; this is based on the reported brightness temperature ratio of $R_{\rm 31}$\,=\,1.00\,$\pm$\,0.10 for the type-2 quasar host IRAS F10214+4724 \citep{Riechers11a}.
+\par
+We calculate the CO($J$\,=\,1 \rarr\ 0) line luminosity using standard relation 
 \citep[\eg][]{Solomon05a,Carilli13a}:
 \begin{equation}
-L^{\prime}_{\rm CO} = \frac{3.25\times10^7}{\nu_{\rm CO (3-2), rest}^2}\times \frac{D_L^2}{\mu} \times
+L^{\prime}_{\rm CO}\,=\,\frac{3.25\times10^7}{\nu_{\rm CO (3-2), rest}^2}\times \frac{D_L^2}{\mu} \times
 \frac{I_{\rm CO(3-2)}} {R_{\rm 31} (1 + z)}
 \end{equation}
-where $\nu_{\rm CO (3-2), rest}$ is the rest-frame frequency of the \CO line in GHz, $D_L$ is the luminosity distance in Mpc, and $I_{\rm CO(3-2)}$ is the \CO line flux in Jy km s\pmOne.
-This corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (2.91 $\pm$ 0.78)$\times$10$^{10}$(10.1/$\mu_{\rm L}$) \LpU\ after correcting for lensing magnification; the inferred total molecular gas mass is therefore $M_{\rm gas}$ = (2.33 $\pm$ 0.62) $\times$10$^{10}$\Msun.
+where $\nu_{\rm CO (3-2), rest}$ is the rest-frame frequency of the \CO line in GHz, $D_L$ is the luminosity distance in Mpc, and $I_{\rm CO(3-2)}$ is the \CO line flux in Jy km\,\,s\pmOne.
+This corresponds to $L^{\prime}_{\rm CO (1-0)}$\,=\,(2.91\,$\pm$\,0.78)$\times$10$^{10}$(10.1/$\mu_{\rm L}$) \LpU\ after correcting for lensing magnification; the inferred total molecular gas mass is therefore $M_{\rm gas}$\,=\,(2.33\,$\pm$\,0.62) $\times$10$^{10}$\Msun.
 We assumed a conversion factor of $\alpha_{\rm CO}$ =
@@
 This results in a gas-to-dust
-ratio of $f_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 47 $\pm$ 21, this is in good agreement with the 
+ratio of $f_{\rm gas-dust}$\,=\,$M_{\rm gas}/M_{\rm dust}$\,=\,47\,$\pm$\,21, this is in good agreement with the 
 values found in other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.
 % find an excellent agreement of blah with blah
-\subsection{Star formation rate}
-We derive the star formation rate (SFR) using the \citet{Kennicutt98a} relation, assuming a \citet{Chabrier03a}
-stellar initial mass (IMF) function. This yields a SFR$_{\rm IR}$ of 874 $\pm$ 122 $M\sun$ yr\pmOne, derived using the lensing-corrected total IR luminosity (L$_{\rm IR}$) derived from SED 
-fitting, and assuming negligible contributions from AGN heating, which is at most BLAH \% as no evidence of warm dust (from MIR). \footnote{SFR$_{\rm FIR}$ = 526 $\pm$ 72 $M_
-\odot$ yr\pmOne\ }
+\subsection{Star Formation Rate}
+No strong evidence of a warm dust component is found in SMM\,J0939 based on the mid-IR continuum measurements (see Figure \ref{fig:SED}), hence we derive the star formation rate (SFR) assuming negligible contributions to the IR luminosity due to AGN heating.
+Using the \citet{Kennicutt98a} relation and assuming \citet{Chabrier03a}
+stellar initial mass (IMF) function\footnote{SFR$_{\rm FIR}$\,=\,526\,$\pm$\,72 $M_
+\odot$ yr\pmOne\ }, 
+the SFR$_{\rm IR}$ is 874\,$\pm$\,122\,\,$M\sun$\,\,yr\pmOne.
+Assuming constant SFR, the time for which the starburst in SMM\,J0939 can be maintained at its
+current SFR can be approximated as the gas depletion timescale, $\tau_{\rm depl}$\,=\,$M_{\rm gas}$/SFR. 
+This corresponds to $\tau_{\rm depl}$\,=\,25.6\,$\pm$\,0.6 Myr, which is in good agreement with that found in other SMGs \citep[\eg][]{Greve05a}.
 
-Assuming constant SFR, the minimum time for which the starburst in SMM J0939 can be maintained at its
-current SFR can be approximated as the gas depletion timescale, $\tau$ = $M_{\rm gas}$/SFR. 
-This corresponds to $\tau_{\rm IR}$ = 25.6 $\pm$ 0.6 Myr.
+\subsection{Star Formation Efficiency}
+The SFR per unit mass of molecular gas is commonly taken as a
+measure of the star formation efficiency, SFE\,=\,SFR/$M_{\rm gas}$. We compute this ratio using lensing-corrected IR 
+luminosity and CO luminosity, i.e., SFE\,=\,$L_{\rm IR}$/\Lp, this makes no assumptions on the CO luminosity to gas mass conversion factor ($\alpha_{\rm CO}$) as well as the 
+choice of IMF, however, this assumes that differential lensing effect between the CO and infrared emission is negligible. 
+The resulting ratio is SFE$_{\rm IR}$\,=\,300\,$\pm$\,10 \Lsun (\LpU)$^{-1}$, this is comparable
+to what is found in ``typical" SMGs \citep{Riechers11c,Tacconi06a,Greve05a}.
 
-Move to discussion: Compare THIS NUMBER: with other SMGs \citep[\eg][]{Greve05a}.
+\subsection{Dynamical Mass} 
+Based on our \CO line measurement, we can estimate the dynamical mass of SMM\,J0939 using an isotropic virial estimator \citep[\eg][]{Engel10a}:
+\begin{equation}
+M_{\rm dyn}\,=\,2.8\times 10^5\Delta v_{\rm line}^ 2 R_{\rm eff}
+\end{equation}
+where $\Delta v_{\rm line}$ is in km\,\,s\pmOne, $R_{\rm eff}$ is in kpc, and $M_{\rm dyn}$ is in \Msun.
+We employ the FWHM linewidth of the \CO line for $\Delta v_{\rm line}$,
+and the half-light radius from our lens model for $R_{\rm eff}$, this assumes that the dust emission traces the same emitting region as the CO.
+The inferred dynamical mass is $M_{\rm dyn}$\,=\,(7.4\,$\pm$\,2.4)\,$\times$\,10$^{10}$\Msun, and the gas-to-dynamical mass fraction is $f_{\rm gas-to-dyn}$\,=\,0.32\,$\pm$\,0.14, this is consistent with that of other SMGs \citep{Tacconi06a}.
 
-\subsection{Star formation efficiency}
-The SFR per unit mass of molecular gas is commonly taken as a
-measure of the star formation efficiency, SFE = SFR/$M_{\rm gas}$. We compute this ratio using lensing-corrected infrared 
-luminosities ($L_{\rm IR}$) and CO($J$ = 1 \rarr\ 0) luminosity: SFE = $L_{\rm IR}$/\Lp, this ratio makes no assumptions on the gas mass conversion factor $\alpha$ as well as the 
-choice of IMF, however, this assumes that differential lensing effect between the CO and infrared emission is negligible. 
-The resulting ratios are SFE$_{\rm IR}$ = 300 $\pm$ 10 Myr\pmOne, which is comparable
-to what is found in "typical" SMGs \citep{Riechers10, Tacconi06, Greve05a}.
+\subsection{Star Formation and Gas Surface Densities}
+To compute surface densities, we divided half the inferred SFR and gas mass by the area subtended by the half-light 
+radius, resulting in $\Sigma_{\rm gas}$\,=\,4.67\,$\times$\,10$^9$\,\,\Msun\,\,kpc$^{-2}$ and $\Sigma_{\rm SF}$\,=\,175.20\,\,\Msun\,\,yr\pmOne\,\,kpc$^{-2}$, in good agreement with values typical for SMGs \citep{Tacconi08a}.
 
-\subsection{Dynamical mass} 
-We derive the dynamical mass of SMM J0939 using an isotropic virial estimator \citep[\eg][]{Engel10a}:
-\begin{equation}
-M_{\rm dyn} = 2.8\times 10^5\Delta v_{\rm line}^ 2 R_{\rm eff}
-\end{equation}
-where $\Delta v_{\rm line}$ is in km s\pmOne, $R_{\rm eff}$ is in kpc, and $M_{\rm dyn}$ is in \Msun.
-We employ the FWHM line width of our \CO measurement for $\Delta v_{\rm line}$,
-and the half-light radius from lens modeling for $R_{\rm eff}$, assuming the dust emission traces the same emitting region as the CO.
-This yields $M_{\rm dyn}$ = (7.4 $\pm$ 2.4) $\times$ 10$^{10}$\Msun , and gas-to-dynamical mass fraction of $f_{\rm gas-to-dyn}$ = $\approx$ 0.32, consistent that of other SMGs \citep{Greve06a,Tacconi06a}.
-
-\subsection{SFR and gas surface densities}
-To compute surface densities we divided half of the star formation rate or gas mass (so that no assumption of IMF) by the area subtended by the half-light (or effective) radius.
- the surface density of star formation against the molecular gas surface density.
+The inferred surface densities of SMM\,J0939 follow a universal Schmidt-Kennicutt relation between the star formation rate
+surface density and the molecular gas surface density reported by \citet{B07a}: $\Sigma_{\rm SF}$\,=\,9.3\,$\times$\,
+10$^{-5}$ ($M_{\rm gas}$/2$\pi R_{\rm 1/2}^2)^{1.71}$, which was derived using a sample consisting of high-redshift 
+galaxies
+ and local star-forming galaxies out to $z\ \sim$ 2.5, and assuming Chabrier IMF.
 
 \section{Discussion And Conclusions} \label{sec:conclusions}
-We present blah
+We present the detection of \CO line emission toward SMM\,J0939+8315, a strongly lensed SMG that is hosting a type-2 quasar, confirming the redshift of SMM\,J0939 with high precision at $z$\,=\,2.22122\,$\pm$\,0.00007.
+The peculiarity of this system allows us to put constraints on the SED of 3C220.3 using the underlying continuum detection at $\sim$104 GHz, we argue that the result is suggestive of a dominant contribution from the lobes and hotspots.
+%% ok up
 
-This paper focuses on a blah source J0939+8315, a lensed SMG that is likely to be hosting a type-2 quasar, this source offers an exceptional opportunity to
-investigate the gas mass and dynamics of this
-poorly-studied population of high z galaxies.
+The detection of CO with CO luminosity of \Lp\,=\,blah \LpU\ in SMM\,J0939 implies the presence of a large molecular gas reservoir, demonstrating the active star formation in 
+this SMG with SFR $\sim$ 874 \Msun\ yr\pmOne. Our findings are typical for SMGs, which supports the picture that SMGs are a 
+population of high-z galaxies that spawn most of the stellar mass in the early universe, thus play an important role 
+in galaxy evolution and formation.
 
-In this paper, we present blah of a strongly lensed blah at z = 2.221, at the epoch of cosmic star formation (cite)
+The detection of thermal dust emission in SMM\,J0939 implies a FIR Luminsoity of 
+Assuming the dominant heating mechanism is from young, massive stars, then the SFR implied from the LIR is blah
+From the IR continuum data, we expected contribution to the bolometric IR luminosity due to heating of the dust-enshrouded AGN is minor, the physical properties are therefore derived using the lensing-corrected bolometric IR luminosity.
+The high dust temperature is unusual for SMGs, but not unseen.
 
-We report a detection of \CO line.
-The continuum detection is marginally resolved, we place constraints on the SED of the foreground galaxy (accounting for radio 
-core and lobes emission). Our CO measurement confirms the redshift of this source, which was previously measured using CIV and HeII lines (H14).
+\input{table_compareSMG}
+We compare the properties of SMM\,J0939 with those found in strongly lensed, submm-bright galaxies at similar redshift -- HLSW-01 and the cosmic Eyelash, which have been studied in great detail.
+We list the gas and dust properties of these galaxies in Table \ref{tab:comapreSMG},
 
-The detection of CO in SMM J0939, implying a large molecular gas reservoir, demonstrates the active SF in SMGs. 
-The large CO luminosity suggests that a signification fraction of the FIR luminosity comes from SF, providing power for dust to re-radiate in FIR.
-BUt we also know that this source has an dust-enshrouded AGN, boosting the IR.
-The SFR inferred from the CO measurement is common for SMGs.
-the large amount of molecular gas further supports the picture that SMGs are galaxies with making up most of the stellar mass in the early universe, and is responsible for galaxy evolution and formation.
+Discussion of SMG, broad, population.
+We compare the properties of SMM\,J0939 to a type-2 quasar host -- F10214+2724, in which the molecular gas has been studied in great detail \citep{Riechers11a}.
 
-The magnification factor is blah, providing an opportunity to carry out detailed studies of the ISM in this population.
-
-The properties of this SMG blah, M$_{\rm dust}$, L$_{\rm FIR}$ of blah, L$_{\rm IR}$ of blah, yielding SFR of 
-blah . Comparing our findings to other SMGs / similar populations, we find blah, which is blah.
-
-We derive physical properties of the molecular gas in the ISM using IR as well as FIR luminosities.
-As studies have shown that contaminations of AGN in the FIR is less than blah \%, while most studies on SMGs uses the bolometric IR luminsoity, hence we derive these quantities using LIR as well for comparison.
-
-We compare the properties of SMM J0939 with two other SMGs with detailed studies -- HLSW-01 and the cosmic Eyelash.
-All sources are lensed, making spectral lines measurements relatively feasible than the fainter, un-lensed sources of the same population.
-
-Properties and comparison with similar galaxies in Table \ref{tab:comapreSMG}
-\input{table_compareSMG}
-Discussion of SMG, broad, population.
-look at "Lensed QSOs at high z observational, CO measurements (DB)" note
-
-In this paper, we blah. However, many questions regarding jets in radio galaxies remain. For example,
-
-Comparison to CO in other type-2 QSO: F10214+2724 \citep{Riechers11a}
+Radio galaxy lensing probability.
 
@@
 We acknowledge the WENSS team for providing the radio measurements for 3C220.3.
+We thank Shane Bussmann for providing {\sc uvmcmcfit} for lens modeling and useful discussion, and Alex Conley for providing {\sc mbb\_emcee} for SED fitting.
 Facilities: \facility{CARMA}
@@
 
-\begin{figure}[!tbp]
-\centering
-\includegraphics[width=0.90\textwidth]{Figure/posteriorPDFs}
-\caption{Marginalized posterior probabilities of each parameter in our lens modeling.
-\label{fig:LensPDF}}
-\end{figure}
+We perform SED fitting to the IR photometric data of SMM\,J0939 using {\sc mbb\_emcee} (see \S \ref{sec:SEDBg}), this code uses MCMC to fully sample the parameter space of each parameter.
+The bolometric IR luminosity and dust mass are then derived from the set of parameter values that maximize the likelihood.
+Figure \ref{fig:sedlikelihood} shows the correlations between each pair of parameters (off-diagonal) as well as the marginalized posterior probability distribution of each parameter (diagonal) for both optically thick and optically thin models.
+The set of best-fit parameters are denoted as black crosses in the 2D correlation plots, and vertical lines in the marginalized posterior probability distribution plots.
 
-\begin{figure}[!tbp]
+\begin{figure}[!tbph]
 \centering
@@
 \includegraphics[width=0.47\textwidth]{Figure/CorrelationPlot__thin_testSMA}
-\caption{Correlation plots from our SED fitting. Plots on the diagonal axes are marginalized posterior probability 
+\caption{Correlation plots from our SED fitting using an optically thick
+model (left), and an optically thin model (right). Marginalized posterior probability 
 distribution of each
-parameter. Off-diagonal plots are 2D histograms between parameters. Crosses denote the best-fit values in 
-the 2D correlation plot. Top: Optically thick
-model. Bottom: Optically thin model. $T/(1+z)$ is the observed-frame characteristic dust temperature.
+parameter is plotted on the diagonal axis of each panel, where the vertical lines indicate the best-fit value.
+The correlation plots between parameters are plotted as 2D histograms in the off-diagonal.
+Black crosses on each 2D histogram denote the
+best-fit values in 
+the 2D correlation plot.
 \label{fig:sedlikelihood}}

### 2015-07-19 Code/Plot_Image.py
RADIO continuum wasn't properly cleaned, now cleaned to 1.5 sigma

@@ -22,7 +22,7 @@ fig_line = plt.figure(2, figsize=(12, 5))
 # user define area
 ########################################
 sigma_9ghz          = 6.41094e-05
-sigma_cont          = 5.1e-4
+sigma_cont          = 4.9e-4
 sigma_line          = 1.0 # 1.35   # chan 65,85 (pretty)     # 1.0      # chan72,90 (pretty) mom0 without options=double,mosaic
 sigma_SMA           = 0.000836951
 

### 2015-07-19 Code/SEDfit.py

@@ -104,9 +104,9 @@ Core_3c220dot3_Jy = np.array([0.8e-3, 0.17e-3])     # Jy
 Core_3c220dot3_Hz = np.array([9.e9, 4.86e9])    # Hz
 
 # Our Data: [peak, integrated, difference]
-Point_Continuum_Jy = np.array([5.56e-3, 7.18e-3, 1.62e-3])
+Point_Continuum_Jy = np.array([5.18e-3, 9.46e-3, 4.28e-3])
 Point_Cont_Hz = np.array([1.042e11, 1.042e11, 1.02e11])     # Hz
-Point_error_Jy = np.array([5.0647e-4, 5.0647e-4, 5.0647e-4])    # Jy
+Point_error_Jy = np.array([0.24e-3, 0.364e-3, 0.88e-3])    # Jy
 
 
 ########################################

### 2015-07-19 Code/NumCrunching.py
replace mu from best to median, replaced I from with cont. to without cont., reformat

@@ -359,7 +359,7 @@ class prettyGalaxies:
         --------
         molecular gas mass fraction
         """
-        print self.M_gas, self.M_dyn
+#        print self.M_gas, self.M_dyn
         return self.M_gas / self.M_dyn
 
     def f_mol_total(self):
@@ -513,8 +513,10 @@ class prettyGalaxies:
             sigma_crit = c**2 / 4 / pi / G * d_AS / d_AL / d_ALS
             M_E_iters = pi * sigma_crit * theta_E_iters**2 / 2e33
             err = np.array(pi * sigma_crit * theta_E_cm*2. * e_theta_E_cm / 2e33)  # (  propagation of error)
+
             M_E[targ] = np.mean(M_E_iters)
             e_M_E[targ] = np.std(M_E_iters)
+            print e_M_E
 
             vdisp2 = theta_E_iters / d_AL / 4 / pi * c**2 * d_AS / d_ALS
             vdisp[targ] = np.mean(np.sqrt(vdisp2) / 1e5)

### 2015-07-19 Code/NumRun.py

@@ -10,11 +10,11 @@ SMG.M_gas()
 SFR_IR = SMG.SFRFunc(SMG.LIR)
 SFR_FIR = SMG.SFRFunc(SMG.LFIR)
 SFE_IR = SMG.SFEFunc(SMG.LIR)
-SFE_FIR = SMG.SFEFunc(SMG.LFIR)
+# SFE_FIR = SMG.SFEFunc(SMG.LFIR)
 t_IR = SMG.depleTime_Gas(SFR_IR)
-t_FIR = SMG.depleTime_Gas(SFR_FIR)
-q_IR, Lradio = SMG.qFactor_normL(SMG.LIR)
-q_FIR, Lradio = SMG.qFactor_normL(SMG.LFIR)
+# t_FIR = SMG.depleTime_Gas(SFR_FIR)
+# q_IR, Lradio = SMG.qFactor_normL(SMG.LIR)
+# q_FIR, Lradio = SMG.qFactor_normL(SMG.LFIR)
 gas_dust = SMG.f_gas_dust()
 M_dyn = SMG.Mdyn()
 f_gas_dyn = SMG.f_molGas_dyn()
@@ -22,25 +22,25 @@ print SMG
 print "SFR using LIR: {:.2f} [M_sun/yr]".format(SFR_IR)
 print "SFR using LFIR: {:.2f} [M_sun/yr]".format(SFR_FIR)
 print "SFE using LIR: {:.2f}".format(SFE_IR)
-print "SFE using LFIR: {:.2f}".format(SFE_FIR)
+# print "SFE using LFIR: {:.2f}".format(SFE_FIR)
 print "depletion Time using IR {:.2f} Myr".format(t_IR/1e6)
-print "Depletion Time using FIR {:.2f} Myr".format(t_FIR/1e6)
-print "rest frame 1.4 GHz Luminosity: {:.2f} [W/Hz]".format(Lradio)
-print "q correlation using IR: {:.2f}".format(q_IR)
-print "q correlation using FIR: {:.2f}".format(q_FIR)
+# print "Depletion Time using FIR {:.2f} Myr".format(t_FIR/1e6)
+# print "rest frame 1.4 GHz Luminosity: {:.2f} [W/Hz]".format(Lradio)
+# print "q correlation using IR: {:.2f}".format(q_IR)
+# print "q correlation using FIR: {:.2f}".format(q_FIR)
 print "gas_dust fraction: {:.2f}".format(gas_dust)
[…]

### 2015-07-19 Code/err.py
recompute using new I_err = 1.345 Jy km/s; changed because this is pretty version

@@ -2,7 +2,7 @@ freq_CO32 = 345.651     # GHz
 dl = 19052          # Mpc at 2.221
 z = 2.221
 I_line = 10.7
-del_I = 2.12   # sigma of CO(3-2) line intensity Jy km/s
+del_I = 1.345   # sigma of CO(3-2) line intensity Jy km/s
 mu = 10.1298
 del_mu = 1.38
 alpha = 0.8

### 2015-07-19 skeleton.tex
Need to finish discussion and appendix

@@
 of the cold gas and dust in the interstellar medium (ISM) of the background SMG which hosts a type-2 quasar, as well as on the spectral energy distribution (SED) of the foreground radio galaxy using the marginally resolved continuum
-emission detected at an integrated flux density of $S_\nu$\,=\,7.5\,$\pm$\,1.3 mJy
+emission detected at an integrated flux density of $S_\nu$\,=\,9.5\,$\pm$\,0.6 mJy
  at 104 GHz.
 We measure a velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$\,=\,(10.7\,$\pm$\,1.3)\,Jy\,km\,s\pmOne,
-corresponding to a lensing- and excitation-corrected CO line luminosity of \Lp\,=\,(2.9\,$\pm$\,0.8)\,$\times$\,10$^{10}$\,(10.1/$\mu_{\rm L}$)\,\LpU, where $\mu_{\rm L}$ is the lensing magnification factor inferred from our lens modeling of the 1\,mm continuum emission.
+corresponding to a lensing- and excitation-corrected CO line luminosity of \Lp\,=\,(2.9\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,(10.1/$\mu_{\rm L}$)\,\LpU, where $\mu_{\rm L}$ is the lensing magnification factor inferred from our lens modeling of the 1\,mm continuum emission.
  This
-translates to a molecular gas mass of $M_{\rm gas}$\,=\,(2.3\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,\Msun. We 
+translates to a molecular gas mass of $M_{\rm gas}$\,=\,(2.3\,$\pm$\,0.5)\,$\times$\,10$^{10}$\,\Msun. We 
 fit optically thick and optically thin modified blackbody models to the SED of the SMG.
@@
 averaging over all line-free channels, this yields a synthesized clean beam size of 11\farcs9\,$\times$\,6\farcs5, at a position angle of $-$55.9$\degr$ east of north and an 
-rms noise of 0.51\,\,mJy\,\,beam\pmOne.
+rms noise of 0.49\,\,mJy\,\,beam\pmOne.
 
@@
 We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission.
-The deconvolved source size is (10\farcs9\,$\pm$\,4\farcs0)\,$\times$\,(3\farcs4\,$\pm$\,2\farcs1), and the integrated flux density is 7.50\,$\pm$\,1.30\,\,mJy.
-At the peak position of the continuum emission, the peak flux density is S$_\nu$\,=\,4.91\,$\pm$\,0.54\,\,mJy\,\,beam\pmOne.
+The deconvolved source size is (10\farcs2\,$\pm$\,1\farcs4)\,$\times$\,(6\farcs1\,$\pm$\,0\farcs7), and the integrated flux density is 9.46\,$\pm$\,0.64\,\,mJy.
+At the peak position of the continuum emission, the peak flux density is S$_\nu$\,=\,5.18\,$\pm$\,0.24\,\,mJy\,\,beam\pmOne.
 An overlay image of the 104 GHz continuum emission on the 9 GHz continuum measurement (H14) is shown in Figure \ref{fig:cont}.
@@
 the redshifted frequencies of 105.86, 107.71, and 108.79\,\,GHz, respectively. We establish 3$\sigma$ upper limits employing a typical line width of 
-$\sim$\,300\,\,km\,\,s\pmOne, based on the CO($J$\,=\,1\,$\rightarrow$\,0) line measurement in the sample of local radio galaxies \citep[$z$ $<$ 0.1; ][]{Smolcic11a}, resulting in 3$\sigma$ of 7.839\,\,Jy\,\,km\,\,s\pmOne.\\ \\
+$\sim$\,300\,\,km\,\,s\pmOne, based on the CO($J$\,=\,1\,$\rightarrow$\,0) line measurements in the sample of local radio galaxies \citep[$z$ $<$ 0.1; ][]{Smolcic11a}, resulting in 3$\sigma$ of 7.84\,\,Jy\,\,km\,\,s\pmOne.\\ \\
 Question for DR: 3sigma using FWHM or total line width (FWZI?)
@@
 Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.83\,$\pm$\,2.68\,\,mJy, superimposed on a continuum level of 4.19\,$\pm$\,0.49\,\,mJy, and full width at half-maximum (FWHM) of 557\,$\pm$\,36\,\,km\,\,s\pmOne.
-We construct a velocity-integrated (0th moment) map of the \CO 
+We construct a velocity-integrated (0th moment) map of the \CO line 
 emission from the data after subtracting continuum emission in the visibility plane.
@@
 This has been observed in a FR-II galaxy at a similar redshift\,--\,3C220.1 at the redshift of $z$\,=\,0.610, where observations were carried out at observed-frame $\sim$\,90 GHz \citep{Hardcastle08a}.
-It is noteworthy that prior to our observations, 3C220.1 was the only FR-II galaxy with high frequency observations at $z$\,$>$\,0.6.
+It is noteworthy that prior to our observations, 3C220.1 was the only FR-II galaxy with high frequency radio observations at $z$\,$>$\,0.6.
 Previous studies of the core component of 3C220.3 have established upper
 limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a} and an unambiguous detection of 0.8 mJy at 9 GHz (H14), suggesting a substantially inverted spectrum of the core (Figure \ref{fig:SED}).
-Consequently, we may naively expect the integrated flux density in our continuum detection of $S_{\rm 104GHz}$\,=\,7.50\,$\pm$\,1.30\,\,mJy to be dominated by the unresolved core component of the foreground FR-II galaxy, which is at $z$\,=\,0.685.
-However, the inferred deconvolved spatial size of the source matching that in the resolved image (see Figure 1) is 
+Consequently, we may naively expect the integrated flux density in our continuum detection of $S_{\rm 104GHz}$\,=\,9.46\,$\pm$\,0.64\,\,mJy to be dominated by the unresolved core component of the foreground FR-II galaxy, which is at $z$\,=\,0.685.
+However, the deconvolved spatial size of the source matching that in the resolved image (see Figure 1) is 
 suggestive of a marginally resolved detection of the extended components with non-negligible emission. 
@@
 distribution. 
-The extrapolated flux density at 104\,\,GHz is consistent with the flux density of our continuum 
+The extrapolated flux density at 104\,\,GHz is consistent with the peak flux density of our continuum 
 measurement (Figure \ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests
-a dominant contribution from the lobes, and the peak flux density therefore does not appear to be emission toward 
+a dominant contribution from the lobes, and the peak flux density does not appear to be emission toward 
 the core. Moreover, the peak position of the 104\,\,GHz continuum is
@@
 across different epochs. 
-EDIT HERE \par
-From our interpretation, we place an upper limit of $S_\nu$\,$<$\,2.59 mJy on the core component using the difference.
+We place an upper limit of $S_\nu$\,$<$\,4.28 mJy on the core component using the difference in flux density.
 \par
 Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, where some exhibit spectral steepening in cm and mm wavelengths (\eg 3C123).
-At the resolution of our observations, it is unclear whether the integrated flux is dominated by the emission from the compact hotspot or the emission from the surrounding diffuse lobe components.
+At the resolution of our observations, it is unclear whether the flux density is dominated by the emission from the compact hotspot or the emission from the surrounding diffuse lobe components.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED_longticks.pdf}
+\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED2_longticks.pdf}
 \caption{The SED of 3C220.3 (solid purple line) and SMM\,J0939 (dashed purple line and solid cyan line) including the new measurements presented in this paper. 
@@
 photometric data obtained with {\it Herschel}/PACS and SPIRE, at wavelengths
-between observed-frame 70 \micron $-$ 500 \micron, and interferometric data with the SMA at 1\,mm (H14). We use the publicly
+between observed-frame 70 \micron\,$-$\,500 \micron, and the interferometric data obtained with the SMA at 1\,mm (H14). We use the publicly
 available software {\sc mbb\_emcee}\footnote{https://github.com/aconley/mbb\_emcee} to perform the SED fitting; the code uses an affine-invariant Markov chain Monte
-Carlo (MCMC) approach, and further details of the code are given by \citet{Riechers13a} and \citet{Dowell14a}. The
+Carlo (MCMC) approach, further details of the code are given by \citet{Riechers13a} and \citet{Dowell14a}. The
 functional form of the fit comprises a single-temperature, modified blackbody function joined to a $S_{\lambda} \propto \lambda^\alpha
@@
 case. In the subsequent analysis, we employ the inferred values from the optically thick model.
-The best-fit solution yields a rest-frame FIR luminosity of $L_{\rm FIR (42.5-122.5\micron)}$\,=\,53.3$^{+1.1}_{-1.1}\times$10$^{12}$\Lsun, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$\,=\,88.5$^{+2.6}_{-2.6}\times$10$
-^{12}$\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$\,=\,2.64 m$^2$ kg\pmOne\ at 125.0 $
+The best-fit solution yields a rest-frame FIR luminosity of $L_{\rm FIR (42.5-122.5\micron)}$\,=\,53.3$^{+1.1}_{-1.1}$\,$\times$\,10$^{12}$\,\Lsun, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$\,=\,88.5$^{+2.6}_{-2.6}$\,$\times$\,10$
+^{12}$\,\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$\,=\,2.64 m$^2$ kg\pmOne\ at 125.0 $
 \micron$ \citep{Dunne03a}, we derive the dust mass using the following expression:
@@
 With the limited amount of data in the FIR waveband, the dust mass is weakly constrained. 
-We perform an additional SED fitting using an optically thick model where we loosen the upper limit of $\beta$ from 2.2 to 3.0, while the difference between all best-fit parameters in this scenario and those using an upper limit of 2.2 (see Table \ref{tab:mbb}) is within 3\%, we find that the dust mass is boosted by a factor of $\sim$2.
+We perform an additional fit using an optically thick model where we loosen the upper limit of $\beta$ from 2.2 to 3.0, while the difference between all best-fit parameters in this scenario and those using an upper limit of 2.2 (see Table \ref{tab:mbb}) is within 3\%, we find that the dust mass is boosted by a factor of $\sim$2.
 
@@
 While the ground state CO transition line, CO($J$\,=\,1 \rarr\ 0) traces the cold molecular gas in the ISM
-\citep*[\eg][]{Downes98a,Wilson70a}, CO($J$ $>$ 1) transition lines are frequently observed at high redshifts as the
+\citep*[\eg][]{Wilson70a,Downes98a}, CO($J$ $>$ 1) transition lines are frequently observed at high redshifts as the
  ground state CO transition line is redshifted to lower frequencies that can only be observed with a few telescopes 
@@
 \begin{equation}
-L^{\prime}_{\rm CO}\,=\,\frac{3.25\times10^7}{\nu_{\rm CO (3-2), rest}^2}\times \frac{D_L^2}{\mu} \times
+L^{\prime}_{\rm CO}\,=\,\frac{3.25\times10^7}{\nu_{\rm CO (3-2)}^2}\times \frac{D_L^2}{\mu} \times
 \frac{I_{\rm CO(3-2)}} {R_{\rm 31} (1 + z)}
 \end{equation}
-where $\nu_{\rm CO (3-2), rest}$ is the rest-frame frequency of the \CO line in GHz, $D_L$ is the luminosity distance in Mpc, and $I_{\rm CO(3-2)}$ is the \CO line flux in Jy km\,\,s\pmOne.
-This corresponds to $L^{\prime}_{\rm CO (1-0)}$\,=\,(2.91\,$\pm$\,0.78)$\times$10$^{10}$(10.1/$\mu_{\rm L}$) \LpU\ after correcting for lensing magnification; the inferred total molecular gas mass is therefore $M_{\rm gas}$\,=\,(2.33\,$\pm$\,0.62) $\times$10$^{10}$\Msun.
-We assumed a conversion factor of $\alpha_{\rm CO}$ =
-0.8 \Msun (\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
+where $\nu_{\rm CO (3-2)}$ is the rest-frame frequency of the \CO transition line in GHz, $D_L$ is the luminosity distance in Mpc, and $I_{\rm CO(3-2)}$ is the \CO line flux in Jy\,\,km\,\,s\pmOne.
+After correcting for lensing magnification, this corresponds to $L^{\prime}_{\rm CO (1-0)}$\,=\,(2.91\,$\pm$\,0.60)\,\,$\times$\,\,10$^{10}$\,(10.1/$\mu_{\rm L}$)\,\,\LpU; the inferred total molecular gas mass is therefore $M_{\rm gas}$\,=\,(2.33\,$\pm$\,0.48)\,\,$\times$\,\,10$^{10}$\,\Msun.
+We assumed a conversion factor of $\alpha_{\rm CO}$\,=\,0.8\,\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
 adopted for SMGs \citep[\eg][]{Tacconi06a,Tacconi08a,Bothwell13a}. 
 This results in a gas-to-dust
-ratio of $f_{\rm gas-dust}$\,=\,$M_{\rm gas}/M_{\rm dust}$\,=\,47\,$\pm$\,21, this is in good agreement with the 
+ratio of $f_{\rm gas-dust}$\,=\,$M_{\rm gas}/M_{\rm dust}$\,=\,47\,$\pm$\,21, in good agreement with the 
 values found in other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.
@@
 Using the \citet{Kennicutt98a} relation and assuming \citet{Chabrier03a}
-stellar initial mass (IMF) function\footnote{SFR$_{\rm FIR}$\,=\,526\,$\pm$\,72 $M_
+stellar initial mass (IMF) function\footnote{SFR$_{\rm FIR}$\,=\,526\,$\pm$\,73 $M_
 \odot$ yr\pmOne\ }, 
@@
 current SFR can be approximated as the gas depletion timescale, $\tau_{\rm depl}$\,=\,$M_{\rm gas}$/SFR. 
-This corresponds to $\tau_{\rm depl}$\,=\,25.6\,$\pm$\,0.6 Myr, which is in good agreement with that found in other SMGs \citep[\eg][]{Greve05a}.
+This corresponds to $\tau_{\rm depl}$\,=\,25.6\,$\pm$\,0.4 Myr, which is in good agreement with those found in other SMGs \citep[\eg][]{Greve05a}.
 
@@
 choice of IMF, however, this assumes that differential lensing effect between the CO and infrared emission is negligible. 
-The resulting ratio is SFE$_{\rm IR}$\,=\,300\,$\pm$\,10 \Lsun (\LpU)$^{-1}$, this is comparable
-to what is found in ``typical" SMGs \citep{Riechers11c,Tacconi06a,Greve05a}.
+The resulting ratio is SFE$_{\rm IR}$\,=\,300\,$\pm$\,9\,\,\Lsun\,(\LpU)$^{-1}$, this is comparable
+to what is found in ``typical" SMGs \citep{Riechers11c,Greve05a,Tacconi06a}.
 
@@
 where $\Delta v_{\rm line}$ is in km\,\,s\pmOne, $R_{\rm eff}$ is in kpc, and $M_{\rm dyn}$ is in \Msun.
-We employ the FWHM linewidth of the \CO line for $\Delta v_{\rm line}$,
+We employ the FWHM linewidth of the \CO line profile for $\Delta v_{\rm line}$,
 and the half-light radius from our lens model for $R_{\rm eff}$, this assumes that the dust emission traces the same emitting region as the CO.
-The inferred dynamical mass is $M_{\rm dyn}$\,=\,(7.4\,$\pm$\,2.4)\,$\times$\,10$^{10}$\Msun, and the gas-to-dynamical mass fraction is $f_{\rm gas-to-dyn}$\,=\,0.32\,$\pm$\,0.14, this is consistent with that of other SMGs \citep{Tacconi06a}.
+The inferred dynamical mass is $M_{\rm dyn}$\,=\,(7.4\,$\pm$\,2.4)\,$\times$\,10$^{10}$\,\Msun, and the gas-to-dynamical mass fraction is $f_{\rm gas-to-dyn}$\,=\,0.32\,$\pm$\,0.12, this is consistent with that of other SMGs \citep{Tacconi06a}.
 
 \subsection{Star Formation and Gas Surface Densities}
-To compute surface densities, we divided half the inferred SFR and gas mass by the area subtended by the half-light 
+To compute surface densities, we divide half the inferred SFR and gas mass by the area subtended by the half-light 
 radius, resulting in $\Sigma_{\rm gas}$\,=\,4.67\,$\times$\,10$^9$\,\,\Msun\,\,kpc$^{-2}$ and $\Sigma_{\rm SF}$\,=\,175.20\,\,\Msun\,\,yr\pmOne\,\,kpc$^{-2}$, in good agreement with values typical for SMGs \citep{Tacconi08a}.
@@
 The inferred surface densities of SMM\,J0939 follow a universal Schmidt-Kennicutt relation between the star formation rate
-surface density and the molecular gas surface density reported by \citet{B07a}: $\Sigma_{\rm SF}$\,=\,9.3\,$\times$\,
-10$^{-5}$ ($M_{\rm gas}$/2$\pi R_{\rm 1/2}^2)^{1.71}$, which was derived using a sample consisting of high-redshift 
+surface density and the molecular gas surface density reported by \citet{B07a}: $\Sigma_{\rm SF}$\,=\,9.3\,$\times$\,10$^{-5}$ ($M_{\rm gas}$/2$\pi R_{\rm 1/2}^2)^{1.71}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
 galaxies
- and local star-forming galaxies out to $z\ \sim$ 2.5, and assuming Chabrier IMF.
+out to $z\ \sim$ 2.5, and assuming Chabrier IMF.
 
 \section{Discussion And Conclusions} \label{sec:conclusions}
-We present the detection of \CO line emission toward SMM\,J0939+8315, a strongly lensed SMG that is hosting a type-2 quasar, confirming the redshift of SMM\,J0939 with high precision at $z$\,=\,2.22122\,$\pm$\,0.00007.
-The peculiarity of this system allows us to put constraints on the SED of 3C220.3 using the underlying continuum detection at $\sim$104 GHz, we argue that the result is suggestive of a dominant contribution from the lobes and hotspots.
-%% ok up
+We present the detection of \CO line emission toward SMM\,J0939+8315, a strongly lensed SMG that is hosting a type-2 quasar, refining the redshift of this SMG to $z$\,=\,2.22122\,$\pm$\,0.00007.
+The peculiarity of this system allows us to put constraints on the SED of 3C220.3 using the underlying continuum detection at $\sim$104 GHz, making this the second high frequency radio continuum measurement of FR-II galaxy at $z$ $>$ 0.6.
+We argue that the detected peak continuum emission is dominated by the emission from the lobes and hotspots, we therefore place an upper limit of $S_\nu$ $<$ 4.28 mJy on the radio core.
 
-The detection of CO with CO luminosity of \Lp\,=\,blah \LpU\ in SMM\,J0939 implies the presence of a large molecular gas reservoir, demonstrating the active star formation in 
-this SMG with SFR $\sim$ 874 \Msun\ yr\pmOne. Our findings are typical for SMGs, which supports the picture that SMGs are a 
+The detection of CO in SMM\,J0939 
+implies a CO luminosity of \Lp\,=\,2.91\,$\pm$\,0.60\,$\times$\,10$^{10}$(10.1/$\mu_{\rm L}$)\,\,\LpU\, suggesting the presence of a large molecular gas reservoir; the inferred high SFR of $\sim$ 874 \Msun\ yr\pmOne
+ SMM\,J0939 is undergoing 
+active star formation, which is typical for SMGs, 
+which supports the picture that SMGs are a 
 population of high-z galaxies that spawn most of the stellar mass in the early universe, thus play an important role 
@@
 
+Lensing prbes the brightess apparent 
+Regardless of lensing, the inferred intrinsic properties of SMM\,J0939 shows that this SMG is representation of the population.
 \input{table_compareSMG}
@@
 \acknowledgments
-
+We thank Shane Bussmann for providing the code {\sc uvmcmcfit} for lens modeling, and useful discussion; Alex Conley for providing the code {\sc mbb\_emcee} for SED fitting.
 We acknowledge the WENSS team for providing the radio measurements for 3C220.3.
-We thank Shane Bussmann for providing {\sc uvmcmcfit} for lens modeling and useful discussion, and Alex Conley for providing {\sc mbb\_emcee} for SED fitting.
 Facilities: \facility{CARMA}

### 2015-07-21 skeleton.tex
compare type-2 qso onwards

@@
 \newcommand{\CO}{\mbox{CO($J$\,=\,3\,$\rightarrow$\,2) }}
-\newcommand{\Lp}{\mbox{$L^{\prime}_{\rm CO(1-0)}$}}
+\newcommand{\Lp}{\mbox{$L^{\prime}_\textrm{CO(1-0)}$}}
 \newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
+%\newcommand{\eg}{{\sl e.g.,}}
 \newcommand{\eg}{{\sl e.g.,~}}
@@
 \begin{abstract}
-We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy\,(SMG) SMM\,J0939+8315 at $z$\,=\,2.2212\,$\pm$\,0.0001, using  
+We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy\,(SMG) SMM\,J0939+8315 at $z$\,=\,2.2212\,$\pm$\,0.001, using  
 the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
@@
  at 104 GHz.
-We measure a velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$\,=\,(10.7\,$\pm$\,1.3)\,Jy\,km\,s\pmOne,
-corresponding to a lensing- and excitation-corrected CO line luminosity of \Lp\,=\,(2.9\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,(10.1/$\mu_{\rm L}$)\,\LpU, where $\mu_{\rm L}$ is the lensing magnification factor inferred from our lens modeling of the 1\,mm continuum emission.
+We measure a velocity-integrated \CO line intensity of $I_\textrm{CO(3-2)}$\,=\,(10.7\,$\pm$\,1.3)\,Jy\,km\,s\pmOne,
+corresponding to a lensing- and excitation-corrected CO line luminosity of \Lp\,=\,(2.9\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling of the 1\,mm continuum emission.
  This
-translates to a molecular gas mass of $M_{\rm gas}$\,=\,(2.3\,$\pm$\,0.5)\,$\times$\,10$^{10}$\,\Msun. We 
+translates to a molecular gas mass of $M_\textrm{gas}$\,=\,(2.3\,$\pm$\,0.5)\,$\times$\,10$^{10}$\,\Msun. We 
 fit optically thick and optically thin modified blackbody models to the SED of the SMG.
-The preferred optically thick model yields a characteristic dust temperature of $T_{\rm dust}$\,=\,63.1$^{+1.1}_{-1.3}$\,K in the rest-frame, a dust mass of $M_{\rm dust}$\,=\,(5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,\Msun, and a total infrared (IR) luminosity of $L_{\rm IR}$\,=\,(9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,\Lsun, after correcting for lensing magnification.
+The preferred optically thick model yields a characteristic dust temperature of $T_\textrm{dust}$\,=\,63.1$^{+1.1}_{-1.3}$\,K in the rest-frame, a dust mass of $M_\textrm{dust}$\,=\,(5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,\Msun, and a total infrared (IR) luminosity of $L_\textrm{IR}$\,=\,(9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,\Lsun, after correcting for lensing magnification.
 We conclude that the intrinsics properties (\eg gas mass, gas mass
@@
 J0939+8315 based on our \CO observations is similar to other high redshift
-SMGs. 
+SMGs. \\
+***Will revise after completing the discussion section.***
 \end{abstract}
@@
 \section{Introduction}\label{sec:intro}
-Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1$-$3, during the epoch of stellar mass and 
+Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1\,--\,3, during the epoch of stellar mass and 
 galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}. 
@@
 rest-frame far-infrared (FIR) wavelengths \citep{blain02a}. 
-In the past $\sim$5\,\,years, considerable amounts of effort have been invested into follow-up observations of SMGs that were 
+In the past $\sim$5~years, considerable amounts of effort have been invested into follow-up observations of SMGs that were 
 discovered in large sky surveys \citep[\eg H-ATLAS, HerMES; ][]{Eales10a,Oliver12a}, conducted using (sub)-mm facilities.
@@
   To characterize the physical properties of the gas reservoirs in the ISM where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[See \eg][]{Carilli13a}.
-Recent observations of CO in SMGs at $z$\,$\sim$\,1$-$3 have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Riechers11c,Riechers11d,Ivison11a,Bothwell13a}.
+Recent observations of CO in SMGs at $z$\,$\sim$\,1\,--\,3 have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Riechers11c,Riechers11d,Ivison11a,Bothwell13a}.
 
@@
 A particularly interesting, peculiar submm-bright lensing system discovered serendipitously  
-consists of a type-2 quasar host SMG -- SMM\,J0939+8315 (hereafter SMM\,J0939), lensed by the double-lobed Fanaroff-Riley 
+consists of a type-2 quasar host SMG --- SMM\,J0939+8315 (hereafter SMM\,J0939), lensed by the double-lobed Fanaroff-Riley 
 Class II \citep*[FR-II; ][]{Fanaroff74} radio galaxy 3C220.3 and its
@@
 SMM\,J0939 is currently one of the brightest known lensed
-SMGs, with a lensing-magnified flux density of $S_{\rm 250\mu m}$\,=\,440\,$\pm$\,15 mJy. 
+SMGs, with a lensing-magnified flux density of $S_\textrm{250\micron m}$\,=\,440\,$\pm$\,15 mJy. 
 Previous detections of CIV\,1459\AA\
  and HeII\,1640\AA\ line emission toward SMM\,J0939 
- place the redshift of this galaxy at $z$\,=\,2.221, and suggest the presence of a type-2 quasar,  
+ placed this galaxy at $z$\,=\,2.221, and suggested the presence of a type-2 quasar,  
 indicating active galactic nucleus activity in this SMG \citep[hereafter H14]{Haas14}.
@@
 
-We adopt a standard $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km\,\,Mpc\pmOne\,\,s\pmOne, $\Omega_{\rm M}$\,=\,0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
+We adopt a standard $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km\,\,Mpc\pmOne\,\,s\pmOne, $\Omega_\textrm{M}$\,=\,0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
 The luminosity distances at $z$\,=\,0.685 and $z$\,=\,2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
@@
 \subsection{CARMA} \label{sec:carmadata}
-Observations of the \CO rotational transition ($\nu_{\rm rest}$\,=\,345.7959899 GHz) toward the background galaxy SMM
+Observations of the \CO rotational transition ($\nu_\textrm{rest}$\,=\,345.7959899 GHz) toward the background galaxy SMM
 J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; P.I.: Riechers).
@@
 The line was placed in the
-upper sideband, with the local oscillator tuned to $\nu_{\rm LO}$\,$\sim$104.2609 GHz.
+upper sideband, with the local oscillator tuned to $\nu_\textrm{LO}$\,$\sim$104.2609 GHz.
 Observations were carried out under good
@@
 This yields a synthesized clean beam size of 11$\farcs$3\,$\times$\,6\farcs1, at a position angle of $-$56.1$\degr$ east of north for the upper sideband image cube.
-The rms noise of the data prior to continuum subtraction is $\sigma_{\rm ch}$\,=\,8.75\,\,mJy\,\,beam\pmOne\ per bin 
+The rms noise of the data prior to continuum subtraction is $\sigma_\textrm{ch}$\,=\,8.75\,\,mJy\,\,beam\pmOne\ per bin 
 with a channel width of $\sim$29 km\,\,s\pmOne
 % spectra
-, whereas the final rms noise of the continuum subtracted data is $\sigma_{\rm ch}$\,=\,8.71\,\,mJy\,\,beam\pmOne\ per bin with 
+, whereas the final rms noise of the continuum subtracted data is $\sigma_\textrm{ch}$\,=\,8.71\,\,mJy\,\,beam\pmOne\ per bin with 
 the same channel width, and $\sigma$\,=\,1.00\,Jy\,\,km\,\,s\pmOne\,\,$\rm beam^{-1}$ over a channel 
@@
 At the peak position of the continuum emission, the peak flux density is S$_\nu$\,=\,5.18\,$\pm$\,0.24\,\,mJy\,\,beam\pmOne.
-An overlay image of the 104 GHz continuum emission on the 9 GHz continuum measurement (H14) is shown in Figure \ref{fig:cont}.
+An overlay image of the 104 GHz continuum emission on the 9 GHz continuum measurement (H14) is shown in Figure~\ref{fig:cont}.
 This demonstrates that at the resolution of our observations, the continuum emission is marginally resolved.
@@
 
-The frequency range of our observations covers the HCO$^+$(2$-$1), HNC($J$\,=\,2\,$\rightarrow$\,1), and H$_2$O(3$_{13}$\,$-$\,2$_{20}$) 
+The frequency range of our observations covers the HCO$^+$(2\,\rarr\,1), HNC($J$\,=\,2\,$\rightarrow$\,1), and H$_2$O(3$_{13}$\,\rarr\,2$_{20}$) 
 transition line emission in the foreground galaxy, at 
-the redshifted frequencies of 105.86, 107.71, and 108.79\,\,GHz, respectively. We establish 3$\sigma$ upper limits employing a typical line width of 
-$\sim$\,300\,\,km\,\,s\pmOne, based on the CO($J$\,=\,1\,$\rightarrow$\,0) line measurements in the sample of local radio galaxies \citep[$z$ $<$ 0.1; ][]{Smolcic11a}, resulting in 3$\sigma$ of 7.84\,\,Jy\,\,km\,\,s\pmOne.\\ \\
-Question for DR: 3sigma using FWHM or total line width (FWZI?)
+the redshifted frequencies of 105.86, 107.71, and 108.79\,\,GHz, respectively. We establish 3$\sigma$ upper limits employing a typical FWHM line width of 
+$\sim$\,300\,\,km\,\,s\pmOne, based on the CO($J$\,=\,1\,$\rightarrow$\,0) line measurements in a sample of local radio galaxies \citep[$z$ $<$ 0.1; ][]{Smolcic11a}, resulting in 3$\sigma$ of 2.44\,\,Jy\,\,km\,\,s\pmOne.
 
@@
 \subsection{New Results: SMM\,J0939\\ \CO Line Emission}
-We detect \CO line emission at $\sim$10(?yes?no?)$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
-The spatial extent of this SMG is $\sim$5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum in Figure \ref{fig:mom0}; as such, the detected \CO line emission is spatially unresolved.
-The line profile in Figure \ref{fig:mom0} is therefore extracted at the peak position of the unresolved CO emission.
-Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.83\,$\pm$\,2.68\,\,mJy, superimposed on a continuum level of 4.19\,$\pm$\,0.49\,\,mJy, and full width at half-maximum (FWHM) of 557\,$\pm$\,36\,\,km\,\,s\pmOne.
+We detect \CO line emission at $\sim$8$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
+The spatial extent of this SMG is $\sim$5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum in Figure~\ref{fig:mom0}; as such, the detected \CO line emission is spatially unresolved.
+The line profile in Figure~\ref{fig:mom0} is therefore extracted at the peak position of the unresolved CO emission.
+Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.83\,$\pm$\,2.68\,\,mJy, superimposed on a continuum level of 4.19\,$\pm$\,0.49\,\,mJy, and a full width at half-maximum (FWHM) line width of 557\,$\pm$\,36\,\,km\,\,s\pmOne.
 We construct a velocity-integrated (0th moment) map of the \CO line 
 emission from the data after subtracting continuum emission in the visibility plane.
-This results in a velocity-integrated \CO line flux of $S_{\rm CO}$\,=\,10.7\,$\pm$\,1.3 Jy km\,\,s\pmOne\ over the FWZI velocity range of $\Delta v\sim$\,914 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration uncertainty.
+This results in a velocity-integrated \CO line flux of $S_\textrm{CO}$\,=\,10.7\,$\pm$\,1.3 Jy km\,\,s\pmOne\ over the FWZI velocity range of $\Delta v\sim$\,914 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration uncertainty.
 We ignore primary beam correction given that the source is close to the phase center and is unresolved (\ie much smaller than the primary beam size).
-Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.22122\,$\pm$\,0.00007.
+Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.2212\,$\pm$\,0.0010.
 
@@
 The angular resolution is 11$\farcs$3\,$\times$\,6\farcs1, at P.A.\,=\,$-$56\degr, as indicated in the bottom left corner.
-Top Right: Contours of the \CO line emission (red) overlaid on the SMA 1\,mm dust continuum (green contours and grayscale; H14) with $\sigma_{\rm 1\,mm}$\,=\,0.84 mJy beam\pmOne.
+Top Right: Contours of the \CO line emission (red) overlaid on the SMA 1\,mm dust continuum (green contours and grayscale; H14) with $\sigma_\textrm{1\,mm}$\,=\,0.84 mJy beam\pmOne.
 The beam size of the SMA data is 1\farcs4$ \times $1\farcs2, P.A.
@@
 in the bottom left corner. 
-The central cross on each image corresponds to the same coordinates as in Figure \ref{fig:cont}. The contour levels start at $\pm$3$\sigma$, incrementing at
+The central cross on each image corresponds to the same coordinates as in Figure~\ref{fig:cont}. The contour levels start at $\pm$3$\sigma$, incrementing at
 steps of $\pm$1$\sigma$. 
 Bottom: 
-Spectrum extracted at the peak position of CO line emission, with a spectral resolution of $\Delta v$ $\sim$29 km\,\,s\pmOne\, and an rms of $\sigma_{\rm ch}$\,=\,8.75 mJy beam\pmOne\ per channel.
+Spectrum extracted at the peak position of CO line emission, with a spectral resolution of $\Delta v$ $\sim$29 km\,\,s\pmOne\, and an rms of $\sigma_\textrm{ch}$\,=\,8.75 mJy beam\pmOne\ per channel.
 Solid black line shows the Gaussian fit to the \CO line profile. Yellow histogram shows the 
@@
 
-We fix the phase center to coordinates ($\alpha$,\,$\delta$)\,\,(J2000)\,=\,(9:39:23.54,\,\,83:15:26.10), the
+We fix the phase center to coordinates ($\alpha$,\,$\delta$)\,\,(J2000)\,=\,(9:39:23.54,\,\,83:15:26.10), where the
 angular offsets of the lenses and source are referenced to this phase center. The primary lens (3C220.3) is
@@
 the chosen phase center in the image ($\Delta \alpha_{\rm
-lens0}$ and $\Delta \delta_{\rm lens0}$), the angular Einstein radius ($\theta_{\rm E0}$), the
-axial ratio ($q_{\rm lens0}$), and the position angle ($\phi_{\rm lens0}$). The secondary lens (companion B) is
-described by three free parameters: $\theta_{\rm E1}$, $q_{\rm lens1}$, and $\phi_{\rm lens1}$. The angular offset
+lens0}$ and $\Delta \delta_\textrm{lens0}$), the angular Einstein radius ($\theta_\textrm{E0}$), the
+axial ratio ($q_\textrm{lens0}$), and the position angle ($\phi_\textrm{lens0}$). The secondary lens (companion B) is
+described by three free parameters: $\theta_\textrm{E1}$, $q_\textrm{lens1}$, and $\phi_\textrm{lens1}$. The angular offset
 of the secondary
-lens is sampled with respect to ($\Delta \alpha_{\rm lens0}$ and $\Delta \delta_{\rm lens0}$) of
+lens is sampled with respect to ($\Delta \alpha_\textrm{lens0}$ and $\Delta \delta_\textrm{lens0}$) of
 the primary lens.
@@
 six free parameters: the position of the source relative to the
-primary lens ($\Delta \alpha_{\rm s}$ and $\Delta
-\delta_{\rm s}$), the total intrinsic flux density ($S_\nu$), the
-effective radius ($r_{\rm s}\,=\,\sqrt{a_{\rm s} b_{\rm s}}$), the axial
-ratio ($q_{\rm s}$\,=\, $b_{\rm s}/a_{\rm s}$), and the position angle
-($\phi_{\rm s}$).
-The total number of free parameters is $N_{\rm free}$\,=\,14. The best-fit model is obtained by maximizing the
+primary lens ($\Delta \alpha_\textrm{s}$ and $\Delta
+\delta_\textrm{s}$), the total intrinsic flux density ($S_\nu$), the
+effective radius ($r_\textrm{s}\,=\,\sqrt{a_\textrm{s} b_\textrm{s}}$), the axial
+ratio ($q_\textrm{s}$\,=\, $b_\textrm{s}/a_\textrm{s}$), and the position angle
+($\phi_\textrm{s}$).
+The total number of free parameters is $N_\textrm{free}$\,=\,14. The best-fit model is obtained by maximizing the
 Gaussian likelihood function $ \mathcal{L} $ according to:
 \begin{equation}
-    \mathcal{L}\,=\,\sum_{u, v}\left( \frac{|V_{\rm data} - V_{\rm
+    \mathcal{L}\,=\,\sum_{u, v}\left( \frac{|V_\textrm{data} - V_{\rm
     model}|^2}{\sigma^2} + {\rm log}(2 \pi \sigma^2) \right)
@@
 these parameters, we impose a uniform prior in the range $\in\pm$3$\sigma$, where $\sigma$ is the uncertainty
-reported in their paper. The axial ratios of the lenses are restricted to $q_{\rm lens} > 0.3$. We initialize 512
+reported in their paper. The axial ratios of the lenses are restricted to $q_\textrm{lens} > 0.3$. We initialize 512
 walkers and 6000 steps to identify the best-fit model parameters.
@@
 Our best-fit model yields a magnification
-factor of $\mu_{\rm L}$\,=\,10.13\,$\pm$\,1.38, this is consistent the value reported by H14 within the errors. All best-fit
+factor of $\mu_\textrm{L}$\,=\,10.13\,$\pm$\,1.38, this is consistent the value reported by H14 within the errors. All best-fit
 parameters are listed in Table \ref{tab:lensParam}.
 The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$\,=\,1.22\,$\pm$\,0.01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$\,=\,0.75\,$\pm$\,0.02 (5.34 kpc at $z$\,=\,0.685),
-the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_{\rm E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_{\rm E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
+the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
 \input{table_lensParams}
@@
 and dominates the flux density at higher frequencies \citep{Kellermann81a,Begelman84a}.
-This has been observed in a FR-II galaxy at a similar redshift\,--\,3C220.1 at the redshift of $z$\,=\,0.610, where observations were carried out at observed-frame $\sim$\,90 GHz \citep{Hardcastle08a}.
-It is noteworthy that prior to our observations, 3C220.1 was the only FR-II galaxy with high frequency radio observations at $z$\,$>$\,0.6.
+This has been observed in a FR-II galaxy at  similar redshift\,--\,3C220.1 at the redshift of $z$\,=\,0.610, where observations were carried out at observed-frame $\sim$\,90 GHz \citep{Hardcastle08a}.
+%It is noteworthy that prior to our observations, 3C220.1 was the only FR-II galaxy with high frequency radio observations at $z$\,$>$\,0.6.
+
 Previous studies of the core component of 3C220.3 have established upper 
-limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a} and an unambiguous detection of 0.8 mJy at 9 GHz (H14), suggesting a substantially inverted spectrum of the core (Figure \ref{fig:SED}).
-Consequently, we may naively expect the integrated flux density in our continuum detection of $S_{\rm 104GHz}$\,=\,9.46\,$\pm$\,0.64\,\,mJy to be dominated by the unresolved core component of the foreground FR-II galaxy, which is at $z$\,=\,0.685.
+limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a} and an unambiguous detection of 0.8 mJy at 9 GHz (H14), suggesting a substantially inverted spectrum of the core (Figure~\ref{fig:SED}).
+Consequently, we may naively expect the integrated flux density in our continuum detection of $S_\textrm{104GHz}$\,=\,9.46\,$\pm$\,0.64\,\,mJy to be dominated by the unresolved core component of the foreground FR-II galaxy, which is at $z$\,=\,0.685.
 However, the deconvolved spatial size of the source matching that in the resolved image (see Figure 1) is 
@@
 axis along the 
-lobes of the radio galaxy, as shown in Figure \ref{fig:cont}. We investigate this disparity by fitting models to 
+lobes of the radio galaxy, as shown in Figure~\ref{fig:cont}. We investigate this disparity by fitting models to 
 existing SED data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to 
@@
 The extrapolated flux density at 104\,\,GHz is consistent with the peak flux density of our continuum 
-measurement (Figure \ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests
+measurement (Figure~\ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests
 a dominant contribution from the lobes, and the peak flux density does not appear to be emission toward 
 the core. Moreover, the peak position of the 104\,\,GHz continuum is
-centered toward the northern lobe (Figure \ref{fig:cont}), which further supports our argument. We did not 
+centered toward the northern lobe (Figure~\ref{fig:cont}), which further supports our argument. We did not 
 extrapolate the core measurements to the frequency of our continuum, as previous measurements of the core are 
@@
 across different epochs. 
-We place an upper limit of $S_\nu$\,$<$\,4.28 mJy on the core component using the difference in flux density.
+We place an upper limit of $S_\nu$\,$<$\,4.28 mJy on the core component using the difference between the integrated and the peak flux densities.
 \par
@@
 case. In the subsequent analysis, we employ the inferred values from the optically thick model.
-The best-fit solution yields a rest-frame FIR luminosity of $L_{\rm FIR (42.5-122.5\micron)}$\,=\,53.3$^{+1.1}_{-1.1}$\,$\times$\,10$^{12}$\,\Lsun, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$\,=\,88.5$^{+2.6}_{-2.6}$\,$\times$\,10$
+The best-fit solution yields a rest-frame FIR luminosity of $L_\textrm{FIR (42.5-122.5\micron)}$\,=\,53.3$^{+1.1}_{-1.1}$\,$\times$\,10$^{12}$\,\Lsun, and a total infrared (IR) luminosity of $L_\textrm{IR (8-1000 \micron)}$\,=\,88.5$^{+2.6}_{-2.6}$\,$\times$\,10$
 ^{12}$\,\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$\,=\,2.64 m$^2$ kg\pmOne\ at 125.0 $
@@
 \begin{equation}
-M_{\rm dust}\,=\,S_{\nu} D_{L}^2 [(1 + z) \kappa_{\nu} B_{\nu}]^{-1} \tau_{\nu} [1-
+M_\textrm{dust}\,=\,S_{\nu} D_{L}^2 [(1 + z) \kappa_{\nu} B_{\nu}]^{-1} \tau_{\nu} [1-
 \exp(-\tau_{\nu})]^{-1}
 \end{equation}
-where $S_{\nu}$ is the flux density in ergs/s/cm$^{2}$/Hz , $D_{\rm L}$ is the luminosity distance in cm, $\kappa_{\nu}$ is the dust
+where $S_{\nu}$ is the flux density in ergs/s/cm$^{2}$/Hz , $D_\textrm{L}$ is the luminosity distance in cm, $\kappa_{\nu}$ is the dust
 absorption coefficient in cm$^2$ g\pmOne, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function,
 all quantities are expressed in the observed-frame.
-We find a dust mass of $M_{\rm dust}$\,=\,50.5$^{20.4}_{-20.2}\times$10$^8$\,\,\Msun, the uncertainties do not include those of $\kappa_{\nu}$.
+We find a dust mass of $M_\textrm{dust}$\,=\,50.5$^{20.4}_{-20.2}\times$10$^8$\,\,\Msun, the uncertainties do not include those of $\kappa_{\nu}$.
 These values are based on SED fitting to the photometric data, \ie prior
@@
 \subsection{Molecular Gas Mass}
-While the ground state CO transition line, CO($J$\,=\,1 \rarr\ 0) traces the cold molecular gas in the ISM
+While the ground state CO transition line, CO($J$\,=\,1\,\rarr\,0) traces the cold molecular gas in the ISM
 \citep*[\eg][]{Wilson70a,Downes98a}, CO($J$ $>$ 1) transition lines are frequently observed at high redshifts as the
@@
  \citep{Carilli13a}, 
- hence assumptions on the CO excitation conditions are required to derive the molecular gas mass using the H$_{\rm 2}$-to-CO 
+ hence assumptions on the CO excitation conditions are required to derive the molecular gas mass using the H$_\textrm{2}$-to-CO 
  relation. 
 Prior to the observations of the ground state CO line in SMGs, it has been assumed that the molecular gas in the
-  ISM traced by CO lines is thermalized due to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
+  ISM traced by CO lines is thermalized owing to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
    Yet, recent observations of this line have demonstrated that SMGs can indeed be subthermally excited
-   \citep{Harris10a,Riechers11c,Riechers11d,Ivison11a}; based on observations toward SMGs of both the \CO and the CO($J$\,=\,1 \rarr\ 0) lines, the 
-   brightness temperature ratio has been inferred as $R_{\rm 31}<$ 0.8 \citep
+   \citep{Harris10a,Riechers11c,Riechers11d,Ivison11a}; based on observations toward SMGs of both the \CO and the CO($J$\,=\,1\,\rarr\,0) lines, the 
+   brightness temperature ratio has been inferred as $R_\textrm{31}<$ 0.8 \citep
    {Harris10a,Carilli10a,Swinbank2010a,Riechers11d,Ivison11a,Ivison10d}. In contrast, observations of high-redshift quasar hosts suggest that the ratio 
-   is $R_{\rm 31}\sim$ 1 \citep{Riechers06a, Riechers11a, Scott11a}. 
+   is $R_\textrm{31}\sim$ 1 \citep{Riechers06a, Riechers11a, Scott11a}. 
 Here, we derive the molecular gas mass 
 assuming thermalized excitation of CO, 
-\eg we adopt $R_{\rm 31}$\,=\,1 as SMM\,J0939 is 
-postulated to be hosting a type-2 quasar; this is based on the reported brightness temperature ratio of $R_{\rm 31}$\,=\,1.00\,$\pm$\,0.10 for the type-2 quasar host IRAS F10214+4724 \citep{Riechers11a}.
+\eg we adopt $R_\textrm{31}$\,=\,1 as SMM\,J0939 is 
+postulated to be hosting a type-2 quasar; this is based on the reported brightness temperature ratio of $R_\textrm{31}$\,=\,1.00\,$\pm$\,0.10 for the type-2 quasar host IRAS F10214+4724 \citep[hereafter F10214; ][]{Riechers11a}.
 \par
@@
 \begin{equation}
-L^{\prime}_{\rm CO}\,=\,\frac{3.25\times10^7}{\nu_{\rm CO (3-2)}^2}\times \frac{D_L^2}{\mu} \times
-\frac{I_{\rm CO(3-2)}} {R_{\rm 31} (1 + z)}
+L^{\prime}_\textrm{CO}\,=\,\frac{3.25\times10^7}{\nu_\textrm{CO (3-2)}^2}\times \frac{D_L^2}{\mu_\textrm{L}} \times
+\frac{I_\textrm{CO(3-2)}} {R_\textrm{31} (1 + z)}
 \end{equation}
-where $\nu_{\rm CO (3-2)}$ is the rest-frame frequency of the \CO transition line in GHz, $D_L$ is the luminosity distance in Mpc, and $I_{\rm CO(3-2)}$ is the \CO line flux in Jy\,\,km\,\,s\pmOne.
-After correcting for lensing magnification, this corresponds to $L^{\prime}_{\rm CO (1-0)}$\,=\,(2.91\,$\pm$\,0.60)\,\,$\times$\,\,10$^{10}$\,(10.1/$\mu_{\rm L}$)\,\,\LpU; the inferred total molecular gas mass is therefore $M_{\rm gas}$\,=\,(2.33\,$\pm$\,0.48)\,\,$\times$\,\,10$^{10}$\,\Msun.
-We assumed a conversion factor of $\alpha_{\rm CO}$\,=\,0.8\,\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
+where $\nu_\textrm{CO (3-2)}$ is the rest-frame frequency of the \CO transition line in GHz, $D_L$ is the luminosity distance in Mpc, $\mu_\textrm{L}$ is the lensing magnification factor, and $I_\textrm{CO(3-2)}$ is the \CO line flux in Jy\,\,km\,\,s\pmOne.
+After correcting for lensing magnification, this corresponds to $L^{\prime}_\textrm{CO (1-0)}$\,=\,(2.91\,$\pm$\,0.60)\,\,$\times$\,\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\,\LpU; the inferred total molecular gas mass is therefore $M_\textrm{gas}$\,=\,(2.33\,$\pm$\,0.48)\,\,$\times$\,\,10$^{10}$\,\Msun.
+We assumed a conversion factor of $\alpha_\textrm{CO}$\,=\,0.8\,\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
 adopted for SMGs \citep[\eg][]{Tacconi06a,Tacconi08a,Bothwell13a}. 
 This results in a gas-to-dust
-ratio of $f_{\rm gas-dust}$\,=\,$M_{\rm gas}/M_{\rm dust}$\,=\,47\,$\pm$\,21, in good agreement with the 
+ratio of $f_\textrm{gas-dust}$\,=\,$M_\textrm{gas}/M_\textrm{dust}$\,=\,47\,$\pm$\,21, in good agreement with the 
 values found in other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.
@@
 \subsection{Star Formation Rate}
-No strong evidence of a warm dust component is found in SMM\,J0939 based on the mid-IR continuum measurements (see Figure \ref{fig:SED}), hence we derive the star formation rate (SFR) assuming negligible contributions to the IR luminosity due to AGN heating.
+No strong evidence of a warm dust component is found in SMM\,J0939 based on the mid-IR continuum measurements (see Figure~\ref{fig:SED}), hence we derive the star formation rate (SFR) assuming negligible contributions to the IR luminosity due to AGN heating.
 Using the \citet{Kennicutt98a} relation and assuming \citet{Chabrier03a}
-stellar initial mass (IMF) function\footnote{SFR$_{\rm FIR}$\,=\,526\,$\pm$\,73 $M_
+stellar initial mass (IMF) function\footnote{SFR$_\textrm{FIR}$\,=\,526\,$\pm$\,73 $M_
 \odot$ yr\pmOne\ }, 
-the SFR$_{\rm IR}$ is 874\,$\pm$\,122\,\,$M\sun$\,\,yr\pmOne.
+the SFR$_\textrm{IR}$ is 874\,$\pm$\,122\,\,$M\sun$\,\,yr\pmOne.
 Assuming constant SFR, the time for which the starburst in SMM\,J0939 can be maintained at its
-current SFR can be approximated as the gas depletion timescale, $\tau_{\rm depl}$\,=\,$M_{\rm gas}$/SFR. 
-This corresponds to $\tau_{\rm depl}$\,=\,25.6\,$\pm$\,0.4 Myr, which is in good agreement with those found in other SMGs \citep[\eg][]{Greve05a}.
+current SFR can be approximated as the gas depletion timescale, $\tau_\textrm{depl}$\,=\,$M_\textrm{gas}$/SFR. 
+This corresponds to $\tau_\textrm{depl}$\,=\,25.6\,$\pm$\,0.4 Myr, which is in good agreement with that found in other SMGs \citep[\eg][]{Greve05a}.
 
@@
 The SFR per unit mass of molecular gas is commonly taken as a
-measure of the star formation efficiency, SFE\,=\,SFR/$M_{\rm gas}$. We compute this ratio using lensing-corrected IR 
-luminosity and CO luminosity, i.e., SFE\,=\,$L_{\rm IR}$/\Lp, this makes no assumptions on the CO luminosity to gas mass conversion factor ($\alpha_{\rm CO}$) as well as the 
+measure of the star formation efficiency, SFE\,=\,SFR/$M_\textrm{gas}$. We compute this ratio using lensing-corrected IR 
+luminosity and CO luminosity, i.e., SFE\,=\,$L_\textrm{IR}$/\Lp, this makes no assumptions on the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$) as well as the 
 choice of IMF, however, this assumes that differential lensing effect between the CO and infrared emission is negligible. 
-The resulting ratio is SFE$_{\rm IR}$\,=\,300\,$\pm$\,9\,\,\Lsun\,(\LpU)$^{-1}$, this is comparable
+The resulting ratio is SFE$_\textrm{IR}$\,=\,300\,$\pm$\,9\,\,\Lsun\,(\LpU)$^{-1}$, this is comparable
 to what is found in ``typical" SMGs \citep{Riechers11c,Greve05a,Tacconi06a}.
@@
 \subsection{Dynamical Mass} 
-Based on our \CO line measurement, we can estimate the dynamical mass of SMM\,J0939 using an isotropic virial estimator \citep[\eg][]{Engel10a}:
+Based on our \CO line measurement, we estimate the dynamical mass of SMM\,J0939 assuming the molecular gas is virialized, and using an isotropic virial estimator \citep[\eg][]{Engel10a}:
 \begin{equation}
-M_{\rm dyn}\,=\,2.8\times 10^5\Delta v_{\rm line}^ 2 R_{\rm eff}
+M_\textrm{dyn}\,=\,2.8\times 10^5\Delta v_\textrm{line}^ 2 R_\textrm{eff}
 \end{equation}
-where $\Delta v_{\rm line}$ is in km\,\,s\pmOne, $R_{\rm eff}$ is in kpc, and $M_{\rm dyn}$ is in \Msun.
-We employ the FWHM linewidth of the \CO line profile for $\Delta v_{\rm line}$,
-and the half-light radius from our lens model for $R_{\rm eff}$, this assumes that the dust emission traces the same emitting region as the CO.
-The inferred dynamical mass is $M_{\rm dyn}$\,=\,(7.4\,$\pm$\,2.4)\,$\times$\,10$^{10}$\,\Msun, and the gas-to-dynamical mass fraction is $f_{\rm gas-to-dyn}$\,=\,0.32\,$\pm$\,0.12, this is consistent with that of other SMGs \citep{Tacconi06a}.
+where $\Delta v_\textrm{line}$ is in km\,\,s\pmOne, $R_\textrm{eff}$ is in kpc, and $M_\textrm{dyn}$ is in \Msun.
+We employ the FWHM linewidth of the \CO line profile for $\Delta v_\textrm{line}$,
+and the half-light radius from our lens model for $R_\textrm{eff}$, this assumes that the dust emission traces the same emitting region as the CO.
+The inferred dynamical mass is $M_\textrm{dyn}$\,=\,(7.4\,$\pm$\,2.4)\,$\times$\,10$^{10}$\,\Msun, and the gas-to-dynamical mass fraction is $f_\textrm{gas-to-dyn}$\,=\,0.32\,$\pm$\,0.12, consistent with that of other SMGs \citep{Tacconi06a}.
 
@@
 To compute surface densities, we divide half the inferred SFR and gas mass by the area subtended by the half-light 
-radius, resulting in $\Sigma_{\rm gas}$\,=\,4.67\,$\times$\,10$^9$\,\,\Msun\,\,kpc$^{-2}$ and $\Sigma_{\rm SF}$\,=\,175.20\,\,\Msun\,\,yr\pmOne\,\,kpc$^{-2}$, in good agreement with values typical for SMGs \citep{Tacconi08a}.
+radius, resulting in $\Sigma_\textrm{gas}$\,=\,4.67\,$\times$\,10$^9$\,\,\Msun\,\,kpc$^{-2}$ and $\Sigma_\textrm{SF}$\,=\,175.20\,\,\Msun\,\,yr\pmOne\,\,kpc$^{-2}$, in good agreement with values typical for SMGs \citep{Tacconi08a}.
 
 The inferred surface densities of SMM\,J0939 follow a universal Schmidt-Kennicutt relation between the star formation rate
-surface density and the molecular gas surface density reported by \citet{B07a}: $\Sigma_{\rm SF}$\,=\,9.3\,$\times$\,10$^{-5}$ ($M_{\rm gas}$/2$\pi R_{\rm 1/2}^2)^{1.71}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
+surface density and the molecular gas surface density reported by \citet{B07a}: $\Sigma_\textrm{SF}$\,=\,9.3\,$\times$\,10$^{-5}$ ($M_\textrm{gas}$/2$\pi R_\textrm{1/2}^2)^{1.71}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
 galaxies
@@
 
-\section{Discussion And Conclusions} \label{sec:conclusions}
-We present the detection of \CO line emission toward SMM\,J0939+8315, a strongly lensed SMG that is hosting a type-2 quasar, refining the redshift of this SMG to $z$\,=\,2.22122\,$\pm$\,0.00007.
-The peculiarity of this system allows us to put constraints on the SED of 3C220.3 using the underlying continuum detection at $\sim$104 GHz, making this the second high frequency radio continuum measurement of FR-II galaxy at $z$ $>$ 0.6.
-We argue that the detected peak continuum emission is dominated by the emission from the lobes and hotspots, we therefore place an upper limit of $S_\nu$ $<$ 4.28 mJy on the radio core.
+\section{Discussion And Conclusions} 
+We present the detection of \CO line emission toward SMM\,J0939+8315, a strongly-lensed SMG host of a type-2 quasar, refining the redshift  
+to $z$\,=\,2.2212\,$\pm$\,0.0010. The underlying continuum is detected at high significance, where the peak flux density is most likely to be 
+dominated by emission from the lobes and hotspot of the foreground radio galaxy 3C220.3, thus an upper limit of $S_\nu$ $<$ 4.28 mJy is 
+placed on the compact core component.
 
 The detection of CO in SMM\,J0939 
-implies a CO luminosity of \Lp\,=\,2.91\,$\pm$\,0.60\,$\times$\,10$^{10}$(10.1/$\mu_{\rm L}$)\,\,\LpU\, suggesting the presence of a large molecular gas reservoir; the inferred high SFR of $\sim$ 874 \Msun\ yr\pmOne
- SMM\,J0939 is undergoing 
-active star formation, which is typical for SMGs, 
-which supports the picture that SMGs are a 
-population of high-z galaxies that spawn most of the stellar mass in the early universe, thus play an important role 
-in galaxy evolution and formation.
+implies a CO luminosity of \Lp\,=\,(2.91\,$\pm$\,0.60)\,$\times$\,10$^{10}$(10.1/$\mu_\textrm{L}$)\,\,\LpU, suggesting the presence of a massive 
+molecular gas reservoir that is fueling the star formation at a rate of $\sim$\,874\,\Msun\ yr\pmOne. We derive the SFR using the lensing 
+corrected bolometric IR luminosity, assuming the dominant IR heating mechanism is from young and massive stars, and ignoring contribution from the 
+dust-enshrouded AGN. If star formation continues consistently at the current SFR, the gas reservoir will be depleted within $\lesssim$ 26 Myr, 
+which is consistent with the short timescale found in SMGs.
+The derived intrinsic properties of SMM\,J0399 are evident of ongoing rapid star formation, which is in good agreement with the current conjecture that SMGs are a
+population of high-redshift galaxies that build up most of the stellar mass in the early universe, thus play an important role 
+in galaxy formation and evolution.
 
-The detection of thermal dust emission in SMM\,J0939 implies a FIR Luminsoity of 
-Assuming the dominant heating mechanism is from young, massive stars, then the SFR implied from the LIR is blah
-From the IR continuum data, we expected contribution to the bolometric IR luminosity due to heating of the dust-enshrouded AGN is minor, the physical properties are therefore derived using the lensing-corrected bolometric IR luminosity.
-The high dust temperature is unusual for SMGs, but not unseen.
+\input{table_compareSMG}
+We investigate variations within the SMG population by comparing SMM\,J0939 with two other exceptionally submm-bright, 
+strongly-lensed SMGs
+found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which have been studied in great detail. The gas and dust properties 
+of these galaxies are listed in Table~\ref{tab:comapreSMG}. While the cosmic Eyelash has the least amount of molecular gas, as well as 
+the 
+longest gas depletion timescale (\ie long-lived), the overall gas and dust properties of SMM\,J0939 are between those of HLSW-01 and the 
+cosmic
+Eyelash, demonstrating the variations in gas and dust content, thus star formation activity within the population at $z$\,$\sim$\,2. 
+Gravitational 
+lensing may be accountable for such discrepancies, in particular with the cosmic Eyelash having the highest lensing magnification among the 
+three, this
+intrinsically fainter, and less gas-rich SMG is unsurprisingly bright 
+at 250\,\micron, with its CO line and IR luminosities lower than those of most SMGs studied to date. While lensing can probe the fainter 
+sources, we find that SMM\,J0939 is representative of the SMG population, with its intrinsic CO line luminosity, IR luminosity, gas mass, 
+dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in un-lensed SMGs studied to date 
+\citep{Greve05a}.
 
-Lensing prbes the brightess apparent 
-Regardless of lensing, the inferred intrinsic properties of SMM\,J0939 shows that this SMG is representation of the population.
-\input{table_compareSMG}
-We compare the properties of SMM\,J0939 with those found in strongly lensed, submm-bright galaxies at similar redshift -- HLSW-01 and the cosmic Eyelash, which have been studied in great detail.
-We list the gas and dust properties of these galaxies in Table \ref{tab:comapreSMG},
+To examine whether SMM\,J0939 is also representative of type-2 quasars at high redshifts, we compare the properties of SMM\,J0939 
+against 
+the mean values of the properties from eight CO-detected obscured AGNs at $z$ = 1.6\,--\,2.8 \citep[][and references therein]{Polletta11a}, 
+we caution that the detected CO 
+transition line varies across each source, hence inducing high systematic uncertainties in the reported values.
 
-Discussion of SMG, broad, population.
-We compare the properties of SMM\,J0939 to a type-2 quasar host -- F10214+2724, in which the molecular gas has been studied in great detail \citep{Riechers11a}.
+% Here
+All properties of J0939 are consistent with the reported (\eg FWHM of CO line, Mgas, SFR, and SFE) are consistent with the reported mean values within the uncertainties.
+
+We compare the properties of SMM\,J0939 to one of the eight type-2 quasar host --- F10214, of which the molecular gas has been studied 
+in great detail \citep{Riechers11a,Solomon05a}. We do not find evidence of low SFE in SMM J0939, our SFE, SFR, gas masses is similar to 
+that of type-1 QSO and SMGs. But F10214 also lensed, with $\mu_\textrm{L}$ = 17 (R11a), similar to cosmic eyelash, so it is plausible 
+that the low SFR,SFE, gas mass (derived using CO(4-3) is due to the intrinsically fainter weaker less gas-rich, less dusty, rather than a 
+difference between type-1 and type-2 QSO.
+We also compare values against
+
+%evolutionary phase
+H14 claim that SMMJ0939 is undergoing a violent breaking of the dust cocoon stage, together with the SFR, may support the paradigm that it is transforming / transitioning from the SMG phase to an unobscured QSO (coppin08a and references therein)
 
 Radio galaxy lensing probability.
+This system is the only known of strong galaxy-scale lensing by radio galaxy.
 
 \acknowledgments
-We thank Shane Bussmann for providing the code {\sc uvmcmcfit} for lens modeling, and useful discussion; Alex Conley for providing the code {\sc mbb\_emcee} for SED fitting.
+We thank Shane Bussmann for providing the code {\sc uvmcmcfit} for lens modeling, and helpful discussion; Alex Conley for providing the code {\sc mbb\_emcee} for SED fitting.
 We acknowledge the WENSS team for providing the radio measurements for 3C220.3.
@@
 The bolometric IR luminosity and dust mass are then derived from the set of parameter values that maximize the likelihood.
-Figure \ref{fig:sedlikelihood} shows the correlations between each pair of parameters (off-diagonal) as well as the marginalized posterior probability distribution of each parameter (diagonal) for both optically thick and optically thin models.
+Figure~\ref{fig:sedlikelihood} shows the correlations between each pair of parameters (off-diagonal) as well as the marginalized posterior probability distribution of each parameter (diagonal) for both optically thick and optically thin models.
 The set of best-fit parameters are denoted as black crosses in the 2D correlation plots, and vertical lines in the marginalized posterior probability distribution plots.
+BLAH
 

### 2015-07-31 skeleton.tex
Done, without new compilation of type2 qso tables and lensing prob

@@
-%\documentclass{emulateapj}
+%\documentclass[12pt,preprint]{aastex}
 \documentclass[twocolumn,apj,numberedappendix]{emulateapj}
@@
 \newcommand\tng{\,\tablenotemark{g}}
+\newcommand\tnh{\,\tablenotemark{h}}
+\newcommand\tni{\,\tablenotemark{i}}
+\newcommand\tnj{\,\tablenotemark{j}}
+\newcommand\tnk{\,\tablenotemark{k}}
 
@@
 \citestyle{aa}
-\shorttitle{Study of a strongly lensed type-2 quasar host SMG at $z$\,=\,2.221}
+\shorttitle{Study of a strongly-lensed type-2 quasar host SMG at $z$\,=\,2.221}
 \shortauthors{Leung \& Riechers}
@@
 \author{T. K. Daisy Leung and Dominik A. Riechers}
-\affil{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; tleung@astro.cornell.edu}
+\affil{Department of Astronomy, Space Sciences Building, Cornell University, Ithaca, NY 14853, USA; \myemail}
 
 \begin{abstract}
-We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy\,(SMG) SMM\,J0939+8315 at $z$\,=\,2.2212\,$\pm$\,0.001, using  
+We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy (SMG) SMM\,J0939+8315 at $z$ = 2.221, using  
 the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
-The SMG is lensed by the radio galaxy 3C220.3 and its companion galaxy at $z$\,=\,0.685. 
-This measurement allows us to place constraints on the intrinsic properties
-of the cold gas and dust in the interstellar medium (ISM) of the background SMG which hosts a type-2 quasar, as well as on the spectral energy distribution (SED) of the foreground radio galaxy using the marginally resolved continuum
-emission detected at an integrated flux density of $S_\nu$\,=\,9.5\,$\pm$\,0.6 mJy
- at 104 GHz.
-We measure a velocity-integrated \CO line intensity of $I_\textrm{CO(3-2)}$\,=\,(10.7\,$\pm$\,1.3)\,Jy\,km\,s\pmOne,
-corresponding to a lensing- and excitation-corrected CO line luminosity of \Lp\,=\,(2.9\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling of the 1\,mm continuum emission.
- This
-translates to a molecular gas mass of $M_\textrm{gas}$\,=\,(2.3\,$\pm$\,0.5)\,$\times$\,10$^{10}$\,\Msun. We 
-fit optically thick and optically thin modified blackbody models to the SED of the SMG.
-The preferred optically thick model yields a characteristic dust temperature of $T_\textrm{dust}$\,=\,63.1$^{+1.1}_{-1.3}$\,K in the rest-frame, a dust mass of $M_\textrm{dust}$\,=\,(5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,\Msun, and a total infrared (IR) luminosity of $L_\textrm{IR}$\,=\,(9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,\Lsun, after correcting for lensing magnification.
-We conclude that the intrinsics properties (\eg gas mass, gas mass
-fraction, star formation rate) of the molecular gas reservoir in SMM
-J0939+8315 based on our \CO observations is similar to other high redshift
-SMGs. \\
-***Will revise after completing the discussion section.***
+The underlying continuum emission toward the foreground radio galaxy 3C220.3, at $z$ = 0.685, is detected with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.42 mJy. 
+Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (10.1\,$\pm$\,1.3)\,Jy\,km\,s\pmOne, we derive 
+ a lensing- and excitation-corrected CO line luminosity of \Lp = (2.7\,$\pm$\,0.6) $\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling performed on the archival 1\,mm continuum emission.
+ This translates to a molecular gas mass of $M_\textrm{gas}$\,=\,(2.3\,$\pm$\,0.5)\,$\times$\,10$^{10}$\,\Msun. 
+Fitting the SED models to the (sub)-millimeter data of this SMG yields a rest-frame dust temperature of $T_\textrm{dust}$ = 
+63.1$^{+1.1}_{-1.3}$\,K, a dust mass of $M_\textrm{dust}$ = (5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,\Msun, and a total infrared luminosity of 
+$L_\textrm{IR}$ = (9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,\Lsun, after correcting for lensing magnification.
+Our comparative study 
+of the intrinsic properties (\eg gas mass, dust mass, star formation rate, and surface densities) in SMM
+J0939+8315 
+and other high-redshift SMGs and type-2 quasars suggests that SMM\,J0939+8315 is a faithful representation of both populations. 
+SMM\,J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase in the currently favored evolutionary link model.
 \end{abstract}
-\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}
+\keywords{cosmology: observations --- galaxies: formation --- galaxies: high-redshift ---  galaxies: starburst --- submillimeter: galaxies}
 
@@
 rest-frame far-infrared (FIR) wavelengths \citep{blain02a}. 
-In the past $\sim$5~years, considerable amounts of effort have been invested into follow-up observations of SMGs that were 
+In the past $\sim$\,5~years, considerable amounts of effort have been invested into follow-up observations of SMGs that were 
 discovered in large sky surveys \citep[\eg H-ATLAS, HerMES; ][]{Eales10a,Oliver12a}, conducted using (sub)-mm facilities.
@@
 
-  To characterize the physical properties of the gas reservoirs in the ISM where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[See \eg][]{Carilli13a}.
+  To characterize the physical properties of the gas reservoirs in the interstellar medium (ISM) where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[See \eg][]{Carilli13a}.
 Recent observations of CO in SMGs at $z$\,$\sim$\,1\,--\,3 have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Riechers11c,Riechers11d,Ivison11a,Bothwell13a}.
@@
 Many recent follow-up observations and thus detailed studies are carried out on SMGs that are gravitationally lensed,
- as lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a,Oliver12a}. 
-A particularly interesting, peculiar submm-bright lensing system discovered serendipitously  
-consists of a type-2 quasar host SMG --- SMM\,J0939+8315 (hereafter SMM\,J0939), lensed by the double-lobed Fanaroff-Riley 
+ as lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a,Oliver12a}, and allowing observations to be carried out in a timely-manner.
+A particularly interesting and peculiar lensing system was discovered serendipitously in a sky survey carried out with the {\it Herschel Space Telescope}, in which 
+a type-2 quasar host SMG --- SMM\,J0939+8315 (hereafter SMM\,J0939) is being lensed by the double-lobed Fanaroff-Riley 
 Class II \citep*[FR-II; ][]{Fanaroff74} radio galaxy 3C220.3 and its
-companion galaxy B at $z$\,=\,0.685, where the two lensing galaxies are separated by 1\farcs5. 
+companion galaxy B at $z$\,=\,0.685.
 SMM\,J0939 is currently one of the brightest known lensed
@@
  and HeII\,1640\AA\ line emission toward SMM\,J0939 
- placed this galaxy at $z$\,=\,2.221, and suggested the presence of a type-2 quasar,  
-indicating active galactic nucleus activity in this SMG \citep[hereafter H14]{Haas14}.
+ placed the redshift of this galaxy at $z$\,=\,2.221, and suggested the presence of a type-2 quasar,  
+indicating active galactic nucleus (AGN) activity in this SMG \citep[hereafter H14]{Haas14}.
 
@@
 Array for Research in Millimeter Astronomy (CARMA), which refines the redshift, and permits the study of the physical conditions in the ISM of SMM\,J0939 in great detail.
-Our measurement of the underlying continuum emission put constraints on the SED of the different components of the foreground FR-II galaxy at mm wavelength ($\sim$104 GHz).
+We report the detection of the underlying continuum emission and place constraints on the SED of the foreground FR-II galaxy at mm wavelength ($\sim$\,104 GHz).
 Based on the magnification factor from our lens model, we infer intrinsic properties of SMM\,J0939 and thereby
-conclude this paper by comparing our findings to other similarly bright, strongly-lensed SMGs at $z$\,\,$\sim$\,\,2.
+conclude this paper by comparing our findings to other similarly bright, strongly-lensed SMGs at $z$$\sim$\,2.
 
@@
 Observations of the \CO rotational transition ($\nu_\textrm{rest}$\,=\,345.7959899 GHz) toward the background galaxy SMM
-J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; P.I.: Riechers).
-The 3\,mm receivers were used to cover the redshifted \CO line and the nearby 2.88\,mm continuum emission, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and a spectral resolution of 5.208 MHz ($\sim$14.5 km\,\,s\pmOne).
+J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; PI: Riechers).
+The 3\,mm receivers were used to cover the redshifted \CO line and the nearby 2.88\,mm continuum emission.
+The correlators were configured to provide a bandwidth of 3.75 GHz in each sideband, and a spectral resolution of 5.208 MHz ($\sim$\,14.5 km\,\,s\pmOne).
 The line was placed in the
-upper sideband, with the local oscillator tuned to $\nu_\textrm{LO}$\,$\sim$104.2609 GHz.
+upper sideband, with the local oscillator tuned to $\nu_\textrm{LO}$\,$\sim$\,104.2609 GHz. % restructure
 Observations were carried out under good
@@
 flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
-$15\% calibration accuracy.
-The {\sc MIRIAD} package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
-the CLEAN algorithm with ``natural" weighting.
-This yields a synthesized clean beam size of 11$\farcs$3\,$\times$\,6\farcs1, at a position angle of $-$56.1$\degr$ east of north for the upper sideband image cube.
-The rms noise of the data prior to continuum subtraction is $\sigma_\textrm{ch}$\,=\,8.75\,\,mJy\,\,beam\pmOne\ per bin 
-with a channel width of $\sim$29 km\,\,s\pmOne
-% spectra
-, whereas the final rms noise of the continuum subtracted data is $\sigma_\textrm{ch}$\,=\,8.71\,\,mJy\,\,beam\pmOne\ per bin with 
-the same channel width, and $\sigma$\,=\,1.00\,Jy\,\,km\,\,s\pmOne\,\,$\rm beam^{-1}$ over a channel 
-width of 198 MHz (corresponding to $\sim$553\,\,km\,\,s\pmOne). 
-%mom0
+$15\% calibration accuracy. \par
+We use the {\sc MIRIAD} package to calibrate and analyze the visibility data, which are deconvolved and imaged with ``natural" weighting. 
+This yields a synthesized clean beam size of 11$\farcs$5\,$\times$\,6\farcs2, $-$56.1$\degr$ east of north for the upper sideband image cube and an rms noise of $\sigma_\textrm{ch}$\,=\,9.49\,\,mJy\,\,beam\pmOne\ per channel
+of width $\sim$\,29 km\,\,s\pmOne.
 The continuum image is created by
-averaging over all line-free channels, this yields a synthesized clean beam size of 11\farcs9\,$\times$\,6\farcs5, at a position angle of $-$55.9$\degr$ east of north and an 
-rms noise of 0.49\,\,mJy\,\,beam\pmOne.
+averaging over all line-free channels, this yields a synthesized clean beam of 12\farcs0\,$\times$\,6\farcs5, $-$55.9$\degr$ east of north, and an rms noise of $\sigma_\textrm{cont}$ = 0.50\,\,mJy\,\,beam\pmOne.
 
@@
 \subsection{New Results: 3C220.3} 
-Averaging over all line-free channels, we detect continuum emission at 9$\sigma$ significance at an averaged frequency of $\nu_{cont}$\,=\,104.2106 GHz ($\sim$2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$1.7 mm) at $z$\,=\,0.685.
+Averaging over all line-free channels, we detect $\sim$\,9$\sigma$ continuum emission at an averaged frequency of $\nu_{cont}$\,=\,104.2106 GHz ($\sim$\,2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$\,1.7 mm) at $z$\,=\,0.685.
 In this lens system, the
-foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum emission to be dominated by the foreground galaxy (see \S \ref{sec:SEDFg} for details).
-We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission.
-The deconvolved source size is (10\farcs2\,$\pm$\,1\farcs4)\,$\times$\,(6\farcs1\,$\pm$\,0\farcs7), and the integrated flux density is 9.46\,$\pm$\,0.64\,\,mJy.
-At the peak position of the continuum emission, the peak flux density is S$_\nu$\,=\,5.18\,$\pm$\,0.24\,\,mJy\,\,beam\pmOne.
-An overlay image of the 104 GHz continuum emission on the 9 GHz continuum measurement (H14) is shown in Figure~\ref{fig:cont}.
-This demonstrates that at the resolution of our observations, the continuum emission is marginally resolved.
-It is therefore plausible that non-thermal emission from both the lobes and the radio core dominate the integrated flux density in our measurement.
-
+foreground galaxy (3C220.3) is radio-loud, we thus expect it to be the dominant source of the continuum emission (see \S \ref{sec:SEDFg} for details).
+The task {\sc imfit} is used to estimate the peak position of the continuum emission, where the flux density is S$_\nu$\,=\,4.93\,$\pm$\,0.31\,\,mJy\,\,beam\pmOne.
+From the continuum measurement, the deconvolved source size
+is (8\farcs4\,$\pm$\,1\farcs1)\,$\times$\,(4\farcs9\,$\pm$\,0\farcs6) at $-$53.8$\degr$, and the integrated flux density is 7.53\,$\pm$\,1.42\,\,mJy. An overlay image of the 104 GHz  
+continuum emission with the 9 GHz continuum emission (H14) is shown in Figure~\ref{fig:cont}, demonstrating that the continuum 
+emission is marginally resolved at the resolution of our observations.
+It is therefore plausible that non-thermal emission from the radio lobes and core of the foreground galaxy dominate the integrated flux
+density of the measured continuum. We discuss this further in Section \ref{sec:SEDFg}. \par
 The frequency range of our observations covers the HCO$^+$(2\,\rarr\,1), HNC($J$\,=\,2\,$\rightarrow$\,1), and H$_2$O(3$_{13}$\,\rarr\,2$_{20}$) 
@@
 the redshifted frequencies of 105.86, 107.71, and 108.79\,\,GHz, respectively. We establish 3$\sigma$ upper limits employing a typical FWHM line width of 
-$\sim$\,300\,\,km\,\,s\pmOne, based on the CO($J$\,=\,1\,$\rightarrow$\,0) line measurements in a sample of local radio galaxies \citep[$z$ $<$ 0.1; ][]{Smolcic11a}, resulting in 3$\sigma$ of 2.44\,\,Jy\,\,km\,\,s\pmOne.
+$\sim$\,300\,\,km\,\,s\pmOne, based on the CO($J$\,=\,1\,$\rightarrow$\,0) line measurements in a sample of local radio galaxies \citep[$z$ $<$ 0.1; ][]{Smolcic11a}.
+This results in upper limits of $<$ 2.66\,\,Jy\,\,km\,\,s\pmOne\ on the integrated emission line strengths.
 
@@
 \includegraphics[width=0.80\textwidth]{Figure/ContPanel.pdf}
-\caption{Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 11\farcs9\,$\times$\,6\farcs5, at P.A.\,=\,
-$-$56$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
-foreground radio galaxy 3C220.3 overlaid on the 9 GHz emission (green contours and grayscale; H14). The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A. 
-76$\degr$. The central cross on each image indicates the position of the radio core of 3C220.3. The contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
+\caption{Left: Contour map of the 104 GHz continuum emission in the foreground radio galaxy 3C220.3. 
+The contour levels start at $\pm$2$\sigma$, where $\sigma$ = 0.5 mJy beam\pmOne, and 
+increment at steps 
+of $\pm$2$\sigma$. 
+The beam size is 12\farcs0\,$\times$\,6\farcs5, at P.A.\,=\,
+$-$56$\degr$, as indicated in the bottom left corner. Right: CARMA 104 GHz continuum emission (red contours) overlaid on the VLA 9 GHz continuum emission (green contours and grayscale; H14). 
+The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A. 
+76$\degr$. The contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
 of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne; the contour levels of the 9 GHz continuum 
-emission start at $\pm$4$\sigma$ where $\sigma$\,=\,0.064 mJy beam\pmOne\ and increment at steps of $\pm$2$^n\sigma$, 
+emission start at $\pm$4$\sigma$, where $\sigma$\,=\,0.064 mJy beam\pmOne, and increment at steps of $\pm$2$^n\sigma$, 
 where $n$ is a positive integer.
-\label{fig:cont}}
+The central cross on each image indicates the position of the radio core of 3C220.3. \label{fig:cont}}
 \end{figure*}
@@
 \subsection{New Results: SMM\,J0939\\ \CO Line Emission}
-We detect \CO line emission at $\sim$8$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
-The spatial extent of this SMG is $\sim$5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum in Figure~\ref{fig:mom0}; as such, the detected \CO line emission is spatially unresolved.
-The line profile in Figure~\ref{fig:mom0} is therefore extracted at the peak position of the unresolved CO emission.
-Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.83\,$\pm$\,2.68\,\,mJy, superimposed on a continuum level of 4.19\,$\pm$\,0.49\,\,mJy, and a full width at half-maximum (FWHM) line width of 557\,$\pm$\,36\,\,km\,\,s\pmOne.
+We detect \CO line emission at $\sim$\,8$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
+The spatial extent of this SMG is $\sim$\,5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum in Figure~\ref{fig:mom0}; as such, 
+the detected \CO line emission is spatially unresolved. We therefore extract the line profile (Figure~\ref{fig:mom0}) at the peak position of the unresolved 
+CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.61\,$\pm$\,2.66\,\,mJy, superimposed on a 
+continuum level of 4.15\,$\pm$\,0.48\,\,mJy, and a full width at half-maximum (FWHM) line width of 546\,$\pm$\,36\,\,km\,\,s\pmOne.  \par
 We construct a velocity-integrated (0th moment) map of the \CO line 
-emission from the data after subtracting continuum emission in the visibility plane.
-This results in a velocity-integrated \CO line flux of $S_\textrm{CO}$\,=\,10.7\,$\pm$\,1.3 Jy km\,\,s\pmOne\ over the FWZI velocity range of $\Delta v\sim$\,914 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration uncertainty.
-We ignore primary beam correction given that the source is close to the phase center and is unresolved (\ie much smaller than the primary beam size).
-Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.2212\,$\pm$\,0.0010.
+emission after subtracting continuum emission in the visibility plane. This results in a velocity-integrated \CO line flux of $I_\textrm{CO}$\,=\,10.1\,$\pm$
+\,1.3 Jy km\,\,s\pmOne\ over the velocity range of $\Delta v$\,$\sim$\,680 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration 
+uncertainty. Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.2212\,$\pm$\,0.0010.
 
@@
 \caption{Top Left: Continuum-subtracted moment-0 map of \CO line emission toward 
-the background SMG with $\sigma$\,=\,1.00\,Jy\,\,km\,\,s\pmOne\ beam\pmOne\ over a velocity range of $\Delta v\sim$553\,km\,\,s\pmOne.
-The angular resolution is 11$\farcs$3\,$\times$\,6\farcs1, at P.A.\,=\,$-$56\degr, as indicated in the bottom left corner.
-Top Right: Contours of the \CO line emission (red) overlaid on the SMA 1\,mm dust continuum (green contours and grayscale; H14) with $\sigma_\textrm{1\,mm}$\,=\,0.84 mJy beam\pmOne.
-The beam size of the SMA data is 1\farcs4$ \times $1\farcs2, P.A.
+the background SMG with $\sigma$\,=\,1.03\,Jy\,\,km\,\,s\pmOne\ beam\pmOne\ over a velocity range of $\Delta v$\,$\sim$\,514\,km\,\,s\pmOne.
+The beam size is 11$\farcs$5\,$\times$\,6\farcs2, at P.A.\,=\,$-$56\degr, as indicated in the bottom left corner.
+Top Right: Velocity-integrated \CO line emission (red contours) overlaid on the SMA 1\,mm dust continuum (green contours and grayscale; H14) with $\sigma_\textrm{1\,mm}$\,=\,0.84 mJy beam\pmOne.
+The beam size of the SMA observations is 1\farcs4$ \times $1\farcs2, P.A.
 $-$34\degr, as shown
@@
 Bottom: 
-Spectrum extracted at the peak position of CO line emission, with a spectral resolution of $\Delta v$ $\sim$29 km\,\,s\pmOne\, and an rms of $\sigma_\textrm{ch}$\,=\,8.75 mJy beam\pmOne\ per channel.
-Solid black line shows the Gaussian fit to the \CO line profile. Yellow histogram shows the 
+Spectrum extracted at the peak position of CO line emission, with a spectral resolution of $\Delta v$ $\sim$\,29 km\,\,s\pmOne\, and an rms of $\sigma_\textrm{ch}$\,=\,9.5 mJy beam\pmOne\ per channel.
+The
+solid black line shows the Gaussian fit to the \CO line profile, and the yellow histogram shows the 
 flux density as a function of velocity offset, where the velocity scale is relative to $z$\,=\,2.221. 
-%where 0 km\,\,s\pmOne\ corresponds to $z$\,=\,2.221. 
 \label{fig:mom0}}
@@
 
-We fix the phase center to coordinates ($\alpha$,\,$\delta$)\,\,(J2000)\,=\,(9:39:23.54,\,\,83:15:26.10), where the
+We fix the phase center to coordinates ($\alpha$,\,$\delta$)\,\,(J2000) = (9:39:23.54,\,\,83:15:26.10), where the
 angular offsets of the lenses and source are referenced to this phase center. The primary lens (3C220.3) is
@@
 
-We initialize the positions and Einstein radii of both lenses, and the position of the source using the
-best-fit values of the lens model H14 performed on Keck K-band (near-infrared) data. For each of
+We initialize the positions and Einstein radii of both lenses, and the position of the source using those
+ from the best-fit lens model performed on Keck K-band (near-infrared) data (H14). For each of
 these parameters, we impose a uniform prior in the range $\in\pm$3$\sigma$, where $\sigma$ is the uncertainty
@@
 Our best-fit model yields a magnification
-factor of $\mu_\textrm{L}$\,=\,10.13\,$\pm$\,1.38, this is consistent the value reported by H14 within the errors. All best-fit
-parameters are listed in Table \ref{tab:lensParam}.
-The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$\,=\,1.22\,$\pm$\,0.01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$\,=\,0.75\,$\pm$\,0.02 (5.34 kpc at $z$\,=\,0.685),
+factor of $\mu_\textrm{L}$ = 10.13\,$\pm$\,1.38, this is consistent the value reported by H14 within the errors. All best-fit
+parameters are listed in Table~\ref{tab:lensParam}.
+The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1.22\,$\pm$\,0.01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0.75\,$\pm$\,0.02 (5.34\,\,kpc at $z$\,=\,0.685),
 the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
@@
 and dominates the flux density at higher frequencies \citep{Kellermann81a,Begelman84a}.
-This has been observed in a FR-II galaxy at  similar redshift\,--\,3C220.1 at the redshift of $z$\,=\,0.610, where observations were carried out at observed-frame $\sim$\,90 GHz \citep{Hardcastle08a}.
-%It is noteworthy that prior to our observations, 3C220.1 was the only FR-II galaxy with high frequency radio observations at $z$\,$>$\,0.6.
+This has been observed in a FR-II galaxy at similar redshift --- 3C220.1 at $z$ = 0.610, where observations were carried out at observed-frame $\sim$\,90 GHz \citep{Hardcastle08a}.
 
@@
 limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a} and an unambiguous detection of 0.8 mJy at 9 GHz (H14), suggesting a substantially inverted spectrum of the core (Figure~\ref{fig:SED}).
-Consequently, we may naively expect the integrated flux density in our continuum detection of $S_\textrm{104GHz}$\,=\,9.46\,$\pm$\,0.64\,\,mJy to be dominated by the unresolved core component of the foreground FR-II galaxy, which is at $z$\,=\,0.685.
+Consequently, we may naively expect the integrated flux density in our continuum detection of $S_\textrm{104GHz}$\,=\,7.39\,$\pm$\,1.42\,\,mJy to be dominated by the unresolved core component of the foreground FR-II galaxy, which is at $z$\,=\,0.685.
 However, the deconvolved spatial size of the source matching that in the resolved image (see Figure 1) is 
-suggestive of a marginally resolved detection of the extended components with non-negligible emission. 
+suggestive of a marginally resolved detection of the extended lobe components with non-negligible emission. 
 This is plausible given that the orientation of the synthesized beam in our observations is in alignment with the 
@@
 lobes of the radio galaxy, as shown in Figure~\ref{fig:cont}. We investigate this disparity by fitting models to 
-existing SED data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to 
+existing SED measurements as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to 
 estimate the flux density of the lobes at the frequency of our continuum measurement. 
@@
 measurement (Figure~\ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests
-a dominant contribution from the lobes, and the peak flux density does not appear to be emission toward 
+a dominant contribution from the lobes, and that the peak flux density does not correspond to emission toward 
 the core. Moreover, the peak position of the 104\,\,GHz continuum is
@@
 across different epochs. 
-We place an upper limit of $S_\nu$\,$<$\,4.28 mJy on the core component using the difference between the integrated and the peak flux densities.
+Based on our argument, we place an upper limit of $S_\nu$\,$<$\,2.60 mJy on the core component using the difference between the integrated and the peak flux densities.
 \par
 Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, where some exhibit spectral steepening in cm and mm wavelengths (\eg 3C123).
-At the resolution of our observations, it is unclear whether the flux density is dominated by the emission from the compact hotspot or the emission from the surrounding diffuse lobe components.
+At the resolution of our observations, it is unclear whether the measured flux density is dominated by emission from the compact hotspot or that from the surrounding diffuse lobe components.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED2_longticks.pdf}
-\caption{The SED of 3C220.3 (solid purple line) and SMM\,J0939 (dashed purple line and solid cyan line) including the new measurements presented in this paper. 
-Black dots represent existing data of 3C220.3 (see Table \ref{tab:SEDdataRadio}). Red dots at 104 GHz correspond to 
-our continuum measurements (integrated, peak, and difference). The purple line corresponds to the parabolic function we 
-fit to the data associated with the radio galaxy, following \citet{Cleary07a}. The dashed purple line and 
-the solid cyan line correspond to the best-fit SED models of the background SMG. The photometric data of the SMG are reported by H14. \label{fig:SED}}
+\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED2.pdf}
+\caption{The SEDs of 3C220.3 (solid purple line) and SMM\,J0939 (dashed purple line and solid cyan line) including the new measurements presented in this paper. 
+The solid purple line corresponds to the parabolic function we 
+fit to the existing data associated with 3C220.3 (black dots; see Table \ref{tab:SEDdataRadio}).
+The red dots at 104 GHz correspond to 
+our continuum measurements (integrated, peak, and difference, respectively).
+The dashed purple line and 
+the solid cyan line correspond to the best-fit SED models of SMM\,J0939, using the photometric data from H14. \label{fig:SED}}
 \end{figure}
@@
 \subsubsection{SMM\,J0939+8315} \label{sec:SEDBg}
-To constrain the dust and gas properties in the ISM of SMM\,J0939, we perform SED fitting to the
+To constrain the dust and gas properties in the ISM of SMM\,J0939, we perform the SED fitting to the
 photometric data obtained with {\it Herschel}/PACS and SPIRE, at wavelengths
-between observed-frame 70 \micron\,$-$\,500 \micron, and the interferometric data obtained with the SMA at 1\,mm (H14). We use the publicly
+between observed-frame 70\,\micron\,$-$\,500\,\micron, and the interferometric data obtained with the SMA at 1\,mm (H14). We use the publicly
 available software {\sc mbb\_emcee}\footnote{https://github.com/aconley/mbb\_emcee} to perform the SED fitting; the code uses an affine-invariant Markov chain Monte
-Carlo (MCMC) approach, further details of the code are given by \citet{Riechers13a} and \citet{Dowell14a}. The
+Carlo (MCMC) approach, and further details of the code are given by \citet{Riechers13a} and \citet{Dowell14a}. \par
+The
 functional form of the fit comprises a single-temperature, modified blackbody function joined to a $S_{\lambda} \propto \lambda^\alpha
@@
 \end{equation}
-where $T$ is the rest-frame characteristic cold dust temperature, $\beta$ is the dust emissivity (or spectral index of the dust extinction
-curve), and $\alpha$ is the power law spectral index. The overall fit is normalized using the observed-frame 500
+where $T$ is the rest-frame cold dust temperature, $\beta$ is the dust emissivity index (equivalently, the spectral index of the dust extinction
+curve), and $\alpha$ is the mid-infrared power law spectral index. The overall fit is normalized using the observed-frame 500
 $\micron$ flux density, hence this becomes an additional parameter in the fit.
@@
 The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in the Appendix. The best-fit solution of an optically thin
-model corresponds to $\chi^2$\,=\,5.31 with 3 degrees of freedom, whereas that of an optically thick model
-corresponds to $\chi^2$\,=\,2.25 with 2 degrees of freedom, suggesting a better fit than in the optically thin
+model corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of an optically thick model
+corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than in the optically thin
 case. In the subsequent analysis, we employ the inferred values from the optically thick model.
-The best-fit solution yields a rest-frame FIR luminosity of $L_\textrm{FIR (42.5-122.5\micron)}$\,=\,53.3$^{+1.1}_{-1.1}$\,$\times$\,10$^{12}$\,\Lsun, and a total infrared (IR) luminosity of $L_\textrm{IR (8-1000 \micron)}$\,=\,88.5$^{+2.6}_{-2.6}$\,$\times$\,10$
-^{12}$\,\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$\,=\,2.64 m$^2$ kg\pmOne\ at 125.0 $
+The best-fit solution yields a FIR luminosity (rest-frame 42.5-122.5\micron) of $L_\textrm{FIR}$ = 53.3$^{+1.1}_{-1.1}$\,$\times$\,10$^{12}$\,\Lsun, and a total infrared (IR) luminosity of $L_\textrm{IR (8-1000 \micron)}$ = 88.5$^{+2.6}_{-2.6}$\,$\times$\,10$
+^{12}$\,\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64\,\,m$^2$\,\,kg\pmOne\ at 125.0\,\,$
 \micron$ \citep{Dunne03a}, we derive the dust mass using the following expression:
@@
 \end{equation}
-where $S_{\nu}$ is the flux density in ergs/s/cm$^{2}$/Hz , $D_\textrm{L}$ is the luminosity distance in cm, $\kappa_{\nu}$ is the dust
-absorption coefficient in cm$^2$ g\pmOne, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function,
+where $S_{\nu}$ is the flux density in erg\,s\pmOne\,cm$^{-2}$\,Hz\pmOne, $D_\textrm{L}$ is the luminosity distance in cm, $\kappa_{\nu}$ is the dust
+absorption coefficient in cm$^2$\,g\pmOne, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function in units of erg\,s\pmOne\,cm$^{-2}$\,Hz\pmOne,
 all quantities are expressed in the observed-frame.
-We find a dust mass of $M_\textrm{dust}$\,=\,50.5$^{20.4}_{-20.2}\times$10$^8$\,\,\Msun, the uncertainties do not include those of $\kappa_{\nu}$.
-These values are based on SED fitting to the photometric data, \ie prior
+We find a dust mass of $M_\textrm{dust}$ = 50.5$^{20.4}_{-20.2}\times$10$^8$\,\,\Msun, the uncertainties do not include those in the dust absorption coefficient ($\kappa_{\nu}$).
+These values are based on the SED fitting to the photometric data, \ie prior
 to lensing correction.
@@
 With the limited amount of data in the FIR waveband, the dust mass is weakly constrained. 
-We perform an additional fit using an optically thick model where we loosen the upper limit of $\beta$ from 2.2 to 3.0, while the difference between all best-fit parameters in this scenario and those using an upper limit of 2.2 (see Table \ref{tab:mbb}) is within 3\%, we find that the dust mass is boosted by a factor of $\sim$2.
-
-\subsection{Molecular Gas Mass}
-While the ground state CO transition line, CO($J$\,=\,1\,\rarr\,0) traces the cold molecular gas in the ISM
-\citep*[\eg][]{Wilson70a,Downes98a}, CO($J$ $>$ 1) transition lines are frequently observed at high redshifts as the
- ground state CO transition line is redshifted to lower frequencies that can only be observed with a few telescopes 
- \citep{Carilli13a}, 
- hence assumptions on the CO excitation conditions are required to derive the molecular gas mass using the H$_\textrm{2}$-to-CO 
- relation. 
-Prior to the observations of the ground state CO line in SMGs, it has been assumed that the molecular gas in the
+We perform an additional fit using an optically thick model where we loosen the upper limit of $\beta$ from 2.2 to 3.0; while the difference between each of all best-fit parameters in this scenario and that using an upper limit of 2.2 (see Table \ref{tab:mbb}) is within 3\%, we find that the dust mass is boosted by a factor of $\sim$\,2.
+\subsection{Physical Properties of the ISM in SMM\,J0939}
+\subsubsection{Molecular Gas Mass}
+While the ground state CO transition line traces the cold molecular gas in the ISM
+\citep*[\eg][]{Wilson70a,Downes98a}, transition lines of higher rotational states ($J$ $>$ 1) are frequently observed in high redshift sources as the
+ ground state transition line is redshifted to lower frequencies that can only be observed with a few telescopes 
+ \citep{Carilli13a}. Consequently, assumptions on the CO excitation conditions are required to derive the molecular gas mass using the H$_\textrm{2}$-to-CO 
+ relation. \par
+Prior to the observations of the ground state CO transition line in SMGs, it has been assumed that the molecular gas in the
   ISM traced by CO lines is thermalized owing to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
    Yet, recent observations of this line have demonstrated that SMGs can indeed be subthermally excited
-   \citep{Harris10a,Riechers11c,Riechers11d,Ivison11a}; based on observations toward SMGs of both the \CO and the CO($J$\,=\,1\,\rarr\,0) lines, the 
-   brightness temperature ratio has been inferred as $R_\textrm{31}<$ 0.8 \citep
-   {Harris10a,Carilli10a,Swinbank2010a,Riechers11d,Ivison11a,Ivison10d}. In contrast, observations of high-redshift quasar hosts suggest that the ratio 
-   is $R_\textrm{31}\sim$ 1 \citep{Riechers06a, Riechers11a, Scott11a}. 
+   \citep{Harris10a,Riechers11c,Riechers11d,Ivison11a}. Namely, observational results of SMGs with both \CO and CO($J$\,=\,1\,\rarr\,0) line measurements have shown that the 
+   brightness temperature ratio is more commonly found to be $R_\textrm{31}<$ 0.8 \citep
+   {Harris10a,Carilli10a,Swinbank2010a,Riechers11d,Ivison11a,Ivison10d}. In contrast, similar observations in high-redshift quasar hosts suggest that the ratio 
+   is $R_\textrm{31}$\,$\sim$\,1 \citep{Riechers06a, Riechers11a, Scott11a}.
+In the case of high-redshift type-2 quasars, \citet{Riechers11a} report a brightness temperature ratio of $R_\textrm{31}$ = 1.00\,$\pm$\,0.10 for IRAS F10214+4724 (hereafter F10214), which is currently the only known type-2 quasar with both \CO and CO($J$\,=\,1\,\rarr\,0) line measurements.
+\par
 Here, we derive the molecular gas mass 
 assuming thermalized excitation of CO, 
-\eg we adopt $R_\textrm{31}$\,=\,1 as SMM\,J0939 is 
-postulated to be hosting a type-2 quasar; this is based on the reported brightness temperature ratio of $R_\textrm{31}$\,=\,1.00\,$\pm$\,0.10 for the type-2 quasar host IRAS F10214+4724 \citep[hereafter F10214; ][]{Riechers11a}.
-\par
-We calculate the CO($J$\,=\,1 \rarr\ 0) line luminosity using standard relation 
+\ie we adopt $R_\textrm{31}$\,=\,1, as SMM\,J0939 is 
+postulated to be hosting a type-2 quasar. 
+We calculate the CO($J$\,=\,1\rarr0) line luminosity using standard relation 
 \citep[\eg][]{Solomon05a,Carilli13a}:
 \begin{equation}
-L^{\prime}_\textrm{CO}\,=\,\frac{3.25\times10^7}{\nu_\textrm{CO (3-2)}^2}\times \frac{D_L^2}{\mu_\textrm{L}} \times
+L^{\prime}_\textrm{CO}\,=\,\frac{3.25\times10^7}{\nu_\textrm{CO(3-2)}^2}\times \frac{D_L^2}{\mu_\textrm{L}} \times
 \frac{I_\textrm{CO(3-2)}} {R_\textrm{31} (1 + z)}
 \end{equation}
-where $\nu_\textrm{CO (3-2)}$ is the rest-frame frequency of the \CO transition line in GHz, $D_L$ is the luminosity distance in Mpc, $\mu_\textrm{L}$ is the lensing magnification factor, and $I_\textrm{CO(3-2)}$ is the \CO line flux in Jy\,\,km\,\,s\pmOne.
-After correcting for lensing magnification, this corresponds to $L^{\prime}_\textrm{CO (1-0)}$\,=\,(2.91\,$\pm$\,0.60)\,\,$\times$\,\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\,\LpU; the inferred total molecular gas mass is therefore $M_\textrm{gas}$\,=\,(2.33\,$\pm$\,0.48)\,\,$\times$\,\,10$^{10}$\,\Msun.
-We assumed a conversion factor of $\alpha_\textrm{CO}$\,=\,0.8\,\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
+where $\nu_\textrm{CO(3-2)}$ is the rest-frame frequency of the \CO transition line in GHz, $D_L$ is the luminosity distance in Mpc, $\mu_\textrm{L}$ is the lensing magnification factor, and $I_\textrm{CO(3-2)}$ is the \CO line flux in Jy\,\,km\,\,s\pmOne.
+This corresponds to $L^{\prime}_\textrm{CO (1-0)}$ = (2.74\,$\pm$\,0.60) $\times$\,\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\,\LpU, hence
+the inferred total molecular gas mass is $M_\textrm{gas}$ = (2.19\,$\pm$\,0.48) $\times$\,\,10$^{10}$\,\Msun\, after correcting for lensing magnification.
+We assumed a conversion factor of $\alpha_\textrm{CO}$ = 0.8\,\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
 adopted for SMGs \citep[\eg][]{Tacconi06a,Tacconi08a,Bothwell13a}. 
 This results in a gas-to-dust
-ratio of $f_\textrm{gas-dust}$\,=\,$M_\textrm{gas}/M_\textrm{dust}$\,=\,47\,$\pm$\,21, in good agreement with the 
+ratio of $f_\textrm{gas-dust}$\,=\,$M_\textrm{gas}/M_\textrm{dust}$\,=\,44\,$\pm$\,21, in good agreement with the 
 values found in other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.
-% find an excellent agreement of blah with blah
-\subsection{Star Formation Rate}
-No strong evidence of a warm dust component is found in SMM\,J0939 based on the mid-IR continuum measurements (see Figure~\ref{fig:SED}), hence we derive the star formation rate (SFR) assuming negligible contributions to the IR luminosity due to AGN heating.
+
+\subsubsection{Star Formation Rate}
+%No strong evidence of a hot dust bump is found in SMM\,J0939 based on the mid-IR (WAIT, BUT ONLY HAVE 70 micron onwards) continuum measurements (see Figure~\ref{fig:SED}), hence 
+We derive the star formation rate (SFR) assuming the dominant IR heating mechanism is from young and massive stars, and ignoring contribution from the 
+dust-enshrouded AGN. 
 Using the \citet{Kennicutt98a} relation and assuming \citet{Chabrier03a}
 stellar initial mass (IMF) function\footnote{SFR$_\textrm{FIR}$\,=\,526\,$\pm$\,73 $M_
-\odot$ yr\pmOne\ }, 
-the SFR$_\textrm{IR}$ is 874\,$\pm$\,122\,\,$M\sun$\,\,yr\pmOne.
+\odot$ yr\pmOne\ using FIR luminosity},
+we derive a SFR$_\textrm{IR}$ of 874\,$\pm$\,122\,\,$M\sun$\,\,yr\pmOne, employing the lensing-corrected bolometric IR luminosity.
 Assuming constant SFR, the time for which the starburst in SMM\,J0939 can be maintained at its
-current SFR can be approximated as the gas depletion timescale, $\tau_\textrm{depl}$\,=\,$M_\textrm{gas}$/SFR. 
-This corresponds to $\tau_\textrm{depl}$\,=\,25.6\,$\pm$\,0.4 Myr, which is in good agreement with that found in other SMGs \citep[\eg][]{Greve05a}.
+current rate can be approximated as the gas depletion timescale, $\tau_\textrm{depl}$\,=\,$M_\textrm{gas}$/SFR. 
+This corresponds to $\tau_\textrm{depl}$\,=\,25.1\,$\pm$\,0.4 Myr, which is in good agreement with that found in other SMGs \citep[\eg][]{Greve05a}.
 
-\subsection{Star Formation Efficiency}
+\subsubsection{Star Formation Efficiency}
 The SFR per unit mass of molecular gas is commonly taken as a
 measure of the star formation efficiency, SFE\,=\,SFR/$M_\textrm{gas}$. We compute this ratio using lensing-corrected IR 
-luminosity and CO luminosity, i.e., SFE\,=\,$L_\textrm{IR}$/\Lp, this makes no assumptions on the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$) as well as the 
-choice of IMF, however, this assumes that differential lensing effect between the CO and infrared emission is negligible. 
-The resulting ratio is SFE$_\textrm{IR}$\,=\,300\,$\pm$\,9\,\,\Lsun\,(\LpU)$^{-1}$, this is comparable
-to what is found in ``typical" SMGs \citep{Riechers11c,Greve05a,Tacconi06a}.
+luminosity and CO luminosity, i.e., SFE\,=\,$L_\textrm{IR}$/\Lp. This makes no assumptions on the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$) as well as the 
+choice of IMF; however, this assumes that differential lensing effect between the CO and infrared emission is negligible. 
+The resulting ratio is SFE$_\textrm{IR}$\,=\,319\,$\pm$\,9\,\,\Lsun\,(\LpU)$^{-1}$, this is comparable
+to what is found in ``typical" SMGs \citep{Greve05a,Tacconi06a,Riechers11c}.
 
-\subsection{Dynamical Mass} 
-Based on our \CO line measurement, we estimate the dynamical mass of SMM\,J0939 assuming the molecular gas is virialized, and using an isotropic virial estimator \citep[\eg][]{Engel10a}:
+\subsubsection{Dynamical Mass} 
+Based on our \CO line measurement, we estimate the dynamical mass of SMM\,J0939 assuming the molecular gas is virialized.
+With this assumption, we use an isotropic virial estimator \citep[\eg][]{Engel10a}:
 \begin{equation}
@@
 where $\Delta v_\textrm{line}$ is in km\,\,s\pmOne, $R_\textrm{eff}$ is in kpc, and $M_\textrm{dyn}$ is in \Msun.
-We employ the FWHM linewidth of the \CO line profile for $\Delta v_\textrm{line}$,
-and the half-light radius from our lens model for $R_\textrm{eff}$, this assumes that the dust emission traces the same emitting region as the CO.
-The inferred dynamical mass is $M_\textrm{dyn}$\,=\,(7.4\,$\pm$\,2.4)\,$\times$\,10$^{10}$\,\Msun, and the gas-to-dynamical mass fraction is $f_\textrm{gas-to-dyn}$\,=\,0.32\,$\pm$\,0.12, consistent with that of other SMGs \citep{Tacconi06a}.
+We employ the FWHM line width of the \CO line profile for $\Delta v_\textrm{line}$,
+and the half-light radius from our lens model for $R_\textrm{eff}$, assuming that the dust emission traces the same emitting region as the CO.
+The inferred dynamical mass is $M_\textrm{dyn}$ = (7.5\,$\pm$\,2.4)\,$\times$\,10$^{10}$\,\Msun, and the gas-to-dynamical mass fraction is $f_\textrm{gas-to-dyn}$ = 0.29\,$\pm$\,0.12, consistent with that of other SMGs \citep{Tacconi06a}.
 
-\subsection{Star Formation and Gas Surface Densities}
+\subsubsection{Star Formation and Gas Surface Densities}
 To compute surface densities, we divide half the inferred SFR and gas mass by the area subtended by the half-light 
-radius, resulting in $\Sigma_\textrm{gas}$\,=\,4.67\,$\times$\,10$^9$\,\,\Msun\,\,kpc$^{-2}$ and $\Sigma_\textrm{SF}$\,=\,175.20\,\,\Msun\,\,yr\pmOne\,\,kpc$^{-2}$, in good agreement with values typical for SMGs \citep{Tacconi08a}.
-
+radius, resulting in $\Sigma_\textrm{gas}$ = 4.39\,$\times$\,10$^9$\,\,\Msun\,\,kpc$^{-2}$ and $\Sigma_\textrm{SF}$ = 175.20 \Msun\,\,yr\pmOne\,\,kpc$^{-2}$, which are in good agreement with values typical for SMGs \citep{Tacconi08a}.
 The inferred surface densities of SMM\,J0939 follow a universal Schmidt-Kennicutt relation between the star formation rate
-surface density and the molecular gas surface density reported by \citet{B07a}: $\Sigma_\textrm{SF}$\,=\,9.3\,$\times$\,10$^{-5}$ ($M_\textrm{gas}$/2$\pi R_\textrm{1/2}^2)^{1.71}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
+surface density and the molecular gas surface density reported by \citet{B07a}: $\Sigma_\textrm{SF}$ = 9.3\,$\times$\,10$^{-5}$ ($M_\textrm{gas}$/2$\pi R_\textrm{1/2}^2)^{1.71}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
 galaxies
-out to $z\ \sim$ 2.5, and assuming Chabrier IMF.
+out to $z$\,$\sim$\,2.5, and assuming Chabrier IMF.
 
 \section{Discussion And Conclusions} 
-We present the detection of \CO line emission toward SMM\,J0939+8315, a strongly-lensed SMG host of a type-2 quasar, refining the redshift  
-to $z$\,=\,2.2212\,$\pm$\,0.0010. The underlying continuum is detected at high significance, where the peak flux density is most likely to be 
-dominated by emission from the lobes and hotspot of the foreground radio galaxy 3C220.3, thus an upper limit of $S_\nu$ $<$ 4.28 mJy is 
+\input{table_compareSMG}
+We present the detection of \CO line emission toward SMM\,J0939+8315, a strongly-lensed SMG that is hosting a type-2 quasar, refining the redshift  
+to $z$\,=\,2.2212\,$\pm$\,0.0010. The underlying continuum is detected at $\sim$\,9$\sigma$ significance, where the flux density is most likely to be 
+dominated by emission from the lobes and hotspot of the foreground radio galaxy 3C220.3, thus an upper limit of $S_\nu$ $<$ 2.60 mJy is 
 placed on the compact core component.
@@
 The detection of CO in SMM\,J0939 
-implies a CO luminosity of \Lp\,=\,(2.91\,$\pm$\,0.60)\,$\times$\,10$^{10}$(10.1/$\mu_\textrm{L}$)\,\,\LpU, suggesting the presence of a massive 
-molecular gas reservoir that is fueling the star formation at a rate of $\sim$\,874\,\Msun\ yr\pmOne. We derive the SFR using the lensing 
-corrected bolometric IR luminosity, assuming the dominant IR heating mechanism is from young and massive stars, and ignoring contribution from the 
-dust-enshrouded AGN. If star formation continues consistently at the current SFR, the gas reservoir will be depleted within $\lesssim$ 26 Myr, 
-which is consistent with the short timescale found in SMGs.
-The derived intrinsic properties of SMM\,J0399 are evident of ongoing rapid star formation, which is in good agreement with the current conjecture that SMGs are a
+implies a CO luminosity of \Lp = (2.7\,$\pm$\,0.6) $\times$ 10$^{10}$ (10.1/$\mu_\textrm{L}$) \LpU, suggesting the presence of a massive 
+molecular gas reservoir that fuels the star formation at a rate of $\sim$\,874\,\Msun~yr\pmOne.
+If the star forming activity continues at the current rate, the gas reservoir will be depleted within $\lesssim$~25 Myr,
+which is consistent with the short timescale found in SMGs \citep{Greve05a}.
+The derived intrinsic properties of SMM\,J0399 are evident of ongoing rapid star formation; this is in good agreement with the current conjecture that SMGs are a
 population of high-redshift galaxies that build up most of the stellar mass in the early universe, thus play an important role 
-in galaxy formation and evolution.
+in galaxy formation and evolution (BLAH cite).
 
-\input{table_compareSMG}
 We investigate variations within the SMG population by comparing SMM\,J0939 with two other exceptionally submm-bright, 
 strongly-lensed SMGs
-found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which have been studied in great detail. The gas and dust properties 
+found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which have been studied in great detail. The properties 
 of these galaxies are listed in Table~\ref{tab:comapreSMG}. While the cosmic Eyelash has the least amount of molecular gas, as well as 
@@
 cosmic
-Eyelash, demonstrating the variations in gas and dust content, thus star formation activity within the population at $z$\,$\sim$\,2. 
-Gravitational 
-lensing may be accountable for such discrepancies, in particular with the cosmic Eyelash having the highest lensing magnification among the 
+Eyelash. Such distinction is likely a result of our selection bias, while these sources appear similarly bright at 250 \micron, their lensing factors 
+vary by a factor of $\sim$\,3. In particular, with the cosmic Eyelash having the highest lensing magnification among the 
 three, this
-intrinsically fainter, and less gas-rich SMG is unsurprisingly bright 
-at 250\,\micron, with its CO line and IR luminosities lower than those of most SMGs studied to date. While lensing can probe the fainter 
-sources, we find that SMM\,J0939 is representative of the SMG population, with its intrinsic CO line luminosity, IR luminosity, gas mass, 
-dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in un-lensed SMGs studied to date 
-\citep{Greve05a}.
+intrinsically fainter, and less gas-rich SMG appears notably bright 
+at 250\,\micron, with its CO line and IR luminosities lower than those of most SMGs studied to date. 
+This demonstrates 
+the large variations in gas mass, dust mass, thus star forming activity within the population at $z$\,$\sim$\,2, which is discernible only
+ with the aid of gravitational lensing. 
+While lensing can probe sources 
+of various intrinsic properties, we find that SMM\,J0939 is representative of the population, with its intrinsic CO line luminosity, IR luminosity, gas mass, 
+dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in ``typical", un-lensed SMGs studied to date 
+\citep[\eg ][]{Greve05a,Tacconi10a}.
 
 To examine whether SMM\,J0939 is also representative of type-2 quasars at high redshifts, we compare the properties of SMM\,J0939 
-against 
-the mean values of the properties from eight CO-detected obscured AGNs at $z$ = 1.6\,--\,2.8 \citep[][and references therein]{Polletta11a}, 
-we caution that the detected CO 
-transition line varies across each source, hence inducing high systematic uncertainties in the reported values.
+against those of eight CO-detected obscured AGNs at $z$ = 1.6\,--\,2.8, using the averaged values reported by \citet[][and references 
+therein]{Polletta11a}. We caution that the detected CO 
+transition line varies across each source, 
+hence inducing high systematic uncertainties in the reported values. 
+In contrast with what was found for F10214, one of the eight sources in their sample with the lowest SFR and gas mass (derived using CO($J$\,=\,4\,\rarr\,3) line emission), we find that the properties
+(\eg FWHM line width of the CO transition line profile, M$_\textrm{gas}$, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a 
+factor of $\sim$\,1.5, is nevertheless consistent within the measurement uncertainties.
+The fact that the gas mass of F10214 in their compilation was derived using CO($J$\,=\,4\,\rarr\,3) line emission has minor effect on the resulting low gas mass, \citet{Riechers11a} report a similarly low gas mass derived using their CO($J$\,=\,1\rarr0) line measurement.
+This demonstrates that despite the variations in the intrinsic properties among lensed sources,
+ SMM\,J0939 is representative of type-2 quasars at high redshifts (at least among the sample from \citet{Polletta11a}).
 
-% Here
-All properties of J0939 are consistent with the reported (\eg FWHM of CO line, Mgas, SFR, and SFE) are consistent with the reported mean values within the uncertainties.
-
-We compare the properties of SMM\,J0939 to one of the eight type-2 quasar host --- F10214, of which the molecular gas has been studied 
-in great detail \citep{Riechers11a,Solomon05a}. We do not find evidence of low SFE in SMM J0939, our SFE, SFR, gas masses is similar to 
-that of type-1 QSO and SMGs. But F10214 also lensed, with $\mu_\textrm{L}$ = 17 (R11a), similar to cosmic eyelash, so it is plausible 
-that the low SFR,SFE, gas mass (derived using CO(4-3) is due to the intrinsically fainter weaker less gas-rich, less dusty, rather than a 
-difference between type-1 and type-2 QSO.
-We also compare values against
-
-%evolutionary phase
-H14 claim that SMMJ0939 is undergoing a violent breaking of the dust cocoon stage, together with the SFR, may support the paradigm that it is transforming / transitioning from the SMG phase to an unobscured QSO (coppin08a and references therein)
-
-Radio galaxy lensing probability.
-This system is the only known of strong galaxy-scale lensing by radio galaxy.
+We conclude this paper by noting that SMM\,J0939 is a faithful representation of both high-redshift type-2 quasars and SMGs, 
+based on the excellent agreements found between theirs properties. In this remarkable lensing system, the background galaxy --- SMM\,J0939 is 
+breaking up its dust cocoon (H14) while undergoing massive star-formation (SFR $\sim$\,874 \Msun~yr\pmOne). 
+This scenario is consistent with the proposed evolutionary phase model \citep{Coppin08a,Simpson12a}, whereby SMM\,J0939 is transitioning from its star-bursting phase to the unobscured quasar phase.
 
 \acknowledgments
-We thank Shane Bussmann for providing the code {\sc uvmcmcfit} for lens modeling, and helpful discussion; Alex Conley for providing the code {\sc mbb\_emcee} for SED fitting.
+We thank Shane Bussmann for providing the code {\sc uvmcmcfit} for lens modeling, and helpful discussions; Alex Conley for providing the code {\sc mbb\_emcee} for SED fitting.
 We acknowledge the WENSS team for providing the radio measurements for 3C220.3.
 Facilities: \facility{CARMA}
-
+\newpage
 \bibliographystyle{apj}
@@
 \appendix
+We perform the SED fitting to the (sub)-mm data of SMM\,J0939 using {\sc mbb\_emcee} (see \S \ref{sec:SEDBg}), this code uses MCMC to sample the parameter space of each parameter.
+The bolometric IR luminosity and dust mass are then derived from the set of parameters that maximizes the likelihood.
+We show in Figure~\ref{fig:sedlikelihood} the resulting correlation plots of each pair of parameters (off-diagonal) as well as the marginalized posterior probability distribution plots of each parameter (diagonal) for the fitted optically thick and optically thin models.
+The parameter values corresponding to the most likely solution are denoted as black crosses in the 2D correlation plots, and vertical lines in the marginalized posterior probability distribution plots.
+\par
 
-We perform SED fitting to the IR photometric data of SMM\,J0939 using {\sc mbb\_emcee} (see \S \ref{sec:SEDBg}), this code uses MCMC to fully sample the parameter space of each parameter.
-The bolometric IR luminosity and dust mass are then derived from the set of parameter values that maximize the likelihood.
-Figure~\ref{fig:sedlikelihood} shows the correlations between each pair of parameters (off-diagonal) as well as the marginalized posterior probability distribution of each parameter (diagonal) for both optically thick and optically thin models.
-The set of best-fit parameters are denoted as black crosses in the 2D correlation plots, and vertical lines in the marginalized posterior probability distribution plots.
-BLAH
+As shown in the figure, the PDF of each parameter in the optically thin model is Gaussian distributed, and 
+the dust emissivity index ($\beta$) is highly anti-correlated with the observed-frame dust temperature ($T/(1+z)$).
+We note that the best-fit emissivity in this model is unusually low for high redshift galaxies ($\beta$ = 0.7$^{+0.2}_{-0.3}$, cf.
+1$-$2.5; \eg \citet{Casey12a} and references therein).
+While this directly affects the slope of the Rayleigh-Jeans tail of the modified blackbody function, such low emissivity has insignificant impact on the inferred IR luminosity.
+We also find no evidence of correlation between the inferred dust mass and IR luminosity, to wit, despite the factor of $\sim$\,2 difference
+in dust masses 
+between models, the derived IR luminosities are comparable.
+
+A comparison of the reduced $\chi^2$ between the two models suggests that the optically thick model is superior than the optically thin model.
+In the preferred model, the marginalized PDF of the dust emissivity index is highly non-Gaussian, with noticeably broad distribution across
+the allowed range (upper limit: 2.2). We therefore fit a second optically thick model, changing the upper limit of $\beta$ to 3.0. The difference in each 
+parameter of the best-fit solution between these two scenarios is within 3\%, whereas the dust mass is boosted by a factor of $\sim$\,2. This is 
+unsurprising given the dearth of data in the FIR waveband, leading to a weakly constrained emissivity, and thus the inferred dust mass. 
+In our analysis, we employed the set of parameters and thus inferred properties (dust mass, and IR luminosity) from the former.
+
+%Mdust highly dependent on T in shorter wavelengths,
+%Mdust uncorrelated with LIR
+% Beta has insignificant effect on LIR
 
@@
 \includegraphics[width=0.47\textwidth]{Figure/CorrelationPlot__thin_testSMA}
-\caption{Correlation plots from our SED fitting using an optically thick
+\caption{Correlation plots from the fitted SEDs, using an optically thick
 model (left), and an optically thin model (right). Marginalized posterior probability 
 distribution of each
-parameter is plotted on the diagonal axis of each panel, where the vertical lines indicate the best-fit value.
-The correlation plots between parameters are plotted as 2D histograms in the off-diagonal.
-Black crosses on each 2D histogram denote the
-best-fit values in 
-the 2D correlation plot.
+parameter is plotted on the diagonal axis of each panel, where the solid black vertical lines indicate the set of parameter values in the PDFs that maximizes the likelihood.
+The correlation plots between parameters are plotted as 2D histograms on the off-diagonals, where the black crosses denote the
+locations 
+at which the most likely solution corresponds to.
 \label{fig:sedlikelihood}}

### 2015-07-31 skeleton.tex
Fixed table format, done paper, changed contour in plot setting

@@
 the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
-The underlying continuum emission toward the foreground radio galaxy 3C220.3, at $z$ = 0.685, is detected with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.42 mJy. 
+The underlying continuum emission toward the foreground radio galaxy 3C220.3, at $z$ = 0.685, is detected with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy. 
 Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (10.1\,$\pm$\,1.3)\,Jy\,km\,s\pmOne, we derive 
@@
  This translates to a molecular gas mass of $M_\textrm{gas}$\,=\,(2.3\,$\pm$\,0.5)\,$\times$\,10$^{10}$\,\Msun. 
-Fitting the SED models to the (sub)-millimeter data of this SMG yields a rest-frame dust temperature of $T_\textrm{dust}$ = 
+Fitting the spectral energy distribution (SED) models to the (sub)-millimeter data of this SMG yields a rest-frame dust temperature of $T_\textrm{dust}$ = 
 63.1$^{+1.1}_{-1.3}$\,K, a dust mass of $M_\textrm{dust}$ = (5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,\Msun, and a total infrared luminosity of 
@@
 J0939+8315 
-and other high-redshift SMGs and type-2 quasars suggests that SMM\,J0939+8315 is a faithful representation of both populations. 
+and other high-redshift SMGs and type-2 quasars shows that SMM\,J0939+8315 is a faithful representation of both populations, suggesting that
 SMM\,J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase in the currently favored evolutionary link model.
@@
 Array for Research in Millimeter Astronomy (CARMA), which refines the redshift, and permits the study of the physical conditions in the ISM of SMM\,J0939 in great detail.
-We report the detection of the underlying continuum emission and place constraints on the SED of the foreground FR-II galaxy at mm wavelength ($\sim$\,104 GHz).
-Based on the magnification factor from our lens model, we infer intrinsic properties of SMM\,J0939 and thereby
-conclude this paper by comparing our findings to other similarly bright, strongly-lensed SMGs at $z$$\sim$\,2.
+We report the detection of the underlying continuum emission and place constraints on the spectral energy distribution (SED) of the foreground FR-II galaxy at mm wavelength ($\sim$\,104 GHz).
+Based on the magnification factor derived from our lens model, we infer intrinsic properties of SMM\,J0939 and thereby
+conclude this paper by comparing our findings to other similarly bright, strongly-lensed SMGs, as well as other type-2 quasars at $z$\,$\sim$\,2 .
 
-We adopt a standard $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km\,\,Mpc\pmOne\,\,s\pmOne, $\Omega_\textrm{M}$\,=\,0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
+We adopt a flat $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km\,\,Mpc\pmOne\,\,s\pmOne, $\Omega_\textrm{M}$\,=\,0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
 The luminosity distances at $z$\,=\,0.685 and $z$\,=\,2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
@@
 Averaging over all line-free channels, we detect $\sim$\,9$\sigma$ continuum emission at an averaged frequency of $\nu_{cont}$\,=\,104.2106 GHz ($\sim$\,2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$\,1.7 mm) at $z$\,=\,0.685.
-In this lens system, the
+In this lensing system, the
 foreground galaxy (3C220.3) is radio-loud, we thus expect it to be the dominant source of the continuum emission (see \S \ref{sec:SEDFg} for details).
@@
 From the continuum measurement, the deconvolved source size
-is (8\farcs4\,$\pm$\,1\farcs1)\,$\times$\,(4\farcs9\,$\pm$\,0\farcs6) at $-$53.8$\degr$, and the integrated flux density is 7.53\,$\pm$\,1.42\,\,mJy. An overlay image of the 104 GHz  
+is (8\farcs4\,$\pm$\,1\farcs1)\,$\times$\,(4\farcs9\,$\pm$\,0\farcs6) at $-$53.8$\degr$, and the integrated flux density is 7.39\,$\pm$\,1.42\,\,mJy. An overlay image of the 104 GHz  
 continuum emission with the 9 GHz continuum emission (H14) is shown in Figure~\ref{fig:cont}, demonstrating that the continuum 
@@
 \caption{Left: Contour map of the 104 GHz continuum emission in the foreground radio galaxy 3C220.3. 
-The contour levels start at $\pm$2$\sigma$, where $\sigma$ = 0.5 mJy beam\pmOne, and 
-increment at steps 
-of $\pm$2$\sigma$. 
+%The contour levels start at $\pm$2$\sigma$, where $\sigma$ = 0.5 mJy beam\pmOne, and 
+%increment at steps of $\pm$2$\sigma$. 
 The beam size is 12\farcs0\,$\times$\,6\farcs5, at P.A.\,=\,
@@
 The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A. 
-76$\degr$. The contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
-of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne; the contour levels of the 9 GHz continuum 
+76$\degr$. The contour levels of the 104 GHz continuum emission start at $\pm$2$\sigma$, incrementing at steps 
+of $\pm$2$\sigma$ of 0.5 mJy beam\pmOne; the contour levels of the 9 GHz continuum 
 emission start at $\pm$4$\sigma$, where $\sigma$\,=\,0.064 mJy beam\pmOne, and increment at steps of $\pm$2$^n\sigma$, 
@@
 We construct a velocity-integrated (0th moment) map of the \CO line 
-emission after subtracting continuum emission in the visibility plane. This results in a velocity-integrated \CO line flux of $I_\textrm{CO}$\,=\,10.1\,$\pm$
-\,1.3 Jy km\,\,s\pmOne\ over the velocity range of $\Delta v$\,$\sim$\,680 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration 
+emission after subtracting continuum emission in the visibility plane.
+This results in a velocity-integrated \CO line flux of $I_\textrm{CO}$\,=\,10.1\,$\pm$\,1.3 Jy km\,\,s\pmOne\ over the velocity range of $\Delta v$\,$\sim$\,680 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration
 uncertainty. Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.2212\,$\pm$\,0.0010.
@@
 The beam size is 11$\farcs$5\,$\times$\,6\farcs2, at P.A.\,=\,$-$56\degr, as indicated in the bottom left corner.
-Top Right: Velocity-integrated \CO line emission (red contours) overlaid on the SMA 1\,mm dust continuum (green contours and grayscale; H14) with $\sigma_\textrm{1\,mm}$\,=\,0.84 mJy beam\pmOne.
+Top Right: Velocity-integrated \CO line emission (red contours) overlaid on the SMA 1\,mm dust continuum (green contours and grayscale; H14), with an rms noise of $\sigma_\textrm{1\,mm}$\,=\,0.84 mJy beam\pmOne.
 The beam size of the SMA observations is 1\farcs4$ \times $1\farcs2, P.A.
@@
 Bottom: 
-Spectrum extracted at the peak position of CO line emission, with a spectral resolution of $\Delta v$ $\sim$\,29 km\,\,s\pmOne\, and an rms of $\sigma_\textrm{ch}$\,=\,9.5 mJy beam\pmOne\ per channel.
+Spectrum extracted at the peak position of CO line emission, with a spectral resolution of $\Delta v$ $\sim$\,29 km\,\,s\pmOne, and an rms of $\sigma_\textrm{ch}$\,=\,9.5 mJy beam\pmOne\ per channel.
 The
@@
 parameters are listed in Table~\ref{tab:lensParam}.
-The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1.22\,$\pm$\,0.01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0.75\,$\pm$\,0.02 (5.34\,\,kpc at $z$\,=\,0.685),
+The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1\farcs22\,$\pm$\,0\farcs01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0\farcs75\,$\pm$\,0\farcs02 (5.34\,\,kpc at $z$\,=\,0.685),
 the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
@@
 and dominates the flux density at higher frequencies \citep{Kellermann81a,Begelman84a}.
-This has been observed in a FR-II galaxy at similar redshift --- 3C220.1 at $z$ = 0.610, where observations were carried out at observed-frame $\sim$\,90 GHz \citep{Hardcastle08a}.
+This has been observed in a FR-II galaxy at similar redshift --- 3C220.1 at $z$ = 0.610, where observations were carried out at the observed-frame frequency of $\sim$\,90 GHz \citep{Hardcastle08a}.
 
@@
 measurement (Figure~\ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests
-a dominant contribution from the lobes, and that the peak flux density does not correspond to emission toward 
+dominant contribution from the lobes, and that the peak flux density does not correspond to emission toward 
 the core. Moreover, the peak position of the 104\,\,GHz continuum is
@@
    brightness temperature ratio is more commonly found to be $R_\textrm{31}<$ 0.8 \citep
-   {Harris10a,Carilli10a,Swinbank2010a,Riechers11d,Ivison11a,Ivison10d}. In contrast, similar observations in high-redshift quasar hosts suggest that the ratio 
+   {Harris10a,Carilli10a,Swinbank2010a,Ivison10d,Ivison11a,Riechers11d}. In contrast, similar observations in high-redshift quasar hosts suggest that the ratio 
    is $R_\textrm{31}$\,$\sim$\,1 \citep{Riechers06a, Riechers11a, Scott11a}.
@@
 dust-enshrouded AGN. 
-Using the \citet{Kennicutt98a} relation and assuming \citet{Chabrier03a}
+Using the \citet{Kennicutt98a} relation and assuming the \citet{Chabrier03a}
 stellar initial mass (IMF) function\footnote{SFR$_\textrm{FIR}$\,=\,526\,$\pm$\,73 $M_
 \odot$ yr\pmOne\ using FIR luminosity},
-we derive a SFR$_\textrm{IR}$ of 874\,$\pm$\,122\,\,$M\sun$\,\,yr\pmOne, employing the lensing-corrected bolometric IR luminosity.
+we derive a SFR$_\textrm{IR}$ of 874\,$\pm$\,122 $M\sun$\,\,yr\pmOne, employing the lensing-corrected bolometric IR luminosity.
 Assuming constant SFR, the time for which the starburst in SMM\,J0939 can be maintained at its
@@
 implies a CO luminosity of \Lp = (2.7\,$\pm$\,0.6) $\times$ 10$^{10}$ (10.1/$\mu_\textrm{L}$) \LpU, suggesting the presence of a massive 
-molecular gas reservoir that fuels the star formation at a rate of $\sim$\,874\,\Msun~yr\pmOne.
+molecular gas reservoir that fuels the star formation at a rate of $\sim$\,874 \Msun~yr\pmOne.
 If the star forming activity continues at the current rate, the gas reservoir will be depleted within $\lesssim$~25 Myr,
@@
 population of high-redshift galaxies that build up most of the stellar mass in the early universe, thus play an important role 
-in galaxy formation and evolution (BLAH cite).
+in galaxy formation and evolution \citep[\eg ][]{Micha10a}.
 
@@
 of various intrinsic properties, we find that SMM\,J0939 is representative of the population, with its intrinsic CO line luminosity, IR luminosity, gas mass, 
-dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in ``typical", un-lensed SMGs studied to date 
+dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in ``typical" SMGs studied to date 
 \citep[\eg ][]{Greve05a,Tacconi10a}.
@@
 based on the excellent agreements found between theirs properties. In this remarkable lensing system, the background galaxy --- SMM\,J0939 is 
-breaking up its dust cocoon (H14) while undergoing massive star-formation (SFR $\sim$\,874 \Msun~yr\pmOne). 
+breaking up its dust cocoon (H14) while undergoing prodigious star-formation (SFR\,$\sim$\,874 \Msun~yr\pmOne). 
 This scenario is consistent with the proposed evolutionary phase model \citep{Coppin08a,Simpson12a}, whereby SMM\,J0939 is transitioning from its star-bursting phase to the unobscured quasar phase.
@@
 The correlation plots between parameters are plotted as 2D histograms on the off-diagonals, where the black crosses denote the
-locations 
+locations in the parameter space
 at which the most likely solution corresponds to.

### 2015-07-31 Code/FgContIm.py

@@ -42,6 +42,16 @@ def sigma_contour_CARMA(sigma):
     arr = [i * sigma for i in arr]
     return arr
 
+def sigma_contour_cont(sigma):
+    """
+    return list of sigma multiples, -4,-2,2,4,6..20  * sigma
+    """
+    arr = range(-4, 20)
+    arr.remove(0)
+#    arr = [i * np.sqrt(2) * sigma for i in arr]
+    arr = [i * 2 * sigma for i in arr]
+    return arr
+
 def sigma_contour_lowSNR(sigma):
     """
     return list of sigma multiples, -4,-3,-2,2,...20  * sigma

### 2015-07-31 Code/Plot_Image.py

@@ -22,8 +22,8 @@ fig_line = plt.figure(2, figsize=(12, 5))
 # user define area
 ########################################
 sigma_9ghz          = 6.41094e-05
-sigma_cont          = 4.9e-4
-sigma_line          = 1.0 # 1.35   # chan 65,85 (pretty)     # 1.0      # chan72,90 (pretty) mom0 without options=double,mosaic
+sigma_cont          = 5e-4
+sigma_line          = 1.03 # 1.365  # chan 65,85     #     1.0  # chan72,90
 sigma_SMA           = 0.000836951
 
 vla_min             = -0.000270099
@@ -38,7 +38,7 @@ SMA_max             = 0.00634805
 VLA_ra              = 1.448437499980E+02
 VLA_dec             = 8.325666666846E+01
 sizep               = 0.0025
-sizePcont_noise     = 0.012
+sizePcont_noise     = 0.020
 sizePLine           = 0.012
 ra_center           = 144.84933
 dec_center          = 83.257175
@@ -64,7 +64,7 @@ dy                  = 0.90
 
 fcont = aplpy.FITSFigure(label['cont'][0], \
         figure=fig, subplot=[x0,row_a,width,dy])
-fcont.show_colorscale(cmap=mpl.cm.jet, stretch='log', vmin=min_cont, vmax=max_cont, vmid=-0.8)
+fcont.show_colorscale(cmap=mpl.cm.jet, stretch='log', vmin=min_cont, vmax=max_cont, vmid=-100000)   # vmid= min_cont-0.0001 ~ orange; min_cont-0.0000001 ~ red
 
 fvla = aplpy.FITSFigure(label['VLA'][0], \
         figure=fig, subplot=[x0+width+2*x_gap, row_a, width, dy])
@@ -75,14 +75,14 @@ flin = aplpy.FITSFigure(label['lin'][0], \
         figure=fig_line, subplot=[x0,row_a,width,dy])
 flin.show_colorscale(cmap=mpl.cm.jet, vmin=min_line, vmax=max_line, vmid=-25, stretch='log')
 fSMA = aplpy.FITSFigure(label['SMA'][0], figure=fig_line, subplot=[x0+width+2*x_gap, row_a, width, dy])
-fSMA.show_grayscale(stretch='log', vmin=SMA_min, vmax=SMA_max, vmid=-0.05)
[…]

### 2015-07-31 Code/SEDfit.py

@@ -104,9 +104,9 @@ Core_3c220dot3_Jy = np.array([0.8e-3, 0.17e-3])     # Jy
 Core_3c220dot3_Hz = np.array([9.e9, 4.86e9])    # Hz
 
 # Our Data: [peak, integrated, difference]
-Point_Continuum_Jy = np.array([5.18e-3, 9.46e-3, 4.28e-3])
+Point_Continuum_Jy = np.array([4.93e-3, 7.53e-3, 2.60e-3])
 Point_Cont_Hz = np.array([1.042e11, 1.042e11, 1.02e11])     # Hz
-Point_error_Jy = np.array([0.24e-3, 0.364e-3, 0.88e-3])    # Jy
+Point_error_Jy = np.array([0.31e-3, 1.42e-3, 1.45e-3])    # Jy
 
 
 ########################################

### 2015-08-19 Code/SED_fittingparamPlot.py
modified font size for publication

@@ -13,11 +13,11 @@ Look at resulting fits from mbb_emcee
 plot probabilities of parameters
 """
 # matplotlib.rc('text', usetex=True)
-matplotlib.rc('xtick', labelsize=12)
-matplotlib.rc('ytick', labelsize=12)
+matplotlib.rc('xtick', labelsize=18)
+matplotlib.rc('ytick', labelsize=18)
 font = {'family': 'Arial Narrow',
         'weight': 'bold',
-        'size': 13}
+        'size': 15}
 matplotlib.rc('font', **font)
 # monospace sans-serif
 axes = {
@@ -437,7 +437,7 @@ def makesubplot2d(ax, samples1, samples2, color=True, weights=None, smooth=True,
                            interpolation='gaussian', norm=matplotlib.colors.LogNorm())
         else:
             c2 = ax.imshow(np.flipud(hist2d.T), extent=extent, aspect=ax.get_aspect(),
-                           interpolation='gaussian')
+                           interpolation='gaussian', alpha=0.8)
 
     if logx:
         ax.set_xscale('log')
@@ -552,7 +552,7 @@ def triplot(chain, color=True, weights=None, interpolate=False, smooth=True,
             if jj == len(parameters) - 1:
                 axarr[jj][ii].xaxis.set_major_formatter(xmajorFormatter)
                 if labels:
-                    axarr[jj][ii].set_xlabel(labels[ii])
+                    axarr[jj][ii].set_xlabel(labels[ii], labelpad=10)
 
             if ii == 0:
                 if jj == 0:
@@ -561,18 +561,19 @@ def triplot(chain, color=True, weights=None, interpolate=False, smooth=True,
                 else:
                     axarr[jj][ii].yaxis.set_major_formatter(ymajorFormatter)
                     if labels:
-                        axarr[jj][ii].set_ylabel(labels[jj])
+                        axarr[jj][ii].set_ylabel(labels[jj], labelpad=10)
 
     # overall plot title
     if title:
-        f.suptitle(title, fontsize=14, y=0.90)
+        f.suptitle(title, fontsize=22, y=0.90)
 
     # make plots closer together
     f.subplots_adjust(hspace=0.1)
     f.subplots_adjust(wspace=0.1)
     if saveFig == True:
         outfile = 'CorrelationPlot__'
-        savefig('../Figure/' + outfile + filename.replace('.h5', '.png'), dvi=600)
[…]

### 2015-08-19 Code/Plot_Image.py
change plot setting for paper

@@ -139,10 +139,11 @@ markers_cross(fSMA, ra_cross, dec_cross, layer='marker_set_1')
 ########################################
 # Labels
 ########################################
-put_label(fvla, 0.18, 0.93, 'VLA 9GHz', 'titleBand')
+put_label(fvla, 0.40, 0.93, 'VLA 9GHz, CARMA 104GHz', 'titleBand')
 put_label(fvla, 0.17, 0.87, '3C220.3', 'titleObj')
-put_label(fcont, 0.31, 0.90, 'CARMA 104GHz', 'titleBand', c='orangered')
-put_label(fcont, 0.2625, 0.85, '3C220.3', 'titleObj', c='orangered')
+put_label(fcont, 0.31, 0.90, 'CARMA 104GHz', 'titleBand', c='black', w=
+'heavy')
+put_label(fcont, 0.2625, 0.85, '3C220.3', 'titleObj', c='black', w='extra bold')
 put_label(flin, 0.31, 0.93, 'CARMA CO(3-2)', 'titleBand', c='black')
 put_label(flin, 0.31, 0.87, 'SMM J0939+8315', 'titleObj', c='black')
 put_label(fSMA, 0.40, 0.935, 'SMA 1 mm, CARMA CO(3-2)', 'titleBand')

### 2015-08-20 skeleton.tex
Edit since DR comments on July31 version

@@
 \documentclass[twocolumn,apj,numberedappendix]{emulateapj}
-\usepackage{hyperref}
+\usepackage[breaklinks,colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
 \newcommand{\vdag}{(v)^\dagger}
@@
 \newcommand{\LpU}{\mbox{K\,\,km\,\,s$^{-1}$\,\,pc$^2$}}
-%\newcommand{\eg}{{\sl e.g.,}}
 \newcommand{\eg}{{\sl e.g.,~}}
@@
 the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
-The underlying continuum emission toward the foreground radio galaxy 3C220.3, at $z$ = 0.685, is detected with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy. 
+The radio galaxy 3C220.3 at $z$ = 0.685 acts as a gravitational lens of this SMG, which hosts a type-2 quasar.
+The underlying 104 GHz continuum emission toward 3C220.3 is detected with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy.
 Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (10.1\,$\pm$\,1.3)\,Jy\,km\,s\pmOne, we derive
- a lensing- and excitation-corrected CO line luminosity of \Lp = (2.7\,$\pm$\,0.6) $\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling performed on the archival 1\,mm continuum emission.
- This translates to a molecular gas mass of $M_\textrm{gas}$\,=\,(2.3\,$\pm$\,0.5)\,$\times$\,10$^{10}$\,\Msun. 
-Fitting the spectral energy distribution (SED) models to the (sub)-millimeter data of this SMG yields a rest-frame dust temperature of $T_\textrm{dust}$ = 
-63.1$^{+1.1}_{-1.3}$\,K, a dust mass of $M_\textrm{dust}$ = (5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,\Msun, and a total infrared luminosity of 
-$L_\textrm{IR}$ = (9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,\Lsun, after correcting for lensing magnification.
+ a lensing- and excitation-corrected CO line luminosity of \Lp = (2.7\,$\pm$\,0.6) $\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling performed on the 1\,mm continuum emission.
+ This translates to a molecular gas mass of $M_\textrm{gas}$ = (2.2\,$\pm$\,0.5)\,$\times$\,10$^{10}$\,\Msun.
+Fitting spectral energy distribution models to the (sub)-millimeter data of this SMG yields a dust temperature of $T_\textrm{dust}$ =
+63.1$^{+1.1}_{-1.3}$\,K, a dust mass of $M_\textrm{dust}$ = (5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,(10.1/$\mu_\textrm{L}$)\,\Msun, and a total infrared luminosity of
+$L_\textrm{IR}$ = (9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,(10.1/$\mu_\textrm{L}$)\,\Lsun.
 Our comparative study
-of the intrinsic properties (\eg gas mass, dust mass, star formation rate, and surface densities) in SMM
+of the gas mass, dust mass, star formation rate, and surface densities in SMM
 J0939+8315
 and other high-redshift SMGs and type-2 quasars shows that SMM\,J0939+8315 is a faithful representation of both populations, suggesting that
-SMM\,J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase in the currently favored evolutionary link model.
+SMM\,J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase.
 \end{abstract}
@@
 In the past $\sim$\,5~years, considerable amounts of effort have been invested into follow-up observations of SMGs that were
-discovered in large sky surveys \citep[\eg H-ATLAS, HerMES; ][]{Eales10a,Oliver12a}, conducted using (sub)-mm facilities.
+discovered in large sky surveys \citep[\eg H-ATLAS, HerMES, SPT; ][]{Eales10a,Oliver12a,Vieira10a}, conducted using (sub)-mm facilities.
 These detailed studies have led to growing consensus that SMGs are a population of high-redshift galaxies that are extremely dusty, gas-rich,
-  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) at the infrared wavebands, with high star formation rates \citep[$\gtrsim $ 500 \Msun yr\pmOne; \eg][]{Lagache05a}.
+  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) at the infrared wavebands, with high star formation rates \citep[$\gtrsim $ 500 \Msun yr\pmOne; \eg][]{Lagache05a,Casey14a}.
 
-  To characterize the physical properties of the gas reservoirs in the interstellar medium (ISM) where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[See \eg][]{Carilli13a}.
+  To characterize the physical properties of the gas reservoirs in the interstellar medium (ISM) where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[See \eg][]{Solomon05a,Carilli13a}.
 Recent observations of CO in SMGs at $z$\,$\sim$\,1\,--\,3 have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Riechers11c,Riechers11d,Ivison11a,Bothwell13a}.
 
-Many recent follow-up observations and thus detailed studies are carried out on SMGs that are gravitationally lensed,
- as lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a,Oliver12a}, and allowing observations to be carried out in a timely-manner.
-A particularly interesting and peculiar lensing system was discovered serendipitously in a sky survey carried out with the {\it Herschel Space Telescope}, in which 
+Many recent detailed studies have been carried out on SMGs that are gravitationally lensed,
+ as lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a,Oliver12a}, and making follow-up studies considerably less time consuming.
+A particularly interesting and peculiar lensing system was discovered serendipitously in a study carried out with the {\it Herschel Space Telescope}, in which
 a type-2 quasar host SMG --- SMM\,J0939+8315 (hereafter SMM\,J0939) is being lensed by the double-lobed Fanaroff-Riley
@@
 SMM\,J0939 is currently one of the brightest known lensed
-SMGs, with a lensing-magnified flux density of $S_\textrm{250\micron m}$\,=\,440\,$\pm$\,15 mJy. 
-Previous detections of CIV\,1459\AA\
- and HeII\,1640\AA\ line emission toward SMM\,J0939 
- placed the redshift of this galaxy at $z$\,=\,2.221, and suggested the presence of a type-2 quasar,  
-indicating active galactic nucleus (AGN) activity in this SMG \citep[hereafter H14]{Haas14}.
+SMGs, with a lensing-magnified flux density of $S_\textrm{250\micron}$\,=\,440\,$\pm$\,15 mJy.
+Previous detections of C{\scriptsize\sc IV}\,1459\AA\
+ and He{\scriptsize\sc II}\,1640\AA\ line emission toward SMM\,J0939
+ placed the redshift of this galaxy at $z$\,=\,2.221, and suggested the presence of an active galactic nucleus (AGN),
+indicating a type-2 quasar in this SMG \citep[hereafter H14]{Haas14}.
 
@@
 Array for Research in Millimeter Astronomy (CARMA), which refines the redshift, and permits the study of the physical conditions in the ISM of SMM\,J0939 in great detail.
-We report the detection of the underlying continuum emission and place constraints on the spectral energy distribution (SED) of the foreground FR-II galaxy at mm wavelength ($\sim$\,104 GHz).
-Based on the magnification factor derived from our lens model, we infer intrinsic properties of SMM\,J0939 and thereby
+We report the detection of the underlying continuum emission and place constraints on the spectral energy distribution (SED) of the foreground FR-II galaxy at millimeter (mm) wavelengths ($\sim$\,104 GHz).
+Based on the magnification factor derived from our lens model, we infer various intrinsic properties of SMM\,J0939.
+We
 conclude this paper by comparing our findings to other similarly bright, strongly-lensed SMGs, as well as other type-2 quasars at $z$\,$\sim$\,2 .
 
-We adopt a flat $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km\,\,Mpc\pmOne\,\,s\pmOne, $\Omega_\textrm{M}$\,=\,0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
+We adopt a flat $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km\,\,Mpc\pmOne\,\,s\pmOne, $\Omega_\textrm{M}$\,=\,0.286, $\Omega_\Lambda$=0.713, based on the WMAP9 results \citep{Hinshaw13a}.
 The luminosity distances at $z$\,=\,0.685 and $z$\,=\,2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
@@
 Observations of the \CO rotational transition ($\nu_\textrm{rest}$\,=\,345.7959899 GHz) toward the background galaxy SMM
-J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; PI: Riechers).
-The 3\,mm receivers were used to cover the redshifted \CO line and the nearby 2.88\,mm continuum emission.
-The correlators were configured to provide a bandwidth of 3.75 GHz in each sideband, and a spectral resolution of 5.208 MHz ($\sim$\,14.5 km\,\,s\pmOne).
+J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{\textrm obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; PI: Riechers).
+The 3\,mm receivers were used to cover the redshifted \CO line and the nearby observed-frame 2.88\,mm continuum emission.
+The correlator was configured to provide a bandwidth of 3.75 GHz in each sideband, and a spectral resolution of 5.208 MHz ($\sim$\,14.5 km\,\,s\pmOne).
 The line was placed in the
@@
 The continuum image is created by
-averaging over all line-free channels, this yields a synthesized clean beam of 12\farcs0\,$\times$\,6\farcs5, $-$55.9$\degr$ east of north, and an rms noise of $\sigma_\textrm{cont}$ = 0.50\,\,mJy\,\,beam\pmOne.
+averaging over all line-free channels, this yields a synthesized clean beam of 12\farcs0\,$\times$\,6\farcs5, $-$55.9$\degr$ east of north, and an rms noise of $\sigma_\textrm{cont}$ = 0.50\,\,mJy\,\,beam\pmOne over 7.BLAH GHz
 
@@
 \subsection{New Results: 3C220.3}
-Averaging over all line-free channels, we detect $\sim$\,9$\sigma$ continuum emission at an averaged frequency of $\nu_{cont}$\,=\,104.2106 GHz ($\sim$\,2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$\,1.7 mm) at $z$\,=\,0.685.
+Averaging over all line-free channels, we detect continuum emission at $\sim$\,9$\sigma$ at an averaged frequency of $\nu_{\textrm cont}$\,=\,104.2106 GHz ($\sim$\,2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$\,1.7 mm) at $z$\,=\,0.685.
 In this lensing system, the
-foreground galaxy (3C220.3) is radio-loud, we thus expect it to be the dominant source of the continuum emission (see \S \ref{sec:SEDFg} for details).
+foreground galaxy (3C220.3) is radio-loud, we thus expect it to be the dominant contributor to the continuum emission (see \S \ref{sec:SEDFg} for details).
 The task {\sc imfit} is used to estimate the peak position of the continuum emission, where the flux density is S$_\nu$\,=\,4.93\,$\pm$\,0.31\,\,mJy\,\,beam\pmOne.
@@
 density of the measured continuum. We discuss this further in Section \ref{sec:SEDFg}. \par
-The frequency range of our observations covers the HCO$^+$(2\,\rarr\,1), HNC($J$\,=\,2\,$\rightarrow$\,1), and H$_2$O(3$_{13}$\,\rarr\,2$_{20}$) 
+The frequency range of our observations covers the HCO$^+$($J$\,=\,2\,\rarr\,1), HNC($J$\,=\,2\,$\rightarrow$\,1), and H$_2$O(3$_{13}$\,\rarr\,2$_{20}$)
 transition line emission in the foreground galaxy, at
@@
 We detect \CO line emission at $\sim$\,8$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
-The spatial extent of this SMG is $\sim$\,5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum in Figure~\ref{fig:mom0}; as such, 
+The lensing-magnified spatial extent of this SMG is $\sim$\,5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum image in Figure~\ref{fig:mom0} (H14); as such,
 the detected \CO line emission is spatially unresolved. We therefore extract the line profile (Figure~\ref{fig:mom0}) at the peak position of the unresolved
 CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.61\,$\pm$\,2.66\,\,mJy, superimposed on a
-continuum level of 4.15\,$\pm$\,0.48\,\,mJy, and a full width at half-maximum (FWHM) line width of 546\,$\pm$\,36\,\,km\,\,s\pmOne.  \par
+continuum level of 4.15\,$\pm$\,0.48\,\,mJy beam\pmOne, and a line full width at half-maximum (FWHM) of 546\,$\pm$\,36\,\,km\,\,s\pmOne.  \par
 We construct a velocity-integrated (0th moment) map of the \CO line
@@
 The
-solid black line shows the Gaussian fit to the \CO line profile, and the yellow histogram shows the 
-flux density as a function of velocity offset, where the velocity scale is relative to $z$\,=\,2.221. 
+solid black line shows a Gaussian fit to the \CO line profile, and the yellow histogram shows the
+line emission, where the velocity scale is relative to $z$\,=\,2.221.
 \label{fig:mom0}}
@@
 To study the intrinsic properties of the background galaxy, we determine the magnification factor by performing
-lens modeling on the SMA 1\,mm archival data of this system. Lens modeling is carried out in the visibility
-({\it uv-}) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}\footnote{https://github.com/sbussmann/uvmcmcfit}
+lens modeling on the SMA 1\,mm continuum data presented by H14 of this system. Lens modeling is carried out in the visibility
+({\it uv-}) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}\footnote{\url{https://github.com/sbussmann/uvmcmcfit}}
 \citep{Bussmann15a}. The code uses an affine-invariant Markov chain Monte Carlo (MCMC) approach to sample the posterior
@@
 We fix the phase center to coordinates ($\alpha$,\,$\delta$)\,\,(J2000) = (9:39:23.54,\,\,83:15:26.10), where the
-angular offsets of the lenses and source are referenced to this phase center. The primary lens (3C220.3) is
+angular offsets of the lenses and source are referenced to this position. The primary lens (3C220.3) is
 described by five free parameters: the angular offset relative to
@@
 The contours start at $\pm$2$\sigma$, incrementing at
-steps of $\pm$2$\sqrt{\rm 2}\sigma$. Solid contours show the positive residuals and dashed contours
-show the negative residuals. 
+steps of $\pm$2$\sqrt{\rm 2}\sigma$.
 Left: SMA 1\,mm continuum (red contours) overlaid on the best-fit model (grayscale image) assuming an elliptical Gaussian profile for the background SMG.
 The lenses are represented as black dots, the half-light area of the background source is represented as magenta ellipse, and the critical curves are represented as orange curves.
-Right: Residual contours and image obtained by taking the Fourier transform of the difference between the SMA data and the best-fit model in the visibility plane. \label{fig:lens}}
+Right: Residual contours and image obtained by taking the Fourier transform of the difference between the SMA data and the best-fit model in the visibility plane.
+Solid contours show the positive residuals and dashed contours
+show the negative residuals.
+\label{fig:lens}}
 \end{figure}
@@
 The extrapolated flux density at 104\,\,GHz is consistent with the peak flux density of our continuum
-measurement (Figure~\ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests
+measurement (Figure~\ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests a
 dominant contribution from the lobes, and that the peak flux density does not correspond to emission toward
@@
 The dashed purple line and
-the solid cyan line correspond to the best-fit SED models of SMM\,J0939, using the photometric data from H14. \label{fig:SED}}
+the solid cyan line correspond to the best-fit optically thick and optically thin models of SMM\,J0939, respectively, using the photometric data from H14. \label{fig:SED}}
 \end{figure}
@@
 \subsubsection{SMM\,J0939+8315} \label{sec:SEDBg}
-To constrain the dust and gas properties in the ISM of SMM\,J0939, we perform the SED fitting to the
+To constrain the dust and gas properties in the ISM of SMM\,J0939, we perform SED fitting to the
 photometric data obtained with {\it Herschel}/PACS and SPIRE, at wavelengths
 between observed-frame 70\,\micron\,$-$\,500\,\micron, and the interferometric data obtained with the SMA at 1\,mm (H14). We use the publicly
-available software {\sc mbb\_emcee}\footnote{https://github.com/aconley/mbb\_emcee} to perform the SED fitting; the code uses an affine-invariant Markov chain Monte
+available software {\sc mbb\_emcee}\footnote{\url{https://github.com/aconley/mbb\_emcee}} to perform the SED fitting; the code uses an affine-invariant Markov chain Monte
 Carlo (MCMC) approach, and further details of the code are given by \citet{Riechers13a} and \citet{Dowell14a}. \par
@@
 where $S_{\nu}$ is the flux density in erg\,s\pmOne\,cm$^{-2}$\,Hz\pmOne, $D_\textrm{L}$ is the luminosity distance in cm, $\kappa_{\nu}$ is the dust
-absorption coefficient in cm$^2$\,g\pmOne, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function in units of erg\,s\pmOne\,cm$^{-2}$\,Hz\pmOne,
+absorption coefficient in cm$^2$\,g\pmOne, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function in units of erg\,s\pmOne\,cm$^{-2}$\,Hz\pmOne;
 all quantities are expressed in the observed-frame.
@@
  ground state transition line is redshifted to lower frequencies that can only be observed with a few telescopes
- \citep{Carilli13a}. Consequently, assumptions on the CO excitation conditions are required to derive the molecular gas mass using the H$_\textrm{2}$-to-CO 
- relation. \par
+ \citep{Carilli13a}. Consequently, assumptions on the CO excitation conditions are required to derive the molecular gas mass using the M(H$_\textrm{2}$)-to-$L^{\prime}_\textrm{CO}$
+ conversion factor from BLAH. \par
 Prior to the observations of the ground state CO transition line in SMGs, it has been assumed that the molecular gas in the
@@
    {Harris10a,Carilli10a,Swinbank2010a,Ivison10d,Ivison11a,Riechers11d}. In contrast, similar observations in high-redshift quasar hosts suggest that the ratio
-   is $R_\textrm{31}$\,$\sim$\,1 \citep{Riechers06a, Riechers11a, Scott11a}.
+   is $R_\textrm{31}$\,$\sim$\,1 \citep{Riechers06a, Riechers11a}.
 In the case of high-redshift type-2 quasars, \citet{Riechers11a} report a brightness temperature ratio of $R_\textrm{31}$ = 1.00\,$\pm$\,0.10 for IRAS F10214+4724 (hereafter F10214), which is currently the only known type-2 quasar with both \CO and CO($J$\,=\,1\,\rarr\,0) line measurements.
@@
 \ie we adopt $R_\textrm{31}$\,=\,1, as SMM\,J0939 is
-postulated to be hosting a type-2 quasar. 
-We calculate the CO($J$\,=\,1\rarr0) line luminosity using standard relation 
+postulated to be hosting a type-2 quasar (H14).
+We calculate the CO($J$\,=\,1\rarr\,0) line luminosity using standard relation
 \citep[\eg][]{Solomon05a,Carilli13a}:
@@
 This results in a gas-to-dust
-ratio of $f_\textrm{gas-dust}$\,=\,$M_\textrm{gas}/M_\textrm{dust}$\,=\,44\,$\pm$\,21, in good agreement with the 
-values found in other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.
+ratio of $f_\textrm{gas-dust}$\,=\,$M_\textrm{gas}/M_\textrm{dust}$\,=\,44\,$\pm$\,21.
+We note that a factor of $\sim$\,2 uncertainty arises from the dust mass estimate.
+The derived gas-to-dust ratio is in good agreement with the
+values found in other SMGs within the uncertainties \citep{Coppin08a,Micha10a,Riechers11c}.
 
@@
 %No strong evidence of a hot dust bump is found in SMM\,J0939 based on the mid-IR (WAIT, BUT ONLY HAVE 70 micron onwards) continuum measurements (see Figure~\ref{fig:SED}), hence
-We derive the star formation rate (SFR) assuming the dominant IR heating mechanism is from young and massive stars, and ignoring contribution from the 
+We derive the star formation rate (SFR) assuming the dominant IR heating source is due to young and massive stars, and ignoring a contribution from the
 dust-enshrouded AGN.
-Using the \citet{Kennicutt98a} relation and assuming the \citet{Chabrier03a}
-stellar initial mass (IMF) function\footnote{SFR$_\textrm{FIR}$\,=\,526\,$\pm$\,73 $M_
-\odot$ yr\pmOne\ using FIR luminosity},
-we derive a SFR$_\textrm{IR}$ of 874\,$\pm$\,122 $M\sun$\,\,yr\pmOne, employing the lensing-corrected bolometric IR luminosity.
-Assuming constant SFR, the time for which the starburst in SMM\,J0939 can be maintained at its
-current rate can be approximated as the gas depletion timescale, $\tau_\textrm{depl}$\,=\,$M_\textrm{gas}$/SFR. 
+Using the \citet{Kennicutt98a} relation and assuming a \citet{Chabrier03a}
+stellar initial mass (IMF) function\footnote{The SFR would be SFR$_\textrm{FIR}$\,=\,526\,$\pm$\,73 $M_
+\odot$ yr\pmOne\ if we were to use only the FIR luminosity},
+we derive a SFR$_\textrm{IR}$ of 874\,$\pm$\,122 $M\sun$\,\,yr\pmOne, employing the lensing-corrected total IR luminosity.
+The starburst in SMM\,J0939 can be maintained at its
+current rate for a time that can be approximated by the gas depletion timescale, $\tau_\textrm{depl}$\,=\,$M_\textrm{gas}$/SFR.
 This corresponds to $\tau_\textrm{depl}$\,=\,25.1\,$\pm$\,0.4 Myr, which is in good agreement with that found in other SMGs \citep[\eg][]{Greve05a}.
@@
 luminosity and CO luminosity, i.e., SFE\,=\,$L_\textrm{IR}$/\Lp. This makes no assumptions on the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$) as well as the
-choice of IMF; however, this assumes that differential lensing effect between the CO and infrared emission is negligible. 
-The resulting ratio is SFE$_\textrm{IR}$\,=\,319\,$\pm$\,9\,\,\Lsun\,(\LpU)$^{-1}$, this is comparable
+choice of IMF; however, this assumes that differential lensing between the CO and infrared emission is negligible.
+The resulting ratio is SFE$_\textrm{IR}$\,=\,319\,$\pm$\,35\,\,\Lsun\,(\LpU)$^{-1}$, this is comparable
 to what is found in ``typical" SMGs \citep{Greve05a,Tacconi06a,Riechers11c}.
@@
 \subsubsection{Dynamical Mass}
-Based on our \CO line measurement, we estimate the dynamical mass of SMM\,J0939 assuming the molecular gas is virialized.
+Based on our \CO line measurement, we estimate the dynamical mass of SMM\,J0939 assuming that the molecular gas is virialized.
 With this assumption, we use an isotropic virial estimator \citep[\eg][]{Engel10a}:
@@
 and the half-light radius from our lens model for $R_\textrm{eff}$, assuming that the dust emission traces the same emitting region as the CO.
+We note that a derived dynamical mass based on this assumption is likely to be biased low as the CO emitting region, in most cases, is spatially more extended than the dust emitting region \citep[\eg][]{Tacconi06a}.
+% 
 The inferred dynamical mass is $M_\textrm{dyn}$ = (7.5\,$\pm$\,2.4)\,$\times$\,10$^{10}$\,\Msun, and the gas-to-dynamical mass fraction is $f_\textrm{gas-to-dyn}$ = 0.29\,$\pm$\,0.12, consistent with that of other SMGs \citep{Tacconi06a}.
@@
 galaxies
-out to $z$\,$\sim$\,2.5, and assuming Chabrier IMF.
+out to $z$\,$\sim$\,2.5, and assuming a Chabrier IMF.
 
@@
 We present the detection of \CO line emission toward SMM\,J0939+8315, a strongly-lensed SMG that is hosting a type-2 quasar, refining the redshift
-to $z$\,=\,2.2212\,$\pm$\,0.0010. The underlying continuum is detected at $\sim$\,9$\sigma$ significance, where the flux density is most likely to be 
-dominated by emission from the lobes and hotspot of the foreground radio galaxy 3C220.3, thus an upper limit of $S_\nu$ $<$ 2.60 mJy is 
-placed on the compact core component.
+to $z$\,=\,2.2212\,$\pm$\,0.0010.
+The underlying continuum is detected at $\sim$\,9$\sigma$ significance, where the flux density is likely dominated by emission from the lobes and hotspot of the foreground radio galaxy 3C220.3.
 
@@
 which is consistent with the short timescale found in SMGs \citep{Greve05a}.
-The derived intrinsic properties of SMM\,J0399 are evident of ongoing rapid star formation; this is in good agreement with the current conjecture that SMGs are a
-population of high-redshift galaxies that build up most of the stellar mass in the early universe, thus play an important role 
-in galaxy formation and evolution \citep[\eg ][]{Micha10a}.
+The derived intrinsic properties of SMM\,J0939 are evident of ongoing rapid star formation; this is in good agreement with the current conjecture that SMGs are a %stellar mass assembly in galaxies
+population of high-redshift galaxies that build up the stellar bulk of present-day galaxies, thus play an important role
+in galaxy formation and evolution \citep[\eg ][]{Dickinson03a}.
 
@@
 cosmic
-Eyelash. Such distinction is likely a result of our selection bias, while these sources appear similarly bright at 250 \micron, their lensing factors 
+Eyelash. Such distinction is likely a result of our selection bias: while these sources appear similarly bright at 250 \micron, their lensing factors
 vary by a factor of $\sim$\,3. In particular, with the cosmic Eyelash having the highest lensing magnification among the
@@
 This demonstrates
-the large variations in gas mass, dust mass, thus star forming activity within the population at $z$\,$\sim$\,2, which is discernible only
- with the aid of gravitational lensing. 
+the large variations in gas mass, dust mass, thus star forming activity within the population at $z$\,$\sim$\,2, which is discernible with the aid of gravitational lensing.
 While lensing can probe sources
@@
 against those of eight CO-detected obscured AGNs at $z$ = 1.6\,--\,2.8, using the averaged values reported by \citet[][and references
-therein]{Polletta11a}. We caution that the detected CO 
-transition line varies across each source, 
-hence inducing high systematic uncertainties in the reported values. 
-In contrast with what was found for F10214, one of the eight sources in their sample with the lowest SFR and gas mass (derived using CO($J$\,=\,4\,\rarr\,3) line emission), we find that the properties
-(\eg FWHM line width of the CO transition line profile, M$_\textrm{gas}$, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a 
+therein]{Polletta11a}. %P11 Mgas from the lowest CO line, but cited 4-3 line width and intensity, etc in Table 2
+% some mysterious SFE 
+In contrast with what was found for F10214, one of the eight sources in their sample with the lowest molecular gas mass and SFR, we find that the properties
+(\eg FWHM of CO line profile \footnote{The statistical mean in \citet{Polletta11a} is based on the line profile of the CO transition closest to $J$ = 4\,\rarr\,3}, M$_\textrm{gas}$\footnote{The molecular gas mass for each source is derived based on its lowest-$J$ CO line emission available in literature}, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a
 factor of $\sim$\,1.5, is nevertheless consistent within the measurement uncertainties.
-The fact that the gas mass of F10214 in their compilation was derived using CO($J$\,=\,4\,\rarr\,3) line emission has minor effect on the resulting low gas mass, \citet{Riechers11a} report a similarly low gas mass derived using their CO($J$\,=\,1\rarr0) line measurement.
+The fact that the gas mass of F10214 in their compilation was derived using \CO line emission \citep{Solomon05a} has minor effect on the resulting low gas mass; \citet{Riechers11a} report a similarly low gas mass derived using their CO($J$\,=\,1\,\rarr\,0) line measurement.
+The molecular gas mass and SFR of F10214 is the lowest among high-redshift type-2 quasars due to the high magnification factor of $\mu_{\textrm L}$ = 17 \citep{Solomon05a} as well as its intrinsically gas poorer nature.
 This demonstrates that despite the variations in the intrinsic properties among lensed sources,
@@
 breaking up its dust cocoon (H14) while undergoing prodigious star-formation (SFR\,$\sim$\,874 \Msun~yr\pmOne).
-This scenario is consistent with the proposed evolutionary phase model \citep{Coppin08a,Simpson12a}, whereby SMM\,J0939 is transitioning from its star-bursting phase to the unobscured quasar phase.
+This scenario is consistent with the proposed evolutionary phase model \citep{Sanders88,Coppin08a,Simpson12a}, whereby SMM\,J0939 is transitioning from its star-bursting phase to the unobscured quasar phase.
 
 \acknowledgments
-We thank Shane Bussmann for providing the code {\sc uvmcmcfit} for lens modeling, and helpful discussions; Alex Conley for providing the code {\sc mbb\_emcee} for SED fitting.
-We acknowledge the WENSS team for providing the radio measurements for 3C220.3.
-Facilities: \facility{CARMA}
+We thank Shane Bussmann for providing the code {\sc uvmcmcfit} for lens modeling, sharing the SMA and VLA data, and for helpful discussions; Alex Conley for providing the code {\sc mbb\_emcee} for SED fitting.
+%We acknowledge the WENSS team for providing the radio measurements for 3C220.3.
+Support for CARMA construction was derived from the
+Gordon and Betty Moore Foundation, the Kenneth T. and Eileen
+L. Norris Foundation, the James S. McDonnell Foundation, the
+Associates of the California Institute of Technology, the University
+of Chicago, the states of Illinois, California, and Maryland,
+and the National Science Foundation. 
+(REMOVE?)Ongoing CARMA development
+and operations are supported by the National Science
+Foundation under a cooperative agreement, and by the CARMA
+consortium universities.
+%Facilities: \facility{CARMA}
 \newpage
@@
 
-As shown in the figure, the PDF of each parameter in the optically thin model is Gaussian distributed, and 
+As shown in the figure, the marginalized PDF of each parameter in the optically thin model is Gaussian, and
 the dust emissivity index ($\beta$) is highly anti-correlated with the observed-frame dust temperature ($T/(1+z)$).
-We note that the best-fit emissivity in this model is unusually low for high redshift galaxies ($\beta$ = 0.7$^{+0.2}_{-0.3}$, cf.
+We note that the best-fit emissivity in this model is unusually low among high redshift galaxies ($\beta$ = 0.7$^{+0.2}_{-0.3}$, cf.
 1$-$2.5; \eg \citet{Casey12a} and references therein).
 While this directly affects the slope of the Rayleigh-Jeans tail of the modified blackbody function, such low emissivity has insignificant impact on the inferred IR luminosity.
-We also find no evidence of correlation between the inferred dust mass and IR luminosity, to wit, despite the factor of $\sim$\,2 difference
+We also find no evidence of correlation between the inferred dust mass and IR luminosity. Despite the factor of $\sim$\,2 difference
 in dust masses
@@
 
-A comparison of the reduced $\chi^2$ between the two models suggests that the optically thick model is superior than the optically thin model.
+A comparison of the reduced $\chi^2$ between the two models suggests that the optically thick model fit is superior to the optically thin model fit.
 In the preferred model, the marginalized PDF of the dust emissivity index is highly non-Gaussian, with noticeably broad distribution across
 the allowed range (upper limit: 2.2). We therefore fit a second optically thick model, changing the upper limit of $\beta$ to 3.0. The difference in each
-parameter of the best-fit solution between these two scenarios is within 3\%, whereas the dust mass is boosted by a factor of $\sim$\,2. This is 
+parameter of the best-fit solution between these two scenarios is less than 3\%, except for the dust mass, which is boosted by a factor of $\sim$\,2. This is
 unsurprising given the dearth of data in the FIR waveband, leading to a weakly constrained emissivity, and thus the inferred dust mass.
@@
 \centering
-\includegraphics[width=0.47\textwidth]{Figure/CorrelationPlot__thick_500_500}
-\includegraphics[width=0.47\textwidth]{Figure/CorrelationPlot__thin_testSMA}
+% minipage
+\begin{minipage}{0.5\textwidth}
+\hspace{-1cm}
+\includegraphics[width=1.15\textwidth]{Figure/CorrelationPlot__thick_500_500.pdf}
+\end{minipage}
+\hspace{-0.9cm}
+\begin{minipage}{0.5\textwidth}
+\includegraphics[width=1.15\textwidth]{Figure/CorrelationPlot__thin_testSMA.pdf}
+\end{minipage}
 \caption{Correlation plots from the fitted SEDs, using an optically thick
 model (left), and an optically thin model (right). Marginalized posterior probability
-distribution of each
-parameter is plotted on the diagonal axis of each panel, where the solid black vertical lines indicate the set of parameter values in the PDFs that maximizes the likelihood.
+distributions of each
+parameter are plotted on the diagonal axis of each panel, where the solid black vertical lines indicate the set of parameter values in the PDFs that maximizes the likelihood.
 The correlation plots between parameters are plotted as 2D histograms on the off-diagonals, where the black crosses denote the
-locations in the parameter space
-at which the most likely solution corresponds to.
+locations of the most likely solution in the parameter space. The solid, dashed, and dotted lines correspond to 1$\sigma$, 2$\sigma$, and $3\sigma$, respectively. 
 \label{fig:sedlikelihood}}

### 2015-08-20 Code/err.py

@@ -21,13 +21,16 @@ Mgas = 2.326e10    # with lensing correction
 
 #####################
 #####################
-sig_LprimeCO = (3.25e7 / freq_CO32**2 * dl**2 / (1+z)) * ((del_I/mu)**2 + (del_mu/mu**2*I_line)**2)**(.5)
-del_LprimeCO = 3.25e7 / freq_CO32**2 * dl**2 / (1+z) * ((del_I/mu) + (del_mu/mu**2*I_line))
+sig_LprimeCO = (3.25e7 / freq_CO32 ** 2 * dl ** 2 / (1 + z)) * \
+    ((del_I / mu) ** 2 + (del_mu / mu ** 2 * I_line) ** 2) ** (.5)
+del_LprimeCO = 3.25e7 / freq_CO32 ** 2 * dl ** 2 / \
+    (1 + z) * ((del_I / mu) + (del_mu / mu ** 2 * I_line))
 
-sig_LprimeCO_noMu = (3.25e7 / freq_CO32**2 * dl**2 / (1+z)) * (del_I/mu)
-del_LprimeCO_noMu = 3.25e7 / freq_CO32**2 * dl**2 / (1+z) * (del_I/mu)
+sig_LprimeCO_noMu = (3.25e7 / freq_CO32 ** 2 * dl ** 2 / (1 + z)) * (del_I)
+del_LprimeCO_noMu = 3.25e7 / freq_CO32 ** 2 * dl ** 2 / (1 + z) * (del_I)
 
-LprimCO_noMu = 3.25e7/freq_CO32**2 * dl**2 / (1+z) * I_line
+LprimCO_noMu = 3.25e7 / freq_CO32 ** 2 * dl ** 2 / (1 + z) * I_line
+#print str(LprimCO_noMu/1.e10) + '+/-' + str(sig_LprimeCO_noMu / 1.e10)
 
 sig_Mgas = alpha * sig_LprimeCO
 del_Mgas = alpha * del_LprimeCO
@@ -37,59 +40,71 @@ sig_Mgas_noMu = alpha * sig_LprimeCO_noMu
 del_Mgas_noMu = alpha * del_LprimeCO_noMu
 
 # With lensing correction, M_dust
-sig_Mdust = ((M_dust/mu**2 * del_mu)**2 + (sig_Mdust_noMu/mu)**2)**(.5)
[…]

### 2015-08-21 skeleton.tex
Revise for missing line flux, as well as lum_distance in paper, and rest freq, FWHM in err.py & numInput.yaml

@@
 the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
-The radio galaxy 3C220.3 at $z$ = 0.685 acts as a gravitational lens of this SMG, which hosts a type-2 quasar.
+This SMG, which hosts a type-2 quasar is gravitationally lensed by the radio galaxy 3C220.3 at $z$ = 0.685.
 The underlying 104 GHz continuum emission toward 3C220.3 is detected with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy.
-Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (10.1\,$\pm$\,1.3)\,Jy\,km\,s\pmOne, we derive
- a lensing- and excitation-corrected CO line luminosity of \Lp = (2.7\,$\pm$\,0.6) $\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling performed on the 1\,mm continuum emission.
- This translates to a molecular gas mass of $M_\textrm{gas}$ = (2.2\,$\pm$\,0.5)\,$\times$\,10$^{10}$\,\Msun.
+Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (12.6\,$\pm$\,2.0)\,Jy\,km\,s\pmOne, we derive
+ a lensing- and excitation-corrected CO line luminosity of \Lp = (3.4\,$\pm$\,0.7) $\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling performed on the 1\,mm continuum emission.
+ This translates to a molecular gas mass of $M_\textrm{gas}$ = (2.7\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,\Msun.
 Fitting spectral energy distribution models to the (sub)-millimeter data of this SMG yields a dust temperature of $T_\textrm{dust}$ =
@@
 
-  To characterize the physical properties of the gas reservoirs in the interstellar medium (ISM) where active star formation takes place, carbon monoxide (CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[See \eg][]{Solomon05a,Carilli13a}.
+  To characterize the physical properties of the gas reservoirs in the interstellar medium (ISM) where active star formation takes place, carbon monoxide ($^{12}$CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[See \eg][]{Solomon05a,Carilli13a}.
 Recent observations of CO in SMGs at $z$\,$\sim$\,1\,--\,3 have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Riechers11c,Riechers11d,Ivison11a,Bothwell13a}.
@@
 We adopt a flat $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km\,\,Mpc\pmOne\,\,s\pmOne, $\Omega_\textrm{M}$\,=\,0.286, $\Omega_\Lambda$=0.713, based on the WMAP9 results \citep{Hinshaw13a}.
-The luminosity distances at $z$\,=\,0.685 and $z$\,=\,2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
-corresponds to 8.406 kpc at $z$\,=\,2.221, and 7.169 kpc at $z$\,=\,0.685.
+The luminosity distances at $z$\,=\,0.685 and $z$\,=\,2.221 are 4214 Mpc and 18052 Mpc, respectively; 1$\arcsec$
+corresponds to 7.169 kpc at $z$\,=\,0.685, and 8.406 kpc at $z$\,=\,2.221.
 
@@
 Observations of the \CO rotational transition ($\nu_\textrm{rest}$\,=\,345.7959899 GHz) toward the background galaxy SMM
-J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{\textrm obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; PI: Riechers).
+J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{\rm obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; PI: Riechers).
 The 3\,mm receivers were used to cover the redshifted \CO line and the nearby observed-frame 2.88\,mm continuum emission.
-The correlator was configured to provide a bandwidth of 3.75 GHz in each sideband, and a spectral resolution of 5.208 MHz ($\sim$\,14.5 km\,\,s\pmOne).
+The correlator was configured to provide a bandwidth of 3.96 GHz in each sideband, and a spectral resolution of 5.208 MHz ($\sim$\,14.5 km\,\,s\pmOne).
+% each sideband 8 windows * 0.494792 GHz = 3.9583 before flagging edge channels
 The line was placed in the
@@
 $15\% calibration accuracy. \par
-We use the {\sc MIRIAD} package to calibrate and analyze the visibility data, which are deconvolved and imaged with ``natural" weighting.
+We use the {\sc miriad} package to calibrate and analyze the visibility data, which are deconvolved and imaged with ``natural" weighting.
 This yields a synthesized clean beam size of 11$\farcs$5\,$\times$\,6\farcs2, $-$56.1$\degr$ east of north for the upper sideband image cube and an rms noise of $\sigma_\textrm{ch}$\,=\,9.49\,\,mJy\,\,beam\pmOne\ per channel
@@
 The continuum image is created by
-averaging over all line-free channels, this yields a synthesized clean beam of 12\farcs0\,$\times$\,6\farcs5, $-$55.9$\degr$ east of north, and an rms noise of $\sigma_\textrm{cont}$ = 0.50\,\,mJy\,\,beam\pmOne over 7.BLAH GHz
-
+averaging over all line-free channels, this yields a synthesized clean beam of 12\farcs0\,$\times$\,6\farcs5, $-$55.9$\degr$ east of north, and an rms noise of $\sigma_\textrm{cont}$ = 0.50\,\,mJy\,\,beam\pmOne\ over 7.0 GHz.
+%6.968 GHz = (total(1520) - edge * 2 * nwin(16))*5.208 MHz - [linechannel (196 - 153) * (2 * 5.208MHz)]
 \section{Results}\label{sec:res}
@@
 \subsection{New Results: 3C220.3}
-Averaging over all line-free channels, we detect continuum emission at $\sim$\,9$\sigma$ at an averaged frequency of $\nu_{\textrm cont}$\,=\,104.2106 GHz ($\sim$\,2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$\,1.7 mm) at $z$\,=\,0.685.
+Averaging over all line-free channels, we detect continuum emission at $\sim$\,9$\sigma$ at an averaged frequency of $\nu_\textrm{cont}$\,=\,104.2106 GHz ($\sim$\,2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$\,1.7 mm) at $z$\,=\,0.685.
 In this lensing system, the
@@
 76$\degr$. The contour levels of the 104 GHz continuum emission start at $\pm$2$\sigma$, incrementing at steps
-of $\pm$2$\sigma$ of 0.5 mJy beam\pmOne; the contour levels of the 9 GHz continuum
+of $\pm$2$\sigma$, where $\sigma$ = 0.5 mJy beam\pmOne. The contour levels of the 9 GHz continuum
 emission start at $\pm$4$\sigma$, where $\sigma$\,=\,0.064 mJy beam\pmOne, and increment at steps of $\pm$2$^n\sigma$,
@@
 CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.61\,$\pm$\,2.66\,\,mJy, superimposed on a
-continuum level of 4.15\,$\pm$\,0.48\,\,mJy beam\pmOne, and a line full width at half-maximum (FWHM) of 546\,$\pm$\,36\,\,km\,\,s\pmOne.  \par
-We construct a velocity-integrated (0th moment) map of the \CO line
+continuum level of 4.15\,$\pm$\,0.48~mJy~beam\pmOne, and a line full width at half-maximum (FWHM) of 546\,$\pm$\,36\,\,km\,\,s\pmOne.  \par
+We construct a velocity-integrated (0$^\textrm{th}$ moment) map of the \CO line
 emission after subtracting continuum emission in the visibility plane.
-This results in a velocity-integrated \CO line flux of $I_\textrm{CO}$\,=\,10.1\,$\pm$\,1.3 Jy km\,\,s\pmOne\ over the velocity range of $\Delta v$\,$\sim$\,680 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration
+This results in a velocity-integrated \CO line flux of $I_\textrm{CO}$\,=\,12.6\,$\pm$\,2.0 Jy km\,\,s\pmOne\ over the velocity range of $\Delta v$\,$\sim$\,1420 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration
 uncertainty. Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.2212\,$\pm$\,0.0010.
@@
 in the bottom left corner.
-The central cross on each image corresponds to the same coordinates as in Figure~\ref{fig:cont}. The contour levels start at $\pm$3$\sigma$, incrementing at
+The central cross on each image corresponds to the same coordinates as in Figure~\ref{fig:cont}. The contour levels 
+in both images
+start at $\pm$3$\sigma$, incrementing at
 steps of $\pm$1$\sigma$.
@@
 The
-solid black line shows a Gaussian fit to the \CO line profile, and the yellow histogram shows the
-line emission, where the velocity scale is relative to $z$\,=\,2.221.
+solid black line shows a Gaussian fit to the \CO line profile, where the velocity scale is relative to $z$\,=\,2.221.
 \label{fig:mom0}}
@@
 angular offsets of the lenses and source are referenced to this position. The primary lens (3C220.3) is
-described by five free parameters: the angular offset relative to
-the chosen phase center in the image ($\Delta \alpha_{\rm
-lens0}$ and $\Delta \delta_\textrm{lens0}$), the angular Einstein radius ($\theta_\textrm{E0}$), the
+described by five free parameters: the angular offset ($\Delta \alpha_{\rm
+lens0}$ and $\Delta \delta_\textrm{lens0}$) relative to
+the chosen phase center ($\alpha$,\,$\delta$) in the image, the angular Einstein radius ($\theta_\textrm{E0}$), the
 axial ratio ($q_\textrm{lens0}$), and the position angle ($\phi_\textrm{lens0}$). The secondary lens (companion B) is
@@
 of the secondary
-lens is sampled with respect to ($\Delta \alpha_\textrm{lens0}$ and $\Delta \delta_\textrm{lens0}$) of
-the primary lens.
+lens is sampled with respect to that of
+the primary lens ($\Delta \alpha_\textrm{lens0}$ and $\Delta \delta_\textrm{lens0}$), we therefore do not consider ($\Delta \alpha_\textrm{lens1}$ and $\Delta \delta_\textrm{lens1}$)  as free parameters.
 The source (SMM\,J0939) is parameterized by
-six free parameters: the position of the source relative to the
+six parameters: the position of the source relative to the
 primary lens ($\Delta \alpha_\textrm{s}$ and $\Delta
@@
 ($\phi_\textrm{s}$).
-The total number of free parameters is $N_\textrm{free}$\,=\,14. The best-fit model is obtained by maximizing the
+%The total number of free parameters is $N_\textrm{free}$\,=\,14. 
+The best-fit model is obtained by maximizing the
 Gaussian likelihood function $ \mathcal{L} $ according to:
@@
 steps of $\pm$2$\sqrt{\rm 2}\sigma$.
-Left: SMA 1\,mm continuum (red contours) overlaid on the best-fit model (grayscale image) assuming an elliptical Gaussian profile for the background SMG.
+Left: SMA 1\,mm continuum (red contours) overlaid on the best-fit model (grayscale image), assuming an elliptical Gaussian profile for the background SMG.
 The lenses are represented as black dots, the half-light area of the background source is represented as magenta ellipse, and the critical curves are represented as orange curves.
 Right: Residual contours and image obtained by taking the Fourier transform of the difference between the SMA data and the best-fit model in the visibility plane.
-Solid contours show the positive residuals and dashed contours
-show the negative residuals.
-\label{fig:lens}}
+Solid (dashed) contours show the positive (negative) residuals.\label{fig:lens}}
 \end{figure}
@@
 parameters are listed in Table~\ref{tab:lensParam}.
-The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1\farcs22\,$\pm$\,0\farcs01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0\farcs75\,$\pm$\,0\farcs02 (5.34\,\,kpc at $z$\,=\,0.685),
+The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1\farcs22\,$\pm$\,0\farcs01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0\farcs75\,$\pm$\,0\farcs02 (5.34\,\,kpc at $z$\,=\,0.685), and
 the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
@@
 
-Previous studies of the core component of 3C220.3 have established upper
-limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a} and an unambiguous detection of 0.8 mJy at 9 GHz (H14), suggesting a substantially inverted spectrum of the core (Figure~\ref{fig:SED}).
+Previously,  an upper
+limit of $<$ 0.17 mJy at 4.6 GHz has been established by \citet{Mullin06a} on the core component of 3C220.3, and an unambiguous detection of 0.8 mJy at 9 GHz has been reported by H14, suggesting a substantially inverted spectrum of the core (Figure~\ref{fig:SED}).
 Consequently, we may naively expect the integrated flux density in our continuum detection of $S_\textrm{104GHz}$\,=\,7.39\,$\pm$\,1.42\,\,mJy to be dominated by the unresolved core component of the foreground FR-II galaxy, which is at $z$\,=\,0.685.
-However, the deconvolved spatial size of the source matching that in the resolved image (see Figure 1) is
+However, the deconvolved spatial size of the source matching that in the resolved image (see Figure~\ref{fig:cont}) is
 suggestive of a marginally resolved detection of the extended lobe components with non-negligible emission.
@@
 unity, and $\nu_c^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy
-distribution.
+distribution. %extrapolated flux density at 104 GHz: 5.10
 The extrapolated flux density at 104\,\,GHz is consistent with the peak flux density of our continuum
@@
 the core. Moreover, the peak position of the 104\,\,GHz continuum is
-centered toward the northern lobe (Figure~\ref{fig:cont}), which further supports our argument. We did not
+centered toward the northern lobe (Figure~\ref{fig:cont}), which further supports our argument. 
+Consequently, a conservative upper limit of $S_\nu$\,$<$\,4.93 mJy on the core emission can be established using the measured peak flux density. Yet, by considering the 
+difference between the integrated flux density and the extrapolated flux density of the lobes ($S_\textrm{104GHz}$ = 5.10 mJy), we establish a more stringent constrain on this upper limit of $S_\nu$\,$<$\,2.29 mJy.
+We did not
  extrapolate the core measurements to the frequency of our continuum, as previous measurements of the core are 
@@
  across different epochs. 
-Based on our argument, we place an upper limit of $S_\nu$\,$<$\,2.60 mJy on the core component using the difference between the integrated and the peak flux densities.
 \par
-Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, where some exhibit spectral steepening in cm and mm wavelengths (\eg 3C123).
+Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested that spectra of hotspots are flat up to optical frequencies, where some exhibit spectral steepening in cm and mm wavelengths (\eg 3C123).
 At the resolution of our observations, it is unclear whether the measured flux density is dominated by emission from the compact hotspot or that from the surrounding diffuse lobe components.
@@
 \end{equation}
-where $T$ is the rest-frame cold dust temperature, $\beta$ is the dust emissivity index (equivalently, the spectral index of the dust extinction
-curve), and $\alpha$ is the mid-infrared power law spectral index. The overall fit is normalized using the observed-frame 500
+where $T$ is the rest-frame cold dust temperature, $\beta$ is the dust emissivity index 
+%(equivalently, the spectral index of the dust extinction curve)
+, and $\alpha$ is the mid-infrared power law spectral index. The overall fit is normalized using the observed-frame 500
 $\micron$ flux density, hence this becomes an additional parameter in the fit.
-For both models, we impose an upper limit on the observed-frame dust temperature ($T/(1+z)$) to 60 K, and for the optically thick model, we impose an upper limit on $\lambda_0$ to 2000\,\,\micron.
-Additionally, we fix the upper limits on
-$\beta$ to be 3.0 and 2.2 for the optically thin model and optically thick model, respectively.
+For both models, we impose an upper limit of 60 K on the observed-frame dust temperature ($T/(1+z)$), an upper limit of 2.2 on
+$\beta$. For the optically thick model, we impose an additional upper limit of 2000\,\micron\ on $\lambda_0$.
 
@@
 case. In the subsequent analysis, we employ the inferred values from the optically thick model.
-The best-fit solution yields a FIR luminosity (rest-frame 42.5-122.5\micron) of $L_\textrm{FIR}$ = 53.3$^{+1.1}_{-1.1}$\,$\times$\,10$^{12}$\,\Lsun, and a total infrared (IR) luminosity of $L_\textrm{IR (8-1000 \micron)}$ = 88.5$^{+2.6}_{-2.6}$\,$\times$\,10$
+The best-fit solution yields a FIR luminosity (rest-frame 42.5$-$122.5\micron) of $L_\textrm{FIR}$ = 53.3$^{+1.1}_{-1.1}$\,$\times$\,10$^{12}$\,\Lsun, and a total infrared (IR; rest-frame 8$-$1000 \micron) luminosity of $L_\textrm{IR}$ = 88.5$^{+2.6}_{-2.6}$\,$\times$\,10$
 ^{12}$\,\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64\,\,m$^2$\,\,kg\pmOne\ at 125.0\,\,$
@@
 where $S_{\nu}$ is the flux density in erg\,s\pmOne\,cm$^{-2}$\,Hz\pmOne, $D_\textrm{L}$ is the luminosity distance in cm, $\kappa_{\nu}$ is the dust
-absorption coefficient in cm$^2$\,g\pmOne, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function in units of erg\,s\pmOne\,cm$^{-2}$\,Hz\pmOne;
+absorption coefficient in cm$^2$\,g\pmOne, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function in units of erg\,s\pmOne\,cm$^{-2}$\,Hz\pmOne\,sr\pmOne;
 all quantities are expressed in the observed-frame.
 We find a dust mass of $M_\textrm{dust}$ = 50.5$^{20.4}_{-20.2}\times$10$^8$\,\,\Msun, the uncertainties do not include those in the dust absorption coefficient ($\kappa_{\nu}$).
-These values are based on the SED fitting to the photometric data, \ie prior
+These properties are derived based on the SED fitting to the photometric data, \ie prior
 to lensing correction.
@@
 With the limited amount of data in the FIR waveband, the dust mass is weakly constrained.
-We perform an additional fit using an optically thick model where we loosen the upper limit of $\beta$ from 2.2 to 3.0; while the difference between each of all best-fit parameters in this scenario and that using an upper limit of 2.2 (see Table \ref{tab:mbb}) is within 3\%, we find that the dust mass is boosted by a factor of $\sim$\,2.
+We perform an additional fit using an optically thick model where we loosen the upper limit of $\beta$ from 2.2 to 3.0; while the difference between each of all best-fit parameters in this scenario and that using an upper limit of 2.2 is within 3\%, we find that the dust mass is boosted by a factor of $\sim$\,2.
 \subsection{Physical Properties of the ISM in SMM\,J0939}
@@
 While the ground state CO transition line traces the cold molecular gas in the ISM
-\citep*[\eg][]{Wilson70a,Downes98a}, transition lines of higher rotational states ($J$ $>$ 1) are frequently observed in high redshift sources as the
+\citep*[\eg][]{Wilson70a,Downes98a}, transition lines of higher rotational states ($J$ $>$ 1) are frequently observed in high-redshift sources as the
  ground state transition line is redshifted to lower frequencies that can only be observed with a few telescopes
  \citep{Carilli13a}. Consequently, assumptions on the CO excitation conditions are required to derive the molecular gas mass using the M(H$_\textrm{2}$)-to-$L^{\prime}_\textrm{CO}$
- conversion factor from BLAH. \par
+ conversion factor from higher-$J$ CO lines. \par
 Prior to the observations of the ground state CO transition line in SMGs, it has been assumed that the molecular gas in the
-  ISM traced by CO lines is thermalized owing to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
+  ISM traceable by CO lines is thermalized owing to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
    Yet, recent observations of this line have demonstrated that SMGs can indeed be subthermally excited
@@
 where $\nu_\textrm{CO(3-2)}$ is the rest-frame frequency of the \CO transition line in GHz, $D_L$ is the luminosity distance in Mpc, $\mu_\textrm{L}$ is the lensing magnification factor, and $I_\textrm{CO(3-2)}$ is the \CO line flux in Jy\,\,km\,\,s\pmOne.
-This corresponds to $L^{\prime}_\textrm{CO (1-0)}$ = (2.74\,$\pm$\,0.60) $\times$\,\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\,\LpU, hence
-the inferred total molecular gas mass is $M_\textrm{gas}$ = (2.19\,$\pm$\,0.48) $\times$\,\,10$^{10}$\,\Msun\, after correcting for lensing magnification.
+This corresponds to \Lp = (3.42\,$\pm$\,0.71) $\times$~10$^{10}$\,(10.1/$\mu_\textrm{L}$)~\LpU, hence
+the inferred total molecular gas mass is $M_\textrm{gas}$ = (2.74\,$\pm$\,0.57) $\times$\,\,10$^{10}$\,\Msun\, after correcting for lensing magnification.
 We assumed a conversion factor of $\alpha_\textrm{CO}$ = 0.8\,\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
@@
 This results in a gas-to-dust
-ratio of $f_\textrm{gas-dust}$\,=\,$M_\textrm{gas}/M_\textrm{dust}$\,=\,44\,$\pm$\,21.
+ratio of $f_\textrm{gas-dust}$\,=\,$M_\textrm{gas}/M_\textrm{dust}$\,=\,55\,$\pm$\,24.
 We note that a factor of $\sim$\,2 uncertainty arises from the dust mass estimate.
@@
 %No strong evidence of a hot dust bump is found in SMM\,J0939 based on the mid-IR (WAIT, BUT ONLY HAVE 70 micron onwards) continuum measurements (see Figure~\ref{fig:SED}), hence
-We derive the star formation rate (SFR) assuming the dominant IR heating source is due to young and massive stars, and ignoring a contribution from the
+We derive the star formation rate (SFR) assuming that the dominant IR heating source is due to young and massive stars, and ignoring a contribution from the
 dust-enshrouded AGN.
@@
 current rate for a time that can be approximated by the gas depletion timescale, $\tau_\textrm{depl}$\,=\,$M_\textrm{gas}$/SFR.
-This corresponds to $\tau_\textrm{depl}$\,=\,25.1\,$\pm$\,0.4 Myr, which is in good agreement with that found in other SMGs \citep[\eg][]{Greve05a}.
+This corresponds to $\tau_\textrm{depl}$\,=\,31\,$\pm$\,5 Myr, which is in good agreement with those found in other SMGs \citep[\eg][]{Greve05a}.
 
@@
 The SFR per unit mass of molecular gas is commonly taken as a
-measure of the star formation efficiency, SFE\,=\,SFR/$M_\textrm{gas}$. We compute this ratio using lensing-corrected IR
-luminosity and CO luminosity, i.e., SFE\,=\,$L_\textrm{IR}$/\Lp. This makes no assumptions on the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$) as well as the
-choice of IMF; however, this assumes that differential lensing between the CO and infrared emission is negligible.
-The resulting ratio is SFE$_\textrm{IR}$\,=\,319\,$\pm$\,35\,\,\Lsun\,(\LpU)$^{-1}$, this is comparable
-to what is found in ``typical" SMGs \citep{Greve05a,Tacconi06a,Riechers11c}.
+measure of the star formation efficiency, SFE\,=\,SFR/$M_\textrm{gas}$. We compute this ratio using the IR
+luminosity and CO luminosity without correcting for lensing magnification, SFE\,=\,$L_\textrm{IR}$/\Lp.
+The derived SFE is therefore independent of the magnification factor, the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$), and of the
+IMF. This, however, assumes that differential lensing between the CO and infrared emission is negligible.
+The resulting ratio is SFE$_\textrm{IR}$\,=\,256\,$\pm$\,41\,\,\Lsun\,(\LpU)$^{-1}$, this is comparable
+to those found in ``typical" SMGs \citep{Greve05a,Tacconi06a,Riechers11c}.
 
@@
 where $\Delta v_\textrm{line}$ is in km\,\,s\pmOne, $R_\textrm{eff}$ is in kpc, and $M_\textrm{dyn}$ is in \Msun.
-We employ the FWHM line width of the \CO line profile for $\Delta v_\textrm{line}$,
+We employ the FWHM of the \CO line profile for $\Delta v_\textrm{line}$,
 and the half-light radius from our lens model for $R_\textrm{eff}$, assuming that the dust emission traces the same emitting region as the CO.
-We note that a derived dynamical mass based on this assumption is likely to be biased low as the CO emitting region, in most cases, is spatially more extended than the dust emitting region \citep[\eg][]{Tacconi06a}.
+We note that a derived dynamical mass based on this assumption is likely to be biased low as the CO-emitting region can be spatially more extended than the dust emitting region \citep[\eg][]{Tacconi06a, Riechers11c,Riechers11d,Ivison11a}.
 % 
-The inferred dynamical mass is $M_\textrm{dyn}$ = (7.5\,$\pm$\,2.4)\,$\times$\,10$^{10}$\,\Msun, and the gas-to-dynamical mass fraction is $f_\textrm{gas-to-dyn}$ = 0.29\,$\pm$\,0.12, consistent with that of other SMGs \citep{Tacconi06a}.
+The inferred dynamical mass is $M_\textrm{dyn}$ = (7.84\,$\pm$\,2.84)\,$\times$\,10$^{10}$\,\Msun, and the gas-to-dynamical mass fraction is $f_\textrm{gas-to-dyn}$ = 0.35\,$\pm$\,0.14, consistent with those of other SMGs \citep{Tacconi06a}.
 
@@
 To compute surface densities, we divide half the inferred SFR and gas mass by the area subtended by the half-light
-radius, resulting in $\Sigma_\textrm{gas}$ = 4.39\,$\times$\,10$^9$\,\,\Msun\,\,kpc$^{-2}$ and $\Sigma_\textrm{SF}$ = 175.20 \Msun\,\,yr\pmOne\,\,kpc$^{-2}$, which are in good agreement with values typical for SMGs \citep{Tacconi08a}.
+radius, resulting in $\Sigma_\textrm{gas}$ = 5.48\,$\times$\,10$^9$ \Msun~kpc$^{-2}$ and $\Sigma_\textrm{SF}$ = 175.20 \Msun~yr\pmOne~kpc$^{-2}$, which are in good agreement with values typical for SMGs \citep{Tacconi08a}.
 The inferred surface densities of SMM\,J0939 follow a universal Schmidt-Kennicutt relation between the star formation rate
-surface density and the molecular gas surface density reported by \citet{B07a}: $\Sigma_\textrm{SF}$ = 9.3\,$\times$\,10$^{-5}$ ($M_\textrm{gas}$/2$\pi R_\textrm{1/2}^2)^{1.71}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
+surface density and the molecular gas surface density: $\Sigma_\textrm{SF}$ = 9.3 ($\pm$\,2) $\times$\,10$^{-5}$ ($M_\textrm{gas}$/2$\pi R_\textrm{1/2}^2)^{1.71(\pm\,0.05)}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
 galaxies
-out to $z$\,$\sim$\,2.5, and assuming a Chabrier IMF.
+out to $z$\,$\sim$\,2.5, and assuming a Chabrier IMF \citep{B07a}.
 
@@
 The detection of CO in SMM\,J0939
-implies a CO luminosity of \Lp = (2.7\,$\pm$\,0.6) $\times$ 10$^{10}$ (10.1/$\mu_\textrm{L}$) \LpU, suggesting the presence of a massive
+implies a CO luminosity of \Lp\ = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU, suggesting the presence of a massive
 molecular gas reservoir that fuels the star formation at a rate of $\sim$\,874 \Msun~yr\pmOne.
-If the star forming activity continues at the current rate, the gas reservoir will be depleted within $\lesssim$~25 Myr,
+If the star forming activity continues at the current rate, the gas reservoir will be depleted within $\lesssim$~31 Myr,
 which is consistent with the short timescale found in SMGs \citep{Greve05a}.
@@
 In contrast with what was found for F10214, one of the eight sources in their sample with the lowest molecular gas mass and SFR, we find that the properties
-(\eg FWHM of CO line profile \footnote{The statistical mean in \citet{Polletta11a} is based on the line profile of the CO transition closest to $J$ = 4\,\rarr\,3}, M$_\textrm{gas}$\footnote{The molecular gas mass for each source is derived based on its lowest-$J$ CO line emission available in literature}, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a
+(\eg FWHM of CO line profile \footnote{The statistical mean is based on the line profile of the CO transition closest to $J$ = 4\,\rarr\,3 available for each source}, M$_\textrm{gas}$\footnote{The molecular gas mass for each source is derived based on its lowest-$J$ CO line emission available in literature}, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a
 factor of $\sim$\,1.5, is nevertheless consistent within the measurement uncertainties.
-The fact that the gas mass of F10214 in their compilation was derived using \CO line emission \citep{Solomon05a} has minor effect on the resulting low gas mass; \citet{Riechers11a} report a similarly low gas mass derived using their CO($J$\,=\,1\,\rarr\,0) line measurement.
-The molecular gas mass and SFR of F10214 is the lowest among high-redshift type-2 quasars due to the high magnification factor of $\mu_{\textrm L}$ = 17 \citep{Solomon05a} as well as its intrinsically gas poorer nature.
+The fact that the gas mass of F10214 in their compilation was derived using \CO line emission \citep{Solomon05a} has a minor effect on the resulting low gas mass; \citet{Riechers11a} report a similarly low gas mass derived using their CO($J$\,=\,1\,\rarr\,0) line measurement.
+With F10214 being the most strongly-lensed high-redshift type-2 quasar \citep[$\mu_{\textrm L}$ = 17; ][]{Solomon05a}, its exceptionally low molecular gas mass and SFR is evident that this source lies on the low end of the CO and IR luminosity functions of the population.
 This demonstrates that despite the variations in the intrinsic properties among lensed sources,
- SMM\,J0939 is representative of type-2 quasars at high redshifts (at least among the sample from \citet{Polletta11a}).
+ SMM\,J0939 is representative of type-2 quasars at high redshifts (at least among the sample from \citealt{Polletta11a}).
 
 We conclude this paper by noting that SMM\,J0939 is a faithful representation of both high-redshift type-2 quasars and SMGs,
-based on the excellent agreements found between theirs properties. In this remarkable lensing system, the background galaxy --- SMM\,J0939 is
+based on the excellent agreement found between theirs properties. In this remarkable lensing system, the background galaxy --- SMM\,J0939 is
 breaking up its dust cocoon (H14) while undergoing prodigious star-formation (SFR\,$\sim$\,874 \Msun~yr\pmOne).
@@
 and the National Science Foundation. 
-(REMOVE?)Ongoing CARMA development
+Ongoing CARMA development
 and operations are supported by the National Science
@@
 We perform the SED fitting to the (sub)-mm data of SMM\,J0939 using {\sc mbb\_emcee} (see \S \ref{sec:SEDBg}), this code uses MCMC to sample the parameter space of each parameter.
-The bolometric IR luminosity and dust mass are then derived from the set of parameters that maximizes the likelihood.
-We show in Figure~\ref{fig:sedlikelihood} the resulting correlation plots of each pair of parameters (off-diagonal) as well as the marginalized posterior probability distribution plots of each parameter (diagonal) for the fitted optically thick and optically thin models.
-The parameter values corresponding to the most likely solution are denoted as black crosses in the 2D correlation plots, and vertical lines in the marginalized posterior probability distribution plots.
-\par
+The total IR luminosity and dust mass are then derived from the set of parameters that maximizes the likelihood.
+We show in Figure~\ref{fig:sedlikelihood} the resulting correlation plots of each pair of parameters (off-diagonals) as well as the marginalized PDFs of each parameter (diagonals) for the fitted optically thick and optically thin models.
+The parameter values corresponding to the most likely solution are denoted as black crosses in the joint probability distribution plots, and vertical lines in the marginalized PDF plots. \par
 
-As shown in the figure, the marginalized PDF of each parameter in the optically thin model is Gaussian, and
-the dust emissivity index ($\beta$) is highly anti-correlated with the observed-frame dust temperature ($T/(1+z)$).
-We note that the best-fit emissivity in this model is unusually low among high redshift galaxies ($\beta$ = 0.7$^{+0.2}_{-0.3}$, cf.
-1$-$2.5; \eg \citet{Casey12a} and references therein).
+The PDFs of the parameters in the optically thin model are shown in the right panel of Figure~\ref{fig:sedlikelihood}, the dust emissivity index ($\beta$) is highly anti-correlated with the observed-frame dust temperature ($T/(1+z)$), and the marginalized PDFs of all parameters are well-approximated by Gaussians --- the best-fit solution is prominent.
+We note that the best-fit emissivity in this model is unusually low among high-redshift galaxies ($\beta$ = 0.7$^{+0.2}_{-0.3}$, cf.
+1$-$2.5; \eg \citealt[][and references therein]{Casey12a}).
 While this directly affects the slope of the Rayleigh-Jeans tail of the modified blackbody function, such low emissivity has insignificant impact on the inferred IR luminosity.
-We also find no evidence of correlation between the inferred dust mass and IR luminosity. Despite the factor of $\sim$\,2 difference
-in dust masses
-between models, the derived IR luminosities are comparable.
+Despite the factor of $\sim$\,2 difference
+in dust mass
+between models, the derived IR luminosities are comparable. As such, we find no evidence of correlation between the inferred dust mass and IR luminosity.
 
 A comparison of the reduced $\chi^2$ between the two models suggests that the optically thick model fit is superior to the optically thin model fit.
-In the preferred model, the marginalized PDF of the dust emissivity index is highly non-Gaussian, with noticeably broad distribution across
+In the preferred model, the marginalized PDF of the dust emissivity index is highly non-Gaussian, with a noticeably broad distribution across
 the allowed range (upper limit: 2.2). We therefore fit a second optically thick model, changing the upper limit of $\beta$ to 3.0. The difference in each
@@
 distributions of each
-parameter are plotted on the diagonal axis of each panel, where the solid black vertical lines indicate the set of parameter values in the PDFs that maximizes the likelihood.
-The correlation plots between parameters are plotted as 2D histograms on the off-diagonals, where the black crosses denote the
+parameter are plotted along the diagonals, where the solid black vertical lines indicate the set of parameter values that maximizes the likelihood.
+The joint PDFs between parameters are plotted as 2D histograms on the off-diagonals, where the black crosses denote the
 locations of the most likely solution in the parameter space. The solid, dashed, and dotted lines correspond to 1$\sigma$, 2$\sigma$, and $3\sigma$, respectively. 

### 2015-08-21 Code/FgContIm.py

@@ -142,6 +142,13 @@ def markers_cross(sp, ra, dec, layer=None, ec='yellow', fc='none', mk='+', s=500
     ra: float
     dec: float
     layer: str
+    ec: str
+        edgecolor
+    fc: str
+        facecolor
+    mk: str
+        symbol
+
     """
     sp.show_markers(ra, dec, layer=layer, edgecolor=ec, facecolor=fc, marker=mk, s=s, alpha=a, linewidth=lw)
 

### 2015-08-21 Code/Plot_Image.py

@@ -73,17 +73,17 @@ fvla.show_grayscale(stretch='log', vmin=vla_min, vmax=vla_max, vmid=-0.001)
 
 flin = aplpy.FITSFigure(label['lin'][0], \
         figure=fig_line, subplot=[x0,row_a,width,dy])
-flin.show_colorscale(cmap=mpl.cm.jet, vmin=min_line, vmax=max_line, vmid=-25, stretch='log')
+flin.show_colorscale(cmap=mpl.cm.jet, vmin=min_line, vmax=max_line, vmid=-2500, stretch='log')
 fSMA = aplpy.FITSFigure(label['SMA'][0], figure=fig_line, subplot=[x0+width+2*x_gap, row_a, width, dy])
 fSMA.show_grayscale(stretch='log', vmin=SMA_min, vmax=SMA_max, vmid=-0.1)
 
 ########################################
 # Contours
 ########################################
-fcont.show_contour(label['cont'][0], colors='black', levels=sigma_contour_cont(sigma_cont), linewidths=1.5, layer='fg')
+fcont.show_contour(label['cont'][0], colors='black', alpha=0.8, levels=sigma_contour_cont(sigma_cont), linewidths=1.8, layer='fg')
 fvla.show_contour(label['VLA'][0], colors="lime", levels=sigma_contour_array(sigma_9ghz), linewidths=2, layer='fg')
 fvla.show_contour(label['cont'][0], colors='red', levels=sigma_contour_cont(sigma_cont), linewidths=2, layer='fg_cont')
-flin.show_contour(label['lin'][0], colors="white", levels=sigma_contour_CARMA(sigma_line), linewidths=2, layer='mol')
+flin.show_contour(label['lin'][0], colors="white", alpha=0.8, levels=sigma_contour_CARMA(sigma_line), linewidths=1.8, layer='mol')
 fSMA.show_contour(label['SMA'][0], colors="lime", levels=sigma_contour_CARMA(sigma_SMA), linewidths=1.8, layer='bf_cont')
 fSMA.show_contour(label['lin'][0], colors="red", levels=sigma_contour_CARMA(sigma_line), linewidths=2, layer='mol')
 
@@ -133,7 +133,7 @@ fSMA.axis_labels.hide()
 ########################################
 markers_cross(fvla, ra_cross, dec_cross, layer='marker_set_1')
 markers_cross(fcont, ra_cross, dec_cross, layer='marker_set_1')
[…]

### 2015-08-21 Code/SEDfit.py

@@ -396,6 +396,7 @@ start_Hz = 1e10
 end_Hz = Avg_cont_freq + epsilon
 x_syn_extend = np.linspace(start_Hz, end_Hz)
 syn_extend_mJy = lobeSyn(x_syn_extend, *theta_best)
+print "extrapolated flux density at 104 GHz: %.2f" % (lobeSyn(104.e9, *theta_best))
 ax.plot(GHz2um(x_syn_extend * Hz2GHz),
         syn_extend_mJy, 'b-', linewidth=2.5, alpha=0.5)
 

### 2015-08-21 Code/err.py

@@ -1,23 +1,23 @@
-freq_CO32 = 345.651     # GHz
-dl = 19052          # Mpc at 2.221
+freq_CO32 = 345.7959899     # GHz
+dl = 18052          # Mpc at 2.221
 z = 2.221
-I_line = 10.7
-del_I = 1.345   # sigma of CO(3-2) line intensity Jy km/s
+I_line = 12.598
+del_I = 2.010   # sigma of CO(3-2) line intensity Jy km/s
 mu = 10.1298
 del_mu = 1.38
 alpha = 0.8
 rkpc = 0.105907102426 * 8.406
 del_kpc = 0.03309 * 8.406
-vel = 541.65
-del_vel = 31.9
+vel = 559.423   # FWHM
+del_vel = 52.3674
 LIR = 88.52e12    # before lensing correction, from mbb
 LFIR = 53.330e12
 del_FIR_noMu = 1.14e12
 del_IR_noMu = 2.62e12
 M_dust = 50.47e+8  # before lensing correction, from mbb
 sig_Mdust_noMu = 20.42e8
-M_dyn = 7.35e10
-Mgas = 2.326e10    # with lensing correction
+M_dyn = 7.48e10
+Mgas = 2.28e10    # with lensing correction
 
 #####################
 #####################

### 2015-08-21 skeleton.tex
quick fix after DR email comment today

@@
 \end{abstract}
-\keywords{cosmology: observations --- galaxies: formation --- galaxies: high-redshift ---  galaxies: starburst --- submillimeter: galaxies}
+\keywords{cosmology: observations --- galaxies: evolution --- galaxies: high-redshift ---  galaxies: starburst --- submillimeter: galaxies}
 
@@
 SMGs, with a lensing-magnified flux density of $S_\textrm{250\micron}$\,=\,440\,$\pm$\,15 mJy.
-Previous detections of C{\scriptsize\sc IV}\,1459\AA\
- and He{\scriptsize\sc II}\,1640\AA\ line emission toward SMM\,J0939
+Previous detections of C {\scriptsize\sc IV}\,1459\AA\
+ and He {\scriptsize\sc II}\,1640\AA\ line emission toward SMM\,J0939
  placed the redshift of this galaxy at $z$\,=\,2.221, and suggested the presence of an active galactic nucleus (AGN),
@@
 emission after subtracting continuum emission in the visibility plane.
-This results in a velocity-integrated \CO line flux of $I_\textrm{CO}$\,=\,12.6\,$\pm$\,2.0 Jy km\,\,s\pmOne\ over the velocity range of $\Delta v$\,$\sim$\,1420 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration
+This results in a velocity-integrated \CO line flux of $I_\textrm{CO}$\,=\,12.6\,$\pm$\,2.0 Jy km\,\,s\pmOne\ over a velocity range of $\Delta v$\,$\sim$\,1420 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration
 uncertainty. Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.2212\,$\pm$\,0.0010.
@@
 
-We fix the phase center to coordinates ($\alpha$,\,$\delta$)\,\,(J2000) = (9:39:23.54,\,\,83:15:26.10), where the
+We fix the phase center to coordinates ($\alpha$,\,$\delta$)\,\,(J2000) = (9$^{\rm h}$39$^{\rm m}$23\fs54,\,\,83\degr15\arcmin26\farcs10), where the
 angular offsets of the lenses and source are referenced to this position. The primary lens (3C220.3) is
@@
 unity, and $\nu_c^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy
-distribution. %extrapolated flux density at 104 GHz: 5.10
+distribution. 
 The extrapolated flux density at 104\,\,GHz is consistent with the peak flux density of our continuum
@@
 Consequently, a conservative upper limit of $S_\nu$\,$<$\,4.93 mJy on the core emission can be established using the measured peak flux density. Yet, by considering the 
-difference between the integrated flux density and the extrapolated flux density of the lobes ($S_\textrm{104GHz}$ = 5.10 mJy), we establish a more stringent constrain on this upper limit of $S_\nu$\,$<$\,2.29 mJy.
+difference between the integrated flux density from our measurement and the flux density from an extrapolation of the model (see Figure~\ref{fig:SED}; $S_\textrm{104GHz, fit}$~=~5.10 mJy), we establish a more stringent constrain on this upper limit of $S_\nu$\,$<$\,2.29 mJy.
 We did not
@@
 To examine whether SMM\,J0939 is also representative of type-2 quasars at high redshifts, we compare the properties of SMM\,J0939
-against those of eight CO-detected obscured AGNs at $z$ = 1.6\,--\,2.8, using the averaged values reported by \citet[][and references
+against those of eight CO-detected obscured AGNs at $z$ = 1.6\,$-$\,2.8, using the averaged values reported by \citet[][and references
 therein]{Polletta11a}. %P11 Mgas from the lowest CO line, but cited 4-3 line width and intensity, etc in Table 2
@@
 The fact that the gas mass of F10214 in their compilation was derived using \CO line emission \citep{Solomon05a} has a minor effect on the resulting low gas mass; \citet{Riechers11a} report a similarly low gas mass derived using their CO($J$\,=\,1\,\rarr\,0) line measurement.
-With F10214 being the most strongly-lensed high-redshift type-2 quasar \citep[$\mu_{\textrm L}$ = 17; ][]{Solomon05a}, its exceptionally low molecular gas mass and SFR is evident that this source lies on the low end of the CO and IR luminosity functions of the population.
+With F10214 being the most strongly-lensed high-redshift type-2 quasar \citep[$\mu_{\textrm L}$ = 17; ][]{Solomon05a}\footnote{Note that \citet{Deane13a} suggest a magnification factor of $\mu_{\textrm L}$ = 6\,$\pm$\,1.5 for the CO emission in F10214}, its exceptionally low molecular gas mass and SFR is evident that this source lies on the low end of the CO and IR luminosity functions of the population.
 This demonstrates that despite the variations in the intrinsic properties among lensed sources,

### 2015-08-21 skeleton.tex
fix to fit guidelines

@@
+% submission prep
+% what does this mean
+% Multiplication
+% Explicit multiplication signs (dots or crosses), except for scientific notation, grids, vector operators, and when a multiplication wraps to a following line, are omitted.
+% online said;: should go in alphabetical order, so should I do Ivison 11 before R11?
 %\documentclass[12pt,preprint]{aastex}
@@
 %\slugcomment{{\sc Accepted to ApJ:} August 1, 2006}
+\slugcomment{To be submitted to the ApJ}
 \usepackage{amsmath}
@@
 The 3\,mm receivers were used to cover the redshifted \CO line and the nearby observed-frame 2.88\,mm continuum emission.
-The correlator was configured to provide a bandwidth of 3.96 GHz in each sideband, and a spectral resolution of 5.208 MHz ($\sim$\,14.5 km\,\,s\pmOne).
+The correlator was configured to provide an effective bandwidth of 3.708 GHz in each sideband, and a spectral resolution of 5.208 MHz ($\sim$\,14.5 km\,\,s\pmOne).
 % each sideband 8 windows * 0.494792 GHz = 3.9583 before flagging edge channels
+% DR said take out edge channels, since the subbands overlap, and the usable bandwidth is 8 * (95 - 6) * 5.208 
 The line was placed in the
@@
 The continuum image is created by
-averaging over all line-free channels, this yields a synthesized clean beam of 12\farcs0\,$\times$\,6\farcs5, $-$55.9$\degr$ east of north, and an rms noise of $\sigma_\textrm{cont}$ = 0.50\,\,mJy\,\,beam\pmOne\ over 7.0 GHz.
-%6.968 GHz = (total(1520) - edge * 2 * nwin(16))*5.208 MHz - [linechannel (196 - 153) * (2 * 5.208MHz)]
+averaging over all line-free channels, this yields a synthesized clean beam of 12\farcs0\,$\times$\,6\farcs5, $-$55.9$\degr$ east of north, and an rms noise of $\sigma_\textrm{cont}$ = 0.50\,\,mJy\,\,beam\pmOne\ over 6.8 GHz.
+%7416.192 MHz = (total(1520) - edge * 2 * nwin(16))*5.208 MHz 
+%7416.192 - [FWZI linechannel (55) * (2 * 5.208MHz)] = 6843.312
 \section{Results}\label{sec:res}
@@
 \centering
-\includegraphics[width=0.80\textwidth]{Figure/ContPanel.pdf}
+\includegraphics[width=0.80\textwidth]{Figure/ContPanel_cmyk.eps}
 \caption{Left: Contour map of the 104 GHz continuum emission in the foreground radio galaxy 3C220.3.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{Figure/LinePanel.pdf}
+\includegraphics[width=0.8\textwidth]{Figure/LinePanel_cmyk.eps}
 \includegraphics[width=0.65\textwidth]{Figure/smmj0939-co32_spec.eps}
@@
 the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
-\input{table_lensParams}
+%\input{table_lensParams}
 
@@
 estimate the flux density of the lobes at the frequency of our continuum measurement.
-\input{table_SED}
+%\input{table_SED}
 Following Equation (1) in \citet{Cleary07a}, the fit to the lobe emission can be expressed as a parabolic function:
@@
 \includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED2.pdf}
-\caption{The SEDs of 3C220.3 (solid purple line) and SMM\,J0939 (dashed purple line and solid cyan line) including the new measurements presented in this paper.
+\caption{SEDs of 3C220.3 (solid purple line) and SMM\,J0939 (dashed purple line and solid cyan line) including the new measurements presented in this paper.
 The solid purple line corresponds to the parabolic function we
@@
 
-\input{table_mbb}
+%\input{table_mbb}
 The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in the Appendix. The best-fit solution of an optically thin
@@
 \section{Discussion And Conclusions}
-\input{table_compareSMG}
+%\input{table_compareSMG}
 We present the detection of \CO line emission toward SMM\,J0939+8315, a strongly-lensed SMG that is hosting a type-2 quasar, refining the redshift
@@
 \bibliographystyle{apj}
-\bibliography{J0939}
+%\bibliography{J0939}
+\begin{thebibliography}{}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Baldwin} {et~al.}(1985){Baldwin}, {Boysen}, {Hales}, {Jennings},
+  {Waggett}, {Warner}, \& {Wilson}}]{r2728}
+{Baldwin}, J.~E., {Boysen}, R.~C., {Hales}, S.~E.~G., {et~al.} 1985, \mnras,
+  217, 717
+
+\bibitem[{{Begelman} {et~al.}(1984){Begelman}, {Blandford}, \&
+  {Rees}}]{Begelman84a}
+{Begelman}, M.~C., {Blandford}, R.~D., \& {Rees}, M.~J. 1984, Reviews of Modern
+  Physics, 56, 255
+
+\bibitem[{{Blain} {et~al.}(2002){Blain}, {Smail}, {Ivison}, {Kneib}, \&
+  {Frayer}}]{blain02a}
+{Blain}, A.~W., {Smail}, I., {Ivison}, R.~J., {Kneib}, J.-P., \& {Frayer},
+  D.~T. 2002, \physrep, 369, 111
+
+\bibitem[{{Bothwell} {et~al.}(2013){Bothwell}, {Smail}, {Chapman}, {Genzel},
+  {Ivison}, {Tacconi}, {Alaghband-Zadeh}, {Bertoldi}, {Blain}, {Casey}, {Cox},
+  {Greve}, {Lutz}, {Neri}, {Omont}, \& {Swinbank}}]{Bothwell13a}
+{Bothwell}, M.~S., {Smail}, I., {Chapman}, S.~C., {et~al.} 2013, \mnras, 429,
+  3047
+
+\bibitem[{{Bouch{\'e}} {et~al.}(2007){Bouch{\'e}}, {Cresci}, {Davies},
+  {Eisenhauer}, {F{\"o}rster Schreiber}, {Genzel}, {Gillessen}, {Lehnert},
+  {Lutz}, {Nesvadba}, {Shapiro}, {Sternberg}, {Tacconi}, {Verma}, {Cimatti},
+  {Daddi}, {Renzini}, {Erb}, {Shapley}, \& {Steidel}}]{B07a}
+{Bouch{\'e}}, N., {Cresci}, G., {Davies}, R., {et~al.} 2007, \apj, 671, 303
+
+\bibitem[{{Bussmann} {et~al.}(2015){Bussmann}, {Riechers}, {Fialkov},
+  {Scudder}, {Hayward}, {Cowley}, {Bock}, {Calanog}, {Chapman}, {Cooray}, {De
+  Bernardis}, {Farrah}, {Fu}, {Gavazzi}, {Hopwood}, {Ivison}, {Jarvis},
+  {Lacey}, {Loeb}, {Oliver}, {Perez-Fournon}, {Rigopoulou}, {Roseboom},
+  {Scott}, {Smith}, {Vieira}, {Wang}, \& {Wardlow}}]{Bussmann15a}
+{Bussmann}, R.~S., {Riechers}, D., {Fialkov}, A., {et~al.} 2015, ArXiv
+  e-prints, arXiv:1504.05256
+
+\bibitem[{{Carilli} \& {Walter}(2013)}]{Carilli13a}
+{Carilli}, C.~L., \& {Walter}, F. 2013, \araa, 51, 105
+
+\bibitem[{{Carilli} {et~al.}(2010){Carilli}, {Daddi}, {Riechers}, {Walter},
+  {Weiss}, {Dannerbauer}, {Morrison}, {Wagg}, {Dav{\'e}}, {Elbaz}, {Stern},
+  {Dickinson}, {Krips}, \& {Aravena}}]{Carilli10a}
+{Carilli}, C.~L., {Daddi}, E., {Riechers}, D., {et~al.} 2010, \apj, 714, 1407
+
+\bibitem[{{Casey}(2012)}]{Casey12a}
+{Casey}, C.~M. 2012, \mnras, 425, 3094
+
+\bibitem[{{Casey} {et~al.}(2014){Casey}, {Narayanan}, \& {Cooray}}]{Casey14a}
+{Casey}, C.~M., {Narayanan}, D., \& {Cooray}, A. 2014, \physrep, 541, 45
+
+\bibitem[{{Chabrier}(2003)}]{Chabrier03a}
+{Chabrier}, G. 2003, \pasp, 115, 763
+
+\bibitem[{{Cleary} {et~al.}(2007){Cleary}, {Lawrence}, {Marshall}, {Hao}, \&
+  {Meier}}]{Cleary07a}
+{Cleary}, K., {Lawrence}, C.~R., {Marshall}, J.~A., {Hao}, L., \& {Meier}, D.
+  2007, \apj, 660, 117
+
+\bibitem[{{Cohen} {et~al.}(2007){Cohen}, {Lane}, {Cotton}, {Kassim}, {Lazio},
+  {Perley}, {Condon}, \& {Erickson}}]{r30}
+{Cohen}, A.~S., {Lane}, W.~M., {Cotton}, W.~D., {et~al.} 2007, \aj, 134, 1245
+
+\bibitem[{{Condon} {et~al.}(1998){Condon}, {Cotton}, {Greisen}, {Yin},
+  {Perley}, {Taylor}, \& {Broderick}}]{r16}
+{Condon}, J.~J., {Cotton}, W.~D., {Greisen}, E.~W., {et~al.} 1998, \aj, 115,
+  1693
+
+\bibitem[{{Conley} {et~al.}(2011){Conley}, {Cooray}, {Vieira}, {Gonz{\'a}lez
+  Solares}, {Kim}, {Aguirre}, {Amblard}, {Auld}, {Baker}, {Beelen}, {Blain},
+  {Blundell}, {Bock}, {Bradford}, {Bridge}, {Brisbin}, {Burgarella},
+  {Carpenter}, {Chanial}, {Chapin}, {Christopher}, {Clements}, {Cox},
+  {Djorgovski}, {Dowell}, {Eales}, {Earle}, {Ellsworth-Bowers}, {Farrah},
+  {Franceschini}, {Frayer}, {Fu}, {Gavazzi}, {Glenn}, {Griffin}, {Gurwell},
+  {Halpern}, {Ibar}, {Ivison}, {Jarvis}, {Kamenetzky}, {Krips}, {Levenson},
+  {Lupu}, {Mahabal}, {Maloney}, {Maraston}, {Marchetti}, {Marsden},
+  {Matsuhara}, {Mortier}, {Murphy}, {Naylor}, {Neri}, {Nguyen}, {Oliver},
+  {Omont}, {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen},
+  {Rangwala}, {Rawlings}, {Raymond}, {Riechers}, {Rodighiero}, {Roseboom},
+  {Rowan-Robinson}, {Schulz}, {Scott}, {Scott}, {Serra}, {Seymour}, {Shupe},
+  {Smith}, {Symeonidis}, {Tugwell}, {Vaccari}, {Valiante}, {Valtchanov},
+  {Verma}, {Viero}, {Vigroux}, {Wang}, {Wiebe}, {Wright}, {Xu}, {Zeimann},
+  {Zemcov}, \& {Zmuidzinas}}]{Conley11a}
+{Conley}, A., {Cooray}, A., {Vieira}, J.~D., {et~al.} 2011, \apjl, 732, L35
+
+\bibitem[{{Coppin} {et~al.}(2008){Coppin}, {Swinbank}, {Neri}, {Cox},
+  {Alexander}, {Smail}, {Page}, {Stevens}, {Knudsen}, {Ivison}, {Beelen},
+  {Bertoldi}, \& {Omont}}]{Coppin08a}
+{Coppin}, K.~E.~K., {Swinbank}, A.~M., {Neri}, R., {et~al.} 2008, \mnras, 389,
+  45
+
+\bibitem[{{Danielson} {et~al.}(2011){Danielson}, {Swinbank}, {Smail}, {Cox},
+  {Edge}, {Weiss}, {Harris}, {Baker}, {De Breuck}, {Geach}, {Ivison}, {Krips},
+  {Lundgren}, {Longmore}, {Neri}, \& {Flaquer}}]{Danielson11a}
+{Danielson}, A.~L.~R., {Swinbank}, A.~M., {Smail}, I., {et~al.} 2011, \mnras,
+  410, 1687
+
+\bibitem[{{Deane} {et~al.}(2013){Deane}, {Heywood}, {Rawlings}, \&
+  {Marshall}}]{Deane13a}
+{Deane}, R.~P., {Heywood}, I., {Rawlings}, S., \& {Marshall}, P.~J. 2013,
+  \mnras, 434, 23
+
+\bibitem[{{Dickinson} {et~al.}(2003){Dickinson}, {Papovich}, {Ferguson}, \&
+  {Budav{\'a}ri}}]{Dickinson03a}
+{Dickinson}, M., {Papovich}, C., {Ferguson}, H.~C., \& {Budav{\'a}ri}, T. 2003,
+  \apj, 587, 25
+
+\bibitem[{{Dowell} {et~al.}(2014){Dowell}, {Conley}, {Glenn}, {Arumugam},
+  {Asboth}, {Aussel}, {Bertoldi}, {B{\'e}thermin}, {Bock}, {Boselli}, {Bridge},
+  {Buat}, {Burgarella}, {Cabrera-Lavers}, {Casey}, {Chapman}, {Clements},
+  {Conversi}, {Cooray}, {Dannerbauer}, {De Bernardis}, {Ellsworth-Bowers},
+  {Farrah}, {Franceschini}, {Griffin}, {Gurwell}, {Halpern}, {Hatziminaoglou},
+  {Heinis}, {Ibar}, {Ivison}, {Laporte}, {Marchetti},
+  {Mart{\'{\i}}nez-Navajas}, {Marsden}, {Morrison}, {Nguyen}, {O'Halloran},
+  {Oliver}, {Omont}, {Page}, {Papageorgiou}, {Pearson}, {Petitpas},
+  {P{\'e}rez-Fournon}, {Pohlen}, {Riechers}, {Rigopoulou}, {Roseboom},
+  {Rowan-Robinson}, {Sayers}, {Schulz}, {Scott}, {Seymour}, {Shupe}, {Smith},
+  {Streblyanska}, {Symeonidis}, {Vaccari}, {Valtchanov}, {Vieira}, {Viero},
+  {Wang}, {Wardlow}, {Xu}, \& {Zemcov}}]{Dowell14a}
+{Dowell}, C.~D., {Conley}, A., {Glenn}, J., {et~al.} 2014, \apj, 780, 75
+
+\bibitem[{{Downes} \& {Solomon}(1998)}]{Downes98a}
+{Downes}, D., \& {Solomon}, P.~M. 1998, \apj, 507, 615
+
+\bibitem[{{Dunne} {et~al.}(2003){Dunne}, {Eales}, \& {Edmunds}}]{Dunne03a}
+{Dunne}, L., {Eales}, S.~A., \& {Edmunds}, M.~G. 2003, \mnras, 341, 589
+
+\bibitem[{{Eales} {et~al.}(2010){Eales}, {Dunne}, {Clements}, {Cooray}, {de
+  Zotti}, {Dye}, {Ivison}, {Jarvis}, {Lagache}, {Maddox}, {Negrello},
+  {Serjeant}, {Thompson}, {van Kampen}, {Amblard}, {Andreani}, {Baes},
+  {Beelen}, {Bendo}, {Benford}, {Bertoldi}, {Bock}, {Bonfield}, {Boselli},
+  {Bridge}, {Buat}, {Burgarella}, {Carlberg}, {Cava}, {Chanial}, {Charlot},
+  {Christopher}, {Coles}, {Cortese}, {Dariush}, {da Cunha}, {Dalton}, {Danese},
+  {Dannerbauer}, {Driver}, {Dunlop}, {Fan}, {Farrah}, {Frayer}, {Frenk},
+  {Geach}, {Gardner}, {Gomez}, {Gonz{\'a}lez-Nuevo}, {Gonz{\'a}lez-Solares},
+  {Griffin}, {Hardcastle}, {Hatziminaoglou}, {Herranz}, {Hughes}, {Ibar},
+  {Jeong}, {Lacey}, {Lapi}, {Lawrence}, {Lee}, {Leeuw}, {Liske},
+  {L{\'o}pez-Caniego}, {M{\"u}ller}, {Nandra}, {Panuzzo}, {Papageorgiou},
+  {Patanchon}, {Peacock}, {Pearson}, {Phillipps}, {Pohlen}, {Popescu},
+  {Rawlings}, {Rigby}, {Rigopoulou}, {Robotham}, {Rodighiero}, {Sansom},
+  {Schulz}, {Scott}, {Smith}, {Sibthorpe}, {Smail}, {Stevens}, {Sutherland},
+  {Takeuchi}, {Tedds}, {Temi}, {Tuffs}, {Trichas}, {Vaccari}, {Valtchanov},
+  {van der Werf}, {Verma}, {Vieria}, {Vlahakis}, \& {White}}]{Eales10a}
+{Eales}, S., {Dunne}, L., {Clements}, D., {et~al.} 2010, \pasp, 122, 499
+
+\bibitem[{{Engel} {et~al.}(2010){Engel}, {Tacconi}, {Davies}, {Neri}, {Smail},
+  {Chapman}, {Genzel}, {Cox}, {Greve}, {Ivison}, {Blain}, {Bertoldi}, \&
+  {Omont}}]{Engel10a}
+{Engel}, H., {Tacconi}, L.~J., {Davies}, R.~I., {et~al.} 2010, \apj, 724, 233
+
+\bibitem[{{Fanaroff} \& {Riley}(1974)}]{Fanaroff74}
+{Fanaroff}, B.~L., \& {Riley}, J.~M. 1974, \mnras, 167, 31P
+
+\bibitem[{{Gavazzi} {et~al.}(2011){Gavazzi}, {Cooray}, {Conley}, {Aguirre},
+  {Amblard}, {Auld}, {Beelen}, {Blain}, {Blundell}, {Bock}, {Bradford},
+  {Bridge}, {Brisbin}, {Burgarella}, {Chanial}, {Chapin}, {Christopher},
+  {Clements}, {Cox}, {Djorgovski}, {Dowell}, {Eales}, {Earle},
+  {Ellsworth-Bowers}, {Farrah}, {Franceschini}, {Fu}, {Glenn}, {Gonz{\'a}lez
+  Solares}, {Griffin}, {Gurwell}, {Halpern}, {Ibar}, {Ivison}, {Jarvis},
+  {Kamenetzky}, {Kim}, {Krips}, {Levenson}, {Lupu}, {Mahabal}, {Maloney},
+  {Maraston}, {Marchetti}, {Marsden}, {Matsuhara}, {Mortier}, {Murphy},
+  {Naylor}, {Neri}, {Nguyen}, {Oliver}, {Omont}, {Page}, {Papageorgiou},
+  {Pearson}, {P{\'e}rez-Fournon}, {Pohlen}, {Rangwala}, {Rawlings}, {Raymond},
+  {Riechers}, {Rodighiero}, {Roseboom}, {Rowan-Robinson}, {Schulz}, {Scott},
+  {Scott}, {Serra}, {Seymour}, {Shupe}, {Smith}, {Symeonidis}, {Tugwell},
+  {Vaccari}, {Valiante}, {Valtchanov}, {Verma}, {Vieira}, {Vigroux}, {Wang},
+  {Wardlow}, {Wiebe}, {Wright}, {Xu}, {Zeimann}, {Zemcov}, \&
+  {Zmuidzinas}}]{Gavazzi11a}
+{Gavazzi}, R., {Cooray}, A., {Conley}, A., {et~al.} 2011, \apj, 738, 125
+
+\bibitem[{{Greve} {et~al.}(2005){Greve}, {Bertoldi}, {Smail}, {Neri},
+  {Chapman}, {Blain}, {Ivison}, {Genzel}, {Omont}, {Cox}, {Tacconi}, \&
+  {Kneib}}]{Greve05a}
+{Greve}, T.~R., {Bertoldi}, F., {Smail}, I., {et~al.} 2005, \mnras, 359, 1165
+
+\bibitem[{{Haas} {et~al.}(2014){Haas}, {Leipski}, {Barthel}, {Wilkes},
+  {Vegetti}, {Bussmann}, {Willner}, {Westhues}, {Ashby}, {Chini}, {Clements},
+  {Fassnacht}, {Horesh}, {Klaas}, {Koopmans}, {Kuraszkiewicz}, {Lagattuta},
+  {Meisenheimer}, {Stern}, \& {Wylezalek}}]{Haas14}
+{Haas}, M., {Leipski}, C., {Barthel}, P., {et~al.} 2014, \apj, 790, 46 (H14)
+
+\bibitem[{{Hales} {et~al.}(1995){Hales}, {Waldram}, {Rees}, \&
+  {Warner}}]{r33-34}
+{Hales}, S.~E.~G., {Waldram}, E.~M., {Rees}, N., \& {Warner}, P.~J. 1995,
+  \mnras, 274, 447
+
+\bibitem[{{Hardcastle} \& {Looney}(2008)}]{Hardcastle08a}
+{Hardcastle}, M.~J., \& {Looney}, L.~W. 2008, \mnras, 388, 176
+
+\bibitem[{{Harris} {et~al.}(2010){Harris}, {Baker}, {Zonak}, {Sharon},
+  {Genzel}, {Rauch}, {Watts}, \& {Creager}}]{Harris10a}
+{Harris}, A.~I., {Baker}, A.~J., {Zonak}, S.~G., {et~al.} 2010, \apj, 723, 1139
+
+\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
+  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
+  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
+  \& {Wright}}]{Hinshaw13a}
+{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {et~al.} 2013, \apjs, 208, 19
+
+\bibitem[{{Ivison} {et~al.}(2011){Ivison}, {Papadopoulos}, {Smail}, {Greve},
+  {Thomson}, {Xilouris}, \& {Chapman}}]{Ivison11a}
+{Ivison}, R.~J., {Papadopoulos}, P.~P., {Smail}, I., {et~al.} 2011, \mnras,
+  412, 1913
+
+\bibitem[{{Ivison} {et~al.}(2010{\natexlab{a}}){Ivison}, {Smail},
+  {Papadopoulos}, {Wold}, {Richard}, {Swinbank}, {Kneib}, \&
+  {Owen}}]{Ivison10d}
+{Ivison}, R.~J., {Smail}, I., {Papadopoulos}, P.~P., {et~al.}
+  2010{\natexlab{a}}, \mnras, 404, 198
+
+\bibitem[{{Ivison} {et~al.}(2010{\natexlab{b}}){Ivison}, {Swinbank},
+  {Swinyard}, {Smail}, {Pearson}, {Rigopoulou}, {Polehampton}, {Baluteau},
+  {Barlow}, {Blain}, {Bock}, {Clements}, {Coppin}, {Cooray}, {Danielson},
+  {Dwek}, {Edge}, {Franceschini}, {Fulton}, {Glenn}, {Griffin}, {Isaak},
+  {Leeks}, {Lim}, {Naylor}, {Oliver}, {Page}, {P{\'e}rez Fournon},
+  {Rowan-Robinson}, {Savini}, {Scott}, {Spencer}, {Valtchanov}, {Vigroux}, \&
+  {Wright}}]{Ivison10c}
+{Ivison}, R.~J., {Swinbank}, A.~M., {Swinyard}, B., {et~al.}
+  2010{\natexlab{b}}, \aap, 518, L35
+
+\bibitem[{{Kellermann} \& {Pauliny-Toth}(1973)}]{r9}
+{Kellermann}, K.~I., \& {Pauliny-Toth}, I.~I.~K. 1973, \aj, 78, 828
+
+\bibitem[{{Kellermann} \& {Pauliny-Toth}(1981)}]{Kellermann81a}
+---. 1981, \araa, 19, 373
+
+\bibitem[{{Kellermann} {et~al.}(1969){Kellermann}, {Pauliny-Toth}, \&
+  {Williams}}]{r11-14-18-22-25-32}
+{Kellermann}, K.~I., {Pauliny-Toth}, I.~I.~K., \& {Williams}, P.~J.~S. 1969,
+  \apj, 157, 1
+
+\bibitem[{{Kennicutt}(1998)}]{Kennicutt98a}
+{Kennicutt}, Jr., R.~C. 1998, \araa, 36, 189
+
+\bibitem[{{Lagache} {et~al.}(2005){Lagache}, {Puget}, \& {Dole}}]{Lagache05a}
+{Lagache}, G., {Puget}, J.-L., \& {Dole}, H. 2005, \araa, 43, 727
+
+\bibitem[{{Laing} \& {Peacock}(1980)}]{r10-13-15-19-20-26-29-31}
+{Laing}, R.~A., \& {Peacock}, J.~A. 1980, \mnras, 190, 903
+
+\bibitem[{{Meisenheimer} {et~al.}(1989){Meisenheimer}, {Roser}, {Hiltner},
+  {Yates}, {Longair}, {Chini}, \& {Perley}}]{Meisenheimer89a}
+{Meisenheimer}, K., {Roser}, H.-J., {Hiltner}, P.~R., {et~al.} 1989, \aap, 219,
+  63
+
+\bibitem[{{Micha{\l}owski} {et~al.}(2010){Micha{\l}owski}, {Watson}, \&
+  {Hjorth}}]{Micha10a}
+{Micha{\l}owski}, M.~J., {Watson}, D., \& {Hjorth}, J. 2010, \apj, 712, 942
+
+\bibitem[{{Mullin} {et~al.}(2006){Mullin}, {Hardcastle}, \&
+  {Riley}}]{Mullin06a}
+{Mullin}, L.~M., {Hardcastle}, M.~J., \& {Riley}, J.~M. 2006, \mnras, 372, 113
+
+\bibitem[{{Negrello} {et~al.}(2010){Negrello}, {Hopwood}, {De Zotti}, {Cooray},
+  {Verma}, {Bock}, {Frayer}, {Gurwell}, {Omont}, {Neri}, {Dannerbauer},
+  {Leeuw}, {Barton}, {Cooke}, {Kim}, {da Cunha}, {Rodighiero}, {Cox},
+  {Bonfield}, {Jarvis}, {Serjeant}, {Ivison}, {Dye}, {Aretxaga}, {Hughes},
+  {Ibar}, {Bertoldi}, {Valtchanov}, {Eales}, {Dunne}, {Driver}, {Auld},
+  {Buttiglione}, {Cava}, {Grady}, {Clements}, {Dariush}, {Fritz}, {Hill},
+  {Hornbeck}, {Kelvin}, {Lagache}, {Lopez-Caniego}, {Gonzalez-Nuevo}, {Maddox},
+  {Pascale}, {Pohlen}, {Rigby}, {Robotham}, {Simpson}, {Smith}, {Temi},
+  {Thompson}, {Woodgate}, {York}, {Aguirre}, {Beelen}, {Blain}, {Baker},
+  {Birkinshaw}, {Blundell}, {Bradford}, {Burgarella}, {Danese}, {Dunlop},
+  {Fleuren}, {Glenn}, {Harris}, {Kamenetzky}, {Lupu}, {Maddalena}, {Madore},
+  {Maloney}, {Matsuhara}, {Micha{\l}owski}, {Murphy}, {Naylor}, {Nguyen},
+  {Popescu}, {Rawlings}, {Rigopoulou}, {Scott}, {Scott}, {Seibert}, {Smail},
+  {Tuffs}, {Vieira}, {van der Werf}, \& {Zmuidzinas}}]{Negrello10a}
+{Negrello}, M., {Hopwood}, R., {De Zotti}, G., {et~al.} 2010, Science, 330, 800
+
+\bibitem[{{Oliver} {et~al.}(2012){Oliver}, {Bock}, {Altieri}, {Amblard},
+  {Arumugam}, {Aussel}, {Babbedge}, {Beelen}, {B{\'e}thermin}, {Blain},
+  {Boselli}, {Bridge}, {Brisbin}, {Buat}, {Burgarella},
+  {Castro-Rodr{\'{\i}}guez}, {Cava}, {Chanial}, {Cirasuolo}, {Clements},
+  {Conley}, {Conversi}, {Cooray}, {Dowell}, {Dubois}, {Dwek}, {Dye}, {Eales},
+  {Elbaz}, {Farrah}, {Feltre}, {Ferrero}, {Fiolet}, {Fox}, {Franceschini},
+  {Gear}, {Giovannoli}, {Glenn}, {Gong}, {Gonz{\'a}lez Solares}, {Griffin},
+  {Halpern}, {Harwit}, {Hatziminaoglou}, {Heinis}, {Hurley}, {Hwang}, {Hyde},
+  {Ibar}, {Ilbert}, {Isaak}, {Ivison}, {Lagache}, {Le Floc'h}, {Levenson},
+  {Faro}, {Lu}, {Madden}, {Maffei}, {Magdis}, {Mainetti}, {Marchetti},
+  {Marsden}, {Marshall}, {Mortier}, {Nguyen}, {O'Halloran}, {Omont}, {Page},
+  {Panuzzo}, {Papageorgiou}, {Patel}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen},
+  {Rawlings}, {Raymond}, {Rigopoulou}, {Riguccini}, {Rizzo}, {Rodighiero},
+  {Roseboom}, {Rowan-Robinson}, {S{\'a}nchez Portal}, {Schulz}, {Scott},
+  {Seymour}, {Shupe}, {Smith}, {Stevens}, {Symeonidis}, {Trichas}, {Tugwell},
+  {Vaccari}, {Valtchanov}, {Vieira}, {Viero}, {Vigroux}, {Wang}, {Ward},
+  {Wardlow}, {Wright}, {Xu}, \& {Zemcov}}]{Oliver12a}
+{Oliver}, S.~J., {Bock}, J., {Altieri}, B., {et~al.} 2012, \mnras, 424, 1614
+
+\bibitem[{{Pauliny-Toth} {et~al.}(1966){Pauliny-Toth}, {Wade}, \&
+  {Heeschen}}]{r17-21}
+{Pauliny-Toth}, I.~I.~K., {Wade}, C.~M., \& {Heeschen}, D.~S. 1966, \apjs, 13,
+  65
+
+\bibitem[{{Polletta} {et~al.}(2011){Polletta}, {Nesvadba}, {Neri}, {Omont},
+  {Berta}, \& {Bergeron}}]{Polletta11a}
+{Polletta}, M., {Nesvadba}, N.~P.~H., {Neri}, R., {et~al.} 2011, \aap, 533, A20
+
+\bibitem[{{Rengelink} {et~al.}(1997){Rengelink}, {Tang}, {de Bruyn}, {Miley},
+  {Bremer}, {Roettgering}, \& {Bremer}}]{r23-24}
+{Rengelink}, R.~B., {Tang}, Y., {de Bruyn}, A.~G., {et~al.} 1997, \aaps, 124,
+  259
+
+\bibitem[{{Riechers} {et~al.}(2006){Riechers}, {Walter}, {Carilli}, {Knudsen},
+  {Lo}, {Benford}, {Staguhn}, {Hunter}, {Bertoldi}, {Henkel}, {Menten},
+  {Weiss}, {Yun}, \& {Scoville}}]{Riechers06a}
+{Riechers}, D.~A., {Walter}, F., {Carilli}, C.~L., {et~al.} 2006, \apj, 650,
+  604
+
+\bibitem[{{Riechers} {et~al.}(2011{\natexlab{a}}){Riechers}, {Hodge}, {Walter},
+  {Carilli}, \& {Bertoldi}}]{Riechers11c}
+{Riechers}, D.~A., {Hodge}, J., {Walter}, F., {Carilli}, C.~L., \& {Bertoldi},
+  F. 2011{\natexlab{a}}, \apjl, 739, L31
+
+\bibitem[{{Riechers} {et~al.}(2011{\natexlab{b}}){Riechers}, {Carilli},
+  {Walter}, {Weiss}, {Wagg}, {Bertoldi}, {Downes}, {Henkel}, \&
+  {Hodge}}]{Riechers11d}
+{Riechers}, D.~A., {Carilli}, L.~C., {Walter}, F., {et~al.} 2011{\natexlab{b}},
+  \apjl, 733, L11
+
+\bibitem[{{Riechers} {et~al.}(2011{\natexlab{c}}){Riechers}, {Carilli},
+  {Maddalena}, {Hodge}, {Harris}, {Baker}, {Walter}, {Wagg}, {Vanden Bout},
+  {Wei{\ss}}, \& {Sharon}}]{Riechers11a}
+{Riechers}, D.~A., {Carilli}, C.~L., {Maddalena}, R.~J., {et~al.}
+  2011{\natexlab{c}}, \apjl, 739, L32
+
+\bibitem[{{Riechers} {et~al.}(2011{\natexlab{d}}){Riechers}, {Cooray}, {Omont},
+  {Neri}, {Harris}, {Baker}, {Cox}, {Frayer}, {Carpenter}, {Auld}, {Aussel},
+  {Beelen}, {Blundell}, {Bock}, {Brisbin}, {Burgarella}, {Chanial}, {Chapman},
+  {Clements}, {Conley}, {Dowell}, {Eales}, {Farrah}, {Franceschini}, {Gavazzi},
+  {Glenn}, {Griffin}, {Gurwell}, {Ivison}, {Kim}, {Krips}, {Mortier}, {Oliver},
+  {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen}, {Rawlings},
+  {Raymond}, {Rodighiero}, {Roseboom}, {Rowan-Robinson}, {Scott}, {Seymour},
+  {Smith}, {Symeonidis}, {Tugwell}, {Vaccari}, {Vieira}, {Vigroux}, {Wang},
+  {Wardlow}, \& {Wright}}]{Riechers11b}
+{Riechers}, D.~A., {Cooray}, A., {Omont}, A., {et~al.} 2011{\natexlab{d}},
+  \apjl, 733, L12
+
+\bibitem[{{Riechers} {et~al.}(2013){Riechers}, {Bradford}, {Clements},
+  {Dowell}, {P{\'e}rez-Fournon}, {Ivison}, {Bridge}, {Conley}, {Fu}, {Vieira},
+  {Wardlow}, {Calanog}, {Cooray}, {Hurley}, {Neri}, {Kamenetzky}, {Aguirre},
+  {Altieri}, {Arumugam}, {Benford}, {B{\'e}thermin}, {Bock}, {Burgarella},
+  {Cabrera-Lavers}, {Chapman}, {Cox}, {Dunlop}, {Earle}, {Farrah}, {Ferrero},
+  {Franceschini}, {Gavazzi}, {Glenn}, {Solares}, {Gurwell}, {Halpern},
+  {Hatziminaoglou}, {Hyde}, {Ibar}, {Kov{\'a}cs}, {Krips}, {Lupu}, {Maloney},
+  {Martinez-Navajas}, {Matsuhara}, {Murphy}, {Naylor}, {Nguyen}, {Oliver},
+  {Omont}, {Page}, {Petitpas}, {Rangwala}, {Roseboom}, {Scott}, {Smith},
+  {Staguhn}, {Streblyanska}, {Thomson}, {Valtchanov}, {Viero}, {Wang},
+  {Zemcov}, \& {Zmuidzinas}}]{Riechers13a}
+{Riechers}, D.~A., {Bradford}, C.~M., {Clements}, D.~L., {et~al.} 2013, \nat,
+  496, 329
+
+\bibitem[{{Sanders} {et~al.}(1988){Sanders}, {Soifer}, {Elias}, {Madore},
+  {Matthews}, {Neugebauer}, \& {Scoville}}]{Sanders88}
+{Sanders}, D.~B., {Soifer}, B.~T., {Elias}, J.~H., {et~al.} 1988, \apj, 325, 74
+
+\bibitem[{{Scott} {et~al.}(2011){Scott}, {Lupu}, {Aguirre}, {Auld}, {Aussel},
+  {Baker}, {Beelen}, {Bock}, {Bradford}, {Brisbin}, {Burgarella}, {Carpenter},
+  {Chanial}, {Chapman}, {Clements}, {Conley}, {Cooray}, {Cox}, {Dowell},
+  {Eales}, {Farrah}, {Franceschini}, {Frayer}, {Gavazzi}, {Glenn}, {Griffin},
+  {Harris}, {Ibar}, {Ivison}, {Kamenetzky}, {Kim}, {Krips}, {Maloney},
+  {Matsuhara}, {Mortier}, {Murphy}, {Naylor}, {Neri}, {Nguyen}, {Oliver},
+  {Omont}, {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen},
+  {Rawlings}, {Raymond}, {Riechers}, {Rodighiero}, {Roseboom},
+  {Rowan-Robinson}, {Scott}, {Seymour}, {Smith}, {Symeonidis}, {Tugwell},
+  {Vaccari}, {Vieira}, {Vigroux}, {Wang}, {Wright}, \& {Zmuidzinas}}]{Scott11a}
+{Scott}, K.~S., {Lupu}, R.~E., {Aguirre}, J.~E., {et~al.} 2011, \apj, 733, 29
+
+\bibitem[{{Simpson} {et~al.}(2012){Simpson}, {Smail}, {Swinbank}, {Alexander},
+  {Auld}, {Baes}, {Bonfield}, {Clements}, {Cooray}, {Coppin}, {Danielson},
+  {Dariush}, {Dunne}, {de Zotti}, {Harrison}, {Hopwood}, {Hoyos}, {Ibar},
+  {Ivison}, {Jarvis}, {Lapi}, {Maddox}, {Page}, {Riechers}, {Valiante}, \& {van
+  der Werf}}]{Simpson12a}
+{Simpson}, J.~M., {Smail}, I., {Swinbank}, A.~M., {et~al.} 2012, \mnras, 426,
+  3201
+
+\bibitem[{{Smol{\v c}i{\'c}} \& {Riechers}(2011)}]{Smolcic11a}
+{Smol{\v c}i{\'c}}, V., \& {Riechers}, D.~A. 2011, \apj, 730, 64
+
+\bibitem[{{Solomon} \& {Vanden Bout}(2005)}]{Solomon05a}
+{Solomon}, P.~M., \& {Vanden Bout}, P.~A. 2005, \araa, 43, 677
+
+\bibitem[{{Swinbank} {et~al.}(2010){Swinbank}, {Smail}, {Longmore}, {Harris},
+  {Baker}, {De Breuck}, {Richard}, {Edge}, {Ivison}, {Blundell}, {Coppin},
+  {Cox}, {Gurwell}, {Hainline}, {Krips}, {Lundgren}, {Neri}, {Siana},
+  {Siringo}, {Stark}, {Wilner}, \& {Younger}}]{Swinbank2010a}
+{Swinbank}, A.~M., {Smail}, I., {Longmore}, S., {et~al.} 2010, \nat, 464, 733
+
+\bibitem[{{Swinbank} {et~al.}(2011){Swinbank}, {Papadopoulos}, {Cox}, {Krips},
+  {Ivison}, {Smail}, {Thomson}, {Neri}, {Richard}, \& {Ebeling}}]{Swinbank11a}
+{Swinbank}, A.~M., {Papadopoulos}, P.~P., {Cox}, P., {et~al.} 2011, \apj, 742,
+  11
+
+\bibitem[{{Tacconi} {et~al.}(2006){Tacconi}, {Neri}, {Chapman}, {Genzel},
+  {Smail}, {Ivison}, {Bertoldi}, {Blain}, {Cox}, {Greve}, \&
+  {Omont}}]{Tacconi06a}
+{Tacconi}, L.~J., {Neri}, R., {Chapman}, S.~C., {et~al.} 2006, \apj, 640, 228
+
+\bibitem[{{Tacconi} {et~al.}(2008){Tacconi}, {Genzel}, {Smail}, {Neri},
+  {Chapman}, {Ivison}, {Blain}, {Cox}, {Omont}, {Bertoldi}, {Greve},
+  {F{\"o}rster Schreiber}, {Genel}, {Lutz}, {Swinbank}, {Shapley}, {Erb},
+  {Cimatti}, {Daddi}, \& {Baker}}]{Tacconi08a}
+{Tacconi}, L.~J., {Genzel}, R., {Smail}, I., {et~al.} 2008, \apj, 680, 246
+
+\bibitem[{{Tacconi} {et~al.}(2010){Tacconi}, {Genzel}, {Neri}, {Cox}, {Cooper},
+  {Shapiro}, {Bolatto}, {Bouch{\'e}}, {Bournaud}, {Burkert}, {Combes},
+  {Comerford}, {Davis}, {Schreiber}, {Garcia-Burillo}, {Gracia-Carpio}, {Lutz},
+  {Naab}, {Omont}, {Shapley}, {Sternberg}, \& {Weiner}}]{Tacconi10a}
+{Tacconi}, L.~J., {Genzel}, R., {Neri}, R., {et~al.} 2010, \nat, 463, 781
+
+\bibitem[{{Vieira} {et~al.}(2010){Vieira}, {Crawford}, {Switzer}, {Ade},
+  {Aird}, {Ashby}, {Benson}, {Bleem}, {Brodwin}, {Carlstrom}, {Chang}, {Cho},
+  {Crites}, {de Haan}, {Dobbs}, {Everett}, {George}, {Gladders}, {Hall},
+  {Halverson}, {High}, {Holder}, {Holzapfel}, {Hrubes}, {Joy}, {Keisler},
+  {Knox}, {Lee}, {Leitch}, {Lueker}, {Marrone}, {McIntyre}, {McMahon}, {Mehl},
+  {Meyer}, {Mohr}, {Montroy}, {Padin}, {Plagge}, {Pryke}, {Reichardt}, {Ruhl},
+  {Schaffer}, {Shaw}, {Shirokoff}, {Spieler}, {Stalder}, {Staniszewski},
+  {Stark}, {Vanderlinde}, {Walsh}, {Williamson}, {Yang}, {Zahn}, \&
+  {Zenteno}}]{Vieira10a}
+{Vieira}, J.~D., {Crawford}, T.~M., {Switzer}, E.~R., {et~al.} 2010, \apj, 719,
+  763
+
+\bibitem[{{Wilson} {et~al.}(1970){Wilson}, {Jefferts}, \&
+  {Penzias}}]{Wilson70a}
+{Wilson}, R.~W., {Jefferts}, K.~B., \& {Penzias}, A.~A. 1970, \apjl, 161, L43
+
+\end{thebibliography}
 
@@
 \hspace{-1cm}
-\includegraphics[width=1.15\textwidth]{Figure/CorrelationPlot__thick_500_500.pdf}
+\includegraphics[width=1.15\textwidth]{Figure/CorrelationPlot__thick_500_500_cmyk}
 \end{minipage}
@@
 \begin{minipage}{0.5\textwidth}
-\includegraphics[width=1.15\textwidth]{Figure/CorrelationPlot__thin_testSMA.pdf}
+\includegraphics[width=1.15\textwidth]{Figure/CorrelationPlot__thin_testSMA_cmyk.pdf}
 \end{minipage}

### 2015-08-22 skeleton.tex
Sync with ms.tex in submit/

@@
-% submission prep
-% what does this mean
-% Multiplication
-% Explicit multiplication signs (dots or crosses), except for scientific notation, grids, vector operators, and when a multiplication wraps to a following line, are omitted.
-% online said;: should go in alphabetical order, so should I do Ivison 11 before R11?
-%\documentclass[12pt,preprint]{aastex}
-\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
+\documentclass[iop]{emulateapj}
+%\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
 \usepackage[breaklinks,colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
@@
 \usepackage{amsmath}
-\usepackage{natbib}
-\citestyle{aa}
+%\usepackage{natbib}
+%\citestyle{aa}
 \shorttitle{Study of a strongly-lensed type-2 quasar host SMG at $z$\,=\,2.221}
@@
 Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (12.6\,$\pm$\,2.0)\,Jy\,km\,s\pmOne, we derive
- a lensing- and excitation-corrected CO line luminosity of \Lp = (3.4\,$\pm$\,0.7) $\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling performed on the 1\,mm continuum emission.
+ a lensing- and excitation-corrected CO line luminosity of \Lp = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling performed on the 1\,mm continuum emission.
  This translates to a molecular gas mass of $M_\textrm{gas}$ = (2.7\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,\Msun.
@@
 \centering
-\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_model_goodfit1970}
-\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_goodfit1970}
+\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_model_goodfit1970_cmyk}
+\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_goodfit1970_cmyk}
 \caption{Double-lens modeling of SMM\,J0939 using {\sc uvmcmcfit} on the SMA 1\,mm continuum data.
@@
 the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
-%\input{table_lensParams}
+\input{table_lensParams}
 
@@
 estimate the flux density of the lobes at the frequency of our continuum measurement.
-%\input{table_SED}
+\input{table_SED}
 Following Equation (1) in \citet{Cleary07a}, the fit to the lobe emission can be expressed as a parabolic function:
@@
 \centering
-\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED2.pdf}
+\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED2}
 \caption{SEDs of 3C220.3 (solid purple line) and SMM\,J0939 (dashed purple line and solid cyan line) including the new measurements presented in this paper.
@@
 
-%\input{table_mbb}
+\input{table_mbb}
 The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in the Appendix. The best-fit solution of an optically thin
@@
 where $\nu_\textrm{CO(3-2)}$ is the rest-frame frequency of the \CO transition line in GHz, $D_L$ is the luminosity distance in Mpc, $\mu_\textrm{L}$ is the lensing magnification factor, and $I_\textrm{CO(3-2)}$ is the \CO line flux in Jy\,\,km\,\,s\pmOne.
-This corresponds to \Lp = (3.42\,$\pm$\,0.71) $\times$~10$^{10}$\,(10.1/$\mu_\textrm{L}$)~\LpU, hence
-the inferred total molecular gas mass is $M_\textrm{gas}$ = (2.74\,$\pm$\,0.57) $\times$\,\,10$^{10}$\,\Msun\, after correcting for lensing magnification.
+This corresponds to \Lp = (3.42\,$\pm$\,0.71)\,$\times$~10$^{10}$\,(10.1/$\mu_\textrm{L}$)~\LpU, hence
+the inferred total molecular gas mass is $M_\textrm{gas}$ = (2.74\,$\pm$\,0.57)\,$\times$\,\,10$^{10}$\,\Msun\, after correcting for lensing magnification.
 We assumed a conversion factor of $\alpha_\textrm{CO}$ = 0.8\,\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
@@
 The inferred surface densities of SMM\,J0939 follow a universal Schmidt-Kennicutt relation between the star formation rate
-surface density and the molecular gas surface density: $\Sigma_\textrm{SF}$ = 9.3 ($\pm$\,2) $\times$\,10$^{-5}$ ($M_\textrm{gas}$/2$\pi R_\textrm{1/2}^2)^{1.71(\pm\,0.05)}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
+surface density and the molecular gas surface density: $\Sigma_\textrm{SF}$ = 9.3 ($\pm$\,2)\,$\times$\,10$^{-5}$ ($M_\textrm{gas}$/2$\pi R_\textrm{1/2}^2)^{1.71(\pm\,0.05)}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
 galaxies
@@
 \section{Discussion And Conclusions}
-%\input{table_compareSMG}
+\input{table_compareSMG}
 We present the detection of \CO line emission toward SMM\,J0939+8315, a strongly-lensed SMG that is hosting a type-2 quasar, refining the redshift
@@
 consortium universities.
-%Facilities: \facility{CARMA}
-\newpage
-\bibliographystyle{apj}
+
+Facilities: \facility{CARMA}
+
+%\bibliographystyle{apj}
 %\bibliography{J0939}
@@
 \centering
-% minipage
-\begin{minipage}{0.5\textwidth}
 \hspace{-1cm}
-\includegraphics[width=1.15\textwidth]{Figure/CorrelationPlot__thick_500_500_cmyk}
-\end{minipage}
-\hspace{-0.9cm}
-\begin{minipage}{0.5\textwidth}
-\includegraphics[width=1.15\textwidth]{Figure/CorrelationPlot__thin_testSMA_cmyk.pdf}
-\end{minipage}
+\includegraphics[width=0.55\textwidth]{f7.eps}
+\hspace{-1.15cm}
+\includegraphics[width=0.55\textwidth]{f8.eps}
+\hspace{-1cm}
 \caption{Correlation plots from the fitted SEDs, using an optically thick

### 2015-08-23 skeleton.tex
correct for grammar from Mike Jones's comments

@@
 SMGs, with a lensing-magnified flux density of $S_\textrm{250\micron}$\,=\,440\,$\pm$\,15 mJy.
-Previous detections of C {\scriptsize\sc IV}\,1459\AA\
- and He {\scriptsize\sc II}\,1640\AA\ line emission toward SMM\,J0939
+Previous detections of C~{\scriptsize\sc IV}~1459\AA\
+ and He~{\scriptsize\sc II}~1640\AA\ line emission toward SMM\,J0939
  placed the redshift of this galaxy at $z$\,=\,2.221, and suggested the presence of an active galactic nucleus (AGN),
@@
 Observations of the \CO rotational transition ($\nu_\textrm{rest}$\,=\,345.7959899 GHz) toward the background galaxy SMM
-J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{\rm obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; PI: Riechers).
+J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{\rm obs}$\,=\,107.357\,\,GHz (2.79\,\,mm; program ID: cf0142; PI: Riechers).
 The 3\,mm receivers were used to cover the redshifted \CO line and the nearby observed-frame 2.88\,mm continuum emission.
@@
  conversion factor from higher-$J$ CO lines. \par
-Prior to the observations of the ground state CO transition line in SMGs, it has been assumed that the molecular gas in the
-  ISM traceable by CO lines is thermalized owing to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
+Prior to the observations of the ground state CO transition line in SMGs, it had been assumed that the molecular gas in the
+  ISM traceable by CO lines was thermalized owing to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
    Yet, recent observations of this line have demonstrated that SMGs can indeed be subthermally excited
@@
 We note that a factor of $\sim$\,2 uncertainty arises from the dust mass estimate.
-The derived gas-to-dust ratio is in good agreement with the
-values found in other SMGs within the uncertainties \citep{Coppin08a,Micha10a,Riechers11c}.
+The derived gas-to-dust ratio is in good agreement, within the uncertainties,
+ with the
+values found in other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.
 
@@
 \hspace{-1cm}
-\includegraphics[width=0.55\textwidth]{f7.eps}
+\includegraphics[width=0.55\textwidth]{Figure/CorrelationPlot__thick_500_500_cmyk}
 \hspace{-1.15cm}
-\includegraphics[width=0.55\textwidth]{f8.eps}
+\includegraphics[width=0.55\textwidth]{Figure/CorrelationPlot__thin_testSMA_cmyk.pdf}
 \hspace{-1cm}

### 2015-08-24 Code/SED_fittingparamPlot.py
fix the x-axis label from labmda_0 to lambda_0 * (1+z), also change the code for x ticks label, so that it is not overlapping

@@ -503,11 +503,20 @@ def triplot(chain, color=True, weights=None, interpolate=False, smooth=True,
 
     for i in range(len(parameters)):
         # for j in len(parameters[np.where(i <= parameters)]:
+
         for j in range(len(parameters)):
+
             ii = i
             jj = len(parameters) - j - 1
+#            print "jj %d: " %(jj)
 
-            xmajorLocator = MaxNLocator(nbins=4, prune='both')
+            if (jj == len(parameters) - 1) and (ii == jj):
+#                 print ii
+#                 print jj
+                # the following line added to make the xtick labels of lambda_0 (1+z) to show clearly
+                xmajorLocator = MaxNLocator(nbins=3, prune='both')
+            else:
+                xmajorLocator = MaxNLocator(nbins=4, prune='both')
             ymajorLocator = MaxNLocator(nbins=4, prune='both')
 
             if j <= len(parameters) - i - 1:
@@ -780,9 +789,9 @@ if __name__ == '__main__':
     chi2 = BestFit()
 
     chainPlot, inj_best = makeChainTriPlot()
-    triplotLabel = ['T/(1+z)', r'$\beta$', r'$\alpha$', r'$f_{\rm norm}$', r'$\lambda_0$']
+    triplotLabel = [r'$T/(1+z)$', r'$\beta$', r'$\alpha$', r'$f_{\rm norm}$', r'$\lambda_0 (1+z)$']
     if res._opthin == True:
-        triplotLabel.remove(r'$\lambda_0$')
+        triplotLabel.remove(r'$\lambda_0 (1+z)$')
     if res._noalpha == True:
         triplotLabel.remove(r'$\alpha$')
 #    triplot(chainPlot, title=(filename.replace('.h5', ' ') + 'Parameters'),            labels=triplotLabel, inj=inj_best, saveFig=save_op)

### 2015-08-25 Code/SEDfit.py
change upper limit on core

@@ -103,10 +103,10 @@ Avg_cont_freq = 104.21e9
 Core_3c220dot3_Jy = np.array([0.8e-3, 0.17e-3])     # Jy
 Core_3c220dot3_Hz = np.array([9.e9, 4.86e9])    # Hz
 
-# Our Data: [peak, integrated, difference]
-Point_Continuum_Jy = np.array([4.93e-3, 7.53e-3, 2.60e-3])
+# Our Data: [peak, integrated, integrated-fit]
+Point_Continuum_Jy = np.array([4.93e-3, 7.53e-3, 2.29e-3])
 Point_Cont_Hz = np.array([1.042e11, 1.042e11, 1.02e11])     # Hz
-Point_error_Jy = np.array([0.31e-3, 1.42e-3, 1.45e-3])    # Jy
+Point_error_Jy = np.array([0.31e-3, 1.42e-3, 0.])    # Jy
 
 
 ########################################
@@ -352,6 +352,10 @@ ax_top.set_xlabel(r'$\nu_{\rm obs}$ [GHz]', size=16, fontweight='bold')
 ax_top.set_viewlim_mode("transform")
 ax_top.axis["right"].toggle(ticklabels=False)
 
+ax.set_xscale('log')
+ax.set_yscale('log')
+ax_top.set_xscale('log')
+ax_top.set_yscale('log')
 
 ############################################
 # Plot foreground galaxy data and fit
@@ -374,15 +378,18 @@ ax.errorbar(GHz2um(Radio_Hz[6:] * Hz2GHz),
             Radio_error[6:] * Jy2mJy,
             fmt='.k', ecolor='darkgray', label='Previous Data', ms=11, capsize=8, elinewidth=4, capthick=1.5) # mJy
 
-ax.errorbar(GHz2um(Point_Cont_Hz * Hz2GHz),
-            Point_Continuum_Jy * Jy2mJy, Point_error_Jy * Jy2mJy,
+ax.errorbar(GHz2um(Point_Cont_Hz[:-1] * Hz2GHz),
+            Point_Continuum_Jy[:-1] * Jy2mJy, Point_error_Jy[:-1] * Jy2mJy,
             fmt='.r', ecolor='darkgrey', label='New continuum data', ms=13, capsize=8, elinewidth=4, capthick=1.5)
+
+# new upper core limit
+ax.errorbar(GHz2um(Point_Cont_Hz[-1] * Hz2GHz),
[…]

### 2015-08-26 Code/FgContIm.py
change setting for Figure 1, 2 to show better, works with cmyk

@@ -70,10 +70,11 @@ def sigma_contour_lowSNR(sigma):
 def standard_plot_setup(sp, ra_center, dec_center, size, tc='black'):
     sp.set_frame_color('black')
     sp.frame.set_linewidth(1)
-    sp.set_system_latex(True)
+#     sp.set_system_latex(True)
+#    sp.set_labels_latex(True)
     sp.recenter(x=ra_center, y=dec_center, radius=size)   # width = blah, height = blah     # Scaling and panning
 
-    sp.tick_labels.set_font(size='large', weight='bold')      # size='10'
+    sp.tick_labels.set_font(size='large', weight='bold')
     sp.tick_labels.set_style('colons')
     sp.tick_labels.set_xformat('hh:mm:ss')
     sp.tick_labels.set_yformat('dd:mm:ss')
@@ -83,11 +84,11 @@ def standard_plot_setup(sp, ra_center, dec_center, size, tc='black'):
     sp.ticks.set_minor_frequency(4)
     # sp.ticks.set_xspacing(45*15/3600.)        # deg
 
-    sp.axis_labels.set_font(size='large', weight='bold')      # (size='12')
+    sp.axis_labels.set_font(size='large', weight='bold')
     sp.axis_labels.set_xtext('Right Ascension (J2000)')
     sp.axis_labels.set_ytext('Declination (J2000)')
     sp.axis_labels.set_xpad(3)
-    sp.axis_labels.set_ypad(-40)
+    sp.axis_labels.set_ypad(-35)
     sp.axis_labels.set_xposition('bottom')
 
 

### 2015-08-26 Code/Plot_Image.py

@@ -5,6 +5,11 @@ import matplotlib.pyplot as plt
 import matplotlib as mpl
 from FgContIm import *
 
+
+font = {'family': 'Arial',
+        'weight': 'normal'}
+mpl.rc('font', **font)
+
 path = '../FinalData/'
 Plotpath = '../Figure/'
 label = dict.fromkeys(['VLA', 'cont', 'lin', 'SMA'])
@@ -29,7 +34,7 @@ sigma_SMA           = 0.000836951
 vla_min             = -0.000270099
 vla_max             = 0.00960869
 max_cont            = 4.796309E-03
-min_cont            = -2.038660E-03
+min_cont            = -0.02 # -2.038660E-03
 max_line            = 8.93562
 min_line            = -8.836704
 SMA_min             = -0.00210908
@@ -64,7 +69,7 @@ dy                  = 0.90
 
 fcont = aplpy.FITSFigure(label['cont'][0], \
         figure=fig, subplot=[x0,row_a,width,dy])
-fcont.show_colorscale(cmap=mpl.cm.jet, stretch='log', vmin=min_cont, vmax=max_cont, vmid=-100000)   # vmid= min_cont-0.0001 ~ orange; min_cont-0.0000001 ~ red
+fcont.show_colorscale(cmap=mpl.cm.jet, stretch='log', vmin=min_cont, vmax=max_cont, vmid=-10000000)   # vmid= min_cont-0.0001 ~ orange; min_cont-0.0000001 ~ red
 
 fvla = aplpy.FITSFigure(label['VLA'][0], \
         figure=fig, subplot=[x0+width+2*x_gap, row_a, width, dy])
@@ -73,17 +78,18 @@ fvla.show_grayscale(stretch='log', vmin=vla_min, vmax=vla_max, vmid=-0.001)
 
 flin = aplpy.FITSFigure(label['lin'][0], \
         figure=fig_line, subplot=[x0,row_a,width,dy])
-flin.show_colorscale(cmap=mpl.cm.jet, vmin=min_line, vmax=max_line, vmid=-2500, stretch='log')
+flin.show_colorscale(cmap=mpl.cm.jet, vmin=min_line, vmax=max_line, vmid=-10, stretch='log')
+
 fSMA = aplpy.FITSFigure(label['SMA'][0], figure=fig_line, subplot=[x0+width+2*x_gap, row_a, width, dy])
 fSMA.show_grayscale(stretch='log', vmin=SMA_min, vmax=SMA_max, vmid=-0.1)
 
[…]

### 2015-10-27 Code/Plot_Image.py
Align left panels of figure 1, 2; added SMA peak on VLA im

@@ -44,7 +44,7 @@ VLA_ra              = 1.448437499980E+02
 VLA_dec             = 8.325666666846E+01
 sizep               = 0.0025
 sizePcont_noise     = 0.020
-sizePLine           = 0.012
+sizePLine           = 0.02 #0.012
 ra_center           = 144.84933
 dec_center          = 83.257175
 
@@ -61,6 +61,20 @@ width               = 0.35
 x_gap               = 0.05
 x0                  = 0.10
 dy                  = 0.90
+
+
+# positions for crosses, centering on SMA peaks
+RA1  = 144.845625      # 09:39:22.950
+Dec1 = 83.2575472222222  # +83:15.27.17
+
+
+RA2  = 144.850916666  # 09:39:24.220
+Dec2 = 83.2575047   # +83:15:27.017
+
+
+RA3  = 144.853454166      # 09:39:24.829
+Dec3 = 83.257044         # +83:15.25.36
+
 
 
 ########################################
@@ -141,6 +155,14 @@ markers_cross(fvla, ra_cross, dec_cross)# , layer='marker_set_1')
 markers_cross(fcont, ra_cross, dec_cross, ec='black') #), layer='marker_set_1')
 markers_cross(flin, ra_cross, dec_cross, ec='black')#, layer='marker_set_1', s=500)
 markers_cross(fSMA, ra_cross, dec_cross)#, layer='marker_set_1')
+
+########################################
+# markers to satisfy referee
+########################################
+markers_cross(fvla, RA1, Dec1, ec='cyan')
+markers_cross(fvla, RA2, Dec2, ec='cyan')
+markers_cross(fvla, RA3, Dec3, ec='cyan')
+
 
 ########################################
 # Labels

### 2015-10-27 skeleton.tex
push changes s.t. content same as 1st submission ms.{tex,pdf}; this has more comments, external bib and fig name different

@@
 \usepackage{amsmath}
-%\usepackage{natbib}
-%\citestyle{aa}
+\usepackage{natbib}
+\citestyle{aa}
 \shorttitle{Study of a strongly-lensed type-2 quasar host SMG at $z$\,=\,2.221}
@@
 the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
-This SMG, which hosts a type-2 quasar is gravitationally lensed by the radio galaxy 3C220.3 at $z$ = 0.685.
-The underlying 104 GHz continuum emission toward 3C220.3 is detected with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy.
+SMM\,J0939+8315 hosts a type-2 quasar, and is gravitationally lensed by the radio galaxy 3C220.3 at $z$ = 0.685.
+The 104 GHz continuum emission underlying the CO line is detected toward 3C220.3 with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy.
 Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (12.6\,$\pm$\,2.0)\,Jy\,km\,s\pmOne, we derive
- a lensing- and excitation-corrected CO line luminosity of \Lp = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling performed on the 1\,mm continuum emission.
- This translates to a molecular gas mass of $M_\textrm{gas}$ = (2.7\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,\Msun.
+ a lensing- and excitation-corrected CO line luminosity of \Lp = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU\ for the SMG, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling performed on the 1\,mm continuum emission.
+ This translates to a molecular gas mass of $M_\textrm{gas}$ = (2.7\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\Msun.
 Fitting spectral energy distribution models to the (sub)-millimeter data of this SMG yields a dust temperature of $T_\textrm{dust}$ =
@@
 J0939+8315
-and other high-redshift SMGs and type-2 quasars shows that SMM\,J0939+8315 is a faithful representation of both populations, suggesting that
+and other high-redshift SMGs and type-2 quasars shows that it is a faithful representation of both populations, suggesting that
 SMM\,J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase.
@@
 galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}.
-These galaxies are luminous at submillimeter (submm) wavelengths due to the re-radiation of dust emission peaking at
+These galaxies are luminous at submillimeter (submm) wavelengths due to the reprocessed stellar light that is being emitted as dust emission peaking at
 rest-frame far-infrared (FIR) wavelengths \citep{blain02a}.
 In the past $\sim$\,5~years, considerable amounts of effort have been invested into follow-up observations of SMGs that were
-discovered in large sky surveys \citep[\eg H-ATLAS, HerMES, SPT; ][]{Eales10a,Oliver12a,Vieira10a}, conducted using (sub)-mm facilities.
+discovered in large sky surveys \citep[\eg H-ATLAS, SPT, HerMES; ][]{Eales10a,Carlstrom11a,Oliver12a}, conducted using (sub)-mm facilities.
 These detailed studies have led to growing consensus that SMGs are a population of high-redshift galaxies that are extremely dusty, gas-rich,
-  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) at the infrared wavebands, with high star formation rates \citep[$\gtrsim $ 500 \Msun yr\pmOne; \eg][]{Lagache05a,Casey14a}.
+  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) at the infrared wavebands, with high star formation rates \citep[$\gtrsim $ 500 \Msun yr\pmOne; see \eg reviews by][]{Lagache05a,Casey14a}.
 
-  To characterize the physical properties of the gas reservoirs in the interstellar medium (ISM) where active star formation takes place, carbon monoxide ($^{12}$CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[See \eg][]{Solomon05a,Carilli13a}.
+  To characterize the physical properties of the gas reservoirs in the interstellar medium (ISM) where active star formation takes place, carbon monoxide ($^{12}$CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[see \eg reviews by][]{Solomon05a,Carilli13a}.
 Recent observations of CO in SMGs at $z$\,$\sim$\,1\,--\,3 have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Riechers11c,Riechers11d,Ivison11a,Bothwell13a}.
@@
 Many recent detailed studies have been carried out on SMGs that are gravitationally lensed,
- as lensing amplifies the intrinsic luminosities of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a,Oliver12a}, and making follow-up studies considerably less time consuming.
+ as lensing amplifies the intrinsic fluxes of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a,Oliver12a}, and making follow-up studies considerably less time consuming.
 A particularly interesting and peculiar lensing system was discovered serendipitously in a study carried out with the {\it Herschel Space Telescope}, in which
@@
  and He~{\scriptsize\sc II}~1640\AA\ line emission toward SMM\,J0939
- placed the redshift of this galaxy at $z$\,=\,2.221, and suggested the presence of an active galactic nucleus (AGN),
-indicating a type-2 quasar in this SMG \citep[hereafter H14]{Haas14}.
+ placed the redshift of this galaxy at $z$\,=\,2.221, and suggested the presence of an active galactic nucleus (AGN) in the form of a type-2 quasar in this SMG \citep[hereafter H14]{Haas14}.
 
 In this paper, we present the detection of \CO line emission toward the background SMG obtained with the Combined
-Array for Research in Millimeter Astronomy (CARMA), which refines the redshift, and permits the study of the physical conditions in the ISM of SMM\,J0939 in great detail.
-We report the detection of the underlying continuum emission and place constraints on the spectral energy distribution (SED) of the foreground FR-II galaxy at millimeter (mm) wavelengths ($\sim$\,104 GHz).
+Array for Research in Millimeter Astronomy (CARMA), which confirms and refines the redshift, and permits a study of the physical conditions in the ISM of SMM\,J0939 in great detail.
+We report the detection of the continuum emission underlying the CO line and place constraints on the spectral energy distribution (SED) of the foreground FR-II galaxy at millimeter (mm) wavelengths ($\sim$\,104 GHz).
 Based on the magnification factor derived from our lens model, we infer various intrinsic properties of SMM\,J0939.
 We
-conclude this paper by comparing our findings to other similarly bright, strongly-lensed SMGs, as well as other type-2 quasars at $z$\,$\sim$\,2 .
+conclude this paper by comparing our findings to other similarly bright, strongly-lensed SMGs, as well as other type-2 quasars at $z$\,$\sim$\,2$-$3.
 
@@
 The continuum image is created by
-averaging over all line-free channels, this yields a synthesized clean beam of 12\farcs0\,$\times$\,6\farcs5, $-$55.9$\degr$ east of north, and an rms noise of $\sigma_\textrm{cont}$ = 0.50\,\,mJy\,\,beam\pmOne\ over 6.8 GHz.
+averaging over all line-free channels; this yields a synthesized clean beam of 12\farcs0\,$\times$\,6\farcs5, $-$55.9$\degr$ east of north, and an rms noise of $\sigma_\textrm{cont}$ = 0.50\,\,mJy\,\,beam\pmOne\ over 6.8 GHz.
 %7416.192 MHz = (total(1520) - edge * 2 * nwin(16))*5.208 MHz 
@@
 \subsection{New Results: 3C220.3}
-Averaging over all line-free channels, we detect continuum emission at $\sim$\,9$\sigma$ at an averaged frequency of $\nu_\textrm{cont}$\,=\,104.2106 GHz ($\sim$\,2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$\,1.7 mm) at $z$\,=\,0.685.
+Averaging over all line-free channels, we detect continuum emission at $\sim$\,9$\sigma$ significance at an averaged frequency of $\nu_\textrm{cont}$\,=\,104.2106 GHz ($\sim$\,2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$\,1.7 mm) at $z$\,=\,0.685.
 In this lensing system, the
@@
 The frequency range of our observations covers the HCO$^+$($J$\,=\,2\,\rarr\,1), HNC($J$\,=\,2\,$\rightarrow$\,1), and H$_2$O(3$_{13}$\,\rarr\,2$_{20}$)
-transition line emission in the foreground galaxy, at
+transition lines in the foreground galaxy, at
 the redshifted frequencies of 105.86, 107.71, and 108.79\,\,GHz, respectively. We establish 3$\sigma$ upper limits employing a typical FWHM line width of
@@
 lens modeling on the SMA 1\,mm continuum data presented by H14 of this system. Lens modeling is carried out in the visibility
-({\it uv-}) plane using the updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}\footnote{\url{https://github.com/sbussmann/uvmcmcfit}}
+({\it uv-}) plane using an updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}\footnote{\url{https://github.com/sbussmann/uvmcmcfit}}
 \citep{Bussmann15a}. The code uses an affine-invariant Markov chain Monte Carlo (MCMC) approach to sample the posterior
@@
 lens is sampled with respect to that of
-the primary lens ($\Delta \alpha_\textrm{lens0}$ and $\Delta \delta_\textrm{lens0}$), we therefore do not consider ($\Delta \alpha_\textrm{lens1}$ and $\Delta \delta_\textrm{lens1}$)  as free parameters.
+the primary lens ($\Delta \alpha_\textrm{lens0}$ and $\Delta \delta_\textrm{lens0}$); we therefore do not consider ($\Delta \alpha_\textrm{lens1}$ and $\Delta \delta_\textrm{lens1}$)  as free parameters.
 The source (SMM\,J0939) is parameterized by
@@
 \centering
-\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_model_goodfit1970_cmyk}
-\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_goodfit1970_cmyk}
+\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_model_goodfit1970_cmyk.eps}
+\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_goodfit1970_cmyk.eps}
 \caption{Double-lens modeling of SMM\,J0939 using {\sc uvmcmcfit} on the SMA 1\,mm continuum data.
@@
 However, the deconvolved spatial size of the source matching that in the resolved image (see Figure~\ref{fig:cont}) is
-suggestive of a marginally resolved detection of the extended lobe components with non-negligible emission.
+suggestive of a marginally resolved detection of the extended lobe components.
 This is plausible given that the orientation of the synthesized beam in our observations is in alignment with the
@@
 \begin{equation}
-\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
+\log F_{\nu}^\mathrm{lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_\mathrm{t})^2  + \log (\exp({\frac{\nu}{\nu_c^\mathrm{lobe}}}))
 \end{equation}
-where $F_{\nu}^{\mathrm lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending
-of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches
+where $F_{\nu}^\mathrm{lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending
+of the parabola, $\nu_\mathrm{t}$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches
 unity, and $\nu_c^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy
@@
 measurement (Figure~\ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests a
-dominant contribution from the lobes, and that the peak flux density does not correspond to emission toward
+dominant contribution from the lobes, and that the peak flux density is not dominated by emission toward
 the core. Moreover, the peak position of the 104\,\,GHz continuum is
-centered toward the northern lobe (Figure~\ref{fig:cont}), which further supports our argument. 
+centered toward the brighter northern lobe (Figure~\ref{fig:cont}), which further supports our argument. 
 Consequently, a conservative upper limit of $S_\nu$\,$<$\,4.93 mJy on the core emission can be established using the measured peak flux density. Yet, by considering the 
@@
  taken 
- across different epochs. 
+ across different epochs, and the core may be time-variable.
 \par
 Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested that spectra of hotspots are flat up to optical frequencies, where some exhibit spectral steepening in cm and mm wavelengths (\eg 3C123).
-At the resolution of our observations, it is unclear whether the measured flux density is dominated by emission from the compact hotspot or that from the surrounding diffuse lobe components.
+At the resolution of our observations, it remains unclear whether the measured flux density is dominated by emission from the compact hotspots or that from the surrounding diffuse lobe components.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED2}
+\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED2_cmyk.eps}
 \caption{SEDs of 3C220.3 (solid purple line) and SMM\,J0939 (dashed purple line and solid cyan line) including the new measurements presented in this paper.
@@
 The red dots at 104 GHz correspond to
-our continuum measurements (integrated, peak, and difference, respectively).
+our continuum measurements (integrated and peak, respectively), and the red triangles correspond to the upper limits on the radio core.
 The dashed purple line and
@@
 $\micron$ flux density, hence this becomes an additional parameter in the fit.
-For both models, we impose an upper limit of 60 K on the observed-frame dust temperature ($T/(1+z)$), an upper limit of 2.2 on
-$\beta$. For the optically thick model, we impose an additional upper limit of 2000\,\micron\ on $\lambda_0$.
+For both models, we impose an upper limit of 60 K on the observed-frame dust temperature ($T/(1+z)$), and an upper limit of 2.2 on
+$\beta$. For the optically thick model, we impose an additional upper limit of 3000\,\micron\ on $\lambda_0 (1+z)$.
 
@@
 \citep*[\eg][]{Wilson70a,Downes98a}, transition lines of higher rotational states ($J$ $>$ 1) are frequently observed in high-redshift sources as the
- ground state transition line is redshifted to lower frequencies that can only be observed with a few telescopes
- \citep{Carilli13a}. Consequently, assumptions on the CO excitation conditions are required to derive the molecular gas mass using the M(H$_\textrm{2}$)-to-$L^{\prime}_\textrm{CO}$
- conversion factor from higher-$J$ CO lines. \par
-Prior to the observations of the ground state CO transition line in SMGs, it had been assumed that the molecular gas in the
+ ground state transition line is redshifted to lower frequencies that can only be observed with tranditional radio telescopes
+ \citep{Carilli13a}. Consequently, assumptions on the CO excitation conditions are required to derive the molecular gas mass using the $M$(H$_\textrm{2}$)-to-$L^{\prime}_\textrm{CO}$
+ conversion factor ($\alpha_\mathrm{CO}$) when extrapolating from higher-$J$ CO lines. \par
+Prior to observations of the ground state CO transition line in SMGs, it had been assumed that the molecular gas in the
   ISM traceable by CO lines was thermalized owing to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
@@
 postulated to be hosting a type-2 quasar (H14).
-We calculate the CO($J$\,=\,1\rarr\,0) line luminosity using standard relation
+We calculate the CO($J$\,=\,1\rarr\,0) line luminosity using a standard relation
 \citep[\eg][]{Solomon05a,Carilli13a}:
 \begin{equation}
-L^{\prime}_\textrm{CO}\,=\,\frac{3.25\times10^7}{\nu_\textrm{CO(3-2)}^2}\times \frac{D_L^2}{\mu_\textrm{L}} \times
+L^{\prime}_\textrm{CO}\,=\,\frac{3.25\times10^7}{\nu_\textrm{CO(3-2)}^2}\times \frac{D_{\rm L}^2}{\mu_\textrm{L}} \times
 \frac{I_\textrm{CO(3-2)}} {R_\textrm{31} (1 + z)}
 \end{equation}
-where $\nu_\textrm{CO(3-2)}$ is the rest-frame frequency of the \CO transition line in GHz, $D_L$ is the luminosity distance in Mpc, $\mu_\textrm{L}$ is the lensing magnification factor, and $I_\textrm{CO(3-2)}$ is the \CO line flux in Jy\,\,km\,\,s\pmOne.
-This corresponds to \Lp = (3.42\,$\pm$\,0.71)\,$\times$~10$^{10}$\,(10.1/$\mu_\textrm{L}$)~\LpU, hence
-the inferred total molecular gas mass is $M_\textrm{gas}$ = (2.74\,$\pm$\,0.57)\,$\times$\,\,10$^{10}$\,\Msun\, after correcting for lensing magnification.
+where $\nu_\textrm{CO(3-2)}$ is the rest-frame frequency of the \CO transition line in GHz, $D_{\rm L}$ is the luminosity distance in Mpc, $\mu_\textrm{L}$ is the lensing magnification factor, and $I_\textrm{CO(3-2)}$ is the \CO line flux in Jy\,\,km\,\,s\pmOne.
+This corresponds to \Lp = (3.42\,$\pm$\,0.71)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU, hence the inferred total molecular gas mass is $M_\textrm{gas}$ = (2.74\,$\pm$\,0.57)\,$\times$\,\,10$^{10}$\,\Msun\, after correcting for lensing magnification.
 We assumed a conversion factor of $\alpha_\textrm{CO}$ = 0.8\,\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
@@
 ratio of $f_\textrm{gas-dust}$\,=\,$M_\textrm{gas}/M_\textrm{dust}$\,=\,55\,$\pm$\,24.
-We note that a factor of $\sim$\,2 uncertainty arises from the dust mass estimate.
+We note that as outlined in the previous section, a factor of $\sim$\,2 uncertainty arises from the dust mass estimate.
 The derived gas-to-dust ratio is in good agreement, within the uncertainties,
@@
 stellar initial mass (IMF) function\footnote{The SFR would be SFR$_\textrm{FIR}$\,=\,526\,$\pm$\,73 $M_
-\odot$ yr\pmOne\ if we were to use only the FIR luminosity},
-we derive a SFR$_\textrm{IR}$ of 874\,$\pm$\,122 $M\sun$\,\,yr\pmOne, employing the lensing-corrected total IR luminosity.
+\odot$ yr\pmOne\ if we were to use only the FIR luminosity.},
+we derive a SFR$_\textrm{IR}$ of 874\,$\pm$\,122 $\Msun$\,\,yr\pmOne, employing the lensing-corrected total IR luminosity.
 The starburst in SMM\,J0939 can be maintained at its
@@
 measure of the star formation efficiency, SFE\,=\,SFR/$M_\textrm{gas}$. We compute this ratio using the IR
-luminosity and CO luminosity without correcting for lensing magnification, SFE\,=\,$L_\textrm{IR}$/\Lp.
+luminosity and CO luminosity assuming the same lensing magnification for both quantities, SFE\,=\,$L_\textrm{IR}$/\Lp.
 The derived SFE is therefore independent of the magnification factor, the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$), and of the
@@
 and the half-light radius from our lens model for $R_\textrm{eff}$, assuming that the dust emission traces the same emitting region as the CO.
-We note that a derived dynamical mass based on this assumption is likely to be biased low as the CO-emitting region can be spatially more extended than the dust emitting region \citep[\eg][]{Tacconi06a, Riechers11c,Riechers11d,Ivison11a}.
+We note that a derived dynamical mass based on this assumption is likely to be biased towards low values, as the CO-emitting region can be spatially more extended than the dust emitting region due to the low dust optical depth at larger radii \citep[\eg][]{Tacconi06a, Riechers11c,Riechers11d,Ivison11a}.
 % 
-The inferred dynamical mass is $M_\textrm{dyn}$ = (7.84\,$\pm$\,2.84)\,$\times$\,10$^{10}$\,\Msun, and the gas-to-dynamical mass fraction is $f_\textrm{gas-to-dyn}$ = 0.35\,$\pm$\,0.14, consistent with those of other SMGs \citep{Tacconi06a}.
+We find a dynamical mass of $M_\textrm{dyn}$ = (7.84\,$\pm$\,2.84)\,$\times$\,10$^{10}$\,\Msun, and a gas-to-dynamical mass fraction of $f_\textrm{gas-to-dyn}$ = 0.35\,$\pm$\,0.14, consistent with those of other SMGs \citep{Tacconi06a}.
 
@@
 out to $z$\,$\sim$\,2.5, and assuming a Chabrier IMF \citep{B07a}.
-
+%EDIT Hodge 15
 \section{Discussion And Conclusions}
@@
 to $z$\,=\,2.2212\,$\pm$\,0.0010.
-The underlying continuum is detected at $\sim$\,9$\sigma$ significance, where the flux density is likely dominated by emission from the lobes and hotspot of the foreground radio galaxy 3C220.3.
+The underlying continuum is detected at $\sim$\,9$\sigma$ significance, where the flux density is likely dominated by emission from the lobes and hotspots of the foreground radio galaxy 3C220.3.
 
@@
 implies a CO luminosity of \Lp\ = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU, suggesting the presence of a massive
-molecular gas reservoir that fuels the star formation at a rate of $\sim$\,874 \Msun~yr\pmOne.
+molecular gas reservoir that fuels the star formation activity taking place at a rate of $\sim$\,874 \Msun~yr\pmOne.
 If the star forming activity continues at the current rate, the gas reservoir will be depleted within $\lesssim$~31 Myr,
-which is consistent with the short timescale found in SMGs \citep{Greve05a}.
+which is consistent with the short timescales found in other SMGs \citep{Greve05a}.
 The derived intrinsic properties of SMM\,J0939 are evident of ongoing rapid star formation; this is in good agreement with the current conjecture that SMGs are a %stellar mass assembly in galaxies
-population of high-redshift galaxies that build up the stellar bulk of present-day galaxies, thus play an important role
+population of high-redshift galaxies that build up the bulk of stellar mass in present-day galaxies, thus play an important role
 in galaxy formation and evolution \citep[\eg ][]{Dickinson03a}.
@@
 the
-longest gas depletion timescale (\ie long-lived), the overall gas and dust properties of SMM\,J0939 are between those of HLSW-01 and the
+longest gas depletion timescale (\ie is the most long-lived), the overall gas and dust properties of SMM\,J0939 fall between those of HLSW-01 and the
 cosmic
-Eyelash. Such distinction is likely a result of our selection bias: while these sources appear similarly bright at 250 \micron, their lensing factors
-vary by a factor of $\sim$\,3. In particular, with the cosmic Eyelash having the highest lensing magnification among the
+Eyelash. Such distinction is likely a result of our selection bias: while these sources appear similarly bright at 250 \micron, the lensing magnification
+varies by a factor of $\sim$\,3. In particular, with the cosmic Eyelash having the highest lensing magnification among the
 three, this
 intrinsically fainter, and less gas-rich SMG appears notably bright
-at 250\,\micron, with its CO line and IR luminosities lower than those of most SMGs studied to date.
+at 250\,\micron, while its CO line and IR luminosities are lower than those of most SMGs studied to date.
 This demonstrates
-the large variations in gas mass, dust mass, thus star forming activity within the population at $z$\,$\sim$\,2, which is discernible with the aid of gravitational lensing.
+the large variations in gas mass, dust mass, and star forming activity within the population at $z$\,$\sim$\,2$-$3, which is discernible with the aid of gravitational lensing.
 While lensing can probe sources
-of various intrinsic properties, we find that SMM\,J0939 is representative of the population, with its intrinsic CO line luminosity, IR luminosity, gas mass,
+of various intrinsic properties, we find that SMM\,J0939 is representative of the SMG population, with its intrinsic CO line luminosity, IR luminosity, gas mass,
 dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in ``typical" SMGs studied to date
-\citep[\eg ][]{Greve05a,Tacconi10a}.
+\citep[\eg ][]{Greve05a,Tacconi08a}.
 
@@
 % some mysterious SFE 
-In contrast with what was found for F10214, one of the eight sources in their sample with the lowest molecular gas mass and SFR, we find that the properties
-(\eg FWHM of CO line profile \footnote{The statistical mean is based on the line profile of the CO transition closest to $J$ = 4\,\rarr\,3 available for each source}, M$_\textrm{gas}$\footnote{The molecular gas mass for each source is derived based on its lowest-$J$ CO line emission available in literature}, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a
-factor of $\sim$\,1.5, is nevertheless consistent within the measurement uncertainties.
-The fact that the gas mass of F10214 in their compilation was derived using \CO line emission \citep{Solomon05a} has a minor effect on the resulting low gas mass; \citet{Riechers11a} report a similarly low gas mass derived using their CO($J$\,=\,1\,\rarr\,0) line measurement.
-With F10214 being the most strongly-lensed high-redshift type-2 quasar \citep[$\mu_{\textrm L}$ = 17; ][]{Solomon05a}\footnote{Note that \citet{Deane13a} suggest a magnification factor of $\mu_{\textrm L}$ = 6\,$\pm$\,1.5 for the CO emission in F10214}, its exceptionally low molecular gas mass and SFR is evident that this source lies on the low end of the CO and IR luminosity functions of the population.
-This demonstrates that despite the variations in the intrinsic properties among lensed sources,
+Among these obscured type-2 quasars, F10214 has the lowest molecular gas mass as well as SFR.
+The fact that the gas mass of F10214 in their compilation was derived using \CO line emission \citep{Solomon05a} has a minor effect on the resulting low gas mass; \citet{Riechers11a} report
+a similarly low gas mass derived using their CO($J$\,=\,1\,\rarr\,0) line emission.
+With F10214 being the most strongly-lensed high-redshift type-2 quasar \citep[$\mu_{\textrm L}$ = 17; ][]{Solomon05a}\footnote{Note that \citet{Deane13a} suggest a magnification factor of $\mu_{\textrm L}$ = 6\,$\pm$\,1.5 for the CO emission in F10214.}, its exceptionally low molecular gas mass and SFR is evident that this source lies on the low end of the CO and IR luminosity distributions of the population.
+In contrast to what was found for F10214, we find that the properties
+(\eg FWHM of the CO line profile \footnote{The statistical mean is based on the line profile of the CO transition closest to $J$ = 4\,\rarr\,3 available for each source.}, M$_\textrm{gas}$\footnote{The molecular gas mass for each source is derived based on its lowest-$J$ CO line emission available in literature.}, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a
+factor of $\sim$\,1.5, but is nevertheless consistent within the measurement uncertainties. This demonstrates that despite the variations in the intrinsic properties among lensed sources,
  SMM\,J0939 is representative of type-2 quasars at high redshifts (at least among the sample from \citealt{Polletta11a}).
@@
 We conclude this paper by noting that SMM\,J0939 is a faithful representation of both high-redshift type-2 quasars and SMGs,
-based on the excellent agreement found between theirs properties. In this remarkable lensing system, the background galaxy --- SMM\,J0939 is
-breaking up its dust cocoon (H14) while undergoing prodigious star-formation (SFR\,$\sim$\,874 \Msun~yr\pmOne).
-This scenario is consistent with the proposed evolutionary phase model \citep{Sanders88,Coppin08a,Simpson12a}, whereby SMM\,J0939 is transitioning from its star-bursting phase to the unobscured quasar phase.
+based on the excellent agreement found between their properties. In this remarkable lensing system, the background galaxy --- SMM\,J0939 is
+breaking up its dust cocoon (H14) while undergoing prodigious star-formation activity (SFR\,$\sim$\,874 \Msun~yr\pmOne).
+This scenario is consistent with the proposed evolutionary phase model \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}, whereby SMM\,J0939 is transitioning from its star-bursting phase to the unobscured quasar phase.
 
@@
 
-%\bibliographystyle{apj}
-%\bibliography{J0939}
-\begin{thebibliography}{}
-\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
-
-\bibitem[{{Baldwin} {et~al.}(1985){Baldwin}, {Boysen}, {Hales}, {Jennings},
-  {Waggett}, {Warner}, \& {Wilson}}]{r2728}
-{Baldwin}, J.~E., {Boysen}, R.~C., {Hales}, S.~E.~G., {et~al.} 1985, \mnras,
-  217, 717
-
-\bibitem[{{Begelman} {et~al.}(1984){Begelman}, {Blandford}, \&
-  {Rees}}]{Begelman84a}
-{Begelman}, M.~C., {Blandford}, R.~D., \& {Rees}, M.~J. 1984, Reviews of Modern
-  Physics, 56, 255
-
-\bibitem[{{Blain} {et~al.}(2002){Blain}, {Smail}, {Ivison}, {Kneib}, \&
-  {Frayer}}]{blain02a}
-{Blain}, A.~W., {Smail}, I., {Ivison}, R.~J., {Kneib}, J.-P., \& {Frayer},
-  D.~T. 2002, \physrep, 369, 111
-
-\bibitem[{{Bothwell} {et~al.}(2013){Bothwell}, {Smail}, {Chapman}, {Genzel},
-  {Ivison}, {Tacconi}, {Alaghband-Zadeh}, {Bertoldi}, {Blain}, {Casey}, {Cox},
-  {Greve}, {Lutz}, {Neri}, {Omont}, \& {Swinbank}}]{Bothwell13a}
-{Bothwell}, M.~S., {Smail}, I., {Chapman}, S.~C., {et~al.} 2013, \mnras, 429,
-  3047
-
-\bibitem[{{Bouch{\'e}} {et~al.}(2007){Bouch{\'e}}, {Cresci}, {Davies},
-  {Eisenhauer}, {F{\"o}rster Schreiber}, {Genzel}, {Gillessen}, {Lehnert},
-  {Lutz}, {Nesvadba}, {Shapiro}, {Sternberg}, {Tacconi}, {Verma}, {Cimatti},
-  {Daddi}, {Renzini}, {Erb}, {Shapley}, \& {Steidel}}]{B07a}
-{Bouch{\'e}}, N., {Cresci}, G., {Davies}, R., {et~al.} 2007, \apj, 671, 303
-
-\bibitem[{{Bussmann} {et~al.}(2015){Bussmann}, {Riechers}, {Fialkov},
-  {Scudder}, {Hayward}, {Cowley}, {Bock}, {Calanog}, {Chapman}, {Cooray}, {De
-  Bernardis}, {Farrah}, {Fu}, {Gavazzi}, {Hopwood}, {Ivison}, {Jarvis},
-  {Lacey}, {Loeb}, {Oliver}, {Perez-Fournon}, {Rigopoulou}, {Roseboom},
-  {Scott}, {Smith}, {Vieira}, {Wang}, \& {Wardlow}}]{Bussmann15a}
-{Bussmann}, R.~S., {Riechers}, D., {Fialkov}, A., {et~al.} 2015, ArXiv
-  e-prints, arXiv:1504.05256
-
-\bibitem[{{Carilli} \& {Walter}(2013)}]{Carilli13a}
-{Carilli}, C.~L., \& {Walter}, F. 2013, \araa, 51, 105
-
-\bibitem[{{Carilli} {et~al.}(2010){Carilli}, {Daddi}, {Riechers}, {Walter},
-  {Weiss}, {Dannerbauer}, {Morrison}, {Wagg}, {Dav{\'e}}, {Elbaz}, {Stern},
-  {Dickinson}, {Krips}, \& {Aravena}}]{Carilli10a}
-{Carilli}, C.~L., {Daddi}, E., {Riechers}, D., {et~al.} 2010, \apj, 714, 1407
-
-\bibitem[{{Casey}(2012)}]{Casey12a}
-{Casey}, C.~M. 2012, \mnras, 425, 3094
-
-\bibitem[{{Casey} {et~al.}(2014){Casey}, {Narayanan}, \& {Cooray}}]{Casey14a}
-{Casey}, C.~M., {Narayanan}, D., \& {Cooray}, A. 2014, \physrep, 541, 45
-
-\bibitem[{{Chabrier}(2003)}]{Chabrier03a}
-{Chabrier}, G. 2003, \pasp, 115, 763
-
-\bibitem[{{Cleary} {et~al.}(2007){Cleary}, {Lawrence}, {Marshall}, {Hao}, \&
-  {Meier}}]{Cleary07a}
-{Cleary}, K., {Lawrence}, C.~R., {Marshall}, J.~A., {Hao}, L., \& {Meier}, D.
-  2007, \apj, 660, 117
-
-\bibitem[{{Cohen} {et~al.}(2007){Cohen}, {Lane}, {Cotton}, {Kassim}, {Lazio},
-  {Perley}, {Condon}, \& {Erickson}}]{r30}
-{Cohen}, A.~S., {Lane}, W.~M., {Cotton}, W.~D., {et~al.} 2007, \aj, 134, 1245
-
-\bibitem[{{Condon} {et~al.}(1998){Condon}, {Cotton}, {Greisen}, {Yin},
-  {Perley}, {Taylor}, \& {Broderick}}]{r16}
-{Condon}, J.~J., {Cotton}, W.~D., {Greisen}, E.~W., {et~al.} 1998, \aj, 115,
-  1693
-
-\bibitem[{{Conley} {et~al.}(2011){Conley}, {Cooray}, {Vieira}, {Gonz{\'a}lez
-  Solares}, {Kim}, {Aguirre}, {Amblard}, {Auld}, {Baker}, {Beelen}, {Blain},
-  {Blundell}, {Bock}, {Bradford}, {Bridge}, {Brisbin}, {Burgarella},
-  {Carpenter}, {Chanial}, {Chapin}, {Christopher}, {Clements}, {Cox},
-  {Djorgovski}, {Dowell}, {Eales}, {Earle}, {Ellsworth-Bowers}, {Farrah},
-  {Franceschini}, {Frayer}, {Fu}, {Gavazzi}, {Glenn}, {Griffin}, {Gurwell},
-  {Halpern}, {Ibar}, {Ivison}, {Jarvis}, {Kamenetzky}, {Krips}, {Levenson},
-  {Lupu}, {Mahabal}, {Maloney}, {Maraston}, {Marchetti}, {Marsden},
-  {Matsuhara}, {Mortier}, {Murphy}, {Naylor}, {Neri}, {Nguyen}, {Oliver},
-  {Omont}, {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen},
-  {Rangwala}, {Rawlings}, {Raymond}, {Riechers}, {Rodighiero}, {Roseboom},
-  {Rowan-Robinson}, {Schulz}, {Scott}, {Scott}, {Serra}, {Seymour}, {Shupe},
-  {Smith}, {Symeonidis}, {Tugwell}, {Vaccari}, {Valiante}, {Valtchanov},
-  {Verma}, {Viero}, {Vigroux}, {Wang}, {Wiebe}, {Wright}, {Xu}, {Zeimann},
-  {Zemcov}, \& {Zmuidzinas}}]{Conley11a}
-{Conley}, A., {Cooray}, A., {Vieira}, J.~D., {et~al.} 2011, \apjl, 732, L35
-
-\bibitem[{{Coppin} {et~al.}(2008){Coppin}, {Swinbank}, {Neri}, {Cox},
-  {Alexander}, {Smail}, {Page}, {Stevens}, {Knudsen}, {Ivison}, {Beelen},
-  {Bertoldi}, \& {Omont}}]{Coppin08a}
-{Coppin}, K.~E.~K., {Swinbank}, A.~M., {Neri}, R., {et~al.} 2008, \mnras, 389,
-  45
-
-\bibitem[{{Danielson} {et~al.}(2011){Danielson}, {Swinbank}, {Smail}, {Cox},
-  {Edge}, {Weiss}, {Harris}, {Baker}, {De Breuck}, {Geach}, {Ivison}, {Krips},
-  {Lundgren}, {Longmore}, {Neri}, \& {Flaquer}}]{Danielson11a}
-{Danielson}, A.~L.~R., {Swinbank}, A.~M., {Smail}, I., {et~al.} 2011, \mnras,
-  410, 1687
-
-\bibitem[{{Deane} {et~al.}(2013){Deane}, {Heywood}, {Rawlings}, \&
-  {Marshall}}]{Deane13a}
-{Deane}, R.~P., {Heywood}, I., {Rawlings}, S., \& {Marshall}, P.~J. 2013,
-  \mnras, 434, 23
-
-\bibitem[{{Dickinson} {et~al.}(2003){Dickinson}, {Papovich}, {Ferguson}, \&
-  {Budav{\'a}ri}}]{Dickinson03a}
-{Dickinson}, M., {Papovich}, C., {Ferguson}, H.~C., \& {Budav{\'a}ri}, T. 2003,
-  \apj, 587, 25
-
-\bibitem[{{Dowell} {et~al.}(2014){Dowell}, {Conley}, {Glenn}, {Arumugam},
-  {Asboth}, {Aussel}, {Bertoldi}, {B{\'e}thermin}, {Bock}, {Boselli}, {Bridge},
-  {Buat}, {Burgarella}, {Cabrera-Lavers}, {Casey}, {Chapman}, {Clements},
-  {Conversi}, {Cooray}, {Dannerbauer}, {De Bernardis}, {Ellsworth-Bowers},
-  {Farrah}, {Franceschini}, {Griffin}, {Gurwell}, {Halpern}, {Hatziminaoglou},
-  {Heinis}, {Ibar}, {Ivison}, {Laporte}, {Marchetti},
-  {Mart{\'{\i}}nez-Navajas}, {Marsden}, {Morrison}, {Nguyen}, {O'Halloran},
-  {Oliver}, {Omont}, {Page}, {Papageorgiou}, {Pearson}, {Petitpas},
-  {P{\'e}rez-Fournon}, {Pohlen}, {Riechers}, {Rigopoulou}, {Roseboom},
-  {Rowan-Robinson}, {Sayers}, {Schulz}, {Scott}, {Seymour}, {Shupe}, {Smith},
-  {Streblyanska}, {Symeonidis}, {Vaccari}, {Valtchanov}, {Vieira}, {Viero},
-  {Wang}, {Wardlow}, {Xu}, \& {Zemcov}}]{Dowell14a}
-{Dowell}, C.~D., {Conley}, A., {Glenn}, J., {et~al.} 2014, \apj, 780, 75
-
-\bibitem[{{Downes} \& {Solomon}(1998)}]{Downes98a}
-{Downes}, D., \& {Solomon}, P.~M. 1998, \apj, 507, 615
-
-\bibitem[{{Dunne} {et~al.}(2003){Dunne}, {Eales}, \& {Edmunds}}]{Dunne03a}
-{Dunne}, L., {Eales}, S.~A., \& {Edmunds}, M.~G. 2003, \mnras, 341, 589
-
-\bibitem[{{Eales} {et~al.}(2010){Eales}, {Dunne}, {Clements}, {Cooray}, {de
-  Zotti}, {Dye}, {Ivison}, {Jarvis}, {Lagache}, {Maddox}, {Negrello},
-  {Serjeant}, {Thompson}, {van Kampen}, {Amblard}, {Andreani}, {Baes},
-  {Beelen}, {Bendo}, {Benford}, {Bertoldi}, {Bock}, {Bonfield}, {Boselli},
-  {Bridge}, {Buat}, {Burgarella}, {Carlberg}, {Cava}, {Chanial}, {Charlot},
-  {Christopher}, {Coles}, {Cortese}, {Dariush}, {da Cunha}, {Dalton}, {Danese},
-  {Dannerbauer}, {Driver}, {Dunlop}, {Fan}, {Farrah}, {Frayer}, {Frenk},
-  {Geach}, {Gardner}, {Gomez}, {Gonz{\'a}lez-Nuevo}, {Gonz{\'a}lez-Solares},
-  {Griffin}, {Hardcastle}, {Hatziminaoglou}, {Herranz}, {Hughes}, {Ibar},
-  {Jeong}, {Lacey}, {Lapi}, {Lawrence}, {Lee}, {Leeuw}, {Liske},
-  {L{\'o}pez-Caniego}, {M{\"u}ller}, {Nandra}, {Panuzzo}, {Papageorgiou},
-  {Patanchon}, {Peacock}, {Pearson}, {Phillipps}, {Pohlen}, {Popescu},
-  {Rawlings}, {Rigby}, {Rigopoulou}, {Robotham}, {Rodighiero}, {Sansom},
-  {Schulz}, {Scott}, {Smith}, {Sibthorpe}, {Smail}, {Stevens}, {Sutherland},
-  {Takeuchi}, {Tedds}, {Temi}, {Tuffs}, {Trichas}, {Vaccari}, {Valtchanov},
-  {van der Werf}, {Verma}, {Vieria}, {Vlahakis}, \& {White}}]{Eales10a}
-{Eales}, S., {Dunne}, L., {Clements}, D., {et~al.} 2010, \pasp, 122, 499
-
-\bibitem[{{Engel} {et~al.}(2010){Engel}, {Tacconi}, {Davies}, {Neri}, {Smail},
-  {Chapman}, {Genzel}, {Cox}, {Greve}, {Ivison}, {Blain}, {Bertoldi}, \&
-  {Omont}}]{Engel10a}
-{Engel}, H., {Tacconi}, L.~J., {Davies}, R.~I., {et~al.} 2010, \apj, 724, 233
-
-\bibitem[{{Fanaroff} \& {Riley}(1974)}]{Fanaroff74}
-{Fanaroff}, B.~L., \& {Riley}, J.~M. 1974, \mnras, 167, 31P
-
-\bibitem[{{Gavazzi} {et~al.}(2011){Gavazzi}, {Cooray}, {Conley}, {Aguirre},
-  {Amblard}, {Auld}, {Beelen}, {Blain}, {Blundell}, {Bock}, {Bradford},
-  {Bridge}, {Brisbin}, {Burgarella}, {Chanial}, {Chapin}, {Christopher},
-  {Clements}, {Cox}, {Djorgovski}, {Dowell}, {Eales}, {Earle},
-  {Ellsworth-Bowers}, {Farrah}, {Franceschini}, {Fu}, {Glenn}, {Gonz{\'a}lez
-  Solares}, {Griffin}, {Gurwell}, {Halpern}, {Ibar}, {Ivison}, {Jarvis},
-  {Kamenetzky}, {Kim}, {Krips}, {Levenson}, {Lupu}, {Mahabal}, {Maloney},
-  {Maraston}, {Marchetti}, {Marsden}, {Matsuhara}, {Mortier}, {Murphy},
-  {Naylor}, {Neri}, {Nguyen}, {Oliver}, {Omont}, {Page}, {Papageorgiou},
-  {Pearson}, {P{\'e}rez-Fournon}, {Pohlen}, {Rangwala}, {Rawlings}, {Raymond},
-  {Riechers}, {Rodighiero}, {Roseboom}, {Rowan-Robinson}, {Schulz}, {Scott},
-  {Scott}, {Serra}, {Seymour}, {Shupe}, {Smith}, {Symeonidis}, {Tugwell},
-  {Vaccari}, {Valiante}, {Valtchanov}, {Verma}, {Vieira}, {Vigroux}, {Wang},
-  {Wardlow}, {Wiebe}, {Wright}, {Xu}, {Zeimann}, {Zemcov}, \&
-  {Zmuidzinas}}]{Gavazzi11a}
-{Gavazzi}, R., {Cooray}, A., {Conley}, A., {et~al.} 2011, \apj, 738, 125
-
-\bibitem[{{Greve} {et~al.}(2005){Greve}, {Bertoldi}, {Smail}, {Neri},
-  {Chapman}, {Blain}, {Ivison}, {Genzel}, {Omont}, {Cox}, {Tacconi}, \&
-  {Kneib}}]{Greve05a}
-{Greve}, T.~R., {Bertoldi}, F., {Smail}, I., {et~al.} 2005, \mnras, 359, 1165
-
-\bibitem[{{Haas} {et~al.}(2014){Haas}, {Leipski}, {Barthel}, {Wilkes},
-  {Vegetti}, {Bussmann}, {Willner}, {Westhues}, {Ashby}, {Chini}, {Clements},
-  {Fassnacht}, {Horesh}, {Klaas}, {Koopmans}, {Kuraszkiewicz}, {Lagattuta},
-  {Meisenheimer}, {Stern}, \& {Wylezalek}}]{Haas14}
-{Haas}, M., {Leipski}, C., {Barthel}, P., {et~al.} 2014, \apj, 790, 46 (H14)
-
-\bibitem[{{Hales} {et~al.}(1995){Hales}, {Waldram}, {Rees}, \&
-  {Warner}}]{r33-34}
-{Hales}, S.~E.~G., {Waldram}, E.~M., {Rees}, N., \& {Warner}, P.~J. 1995,
-  \mnras, 274, 447
-
-\bibitem[{{Hardcastle} \& {Looney}(2008)}]{Hardcastle08a}
-{Hardcastle}, M.~J., \& {Looney}, L.~W. 2008, \mnras, 388, 176
-
-\bibitem[{{Harris} {et~al.}(2010){Harris}, {Baker}, {Zonak}, {Sharon},
-  {Genzel}, {Rauch}, {Watts}, \& {Creager}}]{Harris10a}
-{Harris}, A.~I., {Baker}, A.~J., {Zonak}, S.~G., {et~al.} 2010, \apj, 723, 1139
-
-\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
-  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
-  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
-  \& {Wright}}]{Hinshaw13a}
-{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {et~al.} 2013, \apjs, 208, 19
-
-\bibitem[{{Ivison} {et~al.}(2011){Ivison}, {Papadopoulos}, {Smail}, {Greve},
-  {Thomson}, {Xilouris}, \& {Chapman}}]{Ivison11a}
-{Ivison}, R.~J., {Papadopoulos}, P.~P., {Smail}, I., {et~al.} 2011, \mnras,
-  412, 1913
-
-\bibitem[{{Ivison} {et~al.}(2010{\natexlab{a}}){Ivison}, {Smail},
-  {Papadopoulos}, {Wold}, {Richard}, {Swinbank}, {Kneib}, \&
-  {Owen}}]{Ivison10d}
-{Ivison}, R.~J., {Smail}, I., {Papadopoulos}, P.~P., {et~al.}
-  2010{\natexlab{a}}, \mnras, 404, 198
-
-\bibitem[{{Ivison} {et~al.}(2010{\natexlab{b}}){Ivison}, {Swinbank},
-  {Swinyard}, {Smail}, {Pearson}, {Rigopoulou}, {Polehampton}, {Baluteau},
-  {Barlow}, {Blain}, {Bock}, {Clements}, {Coppin}, {Cooray}, {Danielson},
-  {Dwek}, {Edge}, {Franceschini}, {Fulton}, {Glenn}, {Griffin}, {Isaak},
-  {Leeks}, {Lim}, {Naylor}, {Oliver}, {Page}, {P{\'e}rez Fournon},
-  {Rowan-Robinson}, {Savini}, {Scott}, {Spencer}, {Valtchanov}, {Vigroux}, \&
-  {Wright}}]{Ivison10c}
-{Ivison}, R.~J., {Swinbank}, A.~M., {Swinyard}, B., {et~al.}
-  2010{\natexlab{b}}, \aap, 518, L35
-
-\bibitem[{{Kellermann} \& {Pauliny-Toth}(1973)}]{r9}
-{Kellermann}, K.~I., \& {Pauliny-Toth}, I.~I.~K. 1973, \aj, 78, 828
-
-\bibitem[{{Kellermann} \& {Pauliny-Toth}(1981)}]{Kellermann81a}
----. 1981, \araa, 19, 373
-
-\bibitem[{{Kellermann} {et~al.}(1969){Kellermann}, {Pauliny-Toth}, \&
-  {Williams}}]{r11-14-18-22-25-32}
-{Kellermann}, K.~I., {Pauliny-Toth}, I.~I.~K., \& {Williams}, P.~J.~S. 1969,
-  \apj, 157, 1
-
-\bibitem[{{Kennicutt}(1998)}]{Kennicutt98a}
-{Kennicutt}, Jr., R.~C. 1998, \araa, 36, 189
-
-\bibitem[{{Lagache} {et~al.}(2005){Lagache}, {Puget}, \& {Dole}}]{Lagache05a}
-{Lagache}, G., {Puget}, J.-L., \& {Dole}, H. 2005, \araa, 43, 727
-
-\bibitem[{{Laing} \& {Peacock}(1980)}]{r10-13-15-19-20-26-29-31}
-{Laing}, R.~A., \& {Peacock}, J.~A. 1980, \mnras, 190, 903
-
-\bibitem[{{Meisenheimer} {et~al.}(1989){Meisenheimer}, {Roser}, {Hiltner},
-  {Yates}, {Longair}, {Chini}, \& {Perley}}]{Meisenheimer89a}
-{Meisenheimer}, K., {Roser}, H.-J., {Hiltner}, P.~R., {et~al.} 1989, \aap, 219,
-  63
-
-\bibitem[{{Micha{\l}owski} {et~al.}(2010){Micha{\l}owski}, {Watson}, \&
-  {Hjorth}}]{Micha10a}
-{Micha{\l}owski}, M.~J., {Watson}, D., \& {Hjorth}, J. 2010, \apj, 712, 942
-
-\bibitem[{{Mullin} {et~al.}(2006){Mullin}, {Hardcastle}, \&
-  {Riley}}]{Mullin06a}
-{Mullin}, L.~M., {Hardcastle}, M.~J., \& {Riley}, J.~M. 2006, \mnras, 372, 113
-
-\bibitem[{{Negrello} {et~al.}(2010){Negrello}, {Hopwood}, {De Zotti}, {Cooray},
-  {Verma}, {Bock}, {Frayer}, {Gurwell}, {Omont}, {Neri}, {Dannerbauer},
-  {Leeuw}, {Barton}, {Cooke}, {Kim}, {da Cunha}, {Rodighiero}, {Cox},
-  {Bonfield}, {Jarvis}, {Serjeant}, {Ivison}, {Dye}, {Aretxaga}, {Hughes},
-  {Ibar}, {Bertoldi}, {Valtchanov}, {Eales}, {Dunne}, {Driver}, {Auld},
-  {Buttiglione}, {Cava}, {Grady}, {Clements}, {Dariush}, {Fritz}, {Hill},
-  {Hornbeck}, {Kelvin}, {Lagache}, {Lopez-Caniego}, {Gonzalez-Nuevo}, {Maddox},
-  {Pascale}, {Pohlen}, {Rigby}, {Robotham}, {Simpson}, {Smith}, {Temi},
-  {Thompson}, {Woodgate}, {York}, {Aguirre}, {Beelen}, {Blain}, {Baker},
-  {Birkinshaw}, {Blundell}, {Bradford}, {Burgarella}, {Danese}, {Dunlop},
-  {Fleuren}, {Glenn}, {Harris}, {Kamenetzky}, {Lupu}, {Maddalena}, {Madore},
-  {Maloney}, {Matsuhara}, {Micha{\l}owski}, {Murphy}, {Naylor}, {Nguyen},
-  {Popescu}, {Rawlings}, {Rigopoulou}, {Scott}, {Scott}, {Seibert}, {Smail},
-  {Tuffs}, {Vieira}, {van der Werf}, \& {Zmuidzinas}}]{Negrello10a}
-{Negrello}, M., {Hopwood}, R., {De Zotti}, G., {et~al.} 2010, Science, 330, 800
-
-\bibitem[{{Oliver} {et~al.}(2012){Oliver}, {Bock}, {Altieri}, {Amblard},
-  {Arumugam}, {Aussel}, {Babbedge}, {Beelen}, {B{\'e}thermin}, {Blain},
-  {Boselli}, {Bridge}, {Brisbin}, {Buat}, {Burgarella},
-  {Castro-Rodr{\'{\i}}guez}, {Cava}, {Chanial}, {Cirasuolo}, {Clements},
-  {Conley}, {Conversi}, {Cooray}, {Dowell}, {Dubois}, {Dwek}, {Dye}, {Eales},
-  {Elbaz}, {Farrah}, {Feltre}, {Ferrero}, {Fiolet}, {Fox}, {Franceschini},
-  {Gear}, {Giovannoli}, {Glenn}, {Gong}, {Gonz{\'a}lez Solares}, {Griffin},
-  {Halpern}, {Harwit}, {Hatziminaoglou}, {Heinis}, {Hurley}, {Hwang}, {Hyde},
-  {Ibar}, {Ilbert}, {Isaak}, {Ivison}, {Lagache}, {Le Floc'h}, {Levenson},
-  {Faro}, {Lu}, {Madden}, {Maffei}, {Magdis}, {Mainetti}, {Marchetti},
-  {Marsden}, {Marshall}, {Mortier}, {Nguyen}, {O'Halloran}, {Omont}, {Page},
-  {Panuzzo}, {Papageorgiou}, {Patel}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen},
-  {Rawlings}, {Raymond}, {Rigopoulou}, {Riguccini}, {Rizzo}, {Rodighiero},
-  {Roseboom}, {Rowan-Robinson}, {S{\'a}nchez Portal}, {Schulz}, {Scott},
-  {Seymour}, {Shupe}, {Smith}, {Stevens}, {Symeonidis}, {Trichas}, {Tugwell},
-  {Vaccari}, {Valtchanov}, {Vieira}, {Viero}, {Vigroux}, {Wang}, {Ward},
-  {Wardlow}, {Wright}, {Xu}, \& {Zemcov}}]{Oliver12a}
-{Oliver}, S.~J., {Bock}, J., {Altieri}, B., {et~al.} 2012, \mnras, 424, 1614
-
-\bibitem[{{Pauliny-Toth} {et~al.}(1966){Pauliny-Toth}, {Wade}, \&
-  {Heeschen}}]{r17-21}
-{Pauliny-Toth}, I.~I.~K., {Wade}, C.~M., \& {Heeschen}, D.~S. 1966, \apjs, 13,
-  65
-
-\bibitem[{{Polletta} {et~al.}(2011){Polletta}, {Nesvadba}, {Neri}, {Omont},
-  {Berta}, \& {Bergeron}}]{Polletta11a}
-{Polletta}, M., {Nesvadba}, N.~P.~H., {Neri}, R., {et~al.} 2011, \aap, 533, A20
-
-\bibitem[{{Rengelink} {et~al.}(1997){Rengelink}, {Tang}, {de Bruyn}, {Miley},
-  {Bremer}, {Roettgering}, \& {Bremer}}]{r23-24}
-{Rengelink}, R.~B., {Tang}, Y., {de Bruyn}, A.~G., {et~al.} 1997, \aaps, 124,
-  259
-
-\bibitem[{{Riechers} {et~al.}(2006){Riechers}, {Walter}, {Carilli}, {Knudsen},
-  {Lo}, {Benford}, {Staguhn}, {Hunter}, {Bertoldi}, {Henkel}, {Menten},
-  {Weiss}, {Yun}, \& {Scoville}}]{Riechers06a}
-{Riechers}, D.~A., {Walter}, F., {Carilli}, C.~L., {et~al.} 2006, \apj, 650,
-  604
-
-\bibitem[{{Riechers} {et~al.}(2011{\natexlab{a}}){Riechers}, {Hodge}, {Walter},
-  {Carilli}, \& {Bertoldi}}]{Riechers11c}
-{Riechers}, D.~A., {Hodge}, J., {Walter}, F., {Carilli}, C.~L., \& {Bertoldi},
-  F. 2011{\natexlab{a}}, \apjl, 739, L31
-
-\bibitem[{{Riechers} {et~al.}(2011{\natexlab{b}}){Riechers}, {Carilli},
-  {Walter}, {Weiss}, {Wagg}, {Bertoldi}, {Downes}, {Henkel}, \&
-  {Hodge}}]{Riechers11d}
-{Riechers}, D.~A., {Carilli}, L.~C., {Walter}, F., {et~al.} 2011{\natexlab{b}},
-  \apjl, 733, L11
-
-\bibitem[{{Riechers} {et~al.}(2011{\natexlab{c}}){Riechers}, {Carilli},
-  {Maddalena}, {Hodge}, {Harris}, {Baker}, {Walter}, {Wagg}, {Vanden Bout},
-  {Wei{\ss}}, \& {Sharon}}]{Riechers11a}
-{Riechers}, D.~A., {Carilli}, C.~L., {Maddalena}, R.~J., {et~al.}
-  2011{\natexlab{c}}, \apjl, 739, L32
-
-\bibitem[{{Riechers} {et~al.}(2011{\natexlab{d}}){Riechers}, {Cooray}, {Omont},
-  {Neri}, {Harris}, {Baker}, {Cox}, {Frayer}, {Carpenter}, {Auld}, {Aussel},
-  {Beelen}, {Blundell}, {Bock}, {Brisbin}, {Burgarella}, {Chanial}, {Chapman},
-  {Clements}, {Conley}, {Dowell}, {Eales}, {Farrah}, {Franceschini}, {Gavazzi},
-  {Glenn}, {Griffin}, {Gurwell}, {Ivison}, {Kim}, {Krips}, {Mortier}, {Oliver},
-  {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen}, {Rawlings},
-  {Raymond}, {Rodighiero}, {Roseboom}, {Rowan-Robinson}, {Scott}, {Seymour},
-  {Smith}, {Symeonidis}, {Tugwell}, {Vaccari}, {Vieira}, {Vigroux}, {Wang},
-  {Wardlow}, \& {Wright}}]{Riechers11b}
-{Riechers}, D.~A., {Cooray}, A., {Omont}, A., {et~al.} 2011{\natexlab{d}},
-  \apjl, 733, L12
-
-\bibitem[{{Riechers} {et~al.}(2013){Riechers}, {Bradford}, {Clements},
-  {Dowell}, {P{\'e}rez-Fournon}, {Ivison}, {Bridge}, {Conley}, {Fu}, {Vieira},
-  {Wardlow}, {Calanog}, {Cooray}, {Hurley}, {Neri}, {Kamenetzky}, {Aguirre},
-  {Altieri}, {Arumugam}, {Benford}, {B{\'e}thermin}, {Bock}, {Burgarella},
-  {Cabrera-Lavers}, {Chapman}, {Cox}, {Dunlop}, {Earle}, {Farrah}, {Ferrero},
-  {Franceschini}, {Gavazzi}, {Glenn}, {Solares}, {Gurwell}, {Halpern},
-  {Hatziminaoglou}, {Hyde}, {Ibar}, {Kov{\'a}cs}, {Krips}, {Lupu}, {Maloney},
-  {Martinez-Navajas}, {Matsuhara}, {Murphy}, {Naylor}, {Nguyen}, {Oliver},
-  {Omont}, {Page}, {Petitpas}, {Rangwala}, {Roseboom}, {Scott}, {Smith},
-  {Staguhn}, {Streblyanska}, {Thomson}, {Valtchanov}, {Viero}, {Wang},
-  {Zemcov}, \& {Zmuidzinas}}]{Riechers13a}
-{Riechers}, D.~A., {Bradford}, C.~M., {Clements}, D.~L., {et~al.} 2013, \nat,
-  496, 329
-
-\bibitem[{{Sanders} {et~al.}(1988){Sanders}, {Soifer}, {Elias}, {Madore},
-  {Matthews}, {Neugebauer}, \& {Scoville}}]{Sanders88}
-{Sanders}, D.~B., {Soifer}, B.~T., {Elias}, J.~H., {et~al.} 1988, \apj, 325, 74
-
-\bibitem[{{Scott} {et~al.}(2011){Scott}, {Lupu}, {Aguirre}, {Auld}, {Aussel},
-  {Baker}, {Beelen}, {Bock}, {Bradford}, {Brisbin}, {Burgarella}, {Carpenter},
-  {Chanial}, {Chapman}, {Clements}, {Conley}, {Cooray}, {Cox}, {Dowell},
-  {Eales}, {Farrah}, {Franceschini}, {Frayer}, {Gavazzi}, {Glenn}, {Griffin},
-  {Harris}, {Ibar}, {Ivison}, {Kamenetzky}, {Kim}, {Krips}, {Maloney},
-  {Matsuhara}, {Mortier}, {Murphy}, {Naylor}, {Neri}, {Nguyen}, {Oliver},
-  {Omont}, {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen},
-  {Rawlings}, {Raymond}, {Riechers}, {Rodighiero}, {Roseboom},
-  {Rowan-Robinson}, {Scott}, {Seymour}, {Smith}, {Symeonidis}, {Tugwell},
-  {Vaccari}, {Vieira}, {Vigroux}, {Wang}, {Wright}, \& {Zmuidzinas}}]{Scott11a}
-{Scott}, K.~S., {Lupu}, R.~E., {Aguirre}, J.~E., {et~al.} 2011, \apj, 733, 29
-
-\bibitem[{{Simpson} {et~al.}(2012){Simpson}, {Smail}, {Swinbank}, {Alexander},
-  {Auld}, {Baes}, {Bonfield}, {Clements}, {Cooray}, {Coppin}, {Danielson},
-  {Dariush}, {Dunne}, {de Zotti}, {Harrison}, {Hopwood}, {Hoyos}, {Ibar},
-  {Ivison}, {Jarvis}, {Lapi}, {Maddox}, {Page}, {Riechers}, {Valiante}, \& {van
-  der Werf}}]{Simpson12a}
-{Simpson}, J.~M., {Smail}, I., {Swinbank}, A.~M., {et~al.} 2012, \mnras, 426,
-  3201
-
-\bibitem[{{Smol{\v c}i{\'c}} \& {Riechers}(2011)}]{Smolcic11a}
-{Smol{\v c}i{\'c}}, V., \& {Riechers}, D.~A. 2011, \apj, 730, 64
-
-\bibitem[{{Solomon} \& {Vanden Bout}(2005)}]{Solomon05a}
-{Solomon}, P.~M., \& {Vanden Bout}, P.~A. 2005, \araa, 43, 677
-
-\bibitem[{{Swinbank} {et~al.}(2010){Swinbank}, {Smail}, {Longmore}, {Harris},
-  {Baker}, {De Breuck}, {Richard}, {Edge}, {Ivison}, {Blundell}, {Coppin},
-  {Cox}, {Gurwell}, {Hainline}, {Krips}, {Lundgren}, {Neri}, {Siana},
-  {Siringo}, {Stark}, {Wilner}, \& {Younger}}]{Swinbank2010a}
-{Swinbank}, A.~M., {Smail}, I., {Longmore}, S., {et~al.} 2010, \nat, 464, 733
-
-\bibitem[{{Swinbank} {et~al.}(2011){Swinbank}, {Papadopoulos}, {Cox}, {Krips},
-  {Ivison}, {Smail}, {Thomson}, {Neri}, {Richard}, \& {Ebeling}}]{Swinbank11a}
-{Swinbank}, A.~M., {Papadopoulos}, P.~P., {Cox}, P., {et~al.} 2011, \apj, 742,
-  11
-
-\bibitem[{{Tacconi} {et~al.}(2006){Tacconi}, {Neri}, {Chapman}, {Genzel},
-  {Smail}, {Ivison}, {Bertoldi}, {Blain}, {Cox}, {Greve}, \&
-  {Omont}}]{Tacconi06a}
-{Tacconi}, L.~J., {Neri}, R., {Chapman}, S.~C., {et~al.} 2006, \apj, 640, 228
-
-\bibitem[{{Tacconi} {et~al.}(2008){Tacconi}, {Genzel}, {Smail}, {Neri},
-  {Chapman}, {Ivison}, {Blain}, {Cox}, {Omont}, {Bertoldi}, {Greve},
-  {F{\"o}rster Schreiber}, {Genel}, {Lutz}, {Swinbank}, {Shapley}, {Erb},
-  {Cimatti}, {Daddi}, \& {Baker}}]{Tacconi08a}
-{Tacconi}, L.~J., {Genzel}, R., {Smail}, I., {et~al.} 2008, \apj, 680, 246
-
-\bibitem[{{Tacconi} {et~al.}(2010){Tacconi}, {Genzel}, {Neri}, {Cox}, {Cooper},
-  {Shapiro}, {Bolatto}, {Bouch{\'e}}, {Bournaud}, {Burkert}, {Combes},
-  {Comerford}, {Davis}, {Schreiber}, {Garcia-Burillo}, {Gracia-Carpio}, {Lutz},
-  {Naab}, {Omont}, {Shapley}, {Sternberg}, \& {Weiner}}]{Tacconi10a}
-{Tacconi}, L.~J., {Genzel}, R., {Neri}, R., {et~al.} 2010, \nat, 463, 781
-
-\bibitem[{{Vieira} {et~al.}(2010){Vieira}, {Crawford}, {Switzer}, {Ade},
-  {Aird}, {Ashby}, {Benson}, {Bleem}, {Brodwin}, {Carlstrom}, {Chang}, {Cho},
-  {Crites}, {de Haan}, {Dobbs}, {Everett}, {George}, {Gladders}, {Hall},
-  {Halverson}, {High}, {Holder}, {Holzapfel}, {Hrubes}, {Joy}, {Keisler},
-  {Knox}, {Lee}, {Leitch}, {Lueker}, {Marrone}, {McIntyre}, {McMahon}, {Mehl},
-  {Meyer}, {Mohr}, {Montroy}, {Padin}, {Plagge}, {Pryke}, {Reichardt}, {Ruhl},
-  {Schaffer}, {Shaw}, {Shirokoff}, {Spieler}, {Stalder}, {Staniszewski},
-  {Stark}, {Vanderlinde}, {Walsh}, {Williamson}, {Yang}, {Zahn}, \&
-  {Zenteno}}]{Vieira10a}
-{Vieira}, J.~D., {Crawford}, T.~M., {Switzer}, E.~R., {et~al.} 2010, \apj, 719,
-  763
-
-\bibitem[{{Wilson} {et~al.}(1970){Wilson}, {Jefferts}, \&
-  {Penzias}}]{Wilson70a}
-{Wilson}, R.~W., {Jefferts}, K.~B., \& {Penzias}, A.~A. 1970, \apjl, 161, L43
-
-\end{thebibliography}
+\bibliographystyle{apj}
+\bibliography{J0939}
+%\begin{thebibliography}{}
+%\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+%
+%\bibitem[{{Baldwin} {et~al.}(1985){Baldwin}, {Boysen}, {Hales}, {Jennings},
+%  {Waggett}, {Warner}, \& {Wilson}}]{r2728}
+%{Baldwin}, J.~E., {Boysen}, R.~C., {Hales}, S.~E.~G., {et~al.} 1985, \mnras,
+%  217, 717
+%
+%\bibitem[{{Begelman} {et~al.}(1984){Begelman}, {Blandford}, \&
+%  {Rees}}]{Begelman84a}
+%{Begelman}, M.~C., {Blandford}, R.~D., \& {Rees}, M.~J. 1984, Reviews of Modern
+%  Physics, 56, 255
+%
+%\bibitem[{{Blain} {et~al.}(2002){Blain}, {Smail}, {Ivison}, {Kneib}, \&
+%  {Frayer}}]{blain02a}
+%{Blain}, A.~W., {Smail}, I., {Ivison}, R.~J., {Kneib}, J.-P., \& {Frayer},
+%  D.~T. 2002, \physrep, 369, 111
+%
+%\bibitem[{{Bothwell} {et~al.}(2013){Bothwell}, {Smail}, {Chapman}, {Genzel},
+%  {Ivison}, {Tacconi}, {Alaghband-Zadeh}, {Bertoldi}, {Blain}, {Casey}, {Cox},
+%  {Greve}, {Lutz}, {Neri}, {Omont}, \& {Swinbank}}]{Bothwell13a}
+%{Bothwell}, M.~S., {Smail}, I., {Chapman}, S.~C., {et~al.} 2013, \mnras, 429,
+%  3047
+%
+%\bibitem[{{Bouch{\'e}} {et~al.}(2007){Bouch{\'e}}, {Cresci}, {Davies},
+%  {Eisenhauer}, {F{\"o}rster Schreiber}, {Genzel}, {Gillessen}, {Lehnert},
+%  {Lutz}, {Nesvadba}, {Shapiro}, {Sternberg}, {Tacconi}, {Verma}, {Cimatti},
+%  {Daddi}, {Renzini}, {Erb}, {Shapley}, \& {Steidel}}]{B07a}
+%{Bouch{\'e}}, N., {Cresci}, G., {Davies}, R., {et~al.} 2007, \apj, 671, 303
+%
+%\bibitem[{{Bussmann} {et~al.}(2015){Bussmann}, {Riechers}, {Fialkov},
+%  {Scudder}, {Hayward}, {Cowley}, {Bock}, {Calanog}, {Chapman}, {Cooray}, {De
+%  Bernardis}, {Farrah}, {Fu}, {Gavazzi}, {Hopwood}, {Ivison}, {Jarvis},
+%  {Lacey}, {Loeb}, {Oliver}, {Perez-Fournon}, {Rigopoulou}, {Roseboom},
+%  {Scott}, {Smith}, {Vieira}, {Wang}, \& {Wardlow}}]{Bussmann15a}
+%{Bussmann}, R.~S., {Riechers}, D., {Fialkov}, A., {et~al.} 2015, ArXiv
+%  e-prints, arXiv:1504.05256
+%
+%\bibitem[{{Carilli} \& {Walter}(2013)}]{Carilli13a}
+%{Carilli}, C.~L., \& {Walter}, F. 2013, \araa, 51, 105
+%
+%\bibitem[{{Carilli} {et~al.}(2010){Carilli}, {Daddi}, {Riechers}, {Walter},
+%  {Weiss}, {Dannerbauer}, {Morrison}, {Wagg}, {Dav{\'e}}, {Elbaz}, {Stern},
+%  {Dickinson}, {Krips}, \& {Aravena}}]{Carilli10a}
+%{Carilli}, C.~L., {Daddi}, E., {Riechers}, D., {et~al.} 2010, \apj, 714, 1407
+%
+%\bibitem[{{Casey}(2012)}]{Casey12a}
+%{Casey}, C.~M. 2012, \mnras, 425, 3094
+%
+%\bibitem[{{Casey} {et~al.}(2014){Casey}, {Narayanan}, \& {Cooray}}]{Casey14a}
+%{Casey}, C.~M., {Narayanan}, D., \& {Cooray}, A. 2014, \physrep, 541, 45
+%
+%\bibitem[{{Chabrier}(2003)}]{Chabrier03a}
+%{Chabrier}, G. 2003, \pasp, 115, 763
+%
+%\bibitem[{{Cleary} {et~al.}(2007){Cleary}, {Lawrence}, {Marshall}, {Hao}, \&
+%  {Meier}}]{Cleary07a}
+%{Cleary}, K., {Lawrence}, C.~R., {Marshall}, J.~A., {Hao}, L., \& {Meier}, D.
+%  2007, \apj, 660, 117
+%
+%\bibitem[{{Cohen} {et~al.}(2007){Cohen}, {Lane}, {Cotton}, {Kassim}, {Lazio},
+%  {Perley}, {Condon}, \& {Erickson}}]{r30}
+%{Cohen}, A.~S., {Lane}, W.~M., {Cotton}, W.~D., {et~al.} 2007, \aj, 134, 1245
+%
+%\bibitem[{{Condon} {et~al.}(1998){Condon}, {Cotton}, {Greisen}, {Yin},
+%  {Perley}, {Taylor}, \& {Broderick}}]{r16}
+%{Condon}, J.~J., {Cotton}, W.~D., {Greisen}, E.~W., {et~al.} 1998, \aj, 115,
+%  1693
+%
+%\bibitem[{{Conley} {et~al.}(2011){Conley}, {Cooray}, {Vieira}, {Gonz{\'a}lez
+%  Solares}, {Kim}, {Aguirre}, {Amblard}, {Auld}, {Baker}, {Beelen}, {Blain},
+%  {Blundell}, {Bock}, {Bradford}, {Bridge}, {Brisbin}, {Burgarella},
+%  {Carpenter}, {Chanial}, {Chapin}, {Christopher}, {Clements}, {Cox},
+%  {Djorgovski}, {Dowell}, {Eales}, {Earle}, {Ellsworth-Bowers}, {Farrah},
+%  {Franceschini}, {Frayer}, {Fu}, {Gavazzi}, {Glenn}, {Griffin}, {Gurwell},
+%  {Halpern}, {Ibar}, {Ivison}, {Jarvis}, {Kamenetzky}, {Krips}, {Levenson},
+%  {Lupu}, {Mahabal}, {Maloney}, {Maraston}, {Marchetti}, {Marsden},
+%  {Matsuhara}, {Mortier}, {Murphy}, {Naylor}, {Neri}, {Nguyen}, {Oliver},
+%  {Omont}, {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen},
+%  {Rangwala}, {Rawlings}, {Raymond}, {Riechers}, {Rodighiero}, {Roseboom},
+%  {Rowan-Robinson}, {Schulz}, {Scott}, {Scott}, {Serra}, {Seymour}, {Shupe},
+%  {Smith}, {Symeonidis}, {Tugwell}, {Vaccari}, {Valiante}, {Valtchanov},
+%  {Verma}, {Viero}, {Vigroux}, {Wang}, {Wiebe}, {Wright}, {Xu}, {Zeimann},
+%  {Zemcov}, \& {Zmuidzinas}}]{Conley11a}
+%{Conley}, A., {Cooray}, A., {Vieira}, J.~D., {et~al.} 2011, \apjl, 732, L35
+%
+%\bibitem[{{Coppin} {et~al.}(2008){Coppin}, {Swinbank}, {Neri}, {Cox},
+%  {Alexander}, {Smail}, {Page}, {Stevens}, {Knudsen}, {Ivison}, {Beelen},
+%  {Bertoldi}, \& {Omont}}]{Coppin08a}
+%{Coppin}, K.~E.~K., {Swinbank}, A.~M., {Neri}, R., {et~al.} 2008, \mnras, 389,
+%  45
+%
+%\bibitem[{{Danielson} {et~al.}(2011){Danielson}, {Swinbank}, {Smail}, {Cox},
+%  {Edge}, {Weiss}, {Harris}, {Baker}, {De Breuck}, {Geach}, {Ivison}, {Krips},
+%  {Lundgren}, {Longmore}, {Neri}, \& {Flaquer}}]{Danielson11a}
+%{Danielson}, A.~L.~R., {Swinbank}, A.~M., {Smail}, I., {et~al.} 2011, \mnras,
+%  410, 1687
+%
+%\bibitem[{{Deane} {et~al.}(2013){Deane}, {Heywood}, {Rawlings}, \&
+%  {Marshall}}]{Deane13a}
+%{Deane}, R.~P., {Heywood}, I., {Rawlings}, S., \& {Marshall}, P.~J. 2013,
+%  \mnras, 434, 23
+%
+%\bibitem[{{Dickinson} {et~al.}(2003){Dickinson}, {Papovich}, {Ferguson}, \&
+%  {Budav{\'a}ri}}]{Dickinson03a}
+%{Dickinson}, M., {Papovich}, C., {Ferguson}, H.~C., \& {Budav{\'a}ri}, T. 2003,
+%  \apj, 587, 25
+%
+%\bibitem[{{Dowell} {et~al.}(2014){Dowell}, {Conley}, {Glenn}, {Arumugam},
+%  {Asboth}, {Aussel}, {Bertoldi}, {B{\'e}thermin}, {Bock}, {Boselli}, {Bridge},
+%  {Buat}, {Burgarella}, {Cabrera-Lavers}, {Casey}, {Chapman}, {Clements},
+%  {Conversi}, {Cooray}, {Dannerbauer}, {De Bernardis}, {Ellsworth-Bowers},
+%  {Farrah}, {Franceschini}, {Griffin}, {Gurwell}, {Halpern}, {Hatziminaoglou},
+%  {Heinis}, {Ibar}, {Ivison}, {Laporte}, {Marchetti},
+%  {Mart{\'{\i}}nez-Navajas}, {Marsden}, {Morrison}, {Nguyen}, {O'Halloran},
+%  {Oliver}, {Omont}, {Page}, {Papageorgiou}, {Pearson}, {Petitpas},
+%  {P{\'e}rez-Fournon}, {Pohlen}, {Riechers}, {Rigopoulou}, {Roseboom},
+%  {Rowan-Robinson}, {Sayers}, {Schulz}, {Scott}, {Seymour}, {Shupe}, {Smith},
+%  {Streblyanska}, {Symeonidis}, {Vaccari}, {Valtchanov}, {Vieira}, {Viero},
+%  {Wang}, {Wardlow}, {Xu}, \& {Zemcov}}]{Dowell14a}
+%{Dowell}, C.~D., {Conley}, A., {Glenn}, J., {et~al.} 2014, \apj, 780, 75
+%
+%\bibitem[{{Downes} \& {Solomon}(1998)}]{Downes98a}
+%{Downes}, D., \& {Solomon}, P.~M. 1998, \apj, 507, 615
+%
+%\bibitem[{{Dunne} {et~al.}(2003){Dunne}, {Eales}, \& {Edmunds}}]{Dunne03a}
+%{Dunne}, L., {Eales}, S.~A., \& {Edmunds}, M.~G. 2003, \mnras, 341, 589
+%
+%\bibitem[{{Eales} {et~al.}(2010){Eales}, {Dunne}, {Clements}, {Cooray}, {de
+%  Zotti}, {Dye}, {Ivison}, {Jarvis}, {Lagache}, {Maddox}, {Negrello},
+%  {Serjeant}, {Thompson}, {van Kampen}, {Amblard}, {Andreani}, {Baes},
+%  {Beelen}, {Bendo}, {Benford}, {Bertoldi}, {Bock}, {Bonfield}, {Boselli},
+%  {Bridge}, {Buat}, {Burgarella}, {Carlberg}, {Cava}, {Chanial}, {Charlot},
+%  {Christopher}, {Coles}, {Cortese}, {Dariush}, {da Cunha}, {Dalton}, {Danese},
+%  {Dannerbauer}, {Driver}, {Dunlop}, {Fan}, {Farrah}, {Frayer}, {Frenk},
+%  {Geach}, {Gardner}, {Gomez}, {Gonz{\'a}lez-Nuevo}, {Gonz{\'a}lez-Solares},
+%  {Griffin}, {Hardcastle}, {Hatziminaoglou}, {Herranz}, {Hughes}, {Ibar},
+%  {Jeong}, {Lacey}, {Lapi}, {Lawrence}, {Lee}, {Leeuw}, {Liske},
+%  {L{\'o}pez-Caniego}, {M{\"u}ller}, {Nandra}, {Panuzzo}, {Papageorgiou},
+%  {Patanchon}, {Peacock}, {Pearson}, {Phillipps}, {Pohlen}, {Popescu},
+%  {Rawlings}, {Rigby}, {Rigopoulou}, {Robotham}, {Rodighiero}, {Sansom},
+%  {Schulz}, {Scott}, {Smith}, {Sibthorpe}, {Smail}, {Stevens}, {Sutherland},
+%  {Takeuchi}, {Tedds}, {Temi}, {Tuffs}, {Trichas}, {Vaccari}, {Valtchanov},
+%  {van der Werf}, {Verma}, {Vieria}, {Vlahakis}, \& {White}}]{Eales10a}
+%{Eales}, S., {Dunne}, L., {Clements}, D., {et~al.} 2010, \pasp, 122, 499
+%
+%\bibitem[{{Engel} {et~al.}(2010){Engel}, {Tacconi}, {Davies}, {Neri}, {Smail},
+%  {Chapman}, {Genzel}, {Cox}, {Greve}, {Ivison}, {Blain}, {Bertoldi}, \&
+%  {Omont}}]{Engel10a}
+%{Engel}, H., {Tacconi}, L.~J., {Davies}, R.~I., {et~al.} 2010, \apj, 724, 233
+%
+%\bibitem[{{Fanaroff} \& {Riley}(1974)}]{Fanaroff74}
+%{Fanaroff}, B.~L., \& {Riley}, J.~M. 1974, \mnras, 167, 31P
+%
+%\bibitem[{{Gavazzi} {et~al.}(2011){Gavazzi}, {Cooray}, {Conley}, {Aguirre},
+%  {Amblard}, {Auld}, {Beelen}, {Blain}, {Blundell}, {Bock}, {Bradford},
+%  {Bridge}, {Brisbin}, {Burgarella}, {Chanial}, {Chapin}, {Christopher},
+%  {Clements}, {Cox}, {Djorgovski}, {Dowell}, {Eales}, {Earle},
+%  {Ellsworth-Bowers}, {Farrah}, {Franceschini}, {Fu}, {Glenn}, {Gonz{\'a}lez
+%  Solares}, {Griffin}, {Gurwell}, {Halpern}, {Ibar}, {Ivison}, {Jarvis},
+%  {Kamenetzky}, {Kim}, {Krips}, {Levenson}, {Lupu}, {Mahabal}, {Maloney},
+%  {Maraston}, {Marchetti}, {Marsden}, {Matsuhara}, {Mortier}, {Murphy},
+%  {Naylor}, {Neri}, {Nguyen}, {Oliver}, {Omont}, {Page}, {Papageorgiou},
+%  {Pearson}, {P{\'e}rez-Fournon}, {Pohlen}, {Rangwala}, {Rawlings}, {Raymond},
+%  {Riechers}, {Rodighiero}, {Roseboom}, {Rowan-Robinson}, {Schulz}, {Scott},
+%  {Scott}, {Serra}, {Seymour}, {Shupe}, {Smith}, {Symeonidis}, {Tugwell},
+%  {Vaccari}, {Valiante}, {Valtchanov}, {Verma}, {Vieira}, {Vigroux}, {Wang},
+%  {Wardlow}, {Wiebe}, {Wright}, {Xu}, {Zeimann}, {Zemcov}, \&
+%  {Zmuidzinas}}]{Gavazzi11a}
+%{Gavazzi}, R., {Cooray}, A., {Conley}, A., {et~al.} 2011, \apj, 738, 125
+%
+%\bibitem[{{Greve} {et~al.}(2005){Greve}, {Bertoldi}, {Smail}, {Neri},
+%  {Chapman}, {Blain}, {Ivison}, {Genzel}, {Omont}, {Cox}, {Tacconi}, \&
+%  {Kneib}}]{Greve05a}
+%{Greve}, T.~R., {Bertoldi}, F., {Smail}, I., {et~al.} 2005, \mnras, 359, 1165
+%
+%\bibitem[{{Haas} {et~al.}(2014){Haas}, {Leipski}, {Barthel}, {Wilkes},
+%  {Vegetti}, {Bussmann}, {Willner}, {Westhues}, {Ashby}, {Chini}, {Clements},
+%  {Fassnacht}, {Horesh}, {Klaas}, {Koopmans}, {Kuraszkiewicz}, {Lagattuta},
+%  {Meisenheimer}, {Stern}, \& {Wylezalek}}]{Haas14}
+%{Haas}, M., {Leipski}, C., {Barthel}, P., {et~al.} 2014, \apj, 790, 46 (H14)
+%
+%\bibitem[{{Hales} {et~al.}(1995){Hales}, {Waldram}, {Rees}, \&
+%  {Warner}}]{r33-34}
+%{Hales}, S.~E.~G., {Waldram}, E.~M., {Rees}, N., \& {Warner}, P.~J. 1995,
+%  \mnras, 274, 447
+%
+%\bibitem[{{Hardcastle} \& {Looney}(2008)}]{Hardcastle08a}
+%{Hardcastle}, M.~J., \& {Looney}, L.~W. 2008, \mnras, 388, 176
+%
+%\bibitem[{{Harris} {et~al.}(2010){Harris}, {Baker}, {Zonak}, {Sharon},
+%  {Genzel}, {Rauch}, {Watts}, \& {Creager}}]{Harris10a}
+%{Harris}, A.~I., {Baker}, A.~J., {Zonak}, S.~G., {et~al.} 2010, \apj, 723, 1139
+%
+%\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
+%  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
+%  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
+%  \& {Wright}}]{Hinshaw13a}
+%{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {et~al.} 2013, \apjs, 208, 19
+%
+%\bibitem[{{Ivison} {et~al.}(2011){Ivison}, {Papadopoulos}, {Smail}, {Greve},
+%  {Thomson}, {Xilouris}, \& {Chapman}}]{Ivison11a}
+%{Ivison}, R.~J., {Papadopoulos}, P.~P., {Smail}, I., {et~al.} 2011, \mnras,
+%  412, 1913
+%
+%\bibitem[{{Ivison} {et~al.}(2010{\natexlab{a}}){Ivison}, {Smail},
+%  {Papadopoulos}, {Wold}, {Richard}, {Swinbank}, {Kneib}, \&
+%  {Owen}}]{Ivison10d}
+%{Ivison}, R.~J., {Smail}, I., {Papadopoulos}, P.~P., {et~al.}
+%  2010{\natexlab{a}}, \mnras, 404, 198
+%
+%\bibitem[{{Ivison} {et~al.}(2010{\natexlab{b}}){Ivison}, {Swinbank},
+%  {Swinyard}, {Smail}, {Pearson}, {Rigopoulou}, {Polehampton}, {Baluteau},
+%  {Barlow}, {Blain}, {Bock}, {Clements}, {Coppin}, {Cooray}, {Danielson},
+%  {Dwek}, {Edge}, {Franceschini}, {Fulton}, {Glenn}, {Griffin}, {Isaak},
+%  {Leeks}, {Lim}, {Naylor}, {Oliver}, {Page}, {P{\'e}rez Fournon},
+%  {Rowan-Robinson}, {Savini}, {Scott}, {Spencer}, {Valtchanov}, {Vigroux}, \&
+%  {Wright}}]{Ivison10c}
+%{Ivison}, R.~J., {Swinbank}, A.~M., {Swinyard}, B., {et~al.}
+%  2010{\natexlab{b}}, \aap, 518, L35
+%
+%\bibitem[{{Kellermann} \& {Pauliny-Toth}(1973)}]{r9}
+%{Kellermann}, K.~I., \& {Pauliny-Toth}, I.~I.~K. 1973, \aj, 78, 828
+%
+%\bibitem[{{Kellermann} \& {Pauliny-Toth}(1981)}]{Kellermann81a}
+%---. 1981, \araa, 19, 373
+%
+%\bibitem[{{Kellermann} {et~al.}(1969){Kellermann}, {Pauliny-Toth}, \&
+%  {Williams}}]{r11-14-18-22-25-32}
+%{Kellermann}, K.~I., {Pauliny-Toth}, I.~I.~K., \& {Williams}, P.~J.~S. 1969,
+%  \apj, 157, 1
+%
+%\bibitem[{{Kennicutt}(1998)}]{Kennicutt98a}
+%{Kennicutt}, Jr., R.~C. 1998, \araa, 36, 189
+%
+%\bibitem[{{Lagache} {et~al.}(2005){Lagache}, {Puget}, \& {Dole}}]{Lagache05a}
+%{Lagache}, G., {Puget}, J.-L., \& {Dole}, H. 2005, \araa, 43, 727
+%
+%\bibitem[{{Laing} \& {Peacock}(1980)}]{r10-13-15-19-20-26-29-31}
+%{Laing}, R.~A., \& {Peacock}, J.~A. 1980, \mnras, 190, 903
+%
+%\bibitem[{{Meisenheimer} {et~al.}(1989){Meisenheimer}, {Roser}, {Hiltner},
+%  {Yates}, {Longair}, {Chini}, \& {Perley}}]{Meisenheimer89a}
+%{Meisenheimer}, K., {Roser}, H.-J., {Hiltner}, P.~R., {et~al.} 1989, \aap, 219,
+%  63
+%
+%\bibitem[{{Micha{\l}owski} {et~al.}(2010){Micha{\l}owski}, {Watson}, \&
+%  {Hjorth}}]{Micha10a}
+%{Micha{\l}owski}, M.~J., {Watson}, D., \& {Hjorth}, J. 2010, \apj, 712, 942
+%
+%\bibitem[{{Mullin} {et~al.}(2006){Mullin}, {Hardcastle}, \&
+%  {Riley}}]{Mullin06a}
+%{Mullin}, L.~M., {Hardcastle}, M.~J., \& {Riley}, J.~M. 2006, \mnras, 372, 113
+%
+%\bibitem[{{Negrello} {et~al.}(2010){Negrello}, {Hopwood}, {De Zotti}, {Cooray},
+%  {Verma}, {Bock}, {Frayer}, {Gurwell}, {Omont}, {Neri}, {Dannerbauer},
+%  {Leeuw}, {Barton}, {Cooke}, {Kim}, {da Cunha}, {Rodighiero}, {Cox},
+%  {Bonfield}, {Jarvis}, {Serjeant}, {Ivison}, {Dye}, {Aretxaga}, {Hughes},
+%  {Ibar}, {Bertoldi}, {Valtchanov}, {Eales}, {Dunne}, {Driver}, {Auld},
+%  {Buttiglione}, {Cava}, {Grady}, {Clements}, {Dariush}, {Fritz}, {Hill},
+%  {Hornbeck}, {Kelvin}, {Lagache}, {Lopez-Caniego}, {Gonzalez-Nuevo}, {Maddox},
+%  {Pascale}, {Pohlen}, {Rigby}, {Robotham}, {Simpson}, {Smith}, {Temi},
+%  {Thompson}, {Woodgate}, {York}, {Aguirre}, {Beelen}, {Blain}, {Baker},
+%  {Birkinshaw}, {Blundell}, {Bradford}, {Burgarella}, {Danese}, {Dunlop},
+%  {Fleuren}, {Glenn}, {Harris}, {Kamenetzky}, {Lupu}, {Maddalena}, {Madore},
+%  {Maloney}, {Matsuhara}, {Micha{\l}owski}, {Murphy}, {Naylor}, {Nguyen},
+%  {Popescu}, {Rawlings}, {Rigopoulou}, {Scott}, {Scott}, {Seibert}, {Smail},
+%  {Tuffs}, {Vieira}, {van der Werf}, \& {Zmuidzinas}}]{Negrello10a}
+%{Negrello}, M., {Hopwood}, R., {De Zotti}, G., {et~al.} 2010, Science, 330, 800
+%
+%\bibitem[{{Oliver} {et~al.}(2012){Oliver}, {Bock}, {Altieri}, {Amblard},
+%  {Arumugam}, {Aussel}, {Babbedge}, {Beelen}, {B{\'e}thermin}, {Blain},
+%  {Boselli}, {Bridge}, {Brisbin}, {Buat}, {Burgarella},
+%  {Castro-Rodr{\'{\i}}guez}, {Cava}, {Chanial}, {Cirasuolo}, {Clements},
+%  {Conley}, {Conversi}, {Cooray}, {Dowell}, {Dubois}, {Dwek}, {Dye}, {Eales},
+%  {Elbaz}, {Farrah}, {Feltre}, {Ferrero}, {Fiolet}, {Fox}, {Franceschini},
+%  {Gear}, {Giovannoli}, {Glenn}, {Gong}, {Gonz{\'a}lez Solares}, {Griffin},
+%  {Halpern}, {Harwit}, {Hatziminaoglou}, {Heinis}, {Hurley}, {Hwang}, {Hyde},
+%  {Ibar}, {Ilbert}, {Isaak}, {Ivison}, {Lagache}, {Le Floc'h}, {Levenson},
+%  {Faro}, {Lu}, {Madden}, {Maffei}, {Magdis}, {Mainetti}, {Marchetti},
+%  {Marsden}, {Marshall}, {Mortier}, {Nguyen}, {O'Halloran}, {Omont}, {Page},
+%  {Panuzzo}, {Papageorgiou}, {Patel}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen},
+%  {Rawlings}, {Raymond}, {Rigopoulou}, {Riguccini}, {Rizzo}, {Rodighiero},
+%  {Roseboom}, {Rowan-Robinson}, {S{\'a}nchez Portal}, {Schulz}, {Scott},
+%  {Seymour}, {Shupe}, {Smith}, {Stevens}, {Symeonidis}, {Trichas}, {Tugwell},
+%  {Vaccari}, {Valtchanov}, {Vieira}, {Viero}, {Vigroux}, {Wang}, {Ward},
+%  {Wardlow}, {Wright}, {Xu}, \& {Zemcov}}]{Oliver12a}
+%{Oliver}, S.~J., {Bock}, J., {Altieri}, B., {et~al.} 2012, \mnras, 424, 1614
+%
+%\bibitem[{{Pauliny-Toth} {et~al.}(1966){Pauliny-Toth}, {Wade}, \&
+%  {Heeschen}}]{r17-21}
+%{Pauliny-Toth}, I.~I.~K., {Wade}, C.~M., \& {Heeschen}, D.~S. 1966, \apjs, 13,
+%  65
+%
+%\bibitem[{{Polletta} {et~al.}(2011){Polletta}, {Nesvadba}, {Neri}, {Omont},
+%  {Berta}, \& {Bergeron}}]{Polletta11a}
+%{Polletta}, M., {Nesvadba}, N.~P.~H., {Neri}, R., {et~al.} 2011, \aap, 533, A20
+%
+%\bibitem[{{Rengelink} {et~al.}(1997){Rengelink}, {Tang}, {de Bruyn}, {Miley},
+%  {Bremer}, {Roettgering}, \& {Bremer}}]{r23-24}
+%{Rengelink}, R.~B., {Tang}, Y., {de Bruyn}, A.~G., {et~al.} 1997, \aaps, 124,
+%  259
+%
+%\bibitem[{{Riechers} {et~al.}(2006){Riechers}, {Walter}, {Carilli}, {Knudsen},
+%  {Lo}, {Benford}, {Staguhn}, {Hunter}, {Bertoldi}, {Henkel}, {Menten},
+%  {Weiss}, {Yun}, \& {Scoville}}]{Riechers06a}
+%{Riechers}, D.~A., {Walter}, F., {Carilli}, C.~L., {et~al.} 2006, \apj, 650,
+%  604
+%
+%\bibitem[{{Riechers} {et~al.}(2011{\natexlab{a}}){Riechers}, {Hodge}, {Walter},
+%  {Carilli}, \& {Bertoldi}}]{Riechers11c}
+%{Riechers}, D.~A., {Hodge}, J., {Walter}, F., {Carilli}, C.~L., \& {Bertoldi},
+%  F. 2011{\natexlab{a}}, \apjl, 739, L31
+%
+%\bibitem[{{Riechers} {et~al.}(2011{\natexlab{b}}){Riechers}, {Carilli},
+%  {Walter}, {Weiss}, {Wagg}, {Bertoldi}, {Downes}, {Henkel}, \&
+%  {Hodge}}]{Riechers11d}
+%{Riechers}, D.~A., {Carilli}, L.~C., {Walter}, F., {et~al.} 2011{\natexlab{b}},
+%  \apjl, 733, L11
+%
+%\bibitem[{{Riechers} {et~al.}(2011{\natexlab{c}}){Riechers}, {Carilli},
+%  {Maddalena}, {Hodge}, {Harris}, {Baker}, {Walter}, {Wagg}, {Vanden Bout},
+%  {Wei{\ss}}, \& {Sharon}}]{Riechers11a}
+%{Riechers}, D.~A., {Carilli}, C.~L., {Maddalena}, R.~J., {et~al.}
+%  2011{\natexlab{c}}, \apjl, 739, L32
+%
+%\bibitem[{{Riechers} {et~al.}(2011{\natexlab{d}}){Riechers}, {Cooray}, {Omont},
+%  {Neri}, {Harris}, {Baker}, {Cox}, {Frayer}, {Carpenter}, {Auld}, {Aussel},
+%  {Beelen}, {Blundell}, {Bock}, {Brisbin}, {Burgarella}, {Chanial}, {Chapman},
+%  {Clements}, {Conley}, {Dowell}, {Eales}, {Farrah}, {Franceschini}, {Gavazzi},
+%  {Glenn}, {Griffin}, {Gurwell}, {Ivison}, {Kim}, {Krips}, {Mortier}, {Oliver},
+%  {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen}, {Rawlings},
+%  {Raymond}, {Rodighiero}, {Roseboom}, {Rowan-Robinson}, {Scott}, {Seymour},
+%  {Smith}, {Symeonidis}, {Tugwell}, {Vaccari}, {Vieira}, {Vigroux}, {Wang},
+%  {Wardlow}, \& {Wright}}]{Riechers11b}
+%{Riechers}, D.~A., {Cooray}, A., {Omont}, A., {et~al.} 2011{\natexlab{d}},
+%  \apjl, 733, L12
+%
+%
+%\bibitem[{{Riechers} {et~al.}(2013){Riechers}, {Bradford}, {Clements},
+%  {Dowell}, {P{\'e}rez-Fournon}, {Ivison}, {Bridge}, {Conley}, {Fu}, {Vieira},
+%  {Wardlow}, {Calanog}, {Cooray}, {Hurley}, {Neri}, {Kamenetzky}, {Aguirre},
+%  {Altieri}, {Arumugam}, {Benford}, {B{\'e}thermin}, {Bock}, {Burgarella},
+%  {Cabrera-Lavers}, {Chapman}, {Cox}, {Dunlop}, {Earle}, {Farrah}, {Ferrero},
+%  {Franceschini}, {Gavazzi}, {Glenn}, {Solares}, {Gurwell}, {Halpern},
+%  {Hatziminaoglou}, {Hyde}, {Ibar}, {Kov{\'a}cs}, {Krips}, {Lupu}, {Maloney},
+%  {Martinez-Navajas}, {Matsuhara}, {Murphy}, {Naylor}, {Nguyen}, {Oliver},
+%  {Omont}, {Page}, {Petitpas}, {Rangwala}, {Roseboom}, {Scott}, {Smith},
+%  {Staguhn}, {Streblyanska}, {Thomson}, {Valtchanov}, {Viero}, {Wang},
+%  {Zemcov}, \& {Zmuidzinas}}]{Riechers13a}
+%{Riechers}, D.~A., {Bradford}, C.~M., {Clements}, D.~L., {et~al.} 2013, \nat,
+%  496, 329
+%
+%
+%\bibitem[{{Sanders} {et~al.}(1988){Sanders}, {Soifer}, {Elias}, {Madore},
+%  {Matthews}, {Neugebauer}, \& {Scoville}}]{Sanders88}
+%{Sanders}, D.~B., {Soifer}, B.~T., {Elias}, J.~H., {et~al.} 1988, \apj, 325, 74
+%
+%\bibitem[{{Scott} {et~al.}(2011){Scott}, {Lupu}, {Aguirre}, {Auld}, {Aussel},
+%  {Baker}, {Beelen}, {Bock}, {Bradford}, {Brisbin}, {Burgarella}, {Carpenter},
+%  {Chanial}, {Chapman}, {Clements}, {Conley}, {Cooray}, {Cox}, {Dowell},
+%  {Eales}, {Farrah}, {Franceschini}, {Frayer}, {Gavazzi}, {Glenn}, {Griffin},
+%  {Harris}, {Ibar}, {Ivison}, {Kamenetzky}, {Kim}, {Krips}, {Maloney},
+%  {Matsuhara}, {Mortier}, {Murphy}, {Naylor}, {Neri}, {Nguyen}, {Oliver},
+%  {Omont}, {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen},
+%  {Rawlings}, {Raymond}, {Riechers}, {Rodighiero}, {Roseboom},
+%  {Rowan-Robinson}, {Scott}, {Seymour}, {Smith}, {Symeonidis}, {Tugwell},
+%  {Vaccari}, {Vieira}, {Vigroux}, {Wang}, {Wright}, \& {Zmuidzinas}}]{Scott11a}
+%{Scott}, K.~S., {Lupu}, R.~E., {Aguirre}, J.~E., {et~al.} 2011, \apj, 733, 29
+%
+%\bibitem[{{Simpson} {et~al.}(2012){Simpson}, {Smail}, {Swinbank}, {Alexander},
+%  {Auld}, {Baes}, {Bonfield}, {Clements}, {Cooray}, {Coppin}, {Danielson},
+%  {Dariush}, {Dunne}, {de Zotti}, {Harrison}, {Hopwood}, {Hoyos}, {Ibar},
+%  {Ivison}, {Jarvis}, {Lapi}, {Maddox}, {Page}, {Riechers}, {Valiante}, \& {van
+%  der Werf}}]{Simpson12a}
+%{Simpson}, J.~M., {Smail}, I., {Swinbank}, A.~M., {et~al.} 2012, \mnras, 426,
+%  3201
+%
+%\bibitem[{{Smol{\v c}i{\'c}} \& {Riechers}(2011)}]{Smolcic11a}
+%{Smol{\v c}i{\'c}}, V., \& {Riechers}, D.~A. 2011, \apj, 730, 64
+%
+%\bibitem[{{Solomon} \& {Vanden Bout}(2005)}]{Solomon05a}
+%{Solomon}, P.~M., \& {Vanden Bout}, P.~A. 2005, \araa, 43, 677
+%
+%\bibitem[{{Swinbank} {et~al.}(2010){Swinbank}, {Smail}, {Longmore}, {Harris},
+%  {Baker}, {De Breuck}, {Richard}, {Edge}, {Ivison}, {Blundell}, {Coppin},
+%  {Cox}, {Gurwell}, {Hainline}, {Krips}, {Lundgren}, {Neri}, {Siana},
+%  {Siringo}, {Stark}, {Wilner}, \& {Younger}}]{Swinbank2010a}
+%{Swinbank}, A.~M., {Smail}, I., {Longmore}, S., {et~al.} 2010, \nat, 464, 733
+%
+%\bibitem[{{Swinbank} {et~al.}(2011){Swinbank}, {Papadopoulos}, {Cox}, {Krips},
+%  {Ivison}, {Smail}, {Thomson}, {Neri}, {Richard}, \& {Ebeling}}]{Swinbank11a}
+%{Swinbank}, A.~M., {Papadopoulos}, P.~P., {Cox}, P., {et~al.} 2011, \apj, 742,
+%  11
+%
+%\bibitem[{{Tacconi} {et~al.}(2006){Tacconi}, {Neri}, {Chapman}, {Genzel},
+%  {Smail}, {Ivison}, {Bertoldi}, {Blain}, {Cox}, {Greve}, \&
+%  {Omont}}]{Tacconi06a}
+%{Tacconi}, L.~J., {Neri}, R., {Chapman}, S.~C., {et~al.} 2006, \apj, 640, 228
+%
+%\bibitem[{{Tacconi} {et~al.}(2008){Tacconi}, {Genzel}, {Smail}, {Neri},
+%  {Chapman}, {Ivison}, {Blain}, {Cox}, {Omont}, {Bertoldi}, {Greve},
+%  {F{\"o}rster Schreiber}, {Genel}, {Lutz}, {Swinbank}, {Shapley}, {Erb},
+%  {Cimatti}, {Daddi}, \& {Baker}}]{Tacconi08a}
+%{Tacconi}, L.~J., {Genzel}, R., {Smail}, I., {et~al.} 2008, \apj, 680, 246
+%
+%%\bibitem[{{Tacconi} {et~al.}(2010){Tacconi}, {Genzel}, {Neri}, {Cox}, {Cooper},
+%%  {Shapiro}, {Bolatto}, {Bouch{\'e}}, {Bournaud}, {Burkert}, {Combes},
+%%  {Comerford}, {Davis}, {Schreiber}, {Garcia-Burillo}, {Gracia-Carpio}, {Lutz},
+%%  {Naab}, {Omont}, {Shapley}, {Sternberg}, \& {Weiner}}]{Tacconi10a}
+%%{Tacconi}, L.~J., {Genzel}, R., {Neri}, R., {et~al.} 2010, \nat, 463, 781
+%
+%\bibitem[{{Vieira} {et~al.}(2010){Vieira}, {Crawford}, {Switzer}, {Ade},
+%  {Aird}, {Ashby}, {Benson}, {Bleem}, {Brodwin}, {Carlstrom}, {Chang}, {Cho},
+%  {Crites}, {de Haan}, {Dobbs}, {Everett}, {George}, {Gladders}, {Hall},
+%  {Halverson}, {High}, {Holder}, {Holzapfel}, {Hrubes}, {Joy}, {Keisler},
+%  {Knox}, {Lee}, {Leitch}, {Lueker}, {Marrone}, {McIntyre}, {McMahon}, {Mehl},
+%  {Meyer}, {Mohr}, {Montroy}, {Padin}, {Plagge}, {Pryke}, {Reichardt}, {Ruhl},
+%  {Schaffer}, {Shaw}, {Shirokoff}, {Spieler}, {Stalder}, {Staniszewski},
+%  {Stark}, {Vanderlinde}, {Walsh}, {Williamson}, {Yang}, {Zahn}, \&
+%  {Zenteno}}]{Vieira10a}
+%{Vieira}, J.~D., {Crawford}, T.~M., {Switzer}, E.~R., {et~al.} 2010, \apj, 719,
+%  763
+%
+%\bibitem[{{Wilson} {et~al.}(1970){Wilson}, {Jefferts}, \&
+%  {Penzias}}]{Wilson70a}
+%{Wilson}, R.~W., {Jefferts}, K.~B., \& {Penzias}, A.~A. 1970, \apjl, 161, L43
+%
+%\end{thebibliography}
 
 \appendix
-We perform the SED fitting to the (sub)-mm data of SMM\,J0939 using {\sc mbb\_emcee} (see \S \ref{sec:SEDBg}), this code uses MCMC to sample the parameter space of each parameter.
-The total IR luminosity and dust mass are then derived from the set of parameters that maximizes the likelihood.
+We perform SED fitting to the (sub)-mm data of SMM\,J0939 using {\sc mbb\_emcee} (see \S \ref{sec:SEDBg}).
+This code uses MCMC to sample the parameter spaces, the total IR luminosity and dust mass are then derived from the set of parameters that maximizes the likelihood.
 We show in Figure~\ref{fig:sedlikelihood} the resulting correlation plots of each pair of parameters (off-diagonals) as well as the marginalized PDFs of each parameter (diagonals) for the fitted optically thick and optically thin models.
@@
 parameter of the best-fit solution between these two scenarios is less than 3\%, except for the dust mass, which is boosted by a factor of $\sim$\,2. This is
-unsurprising given the dearth of data in the FIR waveband, leading to a weakly constrained emissivity, and thus the inferred dust mass.
-In our analysis, we employed the set of parameters and thus inferred properties (dust mass, and IR luminosity) from the former.
+unsurprising given the dearth of data in the FIR wavebands, leading to a weakly constrained emissivity, and thus, inferred dust mass.
+In our analysis, we employ the best-fit parameters and the corresponding inferred properties (dust mass, and IR luminosity) from the former, where a tighter constraint is imposed on $\beta$.
 
@@
 \centering
+\hspace{-1.1cm}
+\includegraphics[width=0.55\textwidth]{Figure/CorrelationPlot__thick_500_500_cmyk.eps}
 \hspace{-1cm}
-\includegraphics[width=0.55\textwidth]{Figure/CorrelationPlot__thick_500_500_cmyk}
-\hspace{-1.15cm}
-\includegraphics[width=0.55\textwidth]{Figure/CorrelationPlot__thin_testSMA_cmyk.pdf}
-\hspace{-1cm}
+\includegraphics[width=0.55\textwidth]{Figure/CorrelationPlot__thin_testSMA_cmyk}
+\hspace{-1.1cm}
 \caption{Correlation plots from the fitted SEDs, using an optically thick

### 2015-12-07 mod1/response.txt
in response to referee report. Need to edit conclusion in ms.tex, need to edit Table 4, currently using LIR to derive SFR, etc

We thank the referee for providing constructive comments to improve this manuscipt. We have addressed all the concerns raised by the referee and details can be found in the revised version. A brief description of how we have incoprated the changes can be found below.

Major comments:

- There is already a lensing model in H14 (a paper the authors refer to numerous times) and it is unclear why they redid the lensing model (they use the same SMA data as H14 but a different code). If the derived model is significantly different from H14 then this should be highlighted otherwise the lens modeling section isn't necessary in this paper.
> We moved the lens mass and consistent results into table 1 and its caption, and removed details of the lens model / shortened the section. However, we retained this section in this paper as we provide the best-fit parameters that were not reported in Haas14 and since we use the inferred half-light radius later in the analysis.

- section 4.3 is way too wordy and can be cut down to a few paragraphs and a table summarizing these key values (already given in Table 4). These are all standard calculations and you can refer to CW14 for the equations rather than repeating them here.
> we have removed standard equations.
> combined SFE and SFR into one section, and trimmed a few sentences in ths section.

- You should also summarize the evidence for the AGN in this SMG (maybe when you mention this in the intro) so the reader doesn't have to read H14.
> We have restructured the intro, writing explicitly the evidence of AGN. 
>

- [a further concern/question about Table 4 is whether all the same assumptions such as excitation, alpha_co, etc. were made for the other SMGs otherwise the comparisons are meaningless]
> We added notes to these assumptions in the caption below Tab. 4.
=============================

- The SMG is thought to harbor a luminous AGN. In that case, the LIR will certainly have a contribution from the AGN that should be accounted for otherwise the SFR will be overestimated: see e.g. Coppin+2010, Kirkpatrick+2012, Magdis+2013, Kirkpatrick+2014. Please correct LIR for the AGN emission prior to estimating SFR and include an AGN component in the SED fitting. 
>In our analysis, we fit SED models to the rest-frame FIR, which has been found to have AGN negligible contributions to IR luminosities - Pope+08 report that AGN contributions to the bolometric IR luminosity is at most 30%. Since we do not have MIR data (for just the background SMG, as postive K blueward of dust peak), we didn't fit an AGN component. Including an additional component, and thus free parameters to the SED model will be over-fitted due to the limited amount of data at hand. Instead our SED model includes a power-law to the blue side of the dust peak, which accounts for the MIR excess and allows us to estimate the IR luminosity (Kirkpatrick+15, Riechers+13, Johnson+13, Casey+12). 
or should I change it to FIR --> SFR
> In our analysis, we fit SED models to the rest-frame FIR, which has been found to have negligible AGN contribution to rest-frame FIR (≥ 60µm; Carilli+05, Netzer+07, Mullaney+11, Harrison+15). We derived the SFR and other corresponding properties using the L_FIR, (45-122.5), which SF-driven dust emission.
> --> then change SFR using L_FIR instead of L_IR

- Section 5: why do the authors cherry-pick these 2 SMGs to make comparisons? there are many other sources that could be chosen with a range of properties. A comparison to these 2 SMGs is not useful at all given the diversity in this population (e.g. the sentence "This demonstrates the large ..." is not true when comparing only 3 objects). I suggest comparing to the general properties observed for SMGs (as summarized in CW14 or Casey+14) which will be more useful in placing this object in the context of the SMG population. 
> added columns to table referencing the properties of the population from a review. We picked out two lensed gravitaitonally lensed SMGs to demonstrate the power? extreme cases of SMGs which are intrinsically sit at the bright and faint ends.

- the discussion/conclusions should focus on what is new from this paper and not what is already presented in H14. E.g. the last sentence about this SMG transitioning from starburst to QSO phase. How is that conclusion made or strengthened with this new data?
> SFR and massive gas reservoir, coupled with the low depletion time of gas --> its short phase in the proposed evolutionary link

Minor comments:
**DONE**
- section headings in 3 are strange. Remove the words "New results" since this is obvious and a requirement for publication. Also remove subheading or second line in heading 3.2.
> we have removed "New results" in the subject headings

**DONE**
- the left panels on Fig 1 and 2 should show the same region (have the same RA/DEC axes). It is also tough to tell by eye if the VLA9GHz and SMA emission is coincident. Perhaps these can be overlayed on Fig 1.
> we marked the locations of the peak emission from the SMA as white crosses on the right panel on figure 1

**DONE**
- figure 3: orange is difficult to see. What is the SNR of the residuals in the right panel?
> we modified our caption to state that the quoted contour levels are the same for both panels in the figure. We changed the critical line color to green to easily visualization.

**Ask for clairfication**
- figure 4: again colors (red, orange) are hard to distinguish on a print out version of the paper.
> figure 3?
>

**DONE**
- specify the wavelengths range assumed for FIR.
> We mentioned the FIR range in Section 4.2.2

**DONE**
- last para section 4.2.2: it is limited data in the submm not the FIR [need to be probing Rayleigh Jeans] that makes the dust mass weakly constrained. I don't understand what the last sentence in this para means - I think there are words missing.
> We clarify this by adding the phrase "rest-frame" to FIR. We also wrote/restructured the last paragraph more clearly.

**DONE**
- SF surface density: from resolved studies of SMGs is it reasonable to divide half the SFR and gas mass by the area out to the half-light radii? give appropriate references to justify this assumption.
> We provide a few citations to show that this is typical, and allow our results to be compared across other findings in literature.
> 
>

**DONE**
- intro: the first para makes it sound like our knowledge of SMGs comes primarily from SMGs found in large sky Herschel surveys and SPT but this is not true. Please include references to earlier work that established the basic properties of SMGs (redshift distribution, luminosities, SFRs, Mgas, etc) prior to Herschel even launching.
> we restructured the paragraph and added earlier discoveries.

**DONE**
- the fact that the lensing system has two components isn't presented clearly in this paper. I had to read H14 to understand what the authors meant when they mentioned companion B. Please make this clearer so the reader does not have to read H14
> added a sentence to elaborate.

**DONE**
- last few paras of paper: what does "breaking up its dust cocoon" mean? this is the first time this is mentioned and should be explained if it is relevant.
> we mentioned this as a reference from Haas+14. We have removed this phrase in the revised version given that this has been mentioned in Haas+14, and is not necessary in my discussion.

**DONE**
- end of section 4.3.1: the factor of 2 for dust mass is overshadowed by the factor of >5 in alpha_co
> We removed that sentence.

**DONE**
- related to depletion time, there is a new Nature paper by Narayanan et al (published Sept 23) which discusses how SMGs in sims can last for a Gyr with replenishment from the IGM. In that case, is the depletion timescale really useful? what do we learn if the galaxy is getting new gas?
>The derived depletion timescale is derived the based on the definition of the quantity τ = Mgas/SFR, which descibes 
the time 
it would take for a galaxy to use up the available molecular gas reservoir given the current star formation rate, assuming no 
replenishment of gas (Carilli & Walter 2013). Hence, this quantity provides a lower limit on the timescale for SF activity. 
Based on our observations, we find no evidence of gas inflow in SMMJ0939.

**DONE**- 
dynamical mass calculation: can you estimate how much higher this would be given observations showing the different radii between the molecular and dust emission in SMGs. How different are the radii?
>The half-light radius of dust emitting region is ~ 1.2 kpc based on a recent study by Simpson+15, who collected ALMA 870 µm data over 52 SMGs.
> Tacconi et al. (2006) report a median FWHM size of 4.1 ±1.6 kpc based on CO measurements.
> 
Daisy: @DR, should I calculate a dynamical mass using Median from Tacconi+06 as well? I get Mdyn ~ 36.8e10 Msun. Should I include these sizes in the paper? or just feed this to the referee.?

**DONE**
- appendix: "no evidence of correlation" do the authors mean "covariance" here?
> We used the word "correlation" to indicate that regardless of the variation found in dust mass due to a different prior imposed on the emissivity, the IR luminosity is insensivtive to such changes in dust mass. Both the dust mass and IR lumonisty are inferred from the posterior probability distribution of the SED model, and are not parameters in the model / loss function. For these reasons, we do not mean the covariance here.

=================================

- the depletion time seems short compared to other SMGs which are ~100Myr although maybe it is consistent with other SMGs with AGN in them.
> Taken into account one of the comments listed above, we added literature reference to Table 4, and the depletion time scale is consistent with other SMGs.
> Greve05: 40-100 Myr

### 2015-12-07 mod1/manuscript/ms.tex
in response to referee report. Need to edit conclusion in ms.tex, need to edit Table 4, currently using LIR to derive SFR, etc

--- 2015-10-27 skeleton.tex
@@
 \documentclass[iop]{emulateapj}
-%\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
 \usepackage[breaklinks,colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
@@
 \newcommand{\CO}{\mbox{CO($J$\,=\,3\,$\rightarrow$\,2) }}
+\newcommand{\rot}[3][CO]{\mbox{#1($J$\,=\,#2\,\rarr\,#3)}} 
 \newcommand{\Lp}{\mbox{$L^{\prime}_\textrm{CO(1-0)}$}}
@@
 \newcommand\tni{\,\tablenotemark{i}}
-\newcommand\tnj{\,\tablenotemark{j}}
-\newcommand\tnk{\,\tablenotemark{k}}
 
-%\slugcomment{{\sc Accepted to ApJ:} August 1, 2006}
-\slugcomment{To be submitted to the ApJ}
+\slugcomment{Submitted to the ApJ}
 \usepackage{amsmath}
-\usepackage{natbib}
-\citestyle{aa}
 \shorttitle{Study of a strongly-lensed type-2 quasar host SMG at $z$\,=\,2.221}
@@
 the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
-SMM\,J0939+8315 hosts a type-2 quasar, and is gravitationally lensed by the radio galaxy 3C220.3 at $z$ = 0.685.
+SMM\,J0939+8315 hosts a type-2 quasar, and is gravitationally lensed by the radio galaxy 3C220.3 {\bf and its companion galaxy} at $z$ = 0.685.
 The 104 GHz continuum emission underlying the CO line is detected toward 3C220.3 with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy.
@@
 \section{Introduction}\label{sec:intro}
-Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1\,--\,3, during the epoch of stellar mass and
-galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}.
-These galaxies are luminous at submillimeter (submm) wavelengths due to the reprocessed stellar light that is being emitted as dust emission peaking at
-rest-frame far-infrared (FIR) wavelengths \citep{blain02a}.
-In the past $\sim$\,5~years, considerable amounts of effort have been invested into follow-up observations of SMGs that were
-discovered in large sky surveys \citep[\eg H-ATLAS, SPT, HerMES; ][]{Eales10a,Carlstrom11a,Oliver12a}, conducted using (sub)-mm facilities.
-These detailed studies have led to growing consensus that SMGs are a population of high-redshift galaxies that are extremely dusty, gas-rich,
-  and luminous ($\gtrsim$ 10$^{12}$ \Lsun) at the infrared wavebands, with high star formation rates \citep[$\gtrsim $ 500 \Msun yr\pmOne; see \eg reviews by][]{Lagache05a,Casey14a}.
+{\bf Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1\,--\,3 \citep{Chapman05a}, during the epoch of stellar mass and
+galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}. This galaxy population was first detected 
+$\sim$18 years ago with the Submillimeter Common User Bolometer Array (SCUBA) on the James
+Clerk Maxwell Telescope (JCMT; \citealt{Smail97a, Hughes98a, Barger98a}). 
+Previous works %following this discovery
+have shown that SMGs
+ are extremely luminous in the infrared
+ wavelengths (L$_\textrm{IR} \sim$ 10$^{12}$ \Lsun) with high star formation rates (SFR) \citep[$\gtrsim $ 500 \Msun yr\pmOne; see \eg reviews by][]{Lagache05a,Casey14a}.
+Following this pioneering work, considerable amounts of efforts have been invested into
+obtaining large samples of SMGs by carrying out
+  large sky surveys with (sub)-mm facilities such as the {\it Herschel Space Observatory} \citep[\eg H-ATLAS, SPT, HerMES; ][]{Eales10a,Carlstrom11a,Oliver12a}.  
+  }
 
-  To characterize the physical properties of the gas reservoirs in the interstellar medium (ISM) where active star formation takes place, carbon monoxide ($^{12}$CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[see \eg reviews by][]{Solomon05a,Carilli13a}.
-Recent observations of CO in SMGs at $z$\,$\sim$\,1\,--\,3 have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Riechers11c,Riechers11d,Ivison11a,Bothwell13a}.
+  To characterize the physical properties of the gas reservoirs in the interstellar medium (ISM) where active star formation takes place, carbon monoxide ($^{12}$CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[see \eg reviews by][]{Solomon05a,Carilli13a}.{ \bf Observations of CO in SMGs
+  %at $z$\,$\sim$\,1\,--\,3 
+  have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Frayer98a, Riechers11c, Neri03a, Riechers11d,Ivison11a,Bothwell13a}.}
 
@@
 Class II \citep*[FR-II; ][]{Fanaroff74} radio galaxy 3C220.3 and its
-companion galaxy B at $z$\,=\,0.685.
+companion galaxy B at $z$\,=\,0.685{\bf, where this companion galaxy is identified by \citeauthor{Haas14} (2014; hereafter H14) via observations with the Keck II Observatory and the {\it Hubble Space Telescope}.}
 SMM\,J0939 is currently one of the brightest known lensed
 SMGs, with a lensing-magnified flux density of $S_\textrm{250\micron}$\,=\,440\,$\pm$\,15 mJy.
-Previous detections of C~{\scriptsize\sc IV}~1459\AA\
+{\bf Previous detections of C~{\scriptsize\sc IV}~1459\AA\
  and He~{\scriptsize\sc II}~1640\AA\ line emission toward SMM\,J0939
- placed the redshift of this galaxy at $z$\,=\,2.221, and suggested the presence of an active galactic nucleus (AGN) in the form of a type-2 quasar in this SMG \citep[hereafter H14]{Haas14}.
+ placed the redshift of this galaxy at $z$\,=\,2.221.
+Based on the line fluxes and spectral line widths of these AGN lines, H14 suggested the presence of an active galactic nucleus (AGN) in the form of a type-2 quasar in this SMG.}
 
@@
 The correlator was configured to provide an effective bandwidth of 3.708 GHz in each sideband, and a spectral resolution of 5.208 MHz ($\sim$\,14.5 km\,\,s\pmOne).
-% each sideband 8 windows * 0.494792 GHz = 3.9583 before flagging edge channels
-% DR said take out edge channels, since the subbands overlap, and the usable bandwidth is 8 * (95 - 6) * 5.208 
 The line was placed in the
-upper sideband, with the local oscillator tuned to $\nu_\textrm{LO}$\,$\sim$\,104.2609 GHz. % restructure
+upper sideband, with the local oscillator tuned to $\nu_\textrm{LO}$\,$\sim$\,104.2609 GHz.
 Observations were carried out under good
@@
 averaging over all line-free channels; this yields a synthesized clean beam of 12\farcs0\,$\times$\,6\farcs5, $-$55.9$\degr$ east of north, and an rms noise of $\sigma_\textrm{cont}$ = 0.50\,\,mJy\,\,beam\pmOne\ over 6.8 GHz.
-%7416.192 MHz = (total(1520) - edge * 2 * nwin(16))*5.208 MHz 
-%7416.192 - [FWZI linechannel (55) * (2 * 5.208MHz)] = 6843.312
+
 \section{Results}\label{sec:res}
-%\subsection{New Results: Continuum Emission}
-\subsection{New Results: 3C220.3}
+\subsection{Foreground Galaxy: 3C220.3}
 Averaging over all line-free channels, we detect continuum emission at $\sim$\,9$\sigma$ significance at an averaged frequency of $\nu_\textrm{cont}$\,=\,104.2106 GHz ($\sim$\,2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$\,1.7 mm) at $z$\,=\,0.685.
@@
 \centering
-\includegraphics[width=0.80\textwidth]{Figure/ContPanel_cmyk.eps}
+\includegraphics[width=0.80\textwidth]{f1.eps}
 \caption{Left: Contour map of the 104 GHz continuum emission in the foreground radio galaxy 3C220.3.
-%The contour levels start at $\pm$2$\sigma$, where $\sigma$ = 0.5 mJy beam\pmOne, and
-%increment at steps of $\pm$2$\sigma$.
 The beam size is 12\farcs0\,$\times$\,6\farcs5, at P.A.\,=\,
@@
 emission start at $\pm$4$\sigma$, where $\sigma$\,=\,0.064 mJy beam\pmOne, and increment at steps of $\pm$2$^n\sigma$,
-where $n$ is a positive integer.
-The central cross on each image indicates the position of the radio core of 3C220.3. \label{fig:cont}}
+where $n$ is a positive integer.{\bf The white crosses correspond to the centroid locations of the lensing knots detected in the SMA 1\,mm continuum emission (see Figure \ref{fig:mom0}).}
+The central cross on each panel indicates the position of the radio core of 3C220.3. \label{fig:cont}}
 \end{figure*}
-%\subsection{New Results: \CO Line Emission}
-\subsection{New Results: SMM\,J0939\\ \CO Line Emission}
+\subsection{Background Galaxy: SMM\,J0939}
 We detect \CO line emission at $\sim$\,8$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{Figure/LinePanel_cmyk.eps}
-\includegraphics[width=0.65\textwidth]{Figure/smmj0939-co32_spec.eps}
+\includegraphics[width=0.8\textwidth]{f2.eps}
+\includegraphics[width=0.65\textwidth]{f3.eps}
 \caption{Top Left: Continuum-subtracted moment-0 map of \CO line emission toward
@@
 \subsection{Lens Modelling} \label{sec:Lens}
-To study the intrinsic properties of the background galaxy, we determine the magnification factor by performing
+To study the intrinsic properties of the background galaxy, we determine the magnification factor {\bf and the half-light radius of the dust region} by performing
 lens modeling on the SMA 1\,mm continuum data presented by H14 of this system. Lens modeling is carried out in the visibility
-({\it uv-}) plane using an updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}\footnote{\url{https://github.com/sbussmann/uvmcmcfit}}
-\citep{Bussmann15a}. The code uses an affine-invariant Markov chain Monte Carlo (MCMC) approach to sample the posterior
-probability density function (PDF) of the model parameters. In the code, the surface mass densities of both
-lenses are represented by singular isothermal ellipsoid (SIE) profiles, and the source is assumed to have an
-elliptical Gaussian profile. The code does not include an external shear parameter.
+({\it uv-}) plane using an updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}\footnote{\url{https://github.com/sbussmann/uvmcmcfit}}, details of the parametric lens model can be found in \citet{Bussmann15a}.
+%In the code, the surface mass densities of both
+%lenses are represented by singular isothermal ellipsoid (SIE) profiles, and the source is assumed to have an
+%elliptical Gaussian profile.
 
-We fix the phase center to coordinates ($\alpha$,\,$\delta$)\,\,(J2000) = (9$^{\rm h}$39$^{\rm m}$23\fs54,\,\,83\degr15\arcmin26\farcs10), where the
-angular offsets of the lenses and source are referenced to this position. The primary lens (3C220.3) is
-described by five free parameters: the angular offset ($\Delta \alpha_{\rm
-lens0}$ and $\Delta \delta_\textrm{lens0}$) relative to
-the chosen phase center ($\alpha$,\,$\delta$) in the image, the angular Einstein radius ($\theta_\textrm{E0}$), the
-axial ratio ($q_\textrm{lens0}$), and the position angle ($\phi_\textrm{lens0}$). The secondary lens (companion B) is
-described by three free parameters: $\theta_\textrm{E1}$, $q_\textrm{lens1}$, and $\phi_\textrm{lens1}$. The angular offset
-of the secondary
-lens is sampled with respect to that of
-the primary lens ($\Delta \alpha_\textrm{lens0}$ and $\Delta \delta_\textrm{lens0}$); we therefore do not consider ($\Delta \alpha_\textrm{lens1}$ and $\Delta \delta_\textrm{lens1}$)  as free parameters.
-The source (SMM\,J0939) is parameterized by
-six parameters: the position of the source relative to the
-primary lens ($\Delta \alpha_\textrm{s}$ and $\Delta
-\delta_\textrm{s}$), the total intrinsic flux density ($S_\nu$), the
-effective radius ($r_\textrm{s}\,=\,\sqrt{a_\textrm{s} b_\textrm{s}}$), the axial
-ratio ($q_\textrm{s}$\,=\, $b_\textrm{s}/a_\textrm{s}$), and the position angle
-($\phi_\textrm{s}$).
-%The total number of free parameters is $N_\textrm{free}$\,=\,14. 
-The best-fit model is obtained by maximizing the
-Gaussian likelihood function $ \mathcal{L} $ according to:
-\begin{equation}
-    \mathcal{L}\,=\,\sum_{u, v}\left( \frac{|V_\textrm{data} - V_{\rm
-    model}|^2}{\sigma^2} + {\rm log}(2 \pi \sigma^2) \right)
-\end{equation}
-\noindent where $\sigma$ is determined from the scatter in the visibilities within a
-single spectral window (``natural" weighting).
+%We fix the phase center to coordinates ($\alpha$,\,$\delta$)\,\,(J2000) = (9$^{\rm h}$39$^{\rm m}$23\fs54,\,\,83\degr15\arcmin26\farcs10), where the
+%angular offsets of the lenses and source are referenced to this position. The primary lens (3C220.3) is
+%described by five free parameters: the angular offset ($\Delta \alpha_{\rm
+%lens0}$ and $\Delta \delta_\textrm{lens0}$) relative to
+%the chosen phase center ($\alpha$,\,$\delta$) in the image, the angular Einstein radius ($\theta_\textrm{E0}$), the
+%axial ratio ($q_\textrm{lens0}$), and the position angle ($\phi_\textrm{lens0}$). The secondary lens (companion B) is
+%described by three free parameters: $\theta_\textrm{E1}$, $q_\textrm{lens1}$, and $\phi_\textrm{lens1}$. The angular offset
+%of the secondary
+%lens is sampled with respect to that of
+%the primary lens ($\Delta \alpha_\textrm{lens0}$ and $\Delta \delta_\textrm{lens0}$); we therefore do not consider ($\Delta \alpha_\textrm{lens1}$ and $\Delta \delta_\textrm{lens1}$)  as free parameters.
+%The source (SMM\,J0939) is parameterized by
+%six parameters: the position of the source relative to the
+%primary lens ($\Delta \alpha_\textrm{s}$ and $\Delta
+%\delta_\textrm{s}$), the total intrinsic flux density ($S_\nu$), the
+%effective radius ($r_\textrm{s}\,=\,\sqrt{a_\textrm{s} b_\textrm{s}}$), the axial
+%ratio ($q_\textrm{s}$\,=\, $b_\textrm{s}/a_\textrm{s}$), and the position angle
+%($\phi_\textrm{s}$).The axial ratios of the lenses are restricted to $q_\textrm{lens} > 0.3$. 
+%The best-fit model is obtained by maximizing the
+%Gaussian likelihood function $ \mathcal{L} $ of the interferometric data in the Fourier domain.
+%We initialize 512
+%walkers and 6000 steps to identify the best-fit model parameters.
 
-We initialize the positions and Einstein radii of both lenses, and the position of the source using those
- from the best-fit lens model performed on Keck K-band (near-infrared) data (H14). For each of
-these parameters, we impose a uniform prior in the range $\in\pm$3$\sigma$, where $\sigma$ is the uncertainty
-reported in their paper. The axial ratios of the lenses are restricted to $q_\textrm{lens} > 0.3$. We initialize 512
-walkers and 6000 steps to identify the best-fit model parameters.
+%We initialize the positions and Einstein radii of both lenses, and the position of the source using those
+ %from the best-fit lens model performed on Keck K-band (near-infrared) data (H14). For each of
+%these parameters, we impose a uniform prior in the range $\in\pm$3$\sigma$, where $\sigma$ is the uncertainty
+%reported in their paper. 
 \begin{figure}[!tbpH]
 \centering
-\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_model_goodfit1970_cmyk.eps}
-\includegraphics[width=0.232\textwidth]{Figure/LensedSBmap_residual_goodfit1970_cmyk.eps}
+\includegraphics[width=0.232\textwidth]{f4.eps}
+\includegraphics[width=0.232\textwidth]{f5.eps}
 \caption{Double-lens modeling of SMM\,J0939 using {\sc uvmcmcfit} on the SMA 1\,mm continuum data.
 The contours start at $\pm$2$\sigma$, incrementing at
-steps of $\pm$2$\sqrt{\rm 2}\sigma$.
+steps of $\pm$2$\sqrt{\rm 2}\sigma$ in both panels.
 Left: SMA 1\,mm continuum (red contours) overlaid on the best-fit model (grayscale image), assuming an elliptical Gaussian profile for the background SMG.
-The lenses are represented as black dots, the half-light area of the background source is represented as magenta ellipse, and the critical curves are represented as orange curves.
+The lenses are represented as black dots, the half-light area of the background source is represented as magenta ellipse, {\bf and the critical curves are represented as green curves.}
 Right: Residual contours and image obtained by taking the Fourier transform of the difference between the SMA data and the best-fit model in the visibility plane.
@@
 image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
-Our best-fit model yields a magnification
-factor of $\mu_\textrm{L}$ = 10.13\,$\pm$\,1.38, this is consistent the value reported by H14 within the errors. All best-fit
-parameters are listed in Table~\ref{tab:lensParam}.
-The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1\farcs22\,$\pm$\,0\farcs01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0\farcs75\,$\pm$\,0\farcs02 (5.34\,\,kpc at $z$\,=\,0.685), and
-the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
+{\bf  Our best-fit model yields a magnification
+factor of $\mu_\textrm{L}$ = 10.13\,$\pm$\,1.38
+%, this is consistent the value reported by H14 within the errors. 
+and a half-light radius of 0\farcs11 $\pm$ 0\farcs03, corresponding to a spatial extent of $\sim$0.9 kpc.} 
+All best-fit
+parameters are listed in Table~\ref{tab:lensParam}. {\bf DR: Note changes to Tab 1}
+%The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1\farcs22\,$\pm$\,0\farcs01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0\farcs75\,$\pm$\,0\farcs02 (5.34\,\,kpc at $z$\,=\,0.685), and
+%the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
 \input{table_lensParams}
@@
 \centering
-\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED2_cmyk.eps}
+\includegraphics[width=0.5\textwidth]{f6.pdf}
 \caption{SEDs of 3C220.3 (solid purple line) and SMM\,J0939 (dashed purple line and solid cyan line) including the new measurements presented in this paper.
@@
 where $T$ is the rest-frame cold dust temperature, $\beta$ is the dust emissivity index 
-%(equivalently, the spectral index of the dust extinction curve)
 , and $\alpha$ is the mid-infrared power law spectral index. The overall fit is normalized using the observed-frame 500
@@
 ^{12}$\,\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64\,\,m$^2$\,\,kg\pmOne\ at 125.0\,\,$
-\micron$ \citep{Dunne03a}, we derive the dust mass using the following expression:
-\begin{equation}
-M_\textrm{dust}\,=\,S_{\nu} D_{L}^2 [(1 + z) \kappa_{\nu} B_{\nu}]^{-1} \tau_{\nu} [1-
-\exp(-\tau_{\nu})]^{-1}
-\end{equation}
-where $S_{\nu}$ is the flux density in erg\,s\pmOne\,cm$^{-2}$\,Hz\pmOne, $D_\textrm{L}$ is the luminosity distance in cm, $\kappa_{\nu}$ is the dust
-absorption coefficient in cm$^2$\,g\pmOne, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function in units of erg\,s\pmOne\,cm$^{-2}$\,Hz\pmOne\,sr\pmOne;
-all quantities are expressed in the observed-frame.
-We find a dust mass of $M_\textrm{dust}$ = 50.5$^{20.4}_{-20.2}\times$10$^8$\,\,\Msun, the uncertainties do not include those in the dust absorption coefficient ($\kappa_{\nu}$).
+\micron$ \citep{Dunne03a}, we find a dust mass of $M_\textrm{dust}$ = 50.5$^{20.4}_{-20.2}\times$10$^8$\,\,\Msun{\bf ;} the uncertainties do not include those in the dust absorption coefficient ($\kappa_{\nu}$).
 These properties are derived based on the SED fitting to the photometric data, \ie prior
-to lensing correction.
+to lensing correction.{\bf We note that the dust mass is weakly constrained owing to the dearth of data in the {\bf rest-frame} FIR waveband.
+As such, we investigate how the dust mass would be affected by fitting an additional optically thick model with an upper limit of
+ $\beta$ adjusted from 2.2 to 3.0.
+While the difference in each best-fit parameter between this scenario and the previous model (an upper limit of $\beta$ = 2.2) is within 3\%, we find that the dust mass inferred from the posterior probability distribution of this SED model is boosted by a factor of $\sim$\,2.}
+\subsection{Physical Properties of the ISM in SMM\,J0939}
 
-With the limited amount of data in the FIR waveband, the dust mass is weakly constrained.
-We perform an additional fit using an optically thick model where we loosen the upper limit of $\beta$ from 2.2 to 3.0; while the difference between each of all best-fit parameters in this scenario and that using an upper limit of 2.2 is within 3\%, we find that the dust mass is boosted by a factor of $\sim$\,2.
-\subsection{Physical Properties of the ISM in SMM\,J0939}
-\subsubsection{Molecular Gas Mass}
+\subsubsection{Molecular Gas Mass} \label{sec:gas}
 While the ground state CO transition line traces the cold molecular gas in the ISM
 \citep*[\eg][]{Wilson70a,Downes98a}, transition lines of higher rotational states ($J$ $>$ 1) are frequently observed in high-redshift sources as the
- ground state transition line is redshifted to lower frequencies that can only be observed with tranditional radio telescopes
+ ground state transition line is redshifted to lower frequencies that can only be observed with traditional radio telescopes
  \citep{Carilli13a}. Consequently, assumptions on the CO excitation conditions are required to derive the molecular gas mass using the $M$(H$_\textrm{2}$)-to-$L^{\prime}_\textrm{CO}$
  conversion factor ($\alpha_\mathrm{CO}$) when extrapolating from higher-$J$ CO lines. \par
-Prior to observations of the ground state CO transition line in SMGs, it had been assumed that the molecular gas in the
-  ISM traceable by CO lines was thermalized owing to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
-   Yet, recent observations of this line have demonstrated that SMGs can indeed be subthermally excited
-   \citep{Harris10a,Riechers11c,Riechers11d,Ivison11a}. Namely, observational results of SMGs with both \CO and CO($J$\,=\,1\,\rarr\,0) line measurements have shown that the
-   brightness temperature ratio is more commonly found to be $R_\textrm{31}<$ 0.8 \citep
-   {Harris10a,Carilli10a,Swinbank2010a,Ivison10d,Ivison11a,Riechers11d}. In contrast, similar observations in high-redshift quasar hosts suggest that the ratio
+%Prior to observations of the ground state CO transition line in SMGs, it had been assumed that the molecular gas in the
+%  ISM traceable by CO lines was thermalized owing to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
+{\bf Recent observations of the ground state CO transition line in SMGs have demonstrated that these galaxies can be sub-thermally excited regardless of their high SFRs
+   \citep{Harris10a,Riechers11c,Riechers11d,Ivison11a}. 
+ Moreover, observational results of SMGs with both \CO and CO($J$\,=\,1\,\rarr\,0) line measurements have shown that the
+   brightness temperature ratio is commonly found to be $R_\textrm{31}<$ 0.8 \citep
+   {Harris10a,Carilli10a,Swinbank2010a,Ivison10d,Ivison11a,Riechers11d}.} In contrast, similar observations in high-redshift quasar hosts suggest that the ratio
    is $R_\textrm{31}$\,$\sim$\,1 \citep{Riechers06a, Riechers11a}.
@@
 \par
-Here, we derive the molecular gas mass
-assuming thermalized excitation of CO,
-\ie we adopt $R_\textrm{31}$\,=\,1, as SMM\,J0939 is
-postulated to be hosting a type-2 quasar (H14).
+{\bf Here, we derive the molecular gas mass
+assuming thermalized excitation of CO, as SMM\,J0939 is
+postulated to be hosting a type-2 quasar (H14).}
 We calculate the CO($J$\,=\,1\rarr\,0) line luminosity using a standard relation
-\citep[\eg][]{Solomon05a,Carilli13a}:
-\begin{equation}
-L^{\prime}_\textrm{CO}\,=\,\frac{3.25\times10^7}{\nu_\textrm{CO(3-2)}^2}\times \frac{D_{\rm L}^2}{\mu_\textrm{L}} \times
-\frac{I_\textrm{CO(3-2)}} {R_\textrm{31} (1 + z)}
-\end{equation}
-where $\nu_\textrm{CO(3-2)}$ is the rest-frame frequency of the \CO transition line in GHz, $D_{\rm L}$ is the luminosity distance in Mpc, $\mu_\textrm{L}$ is the lensing magnification factor, and $I_\textrm{CO(3-2)}$ is the \CO line flux in Jy\,\,km\,\,s\pmOne.
-This corresponds to \Lp = (3.42\,$\pm$\,0.71)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU, hence the inferred total molecular gas mass is $M_\textrm{gas}$ = (2.74\,$\pm$\,0.57)\,$\times$\,\,10$^{10}$\,\Msun\, after correcting for lensing magnification.
+\citep[\eg][]{Solomon05a}.
+This corresponds to \Lp = (3.42\,$\pm$\,0.71)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU; hence the inferred total molecular gas mass is $M_\textrm{gas}$ = (2.74\,$\pm$\,0.57)\,$\times$\,\,10$^{10}$\,\Msun\, after correcting for lensing magnification.
 We assumed a conversion factor of $\alpha_\textrm{CO}$ = 0.8\,\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
@@
 ratio of $f_\textrm{gas-dust}$\,=\,$M_\textrm{gas}/M_\textrm{dust}$\,=\,55\,$\pm$\,24. 
-We note that as outlined in the previous section, a factor of $\sim$\,2 uncertainty arises from the dust mass estimate.
-The derived gas-to-dust ratio is in good agreement, within the uncertainties,
- with the
+%We note that as outlined in the previous section, a factor of $\sim$\,2 uncertainty arises from the dust mass estimate. 
+This is in good agreement  with the
 values found in other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.
 
-\subsubsection{Star Formation Rate}
-%No strong evidence of a hot dust bump is found in SMM\,J0939 based on the mid-IR (WAIT, BUT ONLY HAVE 70 micron onwards) continuum measurements (see Figure~\ref{fig:SED}), hence
-We derive the star formation rate (SFR) assuming that the dominant IR heating source is due to young and massive stars, and ignoring a contribution from the
+\subsubsection{{\bf Star Formation Rate \& Star Formation Efficiency}}
+We derive the {\bf SFR} assuming that the dominant IR heating source is due to young and massive stars, and ignoring a contribution from the
 dust-enshrouded AGN.
@@
 
-\subsubsection{Star Formation Efficiency}
+%\subsubsection{Star Formation Efficiency}
 The SFR per unit mass of molecular gas is commonly taken as a
-measure of the star formation efficiency, SFE\,=\,SFR/$M_\textrm{gas}$. We compute this ratio using the IR
-luminosity and CO luminosity assuming the same lensing magnification for both quantities, SFE\,=\,$L_\textrm{IR}$/\Lp.
-The derived SFE is therefore independent of the magnification factor, the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$), and of the
-IMF. This, however, assumes that differential lensing between the CO and infrared emission is negligible.
+measure of the star formation efficiency. 
+{\bf We compute this ratio using the IR
+and CO luminosities ($L_\textrm{IR}$/\Lp). The derived SFE is therefore independent of the magnification factor, the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$), and the
+IMF. }This, however, assumes that differential lensing between the {\bf CO and IR} emission is negligible.
 The resulting ratio is SFE$_\textrm{IR}$\,=\,256\,$\pm$\,41\,\,\Lsun\,(\LpU)$^{-1}$, this is comparable
@@
 Based on our \CO line measurement, we estimate the dynamical mass of SMM\,J0939 assuming that the molecular gas is virialized.
-With this assumption, we use an isotropic virial estimator \citep[\eg][]{Engel10a}:
-\begin{equation}
-M_\textrm{dyn}\,=\,2.8\times 10^5\Delta v_\textrm{line}^ 2 R_\textrm{eff}
-\end{equation}
-where $\Delta v_\textrm{line}$ is in km\,\,s\pmOne, $R_\textrm{eff}$ is in kpc, and $M_\textrm{dyn}$ is in \Msun.
-We employ the FWHM of the \CO line profile for $\Delta v_\textrm{line}$,
-and the half-light radius from our lens model for $R_\textrm{eff}$, assuming that the dust emission traces the same emitting region as the CO.
-We note that a derived dynamical mass based on this assumption is likely to be biased towards low values, as the CO-emitting region can be spatially more extended than the dust emitting region due to the low dust optical depth at larger radii \citep[\eg][]{Tacconi06a, Riechers11c,Riechers11d,Ivison11a}.
-% 
+With this assumption, we use an isotropic virial estimator \citep[\eg][]{Engel10a}, with the FWHM of the \CO line profile and the half-light radius from our lens model for $R_\textrm{eff}$, assuming that the dust emission traces the same emitting region as the CO.
 We find a dynamical mass of $M_\textrm{dyn}$ = (7.84\,$\pm$\,2.84)\,$\times$\,10$^{10}$\,\Msun, and a gas-to-dynamical mass fraction of $f_\textrm{gas-to-dyn}$ = 0.35\,$\pm$\,0.14, consistent with those of other SMGs \citep{Tacconi06a}.
+We note that a derived dynamical mass based on this assumption is likely to be biased towards low values, as the CO-emitting region {\bf that traces the cool gas} can be spatially more extended than the dust emitting region due to the low dust optical depth at larger radii \citep[\eg][]{Tacconi06a, Riechers11c,Riechers11d,Ivison11a}.
+{\bf In particular, \citet{Tacconi06a} report a median FWHM size of 4.1\,$\pm$\,1.6 kpc based on \CO measurements and 
+the small sample of SMGs with spatially resolved \rot{1}{0} observations show that the cool gas are even more extended \citep{Ivison11a, Riechers11c, Hodge13a}.
+For dust-emitting region, \citet{Simpson15a} report a spatial extent of 2.4 kpc in a sample of 52 SMGs.
+% Adopting a physical size of 4.1 kpc, we find a dynamical mass of 3.7\,$\times$\,10$^{11}$\,\Msun.
+ }
 
 \subsubsection{Star Formation and Gas Surface Densities}
-To compute surface densities, we divide half the inferred SFR and gas mass by the area subtended by the half-light
-radius, resulting in $\Sigma_\textrm{gas}$ = 5.48\,$\times$\,10$^9$ \Msun~kpc$^{-2}$ and $\Sigma_\textrm{SF}$ = 175.20 \Msun~yr\pmOne~kpc$^{-2}$, which are in good agreement with values typical for SMGs \citep{Tacconi08a}.
+{\bf We compute the surface densities by dividing half the SFR and gas mass by the area subtended by the half-light
+radius \citep[\eg][]{Genzel10a, Harrison15a}, yielding 
+%To compute surface densities, we divide half the inferred SFR and gas mass by the area subtended by the half-light
+%radius, resulting in 
+$\Sigma_\textrm{SF}$ = 175.20 \Msun~yr\pmOne~kpc$^{-2}$ and $\Sigma_\textrm{gas}$ = 5.48\,$\times$\,10$^9$ \Msun~kpc$^{-2}$, respectively. 
+These results are in good agreement with values typical for SMGs \citep{Tacconi08a}. }
 The inferred surface densities of SMM\,J0939 follow a universal Schmidt-Kennicutt relation between the star formation rate
-surface density and the molecular gas surface density: $\Sigma_\textrm{SF}$ = 9.3 ($\pm$\,2)\,$\times$\,10$^{-5}$ ($M_\textrm{gas}$/2$\pi R_\textrm{1/2}^2)^{1.71(\pm\,0.05)}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
+surface density and the molecular gas surface density: $\Sigma_\textrm{SF}$\,=\,9.3\,($\pm$\,2)\,$\times$\,10$^{-5}$ ($M_\textrm{gas}$/2$\pi R_\textrm{1/2}^2)^{1.71(\pm\,0.05)}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
 galaxies
 out to $z$\,$\sim$\,2.5, and assuming a Chabrier IMF \citep{B07a}.
-%EDIT Hodge 15
+
 \section{Discussion And Conclusions}
@@
 which is consistent with the short timescales found in other SMGs \citep{Greve05a}.
-The derived intrinsic properties of SMM\,J0939 are evident of ongoing rapid star formation; this is in good agreement with the current conjecture that SMGs are a %stellar mass assembly in galaxies
+The derived intrinsic properties of SMM\,J0939 are evident of ongoing rapid star formation; this is in good agreement with the current conjecture that SMGs are a
 population of high-redshift galaxies that build up the bulk of stellar mass in present-day galaxies, thus play an important role
@@
 against those of eight CO-detected obscured AGNs at $z$ = 1.6\,$-$\,2.8, using the averaged values reported by \citet[][and references
-therein]{Polletta11a}. %P11 Mgas from the lowest CO line, but cited 4-3 line width and intensity, etc in Table 2
-% some mysterious SFE 
+therein]{Polletta11a}. 
 Among these obscured type-2 quasars, F10214 has the lowest molecular gas mass as well as SFR.
@@
 
+ %%% EDIT %%%%
 We conclude this paper by noting that SMM\,J0939 is a faithful representation of both high-redshift type-2 quasars and SMGs,
-based on the excellent agreement found between their properties. In this remarkable lensing system, the background galaxy --- SMM\,J0939 is
-breaking up its dust cocoon (H14) while undergoing prodigious star-formation activity (SFR\,$\sim$\,874 \Msun~yr\pmOne).
-This scenario is consistent with the proposed evolutionary phase model \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}, whereby SMM\,J0939 is transitioning from its star-bursting phase to the unobscured quasar phase.
+based on the excellent agreement found between their {\bf gas and dust} properties (see \S~\ref{sec:SEDBg} and \S~\ref{sec:gas}).
+{\bf In the evolutionary BLAH BLAH}
+This is supportive of the proposed evolutionary phase model \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}, whereby SMM\,J0939 is transitioning from its star-bursting phase to the unobscured quasar phase.
 
-\acknowledgments
+\begin{acknowledgments}
 We thank Shane Bussmann for providing the code {\sc uvmcmcfit} for lens modeling, sharing the SMA and VLA data, and for helpful discussions; Alex Conley for providing the code {\sc mbb\_emcee} for SED fitting.
-%We acknowledge the WENSS team for providing the radio measurements for 3C220.3.
 Support for CARMA construction was derived from the
@@
 
-Facilities: \facility{CARMA}
+Facilities: CARMA
+\end{acknowledgments}
 
@@
 \bibliography{J0939}
-%\begin{thebibliography}{}
+
+%\begin{thebibliography}
+
 %\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
@@
 %{Carilli}, C.~L., {Daddi}, E., {Riechers}, D., {et~al.} 2010, \apj, 714, 1407
+%
+%\bibitem[{{Carlstrom} {et~al.}(2011){Carlstrom}, {Ade}, {Aird}, {Benson},
+%  {Bleem}, {Busetti}, {Chang}, {Chauvin}, {Cho}, {Crawford}, {Crites}, {Dobbs},
+%  {Halverson}, {Heimsath}, {Holzapfel}, {Hrubes}, {Joy}, {Keisler}, {Lanting},
+%  {Lee}, {Leitch}, {Leong}, {Lu}, {Lueker}, {Luong-van}, {McMahon}, {Mehl},
+%  {Meyer}, {Mohr}, {Montroy}, {Padin}, {Plagge}, {Pryke}, {Ruhl}, {Schaffer},
+%  {Schwan}, {Shirokoff}, {Spieler}, {Staniszewski}, {Stark}, {Tucker},
+%  {Vanderlinde}, {Vieira}, \& {Williamson}}]{Carlstrom11a}
+%{Carlstrom}, J.~E., {Ade}, P.~A.~R., {Aird}, K.~A., {et~al.} 2011, \pasp, 123,
+%  568
 %  
@@
 %
-%%\bibitem[{{Tacconi} {et~al.}(2010){Tacconi}, {Genzel}, {Neri}, {Cox}, {Cooper},
-%%  {Shapiro}, {Bolatto}, {Bouch{\'e}}, {Bournaud}, {Burkert}, {Combes},
-%%  {Comerford}, {Davis}, {Schreiber}, {Garcia-Burillo}, {Gracia-Carpio}, {Lutz},
-%%  {Naab}, {Omont}, {Shapley}, {Sternberg}, \& {Weiner}}]{Tacconi10a}
-%%{Tacconi}, L.~J., {Genzel}, R., {Neri}, R., {et~al.} 2010, \nat, 463, 781
+%\bibitem[{{Tacconi} {et~al.}(2010){Tacconi}, {Genzel}, {Neri}, {Cox}, {Cooper},
+%  {Shapiro}, {Bolatto}, {Bouch{\'e}}, {Bournaud}, {Burkert}, {Combes},
+%  {Comerford}, {Davis}, {Schreiber}, {Garcia-Burillo}, {Gracia-Carpio}, {Lutz},
+%  {Naab}, {Omont}, {Shapley}, {Sternberg}, \& {Weiner}}]{Tacconi10a}
+%{Tacconi}, L.~J., {Genzel}, R., {Neri}, R., {et~al.} 2010, \nat, 463, 781
 %
@@
 %{Wilson}, R.~W., {Jefferts}, K.~B., \& {Penzias}, A.~A. 1970, \apjl, 161, L43
-%
+
 %\end{thebibliography}
@@
 parameter of the best-fit solution between these two scenarios is less than 3\%, except for the dust mass, which is boosted by a factor of $\sim$\,2. This is
-unsurprising given the dearth of data in the FIR wavebands, leading to a weakly constrained emissivity, and thus, inferred dust mass.
+unsurprising given the dearth of data in the {\bf rest-frame FIR wavebands}, leading to a weakly constrained emissivity, and thus, inferred dust mass.
 In our analysis, we employ the best-fit parameters and the corresponding inferred properties (dust mass, and IR luminosity) from the former, where a tighter constraint is imposed on $\beta$.
-
-%Mdust highly dependent on T in shorter wavelengths,
-%Mdust uncorrelated with LIR
-% Beta has insignificant effect on LIR
 
@@
 \hspace{-1.1cm}
-\includegraphics[width=0.55\textwidth]{Figure/CorrelationPlot__thick_500_500_cmyk.eps}
+\includegraphics[width=0.55\textwidth]{f7.eps}
 \hspace{-1cm}
-\includegraphics[width=0.55\textwidth]{Figure/CorrelationPlot__thin_testSMA_cmyk}
+\includegraphics[width=0.55\textwidth]{f8.pdf}
 \hspace{-1.1cm}

### 2015-12-07 Code/NumCrunching.py

@@ -341,6 +341,7 @@ class prettyGalaxies:
             half light radius ["], major axis of line (resolved)
         """
         r_kpc = cosmo.kpc_proper_per_arcmin(self.z).value * (self.R_halflight/60.)
+        print(" Half light radius: {:.2f} kpc").format(r_kpc)
         self.M_dyn = 2.8e5 * (self.FWHM_Line) ** 2 * r_kpc
         return self.M_dyn
 

### 2015-12-07 mod1/response.txt
write out some reponses in complete sentences.

@@
 We thank the referee for providing constructive comments to improve this manuscipt.
-We have addressed all the concerns raised by the referee and details can be found in the revised version.
-A brief description of how we have incoprated the changes can be found below.
+We have addressed all the concerns raised by the referee and details can be found in the revised version, please see attached.
+A brief description on how we incoprated the changes can be found below.
+=====================
 
 Major comments:
-
 - There is already a lensing model in H14 (a paper the authors refer to numerous times) and it is unclear why they redid the lensing model (they use the same SMA data as H14 but a different code).
@@
 These are all standard calculations and you can refer to CW14 for the equations rather than repeating them here.
-> we have removed standard equations.
-> combined SFE and SFR into one section, and trimmed a few sentences in ths section.
+> We removed standard equations from the manuscript, combined the sections reporting SFE and SFR into one, and trimmed a few sentences.
 
 - You should also summarize the evidence for the AGN in this SMG (maybe when you mention this in the intro) so the reader doesn't have to read H14.
-> We have restructured the intro, writing explicitly the evidence of AGN. 
->
+> We rephrased the introduction to show more clearly the evidence of an AGN.
 
 - [a further concern/question about Table 4 is whether all the same assumptions such as excitation, alpha_co, etc. were made for the other SMGs otherwise the comparisons are meaningless]
-> We added notes to these assumptions in the caption below Tab. 4.
+> We added notes in the caption below Table 4 to recap the assumptions used in deriving these quantities.
 =============================
@@
 Instead our SED model includes a power-law to the blue side of the dust peak, which accounts for the MIR excess and allows us to estimate the IR luminosity (Kirkpatrick+15, Riechers+13, Johnson+13, Casey+12).
+
 or should I change it to FIR --> SFR
@@
 
-Minor comments:
+# Minor comments:
+- the depletion time seems short compared to other SMGs which are ~100Myr although maybe it is consistent with other SMGs with AGN in them.
+> Taken into account one of the comments listed above, we added literature reference to Table 4, and the depletion time scale is consistent with other SMGs.
+> Greve05: 40-100 Myr
+
+============================
 **DONE**
@@
 For these reasons, we do not mean the covariance here.
-
-=================================
-
-- the depletion time seems short compared to other SMGs which are ~100Myr although maybe it is consistent with other SMGs with AGN in them.
-> Taken into account one of the comments listed above, we added literature reference to Table 4, and the depletion time scale is consistent with other SMGs.
-> Greve05: 40-100 Myr

### 2015-12-08 mod1/manuscript/ms.tex
replaced properties with FIR derived, combined SFR SFRSD sections; need to work on Tab.4 and conclusion

@@
 All best-fit
-parameters are listed in Table~\ref{tab:lensParam}. {\bf DR: Note changes to Tab 1}
+parameters are listed in Table~\ref{tab:lensParam}. {\bf DR: Please Note changes to Tab 1}
 %The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1\farcs22\,$\pm$\,0\farcs01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0\farcs75\,$\pm$\,0\farcs02 (5.34\,\,kpc at $z$\,=\,0.685), and
@@
  conversion factor ($\alpha_\mathrm{CO}$) when extrapolating from higher-$J$ CO lines. \par
-%Prior to observations of the ground state CO transition line in SMGs, it had been assumed that the molecular gas in the
-%  ISM traceable by CO lines was thermalized owing to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
 {\bf Recent observations of the ground state CO transition line in SMGs have demonstrated that these galaxies can be sub-thermally excited regardless of their high SFRs
@@
 ratio of $f_\textrm{gas-dust}$\,=\,$M_\textrm{gas}/M_\textrm{dust}$\,=\,55\,$\pm$\,24. 
-%We note that as outlined in the previous section, a factor of $\sim$\,2 uncertainty arises from the dust mass estimate. 
 This is in good agreement  with the
@@
 \subsubsection{{\bf Star Formation Rate \& Star Formation Efficiency}}
-We derive the {\bf SFR} assuming that the dominant IR heating source is due to young and massive stars, and ignoring a contribution from the
-dust-enshrouded AGN.
-Using the \citet{Kennicutt98a} relation and assuming a \citet{Chabrier03a}
-stellar initial mass (IMF) function\footnote{The SFR would be SFR$_\textrm{FIR}$\,=\,526\,$\pm$\,73 $M_
-\odot$ yr\pmOne\ if we were to use only the FIR luminosity.},
-we derive a SFR$_\textrm{IR}$ of 874\,$\pm$\,122 $\Msun$\,\,yr\pmOne, employing the lensing-corrected total IR luminosity.
+{\bf We derive the SFR using the lensing-corrected FIR luminosity assuming 
+that the dominant heating source of cold-dust is young and massive stars and ignoring a contribution from the
+dust-enshrouded AGN.}
+Using the \citet{Kennicutt98a} relation and {\bf adopting} a \citet{Chabrier03a}
+stellar initial mass (IMF) function, {\bf we find a
+SFR$_\textrm{FIR}$\,=\,526\,$\pm$\,73 $M_
+\odot$ yr\pmOne.}
 The starburst in SMM\,J0939 can be maintained at its
-current rate for a time that can be approximated by the gas depletion timescale, $\tau_\textrm{depl}$\,=\,$M_\textrm{gas}$/SFR.
-This corresponds to $\tau_\textrm{depl}$\,=\,31\,$\pm$\,5 Myr, which is in good agreement with those found in other SMGs \citep[\eg][]{Greve05a}.
+current rate for a time that can be approximated by the gas depletion timescale, $\tau_\textrm{depl}$\,=\,$M_\textrm{gas}$/SFR{\bf , which assumes no replenishment of gas and feedbacks.}
+This corresponds to {\bf $\tau_\textrm{depl}$\,=\,52\,$\pm$\,8 Myr}, which is in good agreement with those found in other SMGs \citep[\eg][]{Greve05a}.
 
-%\subsubsection{Star Formation Efficiency}
 The SFR per unit mass of molecular gas is commonly taken as a
 measure of the star formation efficiency. 
-{\bf We compute this ratio using the IR
-and CO luminosities ($L_\textrm{IR}$/\Lp). The derived SFE is therefore independent of the magnification factor, the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$), and the
-IMF. }This, however, assumes that differential lensing between the {\bf CO and IR} emission is negligible.
-The resulting ratio is SFE$_\textrm{IR}$\,=\,256\,$\pm$\,41\,\,\Lsun\,(\LpU)$^{-1}$, this is comparable
+{\bf We compute this ratio using the {\bf FIR}
+and CO luminosities {\bf ($L_\textrm{FIR}$/\Lp)}. The derived SFE is therefore independent of the magnification factor, the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$), and the
+IMF. }This, however, assumes that differential lensing between the {\bf CO and FIR} emission is negligible.
+The resulting ratio is {\bf SFE$_\textrm{FIR}$\,=\,154\,$\pm$\,25\,\,\Lsun\,(\LpU)$^{-1}$}, this is comparable
 to those found in ``typical" SMGs \citep{Greve05a,Tacconi06a,Riechers11c}.
+
+{\bf We compute the surface densities by dividing half the SFR and gas mass by the area subtended by the half-light
+radius \citep[\eg][]{Genzel10a, Harrison15a}, yielding 
+$\Sigma_\textrm{SF}$ = 106  \Msun~yr\pmOne~kpc$^{-2}$} and $\Sigma_\textrm{gas}$ = 5.48\,$\times$\,10$^9$ \Msun~kpc$^{-2}$, respectively. 
+These results are in good agreement with values typical for SMGs {\bf \citep{Tacconi06a, Hodge15a}. }  % compared using their conversion
+The inferred surface densities of SMM\,J0939 follow a universal Schmidt-Kennicutt relation between the star formation rate
+surface density and the molecular gas surface density: $\Sigma_\textrm{SF}$ = 9.3\,($\pm$\,2)\,$\times$\,10$^{-5}$ ($M_\textrm{gas}$/2$\pi R_\textrm{1/2}^2)^{1.71(\pm\,0.05)}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
+galaxies
+out to $z$\,$\sim$\,2.5, and assuming a Chabrier IMF \citep{B07a}.
 
@@
 We note that a derived dynamical mass based on this assumption is likely to be biased towards low values, as the CO-emitting region {\bf that traces the cool gas} can be spatially more extended than the dust emitting region due to the low dust optical depth at larger radii \citep[\eg][]{Tacconi06a, Riechers11c,Riechers11d,Ivison11a}.
-{\bf In particular, \citet{Tacconi06a} report a median FWHM size of 4.1\,$\pm$\,1.6 kpc based on \CO measurements and 
-the small sample of SMGs with spatially resolved \rot{1}{0} observations show that the cool gas are even more extended \citep{Ivison11a, Riechers11c, Hodge13a}.
-For dust-emitting region, \citet{Simpson15a} report a spatial extent of 2.4 kpc in a sample of 52 SMGs.
+{\bf This has been supported by recent observations.
+In particular, \citet{Tacconi06a} report a median FWHM size of 4.1\,$\pm$\,1.6 kpc based on \CO line measurements of their sample, whereas studies with spatially resolved \rot{1}{0} observations have additionally demonstrated that the cool gas regions are even more extended (R$_{\rm eff} \sim$ 7 kpc;  \citealt{Ivison11a}, see also \citealt{Riechers11c, Hodge13a}).
+For the physical size of dust-emitting regions, \citet{Simpson15a} recently report a spatial extent of 2.4 kpc in a sample of 52 SMGs.
 % Adopting a physical size of 4.1 kpc, we find a dynamical mass of 3.7\,$\times$\,10$^{11}$\,\Msun.
  }
-
-\subsubsection{Star Formation and Gas Surface Densities}
-{\bf We compute the surface densities by dividing half the SFR and gas mass by the area subtended by the half-light
-radius \citep[\eg][]{Genzel10a, Harrison15a}, yielding 
-%To compute surface densities, we divide half the inferred SFR and gas mass by the area subtended by the half-light
-%radius, resulting in 
-$\Sigma_\textrm{SF}$ = 175.20 \Msun~yr\pmOne~kpc$^{-2}$ and $\Sigma_\textrm{gas}$ = 5.48\,$\times$\,10$^9$ \Msun~kpc$^{-2}$, respectively. 
-These results are in good agreement with values typical for SMGs \citep{Tacconi08a}. }
-The inferred surface densities of SMM\,J0939 follow a universal Schmidt-Kennicutt relation between the star formation rate
-surface density and the molecular gas surface density: $\Sigma_\textrm{SF}$\,=\,9.3\,($\pm$\,2)\,$\times$\,10$^{-5}$ ($M_\textrm{gas}$/2$\pi R_\textrm{1/2}^2)^{1.71(\pm\,0.05)}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
-galaxies
-out to $z$\,$\sim$\,2.5, and assuming a Chabrier IMF \citep{B07a}.
 
@@
 implies a CO luminosity of \Lp\ = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU, suggesting the presence of a massive
-molecular gas reservoir that fuels the star formation activity taking place at a rate of $\sim$\,874 \Msun~yr\pmOne.
-If the star forming activity continues at the current rate, the gas reservoir will be depleted within $\lesssim$~31 Myr,
+molecular gas reservoir that fuels the star formation activity taking place at a rate of {\bf $\sim$\,526 \Msun~yr\pmOne}.
+If the star forming activity continues at the current rate, the gas reservoir will be depleted within {\bf $\lesssim$~52 Myr,}
 which is consistent with the short timescales found in other SMGs \citep{Greve05a}.
@@
 
-We investigate variations within the SMG population by comparing SMM\,J0939 with two other exceptionally submm-bright,
+{\bf We
+compare our findings for SMM\,J0939
+ with two other exceptionally submm-bright,}
 strongly-lensed SMGs
@@
 at 250\,\micron, while its CO line and IR luminosities are lower than those of most SMGs studied to date.
-This demonstrates
-the large variations in gas mass, dust mass, and star forming activity within the population at $z$\,$\sim$\,2$-$3, which is discernible with the aid of gravitational lensing.
+{\bf This demonstrates BLAH BLAH
+the large variations in gas mass, dust mass, and star forming activity within the population at $z$\,$\sim$\,2$-$3, which is discernible with the aid of gravitational lensing.}
 While lensing can probe sources
@@
  %%% EDIT %%%%
+BLAH BLAH
 We conclude this paper by noting that SMM\,J0939 is a faithful representation of both high-redshift type-2 quasars and SMGs,
 based on the excellent agreement found between their {\bf gas and dust} properties (see \S~\ref{sec:SEDBg} and \S~\ref{sec:gas}).
-{\bf In the evolutionary BLAH BLAH}
+{\bf In the proposed evolutionary paradigm, BLAH}
 This is supportive of the proposed evolutionary phase model \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}, whereby SMM\,J0939 is transitioning from its star-bursting phase to the unobscured quasar phase.

### 2015-12-08 Code/NumRun.py

@@ -10,21 +10,21 @@ SMG.M_gas()
 SFR_IR = SMG.SFRFunc(SMG.LIR)
 SFR_FIR = SMG.SFRFunc(SMG.LFIR)
 SFE_IR = SMG.SFEFunc(SMG.LIR)
-# SFE_FIR = SMG.SFEFunc(SMG.LFIR)
+SFE_FIR = SMG.SFEFunc(SMG.LFIR)
 t_IR = SMG.depleTime_Gas(SFR_IR)
-# t_FIR = SMG.depleTime_Gas(SFR_FIR)
+t_FIR = SMG.depleTime_Gas(SFR_FIR)
 # q_IR, Lradio = SMG.qFactor_normL(SMG.LIR)
 # q_FIR, Lradio = SMG.qFactor_normL(SMG.LFIR)
 gas_dust = SMG.f_gas_dust()
 M_dyn = SMG.Mdyn()
 f_gas_dyn = SMG.f_molGas_dyn()
 print SMG
-print "SFR using LIR: {:.2f} [M_sun/yr]".format(SFR_IR)
+# print "SFR using LIR: {:.2f} [M_sun/yr]".format(SFR_IR)
 print "SFR using LFIR: {:.2f} [M_sun/yr]".format(SFR_FIR)
-print "SFE using LIR: {:.2f}".format(SFE_IR)
-# print "SFE using LFIR: {:.2f}".format(SFE_FIR)
-print "depletion Time using IR {:.2f} Myr".format(t_IR/1e6)
-# print "Depletion Time using FIR {:.2f} Myr".format(t_FIR/1e6)
+# print "SFE using LIR: {:.2f}".format(SFE_IR)
+print "SFE using LFIR: {:.2f}".format(SFE_FIR)
+# print "depletion Time using IR {:.2f} Myr".format(t_IR/1e6)
+print "Depletion Time using FIR {:.2f} Myr".format(t_FIR/1e6)
 # print "rest frame 1.4 GHz Luminosity: {:.2f} [W/Hz]".format(Lradio)
 # print "q correlation using IR: {:.2f}".format(q_IR)
 # print "q correlation using FIR: {:.2f}".format(q_FIR)

### 2015-12-08 Code/err.py

@@ -19,8 +19,13 @@ sig_Mdust_noMu = 20.42e8
 M_dyn = 7.48e10
 Mgas = 2.28e10    # with lensing correction
 
-#####################
-#####################
+###############################################################
+#                           Equations
+###############################################################
+
+###############################################################
+#                           L'
+###############################################################
 sig_LprimeCO = (3.25e7 / freq_CO32 ** 2 * dl ** 2 / (1 + z)) * \
     ((del_I / mu) ** 2 + (del_mu / mu ** 2 * I_line) ** 2) ** (.5)
 del_LprimeCO = 3.25e7 / freq_CO32 ** 2 * dl ** 2 / \
@@ -32,6 +37,9 @@ del_LprimeCO_noMu = 3.25e7 / freq_CO32 ** 2 * dl ** 2 / (1 + z) * (del_I)
 LprimCO_noMu = 3.25e7 / freq_CO32 ** 2 * dl ** 2 / (1 + z) * I_line
 #print str(LprimCO_noMu/1.e10) + '+/-' + str(sig_LprimeCO_noMu / 1.e10)
 
+###############################################################
+#                           M gas
+###############################################################
 sig_Mgas = alpha * sig_LprimeCO
 del_Mgas = alpha * del_LprimeCO
 
@@ -39,19 +47,38 @@ Mgas_noMu = alpha * LprimCO_noMu
 sig_Mgas_noMu = alpha * sig_LprimeCO_noMu
 del_Mgas_noMu = alpha * del_LprimeCO_noMu
 
+
+###############################################################
 # With lensing correction, M_dust
+###############################################################
 sig_Mdust = (
     (M_dust / mu ** 2 * del_mu) ** 2 + (sig_Mdust_noMu / mu) ** 2) ** (.5)
 del_Mdust = M_dust / mu ** 2 * del_mu + sig_Mdust_noMu / mu
 
+###############################################################
 # with lensing correciton, LIR
+###############################################################
[…]

### 2015-12-08 mod1/manuscript/ms.tex
place Tab. 4 to the end of paper and rotate

@@
-\documentclass[iop]{emulateapj}
+\documentclass[iop, revtex4]{emulateapj}
 \usepackage[breaklinks,colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
@@
 \section{Discussion And Conclusions}
-\input{table_compareSMG}
 We present the detection of \CO line emission toward SMM\,J0939+8315, a strongly-lensed SMG that is hosting a type-2 quasar, refining the redshift
@@
 \bibliography{J0939}
+
+\clearpage
+%\begin{landscape}
+\begin{turnpage}
+\input{table_compareSMG}
+\clearpage
+%\end{landscape}
+\end{turnpage}
 

### 2015-12-08 mod1/response.txt
updated bibtex, correct err in SFR for type-2 QSO, clear some finsihed responses

@@
 > We moved the lens mass and consistent results into table 1 and its caption, and removed details of the lens model / shortened the section.
-However, we retained this section in this paper as we provide the best-fit parameters that were not reported in Haas14 and since we use the inferred half-light radius later in the analysis.
-
-- section 4.3 is way too wordy and can be cut down to a few paragraphs and a table summarizing these key values (already given in Table 4).
-These are all standard calculations and you can refer to CW14 for the equations rather than repeating them here.
-> We removed standard equations from the manuscript, combined the sections reporting SFE and SFR into one, and trimmed a few sentences.
-
-- You should also summarize the evidence for the AGN in this SMG (maybe when you mention this in the intro) so the reader doesn't have to read H14.
-> We rephrased the introduction to show more clearly the evidence of an AGN.
-
-- [a further concern/question about Table 4 is whether all the same assumptions such as excitation, alpha_co, etc. were made for the other SMGs otherwise the comparisons are meaningless]
-> We added notes in the caption below Table 4 to recap the assumptions used in deriving these quantities.
-=============================
+However, we retained this section in this paper as we provide the best-fit parameters that were not reported in Haas+14 and since we refered to the inferred half-light radius later in the analysis section.
 
@@
 Please correct LIR for the AGN emission prior to estimating SFR and include an AGN component in the SED fitting.
->In our analysis, we fit SED models to the rest-frame FIR, which has been found to have AGN negligible contributions to IR luminosities - Pope+08 report that AGN contributions to the bolometric IR luminosity is at most 30%.
-Since we do not have MIR data (for just the background SMG, as postive K blueward of dust peak), we didn't fit an AGN component.
+
+> In our analysis, we fit SED models to the rest-frame FIR, which has been found to have negligible AGN contribution to rest-frame FIR (≥ 60µm; Carilli+05, Netzer+07, Mullaney+11, Harrison+15).
+Since we do not have MIR data for just the background SMG.
+Due to the postive K corretion blueward of dust peak, the forground radio galaxy contributes a non-negligible amount to the MIR luminosity, we therefore didn't fit an AGN component.
+Including an additional component, and thus free parameters to the SED model will be over-fitted due to the limited amount of data at hand.
+Instead our SED model includes a power-law to the blue side of the dust peak, which accounts for the MIR excess and allows us to estimate the IR luminosity (Kirkpatrick+15, Riechers+13, Johnson+13, Casey+12).
+We derived the SFR and other corresponding properties using the L_FIR, (45-122.5), which is mostly due to SF-driven dust emission.
+
+> **Backup using IR:**
+> In our analysis, we fit SED models to the rest-frame FIR, which has been found to have AGN negligible contributions to IR luminosities - Pope+08 report that AGN contributions to the bolometric IR luminosity is at most 30%.
+> Since we do not have MIR data (for just the background SMG, as postive K blueward of dust peak), we didn't fit an AGN component.
 Including an additional component, and thus free parameters to the SED model will be over-fitted due to the limited amount of data at hand.
@@
 
-or should I change it to FIR --> SFR
-> In our analysis, we fit SED models to the rest-frame FIR, which has been found to have negligible AGN contribution to rest-frame FIR (≥ 60µm; Carilli+05, Netzer+07, Mullaney+11, Harrison+15).
-We derived the SFR and other corresponding properties using the L_FIR, (45-122.5), which SF-driven dust emission.
-> --> then change SFR using L_FIR instead of L_IR
+- section 4.3 is way too wordy and can be cut down to a few paragraphs and a table summarizing these key values (already given in Table 4).
+These are all standard calculations and you can refer to CW14 for the equations rather than repeating them here.
+
+> We removed standard equations from the manuscript, combined the sections reporting SFE and SFR, SFRSD into one, and trimmed a few sentences.
+
+- You should also summarize the evidence for the AGN in this SMG (maybe when you mention this in the intro) so the reader doesn't have to read H14.
+
+> We rephrased the introduction to show more clearly the evidence of an AGN.
+
+- [a further concern/question about Table 4 is whether all the same assumptions such as excitation, alpha_co, etc. were made for the other SMGs otherwise the comparisons are meaningless]
+
+> We added notes in the caption below Table 4 to recap the assumptions used in deriving these quantities.
+=============================
 
@@
 I suggest comparing to the general properties observed for SMGs (as summarized in CW14 or Casey+14) which will be more useful in placing this object in the context of the SMG population.
-> added columns to table referencing the properties of the population from a review.
-We picked out two lensed gravitaitonally lensed SMGs to demonstrate the power?
-extreme cases of SMGs which are intrinsically sit at the bright and faint ends.
+
+> We picked out two gravitaitonally lensed SMGs to show the ranges of SMGs properties, of which intrinsically sit at faint ends of the luminosity distribution, and thus is not studies in sensitivity-limited samples.
+We have added a compilation of SMG and type-2 QSOs properties to the Table, where SMGs properties are derived from Sharon+15 on a sample of SMGs with both CO(3-2) and CO(1-0) line measurements.
+Hence the SMG properties are free of assumption on the excitation conditions.
+Please see tablenote and comments for details.
+We have incoporated a comparison to these values in our conclusion.
 
@@
 # Minor comments:
+**DONE**
 - the depletion time seems short compared to other SMGs which are ~100Myr although maybe it is consistent with other SMGs with AGN in them.
 > Taken into account one of the comments listed above, we added literature reference to Table 4, and the depletion time scale is consistent with other SMGs.
-> Greve05: 40-100 Myr
+Greve+05 report a range of depletion time τ = 40-100 Myr.
 
-============================
 **DONE**
@@
 >The half-light radius of dust emitting region is ~ 1.2 kpc based on a recent study by Simpson+15, who collected ALMA 870 µm data over 52 SMGs.
-> Tacconi et al. (2006) report a median FWHM size of 4.1 ±1.6 kpc based on CO measurements.
+> Tacconi+06 report a median FWHM size of 4.1 ±1.6 kpc based on CO measurements. Furthermore, Ivison+11 found evidence of extended ground state CO emittiong region of ~7 kpc.
 > 

### 2015-12-08 mod1/response.txt
clean up response file, need to finsih conclusion, update Tab4 with SMG uncertainties

@@
-We thank the referee for providing constructive comments to improve this manuscipt.
-We have addressed all the concerns raised by the referee and details can be found in the revised version, please see attached.
+We thank the referee for providing constructive and useful comments to improve this manuscipt.
+We have addressed all the concerns raised by the referee and details can be found in the revised version -- please see attached.
 A brief description on how we incoprated the changes can be found below.
-=====================
 
-Major comments:
+# Major comments
+1:
 - There is already a lensing model in H14 (a paper the authors refer to numerous times) and it is unclear why they redid the lensing model (they use the same SMA data as H14 but a different code).
@@
 
+2:
 - The SMG is thought to harbor a luminous AGN.
@@
 Please correct LIR for the AGN emission prior to estimating SFR and include an AGN component in the SED fitting.
-
 > In our analysis, we fit SED models to the rest-frame FIR, which has been found to have negligible AGN contribution to rest-frame FIR (≥ 60µm; Carilli+05, Netzer+07, Mullaney+11, Harrison+15).
@@
 
+3:
 - section 4.3 is way too wordy and can be cut down to a few paragraphs and a table summarizing these key values (already given in Table 4).
 These are all standard calculations and you can refer to CW14 for the equations rather than repeating them here.
-
 > We removed standard equations from the manuscript, combined the sections reporting SFE and SFR, SFRSD into one, and trimmed a few sentences.
 
+4:
 - You should also summarize the evidence for the AGN in this SMG (maybe when you mention this in the intro) so the reader doesn't have to read H14.
-
 > We rephrased the introduction to show more clearly the evidence of an AGN.
 
+5:
 - [a further concern/question about Table 4 is whether all the same assumptions such as excitation, alpha_co, etc. were made for the other SMGs otherwise the comparisons are meaningless]
+> We added notes in the caption below Table 4 to recap assumptions used in deriving these quantities.
 
-> We added notes in the caption below Table 4 to recap the assumptions used in deriving these quantities.
-=============================
-
+6:
 - Section 5: why do the authors cherry-pick these 2 SMGs to make comparisons?
@@
 I suggest comparing to the general properties observed for SMGs (as summarized in CW14 or Casey+14) which will be more useful in placing this object in the context of the SMG population.
-
 > We picked out two gravitaitonally lensed SMGs to show the ranges of SMGs properties, of which intrinsically sit at faint ends of the luminosity distribution, and thus is not studies in sensitivity-limited samples.
@@
 We have incoporated a comparison to these values in our conclusion.
+Please see conclusion section for other changes.
 
+7:
 - the discussion/conclusions should focus on what is new from this paper and not what is already presented in H14.
@@
 How is that conclusion made or strengthened with this new data?
-> SFR and massive gas reservoir, coupled with the low depletion time of gas --> its short phase in the proposed evolutionary link
+> We have updated the conclusions.
 
-# Minor comments:
-**DONE**
+# Minor comments
+1:
 - the depletion time seems short compared to other SMGs which are ~100Myr although maybe it is consistent with other SMGs with AGN in them.
@@
 
-**DONE**
+2:
 - section headings in 3 are strange. Remove the words "New results" since this is obvious and a requirement for publication. Also remove subheading or second line in heading 3.2.
@@
 
-**DONE**
+3:
 - the left panels on Fig 1 and 2 should show the same region (have the same RA/DEC axes).
@@
 
-**DONE**
+4:
 - figure 3: orange is difficult to see. What is the SNR of the residuals in the right panel?
@@
 
-**Ask for clairfication**
+5:
 - figure 4: again colors (red, orange) are hard to distinguish on a print out version of the paper.
-> figure 3?
->
+> We were unable to make adjustment to this point as we did not use orange in the figure. Please kindly clarify this.
 
-**DONE**
+6:
 - specify the wavelengths range assumed for FIR.
-> We mentioned the FIR range in Section 4.2.2
+> We mentioned the FIR range in Section 4.2.2.
 
-**DONE**
+7:
 - last para section 4.2.2: it is limited data in the submm not the FIR [need to be probing Rayleigh Jeans] that makes the dust mass weakly constrained.
 I don't understand what the last sentence in this para means - I think there are words missing.
-> We clarify this by adding the phrase "rest-frame" to FIR. We also wrote/restructured the last paragraph more clearly.
+> We clarify this by adding the phrase "rest-frame" to FIR. We also restructured the last paragraph to convey our message more clearly.
 
-**DONE**
+8: 
 - SF surface density: from resolved studies of SMGs is it reasonable to divide half the SFR and gas mass by the area out to the half-light radii?
 give appropriate references to justify this assumption.
-> We provide a few citations to show that this is typical, and allow our results to be compared across other findings in literature.
-> 
->
+> We provided a few citations to show that this is typical, which allows our results to be compared across other findings in literature.
 
-**DONE**
+9:
 - intro: the first para makes it sound like our knowledge of SMGs comes primarily from SMGs found in large sky Herschel surveys and SPT but this is not true.
 Please include references to earlier work that established the basic properties of SMGs (redshift distribution, luminosities, SFRs, Mgas, etc) prior to Herschel even launching.
-> we restructured the paragraph and added earlier discoveries.
+> We restructured the paragraph and added earlier discoveries.
 
-**DONE**
+10:
 - the fact that the lensing system has two components isn't presented clearly in this paper.
@@
 Please make this clearer so the reader does not have to read H14
-> added a sentence to elaborate.
+> We added a sentence to elaborate on this, please see the revised manuscript.
 
-**DONE**
+11:
 - last few paras of paper: what does "breaking up its dust cocoon" mean? this is the first time this is mentioned and should be explained if it is relevant.
-> we mentioned this as a reference from Haas+14. We have removed this phrase in the revised version given that this has been mentioned in Haas+14, and is not necessary in my discussion.
+> We mentioned this as a reference from Haas+14. We have removed this phrase in the revised version given that this has been mentioned in Haas+14, and is not necessary in our discussion.
 
-**DONE**
+12:
 - end of section 4.3.1: the factor of 2 for dust mass is overshadowed by the factor of >5 in alpha_co
@@
 
-**DONE**
+13:
 - related to depletion time, there is a new Nature paper by Narayanan et al (published Sept 23) which discusses how SMGs in sims can last for a Gyr with replenishment from the IGM.
@@
 what do we learn if the galaxy is getting new gas?
->The derived depletion timescale is derived the based on the definition of the quantity τ = Mgas/SFR, which descibes 
-the time 
+>The derived depletion timescale is derived the based on the definition of the quantity τ = Mgas/SFR, which descibes the time 
 it would take for a galaxy to use up the available molecular gas reservoir given the current star formation rate, assuming no 
@@
 
-**DONE**- 
+13:
 dynamical mass calculation: can you estimate how much higher this would be given observations showing the different radii between the molecular and dust emission in SMGs. How different are the radii?
 >The half-light radius of dust emitting region is ~ 1.2 kpc based on a recent study by Simpson+15, who collected ALMA 870 µm data over 52 SMGs.
-> Tacconi+06 report a median FWHM size of 4.1 ±1.6 kpc based on CO measurements. Furthermore, Ivison+11 found evidence of extended ground state CO emittiong region of ~7 kpc.
-> 
+Tacconi+06 report a median FWHM size of 4.1 ±1.6 kpc based on CO measurements.
+Furthermore, Ivison+11 found evidence of extended ground state CO emittiong region of ~7 kpc.
+Please see the revised manuscipt.
+
 Daisy: @DR, should I calculate a dynamical mass using Median from Tacconi+06 as well? I get Mdyn ~ 36.8e10 Msun. Should I include these sizes in the paper? or just feed this to the referee.?
 
-**DONE**
+14:
 - appendix: "no evidence of correlation" do the authors mean "covariance" here?
 > We used the word "correlation" to indicate that regardless of the variation found in dust mass due to a different prior imposed on the emissivity, the IR luminosity is insensivtive to such changes in dust mass.
-Both the dust mass and IR lumonisty are inferred from the posterior probability distribution of the SED model, and are not parameters in the model / loss function.
+Both the dust mass and IR lumonisty are inferred from the posterior probability distribution of the SED model, and are not parameters in the model/loss function.
 For these reasons, we do not mean the covariance here.

### 2015-12-08 mod1/manuscript/ms.tex
Replaced entries for SMMJ0939 with FIR derived, also added SMG,type-2 qso prop
clean up response file, need to finsih conclusion, update Tab4 with SMG uncertainties

@@
 \newcommand\tni{\,\tablenotemark{i}}
+\newcommand\tnj{\,\tablenotemark{j}}
+\newcommand\tnk{\,\tablenotemark{k}}
 
@@
 We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy (SMG) SMM\,J0939+8315 at $z$ = 2.221, using
-the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
+the Combined Array for Research in Millimeter-wave Astronomy. 
 SMM\,J0939+8315 hosts a type-2 quasar, and is gravitationally lensed by the radio galaxy 3C220.3 {\bf and its companion galaxy} at $z$ = 0.685.
-The 104 GHz continuum emission underlying the CO line is detected toward 3C220.3 with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy.
+The 104~GHz continuum emission underlying the CO line is detected toward 3C220.3 with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy.
 Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (12.6\,$\pm$\,2.0)\,Jy\,km\,s\pmOne, we derive
@@
  wavelengths (L$_\textrm{IR} \sim$ 10$^{12}$ \Lsun) with high star formation rates (SFR) \citep[$\gtrsim $ 500 \Msun yr\pmOne; see \eg reviews by][]{Lagache05a,Casey14a}.
-Following this pioneering work, considerable amounts of efforts have been invested into
+Following the pioneering works, considerable amounts of effort have been invested into
 obtaining large samples of SMGs by carrying out
@@
 compare our findings for SMM\,J0939 
- with two other exceptionally submm-bright,}
+with a sample of SMGs with both \CO and \rot{1}{0} line measurements as well as 
+ two other exceptionally submm-bright,}
 strongly-lensed SMGs
-found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which have been studied in great detail. The properties
+found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which have been studied in great detail.
+ The properties
 of these galaxies are listed in Table~\ref{tab:comapreSMG}. While the cosmic Eyelash has the least amount of molecular gas, as well as
@@
 at 250\,\micron, while its CO line and IR luminosities are lower than those of most SMGs studied to date.
-{\bf This demonstrates BLAH BLAH
-the large variations in gas mass, dust mass, and star forming activity within the population at $z$\,$\sim$\,2$-$3, which is discernible with the aid of gravitational lensing.}
+%{\bf 
+%This demonstrates BLAH BLAH
+%the large variations in gas mass, dust mass, and star forming activity within the population at $z$\,$\sim$\,2$-$3, which is discernible with the aid of gravitational lensing.}
 While lensing can probe sources
@@
 \citep[\eg ][]{Greve05a,Tacconi08a}. 
+{\bf Since previous studies lack \rot{1}{0} measurements, extrapolations and assumptions are required in deriving these properties (\eg gas mass, depletion timescale).
+Comparing the properties of the gas reservoir in SMM\,J0939 against those derived based on a sample of SMGs with \rot{1}{0}, we find that SMM\,J0939 is BLAH, GET uncertainties from Chelsea.
+}
 
@@
 (\eg FWHM of the CO line profile \footnote{The statistical mean is based on the line profile of the CO transition closest to $J$ = 4\,\rarr\,3 available for each source.}, M$_\textrm{gas}$\footnote{The molecular gas mass for each source is derived based on its lowest-$J$ CO line emission available in literature.}, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a
-factor of $\sim$\,1.5, but is nevertheless consistent within the measurement uncertainties. This demonstrates that despite the variations in the intrinsic properties among lensed sources,
- SMM\,J0939 is representative of type-2 quasars at high redshifts (at least among the sample from \citealt{Polletta11a}).
+factor of $\sim$\,1.5, but is nevertheless consistent within the measurement uncertainties.
 
- %%% EDIT %%%%
-BLAH BLAH
-We conclude this paper by noting that SMM\,J0939 is a faithful representation of both high-redshift type-2 quasars and SMGs,
-based on the excellent agreement found between their {\bf gas and dust} properties (see \S~\ref{sec:SEDBg} and \S~\ref{sec:gas}).
+%> SFR and massive gas reservoir, coupled with the low depletion time of gas --> its short phase in the proposed evolutionary link
+
+{\bf We thus note that
+ SMM\,J0939 is consistent with the properties found in other SMGs and type-2 quasars at high-z that have CO measurements.
+ BLAH gas content, consuming gas at comparable rates, BLAH}.
 {\bf In the proposed evolutionary paradigm, BLAH}
-This is supportive of the proposed evolutionary phase model \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}, whereby SMM\,J0939 is transitioning from its star-bursting phase to the unobscured quasar phase.
+This is supportive of the proposed evolutionary phase model \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}, whereby SMM\,J0939 {\bf may be} transitioning from its star-bursting phase to the unobscured quasar phase.
 

### 2015-12-09 mod1/response.md
Fix flawed statement

--- 2015-12-08 mod1/response.txt
@@
 - the depletion time seems short compared to other SMGs which are ~100Myr although maybe it is consistent with other SMGs with AGN in them.
-> Taken into account one of the comments listed above, we added literature reference to Table 4, and the depletion time scale is consistent with other SMGs.
+> Greve+05 report a range of depletion time τ = 40-100 Myr.
+
+~~~ python
+# Taken into account one of the comments listed above, we added literature reference to Table 4, and the depletion time scale is consistent with other SMGs.
 Greve+05 report a range of depletion time τ = 40-100 Myr.
-
+~~~
 2:
@@
 give appropriate references to justify this assumption.
-> We provided a few citations to show that this is typical, which allows our results to be compared across other findings in literature.
+> We provided a few citations to show that this is typical.
 

### 2015-12-09 mod1/manuscript/ms.tex
Fix flawed statement

@@
 J0939+8315
-and other high-redshift SMGs and type-2 quasars shows that it is a faithful representation of both populations, suggesting that
-SMM\,J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase.
+and other high-redshift SMGs and type-2 quasars 
+{\bf EDIT AFTER CONCLUSION shows that it is a faithful representation of both populations, suggesting that
+SMM\,J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase. }
 \end{abstract}
@@
  $\beta$ adjusted from 2.2 to 3.0.
-While the difference in each best-fit parameter between this scenario and the previous model (an upper limit of $\beta$ = 2.2) is within 3\%, we find that the dust mass inferred from the posterior probability distribution of this SED model is boosted by a factor of $\sim$\,2.}
+While the difference in each best-fit parameter between this scenario and the previous model (an upper limit of $\beta$ = 2.2) is within 3\%, we find that the dust mass inferred from this best-fit SED model is boosted by a factor of $\sim$\,2.}
 \subsection{Physical Properties of the ISM in SMM\,J0939}

### 2015-12-09 mod1/manuscript/ms.tex
Shorten section 4.3.1 by removing excitation stuff related to SMGs

@@
  conversion factor ($\alpha_\mathrm{CO}$) when extrapolating from higher-$J$ CO lines. \par
-{\bf Recent observations of the ground state CO transition line in SMGs have demonstrated that these galaxies can be sub-thermally excited regardless of their high SFRs
-   \citep{Harris10a,Riechers11c,Riechers11d,Ivison11a}. 
- Moreover, observational results of SMGs with both \CO and CO($J$\,=\,1\,\rarr\,0) line measurements have shown that the
-   brightness temperature ratio is commonly found to be $R_\textrm{31}<$ 0.8 \citep
-   {Harris10a,Carilli10a,Swinbank2010a,Ivison10d,Ivison11a,Riechers11d}.} In contrast, similar observations in high-redshift quasar hosts suggest that the ratio
+{\bf Recent observations} in high-redshift quasar hosts suggest that the ratio
    is $R_\textrm{31}$\,$\sim$\,1 \citep{Riechers06a, Riechers11a}.

### 2015-12-12 mod1/response.md
grammar, also fix some false claims

@@
-We thank the referee for providing constructive and useful comments to improve this manuscipt.
+We thank the referee for providing constructive and thoughtful comments to improve the manuscipt.
 We have addressed all the concerns raised by the referee and details can be found in the revised version -- please see attached.
@@
 If the derived model is significantly different from H14 then this should be highlighted otherwise the lens modeling section isn't necessary in this paper.
-> We moved the lens mass and consistent results into table 1 and its caption, and removed details of the lens model / shortened the section.
+> We moved the lens mass and consistent results into table 1 and its caption, and removed details of the lens model and shortened the section.
 However, we retained this section in this paper as we provide the best-fit parameters that were not reported in Haas+14 and since we refered to the inferred half-light radius later in the analysis section.
@@
 > In our analysis, we fit SED models to the rest-frame FIR, which has been found to have negligible AGN contribution to rest-frame FIR (≥ 60µm; Carilli+05, Netzer+07, Mullaney+11, Harrison+15).
-Since we do not have MIR data for just the background SMG.
-Due to the postive K corretion blueward of dust peak, the forground radio galaxy contributes a non-negligible amount to the MIR luminosity, we therefore didn't fit an AGN component.
+Since we do not have MIR measurements solely from the background SMG and due to the postive K corretion blueward of dust peak, the forground radio galaxy contributes a non-negligible amount to the MIR luminosity, we therefore didn't fit an AGN component.
 Including an additional component, and thus free parameters to the SED model will be over-fitted due to the limited amount of data at hand.
@@
 We derived the SFR and other corresponding properties using the L_FIR, (45-122.5), which is mostly due to SF-driven dust emission.
-
-> **Backup using IR:**
-> In our analysis, we fit SED models to the rest-frame FIR, which has been found to have AGN negligible contributions to IR luminosities - Pope+08 report that AGN contributions to the bolometric IR luminosity is at most 30%.
-> Since we do not have MIR data (for just the background SMG, as postive K blueward of dust peak), we didn't fit an AGN component.
-Including an additional component, and thus free parameters to the SED model will be over-fitted due to the limited amount of data at hand.
-Instead our SED model includes a power-law to the blue side of the dust peak, which accounts for the MIR excess and allows us to estimate the IR luminosity (Kirkpatrick+15, Riechers+13, Johnson+13, Casey+12).
 
@@
 I suggest comparing to the general properties observed for SMGs (as summarized in CW14 or Casey+14) which will be more useful in placing this object in the context of the SMG population.
-> We picked out two gravitaitonally lensed SMGs to show the ranges of SMGs properties, of which intrinsically sit at faint ends of the luminosity distribution, and thus is not studies in sensitivity-limited samples.
+> We picked out two gravitaitonally lensed SMGs to show the ranges of SMGs properties, of which intrinsically sit at faint ends of the luminosity distribution, and thus would not have been studied in sensitivity-limited samples.
 We have added a compilation of SMG and type-2 QSOs properties to the Table, where SMGs properties are derived from Sharon+15 on a sample of SMGs with both CO(3-2) and CO(1-0) line measurements.
@@
 - the depletion time seems short compared to other SMGs which are ~100Myr although maybe it is consistent with other SMGs with AGN in them.
-> Greve+05 report a range of depletion time τ = 40-100 Myr.
+> Greve+05 report a range of depletion time τ = 40-100 Myr for SMGs.
 
-~~~ python
-# Taken into account one of the comments listed above, we added literature reference to Table 4, and the depletion time scale is consistent with other SMGs.
-Greve+05 report a range of depletion time τ = 40-100 Myr.
-~~~
 2:
 - section headings in 3 are strange. Remove the words "New results" since this is obvious and a requirement for publication. Also remove subheading or second line in heading 3.2.
-> we have removed "New results" in the subject headings
+> We have removed "New results" in the subject headings
 
@@
 Perhaps these can be overlayed on Fig 1.
-> we marked the locations of the peak emission from the SMA as white crosses on the right panel on figure 1
+> We marked the locations of the peak emission from the SMA as white crosses on the right panel on figure 1
 
@@
 - figure 3: orange is difficult to see. What is the SNR of the residuals in the right panel?
-> we modified our caption to state that the quoted contour levels are the same for both panels in the figure. We changed the critical line color to green to easily visualization.
+> We modified our caption to state that the quoted contour levels are the same for both panels in the figure. We changed the critical line color to green to easily visualization.
 
@@
 - figure 4: again colors (red, orange) are hard to distinguish on a print out version of the paper.
-> We were unable to make adjustment to this point as we did not use orange in the figure. Please kindly clarify this.
+> We were unable to make adjustment regarding this as we did not use orange in the figure. Please kindly clarify this.
 
@@
 
-Daisy: @DR, should I calculate a dynamical mass using Median from Tacconi+06 as well? I get Mdyn ~ 36.8e10 Msun. Should I include these sizes in the paper? or just feed this to the referee.?
+**@DR, should I calculate a dynamical mass using Median from Tacconi+06 as well? I get Mdyn ~ 36.8e10 Msun. Should I include these sizes in the paper? or just feed this to the referee.?**
 
@@
 > We used the word "correlation" to indicate that regardless of the variation found in dust mass due to a different prior imposed on the emissivity, the IR luminosity is insensivtive to such changes in dust mass.
-Both the dust mass and IR lumonisty are inferred from the posterior probability distribution of the SED model, and are not parameters in the model/loss function.
+Both the dust mass and IR lumonisty are inferred from the best-fit SED model, and are not parameters in the model (and the loss function).
 For these reasons, we do not mean the covariance here.

### 2015-12-20 mod1/response.md
Table 4 completed

@@
 
-6:
+## 6 (NEED TO WORK ON):
 - Section 5: why do the authors cherry-pick these 2 SMGs to make comparisons?
@@
 I suggest comparing to the general properties observed for SMGs (as summarized in CW14 or Casey+14) which will be more useful in placing this object in the context of the SMG population.
+
 > We picked out two gravitaitonally lensed SMGs to show the ranges of SMGs properties, of which intrinsically sit at faint ends of the luminosity distribution, and thus would not have been studied in sensitivity-limited samples.
@@
 
-7:
+## 7 (NEED TO WORK ON):
 - the discussion/conclusions should focus on what is new from this paper and not what is already presented in H14.
@@
 How is that conclusion made or strengthened with this new data?
+
 > We have updated the conclusions.
@@
 - section headings in 3 are strange. Remove the words "New results" since this is obvious and a requirement for publication. Also remove subheading or second line in heading 3.2.
-> We have removed "New results" in the subject headings
+> We have removed "New results" in the subject headings.
 
@@
 Perhaps these can be overlayed on Fig 1.
-> We marked the locations of the peak emission from the SMA as white crosses on the right panel on figure 1
+> We marked the locations of the peak emission from the SMA as white crosses on the right panel on figure 1.
 

### 2015-12-20 mod1/manuscript/ms.tex
Table 4 completed

@@
 \newcommand\tnk{\,\tablenotemark{k}}
+\newcommand\tnl{\,\tablenotemark{l}}
 
@@
 The
-functional form of the fit comprises a single-temperature, modified blackbody function joined to a $S_{\lambda} \propto \lambda^\alpha
+functional form of the fit comprises a single-temperature, modified blackbody function joined to a $B_{\lambda} \propto \lambda^\alpha
 $ power law on the blue
@@
 \begin{equation}
-\rm S_{\lambda} \propto \frac{(1-exp^{-(\frac{\lambda_0 (1+z)}{\lambda})^{\beta}})(\frac{c}{\lambda})^3}
+\rm B_{\lambda} \propto \frac{(1-exp^{-(\frac{\lambda_0 (1+z)}{\lambda})^{\beta}})(\frac{c}{\lambda})^3}
 {exp^{\frac{hc}{\lambda\rm{kT/(1+z)} } }-1}
@@
 \begin{equation}
-\rm S_{\lambda} \propto \frac{(\frac{c}{\lambda})^{\beta+3}}{exp^{\frac{hc}{\lambda\rm{kT/(1+z)}}}-1}
+\rm B_{\lambda} \propto \frac{(\frac{c}{\lambda})^{\beta+3}}{exp^{\frac{hc}{\lambda\rm{kT/(1+z)}}}-1}
 \end{equation}
@@
 compare our findings for SMM\,J0939 
-with a sample of SMGs with both \CO and \rot{1}{0} line measurements as well as 
+with a sample of SMGs presented by \citet{Bothwell13a} as well as 
  two other exceptionally submm-bright,}
 strongly-lensed SMGs
-found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which have been studied in great detail.
- The properties
-of these galaxies are listed in Table~\ref{tab:comapreSMG}. While the cosmic Eyelash has the least amount of molecular gas, as well as
+found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which are well-studied. The properties
+of these galaxies are listed in Table~\ref{tab:comapreSMG}. 
+BLAH comparison with Bothwell13a sample.
+
+While the cosmic Eyelash has the least amount of molecular gas, as well as
 the
-longest gas depletion timescale (\ie is the most long-lived), the overall gas and dust properties of SMM\,J0939 fall between those of HLSW-01 and the
+longest gas depletion timescale, the overall gas and dust properties of SMM\,J0939 fall between those of HLSW-01 and the
 cosmic
@@
 While lensing can probe sources
-of various intrinsic properties, we find that SMM\,J0939 is representative of the SMG population, with its intrinsic CO line luminosity, IR luminosity, gas mass,
-dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in ``typical" SMGs studied to date
-\citep[\eg ][]{Greve05a,Tacconi08a}. 
+of various intrinsic properties, we find that 
+SMM\,J0939 is BLAH BLAH representative of the SMG population, with its intrinsic CO line luminosity, IR luminosity, gas mass,
+dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in ``typical" SMGs studied to data (see Table~\ref{tab:compareSMG}.
 {\bf Since previous studies lack \rot{1}{0} measurements, extrapolations and assumptions are required in deriving these properties (\eg gas mass, depletion timescale).
-Comparing the properties of the gas reservoir in SMM\,J0939 against those derived based on a sample of SMGs with \rot{1}{0}, we find that SMM\,J0939 is BLAH, GET uncertainties from Chelsea.
+Comparing the properties of the gas reservoir in SMM\,J0939 against those derived based on a sample of SMGs with \rot{1}{0}, we find that SMM\,J0939 is BLAH.
 }

### 2015-12-20 mod1/manuscript/ms.tex
ready to send DR to look over, added Bothwell+13 and modified conclusion correspondingly

@@
 and other high-redshift SMGs and type-2 quasars 
-{\bf EDIT AFTER CONCLUSION shows that it is a faithful representation of both populations, suggesting that
+{\bf shows that it is consistent with the properties of both populations.
+Together with the presence of its obscured quasar, massive molecular gas reservoir, on-going intensive star-formation and the short gas depletion timescale suggests that
 SMM\,J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase. }
@@
 {\bf Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1\,--\,3 \citep{Chapman05a}, during the epoch of stellar mass and
-galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}. This galaxy population was first detected 
-$\sim$18 years ago with the Submillimeter Common User Bolometer Array (SCUBA) on the James
-Clerk Maxwell Telescope (JCMT; \citealt{Smail97a, Hughes98a, Barger98a}). 
+galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}. 
+%This galaxy population was first detected 
+%$\sim$18 years ago with the Submillimeter Common User Bolometer Array (SCUBA) on the James
+%Clerk Maxwell Telescope (JCMT; \citealt{Smail97a, Hughes98a, Barger98a}). 
 Previous works %following this discovery
@@
  are extremely luminous in the infrared
- wavelengths (L$_\textrm{IR} \sim$ 10$^{12}$ \Lsun) with high star formation rates (SFR) \citep[$\gtrsim $ 500 \Msun yr\pmOne; see \eg reviews by][]{Lagache05a,Casey14a}.
-Following the pioneering works, considerable amounts of effort have been invested into
+ wavelengths (L$_\textrm{IR} \sim$ 10$^{12}$ \Lsun) with high star formation rates (SFR) \citep[$\gtrsim $ 500 \Msun yr\pmOne; see \eg reviews by][]{Blain02a, Lagache05a,Casey14a}.  
+{\bf Following the pioneering works in the discovery of this population}, considerable amounts of effort have been invested into 
 obtaining large samples of SMGs by carrying out
@@
   %at $z$\,$\sim$\,1\,--\,3 
-  have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Frayer98a, Riechers11c, Neri03a, Riechers11d,Ivison11a,Bothwell13a}.}
+  have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Frayer98a, Neri03a, Riechers11c, Riechers11d, Ivison11a, Bothwell13a}.}
 
@@
 All best-fit
-parameters are listed in Table~\ref{tab:lensParam}. {\bf DR: Please Note changes to Tab 1}
+parameters are listed in Table~\ref{tab:lensParam}. 
 %The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1\farcs22\,$\pm$\,0\farcs01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0\farcs75\,$\pm$\,0\farcs02 (5.34\,\,kpc at $z$\,=\,0.685), and
@@
 We find a dynamical mass of $M_\textrm{dyn}$ = (7.84\,$\pm$\,2.84)\,$\times$\,10$^{10}$\,\Msun, and a gas-to-dynamical mass fraction of $f_\textrm{gas-to-dyn}$ = 0.35\,$\pm$\,0.14, consistent with those of other SMGs \citep{Tacconi06a}.
-We note that a derived dynamical mass based on this assumption is likely to be biased towards low values, as the CO-emitting region {\bf that traces the cool gas} can be spatially more extended than the dust emitting region due to the low dust optical depth at larger radii \citep[\eg][]{Tacconi06a, Riechers11c,Riechers11d,Ivison11a}.
+We note that a derived dynamical mass based on this assumption is likely to be biased towards low values, as the CO-emitting region {\bf that traces the cool gas} can be spatially more extended than the dust emitting region due to the low dust optical depth at larger radii.
+%\citep[\eg][]{Tacconi06a, Riechers11c,Riechers11d,Ivison11a}.
 {\bf This has been supported by recent observations.
@@
 compare our findings for SMM\,J0939 
-with a sample of SMGs presented by \citet{Bothwell13a} as well as 
- two other exceptionally submm-bright,}
+with a sample of SMGs \citep[][hereafter B13]{Bothwell13a}, where their properties are listed in Table~\ref{tab:compareSMG}. This clearly demonstrates that SMM\,J0939 has properties similar
+to other SMGs studied to date except for its gas mass, which is slightly lower than the median found in the B13 sample. 
+This is unsurprising given that SMM\,J0939 is lensed with a magnification factor of $\sim$10, placing it on the fainter end of the CO line luminosity distribution when compared to un-lensed SMGs. 
+We note that the gas properties (CO luminosity and gas mass) of the SMGs in the B13 sample are derived based on the excitation condition found via CO spectral line energy distribution (SLED) modelling, which the authors find it to be very similar to that of the cosmic Eyelash.
+Given that the gas properties in the B13 sample are based on unresolved emission of various higher-$J$ CO transitions, we additionally compare SMM\,J0939 to two other exceptionally submm-bright,
 strongly-lensed SMGs
-found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which are well-studied. The properties
-of these galaxies are listed in Table~\ref{tab:comapreSMG}. 
-BLAH comparison with Bothwell13a sample.
+found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which are well-studied and their properties are derived using similar approach we employed in this paper.}
 
-While the cosmic Eyelash has the least amount of molecular gas, as well as
+{\bf As shown in Table~\ref{tab:compareSMG},} while the cosmic Eyelash has the least amount of molecular gas, as well as
 the
@@
 at 250\,\micron, while its CO line and IR luminosities are lower than those of most SMGs studied to date.
-%{\bf 
-%This demonstrates BLAH BLAH
-%the large variations in gas mass, dust mass, and star forming activity within the population at $z$\,$\sim$\,2$-$3, which is discernible with the aid of gravitational lensing.}
 While lensing can probe sources
 of various intrinsic properties, we find that 
-SMM\,J0939 is BLAH BLAH representative of the SMG population, with its intrinsic CO line luminosity, IR luminosity, gas mass,
-dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in ``typical" SMGs studied to data (see Table~\ref{tab:compareSMG}.
-{\bf Since previous studies lack \rot{1}{0} measurements, extrapolations and assumptions are required in deriving these properties (\eg gas mass, depletion timescale).
-Comparing the properties of the gas reservoir in SMM\,J0939 against those derived based on a sample of SMGs with \rot{1}{0}, we find that SMM\,J0939 is BLAH.
-}
+SMM\,J0939 is consistent with the ``typical" SMG population, with its intrinsic CO line luminosity, IR luminosity, gas mass,
+dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in ``typical" SMGs studied to data.
 
-To examine whether SMM\,J0939 is also representative of type-2 quasars at high redshifts, we compare the properties of SMM\,J0939
-against those of eight CO-detected obscured AGNs at $z$ = 1.6\,$-$\,2.8, using the averaged values reported by \citet[][and references
+{\bf Since SMM\,J0939 also hosts a type-2 quasar, we compare its properties}
+against those of eight CO-detected obscured AGNs at $z$ = 1.6\,$-$\,2.8 \citep[][and references
 therein]{Polletta11a}. 
@@
 In contrast to what was found for F10214, we find that the properties
-(\eg FWHM of the CO line profile \footnote{The statistical mean is based on the line profile of the CO transition closest to $J$ = 4\,\rarr\,3 available for each source.}, M$_\textrm{gas}$\footnote{The molecular gas mass for each source is derived based on its lowest-$J$ CO line emission available in literature.}, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a
+(\eg FWHM of the CO line profile 
+%\footnote{The statistical mean is based on the line profile of the CO transition closest to $J$ = 4\,\rarr\,3 available for each source.}
+, M$_\textrm{gas}$
+%\footnote{The molecular gas mass for each source is derived based on its lowest-$J$ CO line emission available in literature.}
+, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a
 factor of $\sim$\,1.5, but is nevertheless consistent within the measurement uncertainties.
 
-%> SFR and massive gas reservoir, coupled with the low depletion time of gas --> its short phase in the proposed evolutionary link
-
-{\bf We thus note that
- SMM\,J0939 is consistent with the properties found in other SMGs and type-2 quasars at high-z that have CO measurements.
- BLAH gas content, consuming gas at comparable rates, BLAH}.
-{\bf In the proposed evolutionary paradigm, BLAH}
-This is supportive of the proposed evolutionary phase model \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}, whereby SMM\,J0939 {\bf may be} transitioning from its star-bursting phase to the unobscured quasar phase.
+{\bf Our findings therefore suggest that SMM\,J0939 {\bf may be} transitioning from its short, star-bursting phase to the unobscured quasar phase in the proposed evolutionary link model \citep[\eg][]{Sanders88,Coppin08a,Simpson12a} given the presence of its obscured QSO and a massive gas reservoir with an immense SFR, coupled with the low depletion timescale of gas.
+}
+% --> its short phase in the proposed evolutionary link  
+%fits in the proposed evolutionary paradigm \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}, in which it
 

### 2015-12-20 mod1/response.md
put radius instead of physical extent for dust emission size to avoid ambiguity. Updated responses, which is consistent and up to date with changes made to ms.tex

@@
 These are all standard calculations and you can refer to CW14 for the equations rather than repeating them here.
-> We removed standard equations from the manuscript, combined the sections reporting SFE and SFR, SFRSD into one, and trimmed a few sentences.
+> We removed standard equations from the manuscript, and combined the sections reporting SFE, SFR, and SFRSD into one. We also shortened the section.
 
@@
 
-## 6 (NEED TO WORK ON):
+6:
 - Section 5: why do the authors cherry-pick these 2 SMGs to make comparisons?
@@
 > We picked out two gravitaitonally lensed SMGs to show the ranges of SMGs properties, of which intrinsically sit at faint ends of the luminosity distribution, and thus would not have been studied in sensitivity-limited samples.
-We have added a compilation of SMG and type-2 QSOs properties to the Table, where SMGs properties are derived from Sharon+15 on a sample of SMGs with both CO(3-2) and CO(1-0) line measurements.
-Hence the SMG properties are free of assumption on the excitation conditions.
+In addition, these are among the SMGs which are best-studied to date and their properties are deriving using similar approach in this paper.
+Hence, a comparison with these object will have relatively lower uncertainties.
+We have added a compilation of SMG and type-2 QSOs properties to the Table.
 Please see tablenote and comments for details.
@@
 
-## 7 (NEED TO WORK ON):
+## 7
 - the discussion/conclusions should focus on what is new from this paper and not what is already presented in H14.
@@
 
-> We have updated the conclusions.
+> We updated the conclusions.
 
@@
 - the depletion time seems short compared to other SMGs which are ~100Myr although maybe it is consistent with other SMGs with AGN in them.
-> Greve+05 report a range of depletion time τ = 40-100 Myr for SMGs.
+> Greve+05 report a range of depletion time τ = 40-100 Myr for SMGs, please see also Table 4.
 
@@
 - section headings in 3 are strange. Remove the words "New results" since this is obvious and a requirement for publication. Also remove subheading or second line in heading 3.2.
-> We have removed "New results" in the subject headings.
+> We removed "New results" in the subject headings.
 
@@
 >The half-light radius of dust emitting region is ~ 1.2 kpc based on a recent study by Simpson+15, who collected ALMA 870 µm data over 52 SMGs.
-Tacconi+06 report a median FWHM size of 4.1 ±1.6 kpc based on CO measurements.
-Furthermore, Ivison+11 found evidence of extended ground state CO emittiong region of ~7 kpc.
+Tacconi+06 report a median FWHM size of 4.1 ±1.6 kpc based on high-J CO measurements.
+Given the small number statistics on resolved CO(1-0) emission in QSOs, where Riechers+11 find no evidence of extent cold gas emission, we did not include an additional estimate of the dynamical mass assuming some physical size from recent observaitons (still limited) in the paper.
+However, we have noted these phyiscal sizes in the text, which allows readers to scale the dynamical mass correspondingly should they wish to do so.
 Please see the revised manuscipt.
-
-**@DR, should I calculate a dynamical mass using Median from Tacconi+06 as well? I get Mdyn ~ 36.8e10 Msun. Should I include these sizes in the paper? or just feed this to the referee.?**
 

### 2015-12-20 mod1/manuscript/ms.tex
put radius instead of physical extent for dust emission size to avoid ambiguity. Updated responses, which is consistent and up to date with changes made to ms.tex
add timestamp to revised version in heading

@@
 
-\slugcomment{Submitted to the ApJ}
+\slugcomment{Submitted to the ApJ, Revised version December 20, 2015}
 \usepackage{amsmath}
@@
 In particular, \citet{Tacconi06a} report a median FWHM size of 4.1\,$\pm$\,1.6 kpc based on \CO line measurements of their sample, whereas studies with spatially resolved \rot{1}{0} observations have additionally demonstrated that the cool gas regions are even more extended (R$_{\rm eff} \sim$ 7 kpc;  \citealt{Ivison11a}, see also \citealt{Riechers11c, Hodge13a}).
-For the physical size of dust-emitting regions, \citet{Simpson15a} recently report a spatial extent of 2.4 kpc in a sample of 52 SMGs.
+For the physical size of dust-emitting regions, \citet{Simpson15a} recently report a spatial extent with radius of 1.2 kpc in a sample of 52 SMGs.
 % Adopting a physical size of 4.1 kpc, we find a dynamical mass of 3.7\,$\times$\,10$^{11}$\,\Msun.

### 2015-12-20 mod1/manuscript/ms.tex
replace bib sec with bib item, order R11 papers and added short form to H14, G11, etc

@@
 
-\bibliographystyle{apj}
-\bibliography{J0939}
+%
+\begin{thebibliography}{}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Baldwin} {et~al.}(1985){Baldwin}, {Boysen}, {Hales}, {Jennings},
+  {Waggett}, {Warner}, \& {Wilson}}]{r2728}
+{Baldwin}, J.~E., {Boysen}, R.~C., {Hales}, S.~E.~G., {et~al.} 1985, \mnras,
+  217, 717
+
+\bibitem[{{Begelman} {et~al.}(1984){Begelman}, {Blandford}, \&
+  {Rees}}]{Begelman84a}
+{Begelman}, M.~C., {Blandford}, R.~D., \& {Rees}, M.~J. 1984, Reviews of Modern
+  Physics, 56, 255
+
+\bibitem[{{Blain} {et~al.}(2002){Blain}, {Smail}, {Ivison}, {Kneib}, \&
+  {Frayer}}]{Blain02a}
+{Blain}, A.~W., {Smail}, I., {Ivison}, R.~J., {Kneib}, J.-P., \& {Frayer},
+  D.~T. 2002, \physrep, 369, 111
+
+\bibitem[{{Bothwell} {et~al.}(2013){Bothwell}, {Smail}, {Chapman}, {Genzel},
+  {Ivison}, {Tacconi}, {Alaghband-Zadeh}, {Bertoldi}, {Blain}, {Casey}, {Cox},
+  {Greve}, {Lutz}, {Neri}, {Omont}, \& {Swinbank}}]{Bothwell13a}
+{Bothwell}, M.~S., {Smail}, I., {Chapman}, S.~C., {et~al.} 2013, \mnras, 429,
+  3047 (B13)
+
+\bibitem[{{Bouch{\'e}} {et~al.}(2007){Bouch{\'e}}, {Cresci}, {Davies},
+  {Eisenhauer}, {F{\"o}rster Schreiber}, {Genzel}, {Gillessen}, {Lehnert},
+  {Lutz}, {Nesvadba}, {Shapiro}, {Sternberg}, {Tacconi}, {Verma}, {Cimatti},
+  {Daddi}, {Renzini}, {Erb}, {Shapley}, \& {Steidel}}]{B07a}
+{Bouch{\'e}}, N., {Cresci}, G., {Davies}, R., {et~al.} 2007, \apj, 671, 303
+
+\bibitem[{{Bussmann} {et~al.}(2015){Bussmann}, {Riechers}, {Fialkov},
+  {Scudder}, {Hayward}, {Cowley}, {Bock}, {Calanog}, {Chapman}, {Cooray}, {De
+  Bernardis}, {Farrah}, {Fu}, {Gavazzi}, {Hopwood}, {Ivison}, {Jarvis},
+  {Lacey}, {Loeb}, {Oliver}, {Perez-Fournon}, {Rigopoulou}, {Roseboom},
+  {Scott}, {Smith}, {Vieira}, {Wang}, \& {Wardlow}}]{Bussmann15a}
+{Bussmann}, R.~S., {Riechers}, D., {Fialkov}, A., {et~al.} 2015, ArXiv
+  e-prints, arXiv:1504.05256
+
+\bibitem[{{Carilli} \& {Walter}(2013)}]{Carilli13a}
+{Carilli}, C.~L., \& {Walter}, F. 2013, \araa, 51, 105
+
+\bibitem[{{Carlstrom} {et~al.}(2011){Carlstrom}, {Ade}, {Aird}, {Benson},
+  {Bleem}, {Busetti}, {Chang}, {Chauvin}, {Cho}, {Crawford}, {Crites}, {Dobbs},
+  {Halverson}, {Heimsath}, {Holzapfel}, {Hrubes}, {Joy}, {Keisler}, {Lanting},
+  {Lee}, {Leitch}, {Leong}, {Lu}, {Lueker}, {Luong-van}, {McMahon}, {Mehl},
+  {Meyer}, {Mohr}, {Montroy}, {Padin}, {Plagge}, {Pryke}, {Ruhl}, {Schaffer},
+  {Schwan}, {Shirokoff}, {Spieler}, {Staniszewski}, {Stark}, {Tucker},
+  {Vanderlinde}, {Vieira}, \& {Williamson}}]{Carlstrom11a}
+{Carlstrom}, J.~E., {Ade}, P.~A.~R., {Aird}, K.~A., {et~al.} 2011, \pasp, 123,
+  568
+
+\bibitem[{{Casey}(2012)}]{Casey12a}
+{Casey}, C.~M. 2012, \mnras, 425, 3094
+
+\bibitem[{{Casey} {et~al.}(2014){Casey}, {Narayanan}, \& {Cooray}}]{Casey14a}
+{Casey}, C.~M., {Narayanan}, D., \& {Cooray}, A. 2014, \physrep, 541, 45
+
+\bibitem[{{Chabrier}(2003)}]{Chabrier03a}
+{Chabrier}, G. 2003, \pasp, 115, 763
+
+\bibitem[{{Chapman} {et~al.}(2005){Chapman}, {Blain}, {Smail}, \&
+  {Ivison}}]{Chapman05a}
+{Chapman}, S.~C., {Blain}, A.~W., {Smail}, I., \& {Ivison}, R.~J. 2005, \apj,
+  622, 772
+
+\bibitem[{{Cleary} {et~al.}(2007){Cleary}, {Lawrence}, {Marshall}, {Hao}, \&
+  {Meier}}]{Cleary07a}
+{Cleary}, K., {Lawrence}, C.~R., {Marshall}, J.~A., {Hao}, L., \& {Meier}, D.
+  2007, \apj, 660, 117
+
+\bibitem[{{Cohen} {et~al.}(2007){Cohen}, {Lane}, {Cotton}, {Kassim}, {Lazio},
+  {Perley}, {Condon}, \& {Erickson}}]{r30}
+{Cohen}, A.~S., {Lane}, W.~M., {Cotton}, W.~D., {et~al.} 2007, \aj, 134, 1245
+
+\bibitem[{{Condon} {et~al.}(1998){Condon}, {Cotton}, {Greisen}, {Yin},
+  {Perley}, {Taylor}, \& {Broderick}}]{r16}
+{Condon}, J.~J., {Cotton}, W.~D., {Greisen}, E.~W., {et~al.} 1998, \aj, 115,
+  1693
+
+\bibitem[{{Conley} {et~al.}(2011){Conley}, {Cooray}, {Vieira}, {Gonz{\'a}lez
+  Solares}, {Kim}, {Aguirre}, {Amblard}, {Auld}, {Baker}, {Beelen}, {Blain},
+  {Blundell}, {Bock}, {Bradford}, {Bridge}, {Brisbin}, {Burgarella},
+  {Carpenter}, {Chanial}, {Chapin}, {Christopher}, {Clements}, {Cox},
+  {Djorgovski}, {Dowell}, {Eales}, {Earle}, {Ellsworth-Bowers}, {Farrah},
+  {Franceschini}, {Frayer}, {Fu}, {Gavazzi}, {Glenn}, {Griffin}, {Gurwell},
+  {Halpern}, {Ibar}, {Ivison}, {Jarvis}, {Kamenetzky}, {Krips}, {Levenson},
+  {Lupu}, {Mahabal}, {Maloney}, {Maraston}, {Marchetti}, {Marsden},
+  {Matsuhara}, {Mortier}, {Murphy}, {Naylor}, {Neri}, {Nguyen}, {Oliver},
+  {Omont}, {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen},
+  {Rangwala}, {Rawlings}, {Raymond}, {Riechers}, {Rodighiero}, {Roseboom},
+  {Rowan-Robinson}, {Schulz}, {Scott}, {Scott}, {Serra}, {Seymour}, {Shupe},
+  {Smith}, {Symeonidis}, {Tugwell}, {Vaccari}, {Valiante}, {Valtchanov},
+  {Verma}, {Viero}, {Vigroux}, {Wang}, {Wiebe}, {Wright}, {Xu}, {Zeimann},
+  {Zemcov}, \& {Zmuidzinas}}]{Conley11a}
+{Conley}, A., {Cooray}, A., {Vieira}, J.~D., {et~al.} 2011, \apjl, 732, L35
+
+\bibitem[{{Coppin} {et~al.}(2008){Coppin}, {Swinbank}, {Neri}, {Cox},
+  {Alexander}, {Smail}, {Page}, {Stevens}, {Knudsen}, {Ivison}, {Beelen},
+  {Bertoldi}, \& {Omont}}]{Coppin08a}
+{Coppin}, K.~E.~K., {Swinbank}, A.~M., {Neri}, R., {et~al.} 2008, \mnras, 389,
+  45
+
+\bibitem[{{Danielson} {et~al.}(2011){Danielson}, {Swinbank}, {Smail}, {Cox},
+  {Edge}, {Weiss}, {Harris}, {Baker}, {De Breuck}, {Geach}, {Ivison}, {Krips},
+  {Lundgren}, {Longmore}, {Neri}, \& {Flaquer}}]{Danielson11a}
+{Danielson}, A.~L.~R., {Swinbank}, A.~M., {Smail}, I., {et~al.} 2011, \mnras,
+  410, 1687
+
+\bibitem[{{Deane} {et~al.}(2013){Deane}, {Heywood}, {Rawlings}, \&
+  {Marshall}}]{Deane13a}
+{Deane}, R.~P., {Heywood}, I., {Rawlings}, S., \& {Marshall}, P.~J. 2013,
+  \mnras, 434, 23
+
+\bibitem[{{Dickinson} {et~al.}(2003){Dickinson}, {Papovich}, {Ferguson}, \&
+  {Budav{\'a}ri}}]{Dickinson03a}
+{Dickinson}, M., {Papovich}, C., {Ferguson}, H.~C., \& {Budav{\'a}ri}, T. 2003,
+  \apj, 587, 25
+
+\bibitem[{{Dowell} {et~al.}(2014){Dowell}, {Conley}, {Glenn}, {Arumugam},
+  {Asboth}, {Aussel}, {Bertoldi}, {B{\'e}thermin}, {Bock}, {Boselli}, {Bridge},
+  {Buat}, {Burgarella}, {Cabrera-Lavers}, {Casey}, {Chapman}, {Clements},
+  {Conversi}, {Cooray}, {Dannerbauer}, {De Bernardis}, {Ellsworth-Bowers},
+  {Farrah}, {Franceschini}, {Griffin}, {Gurwell}, {Halpern}, {Hatziminaoglou},
+  {Heinis}, {Ibar}, {Ivison}, {Laporte}, {Marchetti},
+  {Mart{\'{\i}}nez-Navajas}, {Marsden}, {Morrison}, {Nguyen}, {O'Halloran},
+  {Oliver}, {Omont}, {Page}, {Papageorgiou}, {Pearson}, {Petitpas},
+  {P{\'e}rez-Fournon}, {Pohlen}, {Riechers}, {Rigopoulou}, {Roseboom},
+  {Rowan-Robinson}, {Sayers}, {Schulz}, {Scott}, {Seymour}, {Shupe}, {Smith},
+  {Streblyanska}, {Symeonidis}, {Vaccari}, {Valtchanov}, {Vieira}, {Viero},
+  {Wang}, {Wardlow}, {Xu}, \& {Zemcov}}]{Dowell14a}
+{Dowell}, C.~D., {Conley}, A., {Glenn}, J., {et~al.} 2014, \apj, 780, 75
+
+\bibitem[{{Downes} \& {Solomon}(1998)}]{Downes98a}
+{Downes}, D., \& {Solomon}, P.~M. 1998, \apj, 507, 615
+
+\bibitem[{{Dunne} {et~al.}(2003){Dunne}, {Eales}, \& {Edmunds}}]{Dunne03a}
+{Dunne}, L., {Eales}, S.~A., \& {Edmunds}, M.~G. 2003, \mnras, 341, 589
+
+\bibitem[{{Eales} {et~al.}(2010){Eales}, {Dunne}, {Clements}, {Cooray}, {de
+  Zotti}, {Dye}, {Ivison}, {Jarvis}, {Lagache}, {Maddox}, {Negrello},
+  {Serjeant}, {Thompson}, {van Kampen}, {Amblard}, {Andreani}, {Baes},
+  {Beelen}, {Bendo}, {Benford}, {Bertoldi}, {Bock}, {Bonfield}, {Boselli},
+  {Bridge}, {Buat}, {Burgarella}, {Carlberg}, {Cava}, {Chanial}, {Charlot},
+  {Christopher}, {Coles}, {Cortese}, {Dariush}, {da Cunha}, {Dalton}, {Danese},
+  {Dannerbauer}, {Driver}, {Dunlop}, {Fan}, {Farrah}, {Frayer}, {Frenk},
+  {Geach}, {Gardner}, {Gomez}, {Gonz{\'a}lez-Nuevo}, {Gonz{\'a}lez-Solares},
+  {Griffin}, {Hardcastle}, {Hatziminaoglou}, {Herranz}, {Hughes}, {Ibar},
+  {Jeong}, {Lacey}, {Lapi}, {Lawrence}, {Lee}, {Leeuw}, {Liske},
+  {L{\'o}pez-Caniego}, {M{\"u}ller}, {Nandra}, {Panuzzo}, {Papageorgiou},
+  {Patanchon}, {Peacock}, {Pearson}, {Phillipps}, {Pohlen}, {Popescu},
+  {Rawlings}, {Rigby}, {Rigopoulou}, {Robotham}, {Rodighiero}, {Sansom},
+  {Schulz}, {Scott}, {Smith}, {Sibthorpe}, {Smail}, {Stevens}, {Sutherland},
+  {Takeuchi}, {Tedds}, {Temi}, {Tuffs}, {Trichas}, {Vaccari}, {Valtchanov},
+  {van der Werf}, {Verma}, {Vieria}, {Vlahakis}, \& {White}}]{Eales10a}
+{Eales}, S., {Dunne}, L., {Clements}, D., {et~al.} 2010, \pasp, 122, 499
+
+\bibitem[{{Engel} {et~al.}(2010){Engel}, {Tacconi}, {Davies}, {Neri}, {Smail},
+  {Chapman}, {Genzel}, {Cox}, {Greve}, {Ivison}, {Blain}, {Bertoldi}, \&
+  {Omont}}]{Engel10a}
+{Engel}, H., {Tacconi}, L.~J., {Davies}, R.~I., {et~al.} 2010, \apj, 724, 233
+
+\bibitem[{{Fanaroff} \& {Riley}(1974)}]{Fanaroff74}
+{Fanaroff}, B.~L., \& {Riley}, J.~M. 1974, \mnras, 167, 31P
+
+\bibitem[{{Frayer} {et~al.}(1998){Frayer}, {Ivison}, {Scoville}, {Yun},
+  {Evans}, {Smail}, {Blain}, \& {Kneib}}]{Frayer98a}
+{Frayer}, D.~T., {Ivison}, R.~J., {Scoville}, N.~Z., {et~al.} 1998, \apjl, 506,
+  L7
+
+\bibitem[{{Gavazzi} {et~al.}(2011){Gavazzi}, {Cooray}, {Conley}, {Aguirre},
+  {Amblard}, {Auld}, {Beelen}, {Blain}, {Blundell}, {Bock}, {Bradford},
+  {Bridge}, {Brisbin}, {Burgarella}, {Chanial}, {Chapin}, {Christopher},
+  {Clements}, {Cox}, {Djorgovski}, {Dowell}, {Eales}, {Earle},
+  {Ellsworth-Bowers}, {Farrah}, {Franceschini}, {Fu}, {Glenn}, {Gonz{\'a}lez
+  Solares}, {Griffin}, {Gurwell}, {Halpern}, {Ibar}, {Ivison}, {Jarvis},
+  {Kamenetzky}, {Kim}, {Krips}, {Levenson}, {Lupu}, {Mahabal}, {Maloney},
+  {Maraston}, {Marchetti}, {Marsden}, {Matsuhara}, {Mortier}, {Murphy},
+  {Naylor}, {Neri}, {Nguyen}, {Oliver}, {Omont}, {Page}, {Papageorgiou},
+  {Pearson}, {P{\'e}rez-Fournon}, {Pohlen}, {Rangwala}, {Rawlings}, {Raymond},
+  {Riechers}, {Rodighiero}, {Roseboom}, {Rowan-Robinson}, {Schulz}, {Scott},
+  {Scott}, {Serra}, {Seymour}, {Shupe}, {Smith}, {Symeonidis}, {Tugwell},
+  {Vaccari}, {Valiante}, {Valtchanov}, {Verma}, {Vieira}, {Vigroux}, {Wang},
+  {Wardlow}, {Wiebe}, {Wright}, {Xu}, {Zeimann}, {Zemcov}, \&
+  {Zmuidzinas}}]{Gavazzi11a}
+{Gavazzi}, R., {Cooray}, A., {Conley}, A., {et~al.} 2011, \apj, 738, 125 (G11)
+
+\bibitem[{{Genzel} {et~al.}(2010){Genzel}, {Tacconi}, {Gracia-Carpio},
+  {Sternberg}, {Cooper}, {Shapiro}, {Bolatto}, {Bouch{\'e}}, {Bournaud},
+  {Burkert}, {Combes}, {Comerford}, {Cox}, {Davis}, {Schreiber},
+  {Garcia-Burillo}, {Lutz}, {Naab}, {Neri}, {Omont}, {Shapley}, \&
+  {Weiner}}]{Genzel10a}
+{Genzel}, R., {Tacconi}, L.~J., {Gracia-Carpio}, J., {et~al.} 2010, \mnras,
+  407, 2091
+
+\bibitem[{{Greve} {et~al.}(2005){Greve}, {Bertoldi}, {Smail}, {Neri},
+  {Chapman}, {Blain}, {Ivison}, {Genzel}, {Omont}, {Cox}, {Tacconi}, \&
+  {Kneib}}]{Greve05a}
+{Greve}, T.~R., {Bertoldi}, F., {Smail}, I., {et~al.} 2005, \mnras, 359, 1165
+
+\bibitem[{{Haas} {et~al.}(2014){Haas}, {Leipski}, {Barthel}, {Wilkes},
+  {Vegetti}, {Bussmann}, {Willner}, {Westhues}, {Ashby}, {Chini}, {Clements},
+  {Fassnacht}, {Horesh}, {Klaas}, {Koopmans}, {Kuraszkiewicz}, {Lagattuta},
+  {Meisenheimer}, {Stern}, \& {Wylezalek}}]{Haas14}
+{Haas}, M., {Leipski}, C., {Barthel}, P., {et~al.} 2014, \apj, 790, 46 (H14)
+
+\bibitem[{{Hales} {et~al.}(1995){Hales}, {Waldram}, {Rees}, \&
+  {Warner}}]{r33-34}
+{Hales}, S.~E.~G., {Waldram}, E.~M., {Rees}, N., \& {Warner}, P.~J. 1995,
+  \mnras, 274, 447
+
+\bibitem[{{Hardcastle} \& {Looney}(2008)}]{Hardcastle08a}
+{Hardcastle}, M.~J., \& {Looney}, L.~W. 2008, \mnras, 388, 176
+
+\bibitem[{{Harrison} {et~al.}(2015){Harrison}, {Simpson}, {Stanley},
+  {Alexander}, {Daddi}, {Mullaney}, {Pannella}, {Rosario}, \&
+  {Smail}}]{Harrison15a}
+{Harrison}, C.~M., {Simpson}, J.~M., {Stanley}, F., {et~al.} 2015, ArXiv
+  e-prints, arXiv:1510.06740
+
+\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
+  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
+  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
+  \& {Wright}}]{Hinshaw13a}
+{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {et~al.} 2013, \apjs, 208, 19
+
+\bibitem[{{Hodge} {et~al.}(2013){Hodge}, {Carilli}, {Walter}, {Daddi}, \&
+  {Riechers}}]{Hodge13a}
+{Hodge}, J.~A., {Carilli}, C.~L., {Walter}, F., {Daddi}, E., \& {Riechers}, D.
+  2013, \apj, 776, 22
+
+\bibitem[{{Hodge} {et~al.}(2015){Hodge}, {Riechers}, {Decarli}, {Walter},
+  {Carilli}, {Daddi}, \& {Dannerbauer}}]{Hodge15a}
+{Hodge}, J.~A., {Riechers}, D., {Decarli}, R., {et~al.} 2015, \apjl, 798, L18
+
+\bibitem[{{Ivison} {et~al.}(2011){Ivison}, {Papadopoulos}, {Smail}, {Greve},
+  {Thomson}, {Xilouris}, \& {Chapman}}]{Ivison11a}
+{Ivison}, R.~J., {Papadopoulos}, P.~P., {Smail}, I., {et~al.} 2011, \mnras,
+  412, 1913
+
+\bibitem[{{Ivison} {et~al.}(2010){Ivison}, {Swinbank}, {Swinyard}, {Smail},
+  {Pearson}, {Rigopoulou}, {Polehampton}, {Baluteau}, {Barlow}, {Blain},
+  {Bock}, {Clements}, {Coppin}, {Cooray}, {Danielson}, {Dwek}, {Edge},
+  {Franceschini}, {Fulton}, {Glenn}, {Griffin}, {Isaak}, {Leeks}, {Lim},
+  {Naylor}, {Oliver}, {Page}, {P{\'e}rez Fournon}, {Rowan-Robinson}, {Savini},
+  {Scott}, {Spencer}, {Valtchanov}, {Vigroux}, \& {Wright}}]{Ivison10c}
+{Ivison}, R.~J., {Swinbank}, A.~M., {Swinyard}, B., {et~al.} 2010, \aap, 518,
+  L35
+
+\bibitem[{{Kellermann} \& {Pauliny-Toth}(1973)}]{r9}
+{Kellermann}, K.~I., \& {Pauliny-Toth}, I.~I.~K. 1973, \aj, 78, 828
+
+\bibitem[{{Kellermann} \& {Pauliny-Toth}(1981)}]{Kellermann81a}
+---. 1981, \araa, 19, 373
+
+\bibitem[{{Kellermann} {et~al.}(1969){Kellermann}, {Pauliny-Toth}, \&
+  {Williams}}]{r11-14-18-22-25-32}
+{Kellermann}, K.~I., {Pauliny-Toth}, I.~I.~K., \& {Williams}, P.~J.~S. 1969,
+  \apj, 157, 1
+
+\bibitem[{{Kennicutt}(1998)}]{Kennicutt98a}
+{Kennicutt}, Jr., R.~C. 1998, \araa, 36, 189
+
+\bibitem[{{Lagache} {et~al.}(2005){Lagache}, {Puget}, \& {Dole}}]{Lagache05a}
+{Lagache}, G., {Puget}, J.-L., \& {Dole}, H. 2005, \araa, 43, 727
+
+\bibitem[{{Laing} \& {Peacock}(1980)}]{r10-13-15-19-20-26-29-31}
+{Laing}, R.~A., \& {Peacock}, J.~A. 1980, \mnras, 190, 903
+
+\bibitem[{{Meisenheimer} {et~al.}(1989){Meisenheimer}, {Roser}, {Hiltner},
+  {Yates}, {Longair}, {Chini}, \& {Perley}}]{Meisenheimer89a}
+{Meisenheimer}, K., {Roser}, H.-J., {Hiltner}, P.~R., {et~al.} 1989, \aap, 219,
+  63
+
+\bibitem[{{Micha{\l}owski} {et~al.}(2010){Micha{\l}owski}, {Watson}, \&
+  {Hjorth}}]{Micha10a}
+{Micha{\l}owski}, M.~J., {Watson}, D., \& {Hjorth}, J. 2010, \apj, 712, 942
+
+\bibitem[{{Mullin} {et~al.}(2006){Mullin}, {Hardcastle}, \&
+  {Riley}}]{Mullin06a}
+{Mullin}, L.~M., {Hardcastle}, M.~J., \& {Riley}, J.~M. 2006, \mnras, 372, 113
+
+\bibitem[{{Negrello} {et~al.}(2010){Negrello}, {Hopwood}, {De Zotti}, {Cooray},
+  {Verma}, {Bock}, {Frayer}, {Gurwell}, {Omont}, {Neri}, {Dannerbauer},
+  {Leeuw}, {Barton}, {Cooke}, {Kim}, {da Cunha}, {Rodighiero}, {Cox},
+  {Bonfield}, {Jarvis}, {Serjeant}, {Ivison}, {Dye}, {Aretxaga}, {Hughes},
+  {Ibar}, {Bertoldi}, {Valtchanov}, {Eales}, {Dunne}, {Driver}, {Auld},
+  {Buttiglione}, {Cava}, {Grady}, {Clements}, {Dariush}, {Fritz}, {Hill},
+  {Hornbeck}, {Kelvin}, {Lagache}, {Lopez-Caniego}, {Gonzalez-Nuevo}, {Maddox},
+  {Pascale}, {Pohlen}, {Rigby}, {Robotham}, {Simpson}, {Smith}, {Temi},
+  {Thompson}, {Woodgate}, {York}, {Aguirre}, {Beelen}, {Blain}, {Baker},
+  {Birkinshaw}, {Blundell}, {Bradford}, {Burgarella}, {Danese}, {Dunlop},
+  {Fleuren}, {Glenn}, {Harris}, {Kamenetzky}, {Lupu}, {Maddalena}, {Madore},
+  {Maloney}, {Matsuhara}, {Micha{\l}owski}, {Murphy}, {Naylor}, {Nguyen},
+  {Popescu}, {Rawlings}, {Rigopoulou}, {Scott}, {Scott}, {Seibert}, {Smail},
+  {Tuffs}, {Vieira}, {van der Werf}, \& {Zmuidzinas}}]{Negrello10a}
+{Negrello}, M., {Hopwood}, R., {De Zotti}, G., {et~al.} 2010, Science, 330, 800
+
+\bibitem[{{Neri} {et~al.}(2003){Neri}, {Genzel}, {Ivison}, {Bertoldi}, {Blain},
+  {Chapman}, {Cox}, {Greve}, {Omont}, \& {Frayer}}]{Neri03a}
+{Neri}, R., {Genzel}, R., {Ivison}, R.~J., {et~al.} 2003, \apjl, 597, L113
+
+\bibitem[{{Oliver} {et~al.}(2012){Oliver}, {Bock}, {Altieri}, {Amblard},
+  {Arumugam}, {Aussel}, {Babbedge}, {Beelen}, {B{\'e}thermin}, {Blain},
+  {Boselli}, {Bridge}, {Brisbin}, {Buat}, {Burgarella},
+  {Castro-Rodr{\'{\i}}guez}, {Cava}, {Chanial}, {Cirasuolo}, {Clements},
+  {Conley}, {Conversi}, {Cooray}, {Dowell}, {Dubois}, {Dwek}, {Dye}, {Eales},
+  {Elbaz}, {Farrah}, {Feltre}, {Ferrero}, {Fiolet}, {Fox}, {Franceschini},
+  {Gear}, {Giovannoli}, {Glenn}, {Gong}, {Gonz{\'a}lez Solares}, {Griffin},
+  {Halpern}, {Harwit}, {Hatziminaoglou}, {Heinis}, {Hurley}, {Hwang}, {Hyde},
+  {Ibar}, {Ilbert}, {Isaak}, {Ivison}, {Lagache}, {Le Floc'h}, {Levenson},
+  {Faro}, {Lu}, {Madden}, {Maffei}, {Magdis}, {Mainetti}, {Marchetti},
+  {Marsden}, {Marshall}, {Mortier}, {Nguyen}, {O'Halloran}, {Omont}, {Page},
+  {Panuzzo}, {Papageorgiou}, {Patel}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen},
+  {Rawlings}, {Raymond}, {Rigopoulou}, {Riguccini}, {Rizzo}, {Rodighiero},
+  {Roseboom}, {Rowan-Robinson}, {S{\'a}nchez Portal}, {Schulz}, {Scott},
+  {Seymour}, {Shupe}, {Smith}, {Stevens}, {Symeonidis}, {Trichas}, {Tugwell},
+  {Vaccari}, {Valtchanov}, {Vieira}, {Viero}, {Vigroux}, {Wang}, {Ward},
+  {Wardlow}, {Wright}, {Xu}, \& {Zemcov}}]{Oliver12a}
+{Oliver}, S.~J., {Bock}, J., {Altieri}, B., {et~al.} 2012, \mnras, 424, 1614
+
+\bibitem[{{Pauliny-Toth} {et~al.}(1966){Pauliny-Toth}, {Wade}, \&
+  {Heeschen}}]{r17-21}
+{Pauliny-Toth}, I.~I.~K., {Wade}, C.~M., \& {Heeschen}, D.~S. 1966, \apjs, 13,
+  65
+
+\bibitem[{{Polletta} {et~al.}(2011){Polletta}, {Nesvadba}, {Neri}, {Omont},
+  {Berta}, \& {Bergeron}}]{Polletta11a}
+{Polletta}, M., {Nesvadba}, N.~P.~H., {Neri}, R., {et~al.} 2011, \aap, 533, A20
+
+\bibitem[{{Rengelink} {et~al.}(1997){Rengelink}, {Tang}, {de Bruyn}, {Miley},
+  {Bremer}, {Roettgering}, \& {Bremer}}]{r23-24}
+{Rengelink}, R.~B., {Tang}, Y., {de Bruyn}, A.~G., {et~al.} 1997, \aaps, 124,
+  259
+
+\bibitem[{{Riechers} {et~al.}(2006){Riechers}, {Walter}, {Carilli}, {Knudsen},
+  {Lo}, {Benford}, {Staguhn}, {Hunter}, {Bertoldi}, {Henkel}, {Menten},
+  {Weiss}, {Yun}, \& {Scoville}}]{Riechers06a}
+{Riechers}, D.~A., {Walter}, F., {Carilli}, C.~L., {et~al.} 2006, \apj, 650,
+  604
+
+\bibitem[{{Riechers} {et~al.}(2011{\natexlab{a}}){Riechers}, {Hodge}, {Walter},
+  {Carilli}, \& {Bertoldi}}]{Riechers11c}
+{Riechers}, D.~A., {Hodge}, J., {Walter}, F., {Carilli}, C.~L., \& {Bertoldi},
+  F. 2011{\natexlab{a}}, \apjl, 739, L31
+
+\bibitem[{{Riechers} {et~al.}(2011{\natexlab{b}}){Riechers}, {Carilli},
+  {Walter}, {Weiss}, {Wagg}, {Bertoldi}, {Downes}, {Henkel}, \&
+  {Hodge}}]{Riechers11d}
+{Riechers}, D.~A., {Carilli}, L.~C., {Walter}, F., {et~al.} 2011{\natexlab{b}},
+  \apjl, 733, L11
+
+\bibitem[{{Riechers} {et~al.}(2011{\natexlab{c}}){Riechers}, {Carilli},
+  {Maddalena}, {Hodge}, {Harris}, {Baker}, {Walter}, {Wagg}, {Vanden Bout},
+  {Wei{\ss}}, \& {Sharon}}]{Riechers11a}
+{Riechers}, D.~A., {Carilli}, C.~L., {Maddalena}, R.~J., {et~al.}
+  2011{\natexlab{c}}, \apjl, 739, L32
+
+\bibitem[{{Riechers} {et~al.}(2011{\natexlab{d}}){Riechers}, {Cooray}, {Omont},
+  {Neri}, {Harris}, {Baker}, {Cox}, {Frayer}, {Carpenter}, {Auld}, {Aussel},
+  {Beelen}, {Blundell}, {Bock}, {Brisbin}, {Burgarella}, {Chanial}, {Chapman},
+  {Clements}, {Conley}, {Dowell}, {Eales}, {Farrah}, {Franceschini}, {Gavazzi},
+  {Glenn}, {Griffin}, {Gurwell}, {Ivison}, {Kim}, {Krips}, {Mortier}, {Oliver},
+  {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen}, {Rawlings},
+  {Raymond}, {Rodighiero}, {Roseboom}, {Rowan-Robinson}, {Scott}, {Seymour},
+  {Smith}, {Symeonidis}, {Tugwell}, {Vaccari}, {Vieira}, {Vigroux}, {Wang},
+  {Wardlow}, \& {Wright}}]{Riechers11b}
+{Riechers}, D.~A., {Cooray}, A., {Omont}, A., {et~al.} 2011{\natexlab{d}},
+  \apjl, 733, L12
+
+\bibitem[{{Riechers} {et~al.}(2013){Riechers}, {Bradford}, {Clements},
+  {Dowell}, {P{\'e}rez-Fournon}, {Ivison}, {Bridge}, {Conley}, {Fu}, {Vieira},
+  {Wardlow}, {Calanog}, {Cooray}, {Hurley}, {Neri}, {Kamenetzky}, {Aguirre},
+  {Altieri}, {Arumugam}, {Benford}, {B{\'e}thermin}, {Bock}, {Burgarella},
+  {Cabrera-Lavers}, {Chapman}, {Cox}, {Dunlop}, {Earle}, {Farrah}, {Ferrero},
+  {Franceschini}, {Gavazzi}, {Glenn}, {Solares}, {Gurwell}, {Halpern},
+  {Hatziminaoglou}, {Hyde}, {Ibar}, {Kov{\'a}cs}, {Krips}, {Lupu}, {Maloney},
+  {Martinez-Navajas}, {Matsuhara}, {Murphy}, {Naylor}, {Nguyen}, {Oliver},
+  {Omont}, {Page}, {Petitpas}, {Rangwala}, {Roseboom}, {Scott}, {Smith},
+  {Staguhn}, {Streblyanska}, {Thomson}, {Valtchanov}, {Viero}, {Wang},
+  {Zemcov}, \& {Zmuidzinas}}]{Riechers13a}
+{Riechers}, D.~A., {Bradford}, C.~M., {Clements}, D.~L., {et~al.} 2013, \nat,
+  496, 329
+
+\bibitem[{{Sanders} {et~al.}(1988){Sanders}, {Soifer}, {Elias}, {Madore},
+  {Matthews}, {Neugebauer}, \& {Scoville}}]{Sanders88}
+{Sanders}, D.~B., {Soifer}, B.~T., {Elias}, J.~H., {et~al.} 1988, \apj, 325, 74
+
+\bibitem[{{Scoville}(2013)}]{Scoville13a}
+{Scoville}, N.~Z. 2013, {Evolution of star formation and gas}, ed.
+  J.~{Falc{\'o}n-Barroso} \& J.~H. {Knapen}, 491
+
+\bibitem[{{Simpson} {et~al.}(2012){Simpson}, {Smail}, {Swinbank}, {Alexander},
+  {Auld}, {Baes}, {Bonfield}, {Clements}, {Cooray}, {Coppin}, {Danielson},
+  {Dariush}, {Dunne}, {de Zotti}, {Harrison}, {Hopwood}, {Hoyos}, {Ibar},
+  {Ivison}, {Jarvis}, {Lapi}, {Maddox}, {Page}, {Riechers}, {Valiante}, \& {van
+  der Werf}}]{Simpson12a}
+{Simpson}, J.~M., {Smail}, I., {Swinbank}, A.~M., {et~al.} 2012, \mnras, 426,
+  3201
+
+\bibitem[{{Simpson} {et~al.}(2015){Simpson}, {Smail}, {Swinbank}, {Almaini},
+  {Blain}, {Bremer}, {Chapman}, {Chen}, {Conselice}, {Coppin}, {Danielson},
+  {Dunlop}, {Edge}, {Farrah}, {Geach}, {Hartley}, {Ivison}, {Karim}, {Lani},
+  {Ma}, {Meijerink}, {Micha{\l}owski}, {Mortlock}, {Scott}, {Simpson},
+  {Spaans}, {Thomson}, {van Kampen}, \& {van der Werf}}]{Simpson15a}
+---. 2015, \apj, 799, 81
+
+\bibitem[{{Smol{\v c}i{\'c}} \& {Riechers}(2011)}]{Smolcic11a}
+{Smol{\v c}i{\'c}}, V., \& {Riechers}, D.~A. 2011, \apj, 730, 64
+
+\bibitem[{{Solomon} \& {Vanden Bout}(2005)}]{Solomon05a}
+{Solomon}, P.~M., \& {Vanden Bout}, P.~A. 2005, \araa, 43, 677
+
+\bibitem[{{Swinbank} {et~al.}(2010){Swinbank}, {Smail}, {Longmore}, {Harris},
+  {Baker}, {De Breuck}, {Richard}, {Edge}, {Ivison}, {Blundell}, {Coppin},
+  {Cox}, {Gurwell}, {Hainline}, {Krips}, {Lundgren}, {Neri}, {Siana},
+  {Siringo}, {Stark}, {Wilner}, \& {Younger}}]{Swinbank2010a}
+{Swinbank}, A.~M., {Smail}, I., {Longmore}, S., {et~al.} 2010, \nat, 464, 733
+
+\bibitem[{{Swinbank} {et~al.}(2011){Swinbank}, {Papadopoulos}, {Cox}, {Krips},
+  {Ivison}, {Smail}, {Thomson}, {Neri}, {Richard}, \& {Ebeling}}]{Swinbank11a}
+{Swinbank}, A.~M., {Papadopoulos}, P.~P., {Cox}, P., {et~al.} 2011, \apj, 742,
+  11
+
+\bibitem[{{Tacconi} {et~al.}(2006){Tacconi}, {Neri}, {Chapman}, {Genzel},
+  {Smail}, {Ivison}, {Bertoldi}, {Blain}, {Cox}, {Greve}, \&
+  {Omont}}]{Tacconi06a}
+{Tacconi}, L.~J., {Neri}, R., {Chapman}, S.~C., {et~al.} 2006, \apj, 640, 228
+
+\bibitem[{{Tacconi} {et~al.}(2008){Tacconi}, {Genzel}, {Smail}, {Neri},
+  {Chapman}, {Ivison}, {Blain}, {Cox}, {Omont}, {Bertoldi}, {Greve},
+  {F{\"o}rster Schreiber}, {Genel}, {Lutz}, {Swinbank}, {Shapley}, {Erb},
+  {Cimatti}, {Daddi}, \& {Baker}}]{Tacconi08a}
+{Tacconi}, L.~J., {Genzel}, R., {Smail}, I., {et~al.} 2008, \apj, 680, 246
+
+\bibitem[{{Vieira} {et~al.}(2010){Vieira}, {Crawford}, {Switzer}, {Ade},
+  {Aird}, {Ashby}, {Benson}, {Bleem}, {Brodwin}, {Carlstrom}, {Chang}, {Cho},
+  {Crites}, {de Haan}, {Dobbs}, {Everett}, {George}, {Gladders}, {Hall},
+  {Halverson}, {High}, {Holder}, {Holzapfel}, {Hrubes}, {Joy}, {Keisler},
+  {Knox}, {Lee}, {Leitch}, {Lueker}, {Marrone}, {McIntyre}, {McMahon}, {Mehl},
+  {Meyer}, {Mohr}, {Montroy}, {Padin}, {Plagge}, {Pryke}, {Reichardt}, {Ruhl},
+  {Schaffer}, {Shaw}, {Shirokoff}, {Spieler}, {Stalder}, {Staniszewski},
+  {Stark}, {Vanderlinde}, {Walsh}, {Williamson}, {Yang}, {Zahn}, \&
+  {Zenteno}}]{Vieira10a}
+{Vieira}, J.~D., {Crawford}, T.~M., {Switzer}, E.~R., {et~al.} 2010, \apj, 719,
+  763
+
+\bibitem[{{Wilson} {et~al.}(1970){Wilson}, {Jefferts}, \&
+  {Penzias}}]{Wilson70a}
+{Wilson}, R.~W., {Jefferts}, K.~B., \& {Penzias}, A.~A. 1970, \apjl, 161, L43
+
+\end{thebibliography}
 
@@
 \end{turnpage}
-
-%\begin{thebibliography}
-
-%\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
-%
-%\bibitem[{{Baldwin} {et~al.}(1985){Baldwin}, {Boysen}, {Hales}, {Jennings},
-%  {Waggett}, {Warner}, \& {Wilson}}]{r2728}
-%{Baldwin}, J.~E., {Boysen}, R.~C., {Hales}, S.~E.~G., {et~al.} 1985, \mnras,
-%  217, 717
-%
-%\bibitem[{{Begelman} {et~al.}(1984){Begelman}, {Blandford}, \&
-%  {Rees}}]{Begelman84a}
-%{Begelman}, M.~C., {Blandford}, R.~D., \& {Rees}, M.~J. 1984, Reviews of Modern
-%  Physics, 56, 255
-%
-%\bibitem[{{Blain} {et~al.}(2002){Blain}, {Smail}, {Ivison}, {Kneib}, \&
-%  {Frayer}}]{blain02a}
-%{Blain}, A.~W., {Smail}, I., {Ivison}, R.~J., {Kneib}, J.-P., \& {Frayer},
-%  D.~T. 2002, \physrep, 369, 111
-%
-%\bibitem[{{Bothwell} {et~al.}(2013){Bothwell}, {Smail}, {Chapman}, {Genzel},
-%  {Ivison}, {Tacconi}, {Alaghband-Zadeh}, {Bertoldi}, {Blain}, {Casey}, {Cox},
-%  {Greve}, {Lutz}, {Neri}, {Omont}, \& {Swinbank}}]{Bothwell13a}
-%{Bothwell}, M.~S., {Smail}, I., {Chapman}, S.~C., {et~al.} 2013, \mnras, 429,
-%  3047
-%
-%\bibitem[{{Bouch{\'e}} {et~al.}(2007){Bouch{\'e}}, {Cresci}, {Davies},
-%  {Eisenhauer}, {F{\"o}rster Schreiber}, {Genzel}, {Gillessen}, {Lehnert},
-%  {Lutz}, {Nesvadba}, {Shapiro}, {Sternberg}, {Tacconi}, {Verma}, {Cimatti},
-%  {Daddi}, {Renzini}, {Erb}, {Shapley}, \& {Steidel}}]{B07a}
-%{Bouch{\'e}}, N., {Cresci}, G., {Davies}, R., {et~al.} 2007, \apj, 671, 303
-%
-%\bibitem[{{Bussmann} {et~al.}(2015){Bussmann}, {Riechers}, {Fialkov},
-%  {Scudder}, {Hayward}, {Cowley}, {Bock}, {Calanog}, {Chapman}, {Cooray}, {De
-%  Bernardis}, {Farrah}, {Fu}, {Gavazzi}, {Hopwood}, {Ivison}, {Jarvis},
-%  {Lacey}, {Loeb}, {Oliver}, {Perez-Fournon}, {Rigopoulou}, {Roseboom},
-%  {Scott}, {Smith}, {Vieira}, {Wang}, \& {Wardlow}}]{Bussmann15a}
-%{Bussmann}, R.~S., {Riechers}, D., {Fialkov}, A., {et~al.} 2015, ArXiv
-%  e-prints, arXiv:1504.05256
-%
-%\bibitem[{{Carilli} \& {Walter}(2013)}]{Carilli13a}
-%{Carilli}, C.~L., \& {Walter}, F. 2013, \araa, 51, 105
-%
-%\bibitem[{{Carilli} {et~al.}(2010){Carilli}, {Daddi}, {Riechers}, {Walter},
-%  {Weiss}, {Dannerbauer}, {Morrison}, {Wagg}, {Dav{\'e}}, {Elbaz}, {Stern},
-%  {Dickinson}, {Krips}, \& {Aravena}}]{Carilli10a}
-%{Carilli}, C.~L., {Daddi}, E., {Riechers}, D., {et~al.} 2010, \apj, 714, 1407
-%
-%\bibitem[{{Carlstrom} {et~al.}(2011){Carlstrom}, {Ade}, {Aird}, {Benson},
-%  {Bleem}, {Busetti}, {Chang}, {Chauvin}, {Cho}, {Crawford}, {Crites}, {Dobbs},
-%  {Halverson}, {Heimsath}, {Holzapfel}, {Hrubes}, {Joy}, {Keisler}, {Lanting},
-%  {Lee}, {Leitch}, {Leong}, {Lu}, {Lueker}, {Luong-van}, {McMahon}, {Mehl},
-%  {Meyer}, {Mohr}, {Montroy}, {Padin}, {Plagge}, {Pryke}, {Ruhl}, {Schaffer},
-%  {Schwan}, {Shirokoff}, {Spieler}, {Staniszewski}, {Stark}, {Tucker},
-%  {Vanderlinde}, {Vieira}, \& {Williamson}}]{Carlstrom11a}
-%{Carlstrom}, J.~E., {Ade}, P.~A.~R., {Aird}, K.~A., {et~al.} 2011, \pasp, 123,
-%  568
-%  
-%\bibitem[{{Casey}(2012)}]{Casey12a}
-%{Casey}, C.~M. 2012, \mnras, 425, 3094
-%
-%\bibitem[{{Casey} {et~al.}(2014){Casey}, {Narayanan}, \& {Cooray}}]{Casey14a}
-%{Casey}, C.~M., {Narayanan}, D., \& {Cooray}, A. 2014, \physrep, 541, 45
-%
-%\bibitem[{{Chabrier}(2003)}]{Chabrier03a}
-%{Chabrier}, G. 2003, \pasp, 115, 763
-%
-%\bibitem[{{Cleary} {et~al.}(2007){Cleary}, {Lawrence}, {Marshall}, {Hao}, \&
-%  {Meier}}]{Cleary07a}
-%{Cleary}, K., {Lawrence}, C.~R., {Marshall}, J.~A., {Hao}, L., \& {Meier}, D.
-%  2007, \apj, 660, 117
-%
-%\bibitem[{{Cohen} {et~al.}(2007){Cohen}, {Lane}, {Cotton}, {Kassim}, {Lazio},
-%  {Perley}, {Condon}, \& {Erickson}}]{r30}
-%{Cohen}, A.~S., {Lane}, W.~M., {Cotton}, W.~D., {et~al.} 2007, \aj, 134, 1245
-%
-%\bibitem[{{Condon} {et~al.}(1998){Condon}, {Cotton}, {Greisen}, {Yin},
-%  {Perley}, {Taylor}, \& {Broderick}}]{r16}
-%{Condon}, J.~J., {Cotton}, W.~D., {Greisen}, E.~W., {et~al.} 1998, \aj, 115,
-%  1693
-%
-%\bibitem[{{Conley} {et~al.}(2011){Conley}, {Cooray}, {Vieira}, {Gonz{\'a}lez
-%  Solares}, {Kim}, {Aguirre}, {Amblard}, {Auld}, {Baker}, {Beelen}, {Blain},
-%  {Blundell}, {Bock}, {Bradford}, {Bridge}, {Brisbin}, {Burgarella},
-%  {Carpenter}, {Chanial}, {Chapin}, {Christopher}, {Clements}, {Cox},
-%  {Djorgovski}, {Dowell}, {Eales}, {Earle}, {Ellsworth-Bowers}, {Farrah},
-%  {Franceschini}, {Frayer}, {Fu}, {Gavazzi}, {Glenn}, {Griffin}, {Gurwell},
-%  {Halpern}, {Ibar}, {Ivison}, {Jarvis}, {Kamenetzky}, {Krips}, {Levenson},
-%  {Lupu}, {Mahabal}, {Maloney}, {Maraston}, {Marchetti}, {Marsden},
-%  {Matsuhara}, {Mortier}, {Murphy}, {Naylor}, {Neri}, {Nguyen}, {Oliver},
-%  {Omont}, {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen},
-%  {Rangwala}, {Rawlings}, {Raymond}, {Riechers}, {Rodighiero}, {Roseboom},
-%  {Rowan-Robinson}, {Schulz}, {Scott}, {Scott}, {Serra}, {Seymour}, {Shupe},
-%  {Smith}, {Symeonidis}, {Tugwell}, {Vaccari}, {Valiante}, {Valtchanov},
-%  {Verma}, {Viero}, {Vigroux}, {Wang}, {Wiebe}, {Wright}, {Xu}, {Zeimann},
-%  {Zemcov}, \& {Zmuidzinas}}]{Conley11a}
-%{Conley}, A., {Cooray}, A., {Vieira}, J.~D., {et~al.} 2011, \apjl, 732, L35
-%
-%\bibitem[{{Coppin} {et~al.}(2008){Coppin}, {Swinbank}, {Neri}, {Cox},
-%  {Alexander}, {Smail}, {Page}, {Stevens}, {Knudsen}, {Ivison}, {Beelen},
-%  {Bertoldi}, \& {Omont}}]{Coppin08a}
-%{Coppin}, K.~E.~K., {Swinbank}, A.~M., {Neri}, R., {et~al.} 2008, \mnras, 389,
-%  45
-%
-%\bibitem[{{Danielson} {et~al.}(2011){Danielson}, {Swinbank}, {Smail}, {Cox},
-%  {Edge}, {Weiss}, {Harris}, {Baker}, {De Breuck}, {Geach}, {Ivison}, {Krips},
-%  {Lundgren}, {Longmore}, {Neri}, \& {Flaquer}}]{Danielson11a}
-%{Danielson}, A.~L.~R., {Swinbank}, A.~M., {Smail}, I., {et~al.} 2011, \mnras,
-%  410, 1687
-%
-%\bibitem[{{Deane} {et~al.}(2013){Deane}, {Heywood}, {Rawlings}, \&
-%  {Marshall}}]{Deane13a}
-%{Deane}, R.~P., {Heywood}, I., {Rawlings}, S., \& {Marshall}, P.~J. 2013,
-%  \mnras, 434, 23
-%
-%\bibitem[{{Dickinson} {et~al.}(2003){Dickinson}, {Papovich}, {Ferguson}, \&
-%  {Budav{\'a}ri}}]{Dickinson03a}
-%{Dickinson}, M., {Papovich}, C., {Ferguson}, H.~C., \& {Budav{\'a}ri}, T. 2003,
-%  \apj, 587, 25
-%
-%\bibitem[{{Dowell} {et~al.}(2014){Dowell}, {Conley}, {Glenn}, {Arumugam},
-%  {Asboth}, {Aussel}, {Bertoldi}, {B{\'e}thermin}, {Bock}, {Boselli}, {Bridge},
-%  {Buat}, {Burgarella}, {Cabrera-Lavers}, {Casey}, {Chapman}, {Clements},
-%  {Conversi}, {Cooray}, {Dannerbauer}, {De Bernardis}, {Ellsworth-Bowers},
-%  {Farrah}, {Franceschini}, {Griffin}, {Gurwell}, {Halpern}, {Hatziminaoglou},
-%  {Heinis}, {Ibar}, {Ivison}, {Laporte}, {Marchetti},
-%  {Mart{\'{\i}}nez-Navajas}, {Marsden}, {Morrison}, {Nguyen}, {O'Halloran},
-%  {Oliver}, {Omont}, {Page}, {Papageorgiou}, {Pearson}, {Petitpas},
-%  {P{\'e}rez-Fournon}, {Pohlen}, {Riechers}, {Rigopoulou}, {Roseboom},
-%  {Rowan-Robinson}, {Sayers}, {Schulz}, {Scott}, {Seymour}, {Shupe}, {Smith},
-%  {Streblyanska}, {Symeonidis}, {Vaccari}, {Valtchanov}, {Vieira}, {Viero},
-%  {Wang}, {Wardlow}, {Xu}, \& {Zemcov}}]{Dowell14a}
-%{Dowell}, C.~D., {Conley}, A., {Glenn}, J., {et~al.} 2014, \apj, 780, 75
-%
-%\bibitem[{{Downes} \& {Solomon}(1998)}]{Downes98a}
-%{Downes}, D., \& {Solomon}, P.~M. 1998, \apj, 507, 615
-%
-%\bibitem[{{Dunne} {et~al.}(2003){Dunne}, {Eales}, \& {Edmunds}}]{Dunne03a}
-%{Dunne}, L., {Eales}, S.~A., \& {Edmunds}, M.~G. 2003, \mnras, 341, 589
-%
-%\bibitem[{{Eales} {et~al.}(2010){Eales}, {Dunne}, {Clements}, {Cooray}, {de
-%  Zotti}, {Dye}, {Ivison}, {Jarvis}, {Lagache}, {Maddox}, {Negrello},
-%  {Serjeant}, {Thompson}, {van Kampen}, {Amblard}, {Andreani}, {Baes},
-%  {Beelen}, {Bendo}, {Benford}, {Bertoldi}, {Bock}, {Bonfield}, {Boselli},
-%  {Bridge}, {Buat}, {Burgarella}, {Carlberg}, {Cava}, {Chanial}, {Charlot},
-%  {Christopher}, {Coles}, {Cortese}, {Dariush}, {da Cunha}, {Dalton}, {Danese},
-%  {Dannerbauer}, {Driver}, {Dunlop}, {Fan}, {Farrah}, {Frayer}, {Frenk},
-%  {Geach}, {Gardner}, {Gomez}, {Gonz{\'a}lez-Nuevo}, {Gonz{\'a}lez-Solares},
-%  {Griffin}, {Hardcastle}, {Hatziminaoglou}, {Herranz}, {Hughes}, {Ibar},
-%  {Jeong}, {Lacey}, {Lapi}, {Lawrence}, {Lee}, {Leeuw}, {Liske},
-%  {L{\'o}pez-Caniego}, {M{\"u}ller}, {Nandra}, {Panuzzo}, {Papageorgiou},
-%  {Patanchon}, {Peacock}, {Pearson}, {Phillipps}, {Pohlen}, {Popescu},
-%  {Rawlings}, {Rigby}, {Rigopoulou}, {Robotham}, {Rodighiero}, {Sansom},
-%  {Schulz}, {Scott}, {Smith}, {Sibthorpe}, {Smail}, {Stevens}, {Sutherland},
-%  {Takeuchi}, {Tedds}, {Temi}, {Tuffs}, {Trichas}, {Vaccari}, {Valtchanov},
-%  {van der Werf}, {Verma}, {Vieria}, {Vlahakis}, \& {White}}]{Eales10a}
-%{Eales}, S., {Dunne}, L., {Clements}, D., {et~al.} 2010, \pasp, 122, 499
-%
-%\bibitem[{{Engel} {et~al.}(2010){Engel}, {Tacconi}, {Davies}, {Neri}, {Smail},
-%  {Chapman}, {Genzel}, {Cox}, {Greve}, {Ivison}, {Blain}, {Bertoldi}, \&
-%  {Omont}}]{Engel10a}
-%{Engel}, H., {Tacconi}, L.~J., {Davies}, R.~I., {et~al.} 2010, \apj, 724, 233
-%
-%\bibitem[{{Fanaroff} \& {Riley}(1974)}]{Fanaroff74}
-%{Fanaroff}, B.~L., \& {Riley}, J.~M. 1974, \mnras, 167, 31P
-%
-%\bibitem[{{Gavazzi} {et~al.}(2011){Gavazzi}, {Cooray}, {Conley}, {Aguirre},
-%  {Amblard}, {Auld}, {Beelen}, {Blain}, {Blundell}, {Bock}, {Bradford},
-%  {Bridge}, {Brisbin}, {Burgarella}, {Chanial}, {Chapin}, {Christopher},
-%  {Clements}, {Cox}, {Djorgovski}, {Dowell}, {Eales}, {Earle},
-%  {Ellsworth-Bowers}, {Farrah}, {Franceschini}, {Fu}, {Glenn}, {Gonz{\'a}lez
-%  Solares}, {Griffin}, {Gurwell}, {Halpern}, {Ibar}, {Ivison}, {Jarvis},
-%  {Kamenetzky}, {Kim}, {Krips}, {Levenson}, {Lupu}, {Mahabal}, {Maloney},
-%  {Maraston}, {Marchetti}, {Marsden}, {Matsuhara}, {Mortier}, {Murphy},
-%  {Naylor}, {Neri}, {Nguyen}, {Oliver}, {Omont}, {Page}, {Papageorgiou},
-%  {Pearson}, {P{\'e}rez-Fournon}, {Pohlen}, {Rangwala}, {Rawlings}, {Raymond},
-%  {Riechers}, {Rodighiero}, {Roseboom}, {Rowan-Robinson}, {Schulz}, {Scott},
-%  {Scott}, {Serra}, {Seymour}, {Shupe}, {Smith}, {Symeonidis}, {Tugwell},
-%  {Vaccari}, {Valiante}, {Valtchanov}, {Verma}, {Vieira}, {Vigroux}, {Wang},
-%  {Wardlow}, {Wiebe}, {Wright}, {Xu}, {Zeimann}, {Zemcov}, \&
-%  {Zmuidzinas}}]{Gavazzi11a}
-%{Gavazzi}, R., {Cooray}, A., {Conley}, A., {et~al.} 2011, \apj, 738, 125
-%
-%\bibitem[{{Greve} {et~al.}(2005){Greve}, {Bertoldi}, {Smail}, {Neri},
-%  {Chapman}, {Blain}, {Ivison}, {Genzel}, {Omont}, {Cox}, {Tacconi}, \&
-%  {Kneib}}]{Greve05a}
-%{Greve}, T.~R., {Bertoldi}, F., {Smail}, I., {et~al.} 2005, \mnras, 359, 1165
-%
-%\bibitem[{{Haas} {et~al.}(2014){Haas}, {Leipski}, {Barthel}, {Wilkes},
-%  {Vegetti}, {Bussmann}, {Willner}, {Westhues}, {Ashby}, {Chini}, {Clements},
-%  {Fassnacht}, {Horesh}, {Klaas}, {Koopmans}, {Kuraszkiewicz}, {Lagattuta},
-%  {Meisenheimer}, {Stern}, \& {Wylezalek}}]{Haas14}
-%{Haas}, M., {Leipski}, C., {Barthel}, P., {et~al.} 2014, \apj, 790, 46 (H14)
-%
-%\bibitem[{{Hales} {et~al.}(1995){Hales}, {Waldram}, {Rees}, \&
-%  {Warner}}]{r33-34}
-%{Hales}, S.~E.~G., {Waldram}, E.~M., {Rees}, N., \& {Warner}, P.~J. 1995,
-%  \mnras, 274, 447
-%
-%\bibitem[{{Hardcastle} \& {Looney}(2008)}]{Hardcastle08a}
-%{Hardcastle}, M.~J., \& {Looney}, L.~W. 2008, \mnras, 388, 176
-%
-%\bibitem[{{Harris} {et~al.}(2010){Harris}, {Baker}, {Zonak}, {Sharon},
-%  {Genzel}, {Rauch}, {Watts}, \& {Creager}}]{Harris10a}
-%{Harris}, A.~I., {Baker}, A.~J., {Zonak}, S.~G., {et~al.} 2010, \apj, 723, 1139
-%
-%\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
-%  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
-%  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
-%  \& {Wright}}]{Hinshaw13a}
-%{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {et~al.} 2013, \apjs, 208, 19
-%
-%\bibitem[{{Ivison} {et~al.}(2011){Ivison}, {Papadopoulos}, {Smail}, {Greve},
-%  {Thomson}, {Xilouris}, \& {Chapman}}]{Ivison11a}
-%{Ivison}, R.~J., {Papadopoulos}, P.~P., {Smail}, I., {et~al.} 2011, \mnras,
-%  412, 1913
-%
-%\bibitem[{{Ivison} {et~al.}(2010{\natexlab{a}}){Ivison}, {Smail},
-%  {Papadopoulos}, {Wold}, {Richard}, {Swinbank}, {Kneib}, \&
-%  {Owen}}]{Ivison10d}
-%{Ivison}, R.~J., {Smail}, I., {Papadopoulos}, P.~P., {et~al.}
-%  2010{\natexlab{a}}, \mnras, 404, 198
-%
-%\bibitem[{{Ivison} {et~al.}(2010{\natexlab{b}}){Ivison}, {Swinbank},
-%  {Swinyard}, {Smail}, {Pearson}, {Rigopoulou}, {Polehampton}, {Baluteau},
-%  {Barlow}, {Blain}, {Bock}, {Clements}, {Coppin}, {Cooray}, {Danielson},
-%  {Dwek}, {Edge}, {Franceschini}, {Fulton}, {Glenn}, {Griffin}, {Isaak},
-%  {Leeks}, {Lim}, {Naylor}, {Oliver}, {Page}, {P{\'e}rez Fournon},
-%  {Rowan-Robinson}, {Savini}, {Scott}, {Spencer}, {Valtchanov}, {Vigroux}, \&
-%  {Wright}}]{Ivison10c}
-%{Ivison}, R.~J., {Swinbank}, A.~M., {Swinyard}, B., {et~al.}
-%  2010{\natexlab{b}}, \aap, 518, L35
-%
-%\bibitem[{{Kellermann} \& {Pauliny-Toth}(1973)}]{r9}
-%{Kellermann}, K.~I., \& {Pauliny-Toth}, I.~I.~K. 1973, \aj, 78, 828
-%
-%\bibitem[{{Kellermann} \& {Pauliny-Toth}(1981)}]{Kellermann81a}
-%---. 1981, \araa, 19, 373
-%
-%\bibitem[{{Kellermann} {et~al.}(1969){Kellermann}, {Pauliny-Toth}, \&
-%  {Williams}}]{r11-14-18-22-25-32}
-%{Kellermann}, K.~I., {Pauliny-Toth}, I.~I.~K., \& {Williams}, P.~J.~S. 1969,
-%  \apj, 157, 1
-%
-%\bibitem[{{Kennicutt}(1998)}]{Kennicutt98a}
-%{Kennicutt}, Jr., R.~C. 1998, \araa, 36, 189
-%
-%\bibitem[{{Lagache} {et~al.}(2005){Lagache}, {Puget}, \& {Dole}}]{Lagache05a}
-%{Lagache}, G., {Puget}, J.-L., \& {Dole}, H. 2005, \araa, 43, 727
-%
-%\bibitem[{{Laing} \& {Peacock}(1980)}]{r10-13-15-19-20-26-29-31}
-%{Laing}, R.~A., \& {Peacock}, J.~A. 1980, \mnras, 190, 903
-%
-%\bibitem[{{Meisenheimer} {et~al.}(1989){Meisenheimer}, {Roser}, {Hiltner},
-%  {Yates}, {Longair}, {Chini}, \& {Perley}}]{Meisenheimer89a}
-%{Meisenheimer}, K., {Roser}, H.-J., {Hiltner}, P.~R., {et~al.} 1989, \aap, 219,
-%  63
-%
-%\bibitem[{{Micha{\l}owski} {et~al.}(2010){Micha{\l}owski}, {Watson}, \&
-%  {Hjorth}}]{Micha10a}
-%{Micha{\l}owski}, M.~J., {Watson}, D., \& {Hjorth}, J. 2010, \apj, 712, 942
-%
-%\bibitem[{{Mullin} {et~al.}(2006){Mullin}, {Hardcastle}, \&
-%  {Riley}}]{Mullin06a}
-%{Mullin}, L.~M., {Hardcastle}, M.~J., \& {Riley}, J.~M. 2006, \mnras, 372, 113
-%
-%\bibitem[{{Negrello} {et~al.}(2010){Negrello}, {Hopwood}, {De Zotti}, {Cooray},
-%  {Verma}, {Bock}, {Frayer}, {Gurwell}, {Omont}, {Neri}, {Dannerbauer},
-%  {Leeuw}, {Barton}, {Cooke}, {Kim}, {da Cunha}, {Rodighiero}, {Cox},
-%  {Bonfield}, {Jarvis}, {Serjeant}, {Ivison}, {Dye}, {Aretxaga}, {Hughes},
-%  {Ibar}, {Bertoldi}, {Valtchanov}, {Eales}, {Dunne}, {Driver}, {Auld},
-%  {Buttiglione}, {Cava}, {Grady}, {Clements}, {Dariush}, {Fritz}, {Hill},
-%  {Hornbeck}, {Kelvin}, {Lagache}, {Lopez-Caniego}, {Gonzalez-Nuevo}, {Maddox},
-%  {Pascale}, {Pohlen}, {Rigby}, {Robotham}, {Simpson}, {Smith}, {Temi},
-%  {Thompson}, {Woodgate}, {York}, {Aguirre}, {Beelen}, {Blain}, {Baker},
-%  {Birkinshaw}, {Blundell}, {Bradford}, {Burgarella}, {Danese}, {Dunlop},
-%  {Fleuren}, {Glenn}, {Harris}, {Kamenetzky}, {Lupu}, {Maddalena}, {Madore},
-%  {Maloney}, {Matsuhara}, {Micha{\l}owski}, {Murphy}, {Naylor}, {Nguyen},
-%  {Popescu}, {Rawlings}, {Rigopoulou}, {Scott}, {Scott}, {Seibert}, {Smail},
-%  {Tuffs}, {Vieira}, {van der Werf}, \& {Zmuidzinas}}]{Negrello10a}
-%{Negrello}, M., {Hopwood}, R., {De Zotti}, G., {et~al.} 2010, Science, 330, 800
-%
-%\bibitem[{{Oliver} {et~al.}(2012){Oliver}, {Bock}, {Altieri}, {Amblard},
-%  {Arumugam}, {Aussel}, {Babbedge}, {Beelen}, {B{\'e}thermin}, {Blain},
-%  {Boselli}, {Bridge}, {Brisbin}, {Buat}, {Burgarella},
-%  {Castro-Rodr{\'{\i}}guez}, {Cava}, {Chanial}, {Cirasuolo}, {Clements},
-%  {Conley}, {Conversi}, {Cooray}, {Dowell}, {Dubois}, {Dwek}, {Dye}, {Eales},
-%  {Elbaz}, {Farrah}, {Feltre}, {Ferrero}, {Fiolet}, {Fox}, {Franceschini},
-%  {Gear}, {Giovannoli}, {Glenn}, {Gong}, {Gonz{\'a}lez Solares}, {Griffin},
-%  {Halpern}, {Harwit}, {Hatziminaoglou}, {Heinis}, {Hurley}, {Hwang}, {Hyde},
-%  {Ibar}, {Ilbert}, {Isaak}, {Ivison}, {Lagache}, {Le Floc'h}, {Levenson},
-%  {Faro}, {Lu}, {Madden}, {Maffei}, {Magdis}, {Mainetti}, {Marchetti},
-%  {Marsden}, {Marshall}, {Mortier}, {Nguyen}, {O'Halloran}, {Omont}, {Page},
-%  {Panuzzo}, {Papageorgiou}, {Patel}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen},
-%  {Rawlings}, {Raymond}, {Rigopoulou}, {Riguccini}, {Rizzo}, {Rodighiero},
-%  {Roseboom}, {Rowan-Robinson}, {S{\'a}nchez Portal}, {Schulz}, {Scott},
-%  {Seymour}, {Shupe}, {Smith}, {Stevens}, {Symeonidis}, {Trichas}, {Tugwell},
-%  {Vaccari}, {Valtchanov}, {Vieira}, {Viero}, {Vigroux}, {Wang}, {Ward},
-%  {Wardlow}, {Wright}, {Xu}, \& {Zemcov}}]{Oliver12a}
-%{Oliver}, S.~J., {Bock}, J., {Altieri}, B., {et~al.} 2012, \mnras, 424, 1614
-%
-%\bibitem[{{Pauliny-Toth} {et~al.}(1966){Pauliny-Toth}, {Wade}, \&
-%  {Heeschen}}]{r17-21}
-%{Pauliny-Toth}, I.~I.~K., {Wade}, C.~M., \& {Heeschen}, D.~S. 1966, \apjs, 13,
-%  65
-%
-%\bibitem[{{Polletta} {et~al.}(2011){Polletta}, {Nesvadba}, {Neri}, {Omont},
-%  {Berta}, \& {Bergeron}}]{Polletta11a}
-%{Polletta}, M., {Nesvadba}, N.~P.~H., {Neri}, R., {et~al.} 2011, \aap, 533, A20
-%
-%\bibitem[{{Rengelink} {et~al.}(1997){Rengelink}, {Tang}, {de Bruyn}, {Miley},
-%  {Bremer}, {Roettgering}, \& {Bremer}}]{r23-24}
-%{Rengelink}, R.~B., {Tang}, Y., {de Bruyn}, A.~G., {et~al.} 1997, \aaps, 124,
-%  259
-%
-%\bibitem[{{Riechers} {et~al.}(2006){Riechers}, {Walter}, {Carilli}, {Knudsen},
-%  {Lo}, {Benford}, {Staguhn}, {Hunter}, {Bertoldi}, {Henkel}, {Menten},
-%  {Weiss}, {Yun}, \& {Scoville}}]{Riechers06a}
-%{Riechers}, D.~A., {Walter}, F., {Carilli}, C.~L., {et~al.} 2006, \apj, 650,
-%  604
-%
-%\bibitem[{{Riechers} {et~al.}(2011{\natexlab{a}}){Riechers}, {Hodge}, {Walter},
-%  {Carilli}, \& {Bertoldi}}]{Riechers11c}
-%{Riechers}, D.~A., {Hodge}, J., {Walter}, F., {Carilli}, C.~L., \& {Bertoldi},
-%  F. 2011{\natexlab{a}}, \apjl, 739, L31
-%
-%\bibitem[{{Riechers} {et~al.}(2011{\natexlab{b}}){Riechers}, {Carilli},
-%  {Walter}, {Weiss}, {Wagg}, {Bertoldi}, {Downes}, {Henkel}, \&
-%  {Hodge}}]{Riechers11d}
-%{Riechers}, D.~A., {Carilli}, L.~C., {Walter}, F., {et~al.} 2011{\natexlab{b}},
-%  \apjl, 733, L11
-%
-%\bibitem[{{Riechers} {et~al.}(2011{\natexlab{c}}){Riechers}, {Carilli},
-%  {Maddalena}, {Hodge}, {Harris}, {Baker}, {Walter}, {Wagg}, {Vanden Bout},
-%  {Wei{\ss}}, \& {Sharon}}]{Riechers11a}
-%{Riechers}, D.~A., {Carilli}, C.~L., {Maddalena}, R.~J., {et~al.}
-%  2011{\natexlab{c}}, \apjl, 739, L32
-%
-%\bibitem[{{Riechers} {et~al.}(2011{\natexlab{d}}){Riechers}, {Cooray}, {Omont},
-%  {Neri}, {Harris}, {Baker}, {Cox}, {Frayer}, {Carpenter}, {Auld}, {Aussel},
-%  {Beelen}, {Blundell}, {Bock}, {Brisbin}, {Burgarella}, {Chanial}, {Chapman},
-%  {Clements}, {Conley}, {Dowell}, {Eales}, {Farrah}, {Franceschini}, {Gavazzi},
-%  {Glenn}, {Griffin}, {Gurwell}, {Ivison}, {Kim}, {Krips}, {Mortier}, {Oliver},
-%  {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen}, {Rawlings},
-%  {Raymond}, {Rodighiero}, {Roseboom}, {Rowan-Robinson}, {Scott}, {Seymour},
-%  {Smith}, {Symeonidis}, {Tugwell}, {Vaccari}, {Vieira}, {Vigroux}, {Wang},
-%  {Wardlow}, \& {Wright}}]{Riechers11b}
-%{Riechers}, D.~A., {Cooray}, A., {Omont}, A., {et~al.} 2011{\natexlab{d}},
-%  \apjl, 733, L12
-%
-%
-%\bibitem[{{Riechers} {et~al.}(2013){Riechers}, {Bradford}, {Clements},
-%  {Dowell}, {P{\'e}rez-Fournon}, {Ivison}, {Bridge}, {Conley}, {Fu}, {Vieira},
-%  {Wardlow}, {Calanog}, {Cooray}, {Hurley}, {Neri}, {Kamenetzky}, {Aguirre},
-%  {Altieri}, {Arumugam}, {Benford}, {B{\'e}thermin}, {Bock}, {Burgarella},
-%  {Cabrera-Lavers}, {Chapman}, {Cox}, {Dunlop}, {Earle}, {Farrah}, {Ferrero},
-%  {Franceschini}, {Gavazzi}, {Glenn}, {Solares}, {Gurwell}, {Halpern},
-%  {Hatziminaoglou}, {Hyde}, {Ibar}, {Kov{\'a}cs}, {Krips}, {Lupu}, {Maloney},
-%  {Martinez-Navajas}, {Matsuhara}, {Murphy}, {Naylor}, {Nguyen}, {Oliver},
-%  {Omont}, {Page}, {Petitpas}, {Rangwala}, {Roseboom}, {Scott}, {Smith},
-%  {Staguhn}, {Streblyanska}, {Thomson}, {Valtchanov}, {Viero}, {Wang},
-%  {Zemcov}, \& {Zmuidzinas}}]{Riechers13a}
-%{Riechers}, D.~A., {Bradford}, C.~M., {Clements}, D.~L., {et~al.} 2013, \nat,
-%  496, 329
-%
-%
-%\bibitem[{{Sanders} {et~al.}(1988){Sanders}, {Soifer}, {Elias}, {Madore},
-%  {Matthews}, {Neugebauer}, \& {Scoville}}]{Sanders88}
-%{Sanders}, D.~B., {Soifer}, B.~T., {Elias}, J.~H., {et~al.} 1988, \apj, 325, 74
-%
-%\bibitem[{{Scott} {et~al.}(2011){Scott}, {Lupu}, {Aguirre}, {Auld}, {Aussel},
-%  {Baker}, {Beelen}, {Bock}, {Bradford}, {Brisbin}, {Burgarella}, {Carpenter},
-%  {Chanial}, {Chapman}, {Clements}, {Conley}, {Cooray}, {Cox}, {Dowell},
-%  {Eales}, {Farrah}, {Franceschini}, {Frayer}, {Gavazzi}, {Glenn}, {Griffin},
-%  {Harris}, {Ibar}, {Ivison}, {Kamenetzky}, {Kim}, {Krips}, {Maloney},
-%  {Matsuhara}, {Mortier}, {Murphy}, {Naylor}, {Neri}, {Nguyen}, {Oliver},
-%  {Omont}, {Page}, {Papageorgiou}, {Pearson}, {P{\'e}rez-Fournon}, {Pohlen},
-%  {Rawlings}, {Raymond}, {Riechers}, {Rodighiero}, {Roseboom},
-%  {Rowan-Robinson}, {Scott}, {Seymour}, {Smith}, {Symeonidis}, {Tugwell},
-%  {Vaccari}, {Vieira}, {Vigroux}, {Wang}, {Wright}, \& {Zmuidzinas}}]{Scott11a}
-%{Scott}, K.~S., {Lupu}, R.~E., {Aguirre}, J.~E., {et~al.} 2011, \apj, 733, 29
-%
-%\bibitem[{{Simpson} {et~al.}(2012){Simpson}, {Smail}, {Swinbank}, {Alexander},
-%  {Auld}, {Baes}, {Bonfield}, {Clements}, {Cooray}, {Coppin}, {Danielson},
-%  {Dariush}, {Dunne}, {de Zotti}, {Harrison}, {Hopwood}, {Hoyos}, {Ibar},
-%  {Ivison}, {Jarvis}, {Lapi}, {Maddox}, {Page}, {Riechers}, {Valiante}, \& {van
-%  der Werf}}]{Simpson12a}
-%{Simpson}, J.~M., {Smail}, I., {Swinbank}, A.~M., {et~al.} 2012, \mnras, 426,
-%  3201
-%
-%\bibitem[{{Smol{\v c}i{\'c}} \& {Riechers}(2011)}]{Smolcic11a}
-%{Smol{\v c}i{\'c}}, V., \& {Riechers}, D.~A. 2011, \apj, 730, 64
-%
-%\bibitem[{{Solomon} \& {Vanden Bout}(2005)}]{Solomon05a}
-%{Solomon}, P.~M., \& {Vanden Bout}, P.~A. 2005, \araa, 43, 677
-%
-%\bibitem[{{Swinbank} {et~al.}(2010){Swinbank}, {Smail}, {Longmore}, {Harris},
-%  {Baker}, {De Breuck}, {Richard}, {Edge}, {Ivison}, {Blundell}, {Coppin},
-%  {Cox}, {Gurwell}, {Hainline}, {Krips}, {Lundgren}, {Neri}, {Siana},
-%  {Siringo}, {Stark}, {Wilner}, \& {Younger}}]{Swinbank2010a}
-%{Swinbank}, A.~M., {Smail}, I., {Longmore}, S., {et~al.} 2010, \nat, 464, 733
-%
-%\bibitem[{{Swinbank} {et~al.}(2011){Swinbank}, {Papadopoulos}, {Cox}, {Krips},
-%  {Ivison}, {Smail}, {Thomson}, {Neri}, {Richard}, \& {Ebeling}}]{Swinbank11a}
-%{Swinbank}, A.~M., {Papadopoulos}, P.~P., {Cox}, P., {et~al.} 2011, \apj, 742,
-%  11
-%
-%\bibitem[{{Tacconi} {et~al.}(2006){Tacconi}, {Neri}, {Chapman}, {Genzel},
-%  {Smail}, {Ivison}, {Bertoldi}, {Blain}, {Cox}, {Greve}, \&
-%  {Omont}}]{Tacconi06a}
-%{Tacconi}, L.~J., {Neri}, R., {Chapman}, S.~C., {et~al.} 2006, \apj, 640, 228
-%
-%\bibitem[{{Tacconi} {et~al.}(2008){Tacconi}, {Genzel}, {Smail}, {Neri},
-%  {Chapman}, {Ivison}, {Blain}, {Cox}, {Omont}, {Bertoldi}, {Greve},
-%  {F{\"o}rster Schreiber}, {Genel}, {Lutz}, {Swinbank}, {Shapley}, {Erb},
-%  {Cimatti}, {Daddi}, \& {Baker}}]{Tacconi08a}
-%{Tacconi}, L.~J., {Genzel}, R., {Smail}, I., {et~al.} 2008, \apj, 680, 246
-%
-%\bibitem[{{Tacconi} {et~al.}(2010){Tacconi}, {Genzel}, {Neri}, {Cox}, {Cooper},
-%  {Shapiro}, {Bolatto}, {Bouch{\'e}}, {Bournaud}, {Burkert}, {Combes},
-%  {Comerford}, {Davis}, {Schreiber}, {Garcia-Burillo}, {Gracia-Carpio}, {Lutz},
-%  {Naab}, {Omont}, {Shapley}, {Sternberg}, \& {Weiner}}]{Tacconi10a}
-%{Tacconi}, L.~J., {Genzel}, R., {Neri}, R., {et~al.} 2010, \nat, 463, 781
-%
-%\bibitem[{{Vieira} {et~al.}(2010){Vieira}, {Crawford}, {Switzer}, {Ade},
-%  {Aird}, {Ashby}, {Benson}, {Bleem}, {Brodwin}, {Carlstrom}, {Chang}, {Cho},
-%  {Crites}, {de Haan}, {Dobbs}, {Everett}, {George}, {Gladders}, {Hall},
-%  {Halverson}, {High}, {Holder}, {Holzapfel}, {Hrubes}, {Joy}, {Keisler},
-%  {Knox}, {Lee}, {Leitch}, {Lueker}, {Marrone}, {McIntyre}, {McMahon}, {Mehl},
-%  {Meyer}, {Mohr}, {Montroy}, {Padin}, {Plagge}, {Pryke}, {Reichardt}, {Ruhl},
-%  {Schaffer}, {Shaw}, {Shirokoff}, {Spieler}, {Stalder}, {Staniszewski},
-%  {Stark}, {Vanderlinde}, {Walsh}, {Williamson}, {Yang}, {Zahn}, \&
-%  {Zenteno}}]{Vieira10a}
-%{Vieira}, J.~D., {Crawford}, T.~M., {Switzer}, E.~R., {et~al.} 2010, \apj, 719,
-%  763
-%
-%\bibitem[{{Wilson} {et~al.}(1970){Wilson}, {Jefferts}, \&
-%  {Penzias}}]{Wilson70a}
-%{Wilson}, R.~W., {Jefferts}, K.~B., \& {Penzias}, A.~A. 1970, \apjl, 161, L43
-
-%\end{thebibliography}
 

### 2016-01-09 Code/SEDfit.py
fix bug

@@ -59,7 +59,7 @@ def read_data_fromtxt(filename):
     """
     import astropy.io.ascii     # for .txt format
     data = astropy.io.ascii.read(filename, comment='^#')
-    if len(filename) == 0:
+    if len(data) == 0:
         errstr = "No data read from %s" % filename
         raise IOError(errstr)
     return data
@@ -113,9 +113,9 @@ Point_error_Jy = np.array([0.31e-3, 1.42e-3, 0.])    # Jy
 # Read in Data
 ########################################
 SMG_data = read_data_fromtxt(SMGfilename)
-SMGwavelg_micron, SMG_mJy, SMG_error_mJy = ([dat[0] for dat in SMG_data],
-                                            [dat[1] for dat in SMG_data],
-                                            [dat[2] for dat in SMG_data])
+SMGwavelg_micron, SMG_mJy, SMG_error_mJy = ([dat[0] for row in SMG_data],
+                                            [dat[1] for row in SMG_data],
+                                            [dat[2] for row in SMG_data])
 
 # np.asarray converts input to array
 freq_Hz, SMGflux_SI, SMGerr_SI = \
@@ -124,9 +124,9 @@ freq_Hz, SMGflux_SI, SMGerr_SI = \
                                 np.asarray(SMG_error_mJy))
 
 Radio_data = read_data_fromtxt(RadioFilename)
-Radio_Hz, Radio_Jy, Radio_error = ([dat[0] for dat in Radio_data],
-                                   [dat[2] for dat in Radio_data],
-                                   [dat[3] for dat in Radio_data])   # Jy
+Radio_Hz, Radio_Jy, Radio_error = ([dat[0] for row in Radio_data],
+                                   [dat[2] for row in Radio_data],
+                                   [dat[3] for row in Radio_data])   # Jy
 
 Radio_Hz, Radio_Jy, Radio_error = (np.asarray(Radio_Hz),
                                    np.asarray(Radio_Jy),

### 2016-01-11 mod1/response.md
DR's comments

@@
-We thank the referee for providing constructive and thoughtful comments to improve the manuscipt.
-We have addressed all the concerns raised by the referee and details can be found in the revised version -- please see attached.
-A brief description on how we incoprated the changes can be found below.
+We thank the referee for providing constructive and thoughtful
+comments to improve the manuscipt. We have addressed all the concerns
+raised by the referee and details can be found in the revised version
+-- please see attached. A brief description on how we incoprated the
+changes can be found below.
 
@@
 1:
-- There is already a lensing model in H14 (a paper the authors refer to numerous times) and it is unclear why they redid the lensing model (they use the same SMA data as H14 but a different code).
-If the derived model is significantly different from H14 then this should be highlighted otherwise the lens modeling section isn't necessary in this paper.
-> We moved the lens mass and consistent results into table 1 and its caption, and removed details of the lens model and shortened the section.
-However, we retained this section in this paper as we provide the best-fit parameters that were not reported in Haas+14 and since we refered to the inferred half-light radius later in the analysis section.
+- There is already a lensing model in H14 (a paper the authors refer
+  to numerous times) and it is unclear why they redid the lensing
+  model (they use the same SMA data as H14 but a different code). If
+  the derived model is significantly different from H14 then this
+  should be highlighted otherwise the lens modeling section isn't
+  necessary in this paper.
+
+> Most parameters obtained in our new analysis with our new lensing
+  code are indeed consistent with the earlier model reported by H14,
+  such that the results are only slightly improved. However, H14 did
+  not report the full range of best-fit parameters and uncertainties
+  in their analysis, such that our results are significantly more
+  detailed. To take this comment into account, we thus significantly
+  shortened the text in this section by removing details on the lens
+  modeling approach (and including a reference to the literature
+  instead), and we have moved the lens mass and consistent results
+  into Table 1 - which is used to briefly summarize the full range of
+  parameters. This includes the important inferred half-light radius,
+  which is used later in the analysis.
+
+-- we need to say explicitly what the different parameters are in this
+   paper - without that it is not possible to understand.
 
 2:
-- The SMG is thought to harbor a luminous AGN.
-In that case, the LIR will certainly have a contribution from the AGN that should be accounted for otherwise the SFR will be overestimated: see e.g.
-Coppin+2010, Kirkpatrick+2012, Magdis+2013, Kirkpatrick+2014.
-Please correct LIR for the AGN emission prior to estimating SFR and include an AGN component in the SED fitting.
-> In our analysis, we fit SED models to the rest-frame FIR, which has been found to have negligible AGN contribution to rest-frame FIR (≥ 60µm; Carilli+05, Netzer+07, Mullaney+11, Harrison+15).
-Since we do not have MIR measurements solely from the background SMG and due to the postive K corretion blueward of dust peak, the forground radio galaxy contributes a non-negligible amount to the MIR luminosity, we therefore didn't fit an AGN component.
-Including an additional component, and thus free parameters to the SED model will be over-fitted due to the limited amount of data at hand.
-Instead our SED model includes a power-law to the blue side of the dust peak, which accounts for the MIR excess and allows us to estimate the IR luminosity (Kirkpatrick+15, Riechers+13, Johnson+13, Casey+12).
-We derived the SFR and other corresponding properties using the L_FIR, (45-122.5), which is mostly due to SF-driven dust emission.
+- The SMG is thought to harbor a luminous AGN. In that case, the LIR
+  will certainly have a contribution from the AGN that should be
+  accounted for otherwise the SFR will be overestimated: see
+  e.g. Coppin+2010, Kirkpatrick+2012, Magdis+2013,
+  Kirkpatrick+2014. Please correct LIR for the AGN emission prior to
+  estimating SFR and include an AGN component in the SED fitting.
+
+> In our analysis, we fit SED models to the rest-frame FIR, which has
+  been found to have negligible AGN contribution to rest-frame FIR (≥
+  60µm; Carilli+05, Netzer+07, Mullaney+11, Harrison+15). Since we do
+  not have MIR measurements solely from the background SMG and due to
+  the postive K corretion blueward of dust peak, the forground radio
+  galaxy contributes a non-negligible amount to the MIR luminosity, we
+  therefore didn't fit an AGN component. Including an additional
+  component, and thus free parameters to the SED model will be
+  over-fitted due to the limited amount of data at hand. Instead our
+  SED model includes a power-law to the blue side of the dust peak,
+  which accounts for the MIR excess and allows us to estimate the IR
+  luminosity (Kirkpatrick+15, Riechers+13, Johnson+13, Casey+12). We
+  derived the SFR and other corresponding properties using the L_FIR,
+  (45-122.5), which is mostly due to SF-driven dust emission.
+
+-- briefly discuss this in the text.
 
 3:
-- section 4.3 is way too wordy and can be cut down to a few paragraphs and a table summarizing these key values (already given in Table 4).
-These are all standard calculations and you can refer to CW14 for the equations rather than repeating them here.
-> We removed standard equations from the manuscript, and combined the sections reporting SFE, SFR, and SFRSD into one. We also shortened the section.
+- section 4.3 is way too wordy and can be cut down to a few paragraphs
+  and a table summarizing these key values (already given in Table
+  4). These are all standard calculations and you can refer to CW14
+  for the equations rather than repeating them here.
+
+> We removed standard equations from the manuscript, and combined the
+  sections reporting SFE, SFR, and SFRSD into one. We also shortened
+  the section.
 
 4:
-- You should also summarize the evidence for the AGN in this SMG (maybe when you mention this in the intro) so the reader doesn't have to read H14.
-> We rephrased the introduction to show more clearly the evidence of an AGN.
+- You should also summarize the evidence for the AGN in this SMG
+  (maybe when you mention this in the intro) so the reader doesn't
+  have to read H14.
+
+> We rephrased the introduction to show more clearly the evidence of
+  an AGN.
 
 5:
-- [a further concern/question about Table 4 is whether all the same assumptions such as excitation, alpha_co, etc. were made for the other SMGs otherwise the comparisons are meaningless]
-> We added notes in the caption below Table 4 to recap assumptions used in deriving these quantities.
+- [a further concern/question about Table 4 is whether all the same
+  assumptions such as excitation, alpha_co, etc. were made for the
+  other SMGs otherwise the comparisons are meaningless]
+
+> We added notes in the caption of Table 4 to recap all assumptions
+  used in deriving these quantities.
 
 6:
-- Section 5: why do the authors cherry-pick these 2 SMGs to make comparisons?
-there are many other sources that could be chosen with a range of properties.
-A comparison to these 2 SMGs is not useful at all given the diversity in this population (e.g.
-the sentence "This demonstrates the large ..." is not true when comparing only 3 objects).
-I suggest comparing to the general properties observed for SMGs (as summarized in CW14 or Casey+14) which will be more useful in placing this object in the context of the SMG population.
+- Section 5: why do the authors cherry-pick these 2 SMGs to make
+  comparisons? there are many other sources that could be chosen with
+  a range of properties. A comparison to these 2 SMGs is not useful at
+  all given the diversity in this population (e.g. the sentence "This
+  demonstrates the large ..." is not true when comparing only 3
+  objects). I suggest comparing to the general properties observed for
+  SMGs (as summarized in CW14 or Casey+14) which will be more useful
+  in placing this object in the context of the SMG population.
 
-> We picked out two gravitaitonally lensed SMGs to show the ranges of SMGs properties, of which intrinsically sit at faint ends of the luminosity distribution, and thus would not have been studied in sensitivity-limited samples.
-In addition, these are among the SMGs which are best-studied to date and their properties are deriving using similar approach in this paper.
-Hence, a comparison with these object will have relatively lower uncertainties.
-We have added a compilation of SMG and type-2 QSOs properties to the Table.
-Please see tablenote and comments for details.
-We have incoporated a comparison to these values in our conclusion.
-Please see conclusion section for other changes.
+> We picked out two apparently similarly bright gravitationally lensed
+  SMGs to show the ranges of SMGs properties, of which intrinsically
+  sit at faint ends of the luminosity distribution, and thus would not
+  have been studied in sensitivity-limited samples. In addition, these
+  are among the SMGs which are best-studied to date and their
+  properties are deriving using similar approach in this paper. Hence,
+  a comparison with these object will have relatively lower
+  uncertainties. We have added a compilation of SMG and type-2 QSOs
+  properties to the Table. Please see the table notes and comments for
+  details. We have incoporated a comparison to these sample-averaged
+  values in our conclusion as well.
+
+-- need to re-write this. we would have seen at least two of these in
+   unlensed samples. just comparing since these are the most
+   well-known ones that similarly stick out from their submm fluxes
+   (>400mJy).
+
+   - differential lensing and ratios 
+   - if source is intrinsically fainter 
+   - write how we address issue raised --> reasons why we kept
 
 ## 7
-- the discussion/conclusions should focus on what is new from this paper and not what is already presented in H14.
-E.g.
-the last sentence about this SMG transitioning from starburst to QSO phase.
-How is that conclusion made or strengthened with this new data?
+- the discussion/conclusions should focus on what is new from this
+  paper and not what is already presented in H14. E.g. the last
+  sentence about this SMG transitioning from starburst to QSO
+  phase. How is that conclusion made or strengthened with this new
+  data?
 
@@
 1:
-- the depletion time seems short compared to other SMGs which are ~100Myr although maybe it is consistent with other SMGs with AGN in them.
-> Greve+05 report a range of depletion time τ = 40-100 Myr for SMGs, please see also Table 4.
+- the depletion time seems short compared to other SMGs which are
+  ~100Myr although maybe it is consistent with other SMGs with AGN in
+  them.
+
+> Greve+05 report a range of depletion time τ = 40-100 Myr for SMGs,
+  please see also Table 4.
 
 2:
-- section headings in 3 are strange. Remove the words "New results" since this is obvious and a requirement for publication. Also remove subheading or second line in heading 3.2.
+- section headings in 3 are strange. Remove the words "New results"
+  since this is obvious and a requirement for publication. Also remove
+  subheading or second line in heading 3.2.
+
 > We removed "New results" in the subject headings.
@@
 3:
-- the left panels on Fig 1 and 2 should show the same region (have the same RA/DEC axes).
-It is also tough to tell by eye if the VLA9GHz and SMA emission is coincident.
-Perhaps these can be overlayed on Fig 1.
-> We marked the locations of the peak emission from the SMA as white crosses on the right panel on figure 1.
+- the left panels on Fig 1 and 2 should show the same region (have the
+  same RA/DEC axes). It is also tough to tell by eye if the VLA9GHz
+  and SMA emission is coincident. Perhaps these can be overlayed on
+  Fig 1.
+
+> We adjusted the panel sizes as suggested, and marked the locations
+  of the peak emission from the SMA as white crosses on the right
+  panel in Figure 1.
 
 4:
-- figure 3: orange is difficult to see. What is the SNR of the residuals in the right panel?
-> We modified our caption to state that the quoted contour levels are the same for both panels in the figure. We changed the critical line color to green to easily visualization.
+- figure 3: orange is difficult to see. What is the SNR of the
+  residuals in the right panel?
+
+> We modified our caption to state that the quoted contour levels are
+  the same for both panels in the figure. We changed the critical line
+  color to green for better readability.
 
 5:
-- figure 4: again colors (red, orange) are hard to distinguish on a print out version of the paper.
-> We were unable to make adjustment regarding this as we did not use orange in the figure. Please kindly clarify this.
+- figure 4: again colors (red, orange) are hard to distinguish on a
+  print out version of the paper.
+
+> We did not use orange in this figure. Please kindly clarify.
 
@@
 - specify the wavelengths range assumed for FIR.
-> We mentioned the FIR range in Section 4.2.2.
+
+> We mentioned the FIR range (42.5-122.5 micron) in Section 4.2.2.
 
 7:
-- last para section 4.2.2: it is limited data in the submm not the FIR [need to be probing Rayleigh Jeans] that makes the dust mass weakly constrained.
-I don't understand what the last sentence in this para means - I think there are words missing.
-> We clarify this by adding the phrase "rest-frame" to FIR. We also restructured the last paragraph to convey our message more clearly.
+- last para section 4.2.2: it is limited data in the submm not the FIR
+  [need to be probing Rayleigh Jeans] that makes the dust mass weakly
+  constrained. I don't understand what the last sentence in this para
+  means - I think there are words missing.
+
+> We clarified this issue by adding the phrase "rest-frame" to FIR. We
+  also restructured the last paragraph to convey our message more
+  clearly.
 
 8: 
-- SF surface density: from resolved studies of SMGs is it reasonable to divide half the SFR and gas mass by the area out to the half-light radii?
-give appropriate references to justify this assumption.
-> We provided a few citations to show that this is typical.
+- SF surface density: from resolved studies of SMGs is it reasonable
+  to divide half the SFR and gas mass by the area out to the
+  half-light radii? give appropriate references to justify this
+  assumption.
+
+> We now provide a few citations to show that this is a common
+  assumption.
 
 9:
-- intro: the first para makes it sound like our knowledge of SMGs comes primarily from SMGs found in large sky Herschel surveys and SPT but this is not true.
-Please include references to earlier work that established the basic properties of SMGs (redshift distribution, luminosities, SFRs, Mgas, etc) prior to Herschel even launching.
+- intro: the first para makes it sound like our knowledge of SMGs
+  comes primarily from SMGs found in large sky Herschel surveys and
+  SPT but this is not true. Please include references to earlier work
+  that established the basic properties of SMGs (redshift
+  distribution, luminosities, SFRs, Mgas, etc) prior to Herschel even
+  launching.
+
 > We restructured the paragraph and added earlier discoveries.
 
+-- probably wants smail+97,hughes+98,barger+98 or so here
+
 10:
-- the fact that the lensing system has two components isn't presented clearly in this paper.
-I had to read H14 to understand what the authors meant when they mentioned companion B.
-Please make this clearer so the reader does not have to read H14
-> We added a sentence to elaborate on this, please see the revised manuscript.
+- the fact that the lensing system has two components isn't presented
+  clearly in this paper. I had to read H14 to understand what the
+  authors meant when they mentioned companion B. Please make this
+  clearer so the reader does not have to read H14
+
+> We added a sentence to elaborate on this, please see the revised
+  manuscript.
+
+-- say where - intro
 
 11:
-- last few paras of paper: what does "breaking up its dust cocoon" mean? this is the first time this is mentioned and should be explained if it is relevant.
-> We mentioned this as a reference from Haas+14. We have removed this phrase in the revised version given that this has been mentioned in Haas+14, and is not necessary in our discussion.
+- last few paras of paper: what does "breaking up its dust cocoon"
+  mean? this is the first time this is mentioned and should be
+  explained if it is relevant.
+
+> We mentioned this as a reference from Haas+14. We have removed this
+  phrase in the revised version given that this has been mentioned in
+  Haas+14, and is not necessary in our discussion.
 
 12:
-- end of section 4.3.1: the factor of 2 for dust mass is overshadowed by the factor of >5 in alpha_co
+- end of section 4.3.1: the factor of 2 for dust mass is overshadowed
+  by the factor of >5 in alpha_co
+
 > We removed that sentence.
@@
 13:
-- related to depletion time, there is a new Nature paper by Narayanan et al (published Sept 23) which discusses how SMGs in sims can last for a Gyr with replenishment from the IGM.
-In that case, is the depletion timescale really useful?
-what do we learn if the galaxy is getting new gas?
->The derived depletion timescale is derived the based on the definition of the quantity τ = Mgas/SFR, which descibes the time 
-it would take for a galaxy to use up the available molecular gas reservoir given the current star formation rate, assuming no 
-replenishment of gas (Carilli & Walter 2013). Hence, this quantity provides a lower limit on the timescale for SF activity. 
-Based on our observations, we find no evidence of gas inflow in SMMJ0939.
+- related to depletion time, there is a new Nature paper by Narayanan
+  et al (published Sept 23) which discusses how SMGs in sims can last
+  for a Gyr with replenishment from the IGM. In that case, is the
+  depletion timescale really useful? what do we learn if the galaxy is
+  getting new gas?
+
+>The derived depletion timescale is derived the based on the
+ definition of the quantity τ = Mgas/SFR, which descibes the time it
+ would take for a galaxy to use up the available molecular gas
+ reservoir given the current star formation rate, assuming no
+ replenishment of gas (Carilli & Walter 2013). Hence, this quantity
+ provides a lower limit on the timescale for SF activity. Based on our
+ observations, we find no evidence of gas inflow in SMMJ0939.
 
 13:
-dynamical mass calculation: can you estimate how much higher this would be given observations showing the different radii between the molecular and dust emission in SMGs. How different are the radii?
->The half-light radius of dust emitting region is ~ 1.2 kpc based on a recent study by Simpson+15, who collected ALMA 870 µm data over 52 SMGs.
-Tacconi+06 report a median FWHM size of 4.1 ±1.6 kpc based on high-J CO measurements.
-Given the small number statistics on resolved CO(1-0) emission in QSOs, where Riechers+11 find no evidence of extent cold gas emission, we did not include an additional estimate of the dynamical mass assuming some physical size from recent observaitons (still limited) in the paper.
-However, we have noted these phyiscal sizes in the text, which allows readers to scale the dynamical mass correspondingly should they wish to do so.
-Please see the revised manuscipt.
+- dynamical mass calculation: can you estimate how much higher this
+  would be given observations showing the different radii between the
+  molecular and dust emission in SMGs. How different are the radii?
+
+>The half-light radii of dust-emitting regions in SMGs typically are ~
+ 1.2 kpc based on a recent study by Simpson+15, who collected ALMA 870
+ µm data for 52 SMGs. Tacconi+06 report a median FWHM size of 4.1 ±1.6
+ kpc based on high-J CO measurements. Given the small number
+ statistics on resolved CO(1-0) emission in QSOs, where Riechers+11
+ find no evidence of extent cold gas emission, we did not include an
+ additional estimate of the dynamical mass assuming some physical size
+ from recent observations (still limited) in the paper. However, we
+ have noted these physical sizes in the text, which allows readers to
+ scale the dynamical mass correspondingly should they wish to do
+ so. Please see the revised manuscipt.
 
 14:
-- appendix: "no evidence of correlation" do the authors mean "covariance" here?
-> We used the word "correlation" to indicate that regardless of the variation found in dust mass due to a different prior imposed on the emissivity, the IR luminosity is insensivtive to such changes in dust mass.
-Both the dust mass and IR lumonisty are inferred from the best-fit SED model, and are not parameters in the model (and the loss function).
-For these reasons, we do not mean the covariance here.
+- appendix: "no evidence of correlation" do the authors mean
+  "covariance" here?
+
+> We used the word "correlation" to indicate that regardless of the
+  variation found in dust mass due to a different prior imposed on the
+  emissivity, the IR luminosity is insensivtive to such changes in
+  dust mass. Both the dust mass and IR lumonisty are inferred from the
+  best-fit SED model, and are not parameters in the model (and the
+  loss function). For these reasons, we do not mean the covariance
+  here.

### 2016-01-11 Code/FgContIm.py
address DR's comments: zoom out for VLA FG plot, change image contrast for BG image

@@ -88,7 +88,7 @@ def standard_plot_setup(sp, ra_center, dec_center, size, tc='black'):
     sp.axis_labels.set_xtext('Right Ascension (J2000)')
     sp.axis_labels.set_ytext('Declination (J2000)')
     sp.axis_labels.set_xpad(3)
-    sp.axis_labels.set_ypad(-35)
+    sp.axis_labels.set_ypad(-25)
     sp.axis_labels.set_xposition('bottom')
 
 

### 2016-01-11 Code/Plot_Image.py

@@ -45,6 +45,7 @@ VLA_dec             = 8.325666666846E+01
 sizep               = 0.0025
 sizePcont_noise     = 0.020
 sizePLine           = 0.02 #0.012
+sizevla             = 0.0035
 ra_center           = 144.84933
 dec_center          = 83.257175
 
@@ -92,7 +93,7 @@ fvla.show_grayscale(stretch='log', vmin=vla_min, vmax=vla_max, vmid=-0.001)
 
 flin = aplpy.FITSFigure(label['lin'][0], \
         figure=fig_line, subplot=[x0,row_a,width,dy])
-flin.show_colorscale(cmap=mpl.cm.jet, vmin=min_line, vmax=max_line, vmid=-10, stretch='log')
+flin.show_colorscale(cmap=mpl.cm.jet, vmin=min_line, vmax=max_line-1, vmid=-15, stretch='log')
 
 fSMA = aplpy.FITSFigure(label['SMA'][0], figure=fig_line, subplot=[x0+width+2*x_gap, row_a, width, dy])
 fSMA.show_grayscale(stretch='log', vmin=SMA_min, vmax=SMA_max, vmid=-0.1)
@@ -139,7 +140,7 @@ setup_scalebar(fSMA, lg_20kpc_bg, str('20kpc'))
 # axes
 ########################################
 standard_plot_setup(fcont, ra_center, dec_center, sizePcont_noise) #, tc='white')
-standard_plot_setup(fvla, ra_center, dec_center, sizep, tc='white')
+standard_plot_setup(fvla, ra_center, dec_center, sizevla, tc='white')
 standard_plot_setup(flin, ra_center, dec_center, sizePLine)
 standard_plot_setup(fSMA, ra_center, dec_center, sizep, tc='white')
 # fcont.tick_labels.hide()

### 2016-01-13 mod1/response.md
added in DR's comments

@@
 We thank the referee for providing constructive and thoughtful
-comments to improve the manuscipt. We have addressed all the concerns
+comments to improve the manuscript. We have addressed all the concerns
 raised by the referee and details can be found in the revised version
--- please see attached. A brief description on how we incoprated the
+-- please see attached. A brief description on how we incorporated the
 changes can be found below.
@@
 
--- we need to say explicitly what the different parameters are in this
-   paper - without that it is not possible to understand.
-
 2:
@@
   not have MIR measurements solely from the background SMG and due to
-  the postive K corretion blueward of dust peak, the forground radio
+  the positive K correction blue-ward of dust peak, the foreground radio
   galaxy contributes a non-negligible amount to the MIR luminosity, we
@@
   (45-122.5), which is mostly due to SF-driven dust emission.
-
--- briefly discuss this in the text.
 
@@
   properties to the Table. Please see the table notes and comments for
-  details. We have incoporated a comparison to these sample-averaged
+  details. We have incorporated a comparison to these sample-averaged
   values in our conclusion as well.
@@
   same RA/DEC axes). It is also tough to tell by eye if the VLA9GHz
-  and SMA emission is coincident. Perhaps these can be overlayed on
+  and SMA emission is coincident. Perhaps these can be overlaid on
   Fig 1.
@@
 
--- probably wants smail+97,hughes+98,barger+98 or so here
-
 10:
@@
 
-> We added a sentence to elaborate on this, please see the revised
-  manuscript.
-
--- say where - intro
+> We added a sentence to the introduction section to elaborate on this, please see the revised manuscript.
 
@@
 >The derived depletion timescale is derived the based on the
- definition of the quantity τ = Mgas/SFR, which descibes the time it
+ definition of the quantity τ = Mgas/SFR, which describes the time it
  would take for a galaxy to use up the available molecular gas
@@
  scale the dynamical mass correspondingly should they wish to do
- so. Please see the revised manuscipt.
+ so. Please see the revised manuscript.
 
@@
   variation found in dust mass due to a different prior imposed on the
-  emissivity, the IR luminosity is insensivtive to such changes in
-  dust mass. Both the dust mass and IR lumonisty are inferred from the
+  emissivity, the IR luminosity is insensitive to such changes in
+  dust mass. Both the dust mass and IR luminosity are inferred from the
   best-fit SED model, and are not parameters in the model (and the

### 2016-01-13 mod1/manuscript/ms.tex
added in DR's comments

@@
 \documentclass[iop, revtex4]{emulateapj}
-\usepackage[breaklinks,colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
+\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=blue]{hyperref}
+\usepackage{amsmath}
+
+\usepackage{etoolbox}
+
+\makeatletter
+
+% Patch case where name and year are separated by aysep
+\patchcmd{\NAT@citex}
+  {\@citea\NAT@hyper@{%
+     \NAT@nmfmt{\NAT@nm}%
+     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
+     \NAT@date}}
+  {\@citea\NAT@nmfmt{\NAT@nm}%
+   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
+
+% Patch case where name and year are separated by opening bracket
+\patchcmd{\NAT@citex}
+  {\@citea\NAT@hyper@{%
+     \NAT@nmfmt{\NAT@nm}%
+     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
+       {\@citeb\@extra@b@citeb}%
+     \NAT@date}}
+  {\@citea\NAT@nmfmt{\NAT@nm}%
+   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
+  {}{}
+
+\makeatother
+
 \newcommand{\vdag}{(v)^\dagger}
@@
 
-\slugcomment{Submitted to the ApJ, Revised version December 20, 2015}
-\usepackage{amsmath}
+\slugcomment{Submitted to the ApJ}
+\input{changelog.tex}       % git revision hash, new command
+
 \shorttitle{Study of a strongly-lensed type-2 quasar host SMG at $z$\,=\,2.221}
@@
 \begin{document}
-\title{A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3}
+{\tiny  \RevisionInfo}        % place it here
+\title{A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Qruasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3}
 \author{T. K. Daisy Leung and Dominik A. Riechers}
@@
 Using the \CO line intensity of $I_\textrm{CO(3-2)}$ = (12.6\,$\pm$\,2.0)\,Jy\,km\,s\pmOne, we derive
- a lensing- and excitation-corrected CO line luminosity of \Lp = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU\ for the SMG, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling performed on the 1\,mm continuum emission.
+ a lensing- and excitation-corrected CO line luminosity of \Lp = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU\ for the SMG, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling.
+ % performed on the 1\,mm continuum emission.
  This translates to a molecular gas mass of $M_\textrm{gas}$ = (2.7\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\Msun.
@@
 $L_\textrm{IR}$ = (9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,(10.1/$\mu_\textrm{L}$)\,\Lsun.
-Our comparative study
-of the gas mass, dust mass, star formation rate, and surface densities in SMM
-J0939+8315
-and other high-redshift SMGs and type-2 quasars 
-{\bf shows that it is consistent with the properties of both populations.
-Together with the presence of its obscured quasar, massive molecular gas reservoir, on-going intensive star-formation and the short gas depletion timescale suggests that
-SMM\,J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase. }
+{\bf 
+We find that the properties of the interstellar medium of
+ SMM J0939+8315 overlap with both SMGs and type-2 quasars. Hence, SMM J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase in the 
+evolutionary link model, according in which this SMG represents an intermediate stage of present-day galaxies
+at an earlier epoch. 
+ }
 \end{abstract}
@@
  are extremely luminous in the infrared
- wavelengths (L$_\textrm{IR} \sim$ 10$^{12}$ \Lsun) with high star formation rates (SFR) \citep[$\gtrsim $ 500 \Msun yr\pmOne; see \eg reviews by][]{Blain02a, Lagache05a,Casey14a}.  
-{\bf Following the pioneering works in the discovery of this population}, considerable amounts of effort have been invested into 
+ wavelengths (L$_\textrm{IR} \sim$ 10$^{12}$ \Lsun) with high star formation rates \citep[SFR $\gtrsim$\,500\,\Msun yr\pmOne; see \eg reviews by][]{Blain02a, Lagache05a,Casey14a}.  
+{\bf Following the pioneering works in the discovery of this population \citep{Barger98a,Smail97a,Hughes98a}}, considerable amounts of effort have been invested into 
 obtaining large samples of SMGs by carrying out
@@
  as lensing amplifies the intrinsic fluxes of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a,Oliver12a}, and making follow-up studies considerably less time consuming.
-A particularly interesting and peculiar lensing system was discovered serendipitously in a study carried out with the {\it Herschel Space Telescope}, in which
+A particularly interesting and peculiar lensing system was discovered serendipitously in a study carried out with {\it Herschel}, in which
 a type-2 quasar host SMG --- SMM\,J0939+8315 (hereafter SMM\,J0939) is being lensed by the double-lobed Fanaroff-Riley
-Class II \citep*[FR-II; ][]{Fanaroff74} radio galaxy 3C220.3 and its
-companion galaxy B at $z$\,=\,0.685{\bf, where this companion galaxy is identified by \citeauthor{Haas14} (2014; hereafter H14) via observations with the Keck II Observatory and the {\it Hubble Space Telescope}.}
+Class II \citep*[FR-II; ][]{Fanaroff74} radio galaxy 3C220.3 {\bf at $z$\,=\,0.685, which has a
+companion galaxy B as seen in Keck 2$\micron$ and the {\it Hubble Space Telescope} 702nm images \citep[hereafter H14]{Haas14}}.
 SMM\,J0939 is currently one of the brightest known lensed
 SMGs, with a lensing-magnified flux density of $S_\textrm{250\micron}$\,=\,440\,$\pm$\,15 mJy.
-{\bf Previous detections of C~{\scriptsize\sc IV}~1459\AA\
+{\bf Detections of C~{\scriptsize\sc IV}~1459\AA\
  and He~{\scriptsize\sc II}~1640\AA\ line emission toward SMM\,J0939
  placed the redshift of this galaxy at $z$\,=\,2.221.
-Based on the line fluxes and spectral line widths of these AGN lines, H14 suggested the presence of an active galactic nucleus (AGN) in the form of a type-2 quasar in this SMG.}
+Based on the line fluxes and spectral line widths of these AGN lines, H14 suggest the presence of an active galactic nucleus (AGN) in the form of a type-2 quasar in this SMG.}
 
@@
 To study the intrinsic properties of the background galaxy, we determine the magnification factor {\bf and the half-light radius of the dust region} by performing
-lens modeling on the SMA 1\,mm continuum data presented by H14 of this system. Lens modeling is carried out in the visibility
-({\it uv-}) plane using an updated version\footnote{commit: 7aee6276} of the publicly available software {\sc uvmcmcfit}\footnote{\url{https://github.com/sbussmann/uvmcmcfit}}, details of the parametric lens model can be found in \citet{Bussmann15a}.
-%In the code, the surface mass densities of both
-%lenses are represented by singular isothermal ellipsoid (SIE) profiles, and the source is assumed to have an
-%elliptical Gaussian profile.
+lens modeling on the SMA 1\,mm continuum data presented by H14 of this system. 
+Lens modeling is carried out in the visibility
+({\it uv-}) plane using an updated version the publicly available software {\sc uvmcmcfit} \citep{uvmcmcfit15a},
+details of the parametric lens model can be found in \citet{Bussmann15a}. 
+{\bf The surface mass densities of the two lensing galaxies, 3C220.3 and its companion galaxy B as mentioned in Section~\ref{sec:intro}, are described by singular isothermal ellipsoid profiles, and the source is assumed to have an
+elliptical Gaussian profile. }
 
@@
 factor of $\mu_\textrm{L}$ = 10.13\,$\pm$\,1.38
-%, this is consistent the value reported by H14 within the errors. 
 and a half-light radius of 0\farcs11 $\pm$ 0\farcs03, corresponding to a spatial extent of $\sim$0.9 kpc.} 
@@
 parameters are listed in Table~\ref{tab:lensParam}. 
-%The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1\farcs22\,$\pm$\,0\farcs01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0\farcs75\,$\pm$\,0\farcs02 (5.34\,\,kpc at $z$\,=\,0.685), and
-%the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
 \input{table_lensParams}
@@
 \input{table_mbb}
-The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in the Appendix. The best-fit solution of an optically thin
-model corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of an optically thick model
+The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in the Appendix. The best-fit solution of optically thin
+models corresponds to $\chi^2$ = 5.31 with 3 degrees of freedom, whereas that of optically thick models
 corresponds to $\chi^2$ = 2.25 with 2 degrees of freedom, suggesting a better fit than in the optically thin
 case. In the subsequent analysis, we employ the inferred values from the optically thick model.
-The best-fit solution yields a FIR luminosity (rest-frame 42.5$-$122.5\micron) of $L_\textrm{FIR}$ = 53.3$^{+1.1}_{-1.1}$\,$\times$\,10$^{12}$\,\Lsun, and a total infrared (IR; rest-frame 8$-$1000 \micron) luminosity of $L_\textrm{IR}$ = 88.5$^{+2.6}_{-2.6}$\,$\times$\,10$
-^{12}$\,\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64\,\,m$^2$\,\,kg\pmOne\ at 125.0\,\,$
+The best-fit solution yields a far-infrared luminosity (rest-frame 42.5$-$122.5\micron) of $L_\textrm{FIR}$ = 53.3$^{+1.1}_{-1.1}$\,$\times$\,10$^{12}$\,\Lsun, and a total infrared (IR; rest-frame 8$-$1000 \micron) luminosity of $L_\textrm{IR}$ = 88.5$^{+2.6}_{-2.6}$\,$\times$\,10$
+^{12}$\,\Lsun
+\footnote{
+Owning to the positive K-correction blue-ward of the dust peak, in which 
+the foreground radio galaxy contributes a non-negligible amount to the MIR luminosity, we do not fit an AGN component.
+Instead, we adopt a power-law to account for the MIR excess, which allows us to estimate the IR
+luminosity \citep{Casey12a, Riechers13a, Kirkpatrick15a}. }. 
+Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64\,\,m$^2$\,\,kg\pmOne\ at 125.0\,\,$
 \micron$ \citep{Dunne03a}, we find a dust mass of $M_\textrm{dust}$ = 50.5$^{20.4}_{-20.2}\times$10$^8$\,\,\Msun{\bf ;} the uncertainties do not include those in the dust absorption coefficient ($\kappa_{\nu}$).
@@
 to lensing correction.{\bf We note that the dust mass is weakly constrained owing to the dearth of data in the {\bf rest-frame} FIR waveband.
-As such, we investigate how the dust mass would be affected by fitting an additional optically thick model with an upper limit of
+As such, we investigate how the dust mass would be affected by fitting additional optically thick models with an upper limit of
  $\beta$ adjusted from 2.2 to 3.0.
-While the difference in each best-fit parameter between this scenario and the previous model (an upper limit of $\beta$ = 2.2) is within 3\%, we find that the dust mass inferred from this best-fit SED model is boosted by a factor of $\sim$\,2.}
+While the difference in each best-fit parameter between this scenario and the previous models (with an upper limit of $\beta$ = 2.2) is within 3\%, we find that the dust mass inferred from this best-fit SED model is boosted by a factor of $\sim$\,2.}
 \subsection{Physical Properties of the ISM in SMM\,J0939}
@@
 In the case of high-redshift type-2 quasars, \citet{Riechers11a} report a brightness temperature ratio of $R_\textrm{31}$ = 1.00\,$\pm$\,0.10 for IRAS F10214+4724 (hereafter F10214), which is currently the only known type-2 quasar with both \CO and CO($J$\,=\,1\,\rarr\,0) line measurements.
-\par
-{\bf Here, we derive the molecular gas mass
+Here, we derive the molecular gas mass
 assuming thermalized excitation of CO, as SMM\,J0939 is
-postulated to be hosting a type-2 quasar (H14).}
+postulated to be hosting a type-2 quasar (H14). \par
 We calculate the CO($J$\,=\,1\rarr\,0) line luminosity using a standard relation
-\citep[\eg][]{Solomon05a}.
+\citep[\eg][]{Solomon05a}
+and assuming a conversion factor of $\alpha_\textrm{CO}$\,= 0.8\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
+adopted for SMGs \citep[\eg][]{Tacconi06a,Tacconi08a,Bothwell13a}.
 This corresponds to \Lp = (3.42\,$\pm$\,0.71)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU; hence the inferred total molecular gas mass is $M_\textrm{gas}$ = (2.74\,$\pm$\,0.57)\,$\times$\,\,10$^{10}$\,\Msun\, after correcting for lensing magnification.
-We assumed a conversion factor of $\alpha_\textrm{CO}$ = 0.8\,\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
-adopted for SMGs \citep[\eg][]{Tacconi06a,Tacconi08a,Bothwell13a}.
 This results in a gas-to-dust
@@
 \subsubsection{{\bf Star Formation Rate \& Star Formation Efficiency}}
-{\bf We derive the SFR using the lensing-corrected FIR luminosity assuming 
-that the dominant heating source of cold-dust is young and massive stars and ignoring a contribution from the
-dust-enshrouded AGN.}
+{\bf 
+We derive the SFR using the lensing-corrected far-infrared luminosity
+assuming 
+that the dominant heating source of cold-dust is young and massive stars, and 
+that a contribution from the
+dust-enshrouded AGN is negligible.
+This assumption stems from the results of recent studies using various approaches, such as spectral decomposition techniques and correlation between far-infrared luminosity and other tracers of star-formation, suggesting that far-infrared emission is originated from star-formation in host galaxies, even in the most energetic QSOs \citep[\eg][]{Netzer07a, Mullaney11a, Harrison15a}.
+} 
 Using the \citet{Kennicutt98a} relation and {\bf adopting} a \citet{Chabrier03a}
@@
 measure of the star formation efficiency. 
-{\bf We compute this ratio using the {\bf FIR}
-and CO luminosities {\bf ($L_\textrm{FIR}$/\Lp)}. The derived SFE is therefore independent of the magnification factor, the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$), and the
-IMF. }This, however, assumes that differential lensing between the {\bf CO and FIR} emission is negligible.
+{\bf We compute this ratio using the far-infrared
+and CO luminosities. The derived SFE is therefore independent of the magnification factor, the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$), and the
+IMF. }This, however, assumes that differential lensing between the CO and  {\bf far-infrared} emission is negligible.
 The resulting ratio is {\bf SFE$_\textrm{FIR}$\,=\,154\,$\pm$\,25\,\,\Lsun\,(\LpU)$^{-1}$}, this is comparable
@@
 
-\subsubsection{Dynamical Mass}
-Based on our \CO line measurement, we estimate the dynamical mass of SMM\,J0939 assuming that the molecular gas is virialized.
+\subsubsection{Physical Size and Dynamical Mass}
+{\bf 
+Our lens model infer a half-light radius of $r_s$\,$\sim$\,1\,kpc for the dust-emitting region in SMM\,J0939. This is comparable to those found in the 
+samples of SMGs with high resolution imaging.
+In particular, \citet{Simpson15a} report a radial extent of 1.2 kpc in a sample un-lensed SMGs with $S_{\rm 850}$ = 8$-$16 mJy, a similar size has also been reported by  \citet{Bussmann13a} of 1.5 kpc in a sample of {\it Herschel}$-$selected lensed SMGs with $S_{500} >$ 100 mJy.
+}
+
+We estimate the dynamical mass of SMM\,J0939 using our \CO line measurement and assuming that the molecular gas is virialized.
 With this assumption, we use an isotropic virial estimator \citep[\eg][]{Engel10a}, with the FWHM of the \CO line profile and the half-light radius from our lens model for $R_\textrm{eff}$, assuming that the dust emission traces the same emitting region as the CO.
 We find a dynamical mass of $M_\textrm{dyn}$ = (7.84\,$\pm$\,2.84)\,$\times$\,10$^{10}$\,\Msun, and a gas-to-dynamical mass fraction of $f_\textrm{gas-to-dyn}$ = 0.35\,$\pm$\,0.14, consistent with those of other SMGs \citep{Tacconi06a}.
-We note that a derived dynamical mass based on this assumption is likely to be biased towards low values, as the CO-emitting region {\bf that traces the cool gas} can be spatially more extended than the dust emitting region due to the low dust optical depth at larger radii.
-%\citep[\eg][]{Tacconi06a, Riechers11c,Riechers11d,Ivison11a}.
-{\bf This has been supported by recent observations.
-In particular, \citet{Tacconi06a} report a median FWHM size of 4.1\,$\pm$\,1.6 kpc based on \CO line measurements of their sample, whereas studies with spatially resolved \rot{1}{0} observations have additionally demonstrated that the cool gas regions are even more extended (R$_{\rm eff} \sim$ 7 kpc;  \citealt{Ivison11a}, see also \citealt{Riechers11c, Hodge13a}).
-For the physical size of dust-emitting regions, \citet{Simpson15a} recently report a spatial extent with radius of 1.2 kpc in a sample of 52 SMGs.
-% Adopting a physical size of 4.1 kpc, we find a dynamical mass of 3.7\,$\times$\,10$^{11}$\,\Msun.
- }
+We note that a derived dynamical mass based on this assumption is likely to be biased towards low values, as the CO-emitting region can be spatially more extended than the dust emitting region due to the low dust optical depth at larger radii.
+{\bf This is supported by recent studies, in which a range of CO source size ranging from $\sim$4$-$20 kpc has been found \citep{Tacconi06a, Ivison11a, Riechers11c, Hodge13a}}.
 
@@
 The detection of CO in SMM\,J0939
-implies a CO luminosity of \Lp\ = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU, suggesting the presence of a massive
+implies a CO luminosity of \Lp\ = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU, {\bf corresponding to a gas mass of 
+$M_{\rm gas}$\,=\,(2.7$\pm$0.6\,$\times$\,10$^{10}$(10.1/$\mu_\textrm{L}$ $\Msun$).
+This }
+suggests the presence of a massive
 molecular gas reservoir that fuels the star formation activity taking place at a rate of {\bf $\sim$\,526 \Msun~yr\pmOne}.
@@
 compare our findings for SMM\,J0939 
-with a sample of SMGs \citep[][hereafter B13]{Bothwell13a}, where their properties are listed in Table~\ref{tab:compareSMG}. This clearly demonstrates that SMM\,J0939 has properties similar
-to other SMGs studied to date except for its gas mass, which is slightly lower than the median found in the B13 sample. 
-This is unsurprising given that SMM\,J0939 is lensed with a magnification factor of $\sim$10, placing it on the fainter end of the CO line luminosity distribution when compared to un-lensed SMGs. 
+with a sample of SMGs which are selected at 850~$\micron$ and are typically unlensed or only weakly magnified \citep[][hereafter B13]{Bothwell13a}. 
+Their properties are listed in Table~\ref{tab:compareSMG}, which clearly demonstrates that SMM\,J0939 has properties similar
+to other SMGs studied to date.
 We note that the gas properties (CO luminosity and gas mass) of the SMGs in the B13 sample are derived based on the excitation condition found via CO spectral line energy distribution (SLED) modelling, which the authors find it to be very similar to that of the cosmic Eyelash.
-Given that the gas properties in the B13 sample are based on unresolved emission of various higher-$J$ CO transitions, we additionally compare SMM\,J0939 to two other exceptionally submm-bright,
+Given that the gas properties in their sample are based on unresolved emission of various higher-$J$ CO transitions, we additionally compare SMM\,J0939 to two other exceptionally submm-bright,
 strongly-lensed SMGs
-found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which are well-studied and their properties are derived using similar approach we employed in this paper.}
+found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which are well-studied and their properties are derived using similar approach employed in this paper.}
 
@@
 cosmic
-Eyelash. Such distinction is likely a result of our selection bias: while these sources appear similarly bright at 250 \micron, the lensing magnification
+Eyelash. Such distinction is likely a result of our selection bias: while these sources appear similarly bright at 250~\micron, the lensing magnification
 varies by a factor of $\sim$\,3. In particular, with the cosmic Eyelash having the highest lensing magnification among the
@@
 of various intrinsic properties, we find that 
-SMM\,J0939 is consistent with the ``typical" SMG population, with its intrinsic CO line luminosity, IR luminosity, gas mass,
-dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in ``typical" SMGs studied to data.
+SMM\,J0939 is consistent with the ``typical" SMG population, with its intrinsic CO line luminosity, IR luminosity, 
+dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in ``typical" SMGs studied to date.
 
@@
 therein]{Polletta11a}. 
-Among these obscured type-2 quasars, F10214 has the lowest molecular gas mass as well as SFR.
+Among these obscured quasars, F10214 has the lowest molecular gas mass as well as SFR.
 The fact that the gas mass of F10214 in their compilation was derived using \CO line emission \citep{Solomon05a} has a minor effect on the resulting low gas mass; \citet{Riechers11a} report
@@
 
-{\bf Our findings therefore suggest that SMM\,J0939 {\bf may be} transitioning from its short, star-bursting phase to the unobscured quasar phase in the proposed evolutionary link model \citep[\eg][]{Sanders88,Coppin08a,Simpson12a} given the presence of its obscured QSO and a massive gas reservoir with an immense SFR, coupled with the low depletion timescale of gas.
+{\bf 
+We note that the gas mass in SMM\,J0939 is slightly lower than the median in the B13 sample, which might be indicative of a 
+lower gas excitation than we have assumed. Yet, we find that the amount of gas in SMM\,J0939 is consistent with other type-2 quasars. 
+As such, given the presence of an obscured quasar and the overlap of properties 
+with both populations,
+%, in which SMM\,J0939 harbors a massive gas reservoir with an immense star formation rate and low depletion timescale of gas, 
+a physical interpretation might be that SMM\,J0939 is transitioning from its short, star-bursting phase to the unobscured quasar phase in the proposed evolutionary link model \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}.
+Further investigate on the gas excitation with spatially resolved \rot[CO]{1}{0} line measurements will provide a 
+more constraining representation of the amount of cold gas present in SMM\,J0939, as well as the impact of differential lensing, which will enable a better understanding of the two galaxy populations at high-redshifts.
 }
+
 % --> its short phase in the proposed evolutionary link  
@@
 \begin{acknowledgments}
+We thank the referee for providing constructive comments to improve this manuscript.
 We thank Shane Bussmann for providing the code {\sc uvmcmcfit} for lens modeling, sharing the SMA and VLA data, and for helpful discussions; Alex Conley for providing the code {\sc mbb\_emcee} for SED fitting.
@@
 
-%
+%\bibliographystyle{apj}
+%\bibliography{J0939}
+
 \begin{thebibliography}{}
@@
   217, 717
+
+\bibitem[{{Barger} {et~al.}(1998){Barger}, {Cowie}, {Sanders}, {Fulton},
+  {Taniguchi}, {Sato}, {Kawara}, \& {Okuda}}]{Barger98a}
+{Barger}, A.~J., {Cowie}, L.~L., {Sanders}, D.~B., {et~al.} 1998, \nat, 394,
+  248
 
@@
 {Bouch{\'e}}, N., {Cresci}, G., {Davies}, R., {et~al.} 2007, \apj, 671, 303
+
+\bibitem[{{Bussmann} {et~al.}(2013){Bussmann}, {P{\'e}rez-Fournon}, {Amber},
+  {Calanog}, {Gurwell}, {Dannerbauer}, {De Bernardis}, {Fu}, {Harris}, {Krips},
+  {Lapi}, {Maiolino}, {Omont}, {Riechers}, {Wardlow}, {Baker}, {Birkinshaw},
+  {Bock}, {Bourne}, {Clements}, {Cooray}, {De Zotti}, {Dunne}, {Dye}, {Eales},
+  {Farrah}, {Gavazzi}, {Gonz{\'a}lez Nuevo}, {Hopwood}, {Ibar}, {Ivison},
+  {Laporte}, {Maddox}, {Mart{\'{\i}}nez-Navajas}, {Michalowski}, {Negrello},
+  {Oliver}, {Roseboom}, {Scott}, {Serjeant}, {Smith}, {Smith}, {Streblyanska},
+  {Valiante}, {van der Werf}, {Verma}, {Vieira}, {Wang}, \&
+  {Wilner}}]{Bussmann13a}
+{Bussmann}, R.~S., {P{\'e}rez-Fournon}, I., {Amber}, S., {et~al.} 2013, \apj,
+  779, 25
 
@@
   e-prints, arXiv:1504.05256
+
+\bibitem[{Bussmann {et~al.}(2015)Bussmann, Leung, \& Conley}]{uvmcmcfit15a}
+Bussmann, S., Leung, T. K.~D., \& Conley, A. 2015, uvmcmcfit,
+  doi:10.5281/zenodo.27357
 
@@
 
+\bibitem[{{Hughes} {et~al.}(1998){Hughes}, {Serjeant}, {Dunlop},
+  {Rowan-Robinson}, {Blain}, {Mann}, {Ivison}, {Peacock}, {Efstathiou}, {Gear},
+  {Oliver}, {Lawrence}, {Longair}, {Goldschmidt}, \& {Jenness}}]{Hughes98a}
+{Hughes}, D.~H., {Serjeant}, S., {Dunlop}, J., {et~al.} 1998, \nat, 394, 241
+
 \bibitem[{{Ivison} {et~al.}(2011){Ivison}, {Papadopoulos}, {Smail}, {Greve},
@@
 
+\bibitem[{{Kirkpatrick} {et~al.}(2015){Kirkpatrick}, {Pope}, {Sajina},
+  {Roebuck}, {Yan}, {Armus}, {D{\'{\i}}az-Santos}, \&
+  {Stierwalt}}]{Kirkpatrick15a}
+{Kirkpatrick}, A., {Pope}, A., {Sajina}, A., {et~al.} 2015, \apj, 814, 9
+
 \bibitem[{{Lagache} {et~al.}(2005){Lagache}, {Puget}, \& {Dole}}]{Lagache05a}
@@
 {Micha{\l}owski}, M.~J., {Watson}, D., \& {Hjorth}, J. 2010, \apj, 712, 942
+
+\bibitem[{{Mullaney} {et~al.}(2011){Mullaney}, {Alexander}, {Goulding}, \&
+  {Hickox}}]{Mullaney11a}
+{Mullaney}, J.~R., {Alexander}, D.~M., {Goulding}, A.~D., \& {Hickox}, R.~C.
+  2011, \mnras, 414, 1082
 
@@
 {Neri}, R., {Genzel}, R., {Ivison}, R.~J., {et~al.} 2003, \apjl, 597, L113
+
+\bibitem[{{Netzer} {et~al.}(2007){Netzer}, {Lutz}, {Schweitzer}, {Contursi},
+  {Sturm}, {Tacconi}, {Veilleux}, {Kim}, {Rupke}, {Baker}, {Dasyra},
+  {Mazzarella}, \& {Lord}}]{Netzer07a}
+{Netzer}, H., {Lutz}, D., {Schweitzer}, M., {et~al.} 2007, \apj, 666, 806
 
@@
 
-\bibitem[{{Scoville}(2013)}]{Scoville13a}
-{Scoville}, N.~Z. 2013, {Evolution of star formation and gas}, ed.
-  J.~{Falc{\'o}n-Barroso} \& J.~H. {Knapen}, 491
-
 \bibitem[{{Simpson} {et~al.}(2012){Simpson}, {Smail}, {Swinbank}, {Alexander},
@@
 
+\bibitem[{{Simpson} {et~al.}(2012){Simpson}, {Smail}, {Swinbank}, {Alexander},
+  {Auld}, {Baes}, {Bonfield}, {Clements}, {Cooray}, {Coppin}, {Danielson},
+  {Dariush}, {Dunne}, {de Zotti}, {Harrison}, {Hopwood}, {Hoyos}, {Ibar},
+  {Ivison}, {Jarvis}, {Lapi}, {Maddox}, {Page}, {Riechers}, {Valiante}, \& {van
+  der Werf}}]{Simpson12a}
+{Simpson}, J.~M., {Smail}, I., {Swinbank}, A.~M., {et~al.} 2012, \mnras, 426,
+  3201
+
 \bibitem[{{Simpson} {et~al.}(2015){Simpson}, {Smail}, {Swinbank}, {Almaini},
@@
 ---. 2015, \apj, 799, 81
+
+\bibitem[{{Smail} {et~al.}(1997){Smail}, {Ivison}, \& {Blain}}]{Smail97a}
+{Smail}, I., {Ivison}, R.~J., \& {Blain}, A.~W. 1997, \apjl, 490, L5
 
@@
 
-The PDFs of the parameters in the optically thin model are shown in the right panel of Figure~\ref{fig:sedlikelihood}, the dust emissivity index ($\beta$) is highly anti-correlated with the observed-frame dust temperature ($T/(1+z)$), and the marginalized PDFs of all parameters are well-approximated by Gaussians --- the best-fit solution is prominent.
+The PDFs of the parameters in the optically thin models are shown in the right panel of Figure~\ref{fig:sedlikelihood}, the dust emissivity index ($\beta$) is highly anti-correlated with the observed-frame dust temperature ($T/(1+z)$), and the marginalized PDFs of all parameters are well-approximated by Gaussians --- the best-fit solution is prominent.
 We note that the best-fit emissivity in this model is unusually low among high-redshift galaxies ($\beta$ = 0.7$^{+0.2}_{-0.3}$, cf.
@@
 \hspace{-1.1cm}
-\caption{Correlation plots from the fitted SEDs, using an optically thick
-model (left), and an optically thin model (right). Marginalized posterior probability
+\caption{Correlation plots from the fitted SEDs, using optically thick
+models (left), and optically thin models (right). Marginalized posterior probability
 distributions of each

### 2016-01-13 mod1/manuscript/table_mbb.tex
add in necessary changes before moving table note to a column

\begin{deluxetable}{lcc}[tbpH]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{SED fitting results}
\tablehead{
\colhead{Parameters}      &
\colhead{Optically Thick} &
\colhead{Optically Thin}
}
\startdata
$\chi^2$                      & 2.25                     & 5.31                    \\
D.O.F                         & 2                        & 3                       \\
$T$                           & 63.1$^{+1.1}_{-1.3}$     & 52.0$^{+1.3}_{-1.2}$    \\
$\beta$                       & 1.9$^{+0.6}_{-0.5}$      & 0.7$^{+0.2}_{-0.3}$     \\
$\alpha$                      & 2.9$^{+0.3}_{-0.4}$      & 2.8$^{+0.2}_{-0.2}$     \\
$\lambda_0$\tna               & 248.7$^{+86.0}_{-123.8}$ & ---                     \\
$\lambda_{\rm peak}$ \tnb     & 254.7$^{+6.2}_{-6.1}$    & 301.4$^{+29.0}_{-30.1}$ \\
$f_{\rm norm,\ 500\mu m}$\tnc & 267.4$^{+16.7}_{-16.3}$  & 244.3$^{+15.3}_{-15.3}$ \\
$L_{\rm IR}$\tnd              & 88.5$^{+2.6}_{-2.6}$     & 89.2$^{+2.5}_{2.5}$     \\
$M_{\rm dust}$\tne            & 50.5$^{+20.4}_{-20.2}$   & 25.7$^{+3.9}_{-5.5}$
\enddata
% if each PDF is Gaussian, mean ~ best
% else mean != best
\label{tab:mbb}
\tablenotetext{a}{Rest-frame wavelength where $\tau_\nu$\,=\,1 in $\micron$}% at which the dust becomes optically thick; upper limit is 2000 $\micron$}
\tablenotetext{b}{Observed-frame wavelength of the SED peak in $\micron$}
\tablenotetext{c}{Observed-frame flux density at 500 $\micron$ in mJy}
\tablenotetext{d}{Rest-frame 8-1000 $\micron$ luminosity in 10$^{12}$ \Lsun}
\tablenotetext{e}{Dust mass in 10$^8$ M$_\odot$, derived assuming a standard absorption mass coefficient $\kappa$=2.64 m$^2$ kg$^{-1}$ at $\lambda$=125.0 $\micron$ \citep{Dunne03a}}
\tablecomments{Errors reported here are $\pm$1$\sigma$. $L_{\rm IR}$ and $M_{\rm d}$ are reported prior to lensing correction.}
\end{deluxetable}

### 2016-01-13 mod1/response.md
With DR's hand-written comments

@@
 
-> We picked out two apparently similarly bright gravitationally lensed
-  SMGs to show the ranges of SMGs properties, of which intrinsically
-  sit at faint ends of the luminosity distribution, and thus would not
-  have been studied in sensitivity-limited samples. In addition, these
-  are among the SMGs which are best-studied to date and their
-  properties are deriving using similar approach in this paper. Hence,
-  a comparison with these object will have relatively lower
-  uncertainties. We have added a compilation of SMG and type-2 QSOs
-  properties to the Table. Please see the table notes and comments for
-  details. We have incorporated a comparison to these sample-averaged
-  values in our conclusion as well.
-
--- need to re-write this. we would have seen at least two of these in
-   unlensed samples. just comparing since these are the most
-   well-known ones that similarly stick out from their submm fluxes
-   (>400mJy).
-
-   - differential lensing and ratios 
-   - if source is intrinsically fainter 
-   - write how we address issue raised --> reasons why we kept
+> We took into account this comment by adding a compilation of SMG and type-2 
+> QSOs properties to Table 4. Please see the table notes and comments for
+  details. We have therefore included a comparison to these sample-averaged
+  values in our conclusion. 
+  We initially picked out two well-studied and apparently similarly bright (submillimeter fluxes >400 mJy)gravitationally lensed
+  SMGs, to be able to investigate a broader range of physical properties - some of which are not well-constrained for the broader population.
+Thus, we decided to also keep this comparison in the paper.
 

### 2016-01-13 mod1/manuscript/ms.tex
With DR's hand-written comments

@@
 We find that the properties of the interstellar medium of
- SMM J0939+8315 overlap with both SMGs and type-2 quasars. Hence, SMM J0939+8315 may be transitioning from its star-bursting phase to the unobscured quasar phase in the 
-evolutionary link model, according in which this SMG represents an intermediate stage of present-day galaxies
+ SMM J0939+8315 overlap with both SMGs and type-2 quasars. Hence, SMM J0939+8315 may be transitioning from a star-bursting phase to an unobscured quasar phase as described by the 
+``evolutionary link'' model, according to which this system may represent an intermediate stage of present-day galaxies
 at an earlier epoch. 
@@
  wavelengths (L$_\textrm{IR} \sim$ 10$^{12}$ \Lsun) with high star formation rates \citep[SFR $\gtrsim$\,500\,\Msun yr\pmOne; see \eg reviews by][]{Blain02a, Lagache05a,Casey14a}.  
-{\bf Following the pioneering works in the discovery of this population \citep{Barger98a,Smail97a,Hughes98a}}, considerable amounts of effort have been invested into 
+{\bf Following the pioneering works in the discovery of this population \citep{Smail97a,Hughes98a,Barger98a}}, considerable amounts of effort have been invested into 
 obtaining large samples of SMGs by carrying out
@@
  as lensing amplifies the intrinsic fluxes of these sources, making them the brightest unveiled in large sky surveys \citep{Negrello10a,Vieira10a,Oliver12a}, and making follow-up studies considerably less time consuming.
-A particularly interesting and peculiar lensing system was discovered serendipitously in a study carried out with {\it Herschel}, in which
+A particularly interesting and peculiar lensing system was discovered serendipitously in a study carried out with the {\it Herschel Space Observatory}, in which
 a type-2 quasar host SMG --- SMM\,J0939+8315 (hereafter SMM\,J0939) is being lensed by the double-lobed Fanaroff-Riley
 Class II \citep*[FR-II; ][]{Fanaroff74} radio galaxy 3C220.3 {\bf at $z$\,=\,0.685, which has a
-companion galaxy B as seen in Keck 2$\micron$ and the {\it Hubble Space Telescope} 702nm images \citep[hereafter H14]{Haas14}}.
+companion galaxy ``B'' as detected in Keck 2.2$\micron$ and the {\it Hubble Space Telescope} 702nm images \citep[hereafter H14]{Haas14}}.
 SMM\,J0939 is currently one of the brightest known lensed
@@
  and He~{\scriptsize\sc II}~1640\AA\ line emission toward SMM\,J0939
- placed the redshift of this galaxy at $z$\,=\,2.221.
-Based on the line fluxes and spectral line widths of these AGN lines, H14 suggest the presence of an active galactic nucleus (AGN) in the form of a type-2 quasar in this SMG.}
+ place the redshift of this galaxy at $z$\,=\,2.221.
+Based on the spectral line fluxes and line widths, H14 suggest the presence of an obscured active galactic nucleus (AGN) in the form of a type-2 quasar in this SMG.}
 
@@
 emission start at $\pm$4$\sigma$, where $\sigma$\,=\,0.064 mJy beam\pmOne, and increment at steps of $\pm$2$^n\sigma$,
-where $n$ is a positive integer.{\bf The white crosses correspond to the centroid locations of the lensing knots detected in the SMA 1\,mm continuum emission (see Figure \ref{fig:mom0}).}
+where $n$ is a positive integer.{\bf The blue crosses correspond to the centroid locations of the lensing knots detected in the SMA 1\,mm continuum emission (see Figure \ref{fig:mom0}).}
 The central cross on each panel indicates the position of the radio core of 3C220.3. \label{fig:cont}}
@@
 details of the parametric lens model can be found in \citet{Bussmann15a}. 
-{\bf The surface mass densities of the two lensing galaxies, 3C220.3 and its companion galaxy B as mentioned in Section~\ref{sec:intro}, are described by singular isothermal ellipsoid profiles, and the source is assumed to have an
+{\bf The surface mass densities of the two lensing galaxies, 3C220.3 and its companion galaxy B, are described by singular isothermal ellipsoid profiles, and the source is assumed to have an
 elliptical Gaussian profile. }
@@
 Left: SMA 1\,mm continuum (red contours) overlaid on the best-fit model (grayscale image), assuming an elliptical Gaussian profile for the background SMG.
-The lenses are represented as black dots, the half-light area of the background source is represented as magenta ellipse, {\bf and the critical curves are represented as green curves.}
+The lenses are represented by the black dots, the half-light area of the background source is represented by the magenta ellipse, {\bf and the critical curves are represented by the green ellipses.}
 Right: Residual contours and image obtained by taking the Fourier transform of the difference between the SMA data and the best-fit model in the visibility plane.
@@
 The resulting best-fit model as shown in Figure\,\,\ref{fig:lens} shows no significant bowls in the residual
-image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
+image, and the knots (lensed emission) in the observed SMA data are reproduced well by the best-fit model.
 {\bf  Our best-fit model yields a magnification
 factor of $\mu_\textrm{L}$ = 10.13\,$\pm$\,1.38
-and a half-light radius of 0\farcs11 $\pm$ 0\farcs03, corresponding to a spatial extent of $\sim$0.9 kpc.} 
+and a half-light radius of $r_{s}$\,=\,0\farcs11 $\pm$ 0\farcs03, corresponding to $\sim$0.9 kpc at $z$\,=\,2.221.} 
 All best-fit
@@
 , and $\alpha$ is the mid-infrared power law spectral index. The overall fit is normalized using the observed-frame 500
-$\micron$ flux density, hence this becomes an additional parameter in the fit.
+$\micron$ flux density, hence this becomes an additional parameter ($f_{\rm norm,\ 500\mu m}$) in the fit.
 For both models, we impose an upper limit of 60 K on the observed-frame dust temperature ($T/(1+z)$), and an upper limit of 2.2 on
@@
 Owning to the positive K-correction blue-ward of the dust peak, in which 
-the foreground radio galaxy contributes a non-negligible amount to the MIR luminosity, we do not fit an AGN component.
+the foreground radio galaxy contributes a non-negligible amount to the MIR luminosity, we do not fit for a separate AGN component.
 Instead, we adopt a power-law to account for the MIR excess, which allows us to estimate the IR
-luminosity \citep{Casey12a, Riechers13a, Kirkpatrick15a}. }. 
+luminosity \citep[\eg][]{Casey12a, Riechers13a, Kirkpatrick15a}. }. 
 Assuming a dust absorption coefficient of $\kappa_{\nu}$ = 2.64\,\,m$^2$\,\,kg\pmOne\ at 125.0\,\,$
@@
 dust-enshrouded AGN is negligible.
-This assumption stems from the results of recent studies using various approaches, such as spectral decomposition techniques and correlation between far-infrared luminosity and other tracers of star-formation, suggesting that far-infrared emission is originated from star-formation in host galaxies, even in the most energetic QSOs \citep[\eg][]{Netzer07a, Mullaney11a, Harrison15a}.
+This assumption stems from the results of recent studies using various approaches, such as spectral decomposition techniques and correlation between far-infrared luminosity and other tracers of star-formation, suggesting that far-infrared emission dominantly originates from star-formation in host galaxies, even in the most energetic QSOs \citep[\eg][]{Netzer07a, Mullaney11a, Harrison15a}.
 } 
@@
 {\bf 
-Our lens model infer a half-light radius of $r_s$\,$\sim$\,1\,kpc for the dust-emitting region in SMM\,J0939. This is comparable to those found in the 
-samples of SMGs with high resolution imaging.
-In particular, \citet{Simpson15a} report a radial extent of 1.2 kpc in a sample un-lensed SMGs with $S_{\rm 850}$ = 8$-$16 mJy, a similar size has also been reported by  \citet{Bussmann13a} of 1.5 kpc in a sample of {\it Herschel}$-$selected lensed SMGs with $S_{500} >$ 100 mJy.
-}
+Our lens model suggests a half-light radius of $r_s$\,$\sim$\,1\,kpc for the dust-emitting region in SMM\,J0939.
+This is comparable to the half-light radii found other SMGs with high resolution imaging.
+Similar sizes have been reported by \citet{Bussmann13a}, who find typical radii of 1.5 kpc for a sample of {\it Herschel}$-$selected lensed SMGs with $S_{500\micron}\,>$\,100 mJy.
+Also, \citet{Simpson15a} report a radial extent of 1.2 kpc for a sample of un-lensed SMGs with $S_{850\micron}$ = 8$-$16 mJy.}
 
@@
 We find a dynamical mass of $M_\textrm{dyn}$ = (7.84\,$\pm$\,2.84)\,$\times$\,10$^{10}$\,\Msun, and a gas-to-dynamical mass fraction of $f_\textrm{gas-to-dyn}$ = 0.35\,$\pm$\,0.14, consistent with those of other SMGs \citep{Tacconi06a}.
-We note that a derived dynamical mass based on this assumption is likely to be biased towards low values, as the CO-emitting region can be spatially more extended than the dust emitting region due to the low dust optical depth at larger radii.
-{\bf This is supported by recent studies, in which a range of CO source size ranging from $\sim$4$-$20 kpc has been found \citep{Tacconi06a, Ivison11a, Riechers11c, Hodge13a}}.
+We note that a derived dynamical mass based on this assumption is likely to be biased towards low values, as the CO-emitting region can be apparently more extended than the dust emitting region
+ due to the low dust optical depth at larger radii. 
+{\bf This is supported by recent studies, in which CO source sizes ranging from $\sim$4$-$20 kpc have been found, which are larger than typical dust continuum sizes \citep{Tacconi06a, Riechers11c, Ivison11a, Hodge13a, Hodge15a}}.
 
@@
 compare our findings for SMM\,J0939 
-with a sample of SMGs which are selected at 850~$\micron$ and are typically unlensed or only weakly magnified \citep[][hereafter B13]{Bothwell13a}. 
-Their properties are listed in Table~\ref{tab:compareSMG}, which clearly demonstrates that SMM\,J0939 has properties similar
+with a sample of typically unlensed or only weakly magnified, 850~$\micron$$-$selected SMGs \citep[][hereafter B13]{Bothwell13a}. 
+Their properties are listed in Table~\ref{tab:compareSMG}, showing that SMM\,J0939 has properties similar
 to other SMGs studied to date. 
-We note that the gas properties (CO luminosity and gas mass) of the SMGs in the B13 sample are derived based on the excitation condition found via CO spectral line energy distribution (SLED) modelling, which the authors find it to be very similar to that of the cosmic Eyelash.
-Given that the gas properties in their sample are based on unresolved emission of various higher-$J$ CO transitions, we additionally compare SMM\,J0939 to two other exceptionally submm-bright,
-strongly-lensed SMGs
-found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which are well-studied and their properties are derived using similar approach employed in this paper.}
+The gas mass in SMM\,J0939 is slightly lower than the median in the B13 sample, but we cannot rule out the possibility that this difference is due to the different assumptions made for the gas excitation conditions.
+The gas properties (CO luminosity and gas mass) of the SMGs in the B13 sample are derived based on the assumption of typical excitation conditions found from CO spectral line energy distribution (SLED) modelling of the sample average, which the authors find them to be very similar to those of the cosmic Eyelash.
+Thus, we additionally compare SMM\,J0939 to two other well-studied, strongly-lensed SMGs
+with comparably high apparent submillimeter fluxes
+found at similar redshifts --- HLSW-01 and the cosmic Eyelash.
+The properties of these sources are derived using similar approaches to those employed in this paper. 
+}
 
@@
 , and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a
-factor of $\sim$\,1.5, but is nevertheless consistent within the measurement uncertainties.
+factor of $\sim$\,1.5, but is nevertheless consistent within the measurement uncertainties. {\bf We thus find that the gas mass in SMM\,J0939 is consistent with other type-2 quasars. }
 
 {\bf 
-We note that the gas mass in SMM\,J0939 is slightly lower than the median in the B13 sample, which might be indicative of a 
-lower gas excitation than we have assumed. Yet, we find that the amount of gas in SMM\,J0939 is consistent with other type-2 quasars. 
+While the gas mass in SMM\,J0939 is slightly lower than the median of SMGs in the B13 sample, we find it to be consistent with other type-2 quasars, suggesting a possible scenario in which the gas has been converted into stars and used for fueling the quasar.
 As such, given the presence of an obscured quasar and the overlap of properties 
-with both populations,
-%, in which SMM\,J0939 harbors a massive gas reservoir with an immense star formation rate and low depletion timescale of gas, 
-a physical interpretation might be that SMM\,J0939 is transitioning from its short, star-bursting phase to the unobscured quasar phase in the proposed evolutionary link model \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}.
-Further investigate on the gas excitation with spatially resolved \rot[CO]{1}{0} line measurements will provide a 
-more constraining representation of the amount of cold gas present in SMM\,J0939, as well as the impact of differential lensing, which will enable a better understanding of the two galaxy populations at high-redshifts.
+with both type-2 quasar and SMG populations,
+a physical interpretation might be that SMM\,J0939 is transitioning from a short, star-bursting phase to an unobscured quasar phase, consistent with the proposed evolutionary link model between dusty starbursts and quasars \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}.
 }
@@
 
-\bibitem[{{Bussmann} {et~al.}(2015){Bussmann}, {Riechers}, {Fialkov},
+\bibitem[{{Bussmann} {et~al.}(2015{\natexlab{a}})Bussmann, Leung, \& Conley}]{uvmcmcfit15a}
+Bussmann, S., Leung, T. K.~D., \& Conley, A. 2015, uvmcmcfit,
+  doi:10.5281/zenodo.27357
+
+\bibitem[{{Bussmann} {et~al.}(2015{\natexlab{b}}){Bussmann}, {Riechers}, {Fialkov},
   {Scudder}, {Hayward}, {Cowley}, {Bock}, {Calanog}, {Chapman}, {Cooray}, {De
@@
   e-prints, arXiv:1504.05256
-
-\bibitem[{Bussmann {et~al.}(2015)Bussmann, Leung, \& Conley}]{uvmcmcfit15a}
-Bussmann, S., Leung, T. K.~D., \& Conley, A. 2015, uvmcmcfit,
-  doi:10.5281/zenodo.27357
 

### 2016-01-13 mod1/manuscript/table_mbb.tex
With DR's hand-written comments

@@
-\begin{deluxetable}{lcc}[tbpH]
+\begin{deluxetable}{lccc}[tbpH]
 \tabletypesize{\scriptsize}
-\tablecolumns{3}
+\tablecolumns{4}
 \tablecaption{SED fitting results}
 \tablehead{
-\colhead{Parameters}      &
+\multicolumn{2}{c}{Parameters}      &
 \colhead{Optically Thick} &
@@
 \startdata
-$\chi^2$                      & 2.25                     & 5.31                    \\
-D.O.F                         & 2                        & 3                       \\
-$T$                           & 63.1$^{+1.1}_{-1.3}$     & 52.0$^{+1.3}_{-1.2}$    \\
-$\beta$                       & 1.9$^{+0.6}_{-0.5}$      & 0.7$^{+0.2}_{-0.3}$     \\
-$\alpha$                      & 2.9$^{+0.3}_{-0.4}$      & 2.8$^{+0.2}_{-0.2}$     \\
-$\lambda_0$\tna               & 248.7$^{+86.0}_{-123.8}$ & ---                     \\
-$\lambda_{\rm peak}$ \tnb     & 254.7$^{+6.2}_{-6.1}$    & 301.4$^{+29.0}_{-30.1}$ \\
-$f_{\rm norm,\ 500\mu m}$\tnc & 267.4$^{+16.7}_{-16.3}$  & 244.3$^{+15.3}_{-15.3}$ \\
-$L_{\rm IR}$\tnd              & 88.5$^{+2.6}_{-2.6}$     & 89.2$^{+2.5}_{2.5}$     \\
-$M_{\rm dust}$\tne            & 50.5$^{+20.4}_{-20.2}$   & 25.7$^{+3.9}_{-5.5}$
+$\chi^2$           &           & 2.25                     & 5.31                    \\
+D.O.F              &           & 2                        & 3                       \\
+$T$                & (K)           & 63.1$^{+1.1}_{-1.3}$     & 52.0$^{+1.3}_{-1.2}$    \\
+$\beta$            &           & 1.9$^{+0.6}_{-0.5}$      & 0.7$^{+0.2}_{-0.3}$     \\
+$\alpha$           &           & 2.9$^{+0.3}_{-0.4}$      & 2.8$^{+0.2}_{-0.2}$     \\
+$\lambda_0$\tna    & ($\micron$)          & 248.7$^{+86.0}_{-123.8}$ & ---             \\
+$\lambda_{\rm peak}$ \tnb  & ($\micron$)   & 254.7$^{+6.2}_{-6.1}$    & 301.4$^{+29.0}_{-30.1}$ \\
+$f_{\rm norm,\ 500\mu m}$\tnc & (mJy) & 267.4$^{+16.7}_{-16.3}$  & 244.3$^{+15.3}_{-15.3}$ \\
+$L_{\rm IR}$        & (10$^{12}$ \Lsun)      & 88.5$^{+2.6}_{-2.6}$     & 89.2$^{+2.5}_{2.5}$     \\
+$M_{\rm dust}$         & (10$^8$ M$_\odot$)   & 50.5$^{+20.4}_{-20.2}$   & 25.7$^{+3.9}_{-5.5}$
 \enddata
@@
 \label{tab:mbb}
-\tablenotetext{a}{Rest-frame wavelength where $\tau_\nu$\,=\,1 in $\micron$}% at which the dust becomes optically thick; upper limit is 2000 $\micron$}
-\tablenotetext{b}{Observed-frame wavelength of the SED peak in $\micron$}
-\tablenotetext{c}{Observed-frame flux density at 500 $\micron$ in mJy}
-\tablenotetext{d}{Rest-frame 8-1000 $\micron$ luminosity in 10$^{12}$ \Lsun}
-\tablenotetext{e}{Dust mass in 10$^8$ M$_\odot$, derived assuming a standard absorption mass coefficient $\kappa$=2.64 m$^2$ kg$^{-1}$ at $\lambda$=125.0 $\micron$ \citep{Dunne03a}}
+\tablenotetext{a}{Rest-frame wavelength where $\tau_\nu$\,=\,1}% at which the dust becomes optically thick; upper limit is 2000 $\micron$}
+\tablenotetext{b}{Observed-frame wavelength of the SED peak}
+\tablenotetext{c}{Observed-frame flux density at 500 $\micron$}
+\tablenotetext{d}{Rest-frame 8-1000 $\micron$ luminosity}
+\tablenotetext{e}{Derived assuming a standard absorption mass coefficient $\kappa$=2.64 m$^2$ kg$^{-1}$ at $\lambda$=125.0 $\micron$ \citep{Dunne03a}}
 \tablecomments{Errors reported here are $\pm$1$\sigma$. $L_{\rm IR}$ and $M_{\rm d}$ are reported prior to lensing correction.}

### 2016-01-13 Code/Plot_Image.py

@@ -42,10 +42,9 @@ SMA_max             = 0.00634805
 
 VLA_ra              = 1.448437499980E+02
 VLA_dec             = 8.325666666846E+01
-sizep               = 0.0025
 sizePcont_noise     = 0.020
 sizePLine           = 0.02 #0.012
-sizevla             = 0.0035
+sizevla             = 0.0029
 ra_center           = 144.84933
 dec_center          = 83.257175
 
@@ -93,7 +92,7 @@ fvla.show_grayscale(stretch='log', vmin=vla_min, vmax=vla_max, vmid=-0.001)
 
 flin = aplpy.FITSFigure(label['lin'][0], \
         figure=fig_line, subplot=[x0,row_a,width,dy])
-flin.show_colorscale(cmap=mpl.cm.jet, vmin=min_line, vmax=max_line-1, vmid=-15, stretch='log')
+flin.show_colorscale(cmap=mpl.cm.jet, vmin=min_line+1, vmax=max_line-1, vmid=-115, stretch='log')
 
 fSMA = aplpy.FITSFigure(label['SMA'][0], figure=fig_line, subplot=[x0+width+2*x_gap, row_a, width, dy])
 fSMA.show_grayscale(stretch='log', vmin=SMA_min, vmax=SMA_max, vmid=-0.1)
@@ -142,7 +141,7 @@ setup_scalebar(fSMA, lg_20kpc_bg, str('20kpc'))
 standard_plot_setup(fcont, ra_center, dec_center, sizePcont_noise) #, tc='white')
 standard_plot_setup(fvla, ra_center, dec_center, sizevla, tc='white')
 standard_plot_setup(flin, ra_center, dec_center, sizePLine)
-standard_plot_setup(fSMA, ra_center, dec_center, sizep, tc='white')
+standard_plot_setup(fSMA, ra_center, dec_center, sizevla, tc='white')
 # fcont.tick_labels.hide()
 fvla.axis_labels.hide()
 # flin.tick_labels.hide()

### 2016-01-13 mod1/response.md
from DR

@@
   code are indeed consistent with the earlier model reported by H14,
-  such that the results are only slightly improved. However, H14 did
+  such that the results are only modestly improved. However, H14 did
   not report the full range of best-fit parameters and uncertainties
@@
   modeling approach (and including a reference to the literature
-  instead), and we have moved the lens mass and consistent results
+  instead), and we have moved the lens masses and consistent results
   into Table 1 - which is used to briefly summarize the full range of
@@
   not have MIR measurements solely from the background SMG and due to
-  the positive K correction blue-ward of dust peak, the foreground radio
-  galaxy contributes a non-negligible amount to the MIR luminosity, we
-  therefore didn't fit an AGN component. Including an additional
-  component, and thus free parameters to the SED model will be
-  over-fitted due to the limited amount of data at hand. Instead our
-  SED model includes a power-law to the blue side of the dust peak,
-  which accounts for the MIR excess and allows us to estimate the IR
-  luminosity (Kirkpatrick+15, Riechers+13, Johnson+13, Casey+12). We
-  derived the SFR and other corresponding properties using the L_FIR,
-  (45-122.5), which is mostly due to SF-driven dust emission.
+  the positive K correction blue-ward of dust peak, the foreground
+  radio galaxy contributes a non-negligible amount to the MIR
+  luminosity, we therefore didn't fit an AGN component. Including an
+  additional component, and thus free parameters to the SED model will
+  be over-fitted due to the limited amount of data at hand. Instead
+  our SED model includes a power-law to the blue side of the dust
+  peak, which accounts for the MIR excess and allows us to estimate
+  the IR luminosity (Kirkpatrick+15, Riechers+13, Johnson+13,
+  Casey+12). We derived the SFR and other corresponding properties
+  using only L_FIR, (45-122.5µm), which is mostly due to SF-driven
+  dust emission.
 
@@
   sections reporting SFE, SFR, and SFRSD into one. We also shortened
-  the section.
+  the section, as suggested.
 
@@
 > We rephrased the introduction to show more clearly the evidence of
-  an AGN.
+  an AGN, as suggested.
 
@@
 > We added notes in the caption of Table 4 to recap all assumptions
-  used in deriving these quantities.
+  used in deriving these quantities, as suggested.
 
@@
 
-> We took into account this comment by adding a compilation of SMG and type-2 
-> QSOs properties to Table 4. Please see the table notes and comments for
-  details. We have therefore included a comparison to these sample-averaged
-  values in our conclusion. 
-  We initially picked out two well-studied and apparently similarly bright (submillimeter fluxes >400 mJy)gravitationally lensed
-  SMGs, to be able to investigate a broader range of physical properties - some of which are not well-constrained for the broader population.
-Thus, we decided to also keep this comparison in the paper.
+> We took into account this comment by adding a compilation of SMG and
+  type-2 QSOs properties to Table 4. Please see the table notes and
+  comments for details. We have therefore included a comparison to
+  these sample-averaged values in our conclusion.  We initially picked
+  out two well-studied and apparently similarly bright (submillimeter
+  fluxes >400 mJy) gravitationally lensed SMGs, to be able to
+  investigate a broader range of physical properties - some of which
+  are not as well-constrained for the broader population. Thus, we
+  decided to also keep this comparison in the paper.
 
@@
 
-> We updated the conclusions.
+> We updated the conclusions accordingly.
 
@@
 
-> We removed "New results" in the subject headings.
+> We removed "New results" in the subject headings, as suggested.
 
@@
   the same for both panels in the figure. We changed the critical line
-  color to green for better readability.
+  color to green for better readability, as suggested.
 
@@
 
-> We restructured the paragraph and added earlier discoveries.
+> We restructured the paragraph and added earlier discoveries, as
+  suggested.
 
@@
 
-> We added a sentence to the introduction section to elaborate on this, please see the revised manuscript.
+> We added a sentence to the introduction section to elaborate on
+  this, as suggested; please see the revised manuscript.
 

### 2016-01-13 mod1/manuscript/ms.tex
with DR's comments, re-submission to apj

@@
 {\tiny  \RevisionInfo}        % place it here
-\title{A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Qruasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3}
+\title{A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3}
 \author{T. K. Daisy Leung and Dominik A. Riechers}
@@
  a lensing- and excitation-corrected CO line luminosity of \Lp = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\LpU\ for the SMG, where $\mu_\textrm{L}$ is the lensing magnification factor inferred from our lens modeling.
- % performed on the 1\,mm continuum emission.
  This translates to a molecular gas mass of $M_\textrm{gas}$ = (2.7\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$)\,\Msun.
-Fitting spectral energy distribution models to the (sub)-millimeter data of this SMG yields a dust temperature of $T_\textrm{dust}$ =
-63.1$^{+1.1}_{-1.3}$\,K, a dust mass of $M_\textrm{dust}$ = (5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,(10.1/$\mu_\textrm{L}$)\,\Msun, and a total infrared luminosity of
+Fitting spectral energy distribution models to the (sub)-millimeter data of this SMG yields a dust temperature of $T$\,=\,63.1$^{+1.1}_{-1.3}$\,K, a dust mass of $M_\textrm{dust}$ = (5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,(10.1/$\mu_\textrm{L}$)\,\Msun, and a total infrared luminosity of
 $L_\textrm{IR}$ = (9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,(10.1/$\mu_\textrm{L}$)\,\Lsun.
@@
  SMM J0939+8315 overlap with both SMGs and type-2 quasars. Hence, SMM J0939+8315 may be transitioning from a star-bursting phase to an unobscured quasar phase as described by the 
-``evolutionary link'' model, according to which this system may represent an intermediate stage of present-day galaxies
+``evolutionary link'' model, according to which this system may represent an intermediate stage in the evolution of present-day galaxies
 at an earlier epoch. 
@@
 emission start at $\pm$4$\sigma$, where $\sigma$\,=\,0.064 mJy beam\pmOne, and increment at steps of $\pm$2$^n\sigma$,
-where $n$ is a positive integer.{\bf The blue crosses correspond to the centroid locations of the lensing knots detected in the SMA 1\,mm continuum emission (see Figure \ref{fig:mom0}).}
+where $n$ is a positive integer. {\bf The blue crosses correspond to the centroid locations of the lensing knots detected in the SMA 1\,mm continuum emission (see Figure \ref{fig:mom0}).}
 The central cross on each panel indicates the position of the radio core of 3C220.3. \label{fig:cont}}
@@
 Lens modeling is carried out in the visibility
-({\it uv-}) plane using an updated version the publicly available software {\sc uvmcmcfit} \citep{uvmcmcfit15a},
+({\it uv-}) plane using an updated version of the publicly available software {\sc uvmcmcfit} \citep{uvmcmcfit15a},
 details of the parametric lens model can be found in \citet{Bussmann15a}. 
@@
 This is in good agreement  with the
-values found in other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.
+values found for other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.
 
@@
 Our lens model suggests a half-light radius of $r_s$\,$\sim$\,1\,kpc for the dust-emitting region in SMM\,J0939.
-This is comparable to the half-light radii found other SMGs with high resolution imaging.
+This is comparable to the half-light radii found in other SMGs with high resolution imaging.
 Similar sizes have been reported by \citet{Bussmann13a}, who find typical radii of 1.5 kpc for a sample of {\it Herschel}$-$selected lensed SMGs with $S_{500\micron}\,>$\,100 mJy.
@@
 The gas mass in SMM\,J0939 is slightly lower than the median in the B13 sample, but we cannot rule out the possibility that this difference is due to the different assumptions made for the gas excitation conditions.
-The gas properties (CO luminosity and gas mass) of the SMGs in the B13 sample are derived based on the assumption of typical excitation conditions found from CO spectral line energy distribution (SLED) modelling of the sample average, which the authors find them to be very similar to those of the cosmic Eyelash.
-Thus, we additionally compare SMM\,J0939 to two other well-studied, strongly-lensed SMGs
+The gas properties (CO luminosity and gas mass) of the SMGs in the B13 sample are derived based on the assumption of typical excitation conditions found from CO spectral line energy distribution (SLED) modelling of the sample average, which the authors find to be very similar to those of the cosmic Eyelash.
+Thus, we additionally compare SMM\,J0939 in more detail to two other well-studied, strongly-lensed SMGs
 with comparably high apparent submillimeter fluxes
@@
 {\bf 
-While the gas mass in SMM\,J0939 is slightly lower than the median of SMGs in the B13 sample, we find it to be consistent with other type-2 quasars, suggesting a possible scenario in which the gas has been converted into stars and used for fueling the quasar.
+While the gas mass in SMM\,J0939 is slightly lower than the median of SMGs in the B13 sample, we find it to be consistent with other type-2 quasars, suggesting a possible scenario in which a significant fraction of the gas has already been converted into stars and used for fueling the quasar.
 As such, given the presence of an obscured quasar and the overlap of properties 
@@
 \bibitem[{{Bussmann} {et~al.}(2015{\natexlab{a}})Bussmann, Leung, \& Conley}]{uvmcmcfit15a}
-Bussmann, S., Leung, T. K.~D., \& Conley, A. 2015, uvmcmcfit,
+Bussmann, S., Leung, T. K.~D., \& Conley, A. 2015{\natexlab{a}}, uvmcmcfit,
   doi:10.5281/zenodo.27357
@@
   Bernardis}, {Farrah}, {Fu}, {Gavazzi}, {Hopwood}, {Ivison}, {Jarvis},
-  {Lacey}, {Loeb}, {Oliver}, {Perez-Fournon}, {Rigopoulou}, {Roseboom},
+  {Lacey}, {Loeb}, {Oliver}, {P{\'e}rez-Fournon}, {Rigopoulou}, {Roseboom},
   {Scott}, {Smith}, {Vieira}, {Wang}, \& {Wardlow}}]{Bussmann15a}
-{Bussmann}, R.~S., {Riechers}, D., {Fialkov}, A., {et~al.} 2015, ArXiv
-  e-prints, arXiv:1504.05256
+{Bussmann}, R.~S., {Riechers}, D., {Fialkov}, A., {et~al.} 2015{\natexlab{b}}, \apj, 812, 43
 

### 2016-01-13 mod1/response.md
strip off comments before resubmission

@@
 
-## 7
+7.
 - the discussion/conclusions should focus on what is new from this
@@
 > We adjusted the panel sizes as suggested, and marked the locations
-  of the peak emission from the SMA as white crosses on the right
+  of the peak emission from the SMA as blue crosses on the right
   panel in Figure 1.

### 2016-01-13 mod1/manuscript/ms.tex
strip off comments before resubmission

@@
 \slugcomment{Submitted to the ApJ}
-\input{changelog.tex}       % git revision hash, new command
+%\input{changelog.tex}
 
@@
 \begin{document}
-{\tiny  \RevisionInfo}        % place it here
+%{\tiny  \RevisionInfo}
 \title{A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3}
@@
 galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}.
-%This galaxy population was first detected 
-%$\sim$18 years ago with the Submillimeter Common User Bolometer Array (SCUBA) on the James
-%Clerk Maxwell Telescope (JCMT; \citealt{Smail97a, Hughes98a, Barger98a}). 
-Previous works %following this discovery
+Previous works
 have shown that SMGs
@@
   To characterize the physical properties of the gas reservoirs in the interstellar medium (ISM) where active star formation takes place, carbon monoxide ($^{12}$CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[see \eg reviews by][]{Solomon05a,Carilli13a}.{ \bf Observations of CO in SMGs
-  %at $z$\,$\sim$\,1\,--\,3 
   have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Frayer98a, Neri03a, Riechers11c, Riechers11d, Ivison11a, Bothwell13a}.}
@@
 elliptical Gaussian profile. }
-
-%We fix the phase center to coordinates ($\alpha$,\,$\delta$)\,\,(J2000) = (9$^{\rm h}$39$^{\rm m}$23\fs54,\,\,83\degr15\arcmin26\farcs10), where the
-%angular offsets of the lenses and source are referenced to this position. The primary lens (3C220.3) is
-%described by five free parameters: the angular offset ($\Delta \alpha_{\rm
-%lens0}$ and $\Delta \delta_\textrm{lens0}$) relative to
-%the chosen phase center ($\alpha$,\,$\delta$) in the image, the angular Einstein radius ($\theta_\textrm{E0}$), the
-%axial ratio ($q_\textrm{lens0}$), and the position angle ($\phi_\textrm{lens0}$). The secondary lens (companion B) is
-%described by three free parameters: $\theta_\textrm{E1}$, $q_\textrm{lens1}$, and $\phi_\textrm{lens1}$. The angular offset
-%of the secondary
-%lens is sampled with respect to that of
-%the primary lens ($\Delta \alpha_\textrm{lens0}$ and $\Delta \delta_\textrm{lens0}$); we therefore do not consider ($\Delta \alpha_\textrm{lens1}$ and $\Delta \delta_\textrm{lens1}$)  as free parameters.
-%The source (SMM\,J0939) is parameterized by
-%six parameters: the position of the source relative to the
-%primary lens ($\Delta \alpha_\textrm{s}$ and $\Delta
-%\delta_\textrm{s}$), the total intrinsic flux density ($S_\nu$), the
-%effective radius ($r_\textrm{s}\,=\,\sqrt{a_\textrm{s} b_\textrm{s}}$), the axial
-%ratio ($q_\textrm{s}$\,=\, $b_\textrm{s}/a_\textrm{s}$), and the position angle
-%($\phi_\textrm{s}$).The axial ratios of the lenses are restricted to $q_\textrm{lens} > 0.3$. 
-%The best-fit model is obtained by maximizing the
-%Gaussian likelihood function $ \mathcal{L} $ of the interferometric data in the Fourier domain.
-%We initialize 512
-%walkers and 6000 steps to identify the best-fit model parameters.
-
-%We initialize the positions and Einstein radii of both lenses, and the position of the source using those
- %from the best-fit lens model performed on Keck K-band (near-infrared) data (H14). For each of
-%these parameters, we impose a uniform prior in the range $\in\pm$3$\sigma$, where $\sigma$ is the uncertainty
-%reported in their paper. 
 \begin{figure}[!tbpH]
@@
 In contrast to what was found for F10214, we find that the properties
-(\eg FWHM of the CO line profile 
-%\footnote{The statistical mean is based on the line profile of the CO transition closest to $J$ = 4\,\rarr\,3 available for each source.}
-, M$_\textrm{gas}$
-%\footnote{The molecular gas mass for each source is derived based on its lowest-$J$ CO line emission available in literature.}
-, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a
+(\eg FWHM of the CO line profile, M$_\textrm{gas}$, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a
 factor of $\sim$\,1.5, but is nevertheless consistent within the measurement uncertainties. {\bf We thus find that the gas mass in SMM\,J0939 is consistent with other type-2 quasars. }
@@
 }
-
-% --> its short phase in the proposed evolutionary link  
-%fits in the proposed evolutionary paradigm \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}, in which it
 

### 2016-01-15 mod1/manuscript/ms.tex
remove bold font, submit to arxiv

@@
 
-\slugcomment{Submitted to the ApJ}
+\slugcomment{Accepted to the ApJ}
 %\input{changelog.tex}
@@
 the Combined Array for Research in Millimeter-wave Astronomy.
-SMM\,J0939+8315 hosts a type-2 quasar, and is gravitationally lensed by the radio galaxy 3C220.3 {\bf and its companion galaxy} at $z$ = 0.685.
+SMM\,J0939+8315 hosts a type-2 quasar, and is gravitationally lensed by the radio galaxy 3C220.3 and its companion galaxy at $z$ = 0.685.
 The 104~GHz continuum emission underlying the CO line is detected toward 3C220.3 with an integrated flux density of $S_\textrm{cont}$ = 7.4\,$\pm$\,1.4 mJy.
@@
 $L_\textrm{IR}$ = (9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,(10.1/$\mu_\textrm{L}$)\,\Lsun.
-{\bf
 We find that the properties of the interstellar medium of
@@
 at an earlier epoch.
- }
 \end{abstract}
@@
 \section{Introduction}\label{sec:intro}
-{\bf Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1\,--\,3 \citep{Chapman05a}, during the epoch of stellar mass and
+Submillimeter-selected galaxies (SMGs) are predominantly found at redshifts $z$\,$\sim$\,1\,--\,3 \citep{Chapman05a}, during the epoch of stellar mass and
 galaxy assembly, with a tail out to $z>$ 6 \citep{Riechers13a}.
@@
  wavelengths (L$_\textrm{IR} \sim$ 10$^{12}$ \Lsun) with high star formation rates \citep[SFR $\gtrsim$\,500\,\Msun yr\pmOne; see \eg reviews by][]{Blain02a, Lagache05a,Casey14a}.
-{\bf Following the pioneering works in the discovery of this population \citep{Smail97a,Hughes98a,Barger98a}}, considerable amounts of effort have been invested into
+Following the pioneering works in the discovery of this population \citep{Smail97a,Hughes98a,Barger98a}, considerable amounts of effort have been invested into
 obtaining large samples of SMGs by carrying out
   large sky surveys with (sub)-mm facilities such as the {\it Herschel Space Observatory} \citep[\eg H-ATLAS, SPT, HerMES; ][]{Eales10a,Carlstrom11a,Oliver12a}.
-  }
-
-  To characterize the physical properties of the gas reservoirs in the interstellar medium (ISM) where active star formation takes place, carbon monoxide ($^{12}$CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[see \eg reviews by][]{Solomon05a,Carilli13a}.{ \bf Observations of CO in SMGs
-  have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Frayer98a, Neri03a, Riechers11c, Riechers11d, Ivison11a, Bothwell13a}.}
+
+  To characterize the physical properties of the gas reservoirs in the interstellar medium (ISM) where active star formation takes place, carbon monoxide ($^{12}$CO) rotational lines have been commonly used as tracers due to its high abundance in the ISM as well as its low excitation energy; the ground state transition line thereby directly probes the cool gas that is essential to fuel star formation \citep[see \eg reviews by][]{Solomon05a,Carilli13a}.
+Observations of CO in SMGs
+  have demonstrated that these galaxies have large gas reservoirs typical of \textgreater 10$^{10}$\Msun \citep[\eg][]{Frayer98a, Neri03a, Riechers11c, Riechers11d, Ivison11a, Bothwell13a}.
 
@@
 a type-2 quasar host SMG --- SMM\,J0939+8315 (hereafter SMM\,J0939) is being lensed by the double-lobed Fanaroff-Riley
-Class II \citep*[FR-II; ][]{Fanaroff74} radio galaxy 3C220.3 {\bf at $z$\,=\,0.685, which has a
-companion galaxy ``B'' as detected in Keck 2.2$\micron$ and the {\it Hubble Space Telescope} 702nm images \citep[hereafter H14]{Haas14}}.
+Class II \citep*[FR-II; ][]{Fanaroff74} radio galaxy 3C220.3 at $z$\,=\,0.685, which has a
+companion galaxy ``B'' as detected in Keck 2.2$\micron$ and the {\it Hubble Space Telescope} 702nm images \citep[hereafter H14]{Haas14}.
 SMM\,J0939 is currently one of the brightest known lensed
 SMGs, with a lensing-magnified flux density of $S_\textrm{250\micron}$\,=\,440\,$\pm$\,15 mJy.
-{\bf Detections of C~{\scriptsize\sc IV}~1459\AA\
+Detections of C~{\scriptsize\sc IV}~1459\AA\
  and He~{\scriptsize\sc II}~1640\AA\ line emission toward SMM\,J0939
  place the redshift of this galaxy at $z$\,=\,2.221.
-Based on the spectral line fluxes and line widths, H14 suggest the presence of an obscured active galactic nucleus (AGN) in the form of a type-2 quasar in this SMG.}
+Based on the spectral line fluxes and line widths, H14 suggest the presence of an obscured active galactic nucleus (AGN) in the form of a type-2 quasar in this SMG.
 
@@
 emission start at $\pm$4$\sigma$, where $\sigma$\,=\,0.064 mJy beam\pmOne, and increment at steps of $\pm$2$^n\sigma$,
-where $n$ is a positive integer. {\bf The blue crosses correspond to the centroid locations of the lensing knots detected in the SMA 1\,mm continuum emission (see Figure \ref{fig:mom0}).}
-The central cross on each panel indicates the position of the radio core of 3C220.3. \label{fig:cont}}
+where $n$ is a positive integer.
+The blue crosses correspond to the centroid locations of the lensing knots detected in the SMA 1\,mm continuum emission (see Figure \ref{fig:mom0}).
+The central cross on each panel indicates the position of the radio core of 3C220.3.
+\label{fig:cont}}
 \end{figure*}
@@
 \subsection{Lens Modelling} \label{sec:Lens}
-To study the intrinsic properties of the background galaxy, we determine the magnification factor {\bf and the half-light radius of the dust region} by performing
+To study the intrinsic properties of the background galaxy, we determine the magnification factor and the half-light radius of the dust region by performing
 lens modeling on the SMA 1\,mm continuum data presented by H14 of this system.
@@
 details of the parametric lens model can be found in \citet{Bussmann15a}.
-{\bf The surface mass densities of the two lensing galaxies, 3C220.3 and its companion galaxy B, are described by singular isothermal ellipsoid profiles, and the source is assumed to have an
-elliptical Gaussian profile. }
+The surface mass densities of the two lensing galaxies, 3C220.3 and its companion galaxy B, are described by singular isothermal ellipsoid profiles, and the source is assumed to have an
+elliptical Gaussian profile. 
 \begin{figure}[!tbpH]
@@
 Left: SMA 1\,mm continuum (red contours) overlaid on the best-fit model (grayscale image), assuming an elliptical Gaussian profile for the background SMG.
-The lenses are represented by the black dots, the half-light area of the background source is represented by the magenta ellipse, {\bf and the critical curves are represented by the green ellipses.}
+The lenses are represented by the black dots, the half-light area of the background source is represented by the magenta ellipse, and the critical curves are represented by the green ellipses.
 Right: Residual contours and image obtained by taking the Fourier transform of the difference between the SMA data and the best-fit model in the visibility plane.
@@
 image, and the knots (lensed emission) in the observed SMA data are reproduced well by the best-fit model.
-{\bf  Our best-fit model yields a magnification
+ Our best-fit model yields a magnification
 factor of $\mu_\textrm{L}$ = 10.13\,$\pm$\,1.38
-and a half-light radius of $r_{s}$\,=\,0\farcs11 $\pm$ 0\farcs03, corresponding to $\sim$0.9 kpc at $z$\,=\,2.221.}
+and a half-light radius of $r_{s}$\,=\,0\farcs11 $\pm$ 0\farcs03, corresponding to $\sim$0.9 kpc at $z$\,=\,2.221.
 All best-fit
@@
 These properties are derived based on the SED fitting to the photometric data, \ie prior
-to lensing correction.{\bf We note that the dust mass is weakly constrained owing to the dearth of data in the {\bf rest-frame} FIR waveband.
+to lensing correction.
+We note that the dust mass is weakly constrained owing to the dearth of data in the rest-frame FIR waveband.
 As such, we investigate how the dust mass would be affected by fitting additional optically thick models with an upper limit of
  $\beta$ adjusted from 2.2 to 3.0.
-While the difference in each best-fit parameter between this scenario and the previous models (with an upper limit of $\beta$ = 2.2) is within 3\%, we find that the dust mass inferred from this best-fit SED model is boosted by a factor of $\sim$\,2.}
+While the difference in each best-fit parameter between this scenario and the previous models (with an upper limit of $\beta$ = 2.2) is within 3\%, we find that the dust mass inferred from this best-fit SED model is boosted by a factor of $\sim$\,2.
 \subsection{Physical Properties of the ISM in SMM\,J0939}
@@
  conversion factor ($\alpha_\mathrm{CO}$) when extrapolating from higher-$J$ CO lines. \par
-{\bf Recent observations} in high-redshift quasar hosts suggest that the ratio
+Recent observations in high-redshift quasar hosts suggest that the ratio
    is $R_\textrm{31}$\,$\sim$\,1 \citep{Riechers06a, Riechers11a}.
@@
 
-\subsubsection{{\bf Star Formation Rate \& Star Formation Efficiency}}
-{\bf
+\subsubsection{Star Formation Rate \& Star Formation Efficiency}
 We derive the SFR using the lensing-corrected far-infrared luminosity
@@
 This assumption stems from the results of recent studies using various approaches, such as spectral decomposition techniques and correlation between far-infrared luminosity and other tracers of star-formation, suggesting that far-infrared emission dominantly originates from star-formation in host galaxies, even in the most energetic QSOs \citep[\eg][]{Netzer07a, Mullaney11a, Harrison15a}.
-}
-Using the \citet{Kennicutt98a} relation and {\bf adopting} a \citet{Chabrier03a}
-stellar initial mass (IMF) function, {\bf we find a
+
+Using the \citet{Kennicutt98a} relation and adopting a \citet{Chabrier03a}
+stellar initial mass (IMF) function, we find a
 SFR$_\textrm{FIR}$\,=\,526\,$\pm$\,73 $M_
-\odot$ yr\pmOne.}
+\odot$ yr\pmOne.
 The starburst in SMM\,J0939 can be maintained at its
-current rate for a time that can be approximated by the gas depletion timescale, $\tau_\textrm{depl}$\,=\,$M_\textrm{gas}$/SFR{\bf , which assumes no replenishment of gas and feedbacks.}
-This corresponds to {\bf $\tau_\textrm{depl}$\,=\,52\,$\pm$\,8 Myr}, which is in good agreement with those found in other SMGs \citep[\eg][]{Greve05a}.
+current rate for a time that can be approximated by the gas depletion timescale, $\tau_\textrm{depl}$\,=\,$M_\textrm{gas}$/SFR, which assumes no replenishment of gas and feedbacks.
+This corresponds to $\tau_\textrm{depl}$\,=\,52\,$\pm$\,8 Myr, which is in good agreement with those found in other SMGs \citep[\eg][]{Greve05a}.
 
@@
 measure of the star formation efficiency.
-{\bf We compute this ratio using the far-infrared
+We compute this ratio using the far-infrared
 and CO luminosities. The derived SFE is therefore independent of the magnification factor, the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$), and the
-IMF. }This, however, assumes that differential lensing between the CO and  {\bf far-infrared} emission is negligible.
-The resulting ratio is {\bf SFE$_\textrm{FIR}$\,=\,154\,$\pm$\,25\,\,\Lsun\,(\LpU)$^{-1}$}, this is comparable
+IMF. This, however, assumes that differential lensing between the CO and far-infrared emission is negligible.
+The resulting ratio is SFE$_\textrm{FIR}$\,=\,154\,$\pm$\,25\,\,\Lsun\,(\LpU)$^{-1}$, this is comparable
 to those found in ``typical" SMGs \citep{Greve05a,Tacconi06a,Riechers11c}.
 
-{\bf We compute the surface densities by dividing half the SFR and gas mass by the area subtended by the half-light
+We compute the surface densities by dividing half the SFR and gas mass by the area subtended by the half-light
 radius \citep[\eg][]{Genzel10a, Harrison15a}, yielding
-$\Sigma_\textrm{SF}$ = 106  \Msun~yr\pmOne~kpc$^{-2}$} and $\Sigma_\textrm{gas}$ = 5.48\,$\times$\,10$^9$ \Msun~kpc$^{-2}$, respectively.
-These results are in good agreement with values typical for SMGs {\bf \citep{Tacconi06a, Hodge15a}. }  % compared using their conversion
+$\Sigma_\textrm{SF}$ = 106  \Msun~yr\pmOne~kpc$^{-2}$ and $\Sigma_\textrm{gas}$ = 5.48\,$\times$\,10$^9$ \Msun~kpc$^{-2}$, respectively.
+These results are in good agreement with values typical for SMGs \citep{Tacconi06a, Hodge15a}. 
 The inferred surface densities of SMM\,J0939 follow a universal Schmidt-Kennicutt relation between the star formation rate
@@
 \subsubsection{Physical Size and Dynamical Mass}
-{\bf
 Our lens model suggests a half-light radius of $r_s$\,$\sim$\,1\,kpc for the dust-emitting region in SMM\,J0939.
@@
 Similar sizes have been reported by \citet{Bussmann13a}, who find typical radii of 1.5 kpc for a sample of {\it Herschel}$-$selected lensed SMGs with $S_{500\micron}\,>$\,100 mJy.
-Also, \citet{Simpson15a} report a radial extent of 1.2 kpc for a sample of un-lensed SMGs with $S_{850\micron}$ = 8$-$16 mJy.}
+Also, \citet{Simpson15a} report a radial extent of 1.2 kpc for a sample of un-lensed SMGs with $S_{850\micron}$ = 8$-$16 mJy.
 
@@
  due to the low dust optical depth at larger radii.
-{\bf This is supported by recent studies, in which CO source sizes ranging from $\sim$4$-$20 kpc have been found, which are larger than typical dust continuum sizes \citep{Tacconi06a, Riechers11c, Ivison11a, Hodge13a, Hodge15a}}.
+This is supported by recent studies, in which CO source sizes ranging from $\sim$4$-$20 kpc have been found, which are larger than typical dust continuum sizes \citep{Tacconi06a, Riechers11c, Ivison11a, Hodge13a, Hodge15a}.
 
@@
 The detection of CO in SMM\,J0939
-implies a CO luminosity of \Lp\ = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU, {\bf corresponding to a gas mass of
+implies a CO luminosity of \Lp\ = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU, corresponding to a gas mass of
 $M_{\rm gas}$\,=\,(2.7$\pm$0.6\,$\times$\,10$^{10}$(10.1/$\mu_\textrm{L}$ $\Msun$).
-This }
+This 
 suggests the presence of a massive
-molecular gas reservoir that fuels the star formation activity taking place at a rate of {\bf $\sim$\,526 \Msun~yr\pmOne}.
-If the star forming activity continues at the current rate, the gas reservoir will be depleted within {\bf $\lesssim$~52 Myr,}
+molecular gas reservoir that fuels the star formation activity taking place at a rate of $\sim$\,526 \Msun~yr\pmOne.
+If the star forming activity continues at the current rate, the gas reservoir will be depleted within $\lesssim$~52 Myr,
 which is consistent with the short timescales found in other SMGs \citep{Greve05a}.
@@
 
-{\bf We
+We
 compare our findings for SMM\,J0939
@@
 The properties of these sources are derived using similar approaches to those employed in this paper.
-}
-
-{\bf As shown in Table~\ref{tab:compareSMG},} while the cosmic Eyelash has the least amount of molecular gas, as well as
+
+As shown in Table~\ref{tab:compareSMG}, while the cosmic Eyelash has the least amount of molecular gas, as well as
 the
@@
 
-{\bf Since SMM\,J0939 also hosts a type-2 quasar, we compare its properties}
+Since SMM\,J0939 also hosts a type-2 quasar, we compare its properties
 against those of eight CO-detected obscured AGNs at $z$ = 1.6\,$-$\,2.8 \citep[][and references
@@
 (\eg FWHM of the CO line profile, M$_\textrm{gas}$, and SFE) of SMM\,J0939 are similar to the statistical means, except for the SFR, which is lower by a
-factor of $\sim$\,1.5, but is nevertheless consistent within the measurement uncertainties. {\bf We thus find that the gas mass in SMM\,J0939 is consistent with other type-2 quasars. }
-
-{\bf
+factor of $\sim$\,1.5, but is nevertheless consistent within the measurement uncertainties. We thus find that the gas mass in SMM\,J0939 is consistent with other type-2 quasars.
+
 While the gas mass in SMM\,J0939 is slightly lower than the median of SMGs in the B13 sample, we find it to be consistent with other type-2 quasars, suggesting a possible scenario in which a significant fraction of the gas has already been converted into stars and used for fueling the quasar.
@@
 a physical interpretation might be that SMM\,J0939 is transitioning from a short, star-bursting phase to an unobscured quasar phase, consistent with the proposed evolutionary link model between dusty starbursts and quasars \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}.
-}
 
@@
 parameter of the best-fit solution between these two scenarios is less than 3\%, except for the dust mass, which is boosted by a factor of $\sim$\,2. This is
-unsurprising given the dearth of data in the {\bf rest-frame FIR wavebands}, leading to a weakly constrained emissivity, and thus, inferred dust mass.
+unsurprising given the dearth of data in the rest-frame FIR wavebands, leading to a weakly constrained emissivity, and thus, inferred dust mass.
 In our analysis, we employ the best-fit parameters and the corresponding inferred properties (dust mass, and IR luminosity) from the former, where a tighter constraint is imposed on $\beta$.

### 2016-01-20 mod1/manuscript/ms.tex
1459 to 1549

@@
 SMGs, with a lensing-magnified flux density of $S_\textrm{250\micron}$\,=\,440\,$\pm$\,15 mJy.
-Detections of C~{\scriptsize\sc IV}~1459\AA\
+Detections of C~{\scriptsize\sc IV}~1549\AA\
  and He~{\scriptsize\sc II}~1640\AA\ line emission toward SMM\,J0939
